### 2021-03-10 latex/notes.tex
update

\documentclass[twocolumn]{article}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
\usepackage[utf8]{inputenc}

\newcommand{\n}[1]{\ensuremath{\nu_{#1}}}
\newcommand{\na}{\ensuremath{\nu_\alpha}}
\newcommand{\nb}{\ensuremath{\nu_\beta}}
\newcommand{\ana}{\ensuremath{\bar{\nu}_\alpha}}
\newcommand{\an}[1]{\ensuremath{\bar{\nu}_{\text{#1}}}}
\newcommand{\anb}{\ensuremath{\bar{\nu}_\beta}}
\renewcommand{\a}{\ensuremath{\alpha}}
\renewcommand{\b}{\ensuremath{\beta}}
\newcommand{\ab}{\ensuremath{\alpha\beta}}

\renewcommand{\ne}{\ensuremath{\nu_e}}
\newcommand{\nm}{\ensuremath{\nu_\mu}}
\newcommand{\nt}{\ensuremath{\nu_\tau}}
\newcommand{\ns}{\ensuremath{\nu_s}}

\newcommand{\nee}{\ensuremath{\nu_e \to \nu_e}}
\newcommand{\nem}{\ensuremath{\nu_e \to \nu_\mu}}
\newcommand{\net}{\ensuremath{\nu_e \to \nu_\tau}}
\newcommand{\nes}{\ensuremath{\nu_e \to \nu_s}}

\newcommand{\nme}{\ensuremath{\nu_\mu \to \nu_e}}
\newcommand{\nmm}{\ensuremath{\nu_\mu \to \nu_\mu}}
\newcommand{\nmt}{\ensuremath{\nu_\mu \to \nu_\tau}}
\newcommand{\nms}{\ensuremath{\nu_\mu \to \nu_s}}

\newcommand{\nte}{\ensuremath{\nu_\tau \to \nu_e}}
\newcommand{\ntm}{\ensuremath{\nu_\tau \to \nu_\mu}}
\newcommand{\ntt}{\ensuremath{\nu_\tau \to \nu_\tau}}
\newcommand{\nts}{\ensuremath{\nu_\mu \to \nu_s}}

\renewcommand{\th}[1][]{%
  \theta\ifx\\#1\\\else_\text{#1}\fi
}
\newcommand{\thm}[1][]{%
  \theta^\text{M}\ifx\\#1\\\else_\text{#1}\fi
}
\renewcommand{\t}[1]{\ensuremath{\text{{#1}}}}
\newcommand{\avg}[1]{\ensuremath{\left\langle {#1} \right \rangle}}
\newcommand*{\dm}[1][]{%
  \Delta m^2\ifx\\#1\\\else_\text{#1}\fi
}

\begin{document}

\section{Notes from~\cite{IC2012}}.

DeepCorelowers the IC neutrino energy threshold to 10 GeV.
DC sits 2100 m below the ice, beneath the IC array.
It uses the existing IC array as a "veto" against the background downward cosmic muons. Together with increased module density, better PMTs, clear ice, and this "veto", DC improves the sensitivity.

There is a dust layer between 2000 and 2100 m that DC tries to avoid. There are no DOMs there because of the significant scattering of light. Instead, the remaining DOMs are placed directly above this region in a higher density.

\section{Notes from~\cite{giunti}}
\subsection*{5.1 Weak interactions}
Leptonic charged current
\begin{align}
  j^\rho_{Z,\nu} = 2\sum_{\alpha = e,\mu,\tau} \bar{\nu}_{\alpha L} \gamma^\rho \ell_{\alpha L}
= \sum_{\alpha = e,\mu,\tau} \bar{\nu}_\alpha \gamma^\rho(1-\gamma^5)\ell_\alpha
\end{align}
Leptonic charged current weak interaction Lagrangian
\begin{align}
  \mathcal{L}^{(CC)}_{\mathrm{int,L}} = - \frac{g}{2\sqrt{2}}\left( j^\rho_{W,L}W_\rho + {j^\rho_{W,L}}^{\dagger} W^\dagger_\rho \right)
\end{align}

Neutrino neutral current
\begin{align}
  j^\rho_{Z,\nu} = \sum_{\alpha = e,\mu,\tau} \bar{\nu}_{\alpha L} \gamma^\rho \nu_{\alpha L}
= \frac{1}{2} \sum_{\alpha = e,\mu,\tau} \bar{\nu}_\alpha \gamma^\rho(1-\gamma^5)\na 
\end{align}
Neutrino neutral current weak interaction Lagrangian
\begin{align}
  \mathcal{L}_{\mathrm{I}, \nu}^{(\mathrm{NC})}=-\frac{g}{2 \cos \vartheta_{\mathrm{W}}} j_{Z, \nu}^{\rho} Z_{\rho}
\end{align}

To lowest perturbation order, neutrinos only interact with free leptons, whose interaction amplitudes can be calculated exactly.

\subsection*{5.3 Neutrino-nucleon scattering}
When considering nucleon scatterings, we need the parton distribution functions of the nucleon. We use the quark-parton model of hadrons. According to this model, a nucleon is a composite system of
three valence quarks and a sea of quark–antiquark pairs of all flavors.

\subsection*{6.1 Dirac masses}
Neutrino masses might be a low-energy manifestation of BSM physics. Their smallness might be due to a high-energy scale, perhaps for force unification (related to see-saw in some way).

Introduce right-handed components $\nu_{\alpha R}$ to the SM. The "Dirac neutrino" masses are then generated by the familiar Higgs mechanism, $m_k = y^\nu_k v / \sqrt{2}$. We then eliminate the asymmetry between the lepton and quark sectors. Since they are right-handed, the fields $\nu_{\alpha R}$ are singlets of both $SU(3)_C \times SU(2)_L$ and the electroweak $SU(2)_L \times U(1)_Y$, so they are invariant under the SM symmetries.

We can also construct sterile neutrinos from the left-handed chiral fields $\tilde{\nu}_{\alpha L} = \nu^C_{\alpha R}$. As long as they are singlets under the SM symmetries, they are per definition sterile. However, convention is calling all sterile fields right-handed. Chiral fermion fields are the building block of the SM.

The only characteristic that distinguishes the three charged
leptons is their mass and the flavor of a charged lepton is identified by measuring its
mass. Neutrinos are detected indirectly by observing the flavor of the lepton in weak interactions, so "flavor neutrinos are not required to have a definite mass", so instead they are superpositions of neutrinos in their mass eigenstates.

\subsection*{6.2 Majorana masses}
If $q \neq 0$, $\psi$ and $\psi^C$ obey different equations. Thus, $\psi \neq \psi^C$ and we don't have Majorana particles. Majorana spinors are simpler (only two components) than Dirac spinors, so Majorana neutrino's might be preferable due to Occhams razor. BSM neutrinos are usually Majorana. Dirac vs Majorana neutrinos can't be distinguished from neutrino oscillations, since the oscillations are kinematic phenomena. Dirac and Majorana are kinematic ally equivalent since they satisfy the same energy-momentum dispersion relation.

It is important, however, to realize that the SM cannot be considered as
the final theory of everything, but only as an effective low-energy theory which is
the low-energy product of the symmetry breaking of a high-energy unified theory. The Lagrangian has energy dimension 4, so a coupling constant of a dimension $d$ operator is proportional to $\mathcal{M}^{4-d}$ of the high-energy theory. This dependence suppressed the low-energy effect of SM physics. A Majorana mass can be expressed in the Lagrangian as 
\begin{align*}
  \mathcal{L}_{5}=\frac{g}{\mathcal{M}}\left(L_{L}^{T} \tau_{2} \Phi\right) \mathcal{C}^{\dagger}\left(\Phi^{T} \tau_{2} L_{L}\right)+\mathrm{H.c.}
\end{align*}
which is proportional only to $\mathcal{M}^{-1}$. While not renormalizable in SM, the study of neutrino masses provides the most accessible low-energy window on BSM physics. A high-energy GUT can bleed into the low-energy SM through non-renormalizable Lagrangian terms, whose effects are suppressed by the coupling constants.

The Majorana mass term 
\begin{align*}
  \mathcal{L}_{\mathrm{mass}}^{\mathrm{M}}=\frac{1}{2} n_{L}^{T} \mathcal{C}^{\dagger} M \boldsymbol{n}_{L}+\mathrm{H.c.}=\frac{1}{2} \sum_{k=1}^{3} m_{k} \nu_{kL}^{T} \mathcal{C}^{\dagger} \n{k L}+\mathrm{H.c.}
\end{align*}
is not invariant under the global $U(1)$ gauge transformation
\begin{align*}
  \n{k L} \to e^{i \varphi} \n{k L}\,.
\end{align*}
This implies a violation of the total lepton number. Moreover, this asymmetry means that the Majorana mixing matrix has three physical CP-violating phases, apart from just one in the Dirac case. Thus, the $3 \times 3$ Majorana mixing matrix depends of three mixing angles and three physical CP-violating phases.

These can be grouped as the Dirac phase (three mixing angles and one phase) and as the Majorana phase (two phases):
$U=U^D D^M$
$U^D$ has similarities to the quark mixing matrix CKM. $D^M$ is usually parametrized as 
\begin{align*}
  \text{diag}(1, e^{i \lambda_2},e^{i \lambda_3})
.\end{align*}

If only $\nu_L$ exists, the neutrino Lagrangian only contains the Majorana mass term (which is not invariant under $SU(2)_L \times U(1)_Y$)
\begin{align*}
  \mathcal{L}^L_\text{mass} = \frac{1}{2} m_L \n{L}{T} \mathcal{C}^\dagger \n{L} + \text{H.c.}\,.
\end{align*}
If $\nu_R$ also exists, we can have both the Dirac and Majorana mass terms in the neutrino Lagrangian:
\begin{align*}
  \mathcal{L}^D_\text{mass} &= -m_D \an{R} \n{L} + \text{H.c.} \\
  \mathcal{L}^R_\text{mass} &= \frac{1}{2}m_R \n{R}{T} \mathcal{C}^\dagger \n{R} + \text{H.c.}\,.
\end{align*}
Together, we can then have the general Dirac-Majorana neutrino mass term 
\begin{align*}
  \mathcal{L}^{D+M} = \mathcal{L}^D + \mathcal{L}^L + \mathcal{L}^R\,,
\end{align*}
which through calculations implies that massive neutrinos are Majorana if we have a Dirac-Majorana mass term.

Conclusions:
\begin{itemize}
  \item With one generation of $\nu_L$ and $\nu_R$, there are two massive Majorana fields $\n{1}$ and $\n{2}$
  \item Convention: refer to $\nu_L$ and $\nu_R^C$ as the left-handed fields in the flavor basis.
  \item Mixing between $\nu_L$ and $\nu_R^C$ implies active-sterile neutrino oscillations.
\end{itemize}

\subsection{Weak interactions}
The active field $\nu_L$ and the sterile field $\nu_R$ are linear combinations of the same (massive) neutrino fields $\nu_{1L}$ and $\nu_{2L}$. CC interactions create superpositions of these, which we can see from the CC Langrangian
\begin{align*}
  \mathcal{L}^\text{CC}_\text{int} = -\frac{g}{\sqrt{2}} \sum_{k=1,2} (U^*_{1k}\bar{\nu}_{kL}\gamma^\mu \ell_L W_\mu + U_{1k}\bar{\ell}_L \gamma^\mu \nu_{kL} W^\dagger_\mu)
\end{align*}
Depending on their masses, we get a linear combination of active and sterile neutrinos, with a oscillatory probability of detecting the active part. The sterile part manifests itself through a survival probability of active neutrinos smaller than one.

For NC, we can have transitions among different massive neutrinos since we have the Lagrangian
\begin{align*}
  \mathcal{L}^\text{NC}_\text{int} = \frac{-g}{2\cos{\theta_W}} \sum_{k,j=1,2} U^*_{1k}U_{1j} \bar{\nu}_{kL}\gamma^\mu \nu_{jL} Z_\mu
\end{align*}

\subsection{CP invariance}
A real mass matrix implies CP invariance. The mixing matrix $U$ can contain imaginary elements while maintaining CP invariance. The column matrix of left-handed fields transforms as 
\begin{align*}
  N_L \overset{\text{CP}}{\to} \cup_\text{CP} N_L \cup_{\mathrm{CP}}^{-1} = i \gamma^0 C \bar{N}_L^T
\end{align*}
Likewise, the chiral left-handed fields $n_L$ $(N_L = Un_L)$ transform as
\begin{align*}
  n_L \overset{\text{CP}}{\to} \cup_\text{CP} n_L \cup_{\mathrm{CP}}^{-1} = i U^\dagger U^* \gamma^0 C \bar{n}_L^T = i (\rho \mathcal{O}^T \mathcal{O}\rho)^* \gamma^0 C \bar{n}_L^T = i \rho^2 \gamma^0 C \bar{n}_L^T\,,
\end{align*}
so the  CP parities of the massive Majorana fields are determined by the phases $\rho_k$ as
\begin{align*}
  \chi^\text{CP}_k = i \rho^2_k\,.
\end{align*}
Finally, the column matrix $n = n_L + n_L^C$ transforms as
\begin{align*}
  n \overset{\text{CP}}{\to}  i \rho^2 \gamma^0 n\,.
\end{align*}
So a Majorana neutrino has imaginary CP parity with sign determined by $\rho^2_k$
\begin{itemize}
  \item If $m_L = m_R = 0$, we have a Dirac field which is equivalent to two Majorana fields with the
same mass and opposite CP parities. A Dirac field has a definite CP parity $\chi^\text{CP} = i$.
  \item If $\abs{m_L}, m_R \ll m_D$, we have pseudo-Dirac neutrinos which are Majorana. 
  \item If $m_D \ll m_R, \quad m_L = 0$, we have the see-saw $m_1 \simeq \frac{m_D^2}{m_R}, m_2 \simeq m_R$, where the heavy mass of $\nu_2$ is responsible for the light mass of $\nu_1$. They have a small mixing angle, which implies that $\nu_1$ mainly consists of $\nu_L$ and $v_2$ mainly of $\nu_R$. 
\end{itemize}

The assumption $m_L = 0$ is "natural" since $m_L$ is forbidden in SM. $m_D$ can be generated by the Higgs, and is thus proportional to the symmetry-breaking scale (electroweak) \SI{e2}{GeV}. So the symmetries of SM "protects" $m_D$, while $m_R$ (being a singlet of the SM symmetries) is not. If $m_R$ is generated by BSM physics, $\nu_R$ can belong to a non-trivial multiplet of their symmetries. Then, $m_R$ is protected by the high-energy theory and can have a GUT scale (\SIrange{e14}{e16}{GeV}). Thus, the see-saw model produces the ratio $m_D/m_R \sim 10^{-14}-10^{-12}$.

\subsection*{7 Neutrino oscillations}
Neutrinos in oscillation experiments are ultrarelativistic. Only neutrinos with energy lager than 100 keV can be detected.
The number of massive neutrinos are equal to of greater than three. If it is greater than three, the additional neutrinos in the flavor basis are sterile.

Plane wave computations lead to the transition probability (using $t \approx L$ for astronomical distances)

\begin{align*}
  P_{\na \to \nu_\beta} 
  &= \sum_{k,j} U^*_{\alpha k} U_{\beta k} U_{\alpha j} U^*_{\beta j} \exp\left( -i \frac{\Delta m_{kj}^2 L}{2E}\right) \\
  &= \sum_k \abs{U_{\alpha k}}^2 \abs{U_{\beta k}^2} \\
  & \qquad + 2 \text{Re}\sum_{k>j} U^*_{\alpha k} U_{\beta k} U_{\alpha j} U^*_{\beta j} \exp \left( -2\pi i \frac{L}{L^\text{osc}_{kj}}\right) \\
  &= \delta_{\alpha \beta} - 4\sum_{k > j} \text{Re}[U^*_{\alpha k} U_{\beta k} U_{\alpha j} U^*_{\beta j}] \sin^2\left(\frac{\Delta_{kj}^2L}{4E}\right) \\
  &+ 2\sum_{k>j} \text{Im}[U^*_{\alpha k}U_{\beta k}U_{\alpha j} U^*_{\beta j}]\sin\left( \frac{\Delta m_{kj}^2 L}{2E} \right)
\,,\end{align*}
where we have defined the oscillation lengths $L^\text{osc}_{kj} = 4\pi E / \Delta m_{kj}^2$. For antineutrinos (Dirac antineutrinos with positive helicity or Majorana neutrinos with positive helicity), we have the same expression except for the sign in from of the imaginary part, and the quartic product $U_{\alpha k}U^*_{\beta k}U^*_{\alpha j} U_{\beta j}]$ instead.
Measurements of neutrino oscillations yield only information about the squared mass-differences $\Delta m_{kj}^2$ and the elements of the mixing matrix $U$. Moreover, we have quartic products of $U$. They are independent of the parametrization since they are invariant under the rephasing transformation 
\begin{align*}
  U_{\alpha k} \to e^{i \psi_\alpha} U_{\alpha k} e^{i\phi_k}
,\end{align*}
so the quartic products are independent of the factorized phases of the mixing matrix. This corresponds to a rephasing of the charged lepton and neutrino fields. If we have Majorana neutrinos, we have two Majorana phases in the diagonal matrix to the right of the mixing matrix. These phases are not included in the quartic product, and are thus unmeasurable in neutrino oscillation experiments.

The oscillating term depends on the coherence of massive neutrino components. If different massive neutrinos are produced in an incoherent way, the transition probability $P$ reduces to the constant term. This also happens if we have an uncertainty in the distance $L$ or when we average over the energy resolution of the detector, since the average of the exponential is zero.

The oscillation probabilities of the channels with $\alpha \neq \beta$ are called transition probabilities, while the channels with $\alpha = \beta$ are called survival probabilities. For the survival probability of $\alpha$, we get 
\begin{align*}
  P_{\na \to \nu_\alpha} = 1-4\sum_{k > j}\abs{U_{\alpha k}}^2 \abs{U_{\alpha j}}^2 \sin^2 \left( \frac{\Delta m_{kj}^2 L}{4E} \right)
.\end{align*}

The average transition probability has a maximum at $\frac{1}{N}$, and the average survival probability a minimum at $\frac{1}{N}$. If all elements of the $N \times N$ matrix $U$ have the same absolute value, we have N-maximal mixing: minimal average survival probability equal to $\frac{1}{N}$ and maximal average transition probability equal to $\frac{1}{N}$ in each possible channel.

Neutrinos mass states produced/detected in CC interactions are linearly combined by the mixing matrix $U$ to form flavor states. If the experiment is not sensitive to the differences of the contribution of the different neutrino masses, these flavor states reduce to this standard linear combination.

\subsection*{7.3 Symmetries}
The neutrino oscillation theory is based on a local quantum field theory, and is thus CPT invariant. Thus,
\begin{align*}
  P_{\na \to \nb} &= P_{\anb \to \ana} \\
  P_{\na \to \na} &= P_{\ana \to \ana} 
.\end{align*}
So the survival probabilities for neutrinos and antineutrinos are equal. If the description of nature through local quantum field theories are only approximate, we could expect the CPT invariance to be violated. 
regarding CP invariance, we know that this is violated due to the complex elements of the three-neutrino mixing matrix. Thus, T symmetry should also be violated in order to keep CPT invariant.

We can inspect these violations by studying the asymmetry parameters
\begin{align*}
  A^\text{CPT}_{\alpha \beta}     &= P_{\na \to \nb} - P_{\anb \to \ana} \\
  A^\text{CP}_{\alpha \beta}       &= P_{\na \to \nb} - P_{\ana \to \anb} \\
  A^\text{T}_{\alpha \beta}       &= P_{\na \to \nb} - P_{\nb \to \na}   \\
  \bar{A}^\text{T}_{\alpha \beta} &= P_{\ana \to \anb} - P_{\anb \to \ana}
.\end{align*}
The CPT symmetry implies that the CP asymmetry is antisymmetric, i.e.
\begin{align*}
  A^\text{CP}_{\alpha \beta} = - A^\text{CP}_{\beta \alpha}
,\end{align*}
which implies $P_{\ana \to \anb} = P_{\nb \to \na}$. Thus, a CP asymmetry can only be measured in transitions between different flavors. Moreover $A^\text{CP}$ only contains the imaginary oscillatory part. Thus, experiments must be sensitive to the oscillatory behavior of the transition probabilities, i.e. $\dm_{kj} / 2E$ needs to be of order one. If the phases are smaller, the probabilities are too small to be measured. If they are much greater than unity, the CP asymmetry shadows the sine.

Regarding the T violation, the CPT relation implies that 
\begin{align*}
  A^\text{T}_{\ab} = -\bar{A}^\text{T}_{\ab} = A^\text{CP}_{\ab}
.\end{align*}
Thus, measuring a CP asymmetry is equivalent to measuring a T asymmetry. We can then measure a T asymmetry by designing an experiment that is sensitive to the oscillations in the flavor transition probabilities (so we can see the CP asymmetry).

\subsection*{Two-neutrino mixing}
By restricting the mixing angle $0 \le \theta \le \pi / 2$, and since the mixing angle dependence of the transition probability is expressed by $\sin^2 2 \theta$ which is symmetric under the exchange $ \theta \to \pi / 2 - \theta $, there is a degeneracy of the transition probability for $\theta$ and $\pi / 2 - \theta$. The difference is that mixing angles $\theta < \pi / 4$ correspond to the case then the incoming neutrino $\na$ consists of more $\n{1}$ than $\n{2}$. When $\theta > \pi / 4$, $\na$ consists of more $\n{2}$ than $\n{1}$. This is not a feature in matter oscillations.

If 
\begin{align*}
  \frac{\dm L}{2E} \ll 1
\,,\end{align*}
the different flavors can't be measured.
If 
\begin{align*}
  \frac{\dm L}{2E} \gg 1
\,,\end{align*}
only the average transition probability is observable. We can then define the sensitivity as the value of $\dm$ for which 
\begin{align*}
  \frac{\dm L}{2E} \sim 1
,\end{align*}
so the sensitivity is then E[MeV] / L[m] = E[GeV]/L[km]
\subsection*{Experiment}
\begin{itemize}
  \item Appearance: Measure transitions between flavors. If the final flavor is not present in the incoming beam, the experiment is sensitive to small mixing angles.
  \item Disappearance: Measures the survival probability by counting the number of interactions with the expected one. Even we have no oscillations, we still have statistical fluctuations. Therefore, it is harder to measure small mixing angles here.
\end{itemize}

Since we have spacial uncertainties in both $L$ and $E$, it is always necessary to average the oscillation probability over the distributions of $L$ and $E$. For two-neutrino mixing, we have the following transition probability for $x = L / E$:
\begin{align*}
  P_{\na \to \nb}(x) = \frac{1}{2} \sin^2 2\theta \left[1 - \left\langle \cos \left( \frac{\Delta m^2 x}{2} \right) \right\rangle \right]
\,,\end{align*}
with
\begin{align*}
  \left \langle \cos \left (\frac{\dm}{2} x \right) \right \rangle = \int \cos \left (\frac{\dm}{2} x \right ) \, \phi(x) \, \dd x
.\end{align*}
Assuming Gaussian distribution with average $\avg{x}$ and standard deviation $\sigma$, we have 
\begin{align*}
  \avg{\cos\left( \frac{\dm x}{2} \right)} = \cos\left( \frac{\dm}{2} \avg{x}\right)\exp\left[-\frac{1}{2} \left(\frac{\dm}{2}\sigma\right)^2\right]
.\end{align*}.
Since the uncertainties in $L$ and $E$ are independent, we have
\begin{align*}
  \left(\frac{\sigma_{L/E}}{\avg{L/E}}\right)^2 = \left(\frac{\sigma_L}{\avg{L}}\right)^2 + \left(\frac{\sigma_E}{\avg{E}}\right)^2 
.\end{align*}

For distances $\avg{L} \le L^\text{osc}$, $\avg{P}$ oscillates as the unaveraged $P$ with a somewhat suppressed amplitude. The suppression is dependent on the width $\sigma$. For distances $\avg{L} \gg L^\text{osc}$, the oscillations are completely suppressed.
If we don't have any oscillations, the data imply an upper limit on $\avg{P}$:
\begin{align*}
  \avg{P_{\na \to \nb}} \le P^\text{max}_{\na \to \nb}
,\end{align*}
which implies an upper limit for $\sin^2 2\theta$ as a function of $\dm$, called the exclusion curve:
\begin{align*}
  \sin^2 2\theta \le \frac{2 P^\text{max}_{\na \to \nb}}{1- \avg{\cos \left( \frac{\dm L}{2E} \right)}}
.\end{align*}

\subsection*{8. Oscillations in vacuum}
Energy-momentum conservation implies that neutrinos emitted with definite energy and momenta must be produced with definite energies and momenta. Energy-momentum conservation cannot hold for different massive neutrinos and the production of superpositioned massive neutrinos is forbidden. Thus, we need to treat the neutrinos as wave packets.

The state of the asymptotic final flavor $\nb$ is defined in terms of the state which describes an asymptotic initial state  resulting fro a weak interaction process, expressed by the $S$-matrix operator as 
\begin{align*}
  \ket{\nb} = S \ket{\na}
.\end{align*}
If the final state is a superposition of orthogonal and normalized states, it can be decomposed using the $S$-matrix coefficients $\mathcal{A}_k = \bra{\nu_{\b k}} S \ket{\na}$ 
\begin{align*}
\ket{\nb} = \sum_k \mathcal{A}_k \ket{\nu_{\b k}}
.\end{align*}
\subsection{Questions}
\begin{itemize}
  \item Do charged leptons oscillate?: The flavor of a charged lepton is defined by its mass, which does not oscillate.
  \item What are the energies and momenta?: Both the plane-wave approximation and the wave-packet treatment are independent of the values of the energies and momenta as long as the relativistic dispersion relation is satisfied and massive neutrinos are ultrarelativistic.
  \item Are wave packets necessary?: In practical applications, the oscillation probabilities are indistinguishable.
\end{itemize}
\subsection*{9. Oscillations in matter}
Neutrinos propagating in matter are subject to a potential due to the coherent forward elastic scattering with the particles in the medium. This works as a refraction index and modifie the neutrino mixing angle. The small number of incoherent scatterings with the particles in the medium can be neglected since the mean free path of solar neutrinos ($E \sim \si{1}{MeV} $) in normal matter is 0.1 light years. e can ignore incoherent cattering in Earth for $E > \si{10e5}{MeV}$.

In matter with varying density, it is possible through the MSW mechanism to have resonant flavor transitions, when the matter modified mixing angle reache its maximum of $\pi /4$. Thi eplain hy e can have maial flavor tranition ithout a maimal vacuum miing angle.

For CC, we have the effective average Hamiltonian
\begin{align*}
  \bar{H}^\text{CC}_\text{eff}(x) = \sqrt{2}\, G_F N_e \an{eL}(x) \gamma^0 \n{eL}(x)      
\,,\end{align*}
with $V^\text{CC} = \sqrt{2}G_F N_e $. For NC, if we assume electric neutrality, the only contributing g-factors are the neutrons, so $V^\text{NC} = -\sqrt{2}/2 G_F N_n$, and the total Hamiltonian is now
\begin{align*}
  \bar{H}_\text{eff} = \sum_{\a = e, \mu, \tau} V_\a \an{\a L}(x) \gamma^0 \n{\a L}(x)
\,,\end{align*}
with the potentials
\begin{align*}
  V_\a = V_\text{CC} \delta_{\a e} + V_\text{NC} = \sqrt{2} G_F \left( N_e \delta_{\a e} - \frac{1}{2} N_n \right) 
\,.\end{align*}

The potential energy of ultrarelativistic right-handed Dirac antineutrinos have opposite sign to the potential of the left-handed neutrinos, and the potential of ultrarelativistic left-handed Dirac antineutrinos is strongly suppressed.
In the ultrarelativistic limit, neutrinos can be considered massless in interactions. The potential energy of ultrarelativistic left-handed Majorana neutrinos are the same as the potential for left-handed Dirac neutrinos. The potential energy of ultrarelativistic right-handed Majorana neutrinos is the same as that of right-handed Dirac antineutrinos.

Interactions with matter conserve helicity. 
The evolution equation for the flavor transition amplitudes is 
\begin{align*}
  i \dv{}{x}\psi_{\a \b}(x) = \sum_\eta \left( \sum_k U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} + \delta _{\b e} \delta_{\eta e} V_\text{CC} \right) \psi_{\alpha \eta}(x)
.\end{align*}
And the matrix form is
\begin{align*}
  i \dv{}{x} \Psi_\a = H_F \Psi_\a, \quad H_F = \frac{1}{2E}(U \mathbb{M}^2 U^\dagger + \mathbb{A})
,\end{align*}
with
\begin{align*}
  \Psi_\a &= \begin{pmatrix} \psi_{\a e} \\ \psi_{\a \mu} \\ \psi_{\a \tau} \end{pmatrix} , \quad
  \mathbb{M}^2 = \begin{pmatrix} 0 & 0 & 0 \\
                                 0 & \\dm[21] & 0 \\
                                 0 & 0 & \dm_{31}
                 \end{pmatrix}, \\
    \mathbb{A} &= \begin{pmatrix} A_\text{CC} & 0 & 0 \\
                                 0 & 0 & 0 \\
                                 0 & 0 & 0
                 \end{pmatrix}
\,,\end{align*}
where 
\begin{align*}
  A_\text{CC} = 2EV_\text{CC} = 2 \sqrt{2}E G_F N_e 
.\end{align*}
From this we can prove that the Majorana phases are irrelevant for vacuum oscillations as well as matter oscillations.

\subsection*{MSW}
The effective mixing angle in matter is given by
\begin{align*}
\tan 2\theta_\t{M} = \frac{\tan 2\theta}{1- \frac{A_\text{CC}}{\dm \cos 2\theta}}
,\end{align*}
and is resonant when $A_\text{CC}$ becomes equal to
\begin{align*}
  A^\t{R}_\t{CC} = \dm \cos 2\theta
,\end{align*}
which corresponds to the electron number density
\begin{align*}
  N^\t{R}_\t{e} = \frac{\dm \cos 2\theta}{2\sqrt{2} E G_\t{F} }
.\end{align*}
Resonance can exist only if $\theta < \pi / 4$ for neutrinos, and only if $\theta > \pi / 4$ for antineutrinos.

We have the evolution equation
\begin{align*}
  i \dv{}{x} \begin{pmatrix} \varphi_\t{e1} \\ \varphi_\t{e2} \end{pmatrix} 
  = \frac{1}{4E} \begin{pmatrix} -\dm_\t{M} & -4Ei \dd \theta_\t{M} / \dd x \\
                                 4Ei \dd \theta_\t{M} / \dd x & -\dm_\t{M}  
                 \end{pmatrix}
                 \begin{pmatrix} \varphi_\t{e1} \\ \varphi_\t{e2}  \end{pmatrix} 
.\end{align*} 
If matter density is constant, we recover 
\begin{align*}
  P_{\nu_{e} \to \nu_{\mu}} = \sin^2 2 \theta_{\t{M}} \sin^2 \left( \frac{\dm_{\t{M}}x}{4E} \right)
.\end{align*}
If matter density is not constant, we need to account for 
\begin{align*}
  \dv{\theta_\t{M}}{x} = \frac{1}{2} \frac{\sin 2\theta_\t{M}}{\dm_\t{M}} \dv{A_\t{CC}}{x}
.\end{align*}
The off-diagonal elements in the evolution equation generate transitions between $\n{1}^\t{M}$ and $\n{2}^\t{M}$, which can be neglected if they are much smaller than the diagonal elements. To quantify this, we introduce the adiabaticity parameter
\begin{align*}
  \gamma = \frac{\dm_\t{M}}{4E \abs{\dd \theta_\t{M} / \dd x}} = \frac{(\dm_\t{M})^2}{2E \sin 2\theta_\t{M} \abs{\dd A_\t{CC}} / \dd x}
.\end{align*}
If $\gamma \gg 1$ in all points of the trajectory, the evolution is adiabatic, and the transitions between $\nu_1^\t{M}$ and $\nu_2^\t{M}$ are negligible. In this case, the survival probability is given by
\begin{align*}
  P^\t{adiabatic}_{\ne \to \ne}(x) &= \frac{1}{2} + \frac{1}{2} \cos 2\theta_\t{M}^\t{(i)} \cos 2\theta_\t{M}^\t{(f)} \\
                                       & \quad + \frac{1}{2} \sin 2\theta_\t{M}^\t{(i)} \sin 2\theta_\t{M}^\t{(f)} \cos{\left(\int_0^x \frac{\dm_\t{M}(x')}{2E} \dd x' \right)}
,\end{align*}
where $\theta_\t{M}^\t{(f)}$ is the effective mixing angle at the detection point.
For solar or supernova neutrinos, we can set the final effective mixing angle $\thm{(f)}$ equal to the vacuum mixing angle $\theta$ since the density of the detector is too small. Thus we set the final angle to the effective angle of the propagating medium. If the travel distance is very large and $\dm_\t{M}$ not too small, the phases in the probabilities are very large and rapidly oscillating as functions of the neutrino energy. The average of the probability over the energy resolution of the detector then washes out all interference terms. 
 The distance between source and detector is huge, so the phase of the cosine is very large and has a variation much larger than $2\pi$ in the energy resolution interval of the detector. Thus, the cosine averages to zero and we have the average survival probability 
\begin{align*}
  \bar{P}^\t{adiabatic}_{\ne \to \ne} = \frac{1}{2} + \frac{1}{2}\cos{2 \theta^\t{(i)}_\t{M}}\cos{2\theta}
.\end{align*}

The maximum violation of adiabaticity (MVA) occurs when $\gamma$ is in the order of 1 or smaller, and the transitions reach their maximal size at the minimum of $\gamma$. This is in general a different point than the resonance point. Nonadiabatic transitions between $\n{1}^\t{M}$ and $\n{2}^\t{M}$ can be calculated by approximating the MVA point with the resonance point (except for solar neutrinos).

\subsection*{Slab approximation}
When the mediums density can be approximated by a series of slabs with constant density, we have plane wave propagation with phases

$\exp(\pm i \dm_\t{M} \Delta x / 4E)$. 
We have the flavor wave function evolution

\begin{align*}
  \Psi_e(x_n) = \sum_{i=0}^{n-1}[U_\t{M}\,\mathcal{U}_\t{M}(x_{i+1} - x_{i})\,U^\dagger_\t{M}]_{(i+1)}\Psi_e(x_i)
,\end{align*}
with the unitary evolution operator per slab
\begin{align*}
  \mathcal{U}_\t{M}(\Delta x) = \begin{pmatrix} 
    \exp(i\dm_\t{M} \Delta x / 4E) & 0 \\
                                  0 & \exp(-i\dm_\t{M} \Delta x / 4E) 
                                \end{pmatrix}
,\end{align*} 
in the slab diagonal basis. 
The unitary evolution operator in the flavor basis in each slab with constant density is given by
\begin{align*}
  \mathcal{U}(x) = \cos{\varphi (x)} - i(\vec{n} \cdot \vec{\sigma})\sin{\varphi (x)}
.\end{align*}
with the phase
\begin{align*}
  \varphi (x) = \frac{\dm_\t{M} x}{4E}
.\end{align*}

Parametric resonance occurs when we have a dynamical system whose parameters, such as the matter potential, vary periodically in time. The phase oscillations then amplifies the transition probability.

\subsection*{Three neutrino mixing}
Now, simultaneous transitions among all three flavors are allowed.
Neutrinos oscillate with two different squared-mass differences: $\dm[SOL]$ and $\dm[ATM]$ with the hierarchy $\dm[SOL] \ll \dm[ATM]$. The three massive neutrinos could be Dirac, Majorana, or be generated by a Dirac-Majorana mass term through the see-saw mechanism. We have three squared-mass differences, two of which are independent since they sum to zero. From these requirements, we can form two three-neutrino mass hierarchies. These hierarchies can allow us to approximate three-neutrino mixing to two-neutrino mixing since the effects of large and small squared-mass differences can be separated.

We have the following possible channels:
\begin{align*}
  \ne \leftrightarrow \nm\,, \quad \ne \leftrightarrow \nt\,, \quad \nm \leftrightarrow \nt
.\end{align*}

Atmospheric experiments are sensitive to the oscillations due to $\dm[31]$. Considering the hierarchy
\begin{align*}
  \dm[21] \ll \dm[31] \simeq \dm[32]
,\end{align*}
which implies that there is a dominance of the largest squared-mass difference $\dm[31]$. We then have two groups of massive neutrinos: $\{\nu_\t{1}, \nu_\t{2}\}$ and $\{\nu_\t{3}\}$. Thus, we have a two-neutrino-like effective oscillation probability
\begin{align*}
  P^\t{eff}_{\na \to \nb} = \sin^2{2 \th^\t{eff}_{\a\b}} \sin^2{\left( \frac{\dm[31]L}{4E} \right)}
.\end{align*}
All oscillation channels are open and have the same oscillation length. The probabilities are independent of the mixing angle $\th[12]$. The sign of $\dm[31]$ tells us what squared-mass hierarchy we have.

Solar experiments are sensitive to the oscillations due to $\dm[21]$. Here we have an active small mass dominance, and oscillations due to the large squared-mass difference $\dm[31]$ are washed out. We have one neutrino per group.

If one if the elements of the mixing matrix is small, we have bilarge mixing. We can then parametrize the mixing matrix with only two mixing angles. The matrix is then real and no CP or T violations exist. We can use this case to analyze data in which $\ne$ are produced or detected.

For antineutrinos, the matter potential changes sign, so the oscillation probabilities of neutrinos and antineutrinos are different even if the fundamental Lagrangian is CP invariant. In other words, there is a matter-induce CP violation in the oscillation probabilities due to the fact that the medium is not CP-invariant. However, if the probability is independent of the CP violating phase $\delta_\t{13}$, the violation is not observable. Moreover, since the medium is also not CPT-invariant, there is a matter-induced CPT violation in the oscillation probabilities.

\section*{Notes from~\cite{heros2020}}
\subsection{5. Standard Neutrino Oscillations}
The flavor states have extremely small cross-sections compared to all the other particles, and propagate as an admixture of "hidden" mass states. The energy expression in the time-evolution operator can be expressed as a binomial expansion and truncated, yielding the ultrarelativistic approximation $t \simeq L, p \simeq E$. We then have
\begin{align*}
  \ket{\nu_j,t} &= e^{-iE_j t}\ket{\nu_j,0} \\
                &= e^{-i\left( p + \frac{m^2_j}{2p}L \right)}\ket{\nu_j,0} \\
                &= e^{-ipL} e^{-i\left(\frac{m^2_j L}{2p} \right)}\ket{\nu_j,0} \\
                &\simeq e^{-i \frac{m^2_j L}{2E}}\ket{\nu_j,0} 
,\end{align*}   
where $\exp(-ipL)$ was be regarded as a irrelevant phase factor that disappears when calculating the probabilities. With the PMNS matrix, we now have
\begin{align*}
  \sum_j U^*_{\a j}\ket{\nu_j} = \sum_j U^*_{\a j} e^{-i \frac{m^2_j L}{2E}}\ket{\nu_j,0} 
.\end{align*}

The neut oscillations are driven by the squared-mass differences between the mass eigenstates. If $\dm_{ji} = 0$, the flavor transition probability is constant for all $E$ and all $L$. Experimental oscillation results confirm the non-zero nature of at least two of the three mass eigenstates. All in all, we have nine elements of the mixing matrix, and two squared-mass differences.

Experimental uncertainties on the mixing matrix elements create unphysical probabilities. Using the $+3\sigma$ values for all the individual elements will make some oscillation channels go below 0 and above 1. To preserve probabilities in the $[0-1]$ range, we can reparametrize the contributions of the matrix elements. By considering atmospheric and solar neutrinos separately, and considering the experiment sensitivities, we can substitute e.g. $\dm[31]$ with $\dm[32]$. We can then construct simplified transition probabilities for each channel. We make approximations such as $\cos{\th{13}} \simeq 1$, since $\th{13} \simeq 8.5 ^\circ$ if magnitude of the oscillation is driven by a larger angle, such as $\th{23}$. Thus, we can express different probability channels, having different mixing elements, with the same angles.

If the mixing matrix is unitary, we can express the elements in terms of each other through a unitary triangle, similar to the construction of the squared-mass differences.

The mixing matrix can be decomposed as 
\begin{align*}
  &\t{LBL \& Atmospheric} \hspace{1.4 cm} \t{Reactor} \hspace{2.3 cm} \t{Solar} \\
  &\left[\begin{array}{ccc}
1 & 0 & 0 \\
0 & c_{23} & s_{23} \\
0 & -s_{23} & c_{23}
\end{array}\right]\left[\begin{array}{ccc}
c_{13} & 0 & s_{13} e^{-i \delta} \\
0 & 1 & 0 \\
-s_{13} e^{i \delta} & 0 & c_{13}
\end{array}\right]\left[\begin{array}{ccc}
c_{12} & s_{12} & 0 \\
-s_{12} & c_{12} & 0 \\
0 & 0 & 1
\end{array}\right]
\,.\end{align*}

The higher mass of the $\tau$ lepton suppresses the other pion and kaon decay channels kinematically. Thus, there is an abundance of pion and kaon decay into atmospheric $\ne$ and $\nm$. Atmospheric neutrinos has a wide range of $L / E$ combinations, which is a significant benefit for the study. This fact, together with the physical size, somewhat makes up for the (c.f accelerator experiments) poor energy and direction resolution of neutrino telescopes. The deeper a neutrino telescope is
located, the more atmospheric muons are absorbed by the material. Atmospheric neutrinos are always down-going, since they can't penetrate the whole Earth. Oscillated neutrinos are up-going. Atmospheric neutrinos emit observable light as they enter a detector, so they have an "uncontained" starting vertex at the edge of the detector. This can veto background muons, which have a "contained" starting vertex. Events reconstructed as down-going may be selected only if the starting vertex is contained and reconstructs sufficiently far from the outer edge of the detector. We can use ML to create event selections to reject background atmospheric muons while keeping neutrinos. A muon from a $\nm$ CC will produce a track-type event as opposed to a cascade for CC $\ne$ and $\nt$ or NC $\ne, \nm, \nt$ interactions. For a $\nmm$ analysis, we optimize the event selection to select samples that are rich in tracks. For analyses involving final states $\ne$ or $\nt$, we priorotize tracks and cascades.

Oscillation parameters are taken from data and MC simulations, binned into histograms of the incoming zenith angle, and compared to e.g. $\chi^2$. If the events can be sub-divided into tracks and cascade (or any other event based to event selection), we can use the feature that $\chi^2$ is the combination of $\chi^2_\t{track} + \chi^2_\t{cascade}$.
$\nt$ survival has direct measurements that relates to $\abs{U_{\tau 3}}$. The energy threshold for $\nt$ to $\tau$ lepton decay is $\sim 3.4$ GeV. Most accelerator beams have a peak $< 3$ GeV, so most of the oscillated $\nt$ from an accelerator are forbidden from interacting via CC. $\nt$ also has a smaller cross-section compared to the other neutrinos.

Because conventional neutrino oscillation experiments measured the mass-squared difference as functions of trigonometric expressions that assume vacuum oscillations and that are insensitive to whether $\dm$ is positive or negative, the ordering of the mass eigenstates requires other methods. We can have a normal NMO ($\nu_3$ heaviest), or an inverted ($nu_3 lightest$). To probe this, we need a large sample and coherent scatterings of neutrinos with atomic electrons as the neutrinos propagate through matter. For a $50:50$ flux of neutrinos:antineutrinos composed of $\nu_{\mu,e}$, the the oscillation probabilities due to mass ordering will average out. Thus, detectors what cannot distinguish between particles and antiparticles, will have a hard time probing the NMO if we don't have a statistical significance between neutrino and antineutrino events. Since the NMO hypothesis is binary, different statistical treatments are needed, as opposed to the ones needed for the other oscillation parameters.

\subsection*{6. Sterile Neutrinos}
The scale of the BSM physics that produce neutrino oscillations is unknown. The particles involved in neutrino mass generation could have an impact in oscillations, either by direct production of sterile states or by indirect effects of non-standard interactions induced by the new particles producing neutrino masses.

Sterile neutrinos in the eV range can account for anomalies found in short-baseline accelerator oscillation experiments. There are ways to avoid the bounds on extra relativistic neutrino species placed by cosmology (non-standard cosmology, right-handed neutrino interactions, light mediators). 
There are two possible scenarios:
\begin{itemize}
  \item Phenomenological models (PM): The sterile neutrino states do not contribute to the observes active neutrino masses. Therefore, the complete model must contain extra particles that generate such masses. It is also assumed that the new physics responsible for neutrino masses has no impact on their oscillations. Thus, we can use a model-independent phenomenological approach in which only the light neutrinos are included. We then have  a generic neutrino mass matrix of dimension $3+N_s$. For $n = 3+N_s$ neutrino flavors, we have $n(n-1)/2$ rotation angles $\th_{ij}$ and $(n-1)(n-2)/2$ physical phases.
  \item Mini-seesaw models (MM): The sterile neutrinos have for Ev Majorana masses, as well as Dirac masses that mix them with the active ones. This is the simplest extension of the standard model that can account for active neutrino masses. The masses and mixings of the sterile neutrinos are partially determined by the PMNS matrix as well as the measured neutrino mass splitting. MM has fewer free parameters than PM. Here, we have $2N_s$ free angles and $3(N_s-1)$ free phases, if $N_s \le 3$. The remaining angles and phases are not independent, and can be written in terms of the sterile neutrino Majorana masses and the Dirac masses that mix left-handed active neutrinos with the right-handed ones.
\end{itemize}

With the additions of $N_s$ sterile neutrinos, we extend the kets:
\begin{align*}
  \ket{\na}\,, \quad \a &= e,\mu,\tau,s_1,\ldots ,s_{N_s} \\
  \ket{\nu_i}\,, \quad i &= 1,2,3, \ldots, 3+N_s
\,\end{align*}
A standard parametrization of the extended U matrix consists of a series of unitary rotations $V_{ij}$ in the $i-j$ plane
\begin{align*}
  U = V_{3n}V_{2n}V_{1n} \ldots V_{34}V_{24}V_{14}U_{0}
\,,\end{align*}
where $U_0 = V_{23}V_{13}V_{12}$ contains the usual $U_\nu$ matrix in the upper left $3 \times 3$ block.
With this convention, the full matrix $U$ can be expressed as 
\begin{align*}
  U = AU_0 = \begin{pmatrix} 
              (1-\a) & \Theta \\ 
                   X & Y 
            \end{pmatrix}
            \begin{pmatrix} 
              U_\nu & 0 \\
                  0 & 1
            \end{pmatrix} 
\,,\end{align*}
with
\begin{align*}
  \a = \begin{pmatrix} 
        \a_{ee} & 0 & 0 \\
        \a_{\mu e} & \a_{\mu \mu} & 0 \\
        \a_{\tau e} & \a_{\tau \mu} & \a_{\tau \tau}
       \end{pmatrix}
\,,\end{align*}
with $a_{\beta \gamma} \ll 1$,
\begin{align}
  \label{abg}
  \alpha_{\beta \gamma} \simeq\left\{
    \begin{array}{ll}
      \frac{1}{2} \sum_{i=4}^{n}\left|U_{\beta i}\right|^{2}, & \beta=\gamma \\
      \sum_{i=4}^{n} U_{\beta i} U_{\gamma_{i}}^{*}, & \beta>\gamma \\
      0, & \gamma>\beta
    \end{array}\right.
\end{align}
The $3 \times 3$ active-light mixing sub-block is described by $N=(1-\a)U_\nu$ which is no longer unitary. $\Theta$ is a $3 \times N_s$ sub-block that mixes the active and heavy states. $R = X U_\nu$ and $Y$ sub-blocks define the mixing of the sterile with the light and heavy states, respectively. Neither $R$ nor $Y$ affect oscillations among active flavors.

The impact of sterile neutrinos on oscillations is very different depending on whether the heavy neutrinos are kinematically accessible or not.
\begin{itemize}
  \item PM: The full $(3+N_s) \times (3+N_s)$ oscillation evolution matrix $S$ has to be considered.
  \item MM: Only the $3 \times 3$ sub-matrix $N = (1-\a)U_\nu$ enters in the oscillation evolution equations, but the effect of the heavy states could still be detected due to the non-unitarity of $N$. In the limit of large mass-squared splitting, $\dm L/E_\nu \gg 1$, the oscillations are too fast to be resolved, and only the averaged-out effect is observable.  This effect is equivalent to non-unitarity to leading order in the active-heavy mixing parameters.
\end{itemize}

NC NSI are often called matter NSI since they modify neutrino propagation through matter. CC NSI are referred as production/source and detection NSI.
\subsection*{NSI and tests of Lorentz invariance}
TODO
\subsection*{Formalism}

When propagating through the Earth, $\ne, \nm$ are absorbed via charged-current interactions and redistributed via NC. $\nt$ on the other hand, is regenerated, since it produces a $\tau$ that in turn decays into a $\nt$ before losing energy, and the Earth never becomes opaque to high energy $\nt$. Additionally, secondary $\ne$ and $\nm$ are also produced after $\tau$ decay into leptonic channels. For atmospheric neutrinos however, the $\nt$ flux is negligible.

Attenuation and regeneration effects from high-energy astrophysical sources are described by a set of couples PDE's. Due to the long distance traveled, the oscillations average out and the arriving neutrinos can be treated as an incoherent superposition of mass eigenstates. For atmospheric neutrinos, this is not the case since oscillations, attenuations, and regeneration effects occur simultaneously when the neutrino beam crosses the Earth. We emply the density matrix formalism for neutrino propagation through the Earth: $\rho\left(E_{\nu}, x\right)=\nu\left(E_{\nu}, x\right) \otimes \nu\left(E_{\nu}, x\right)^{\dagger}$. We have the evolution equation:
\begin{align*}
\frac{d \rho\left(E_{\nu}, x\right)}{d x}=&-i\left[H\left(E_{\nu}, x\right), \rho\left(E_{\nu}, x\right)\right] \\
&-\sum_{\alpha} \frac{1}{2 \lambda_{\alpha}\left(E_{\nu}, x\right)}\left\{\Pi_{\alpha}\left(E_{\nu}\right), \rho\left(E_{\nu}, x\right)\right\} \\
&+\int_{E_{\nu}}^{\infty} \rho\left(E_{\nu}^{\prime}, x\right) n_{N}(x) \frac{d \sigma_{\mathrm{NC}}\left(E_{\nu}^{\prime}, E_{\nu}\right)}{d E_{\nu}} d E_{\nu}^{\prime}
\end{align*},
where $\Pi_a$ is the $\na$ projector, $\lambda_\a = 1/[n_N(x) \sigma^\t{tot}_\a(E_\nu)]$ is the attenuation length of $\na$ with $n_N(x)$ the nucleon number density in the Earth, and $\sigma^\t{tot}_\alpha(E_\nu)$ the $\na$ total (CC+NC) cross-section. The first term is oscillations, second absorption, and the third term is the redistribution of the flux due to NC interactions. 
For atmospheric neutrinos, the interplay of oscillations and Earth attenuation is described by an overall exponential suppression in the oscillated fluxes:
\begin{align*}
\phi_{\alpha}\left(E_{\nu}, \theta_{z}\right)=& \phi_{\mu}^{0}\left(E_{\nu}, \theta_{z}\right) P\left(\nu_{\mu} \rightarrow \nu_{\alpha} ; E_{\nu}, L\left(\theta_{z}\right)\right) \\
& \times \exp \left\{-\int_{0}^{L\left(\theta_{z}\right)} d x / \lambda_{\alpha}\left(E_{\nu}, x\right)\right\}
\,,\end{align*}
where $L(\th_z)$ is the baseline across the Earth in a direction with zenith angle $\th_z$.

In the presence if $N_s$ light sterile neutrinos, the $(3+N_s)\times(3+N_s)$ evolution Hamiltonian is given by
\begin{align*}
  H = H_\t{vac} + U^\dagger \t{diag}(V_e + V_\t{NC}, V_\t{NC}, V_\t{NC}, 0, \ldots, 0)U
\,,\end{align*}
where $H_\t{vac} = \t{diag}[\dm_j1/2E]$, and the second term contains the matter potentials $V_e = V_\t{CC} = \sqrt{2}G_F n_e$ and $V_\t{NC} = -\sqrt{2}G_F n_n/2$ where $n_n$ is the neutron number density. Consider only one sterile neutrino and neglect solar and atmospheric oscillation lengths (good approximation of $\mathcal{O}(\t{TeV})$). We have:
\begin{align*}
  P_{\nms} = \sin^2 2\thm \sin^2 \left( \frac{\dm[M] L}{4E_\nu} \right) 
\,\end{align*}
where the effective mass difference and matter mixing angles are given by
\begin{align*}
  \dm[M] &= \sqrt{(\dm \cos 2\th[24] - 2E_\nu V_\t{NC})^2 + (\dm \sin 2\th[24])^2}\\
  \sin 2\thm &= \frac{\dm \sin 2\th[24]}{\dm[M]}
\,\end{align*}
where the mass splitting between the heavy state and the three light ones are approximated by $\Delta m$.Even for a small vacuum mixing angle $\th[24]$ the probability $\nms$ can be enhanced through MSW resonance:
\begin{align*}
  E_\nu \sim - \cos 2\th[24] \frac{\dm}{2 V_\t{NC}}
\,\end{align*}.

Heavy sterile neutrinos lead to non-unitarity can be described by extending the three-flavor oscillation framework as :
\begin{align*}
  H = H_\t{std} + \sum_n \left(\frac{E^n}{\Lambda_n})^n \tilde{U}^\dagger_n O_n \tilde{U}_n\right)
\,\end{align*}
where the first term is the standard neutrino Hamiltonian (including the matter potential). $O_n = \t{diag}(O_{n1}, O_{n2}, O_{n3})$ and $\Lambda_n$ set the new physics scale, and $\tilde{U}_n$ stands for the mixing matrix that describes the flavor structure of the new physics. A minimal SM extension is restricted to dimension 4, and only has two terms corresponding to $n = 0,1$. NSI (and thus non-unitarity) also lead to $n=0$ terms. 
The $\nmt$ sector is a good approximation for high energies where the solar oscillation scale is very suppressed. Herem the matter potential drops out of the Hamiltonian, and we have
\begin{align*}
  H &= \frac{1}{2E}U^\dagger(\th)\begin{pmatrix} 
                                  0 & 0 \\
                                  0 & \dm[31]
                                \end{pmatrix}
                  U(\th) \\
    &+ \sum_n \sigma^\pm_n \frac{\Delta \delta_n E^n}{2}U(\xi_n) \begin{pmatrix} 1 & 0 \\ 0 & -1 \end{pmatrix}U^\dagger(\xi_n)
\,,\end{align*}  
where $\sigma^\pm_n$ accounts for the possible relative sign of the new physics contribution between neutrinos and antineutrinos. $\Delta \delta_n = 2 \Delta O_n / \Lambda ^n_n$ is the difference of the eigenvalues divided by the new physics scale, and $\xi_n$ is the mixing angle.

For this Hamiltonian, the transition probability for the $\nmt$ sector is given by
\begin{align*}
  P_{\nmt} = 1- \t{Tr}(\Pi_\mu \rho) = \sin^2 2\Theta sin^2 \left( \frac{\dm[31]L}{4E_\nu}R \right)
\,,\end{align*}
where
\begin{align*}
  R^{2}&=1+R_{n}^{2}+2R_{n}\left(\cos 2\theta_{23}\cos 2\xi_{n}+\sin 2 \theta_{23} \sin 2\xi_{n} \cos \eta_{n}\right)\\
  \sin ^{2} 2 \Theta &= \frac{1}{R^{2}}\left(\sin 2 \theta_{23}+R_{n}^{2} \sin ^{2} 2 \xi_{n}+2 R_{n} \sin 2 \theta_{23} \sin 2 \xi_{n} \cos \eta_{n}\right) \\
  R_{n}&=\sigma_{n}^{+} \Delta \delta_{n} \frac{2 E^{n+1}}{\Delta m_{31}^{2}}
\,\end{align*}
\subsection*{Searches with Neutrino Telescopes}
TODO
\subsection*{Sterile neutrino oscillations}
Sterile neutrinos produce a very fast oscillations at the low-energy part of the atmospheric neutrino flux. In the two flavor approximation, the effective Hamiltonian for the averaged oscillations is given by
\begin{align*}
  \tilde{H}_0 = \frac{\dm[31]}{4E} 
  \begin{pmatrix} -\cos(2\th_{23}) & \sin(2\th_{23}) \\ \sin(2\th_{23}) & \cos(2\th_{23}) \end{pmatrix}
  + V_\t{NC} \begin{pmatrix} 2 \a_{\mu\mu} & \a^*_{\tau\mu} \\ \a_{\tau\mu} & 2\a_{\tau\tau} \end{pmatrix} 
\,,\end{align*}
$V_\t{NC} = \sqrt{2}G_F n_n/2 $ where $V_\t{NC} = -\sqrt{2}G_F n_n/2 $ and the matrix elements $\a_{\b \gamma}$ depend on the sterile-active mixing and are defined in \eqref{abg}.

An eV mass splitting produces a large effect when neutrinos propagate in the Earth at TeV energies. So we have an enchantment due to matter effects with atmospheric neutrinos. IceCube has done this analysis for $\nm$ disappearance, and found $dm[41] = 0.92 eV^2$, $\abs{U_{\mu 4}} = 0.14$.

If the mass scale $\dm$ is much larger than $E/L$, the oscillation effect is averaged out. Changes is the matter potential are still visible, though. This allows the usage of high-energy atmospheric data to test mass sterility above 10 eV.

Since most of the neutrinos observed in experiments travel through ordinary matter, they may be a good test of NSI neutrino-matter interactions.
\begin{itemize}
  \item Low energy: For low energies, vacuum oscillations are dominating. We are restricted to the $\nmt$ sector. The small effect of the matter potential comes from measuring distortions on the oscillation effect.
  \item High energy: The oscillation frequency in vacuum goes as $\dm/E$, and the matter potential term does not depend on the neutrino energy. Thus, the propagation of high-energy neutrinos is going to be dominated by the matter potential, and may be a great tool to test NSI.
\end{itemize}

At low energies, the telescopes are able to measure the atmospheric oscillation. In the two-flavor approximation, we have
\begin{align*}
  P_{\nmt} = \sin^2 2\Theta \sin^2 \left( \frac{\dm[31]L}{4E_\nu}R \right)  
\,,\end{align*}
with
\begin{align*}
\sin ^{2} 2 \Theta &=\frac{1}{R^{2}}\left(\sin 2 \theta_{23}+R_{0} \sin 2 \xi\right)^{2} \\
R &=\sqrt{1+R_{0}^{2}+2 R_{0} \cos 2\left(\theta_{23}-\xi\right)} \\
R_{0} &=\frac{\phi_{\operatorname{mat}}}{\phi_{\mathrm{vac}}}=V_{d} \frac{2 E}{\Delta m^{2}} \sqrt{4 \varepsilon_{\mu \tau}^{2}+\varepsilon^{2}} \\
\sin 2 \xi &=\frac{2 \varepsilon_{\mu \tau}}{\sqrt{4 \varepsilon_{\mu \tau}^{2}+\varepsilon^{\prime 2}}}
\,,\end{align*}
and the matter potential $\phi_{\mathrm{mat}}=\left(V_{d} L \sqrt{4 \varepsilon_{\mu \tau}^{2}+\varepsilon^{\prime 2}}\right) / 2$ with $V_d = \sqrt{2}G_F n_d$.

For low energies, the effect of NSI and attenuation differs from neutrinos and antineutrinos, while at high energies, the ratio of propagated fluxes coincides. In the case in which the vacuum and matter terms in the oscillation phase are of the same order of magnitude ($\dm[31]L/4E_\nu \sim V_d \sqrt{4\varepsilon^2_{\mu \tau}} + \varepsilon^{\prime 2} $, i.e. $R_0 = \mathcal{O} (1)$) we have
\begin{align*}
  P_{\nmt} \simeq \left( \sin 2 \th[23] \frac{\dm[31]}{2e_\nu} + 2V_d \varepsilon_{\nu \tau} \right)^2 + \left( \frac{L}{2} \right) 
\,.\end{align*}

For higher energies, the matter NSI term dominates over vacuum oscillations, and for $V_\t{NSI}/L \ll 1$ we have
\begin{align*}
  P_{\nmt} \simeq (\sin 2\xi)\phi_\t{mat}^2= (\varepsilon_{\mu\tau}V_d L)^2
\,.\end{align*}

The optimal strategy is to combine the low- and high-energy samples like above to constrain the diagonal NSI parameter $\varepsilon^\prime$.

\subsection*{Tests of Lorentz invariance}
TODO

\section*{Notes from~\cite{kopp2013}}
We do not assume a seesaw scenario, where the Dirac and Majorana mass matrices of the sterile neutrinos are the only source of neutrino mass and mixing. Instead, we consider so-called phenomenological sterile neutrino models, where the $3+s$ neutrino mass eigenvalues and the mixing parameter $U_{\a i}$ are considered to be completely independent. 
Neutrino masses in excess of a few eV may be difficult to reconcile with cosmological observations. CMB data from the PLANCK satellite puts $N_\t{eff}$ in BBN between $3.30^{+0.54}_{-0.51}$ and $3.62^{+0.50}_{-0.48}$.

The mass eigenstates $\nu_1,\ldots, \nu_{3+s}$ are labeled such that $\nu_1, \nu_2, \nu_3$ contribute mostly to the active flavor eigenstates. The mass states $\nu_4, \nu_5$ are then mostly sterile, and provide mass-squared differences in the range $\SI{0.1}{eV^2} \lesssim \abs{\dm[41]}, \abs{\dm[51]} \lesssim \SI{10}{eV^2}$. For $s=1$, we always assume $\dm[41] > 0$, and for $s=2$ we have two cases. When both $\dm[41], \dm[51]>0$, we say "3+2". When one of them is negative, we say "1+3+1".

The appearance probability in the SBL limit (effects of $\dm[21]$ and $\dm[31]$ can be neglected) for the 3+2 case:
\begin{align*}
  P_{\nu_{\alpha} \rightarrow \nu_{\beta}}^{\mathrm{SBL}, 3+2}=4\left|U_{\alpha 4}\right|^{2}\left|U_{\beta 4}\right|^{2} \sin ^{2} \phi_{41}+4\left|U_{\alpha 5}\right|^{2}\left|U_{\beta 5}\right|^{2} \sin ^{2} \phi_{51} & \\
  +8\left|U_{\alpha 4} U_{\beta 4} U_{\alpha 5} U_{\beta 5}\right| \sin \phi_{41} \sin \phi_{51} \cos \left(\phi_{54}-\gamma_{\alpha \beta}\right)
\,,\end{align*}
with 
\begin{align*}
  \phi_{i j} \equiv \frac{\Delta m_{i j}^{2} L}{4 E}, \quad \gamma_{\alpha \beta} \equiv \arg \left(I_{\alpha \beta 54}\right), \quad I_{\alpha \beta i j} \equiv U_{\alpha i}^{*} U_{\beta i} U_{\alpha j} U_{\beta j}^{*}
\,.\end{align*}
Since the probability is invariant under the transformations $4 \leftrightarrow 5$ and $\gamma_{\a \b} \to -\gamma_{\a \b}$, we can restrict the parameter range to $\dm[54] \ge 0$, or equivalently $\dm[51] \ge \dm[41]$. 
The survival probability is given by
\begin{align*}
  P_{\nu_{\alpha} \rightarrow \nu_{\alpha}}^{\mathrm{SBL}, 3+2}
  &=1-4\left(1-\sum_{i=4,5}\left|U_{\alpha i}\right|^{2}\right) \sum_{i=4,5}\left|U_{\alpha i}\right|^{2} \sin ^{2} \phi_{i 1} \\
  &-4\left|U_{\alpha 4}\right|^{2}\left|U_{\alpha 5}\right|^{2} \sin ^{2} \phi_{54}
\,.\end{align*}
We also have the LBL approximations in the limit $\th[41], \th[51], \th[54] \to \infty$ and $\th[21] \to 0 (\dm[21] \to 0)$:
\begin{align*}
  P_{\nu_{\alpha} \rightarrow \nu_{\beta}}^{\mathrm{LBL}, 3+2}
  &= 4\left|U_{\alpha 3}\right|^{2} \abs{U_{\beta 3}}^{2} \sin ^{2} \phi_{31}+2 \sum_{i=4}^{5}\left|U_{\alpha i}\right|^{2}\left|U_{\beta i}\right|^{2}\\
  &+2 \operatorname{Re}\left(I_{\alpha \beta 45}\right)+4 \operatorname{Re}\left(I_{\alpha \beta 43}+I_{\alpha \beta 53}\right) \sin ^{2} \phi_{31} \\
  &+2 \operatorname{Im}\left(I_{\alpha \beta 43}+I_{\alpha \beta 53}\right) \sin \left(2 \phi_{31}\right)
\,,\end{align*}
and the survival probability
\begin{align*}
  P_{\nu_{\alpha} \rightarrow \nu_{\alpha}}^{\mathrm{LBL}, 3+2}
  &= \left(1-\sum_{i=3}^{5}\left|U_{\alpha i}\right|^{2}\right)^{2}+\sum_{i=3}^{5}\left|U_{\alpha i}\right|^{4} \\
  &+2\left(1-\sum_{i=3}^{5}\left|U_{\alpha i}\right|^{2}\right)\left|U_{\alpha 3}\right|^{2} \cos \left(2 \phi_{31}\right)
\,,\end{align*}

We use the following parametrization for U when $n = 3+s = 5$:
\begin{align*}
  U=V_{35} O_{34} V_{25} V_{24} O_{23} O_{15} O_{14} V_{13} V_{12}
\,,\end{align*}
where $O_{ij}$ represents a real rotation matrix by an angle $\th_{ij}$ in the $i-j$ plane, and $V_{ij}$ represents a complex rotation by an angle $\th_{ij}$ and a phase $\varphi_{ij}$. $V_{45}$ mixes sterile states and is unobservable and not included.

Disappearance experiments in the $\ne$ sector probe $\abs{U_{ei}}$. In the SBL limit of the 3+1 scenario, the only relevant parameter is $\abs{U_{e4}}$. For 3+2, $\abs{U_{e5}}$ too.

\begin{align*}
  P_{e e}^{\mathrm{SBL}, 3+1}
  &=1-4\left|U_{e 4}\right|^{2}\left(1-\left|U_{e 4}\right|^{2}\right) \sin ^{2} \frac{\Delta m_{41}^{2} L}{4 E} \\
  &=1-\sin ^{2} 2 \theta_{e e} \sin ^{2} \frac{\Delta m_{41}^{2} L}{4 E}
\,,\end{align*}
where the effective $\ne$ mixing angle is 
\begin{align*}
  \sin^2 2\theta_{ee} = 4 \abs{U_{e4}}^2(1 - \abs{U_{e4}^2})
\,,\end{align*}

\section*{Articles}
\subsection*{Notes from https://inspirehep.net/files/b82d969033bc053e64b4b90b3806ea7f}

A neutrino produced at a source in association with a charged lepton $\ell_\a$ is simply
\begin{align*}
  \ket{\na^s} = \ket{\na}
\,,\end{align*}
and a neutrino that produces a charged lepton $\ell_\b$ at a detector is
\begin{align*}
  \bra{\nb^d} = \bra{\nb}
\,.\end{align*}
The propagation is governed by the time-evolution equation
\begin{align*}
  i \dv{}{t} \begin{pmatrix} 
                \ne \\ \nm \\ \nt
             \end{pmatrix}
  = \frac{1}{2E} 
  \left[ 
    U^\dagger \begin{pmatrix} 
                0 & 0 & 0 \\
                0 & \dm[21] & 0 \\
                0 & 0 & \dm[31]
              \end{pmatrix} 
    U +
    \begin{pmatrix} 
      A & 0 & 0 \\
      0 & 0 & 0 \\
      0 & 0 & 0
    \end{pmatrix}
  \right]
  \begin{pmatrix} 
    \ne \\ \nm \\ \nt
  \end{pmatrix}
\,,\end{align*}
with the matter potential $A = 2\sqrt{2}G_F n_e E $.

BSM, it's possible to have CC-like operators that affect the interactions of neutrinos with charged leptons. If thee operator are not diagonal in the flavor basis, then the production and the detection of neutrinos are affected. Thus, the neutrino state produced at the source in association with the charged lepton $\ell_\a$ then also has components of the other flavor:
\begin{align*}
  \ket{\na^s} &= \ket{\na} + \sum_{\gamma = e,\,\mu,\,\tau} \varepsilon_{\a \gamma}^s \ket{\nu_\gamma} \\
  \bar{\nb^d} &= \bar{\nb} + \sum_{\gamma = e,\,\mu,\,\tau} \varepsilon_{\gamma \b}^d \bra{\nu_\gamma}
\,.\end{align*}
The matrices $\varepsilon^s = (\varepsilon_{\a \gamma}^s)$ and $\varepsilon^d = (\varepsilon^d_{\gamma \beta})$ are complex with 18 real parameters each.

The NC-like operators affect the matter potential:
\begin{align*}
  i \dv{}{t} \begin{pmatrix} 
                \ne \\ \nm \\ \nt
             \end{pmatrix}
  &= \frac{1}{2E} 
  \left[ 
    U^\dagger \begin{pmatrix} 
                0 & 0 & 0 \\
                0 & \dm[21] & 0 \\
                0 & 0 & \dm[31]
              \end{pmatrix} 
  U + A
    \begin{pmatrix} 
      1 + \varepsilon_{ee}^m & \varepsilon_{e\mu}^m & \varepsilon_{e\tau}^m   \\
     \varepsilon_{\mu e}^m   &\varepsilon_{\mu \mu}^m   &\varepsilon_{\mu \tau}^m   \\
     \varepsilon_{\tau e}^m   &\varepsilon_{\tau \mu}^m   &\varepsilon_{\tau \tau}^m  
    \end{pmatrix}
  \right]
  \begin{pmatrix} 
    \ne \\ \nm \\ \nt
  \end{pmatrix}
\,.\end{align*}
For the Hamiltonian to be Hermitian, we require $\varepsilon_{\a\b}^m = \varepsilon_{\b\a}^{m\,*} $.

\subsection*{Notes from 1207.4765}

The probability of observing oscillations is large when $\dm \sim E/L$. For signals in the $\dm \sim \SI{1}{ev^2}$ range, the experiments are therefore designed with $E/L \sim \SI{1}{GeV/km}$. We call these experiments with sensitivity to $\dm \sim \SI{1}{eV^2}$ oscillations "short baseline experiments". In the wave where $E/L \ll \SI{1}{GeV/km}$, the oscillations will be rapid. When $\dm \sim \SI{1}{eV^2}$, the sensitivity to the mass splitting is lost because the oscillation probability averages to only depends on the mixing angle. Thus, "long baseline experiments" probe the mixing angle, but not $\dm$.

If the mass scales are quite different ($m_3 \gg m_2 \gg m_1$), the oscillation phenomena decouple, and the two neutrino mixing model is a good approximation in limited regions.

The short baseline approximation assumes that the tree lowest states $\nu_1, \nu_2, \nu_3$ have masses so small as to be effectively degenerate with zero mass, more explicitly: $\nu_1 =\simeq \nu_2 \simeq \nu_3 = 0$ Thus, it reduces the for to two-, three-, and four-neutrino mass models, corresponding to (3+1), (3+2), and (3+3), respectively. SBL experiments have no $\nt$ sensitivity, so we assume $\abs{U_{\tau i}} = 0$.

In matter, the $\ne$ experiences both CC and NC elastic forward-scattering. $\nm,\nt$ only experience NC forward-scattering.

The data fall into to types:
\begin{itemize}
  \item Disappearance: the active flavor is assumed to have oscillated into a sterile neutrino and/or another flavor which is kinematically not allowed to interact.
  \item Appearance: The transition is between active flaors, but with mass splittings correpsonding to the mostly-sterile states.
\end{itemize}

\subsection*{Notes from 1202.1024}
Setting $\dm[32] \simeq \dm[21] \simeq 0$ and $\dm[41] \simeq \dm[43] \simeq \dm[42]$, and the orthogonality relations $U_{\mu1} U_{e1}^* = -U_{\mu 4}U_{e4}^*$,$\abs{U_{e1}}^2 = 1-\abs{U_{e4}}^2$, and $\sin^2 2\th_{\mu e} = 4 \abs{U_{e4}}^2 \abs{U_{\mu 4}}^2$ we have the $\ne$ appearance probability
\begin{align*}
  P_{\nme} = \sin^2 3\th_{\mu e} sin^2(1.267\dm[41] L/E)
\,,\end{align*}
and the survival probability
\begin{align*}
  P_{\nee} &= 1- \sin^2 2\th_{ee} \sin^2(1.27 \dm[41 L/E]) \\
           &= 1 - 4\abs{U_{e4}}^2(1- \abs{U_{e4}}^2)\sin^2(1.27\dm[41]L/E)
\,.\end{align*}

We can assume that the matter potential $V_s$ experienced by $\ns$ is much larger in amplitude than the standard model matter effect potentials $V_\t{CC}, V_\t{NC}$. Thus,
\begin{align*}
  V = \begin{pmatrix}
    V_\t{CC} + V_\t{NC} & 0 & 0 & 0 \\
    0 & V_\t{NC} & 0 & 0  \\
    0 & 0 & V_\t{NC} & 0  \\
    0 & 0 & 0 & V_s 
  \end{pmatrix}
  \simeq
  \begin{pmatrix}
    0 & 0 & 0 & 0\\
    0 & 0 & 0 & 0\\
    0 & 0 & 0 & 0\\
    0 & 0 & 0 & V_s
  \end{pmatrix}
\,.\end{align*}
We can also assume that the active masses in vaccum are degenerate and negligible. Thus, $\dm[41] = \dm$. Also assume that $m^2_{2,3}/2E$ are negligible relative to $V_s$. We then have the effective Hamiltonian
\begin{align*}
  H_\t{m} = \frac{\dm}{2E}\begin{pmatrix}
    U_{e4}U^*_{e4} & U_{e4}U^*_{\mu4} & U_{e4}U^*_{\tau4} & U_{e4}U^*_{s4} \\
    U_{\mu4}U^*_{e4} & U_{\mu4}U^*_{\mu4} & U_{\mu4}U^*_{\tau4} & U_{\mu4}U^*_{s4} \\
    U_{\tau4}U^*_{e4} & U_{\tau4}U^*_{\mu4} & U_{\tau4}U^*_{\tau4} & U_{\tau4}U^*_{e4} \\
    U_{s4}U^*_{e4} & U_{s4}U^*_{\mu4} & U_{s4}U^*_{\tau4} & U_{s4}U^*_{s4} + 2EV_s/\dm \\
  \end{pmatrix}
\,.\end{align*}
The eigenvalues can be reduced by assuming unitarity together
\begin{align*}
    \lambda_{1}=0 \\
    \lambda_{2}=0 \\
    \lambda_{3}=\frac{1}{4 E}\left(2 E V_{s}+\Delta m^{2}-\sqrt{\left(2 E V_{s}+\Delta m^{2}\right)^{2}-8 E V_{s} \Delta m^{2}\left(1-\left|U_{s 4}\right|^{2}\right)}\right) \\
    \lambda_{4}=\frac{1}{4 E}\left(2 E V_{s}+\Delta m^{2}+\sqrt{\left(2 E V_{s}+\Delta m^{2}\right)^{2}-8 E V_{s} \Delta m^{2}\left(1-\left|U_{s 4}\right|^{2}\right)}\right)
\,.\end{align*}.
If the active favlor content of the fourth mass eigenstate is small, we can approximate 
\begin{align*}
  1 \abs{U_{s4}}^2 \simeq 0
\,,\end{align*}
and all eigenvalues except $\lambda_4 = 1/2E(2EV_s + \dm)$ become zero, implying one effective $\dm_M$, which corresponds to 
\begin{align*}
  \dm_M = \dm + 2EV_s
\,.\end{align*}

By requiring $\abs{U_{e4}}^2 < 0.05$ and $\abs{U_{\mu 4}}^2 < 0.05$, we keep unitarity of the $3 \times 3$ matrix at the $5\%$ level. To keep $L/E \sim \SI{1}{eV^2}$, we can let $A_s$ be in the range \SIrange{10e-3}{10e-9}{eV}

\section*{Diagonalizing H}
\subsection*{2 gen}
\begin{align*}

\,.\end{align*}

\begin{align*}
  H_{M1} &= - \frac{\sqrt{A_{cc}^{2} + 4 A_{cc} \dm[21] \sin^{2}{\left(\theta_{12} \right)} - 2 A_{cc} \dm[21] + (\dm[21])^{2}}}{4 E} \\
  H_{M2,3} &=0 \\
  H_{M4} &= \frac{\sqrt{A_{cc}^{2} + 4 A_{cc} \dm[21] \sin^{2}{\left(\theta_{12} \right)} - 2 A_{cc} \dm[21] + (\dm[21])^{2}}}{4 E}
\,.\end{align*}

\bibliographystyle{apalike}
\bibliography{notes} 
\end{document}

### 2021-03-10 latex/questions.tex
update

\documentclass{article}
\usepackage{physics,amsmath}
\begin{document}

Page 181~\cite{giunti}: It is also important to note that the presence of sterile right-handed neutrino
fields is totally irrelevant for the cancellation of quantum anomalies [31, 201], which
constrain the properties of the other elementary fermion fields [268, 572, 517, 516,
606, 805, 915, 551, 459, 692]. As a consequence, the number of sterile right-handed
neutrino fields is not constrained by the theory, and the introduction of three right-
handed neutrino fields, one for each generation, is not even the minimal extension
of the SM, because the presence of only one right-handed neutrino field cannot be
excluded.

What are the quantum anomalies referring to?

The it is impossible to find a transformation that leaves both the diagonalized Higgs-lepton Yukawa Lagrangian and the right-handed neutrino fields invariant under global U(1) symmetry. So flavour lepton number is broken by sterile neutrinos? Obviously flavour is not conserved, but I thought that this was due to the introduction of mass, not the introduction of right-handed neutrinos.
Ans: If we only have Dirac mass, we make a minimal extension of SM. By introducing more than 1 neutrinos, and a RH- one, 6.55 becomes a matrix eq, and flavour oscilaltes. Wheter the matrix is diagonal or not is dictated by the data.
we have two U(1) symmetris: total lepton number (no flavor). 6.63 breaks this by 2 units (net u1 charge of 2 instead of 0). Outside of osc, flavor is conserved.

CP and T violations depend on the Dirac phases, and if neutrino experiments are independent of the Majorana phases, what is their significance?
Ans: If neutrinos are Dirac, we would only have one Dirac phase (as in quarks). To observe

"We will show that these flavor states reduce to the standard ones in eqn (7.4) in the case of experiments which are not sensitive to the
differences of the contributions of the different neutrino masses to the production
and detection processes. This is the case for all neutrino oscillation experiments."
Is this "differences of the contributions" referring to $\Delta m_{kj}^2$ or just $m_{kj}^2$?

Can IceCube detect CP asymmetry? I.e. is it sensitive to the oscillations of the flavor transition probabilities.

Next month 
Write code for 3 generation neutrino oscillation probability and extend to 3+x, x=0,1,2. 
Code for matter density through earth. Runge kutta is slow. 
Write own code for icecube

I will do both NC and CC. Data classified as cascade events (from NC and CC-electron/tau), or muon events (CC-muon).
NC: neutrino + nucleon(quarks) + Z = neutrino + other nucleons (t-channel) (can be DIS)
hadrons have strong interactions so they shower like crazy

CC neutrino + quarks +W = charged lepton (easy to see)
electron creates shower through bremsstrahlung. muon doesn't

Which parameters can I assume are given, and which parameters will be my "output"?
Should I focus/read up more on atmospheric or solar neutrinos?

Is there a reason to doubt unitarity of the PMNS matrix? Do sterile neutrinos break unitarity?

Why does large mass-squared splittings with sterile neutrinos imply non-unitarity?

P 169 in \cite{heros2020}: Sterile neutrinos produce a very fast oscillations at the ow-energy part of the atmospheric neutrino flux. This that Deepcore may not be sensitive to the sterile neutrinos.

What is the purpose of forecasting data? How is it done, and why?
\bibliographystyle{apalike}
\bibliography{notes}
\end{document}

### 2021-03-10 get_events.py

@@ -30,19 +30,19 @@ def probs(E_index, z_index, alpha, npoints, params=ic_params):
     Et, _, _ = get_Etrue(E_index=E_index,npoints=npoints, model=models, left_alpha=alpha, right_alpha=alpha) 
 
     try:
-        get_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=4)
+        get_probabilities('m','m',E_index, z_index, params,False,npoints,ndim=4)
     except:
         generate_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=4)
     try:
-        get_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=4)
+        get_probabilities('m','m',E_index, z_index, params,True,npoints,ndim=4)
     except:
         generate_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=4)
     try:
-        get_probabilities('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=4)
+        get_probabilities('e','m',E_index, z_index, params,False,npoints,ndim=4)
     except:
         generate_probabilities('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=4)
     try:
-        get_probabilities('e','m',Et,zr,E_index, z_index, params,True,npoints,ndim=4)
+        get_probabilities('e','m',E_index, z_index, params,True,npoints,ndim=4)
     except:
         generate_probabilities('e','m',Et,zr,E_index, z_index, params,True,npoints,ndim=4)
 
@@ -64,7 +64,7 @@ if __name__ == '__main__':
     s24_range = np.logspace(np.log10(args.sFrom),np.log10(args.sTo),args.sN)
     s34_range = np.logspace(np.log10(args.s34From),np.log10(args.s34To),args.s34N)
     param_list = list_of_params(ic_params,dm41_range, s24_range, s34_range=s34_range, s24_eq_s34=args.s34, short=False)
-    print(f'Precomputing probabilities for dm_41({args.dmFrom},{args.dmTo},{args.dmN}), s24({args.sFrom},{args.sTo},{args.sN}), s24({args.s34From},{args.s34To},{args.s34N}), for N = {args.N}. s={args.s+1}/{args.sT}')
[…]

### 2021-03-10 plots/sandhya_paper_1.py

@@ -1,0 +1,79 @@
+# File for plots in 0509197
+from main import *
+
+def fig1():
+    #Fig 1 in sandhyas paper
+    fig, ax = plt.subplots(3,2,sharex=True,sharey=True)
+    ax= ax.flatten()
+    for i,E in enumerate(range(2,8)):
+        x_mat,y_mat=P_num(flavor_from='m', flavor_to='m', E=E, L=None,  param_min=0, param_max=L,earth_start = 0, ndim = 3)
+        x_vac,y_vac=P_num(flavor_from='m', flavor_to='m', E=E, L=None,  param_min=0, param_max=L,earth_start = 0, ndim = 3, vacuum=True)
+        ax[i].plot(x_mat,y_mat[1], label='mm mat', color='black')
+        ax[i].plot(x_vac,y_vac[1], label='mm vac', color='red', linestyle='dotted')
+        ax[i].set_xlim((2000, 12000))
+        ax[i].set_ylim((0, 1))
+        ax[i].set_title(f'E={E} GeV')
+    plt.suptitle(r'3 gen matter and vacuum $P_{\mu\mu}$ as a function of L with fixed E.')
+    plt.show()
+
+
+def fig2():
+    #Fig 2 in sandhyas paper    
+    L_range_Eres = np.linspace(100, 10000, 100)
+    E_baseline = []
+    E_res_all=[]
+    for ell in L_range_Eres:
+        Er = []
+        for th in theta_i:
+            r = get_radial_distance(ell,th)
+            if np.round(r,5) <= r_earth:
+                Eres = 1e-18 * 2e-3 * (1-2*0.1) / (2*V(r)[0])
+                Er.append(Eres)
+            else:
+                #Er.append(0)
+                pass
+        E_baseline.append(np.mean(Er))
+    E_spmin1 = [2/np.pi * 1.27 * 2e-3*x for x in L_range_Eres]
+    E_spmax = [1/np.pi * 1.27 * 2e-3*x for x in L_range_Eres]
+    E_spmin2 = [2/(3*np.pi) * 1.27 * 2e-3*x for x in L_range_Eres]
+    
+    plt.plot(L_range_Eres, E_baseline, label=r'$E_{res,avg}$')
+    plt.plot(L_range_Eres, E_spmin1, label=r'$E_{SPMIN1}$')
+    plt.plot(L_range_Eres, E_spmax, label=r'$E_{SPMAX}$')
[…]

### 2021-03-10 plots/sandya_paper_2.py

@@ -1,0 +1,290 @@
+#File for 0709.1937
+from main import *
+from constants import param_dict,V,theta,dm,GeV2tokm1
+from analytical import P_an
+from numerical import P_num_over_E_single
+from multiprocessing import Pool,Process
+import csv
+import time
+def fig4(type, npoints):
+    L = 2*r_earth
+    L_range = np.linspace(0,L,500)
+    
+    param_dict.update({'dm_31': 2.5e-3,
+                       'dm_21': 8e-5,
+                       'theta_23': np.arcsin(np.sqrt(0.5)),
+                       'theta_13': 0,  
+                       'theta_24': np.arcsin(np.sqrt(0.04)),
+                       'theta_12': np.arcsin(np.sqrt(0.3)),
+                       'delta_ij': 0,
+                       'dm_41': -1,
+                       'theta_14': 0,
+                       'theta_34': np.arcsin(np.sqrt(0.04))
+                        }) 
+    #plt.title(rf'$E = {E}, dm = {param_dict["dm_41"]}, theta_24 = {param_dict["theta_24"]}$')
+    E_range= np.linspace(0.1e3,10e3, npoints)
+    x,P = P_over_E_parameter(type=type,flavor_from='m', flavor_to='m',E_range=E_range, L=L, earth_start = 0, ndim = 4,vacuum=False,param_dict_list=[param_dict],eval_at=L)
+
+    x,P_vac = P_over_E_parameter(type=type,flavor_from='m', flavor_to='m', E_range=E_range, L=L,  earth_start = 0, ndim = 4,vacuum=True,param_dict_list=[param_dict],eval_at=L)
+
+    plt.subplot(221)
+    plt.tight_layout()
+    plt.xscale('log')
+    plt.title(r'$P_{\mu\mu}$')
+    plt.plot(x[0],P[0][1], color='black')
+    plt.plot(x[0],P_vac[0][1], linestyle='dotted', color='darkviolet')
+    plt.ylim((0,1))
+    plt.xlim((0.1e3,10e3))
+    plt.subplot(222)
+    plt.title(r'$P_{\mu\tau}$')
+    plt.xscale('log')
+    plt.tight_layout()
+    plt.plot(x[0],P[0][2], color='black')
[…]

### 2021-03-10 plots/smirnov_2013.py

@@ -1,0 +1,26 @@
+# Plots for Smirnov 2013
+from main import *
+if __name__ == '__main__':
+    E_range = np.linspace(0.1e3,7e3,100)
+    sin_34 = [0,0.1,0.2,0.3,0.5]
+    th_34 = np.arcsin(np.sqrt(sin_34))/2
+    param_dict.update({'dm_21':7.4e-5,
+                       'dm_31':2.4e-3,
+                       'dm_41':1,
+                       'theta_12': 33.36 * np.pi/180,
+                       'theta_23': 45 * np.pi/180,
+                       'theta_13': 8.66 * np.pi/180,
+                       'delta_ij': 300 * np.pi/180,
+                       'theta_12': 33.36 * np.pi/180,
+                       'theta_24': np.arcsin(np.sqrt(0.04))/2})
+    dicts = [dict(param_dict,theta_34=t_34) for t_34 in th_34]
+    theta_1 = np.pi - np.arccos(-0.8)
+    theta_2 = np.pi - np.arccos(-1)
+    x_1,P_1 = P_over_E_parameter('local','m',dicts,E_range,ndim=4,anti=True, theta_i = theta_1)
+    x_2,P_2 = P_over_E_parameter('local','m',dicts,E_range,ndim=4,anti=True, theta_i = theta_2)
+    fig, ax = plt.subplots(2,1,sharex=True,sharey=True)
+    ax= ax.flatten()
+    plot_P_E_params(x_1,P_1, ax[0],'m',legend_name='s34', legend_values= sin_34,ylabel=r'$P_{\bar{\mu}\bar{\mu}}$', xlabel='E (TeV)', title=r'$P_{\bar{\mu}\bar{\mu}}\,, \cos{\theta_z} = -0.8$')
+
+    plot_P_E_params(x_2,P_2, ax[1],'m',legend_name='s34', legend_values= sin_34,ylabel=r'$P_{\bar{\mu}\bar{\mu}}$', xlabel='E (TeV)', title=r'$P_{\bar{\mu}\bar{\mu}}\,, \cos{\theta_z} = -1$')
+    plt.show()

### 2021-03-23 latex/SM.tex
N=13 nsi med s24(0.01,1,10) emm(-0.1,0.1,10), dm=0.93

\documentclass[twocolumn]{article}
\input{commands.tex}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
%\externaldocument{sterile}

\begin{document}
\section{The Standard Model}\label{ch:SM}
In order to describe the three forces of nature, we gather the mediators of each force -- the vector gauge bosons -- into gauge groups. Each vector boson has one corresponding generator in the group that describes the force. 
The strong charge is mediated by eight gluons, which correspond to the eight generators of $\t{SU}(3)_C$. The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$ and the massless boson $\gamma$, which constitute the generators of $\t{SU}(2)_L$. Finally, the massless gauge boson, the photon, is the generator of $\t{U}(1)_Y$. Together, these groups make up the local symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. This symmetry group determines the form of the three coupling constants of nature, whose numerical values but be experimentally derived. Thus, the vector bosons are wholly constrained by the symmetry group. However, the scalar bosons and fermions are free as long as they belong to representations of the symmetry group.

The subscript of each group denotes by which mechanism that force is mediated. The gluons mediate the strong force through interactions of color, $C$. The weak force only sees left-handed particles, $L$. And the electroweak interaction that a particle undergoes is determined by its hypercharge, $Y$. For example, the quarks all have a nonzero color and (hyper)charge, so they participate in the strong and electromagnetic interactions. If a given quark is left-handed, it will also feel the weak interaction. The neutrinos on the other hand have neither charge nor color, so they are insivible to both the strong and electromagnetic force.

\subsection{Lepton mixing}
In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \label{eq:YukawaLagrangian}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
\end{align}
has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the lepton masses being non-definite. This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
\begin{align}\label{eq:leptonYukawaDiag}
    V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
\end{align}
This procedure give the lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
\begin{align}
    \label{eq:j_CC}
    j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
\end{align}
where each fermion field and matrix have an implied $L$ subscript which was dropped for clarity. The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$. However, since we still operate under the SM framework, $\nu_\alpha$ is still massless, since any flavor rotation $V_{L}^{\ell \dagger}$ can make massless fields massive.

The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. When we introduce neutrino mixing, this conservation will be broken. 
%\bibliographystyle{apalike}
%\bibliography{ref}
\end{document}

### 2021-03-23 latex/nsi.tex
N=13 nsi med s24(0.01,1,10) emm(-0.1,0.1,10), dm=0.93

\documentclass[twocolumn]{article}
\input{commands.tex}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
\usepackage[utf8]{inputenc}

\begin{document}
Just as we before only considered matter interactions with electrons, we can extend this to include the up and down quarks which are present in the Earth as components of neutrons and protons. 
Consider interactions beyond the Standard Model through the following Lagrangians,
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with $f \in \{e,u,d\}$. 
\bibliographystyle{apalike}
\bibliography{ref}
\end{document}

### 2021-03-23 latex/sterile.tex
N=13 nsi med s24(0.01,1,10) emm(-0.1,0.1,10), dm=0.93

\documentclass[twocolumn]{article}
\input{commands.tex}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
%\usepackage{hyperref}
\externaldocument{SM}

\begin{document}
\section{Sterile and Massive Neutrinos}\label{ch:sterile}
As we saw in Eq.~\ref{eq:j_CC}
, the neutrino fields $\nu_\alpha$ only couple to the associated lepton fields $\ell_\alpha$, conserving the lepton number $L_\alpha$. We will now introduce two separate extensions to this part of the Standard Model.

We introduce a right-handed neutrino field, $\nu_R$. It has the usual properties of the conventional left-handed neutrino such as hypercharge and color zero. Moreover, since the electroweak gauge group $\t{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, it transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. This neutrino is \emph{sterile} since it doesn't participate any of the SM interactions.

We extend the SM by adding a right-handed component to the Higgs-lepton Yukawa Lagrangian from Eq.~\ref{eq:YukawaLagrangian} with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ ,

\begin{align}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]
\end{align}
Similar to how we diagonalized the lepton Yukawa couplings $Y_{\alpha \beta}^{\prime \ell}$ in Eq.~~\ref{eq:leptonYukawaDiag}, we diagonalize $Y_{\alpha \beta}^{\prime \nu}$ as
\begin{align}
    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
\end{align}
Now, let the neutrino field with chriality $X$ be denoted $n_X$, with components Latin numerals to distinguish them from the flavour components, i.e 
\begin{align}
    \nu_{k X} =  V_{kj X}^{\nu \dagger} \nu_{jX}^\prime\,.
\end{align}
The diagonalized Lagrangian now takes the form 
\begin{align}
    \mathcal{L}_{H} &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}\right.\\
    &\hspace{5.7em}+\left. \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]
\end{align}
Now using the fact that $Y^\nu_{kj}$ is diagonal, we write it as $Y_{k j}^{\nu}=y_{k}^{\nu} \delta_{k j}$, leaving the Lagrangian as 
\begin{align}
    \mathcal{L}_{H} 
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell} \delta_{\alpha \beta} \ell_{\beta R} + \bar{\nu}_{k L} y_{k}^{\nu} \delta_{k j} \nu_{j R}\right] \nonumber \\
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell}  \ell_{\alpha R} + \bar{\nu}_{k L} y_{k}^{\nu} \nu_{k R}\right] \nonumber \\
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}  \bar{\ell}_{\alpha L}\ell_{\alpha R} +  y_{k}^{\nu}\bar{\nu}_{k L} \nu_{k R}\right] 
\end{align}

Now, the Dirac neutrino field is
\begin{align}
    \nu_k = \nu_{kL} + \nu_{kR}\,.
\end{align}
Multiplying $\nu_k$ with its conjugate $\bar{\nu}_k$, we get 
\begin{align}
    \bar{\nu}_k \nu_k 
    & = \bar{\nu}_{k L} \nu_{k L} +\bar{\nu}_{k R}\nu_{k L} + \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k R} \nonumber \\
    & = \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k L} \nonumber \\
    & = \bar{\nu}_{k L}\nu_{k R} + \t{h.c.}
\end{align}
The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and expanding the Higgs VEV into the fields gives us
\begin{align}
    \mathcal{L}_{H} 
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}   \bar{\ell}_\alpha \ell_\alpha  +  y_{k}^{\nu} \bar{\nu}_k \nu_k \right] \nonumber \\
    &=- \frac{y_{\alpha}^{\ell} v}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha   -  \frac{ y_{k}^{\nu} v}{\sqrt{2}} \bar{\nu}_k \nu_k  - \frac{y_{\alpha}^{\ell}}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha H  -  \frac{ y_{k}^{\nu}}{\sqrt{2}} \bar{\nu}_k \nu_k H\,.
\end{align}
Thus, this extension to the SM generates neutrino masses by the Higgs mechanism, in the same fashion as with the charged leptons and the quarks:
\begin{align}
    m_k = \frac{y_k^\nu v}{\sqrt{2}}
\end{align}
%\bibliographystyle{apalike}
%\bibliography{ref}
\end{document}

### 2021-03-23 dataProcesser.py

@@ -145,12 +145,13 @@ def generate_probabilities(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,p
         except FileExistsError: #Sometimes, the dir was already created by another thread
             pass
         np.save(file_dir + filename,res)
-    if anti:
-        with open(f'./pre_computed/{ndim}gen/Pa{flavor_from}a{flavor_to}/{N}/hashed_params.csv','a') as fd:
-            fd.write(f'{params};{filename}\n')
-    else:
-        with open(f'./pre_computed/{ndim}gen/P{flavor_from}{flavor_to}/{N}/hashed_params.csv','a') as fd:
-            fd.write(f'{params};{filename}\n')
+    if E_bin == 5 and z_bin == 5:
+        if anti:
+            with open(f'./pre_computed/{ndim}gen/Pa{flavor_from}a{flavor_to}/{N}/hashed_params.csv','a') as fd:
+                fd.write(f'{params};{filename}\n')
+        else:
+            with open(f'./pre_computed/{ndim}gen/P{flavor_from}{flavor_to}/{N}/hashed_params.csv','a') as fd:
+                fd.write(f'{params};{filename}\n')
     
 
 def train_energy_resolution(recompute=False):

### 2021-03-23 event_processing.py

@@ -170,7 +170,7 @@ def is_precomputed(N,ndim, dict, check=False):
                     raise FileNotFoundError(f'P{flavor_from}{flavor_to} for N={N}, dm={dict["dm_41"]}, s24={np.sin(2*dict["theta_24"])**2}, s34={np.sin(2*dict["theta_34"])**2}, not found')
             return True
 
-def return_precomputed(N,ndim,params):
+def return_precomputed(N,ndim,params, nsi=False):
     params= np.array(params)
     precomputed_list = np.array([is_precomputed(N,ndim, p, check=True) for p in params])
     mask = precomputed_list == True

### 2021-03-23 post_process.py

@@ -14,6 +14,7 @@ flavors = ['Pamam', 'Paeam','Pem','Pmm', 'Pmt','Pamat']
 
 
 def gather_precomputed(npoints=args.N, update=args.u):
+    print('Inserting precomputed arrays into dfs')
     for flavor in flavors:
         for En in E_range:
             for zn in z_range:
@@ -43,6 +44,7 @@ def gather_precomputed(npoints=args.N, update=args.u):
 
 
 def merge_precomputed_df(npoints=args.N):
+    print('Merging precomputed dfs')
     for flavor in flavors:
         for En in E_range:
             for zn in z_range:
@@ -71,6 +73,6 @@ def delete_files(npoints=args.N):
                 except FileNotFoundError:
                     pass
 if __name__ == '__main__':
-    #gather_precomputed(args.N)
+    gather_precomputed(args.N)
     #delete_files(args.N)
-    merge_precomputed_df()
+    #merge_precomputed_df()

### 2021-03-24 latex/SM.tex
update

@@
 The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$.
-However, since we still operate under the SM framework, $\nu_\alpha$ is still massless, since any flavor rotation $V_{L}^{\ell \dagger}$ can make massless fields massive.
+However, since we still operate under the SM framework, $\nu_\alpha$ is still massless, since no flavor rotation $V_{L}^{\ell \dagger}$ can make massless fields massive.
 
-The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. When we introduce neutrino mixing, this conservation will be broken. 
+The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. 
 %\bibliographystyle{apalike}

### 2021-03-24 latex/nsi.tex
update

@@
 \usepackage[utf8]{inputenc}
+\usepackage{xr-hyper}
+\externaldocument{SM}
 
 \begin{document}
+\section{Non-Standard Interactions}
 Just as we before only considered matter interactions with electrons, we can extend this to include the up and down quarks which are present in the Earth as components of neutrons and protons. 
@@
 where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with $f \in \{e,u,d\}$.
+
+We have no independent sensitivity for the neither chirality nor flavor type of $\varepsilon^X$, so we sum over these and study the effective matter NSI parameter $\varepsilon_{\ab}$:
+\begin{align}
+    \varepsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \varepsilon^{fX}_{\ab}\,.
+\end{align}
+Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, we get $N_u/N_e \simeq U_d/N_e \simeq 3$.
+Thus,
+\begin{align}
+    \varepsilon_{\ab} =  \sum_X [\varepsilon_{\ab}^{eX} + 3(\varepsilon_{\ab}^{uX} + \varepsilon_{\ab}^{dX})]
+\end{align}
+Now, $\varepsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix:
+\begin{align}\label{eq:NSIH}
+    H &= \frac{1}{2E} \left[UMU^\dagger + A_{CC}\text{diag}(1,0,0,\kappa) + A_{CC} \varepsilon \right] \nonumber \\
+      &= \frac{1}{2E} \left[UMU^\dagger + A_{CC}
+      \begin{pmatrix}
+          1 + \varepsilon_{ee} & \varepsilon_{e\mu} & \varepsilon_{e\tau} & \varepsilon_{es} \\
+          \varepsilon_{\mu e} & \varepsilon_{\mu\mu} & \varepsilon_{\mu\tau} & \varepsilon_{\mu s} \\
+          \varepsilon_{\tau e} & \varepsilon_{\tau\mu} & \varepsilon_{\tau\tau} & \varepsilon_{\tau s} \\
+          \varepsilon_{ss} & \varepsilon_{s\mu} & \varepsilon_{s\tau} & \kappa+\varepsilon_{ss} \\
+      \end{pmatrix} \right]\,, 
+\end{align}
+where $\kappa$ denotes the ratio $A_{NC}/A_{CC} = N_n/2N_e$ and can be taken to be $\simeq 0.5$ since $N_n/N_e\simeq 1$.
+
+We can draw several conclusions from this form of the Hamiltonian.
+The any nonzero off-diagonal element $\varepsilon_{\ab}, \a \neq \b$ will make the NSI violate lepton flavor, just as the off-diagonal elements of $U$ does in the SM.
+Moreover, since both SM potential entries are of $\mathcal{O}(1)$, any $\varepsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
+As in Ref.~\cite{tommyNSI}, $\varepsilon_{\ab}$ have the scale
+\begin{align}
+    \varepsilon_{\ab} \propto \frac{m_W^2}{m_{\varepsilon}^2} \sim \frac{10^{-2}}{m_\varepsilon^2}\,
+\end{align} 
+in TeV, so the new interactions generated at a mass scale of $m_\varepsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, , two magnitudes below the SM matter effect.
+Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.
 \bibliographystyle{apalike}

### 2021-03-24 latex/oscillations.tex
update

--- 2021-03-23 latex/sterile.tex
@@
 \begin{document}
-\section{Sterile and Massive Neutrinos}\label{ch:sterile}
+\section{Neutrino Masses and Oscillations}\label{ch:oscillation}
 As we saw in Eq.~\ref{eq:j_CC}
@@
 \end{align}
-Now, let the neutrino field with chriality $X$ be denoted $n_X$, with components Latin numerals to distinguish them from the flavour components, i.e 
-\begin{align}
-    \nu_{k X} =  V_{kj X}^{\nu \dagger} \nu_{jX}^\prime\,.
+Now we introduce a crucial difference between the properties of the charged lepton and the neutrino fields.
+While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates.
+This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement of neutrino flavor eigenstates to have a definite mass.
+The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton.
+This is commonly introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
+
+So, let the neutrino field with chriality $X$ be denoted $\nu_X$, with components having Latin numerals to distinguish them from the flavour components, i.e 
+\begin{align}\label{eq:nu_rotation}
+    \nu_{k X} =  V_{k\beta X}^{\nu \dagger} \nu_{\beta X}^\prime\,.
 \end{align}
@@
     \mathcal{L}_{H} &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}\right.\\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}\right.
+\nonumber \\
     &\hspace{5.7em}+\left. \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
@@
 \end{align}
-Now using the fact that $Y^\nu_{kj}$ is diagonal, we write it as $Y_{k j}^{\nu}=y_{k}^{\nu} \delta_{k j}$, leaving the Lagrangian as 
-\begin{align}
+By construction, $Y^\ell_{\alpha \beta}$ and $Y^\nu_{kj}$ are diagonal, so we write them as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as
+\begin{align}\label{eq:L_H}
     \mathcal{L}_{H} 
@@
 \end{align}
+
+Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
+\begin{align}\label{eq:j_CC2}
+    j^\rho_L &= 2\bar{\nu}^\prime_{\alpha L} \gamma^\rho \ell_{\alpha L}^\prime \nonumber \\
+             &= 2\bar{\nu}_{k L} V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} \gamma^\rho  \ell_{\alpha L}
+\end{align}
+Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$
+Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$.
+However, the Higgs-lepton Yukawa Lagrangian
+in Eq.~\ref{eq:L_H} violates lepton number conservation since it couples the charged lepton flavor $\alpha$ to the neutrino mass eigenstate $k$, which is a superposition of flavors.
+There is no transformation that leaves both the interaction and kinetic Lagrangian invariant.
+We now have 
+\begin{align}
+    j^\rho_L &= 2 U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}
+\end{align}
+
+Derivation of neutrino oscillation formula
 %\bibliographystyle{apalike}

### 2021-03-24 dataImporter.py

@@ -31,7 +31,10 @@ def get_aeff_df():
     pickle.dump(df_list,open('./pre_computed/aeff.p','wb'))
     return df_list
 
-
+def get_aeff_df_dc():
+    filename = './data/dc_aeff.csv'
+    dc_aeff = pd.read_csv(filename, names=['logE','Aeff'])
+    return dc_aeff
 
 def get_flux_factor():
     file1 = 'data/event_rate_conv.csv'
@@ -112,8 +115,8 @@ def DC_event_data():
                        [252, 236, 260, 279, 338, 343, 347, 262], 
                        [218, 192, 211, 206, 220, 215, 218, 186], 
                        [182, 197, 206, 206, 171, 137, 128, 113]])
-    z_range = np.linspace(-1,1,9)
-    E_buckets = np.logspace(0.75,1.75,9)
+    z_range = np.linspace(-1,-0.25,8)
+    E_buckets = np.logspace(0.75,1.5,8)
 
     df = pd.DataFrame(events, columns= E_buckets, index=z_range)
     return df

### 2021-03-24 dataProcesser.py

@@ -2,7 +2,7 @@ import numpy as np
 import pandas as pd
 from scipy.interpolate import CloughTocher2DInterpolator as CT
 from functions import mass_dict
-from dataImporter import get_flux_df,get_aeff_df,get_flux_df_DC
+from dataImporter import get_flux_df,get_aeff_df,get_flux_df_DC, get_aeff_df_dc
 from dict_hash import sha256
 import pandas as pd
 from numerical import wrapper 
@@ -14,13 +14,13 @@ from sklearn.gaussian_process.kernels import WhiteKernel, RBF
 def get_flux(flavor,E,z,df):
     '''
     Returns flux for a set of flavor, energy [GeV], and z=cos(theta_z).
-    Returns the absolute value since the flux has a small negative dip at the boundary between the interpolated and extrapolated fluxes at 1e4 GeV. TODO:Fix this in fit_flux()
     '''
     try:
         flux_avg = df[f'{flavor}_flux'][0](E,z)
     except KeyError:
         raise KeyError('NYI for tau flux')
     return np.abs(flux_avg) 
+
 
 def get_aeff(anti,E,z,df_list):
     if anti:
@@ -29,6 +29,14 @@ def get_aeff(anti,E,z,df_list):
         index = 0
     aeff = df_list[index](E,z)
     return aeff
+
+def get_aeff_dc(E,interpolator):
+    try:
+        return interpolator(np.log10(E))
+    except ValueError: #extrapolate
+        y1 = interpolator(1.13)
+        y2 = interpolator(1.2)
+        return (y2-y1)/(1.2-1.13) * np.log10(E)
 
 
 def interpolate_flux(recompute=False):
@@ -140,6 +148,19 @@ def interpolate_aeff(recompute=False):
         pickle.dump(aeff_list,open('./pre_computed/aeff_interpolator.p','wb'))
     return aeff_list
 
+def interpolate_aeff_dc(recompute=False):
+    if not recompute:
+        try:
+            inter = pickle.load(open('./pre_computed/aeff_dc_interpolator.p','rb'))
+        except:
+            raise FileNotFoundError('File aeff_dc_interpolator.p´ not present in ´./pre_computed/´. Run ´interpolate_aeff_dc()´ with recompute = True to generate it.')
+    else:
+        aeff_df = get_aeff_df_dc()
+        from scipy.interpolate import interp1d
[…]

### 2021-03-24 dc_events.py

@@ -1,5 +1,5 @@
 import numpy as np
-from dataProcesser import get_flux,get_aeff, generate_probabilities, get_probabilities, get_Etrue, get_interpolators_dc
+from dataProcesser import get_flux,get_aeff, generate_probabilities, get_probabilities, get_Etrue, get_interpolators_dc,get_aeff_dc
 from dataImporter import *
 from multiprocessing import Pool
 from functions import ic_params, integrate
@@ -20,17 +20,19 @@ def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shif
     Et = np.logspace(np.log10(norm.ppf(1-alpha, scale=0.24*Er[0], loc= Er[0])), 
                          np.log10(norm.ppf(alpha, scale=0.24*Er[-1], loc= Er[-1])),npoints)
 
-    zt = -np.linspace(norm.ppf(1-alpha, scale=-0.1*zr[0], loc= -zr[0]), 
-                         norm.ppf(alpha, scale=-0.1*zr[-1], loc= -zr[-1]),npoints)
-
+    zt = np.linspace(norm.ppf(1-alpha, scale=0.1*np.abs(zr[0]), loc= zr[0]), 
+                         norm.ppf(alpha, scale=0.1*np.abs(zr[-1]+0.001), loc= zr[-1]),npoints)
+    # Reflect zenith around -1
+    mask = zt < -1
+    zt[mask] = -zt[mask] -2
+    
     Eresolution_gaussian = norm.pdf(Et, scale = 0.24*Et, loc=Er)
 
-    zresolution_gaussian = norm.pdf(-zt, scale = -0.1*zt, loc=-zr)
-
+    zresolution_gaussian = norm.pdf(zt, scale = 0.1*np.abs(zt), loc= zr)
+    
     zr_mesh,zt_mesh, Er_mesh, Et_mesh = np.meshgrid(zr,zt, Er, Et)
-
-    aeff_m = 10#interp_aeff(Et_mesh,zt_mesh)
-    aeff_mbar = 20#interp_aeff(Et_mesh,zt_mesh)
+    aeff_m = get_aeff_dc(Et_mesh,interp_aeff)
+    aeff_mbar = aeff_m
 
     if spectral_shift_parameters[0]:
         E_pivot = spectral_shift_parameters[1]
@@ -79,17 +81,16 @@ def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shif
[…]

### 2021-04-04 plotter.py
update

@@ -127,4 +127,4 @@ def oscillogram(E_range, z_range, params, nsi=False):
 
 
 if __name__ == '__main__':
-    P_over_E_parameter('m', [ic_params, ic_params], [1e3])
+    pass

### 2021-04-04 src/events/event_processing.py

@@ -197,7 +197,7 @@ def normalize_events(H0_events,H1_events_list,z_bins):
 
     return H0_normalized, H1_list_normalized
 
-def get_deltachi(H1_list_normalized,H0_normalized,dm41_range,s24_range, delta_T, sigma = [0.25,0.15], f=0.09, x0=[1,0,0], emt_range=None):
+def get_deltachi(H1_list_normalized,H0_normalized,y_range,x_range, delta_T, sigma = [0.25,0.15], f=0.09, x0=[1,0,0], z_range=None):
     sigma_a = sigma[0]
     sigma_b = sigma[1]
     sigma_g = delta_T
@@ -209,23 +209,24 @@ def get_deltachi(H1_list_normalized,H0_normalized,dm41_range,s24_range, delta_T,
     delta_chi = chisq_H1_list - np.min(chisq_H1_list)#chisq_H1_list - chisq_H0
 
     best_fit_index = np.argmin(delta_chi)
-    if emt_range is not None:
-        deltachi_reshaped = delta_chi.reshape(len(s24_range),len(dm41_range),len(emt_range))
+    
+    if z_range is not None:
+        deltachi_reshaped = delta_chi.reshape(len(y_range),len(x_range),len(z_range))
     else:
-        deltachi_reshaped = delta_chi.reshape(len(s24_range),len(dm41_range))
+        deltachi_reshaped = delta_chi.reshape(len(y_range),len(x_range))
     return deltachi_reshaped, best_fit_index, np.min(chisq_H1_list), chisq_H0
 
-def get_contour(deltachi, dm41_range,s24_range):
-    cl_99_bool = np.where(deltachi < chi2.ppf(q = 0.99,df=2),True,False)
-    cl_90_bool = np.where(deltachi < chi2.ppf(q = 0.90,df=2),True,False)
+def get_contour(deltachi, y_range,x_range, df):
+    cl_99_bool = np.where(deltachi < chi2.ppf(q = 0.99,df=df),True,False)
+    cl_90_bool = np.where(deltachi < chi2.ppf(q = 0.90,df=df),True,False)
 
-    s24_cl90_index = get_boundary(cl_90_bool)
-    dm41_cl90_index = np.linspace(0,len(s24_cl90_index)-1,len(s24_cl90_index)).astype('int')
-    s24_cl99_index = get_boundary(cl_99_bool)
[…]

### 2021-04-04 src/make_probs.py

@@ -4,7 +4,7 @@ sys.path.append('./src/data')
 sys.path.append('./src/events')
 sys.path.append('./src/probability')
 import argparse
-from events.events import list_of_params, ic_params
+from events.main import list_of_params, ic_params
 from data.processer import generate_probabilities, get_Etrue, train_energy_resolution, get_probabilities
 import numpy as np
 import time

### 2021-04-19 latex/article/article.tex
update

\documentclass{article}
%\input{commands.tex}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
\newcommand{\emm}{\ensuremath{\varepsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\varepsilon_{\mu\tau}}}
\newcommand{\ett}{\ensuremath{\varepsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\varepsilon^\prime}}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite, graphicx}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Methodology}

In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in an $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.

The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
They are applied as correction factors using the best-fit points from the DeepCore 2019 $\nu_\tau$ appearance 
analysis~\cite{DC2019tauappearance}.

The data events include 14901 track-live events and 26001 cascade-like events, both divided into eight 
$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins.

The neutrino flux at the detector is calculated by propagating atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The oscillation parameters are from the
best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
marginalize over $\Delta m^2_{31}$ and $\theta_{23}$.
The oscillation probability $P_{\alpha \beta}$ then acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
\begin{align}\label{eq:propFlux}
    \Phi_\beta = \sum_\alpha \frac{\dd^2 \phi_\alpha}{\dd E^t \dd \cos{\theta^t_z}} P_{\alpha\beta}\,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in {e,\mu, \bar{e}, \bar{\mu}}$.
The event rate for each bin reads
\begin{align}\label{eq:events}
    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t \nonumber\\
        &\times \left[ \sum_\beta \Phi_\beta  A^\text{eff}_\beta\right]\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$. $R(x^r,x^t)$ is a Gaussian resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. It takes the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}} \exp\left[\frac{(x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
simulated events is skewed. Instead, we assume a log-normal distribution between $E^{true}$ and $E^{reco}$, and train a Gaussian Process Regressor on the dataset, from which
we can extract a predicted mean and standard deviation for each $E^{reco}$. We then sample values from this distribution to yield 
the points of $E^{true}$ at which to integrate over.

In Icecube, the zenith angle resolution for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.48\linewidth]{figures/IC_MC_counts.eps}
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample}\label{fig:IC_MC_counts}
 \end{figure}

Given a Monte Carlo simulation with weights $w_{k\beta}$, we can construct the event count as
\begin{align}\label{eq:MCevents}
    N_{ijk} &= C_{ijk}\sum_{\beta}w_{ijk,\beta} \Phi_\beta\,,
\end{align}
where $C_{k\beta}$ is the correction factor from the detector systematic uncertainty and $\Phi_\beta$ is defined as Eq.~\ref{eq:propFlux}. We have now substituted the effect of the Gaussian smearing 
by treating the reconstructed and true quantities as a migration matrix.

We define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ijk} \frac{\left(N^\text{th}+N^{\mu_{atm}}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}\right)_{ijk}^{2}+\left(\sigma_{\nu + \mu_\text{atm}}^\text{uncor}\right)_{ijk}^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\Delta m_{31}^2, \theta_{23}, \ep, \emt\}$, and the penalty terms $\alpha$ and $\beta$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. 
The event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the analysis.
We use $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{i}^\text{data} = \sqrt{N_{i}^\text{data}}$. 
The term $\sigma_{\nu + \mu_\text{atm}}^\text{uncor}$ accounts for both uncertanties in the finite MC statistics and in the data-driven 
muon background estimate~\cite{DC2019data}.

\bibliographystyle{elsarticle-num}
\bibliography{article}
\end{document}

### 2021-04-19 src/events/IC/make_probs.py

@@ -4,32 +4,36 @@ sys.path.append('./src/data')
 sys.path.append('./src/events')
 sys.path.append('./src/probability')
 import argparse
-from probability.functions import ic_params_nsi
+from functions import nufit_params_nsi, nufit_params_nsi_IO
 from IC.processer import generate_probabilities, get_Etrue, train_energy_resolution, get_probabilities
-from IC.event_processing import list_of_params_nsi
+from DC.event_processing import list_of_params_nsi
 import numpy as np
 import time
 import pandas as pd
 import pickle
 from multiprocessing import Pool
 parser = argparse.ArgumentParser()
-parser.add_argument('-s24From', default=0.01, type=float)
-parser.add_argument('-s24To', default=1, type=float)
-parser.add_argument('-s24N', default=10, type=int)
+parser.add_argument('-dm31From', default=2.489, type=float)
+parser.add_argument('-dm31To', default=2.543, type=float)
+parser.add_argument('-dm31N', default=10, type=int)
+
+parser.add_argument('-th23From', default=48*np.pi/180, type=float)
+parser.add_argument('-th23To', default=50.1*np.pi/180, type=float)
+parser.add_argument('-th23N', default=10, type=int)
+
 parser.add_argument('-emm', default=1e-1, type=float)
 parser.add_argument('-emmN', default=10, type=int)
-parser.add_argument('-emt', default=None, type=float)
+parser.add_argument('-emt', default=1e-2, type=float)
 parser.add_argument('-emtN', default=10, type=int)
-parser.add_argument('-N', default = 13, type=int)
 parser.add_argument('-s', default = 0, type=int)
 parser.add_argument('-sT', default = 1, type=int)
-parser.add_argument('-v', action='store_true')
-parser.add_argument('-Ndim', default=4, type=int)
+parser.add_argument('-nonsi', action='store_false')
+parser.add_argument('-IO', action='store_true')
 args = parser.parse_args()
 
 
 
-def probs(E_index, z_index, alpha, npoints, params=ic_params_nsi, nsi=True, ndim=args.Ndim):
+def probs(E_index, z_index, alpha, npoints, params=nufit_params_nsi, nsi=True, ndim=3):
     z_buckets = np.linspace(-1,0,21)
 
[…]

### 2021-04-19 src/events/IC/make_probs.py
update

@@ -29,6 +29,7 @@ parser.add_argument('-s', default = 0, type=int)
 parser.add_argument('-sT', default = 1, type=int)
 parser.add_argument('-nonsi', action='store_false')
 parser.add_argument('-IO', action='store_true')
+parser.add_argument('-N', default=13, type=int)
 args = parser.parse_args()
 
 

### 2021-04-20 latex/article/article.tex
update

@@
-\documentclass{article}
-%\input{commands.tex}
+\documentclass[draft=True]{revtex4-2}
 \newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
 \newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
-\newcommand{\emm}{\ensuremath{\varepsilon_{\mu\mu}}}
-\newcommand{\emt}{\ensuremath{\varepsilon_{\mu\tau}}}
-\newcommand{\ett}{\ensuremath{\varepsilon_{\tau\tau}}}
-\newcommand{\ep}{\ensuremath{\varepsilon^\prime}}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite, graphicx}
+\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
+\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
+\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
+\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
+\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
 \usepackage[utf8]{inputenc}
@@
 \section{Methodology}
+The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
+Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. 
+The oscillation probability $P_{\alpha \beta}$ then acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
+\begin{align}\label{eq:propFlux}
+    \phi_\beta^\text{det} = \sum_\alpha \frac{\dd^2 \phi_\alpha^\text{atm}}{\dd E^t \dd \cos{\theta^t_z}} P_{\alpha\beta}\,,
+\end{align}
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
+\subsection{IceCube}\label{ch:ICmethod}
+The event rate for each bin reads
+\begin{align}\label{eq:ICevents}
+    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
+    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
+\end{align}
+where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$.
+We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}.
+$R(x^r,x^t)$ is a Gaussian resolution function,
+which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. It takes the form 
+\begin{align}
+    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}} \exp\left[\frac{(x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
+\end{align}
+Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
+simulated events is skewed. Instead, we assume a log-normal distribution between $E^{true}$ and $E^{reco}$, and train a Gaussian Process Regressor on the dataset~\cite{IC2016}, from which
+we can extract a predicted mean and standard deviation for each $E^{reco}$. We then sample values from this distribution to yield 
+the points of $E^{true}$ at which to integrate over.
 
+In Icecube, the zenith angle resolution for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
+\begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
+    \end{center}
+    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}.
+Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
+ \end{figure}
+The data is from the IC86 sterile analysis~\cite{IC2020}.
+
+\subsection{DeepCore}\label{ch:DCmethod}
 In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
@@
 
-The data events include 14901 track-live events and 26001 cascade-like events, both divided into eight 
+The data include 14901 track-live events and 26001 cascade-like events, both divided into eight 
 $ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins.
 
-The neutrino flux at the detector is calculated by propagating atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
-Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The oscillation parameters are from the
+The oscillation parameters are from the
 best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
 marginalize over $\Delta m^2_{31}$ and $\theta_{23}$.
-The oscillation probability $P_{\alpha \beta}$ then acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
-\begin{align}\label{eq:propFlux}
-    \Phi_\beta = \sum_\alpha \frac{\dd^2 \phi_\alpha}{\dd E^t \dd \cos{\theta^t_z}} P_{\alpha\beta}\,,
-\end{align}
-where we sum over the initial lepton flavors $\alpha \in {e,\mu, \bar{e}, \bar{\mu}}$.
-The event rate for each bin reads
-\begin{align}\label{eq:events}
-    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t \nonumber\\
-        &\times \left[ \sum_\beta \Phi_\beta  A^\text{eff}_\beta\right]\,,
-\end{align}
-where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$. $R(x^r,x^t)$ is a Gaussian resolution function, 
-which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. It takes the form 
-\begin{align}
-    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}} \exp\left[\frac{(x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
-\end{align}
-Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
-simulated events is skewed. Instead, we assume a log-normal distribution between $E^{true}$ and $E^{reco}$, and train a Gaussian Process Regressor on the dataset, from which
-we can extract a predicted mean and standard deviation for each $E^{reco}$. We then sample values from this distribution to yield 
-the points of $E^{true}$ at which to integrate over.
-
-In Icecube, the zenith angle resolution for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.48\linewidth]{figures/IC_MC_counts.eps}
-    \end{center}
-    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample}\label{fig:IC_MC_counts}
- \end{figure}
 
@@
 \begin{align}\label{eq:MCevents}
-    N_{ijk} &= C_{ijk}\sum_{\beta}w_{ijk,\beta} \Phi_\beta\,,
+    N_{ijk} &= C_{ijk}\sum_{\beta}w_{ijk,\beta} \phi_\beta^\text{det}\,,
 \end{align}
-where $C_{k\beta}$ is the correction factor from the detector systematic uncertainty and $\Phi_\beta$ is defined as Eq.~\ref{eq:propFlux}. We have now substituted the effect of the Gaussian smearing 
+where $C_{k\beta}$ is the correction factor from the detector systematic uncertainty and $\phi_\beta^\text{det}$ is defined as Eq.~\ref{eq:propFlux}.
+We have now substituted the effect of the Gaussian smearing
 by treating the reconstructed and true quantities as a migration matrix. 
+\subsection{PINGU}\label{ch:PINGUmethod}
+The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}.
+We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+As with the DeepCore data, the PINGU MC is divided into eight 
+$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
+We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
+\begin{align}\label{eq:PINGUparams}
+    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
+    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+\end{align}
 
-We define our $\chi^2$ as
-\begin{align} \label{eq:chisq}
-    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ijk} \frac{\left(N^\text{th}+N^{\mu_{atm}}-N^\text{data}\right)_{ijk}^{2}}
-    {\left(\sigma^\text{data}\right)_{ijk}^{2}+\left(\sigma_{\nu + \mu_\text{atm}}^\text{uncor}\right)_{ijk}^{2}}+ 
+\section{Results}
+For our analyses, we define our $\chi^2$ as
+\begin{align} \label{eq:ICchisq}
+    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
+    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
     \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
 \end{align}
-where we minimize over the model parameters $\hat{\theta} \in \{\Delta m_{31}^2, \theta_{23}, \ep, \emt\}$, and the penalty terms $\alpha$ and $\beta$.
+where we minimize over the model parameters $\hat{\theta} \in \{\Delta m_{31}^2, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
 $N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
-The event count takes the form
+We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}.
+The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
+
+For IceCube, the event count takes the form
 \begin{align}
-    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta})\,,
+    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
 \end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the analysis.
-We use $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
-The observed event number has an associated Poissonian uncertainty $\sigma_{i}^\text{data} = \sqrt{N_{i}^\text{data}}$. 
-The term $\sigma_{\nu + \mu_\text{atm}}^\text{uncor}$ accounts for both uncertanties in the finite MC statistics and in the data-driven 
+with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents} Here, we allow the event distribution to rotate around the median zenith of $-0.5$.
+
+For DeepCore and PINGU, the event count takes the form
+\begin{align}
+    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
+\end{align}
+with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
+The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,.
+For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
 muon background estimate~\cite{DC2019data}.
+
+We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
+assuming (non-)standard interactions. This gives the normalized difference in the
+number of expected events at the detector, and illustrates the expected sensitivity for the NSI parameters.
+
+\begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
+    \end{center}
+    \caption{Expected pulls of predicted event numbers for DeepCore. We compare the NSI event count with $\emt=-0.05$
+     to the standard interaction count}\label{fig:DC_event_pulls}
+ \end{figure}
+
+ \begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
+    \end{center}
+    \caption{Expected pulls of predicted event numbers for PINGU. We compare the NSI event count with $\emt=-0.05$
+    to the standard interaction count}\label{fig:PINGU_event_pulls}
+ \end{figure}
+
+ \begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/PINGU_emm.pdf}
+       %\includegraphics[width=0.4\linewidth]{figures/PINGU_emt.pdf}
+    \end{center}
+    \caption{Expected pulls of predicted event numbers for PINGU. We compare the NSI event count with $\emt=-0.05$
+    to the standard interaction count}\label{fig:PINGU_chisq}
+ \end{figure}
+
+ \begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
+       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
+    \end{center}
+    \caption{Confidence levels from this analysis on the NSI
+    parameters for systematic error and without. The black lines show the 90\% credibility region from~\cite{demidov}.}\label{fig:DC_chisq}
+ \end{figure}
 

### 2021-04-20 plotter.py

@@ -5,6 +5,7 @@ from analytical import P_an
 from functions import ic_params,r_earth, mass_dict
 import matplotlib
 from multiprocessing import Pool
+from IC.main import get_interpolators, get_flux
 matplotlib.rcParams['mathtext.fontset'] = 'cm'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 matplotlib.rc('text', usetex=True)
@@ -107,22 +108,64 @@ def oscillogram(E_range, z_range, params, nsi=False):
     ax.set_yscale('log')
     fig.colorbar(c, ax=ax)
     '''
-    lista_m = [('m', E_range, z, 4, True, params,nsi) for z in z_range]
-    lista_e = [('e', E_range, z, 4, True, params,nsi) for z in z_range]
+    lista_mbar = [('m', E_range, z, 3, True, params,False) for z in z_range]
+    lista_ebar = [('e', E_range, z, 3, True, params,False) for z in z_range]
+    lista_m = [('m', E_range, z, 3, False, params,False) for z in z_range]
+    lista_e = [('e', E_range, z, 3, False, params,False) for z in z_range]
     Pmm = _oscillogram(lista_m)
     Pem = _oscillogram(lista_e)
+    Pamam = _oscillogram(lista_mbar)
+    Paeam = _oscillogram(lista_ebar)
 
-    from main import get_interpolators, get_flux
+    
     interp_flux, interp_aeff, energy_resolution_models = get_interpolators()
     E_mesh, z_mesh = np.meshgrid(E_range, z_range)
+    flux_m = get_flux('m',E_mesh,z_mesh,interp_flux)
+    flux_e = get_flux('e',E_mesh,z_mesh,interp_flux)
     flux_mbar = get_flux('mbar',E_mesh,z_mesh,interp_flux)
     flux_ebar = get_flux('ebar',E_mesh,z_mesh,interp_flux)
 
-    flux_initial = flux_mbar + flux_ebar
-    flux_final = flux_mbar*Pmm + flux_ebar*Pem
+    flux_initial = flux_mbar + flux_ebar + flux_m + flux_e
+    flux_final = flux_mbar*Pamam + flux_ebar*Paeam + flux_m*Pmm + flux_e*Pem
 
     return 1-flux_final/flux_initial
 
+
+def nsi_oscillogram(E_range, z_range, params):
[…]

### 2021-04-20 src/events/IC/make_events.py
update

@@ -9,62 +9,80 @@ import pandas as pd
 from IC.importer import *
 from IC.processer import *
 from IC.event_processing import *
+from DC.event_processing import list_of_params_nsi
 from IC.main import sim_events
-from functions import ic_params_nsi, ic_params
+from functions import nufit_params_nsi, nufit_params_nsi_IO
 import pickle
 import argparse
 parser = argparse.ArgumentParser()
-parser.add_argument('-s24From', default=0.01, type=float)
-parser.add_argument('-s24To', default=1, type=float)
-parser.add_argument('-s24N', default=10, type=int)
+parser.add_argument('-dm31From', default=2.489, type=float)
+parser.add_argument('-dm31To', default=2.543, type=float)
+parser.add_argument('-dm31N', default=10, type=int)
+
+parser.add_argument('-th23From', default=48*np.pi/180, type=float)
+parser.add_argument('-th23To', default=50.1*np.pi/180, type=float)
+parser.add_argument('-th23N', default=10, type=int)
+
 parser.add_argument('-emm', default=1e-1, type=float)
 parser.add_argument('-emmN', default=10, type=int)
-parser.add_argument('-emt', default=None, type=float)
+parser.add_argument('-emt', default=1e-2, type=float)
 parser.add_argument('-emtN', default=10, type=int)
-parser.add_argument('-N', default = 13, type=int)
-parser.add_argument('-Ndim', default=4, type=int)
+parser.add_argument('-s', default = 0, type=int)
+parser.add_argument('-sT', default = 1, type=int)
+parser.add_argument('-nonsi', action='store_false')
+parser.add_argument('-IO', action='store_true')
+parser.add_argument('-N', default=13, type=int)
 args = parser.parse_args()
 
 if __name__ == '__main__':
-    ndim = args.Ndim
-    N = args.N
     alpha = 0.99
-    precomputed_events = False
     gamma=0
-    ic_params_nsi['dm_41'] = 0.93
-    ic_params['dm_41'] = 0.93
-    emm_range = np.linspace(-args.emm,args.emm,args.emmN)
-    if ndim == 3:
-        s24_range = np.linspace(0.,0.,1)
+    if args.IO is False:
+        dm31_range = np.linspace(args.dm31From*1e-3,args.dm31To*1e-3,args.dm31N-1)
[…]

### 2021-04-21 latex/article/article.tex
update

@@
 
+For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construnt the joint $\chi^2$ as 
+\begin{align}
+    \chi^2_{joint} = \chi^2_{IC} + \chi^2_{DC} + \chi^2_{P} - \chi^2_{IC,min} + \chi^2_{DC,min} + \chi^2_{P,min}\,
+\end{align}
+with test statistic $\chi^2_{joint,min}$.
+
+\begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
+       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
+       Cascade-like events
+    \end{center}
+    \caption{Ratio of detector level NSI to SI $\nu_\mu + \bar\nu_\mu$ fluxes. Dotted (dashed) lines show the region in which 90\% of the 
+    DeepCore/PINGU (IceCube) data are contained}\label{fig:flux_ratio}
+ \end{figure}
 \bibliographystyle{elsarticle-num}

### 2021-04-21 plotter.py

@@ -5,7 +5,7 @@ from analytical import P_an
 from functions import ic_params,r_earth, mass_dict
 import matplotlib
 from multiprocessing import Pool
-from IC.main import get_interpolators, get_flux
+from DC.main import get_interpolators_DC, get_flux
 matplotlib.rcParams['mathtext.fontset'] = 'cm'
 matplotlib.rcParams['font.family'] = 'STIXGeneral'
 matplotlib.rc('text', usetex=True)
@@ -97,9 +97,11 @@ def _oscillogram(p_list):
     '''
     p = Pool() 
     res = p.starmap(wrap, p_list)
-    Pmm = np.array(res)[:,1,:]
     p.close()
-    return Pmm
+    Pxm = np.array(res)[:,1,:]
+    Pxe = np.array(res)[:,0,:]
+    Pxt = np.array(res)[:,2,:]
+    return Pxe,Pxm,Pxt
 
 def oscillogram(E_range, z_range, params, nsi=False):
     '''
@@ -118,7 +120,7 @@ def oscillogram(E_range, z_range, params, nsi=False):
     Paeam = _oscillogram(lista_ebar)
 
     
-    interp_flux, interp_aeff, energy_resolution_models = get_interpolators()
+    interp_flux, _ = get_interpolators_DC()
     E_mesh, z_mesh = np.meshgrid(E_range, z_range)
     flux_m = get_flux('m',E_mesh,z_mesh,interp_flux)
     flux_e = get_flux('e',E_mesh,z_mesh,interp_flux)
@@ -131,7 +133,7 @@ def oscillogram(E_range, z_range, params, nsi=False):
     return 1-flux_final/flux_initial
 
 
-def nsi_oscillogram(E_range, z_range, params):
+def nsi_oscillogram(E_range, z_range, params, only_m=True):
     lista_mbar_nsi = [('m', E_range, z, 3, True, params,True) for z in z_range]
     lista_ebar_nsi = [('e', E_range, z, 3, True, params,True) for z in z_range]
     lista_m_nsi = [('m', E_range, z, 3, False, params,True) for z in z_range]
@@ -142,28 +144,36 @@ def nsi_oscillogram(E_range, z_range, params):
[…]

### 2021-04-21 src/events/IC/event_processing.py

@@ -197,11 +197,10 @@ def normalize_events(H0_events,H1_events_list,z_bins):
 
     return H0_normalized, H1_list_normalized
 
-def get_deltachi(H1_list_normalized,H0_normalized,y_range,x_range, delta_T, sigma = [0.25,0.15], f=0.09, x0=[1,0,0], z_range=None):
+def get_deltachi(H1_list_normalized, delta_T, sigma = [0.25,0.15], f=0.09, x0=[1,0,0]):
     sigma_a = sigma[0]
     sigma_b = sigma[1]
     sigma_g = delta_T
-    f = f
     if np.ndim(H1_list_normalized) != 3:
         data = np.sum(IC_observed, axis=0)
     elif H1_list_normalized.shape[2] == 13: 
@@ -209,18 +208,12 @@ def get_deltachi(H1_list_normalized,H0_normalized,y_range,x_range, delta_T, sigm
     else:
         data = IC_observed  
     sigma_syst = f*data
-    x0=x0
-    #chisq_H0, a_H0 = perform_chisq(H0_normalized,data,sigma_syst=sigma_syst,z=zreco,sigma_a=sigma_a,sigma_b=sigma_b,sigma_g=sigma_g , x0=x0)
     chisq_H1_list  = np.array([perform_chisq(H1_norm, data,sigma_syst=sigma_syst,z=zreco, sigma_a=sigma_a,sigma_b=sigma_b,sigma_g=sigma_g, x0=x0)[0] for H1_norm in H1_list_normalized])
     delta_chi = chisq_H1_list - np.min(chisq_H1_list)#chisq_H1_list - chisq_H0
 
     best_fit_index = np.argmin(delta_chi)
     
-    if z_range is not None:
-        deltachi_reshaped = delta_chi.reshape(len(y_range),len(x_range),len(z_range))
-    else:
-        deltachi_reshaped = delta_chi.reshape(len(y_range),len(x_range))
-    return chisq_H1_list, best_fit_index, np.min(chisq_H1_list)#, chisq_H0
+    return chisq_H1_list, best_fit_index
 
 def get_contour(deltachi, y_range,x_range, df):
     cl_99_bool = np.where(deltachi < chi2.ppf(q = 0.99,df=df),True,False)

### 2021-04-21 src/events/IC/main.py

@@ -50,28 +50,28 @@ def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shif
         try:
             Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
         except KeyError:
-            Pmm = generate_probabilitiesOLD('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim)
+            Pmm = generate_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim)
             #gather_specific_prob('Pmm',npoints,E_index,z_index,update=True,ndim=ndim)
             #Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
 
         try:
             P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         except KeyError:
-            P_amam = generate_probabilitiesOLD('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim)
+            P_amam = generate_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim)
             #gather_specific_prob('Pamam',npoints,E_index,z_index,update=True,ndim=ndim)
             #P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         
         try:
             Pem = get_probabilities('e', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
         except KeyError:
-            Pem = generate_probabilitiesOLD('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim)
+            Pem = generate_probabilities('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim)
             #gather_specific_prob('Pem',npoints,E_index,z_index,update=True,ndim=ndim)
             #Pem = get_probabilities('e', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
 
         try:
             P_aeam = get_probabilities('e', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         except KeyError:
-            P_aeam=generate_probabilitiesOLD('e','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim)
+            P_aeam=generate_probabilities('e','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim)
[…]

### 2021-04-21 latex/article/article.tex
update

--- 2021-04-20 latex/article/article.tex
@@
 \newcommand{\ep}{\ensuremath{\epsilon^\prime}}
+\renewcommand{\ne}{\nu_e}
+\newcommand{\nm}{\nu_\mu}
+\newcommand{\nt}{\nu_\tau}
+\newcommand{\ane}{\bar\nu_e}
+\newcommand{\anm}{\bar\nu_\mu}
+\newcommand{\ant}{\bar\nu_\tau}
 \usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
@@
 by treating the reconstructed and true quantities as a migration matrix.
+
 \subsection{PINGU}\label{ch:PINGUmethod}
@@
 We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
 As with the DeepCore data, the PINGU MC is divided into eight 
@@
 We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
+
 \begin{align}\label{eq:PINGUparams}
@@
 
+For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
+\begin{align}
+    \chi^2_{joint} = \chi^2_{IC} + \chi^2_{DC} + \chi^2_{P} - \chi^2_{IC,min} - \chi^2_{DC,min} - \chi^2_{P,min}\,
+\end{align}
+with test statistic $\chi^2_{joint,min}$.
+
+\begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/emm_deltachi.pdf}
+    \end{center}
+    \caption{}\label{fig:emm_deltachi}
+ \end{figure}
+
+ \begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
+    \end{center}
+    \caption{}\label{fig:emm_emp_contour}
+ \end{figure}
+At $90\%$ CL:
+PINGU: $-0.046 < \emm < 0.041$
+DC: $-0.045 < \emm < 0.041$
+joint: $-0.038 < \emm < 0.033$
+\begin{figure}[!tb]
+    \begin{center}
+       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
+       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
+    \end{center}
+    \caption{Ratio of NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
+    DeepCore (IceCube) MC events are contained.}\label{fig:flux_ratio}
+ \end{figure}
 \bibliographystyle{elsarticle-num}

### 2021-04-21 src/data/DC/importer.py

@@ -174,6 +174,8 @@ def get_flux_df_DC():
     new_rightmost['z_min'] = 1
     new_rightmost['z_max'] = 1.1
     df = pd.concat([new_leftmost,df,new_rightmost])
+    from IC.importer import extrapolate_flux
+    df = extrapolate_flux(df)
     return df
 
 if __name__ == '__main__':

### 2021-04-21 src/data/DC/processer.py

@@ -47,9 +47,9 @@ def interpolate_flux_DC(recompute=False):
     colnames = ['m_flux', 'mbar_flux', 'e_flux', 'ebar_flux']
     if not recompute:
         try:
-            inter_df = pickle.load(open('./pre_computed/flux_interpolator_DC.p','rb'))
+            inter_df = pickle.load(open('./pre_computed/flux_interpolator.p','rb'))
         except:
-            raise FileNotFoundError('File ´flux_interpolator_DC.p´ not present in ´./pre_computed/´. Rerun with recompute = True to generate it.')
+            interpolate_flux_DC(recompute=True)
     else:
         df = get_flux_df_DC()
         E = df.GeV
@@ -66,7 +66,7 @@ def interpolate_flux_DC(recompute=False):
             interp_list.append([f_avg])
 
         inter_df = pd.DataFrame(np.transpose(interp_list), columns=colnames)
-        pickle.dump(inter_df,open('./pre_computed/flux_interpolator_DC.p','wb'))
+        pickle.dump(inter_df,open('./pre_computed/flux_interpolator.p','wb'))
     return inter_df
 
 

### 2021-04-22 latex/article/article.tex
update

@@
  \end{figure}
+
+ \newpage
+\begin{tabular}{p{55mm}p{55mm}p{55mm}}
+   DeepCore (2017)
+      \begin{itemize}
+         \item[$\checkmark$] Honda atmospheric fluxes
+         \item[$\times$] Only look at tracks and $\emt$
+         \vspace{1em}  
+         \item[$\times$] DC Monte Carlo from an older dataset 
+         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+         \item[$\times$] 8 z bins from -1 to 0 
+         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
+         \item[$\times$] Prior on spectral index
+         \item[$\times$] No zenith angle normalization
+         \item[$\checkmark$] No priors on $\Delta m_{31}^2, \theta_{23},\theta_{13}$
+      \end{itemize} &
+    Demidov (2020) DC analysis
+      \begin{itemize}
+         \item[$\checkmark$] Honda atmospheric fluxes
+         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
+         \item[$\checkmark$] Data and Monte Carlo from DC 2018
+         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+         \item[$\checkmark$] 8 z bins from -1 to 1
+         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
+         \item[$\times$] Prior on spectral index
+         \item[$\times$] No zenith angle normalization
+         \item[$\checkmark$] No priors on $\Delta m_{31}^2, \theta_{23}$
+         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
+         \item[$\times$] Uncertainty on hadron production in atmosphere
+         \item[$\times$] Uncertainty on neutrino nucleon cross section 
+      \end{itemize} &
+    Choubey et. al. PINGU analysis
+      \begin{itemize}
+         \item[$\checkmark$] Honda atmospheric fluxes
+         \item[$\times$] Only consider $\nm$ events
+         \vspace{1em} 
+         \item[$\times$] $A_\text{eff}$ and resolution from PINGU Letter of intent
+         \item[$\times$] 27 E bins from 2 to $\SI{101}{\electronvolt^2}$
+         \item[$\times$] 10 z bins from -1 to 0
+         \item[$\checkmark$] Flux normalization uncertainty of 20\%
+         \item[$\times$] Uncertanties in cross-section and spectral index 
+         \item[$\checkmark$] Zenith angle uncertainty of 5\% 
+         \item[$\times$] Priors on $\Delta m_{31}^2, \theta_{23},\theta_{13}$
+      \end{itemize} 
+\end{tabular}
+
 \bibliographystyle{elsarticle-num}

### 2021-04-22 plots/sandhya_paper_1.py

@@ -1,79 +1,0 @@
-# File for plots in 0509197
-from main import *
-
-def fig1():
-    #Fig 1 in sandhyas paper
-    fig, ax = plt.subplots(3,2,sharex=True,sharey=True)
-    ax= ax.flatten()
-    for i,E in enumerate(range(2,8)):
-        x_mat,y_mat=P_num(flavor_from='m', flavor_to='m', E=E, L=None,  param_min=0, param_max=L,earth_start = 0, ndim = 3)
-        x_vac,y_vac=P_num(flavor_from='m', flavor_to='m', E=E, L=None,  param_min=0, param_max=L,earth_start = 0, ndim = 3, vacuum=True)
-        ax[i].plot(x_mat,y_mat[1], label='mm mat', color='black')
-        ax[i].plot(x_vac,y_vac[1], label='mm vac', color='red', linestyle='dotted')
-        ax[i].set_xlim((2000, 12000))
-        ax[i].set_ylim((0, 1))
-        ax[i].set_title(f'E={E} GeV')
-    plt.suptitle(r'3 gen matter and vacuum $P_{\mu\mu}$ as a function of L with fixed E.')
-    plt.show()
-
-
-def fig2():
-    #Fig 2 in sandhyas paper    
-    L_range_Eres = np.linspace(100, 10000, 100)
-    E_baseline = []
-    E_res_all=[]
-    for ell in L_range_Eres:
-        Er = []
-        for th in theta_i:
-            r = get_radial_distance(ell,th)
-            if np.round(r,5) <= r_earth:
-                Eres = 1e-18 * 2e-3 * (1-2*0.1) / (2*V(r)[0])
-                Er.append(Eres)
-            else:
-                #Er.append(0)
-                pass
-        E_baseline.append(np.mean(Er))
-    E_spmin1 = [2/np.pi * 1.27 * 2e-3*x for x in L_range_Eres]
-    E_spmax = [1/np.pi * 1.27 * 2e-3*x for x in L_range_Eres]
-    E_spmin2 = [2/(3*np.pi) * 1.27 * 2e-3*x for x in L_range_Eres]
-    
-    plt.plot(L_range_Eres, E_baseline, label=r'$E_{res,avg}$')
-    plt.plot(L_range_Eres, E_spmin1, label=r'$E_{SPMIN1}$')
-    plt.plot(L_range_Eres, E_spmax, label=r'$E_{SPMAX}$')
[…]

### 2021-04-22 plots/sandya_paper_2.py

@@ -1,290 +1,0 @@
-#File for 0709.1937
-from main import *
-from constants import param_dict,V,theta,dm,GeV2tokm1
-from analytical import P_an
-from numerical import P_num_over_E_single
-from multiprocessing import Pool,Process
-import csv
-import time
-def fig4(type, npoints):
-    L = 2*r_earth
-    L_range = np.linspace(0,L,500)
-    
-    param_dict.update({'dm_31': 2.5e-3,
-                       'dm_21': 8e-5,
-                       'theta_23': np.arcsin(np.sqrt(0.5)),
-                       'theta_13': 0,  
-                       'theta_24': np.arcsin(np.sqrt(0.04)),
-                       'theta_12': np.arcsin(np.sqrt(0.3)),
-                       'delta_ij': 0,
-                       'dm_41': -1,
-                       'theta_14': 0,
-                       'theta_34': np.arcsin(np.sqrt(0.04))
-                        }) 
-    #plt.title(rf'$E = {E}, dm = {param_dict["dm_41"]}, theta_24 = {param_dict["theta_24"]}$')
-    E_range= np.linspace(0.1e3,10e3, npoints)
-    x,P = P_over_E_parameter(type=type,flavor_from='m', flavor_to='m',E_range=E_range, L=L, earth_start = 0, ndim = 4,vacuum=False,param_dict_list=[param_dict],eval_at=L)
-
-    x,P_vac = P_over_E_parameter(type=type,flavor_from='m', flavor_to='m', E_range=E_range, L=L,  earth_start = 0, ndim = 4,vacuum=True,param_dict_list=[param_dict],eval_at=L)
-
-    plt.subplot(221)
-    plt.tight_layout()
-    plt.xscale('log')
-    plt.title(r'$P_{\mu\mu}$')
-    plt.plot(x[0],P[0][1], color='black')
-    plt.plot(x[0],P_vac[0][1], linestyle='dotted', color='darkviolet')
-    plt.ylim((0,1))
-    plt.xlim((0.1e3,10e3))
-    plt.subplot(222)
-    plt.title(r'$P_{\mu\tau}$')
-    plt.xscale('log')
-    plt.tight_layout()
-    plt.plot(x[0],P[0][2], color='black')
[…]

### 2021-04-22 plots/smirnov_2013.py

@@ -1,29 +1,0 @@
-# Plots for Smirnov 2013
-import numpy as np 
-import matplotlib.pyplot as plt
-from functions import param_dict
-from plotter import P_over_E_parameter
-if __name__ == '__main__':
-    E_range = np.linspace(0.1e3,7e3,100)
-    sin_34 = [0,0.1,0.2,0.3,0.5]
-    th_34 = np.arcsin(np.sqrt(sin_34))/2
-    param_dict.update({'dm_21':7.4e-5,
-                       'dm_31':2.4e-3,
-                       'dm_41':1,
-                       'theta_12': 33.36 * np.pi/180,
-                       'theta_23': 45 * np.pi/180,
-                       'theta_13': 8.66 * np.pi/180,
-                       'delta_ij': 300 * np.pi/180,
-                       'theta_12': 33.36 * np.pi/180,
-                       'theta_24': np.arcsin(np.sqrt(0.04))/2})
-    dicts = [dict(param_dict,theta_34=t_34) for t_34 in th_34]
-    theta_1 = np.pi - np.arccos(-0.8)
-    theta_2 = np.pi - np.arccos(-1)
-    x_1,P_1 = P_over_E_parameter('local','m',dicts,E_range,ndim=4,anti=True, theta_i = theta_1)
-    x_2,P_2 = P_over_E_parameter('local','m',dicts,E_range,ndim=4,anti=True, theta_i = theta_2)
-    fig, ax = plt.subplots(2,1,sharex=True,sharey=True)
-    ax= ax.flatten()
-    plot_P_E_params(x_1,P_1, ax[0],'m',legend_name='s34', legend_values= sin_34,ylabel=r'$P_{\bar{\mu}\bar{\mu}}$', xlabel='E (TeV)', title=r'$P_{\bar{\mu}\bar{\mu}}\,, \cos{\theta_z} = -0.8$')
-
-    plot_P_E_params(x_2,P_2, ax[1],'m',legend_name='s34', legend_values= sin_34,ylabel=r'$P_{\bar{\mu}\bar{\mu}}$', xlabel='E (TeV)', title=r'$P_{\bar{\mu}\bar{\mu}}\,, \cos{\theta_z} = -1$')
-    plt.show()

### 2021-04-22 plotter.py

@@ -103,12 +103,43 @@ def _oscillogram(p_list):
     Pxt = np.array(res)[:,2,:]
     return Pxe,Pxm,Pxt
 
-def oscillogram(E_range, z_range, params, nsi=False):
+def oscillogram(E_range, z_range, params):
     '''
-    fig, ax = plt.subplots(1, figsize=(8,6))
-    c=ax.pcolormesh(z_range, E_range,P,cmap='jet', shading='auto')
-    ax.set_yscale('log')
-    fig.colorbar(c, ax=ax)
+    Returns (Pex, Pmx, Paeax, Pamax)
+    '''
+    lista_mbar = [('m', E_range, z, 3, True, params,False) for z in z_range]
+    lista_ebar = [('e', E_range, z, 3, True, params,False) for z in z_range]
+    lista_m = [('m', E_range, z, 3, False, params,False) for z in z_range]
+    lista_e = [('e', E_range, z, 3, False, params,False) for z in z_range]
+
+    Pmx = _oscillogram(lista_m)
+    Pex = _oscillogram(lista_e)
+    Pamax = _oscillogram(lista_mbar)
+    Paeax = _oscillogram(lista_ebar)
+
+    return Pex, Pmx, Paeax, Pamax
+def nsi_oscillogram(E_range, z_range, params):
+    '''
+    Returns (Pex_nsi, Pmx_nsi, Paeax_nsi, Pamax_nsi)
+    '''
+    lista_mbar_nsi = [('m', E_range, z, 3, True, params,True) for z in z_range]
+    lista_ebar_nsi = [('e', E_range, z, 3, True, params,True) for z in z_range]
+    lista_m_nsi = [('m', E_range, z, 3, False, params,True) for z in z_range]
+    lista_e_nsi = [('e', E_range, z, 3, False, params,True) for z in z_range]
+
+    
+
+    Pmx_nsi = _oscillogram(lista_m_nsi)
+    Pex_nsi = _oscillogram(lista_e_nsi)
+    Pamax_nsi = _oscillogram(lista_mbar_nsi)
+    Paeax_nsi = _oscillogram(lista_ebar_nsi)
+
+    return Pex_nsi, Pmx_nsi, Paeax_nsi, Pamax_nsi
+
+
+def flux_oscillogram(E_range, z_range, params, nsi=False):
+    '''
+    Returns 1-flux_final/flux_initial for Pxm
     '''
     lista_mbar = [('m', E_range, z, 3, True, params,False) for z in z_range]
[…]

### 2021-04-22 src/events/DC/event_processing.py

@@ -88,23 +88,18 @@ def perform_chisq(events, data,background,sigma_syst, z = np.linspace(-1,1,9), s
     assert res.success, res
     return res.fun, res.x
 
-def get_deltachi(H1_list,y_range,x_range, delta_T, sigma = [0.25,0.15], f=0.09, x0=[1,0,0], z_range=None):
+def get_deltachi(H1_list, delta_T, sigma = [0.25,0.15], f=0.09, x0=[1,0,0]):
     sigma_a = sigma[0]
     sigma_b = sigma[1]
     sigma_g = delta_T
     data = np.array([get_hist(events2018_DC().query(f'pid==0'), 'count_events'),get_hist(events2018_DC().query(f'pid==1'), 'count_events')])
     background =np.array([get_hist(events2018_DC().query(f'pid==0'), 'count_background'),get_hist(events2018_DC().query(f'pid==1'), 'count_background')])
     sigma_syst = f * np.array([get_hist(events2018_DC().query(f'pid==0'), 'abs_uncert'),get_hist(events2018_DC().query(f'pid==1'), 'abs_uncert')])
-    chisq_H1_list  = np.array([perform_chisq(H1, data, background,z=zbins_2018, sigma_syst=sigma_syst,sigma_a=sigma_a,sigma_b=sigma_b,sigma_g=sigma_g, x0=x0)[0] for H1 in H1_list])
-    delta_chi = chisq_H1_list - np.min(chisq_H1_list)
+    chisq_H1_list  = np.array([perform_chisq(H1, data, background,z=zreco, sigma_syst=sigma_syst,sigma_a=sigma_a,sigma_b=sigma_b,sigma_g=sigma_g, x0=x0)[0] for H1 in H1_list])
 
-    best_fit_index = np.argmin(delta_chi)
+    best_fit_index = np.argmin(chisq_H1_list)
     
-    if z_range is not None:
-        deltachi_reshaped = delta_chi.reshape(len(y_range),len(x_range),len(z_range))
-    else:
-        deltachi_reshaped = delta_chi.reshape(len(y_range),len(x_range))
-    return chisq_H1_list, best_fit_index, np.min(chisq_H1_list)#, chisq_H0
+    return chisq_H1_list, best_fit_index
 
 def get_contour(deltachi, y_range,x_range, df):
     cl_99_bool = np.where(deltachi < chi2.ppf(q = 0.99,df=df),True,False)

### 2021-04-26 src/data/DC/processer.py
update

@@ -14,6 +14,7 @@ from numerical import P_num
 import h5py
 from scipy.stats import lognorm
 import pickle
+import time
 
 pdg_dict={'e':12,'m':14,'t':16}
 Ebins_2018 = [5.623413,  7.498942, 10. , 13.335215, 17.782795, 23.713737, 31.622776, 42.16965 , 56.23413]
@@ -112,7 +113,11 @@ def generate_probabilities_DC(flavor_from, flavor_to, E_range,z_range,E_bin,z_bi
     if anti:
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
-    f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
+    try:
+        f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
+    except OSError: #File busy, try again
+        time.sleep(np.random.random())
+        f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
     try:
         dset = f.create_dataset(f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}', data=prob, chunks=True)
         for key in param_dict.keys():

### 2021-04-26 src/events/make_probs.py

@@ -18,14 +18,14 @@ parser.add_argument('-dm31N', default=10, type=int)
 parser.add_argument('-th23N', default=10, type=int)
 
 parser.add_argument('-ett', default=5e-2, type=float)
-parser.add_argument('-ettN', default=10, type=int)
+parser.add_argument('-ettN', default=1, type=int)
 parser.add_argument('-emt', default=2e-2, type=float)
-parser.add_argument('-emtN', default=10, type=int)
+parser.add_argument('-emtN', default=1, type=int)
 
 parser.add_argument('-eem', default=2e-1, type=float)
-parser.add_argument('-eemN', default=10, type=int)
+parser.add_argument('-eemN', default=1, type=int)
 parser.add_argument('-eet', default=2e-1, type=float)
-parser.add_argument('-eetN', default=10, type=int)
+parser.add_argument('-eetN', default=1, type=int)
 
 parser.add_argument('-s', default = 0, type=int)
 parser.add_argument('-sT', default = 1, type=int)
@@ -79,7 +79,7 @@ def event_wrapper(param_list):
     E_index,z_index, alpha, params, npoints,nsi = param_list[0], param_list[1], param_list[2], param_list[3], param_list[4], param_list[5]
     return probs(E_index=E_index, z_index=z_index, params=params, npoints=npoints, alpha=alpha, nsi=nsi)
 
-def precompute_probs(args_tuple, nsi=True):
+def precompute_probs(args_tuple):
     i,j,params = args_tuple
     if args.PINGU:
         res_track = get_events_PINGU(Ebin=i,zbin=j,params=params,pid=1,nsi=args.nonsi)
@@ -128,7 +128,6 @@ if __name__ == '__main__':
     rng.shuffle(arg_tuples)
     split_arg_tuples=  np.array_split(arg_tuples,args.sT)[args.s]
     start = time.time()
-
 
     p=Pool()
     for i, res in enumerate(p.imap(precompute_probs, split_arg_tuples), 1):

### 2021-04-26 src/data/DC/processer.py
upldate

@@ -92,10 +92,13 @@ def get_probabilities_DC(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,pid
     if anti:
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
-    try:
-        f = h5py.File(f'./pre_computed/DC/E{Ebin}z{zbin}.hdf5', 'r')
-    except OSError:
-        raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/DC/')
+    for i in range(10):
+        try:
+            f = h5py.File(f'./pre_computed/DC/E{Ebin}z{zbin}.hdf5', 'r')
+        except OSError: #File busy, try again
+            time.sleep(np.random.random())
+            f = h5py.File(f'./pre_computed/DC/E{Ebin}z{zbin}.hdf5', 'r')
+        #raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/DC/')
     try:
         fh = f[f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}']
     except KeyError:

### 2021-04-26 src/data/DC/processer.py
update

@@ -116,11 +116,12 @@ def generate_probabilities_DC(flavor_from, flavor_to, E_range,z_range,E_bin,z_bi
     if anti:
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
-    try:
-        f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
-    except OSError: #File busy, try again
-        time.sleep(np.random.random())
-        f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
+    for i in range(10):
+        try:
+            f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
+        except OSError: #File busy, try again
+            time.sleep(np.random.random())
+            f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
     try:
         dset = f.create_dataset(f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}', data=prob, chunks=True)
         for key in param_dict.keys():

### 2021-04-26 src/data/PINGU/processer.py

@@ -11,6 +11,7 @@ from numerical import P_num
 import h5py
 from scipy.stats import lognorm
 import pickle
+import time
 pdg_dict={'e':12,'m':14,'t':16}
 Ebins_2018 = [5.623413,  7.498942, 10. , 13.335215, 17.782795, 23.713737, 31.622776, 42.16965 , 56.23413]
 zbins_2018 = [-1., -0.75, -0.5 , -0.25,  0., 0.25, 0.5, 0.75, 1.]
@@ -24,10 +25,13 @@ def get_probabilities_PINGU(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,
     if anti:
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
-    try:
-        f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
-    except OSError:
-        raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/PINGU/')
+    for i in range(10):
+        try:
+            f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
+        except OSError: #File busy, try again
+            time.sleep(np.random.random())
+            f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
+        #raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/PINGU/')
     try:
         fh = f[f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}']
     except KeyError:
@@ -47,7 +51,12 @@ def generate_probabilities_PINGU(flavor_from, flavor_to, E_range,z_range,E_bin,z
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
     
-    f = h5py.File(f'./pre_computed/PINGU/E{E_bin}z{z_bin}.hdf5', 'a')
+    for i in range(10):
+        try:
+            f = h5py.File(f'./pre_computed/PINGU/E{E_bin}z{z_bin}.hdf5', 'a')
+        except OSError: #File busy, try again
+            time.sleep(np.random.random())
+            f = h5py.File(f'./pre_computed/PINGU/E{E_bin}z{z_bin}.hdf5', 'a')
     try:
[…]

### 2021-04-26 src/data/PINGU/processer.py
update

@@ -30,7 +30,7 @@ def get_probabilities_PINGU(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,
             f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
         except OSError: #File busy, try again
             time.sleep(np.random.random())
-            f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
+            #f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
         #raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/PINGU/')
     try:
         fh = f[f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}']
@@ -56,7 +56,7 @@ def generate_probabilities_PINGU(flavor_from, flavor_to, E_range,z_range,E_bin,z
             f = h5py.File(f'./pre_computed/PINGU/E{E_bin}z{z_bin}.hdf5', 'a')
         except OSError: #File busy, try again
             time.sleep(np.random.random())
-            f = h5py.File(f'./pre_computed/PINGU/E{E_bin}z{z_bin}.hdf5', 'a')
+            #f = h5py.File(f'./pre_computed/PINGU/E{E_bin}z{z_bin}.hdf5', 'a')
     try:
         dset = f.create_dataset(f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}', data=prob, chunks=True)
         for key in param_dict.keys():

### 2021-04-26 src/data/DC/processer.py
update

@@ -92,13 +92,10 @@ def get_probabilities_DC(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,pid
     if anti:
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
-    for i in range(10):
-        try:
-            f = h5py.File(f'./pre_computed/DC/E{Ebin}z{zbin}.hdf5', 'r')
-        except OSError: #File busy, try again
-            time.sleep(np.random.random())
-            f = h5py.File(f'./pre_computed/DC/E{Ebin}z{zbin}.hdf5', 'r')
-        #raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/DC/')
+    try:
+        f = h5py.File(f'./pre_computed/DC/E{Ebin}z{zbin}.hdf5', 'r')
+    except OSError:
+        raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/DC/')
     try:
         fh = f[f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}']
     except KeyError:
@@ -108,36 +105,33 @@ def get_probabilities_DC(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,pid
     f.close()
     return res
 
-def generate_probabilities_DC(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,param_dict,anti,pid, ndim=4, nsi=True, overwrite=False):
+def generate_probabilities_DC(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,param_dict,anti,pid, ndim=4, nsi=True, save=True):
     if not nsi:
         param_dict = dc_params
     prob = np.array([P_num(flavor_from=flavor_from, E=E_range[i], ndim = ndim, anti=anti,params=param_dict,zenith=z, nsi=nsi)[mass_dict[flavor_to],-1] for i,z in enumerate(z_range)]).reshape(-1,1)
-    hashed_param_name = sha256(param_dict)
-    if anti:
-        flavor_from = 'a' + flavor_from
-        flavor_to = 'a' + flavor_to
-    for i in range(10):
+    if save:
+        hashed_param_name = sha256(param_dict)
+        if anti:
+            flavor_from = 'a' + flavor_from
+            flavor_to = 'a' + flavor_to
+
+        f = h5py.File(f'./pre_computed/DC/E{E_bin}z{z_bin}.hdf5', 'a')
         try:
[…]

### 2021-04-26 src/events/make_events.py

@@ -13,23 +13,26 @@ from PINGU.main import get_all_events as PINGU_events
 from DC.main import get_all_events as DC_events
 from IC.main import sim_events as IC_events
 from functions import nufit_params_nsi, nufit_params_nsi_IO
+from PINGU.main import get_events as get_events_PINGU
+from DC.main import get_events as get_events_DC
+from tqdm import tqdm
 import pickle
 import argparse
-from multiprocessing import Pool
+from tqdm.contrib.concurrent import process_map
 parser = argparse.ArgumentParser()
 
 parser.add_argument('-dm31N', default=10, type=int)
 parser.add_argument('-th23N', default=10, type=int)
 
 parser.add_argument('-ett', default=5e-2, type=float)
-parser.add_argument('-ettN', default=10, type=int)
+parser.add_argument('-ettN', default=1, type=int)
 parser.add_argument('-emt', default=2e-2, type=float)
-parser.add_argument('-emtN', default=10, type=int)
+parser.add_argument('-emtN', default=1, type=int)
 
 parser.add_argument('-eem', default=2e-1, type=float)
-parser.add_argument('-eemN', default=10, type=int)
+parser.add_argument('-eemN', default=1, type=int)
 parser.add_argument('-eet', default=2e-1, type=float)
-parser.add_argument('-eetN', default=10, type=int)
+parser.add_argument('-eetN', default=1, type=int)
 
 parser.add_argument('-s', default = 0, type=int)
 parser.add_argument('-sT', default = 1, type=int)
@@ -38,6 +41,17 @@ parser.add_argument('-IC', action='store_true')
 parser.add_argument('-DC', action='store_true')
 parser.add_argument('-PINGU', action='store_true')
 args = parser.parse_args()
+i = 0
+
+def compute_events(arg_tuple):
+    Ebin, zbin, params = arg_tuple
+    if args.PINGU:
+        track = get_events_PINGU(Ebin,zbin,params,pid=1,nsi=True,save=False)
+        cascade = get_events_PINGU(Ebin,zbin,params,pid=0,nsi=True,save=False)
+    elif args.DC:
+        track = get_events_DC(Ebin,zbin,params,pid=1,nsi=True,save=False)
+        cascade = get_events_DC(Ebin,zbin,params,pid=0,nsi=True,save=False)
+    return np.array([cascade, track])
 
 if __name__ == '__main__':
[…]

### 2021-04-26 latex/article/article.tex
update

@@
 The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
-Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. 
+Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
+production height of 15 km and an Earth radius of 6371 km. 
 The oscillation probability $P_{\alpha \beta}$ then acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
 \begin{align}\label{eq:propFlux}
-    \phi_\beta^\text{det} = \sum_\alpha \frac{\dd^2 \phi_\alpha^\text{atm}}{\dd E^t \dd \cos{\theta^t_z}} P_{\alpha\beta}\,,
+    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
 \end{align}
@@
 
-The data include 14901 track-live events and 26001 cascade-like events, both divided into eight 
-$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins.
-
-The oscillation parameters are from the
-best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\Delta m^2_{31}$ and $\theta_{23}$.
-
-Given a Monte Carlo simulation with weights $w_{k\beta}$, we can construct the event count as
+The data include 14901 track-like events and 26001 cascade-like events, both divided into eight 
+$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{k\beta}$,
+from which we can construct the event count as
 \begin{align}\label{eq:MCevents}
@@
 by treating the reconstructed and true quantities as a migration matrix.
+
+The oscillation parameters used on our DeepCore simulations are from the
+best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
+marginalize over $\Delta m^2_{31}$ and $\theta_{23}$.
 

### 2021-04-26 src/data/PINGU/processer.py

@@ -25,13 +25,11 @@ def get_probabilities_PINGU(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,
     if anti:
         flavor_from = 'a' + flavor_from
         flavor_to = 'a' + flavor_to
-    for i in range(10):
-        try:
-            f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
-        except OSError: #File busy, try again
-            time.sleep(np.random.random())
-            #f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
-        #raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/PINGU/')
+
+    try:
+        f = h5py.File(f'./pre_computed/PINGU/E{Ebin}z{zbin}.hdf5', 'r')
+    except OSError:
+        raise KeyError(f'E{Ebin}z{zbin}.hdf5 doesnt exist in ./pre_computed/PINGU/')
     try:
         fh = f[f'{ndim}gen/P{flavor_from}{flavor_to}/{pid}/{hashed_param_name}']
     except KeyError:
@@ -42,37 +40,34 @@ def get_probabilities_PINGU(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,
     f.close()
     return res
 
-def generate_probabilities_PINGU(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,param_dict,anti,pid, ndim=4, nsi=True, overwrite=False):
+def generate_probabilities_PINGU(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,param_dict,anti,pid, ndim=4, nsi=True, save=True):
     if not nsi: #Use best fit to generate 'data'. nufit_params_nsi has all epsilon=0
         param_dict = nufit_params_nsi
     prob = np.array([P_num(flavor_from=flavor_from, E=E_range[i], ndim = ndim, anti=anti,params=param_dict,zenith=z, nsi=nsi)[mass_dict[flavor_to],-1] for i,z in enumerate(z_range)]).reshape(-1,1)
-    hashed_param_name = sha256(param_dict)
-    if anti:
-        flavor_from = 'a' + flavor_from
-        flavor_to = 'a' + flavor_to
-    
-    for i in range(10):
+    if save:
+        hashed_param_name = sha256(param_dict)
+        if anti:
[…]

### 2021-04-26 src/events/DC/main.py

@@ -11,7 +11,7 @@ df = MC2018_DC()
 interp_flux,_ = get_interpolators_DC()
 systematics = systematics2018_DC()
 
-def get_events(Ebin,zbin,params,pid,nsi, no_osc=False):
+def get_events(Ebin,zbin,params,pid,nsi, no_osc=False, save=True):
     binned_df = get_binned_DC(pid,Ebin,zbin,df)
     events = 0
     
@@ -36,11 +36,11 @@ def get_events(Ebin,zbin,params,pid,nsi, no_osc=False):
         try:
             Pe = get_probabilities_DC('e', flavor_to, Ebin,zbin,params,anti=False,pid=pid,ndim=3,nsi=nsi).reshape(-1,)
         except KeyError:
-            Pe = generate_probabilities_DC('e', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi).reshape(-1,)
+            Pe = generate_probabilities_DC('e', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi, save=save).reshape(-1,)
         try:
             Pm = get_probabilities_DC('m', flavor_to, Ebin,zbin,params,anti=False,pid=pid,ndim=3,nsi=nsi).reshape(-1,)
         except KeyError:
-            Pm = generate_probabilities_DC('m', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi).reshape(-1,)
+            Pm = generate_probabilities_DC('m', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi, save=save).reshape(-1,)
         if not no_osc:
             rate_weight[mask] = binned_df[mask]['weight'] * (m_flux*Pm + e_flux*Pe)
         else:
@@ -58,11 +58,11 @@ def get_events(Ebin,zbin,params,pid,nsi, no_osc=False):
         try:
             Pebar = get_probabilities_DC('e', flavor_to, Ebin,zbin,params,anti=True,pid=pid,ndim=3,nsi=nsi).reshape(-1,)
         except KeyError:
-            Pebar = generate_probabilities_DC('e', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=True, pid=pid, ndim=3, nsi=nsi).reshape(-1,)
[…]

### 2021-04-26 src/events/PINGU/main.py

@@ -11,7 +11,7 @@ from functions import dc_params_nsi,dc_params, nufit_params_nsi
 df = MC_PINGU()
 interp_flux,_ = get_interpolators_DC()
 
-def get_events(Ebin,zbin,params,pid,nsi):
+def get_events(Ebin,zbin,params,pid,nsi,save=True):
     binned_df = get_binned_PINGU(pid,Ebin,zbin,df)
     events = 0
     
@@ -36,11 +36,11 @@ def get_events(Ebin,zbin,params,pid,nsi):
         try:
             Pe = get_probabilities_PINGU('e', flavor_to, Ebin,zbin,params,anti=False,pid=pid,ndim=3,nsi=nsi).reshape(-1,)
         except KeyError:
-            Pe = generate_probabilities_PINGU('e', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi).reshape(-1,)
+            Pe = generate_probabilities_PINGU('e', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi, save=save).reshape(-1,)
         try:
             Pm = get_probabilities_PINGU('m', flavor_to, Ebin,zbin,params,anti=False,pid=pid,ndim=3,nsi=nsi).reshape(-1,)
         except KeyError:
-            Pm = generate_probabilities_PINGU('m', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi).reshape(-1,)
+            Pm = generate_probabilities_PINGU('m', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=False, pid=pid, ndim=3, nsi=nsi, save=save).reshape(-1,)
 
         rate_weight[mask] = binned_df[mask]['weight'] * (m_flux*Pm + e_flux*Pe)
 
@@ -53,17 +53,17 @@ def get_events(Ebin,zbin,params,pid,nsi):
         try:
             Pebar = get_probabilities_PINGU('e', flavor_to, Ebin,zbin,params,anti=True,pid=pid,ndim=3,nsi=nsi).reshape(-1,)
         except KeyError:
-            Pebar = generate_probabilities_PINGU('e', flavor_to, Etrue, ztrue, Ebin, zbin, params, anti=True, pid=pid, ndim=3, nsi=nsi).reshape(-1,)
[…]

### 2021-04-26 src/events/DC/main.py
update

@@ -77,6 +77,7 @@ def get_events(Ebin,zbin,params,pid,nsi, no_osc=False, save=True):
     return np.sum(res) #np.sum(binned_df["rate_weight"])
 
 
-def get_all_events(params, pid, nsi, no_osc=False,save=True):
-    result = [get_events(Ebin,zbin,params,pid,nsi,no_osc,save) for Ebin in range(8) for zbin in range(8)]
-    return np.array(result).reshape(8,8)
+def get_all_events(params, nsi, no_osc=False,save=True):
+    cascades = np.array([get_events(Ebin,zbin,params,0,nsi,no_osc,save) for Ebin in range(8) for zbin in range(8)]).reshape(8,8)
+    tracks = np.array([get_events(Ebin,zbin,params,1,nsi,no_osc,save) for Ebin in range(8) for zbin in range(8)]).reshape(8,8)
+    return np.array([cascades, tracks])

### 2021-04-26 src/events/make_events.py

@@ -13,8 +13,6 @@ from PINGU.main import get_all_events as PINGU_events
 from DC.main import get_all_events as DC_events
 from IC.main import sim_events as IC_events
 from functions import nufit_params_nsi, nufit_params_nsi_IO
-from PINGU.main import get_events as get_events_PINGU
-from DC.main import get_events as get_events_DC
 from tqdm import tqdm
 import pickle
 import argparse
@@ -41,17 +39,14 @@ parser.add_argument('-IC', action='store_true')
 parser.add_argument('-DC', action='store_true')
 parser.add_argument('-PINGU', action='store_true')
 args = parser.parse_args()
-i = 0
 
-def compute_events(arg_tuple):
-    Ebin, zbin, params = arg_tuple
+
+def compute_events(params):
     if args.PINGU:
-        track = get_events_PINGU(Ebin,zbin,params,pid=1,nsi=True,save=False)
-        cascade = get_events_PINGU(Ebin,zbin,params,pid=0,nsi=True,save=False)
+        result = PINGU_events(params,snsi=True,save=False)
     elif args.DC:
-        track = get_events_DC(Ebin,zbin,params,pid=1,nsi=True,save=False)
-        cascade = get_events_DC(Ebin,zbin,params,pid=0,nsi=True,save=False)
-    return np.array([cascade, track])
+        result = DC_events(params,nsi=True,save=False)
+    return result
 
 if __name__ == '__main__':
     assert args.PINGU or args.DC or args.IC
@@ -71,20 +66,17 @@ if __name__ == '__main__':
     param_dict = nufit_params_nsi_IO if args.IO else nufit_params_nsi
 
     param_list = list_of_params_nsi(param_dict, dm31_range, th23_range, ett_range, emt_range, eem_range, eet_range)
-    arg_tuples = [(i,j, p) for i in range(8) for j in range(8) for p in param_list]
     
     #data = [(p) for p in param_list]
     if args.PINGU:
         #p = Pool()
-        H1_events_list = process_map(compute_events, arg_tuples)
+        H1_events_list = process_map(compute_events, param_list)
 
-        H1_events_list = np.array(H1_events_list).reshape(len(param_list),2,8,8)
         #p.close()
[…]

### 2021-04-26 src/events/make_events.py
update

@@ -43,7 +43,7 @@ args = parser.parse_args()
 
 def compute_events(params):
     if args.PINGU:
-        result = PINGU_events(params,snsi=True,save=False)
+        result = PINGU_events(params,nsi=True,save=False)
     elif args.DC:
         result = DC_events(params,nsi=True,save=False)
     return result

### 2021-04-26 src/events/PINGU/main.py
update

@@ -64,6 +64,7 @@ def get_events(Ebin,zbin,params,pid,nsi,save=True):
     return np.sum(binned_df["rate_weight"])
 
 
-def get_all_events(params, pid, nsi, save=True):
-    result = [get_events(Ebin,zbin,params,pid,nsi,save) for Ebin in range(8) for zbin in range(8)]
-    return np.array(result).reshape(8,8)
+def get_all_events(params, nsi, no_osc=False,save=True):
+    cascades = np.array([get_events(Ebin,zbin,params,0,nsi,save) for Ebin in range(8) for zbin in range(8)]).reshape(8,8)
+    tracks = np.array([get_events(Ebin,zbin,params,1,nsi,save) for Ebin in range(8) for zbin in range(8)]).reshape(8,8)
+    return np.array([cascades, tracks])

### 2021-04-26 latex/article/article.tex
update

@@
 \newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
+\newcommand{\eet}{\epsilon_{e\tau}}
+\newcommand{\eem}{\epsilon_{e\mu}}
 \newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
@@
 \newcommand{\ant}{\bar\nu_\tau}
+\newcommand{\dm}{\Delta m^2_{31}}
+\newcommand{\sth}{\sin^2(2\theta_{23})}
+
 \usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
@@
 Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. 
-The oscillation probability $P_{\alpha \beta}$ then acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
+production height of 15 km and an Earth radius of 6371 km. %TODO: add more here?
+
+The oscillation probability $P_{\alpha \beta}$ acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
 \begin{align}\label{eq:propFlux}
@@
 \end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of NSI on both probability
+and flux level, we plot the oscillograms in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
+DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
+and DeepCore track events originating from $\nm$ fluxes are contained.
+
+\begin{figure}[!tb]
+   \begin{center}
+      \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
+      \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
+   \end{center}
+   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
+   DeepCore (IceCube) MC events are contained. \emph{Left panel:} Propagated fluxes of $\ne$ and $\nt$ neutrinos and anti-neutrinos. 
+   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale
+\end{figure}
+
 \subsection{IceCube}\label{ch:ICmethod}
@@
 We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}.
-$R(x^r,x^t)$ is a Gaussian resolution function,
-which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. It takes the form 
+$R(x^r,x^t)$ is a resolution function,
+which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
 \begin{align}
-    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}} \exp\left[\frac{(x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
+    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
 \end{align}
 Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
-simulated events is skewed. Instead, we assume a log-normal distribution between $E^{true}$ and $E^{reco}$, and train a Gaussian Process Regressor on the dataset~\cite{IC2016}, from which
-we can extract a predicted mean and standard deviation for each $E^{reco}$. We then sample values from this distribution to yield 
-the points of $E^{true}$ at which to integrate over.
-
-In Icecube, the zenith angle resolution for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
+simulated events is skewed in energy. To model this bias between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
+we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $E^\text{true}$ points of the 99th percentile of each distribution to obtain
+the limits of $E^\text{true}$ at which to integrate over.
+We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
+The data is from the IC86 sterile analysis~\cite{IC2020}.
 \begin{figure}[!tb]
@@
  \end{figure}
-The data is from the IC86 sterile analysis~\cite{IC2020}.
 
@@
 In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
-IceCube collaboration in an $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.
+IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.
 
@@
 The data include 14901 track-like events and 26001 cascade-like events, both divided into eight 
-$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{k\beta}$,
+$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{ijk,\beta}$,
 from which we can construct the event count as
@@
 best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\Delta m^2_{31}$ and $\theta_{23}$.
+marginalize over $\dm$ and $\theta_{23}$.
+
+We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
+assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
+number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
+
+\begin{figure}[!tb]
+   \begin{center}
+      \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
+      \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
+   \end{center}
+   \caption{Expected pulls of predicted event numbers for DeepCore and PINGU after 3 years. We compare the NSI event count with $\emt=-0.05$
+    to the standard interaction count}\label{fig:event_pulls} %TODO: remake these with clearer titles and better labels
+\end{figure}
 
@@
 \begin{align}\label{eq:PINGUparams}
-    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
+    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
     &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
@@
 \end{align}
-where we minimize over the model parameters $\hat{\theta} \in \{\Delta m_{31}^2, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
+where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
 $N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
@@
 
-We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
-assuming (non-)standard interactions. This gives the normalized difference in the
-number of expected events at the detector, and illustrates the expected sensitivity for the NSI parameters.
+First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
+which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
 
@@
     \begin{center}
-       \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
+       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_ett.pdf}
+       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_emt.pdf}
+       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eem.pdf}
+       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eet.pdf}
     \end{center}
-    \caption{Expected pulls of predicted event numbers for DeepCore. We compare the NSI event count with $\emt=-0.05$
-     to the standard interaction count}\label{fig:DC_event_pulls}
- \end{figure}
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
-    \end{center}
-    \caption{Expected pulls of predicted event numbers for PINGU. We compare the NSI event count with $\emt=-0.05$
-    to the standard interaction count}\label{fig:PINGU_event_pulls}
- \end{figure}
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/PINGU_emm.pdf}
-       %\includegraphics[width=0.4\linewidth]{figures/PINGU_emt.pdf}
-    \end{center}
-    \caption{Expected pulls of predicted event numbers for PINGU. We compare the NSI event count with $\emt=-0.05$
-    to the standard interaction count}\label{fig:PINGU_chisq}
+    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all NSI 
+    parameters not shown in each plot are set to zero.}\label{fig:PINGU_3D}
  \end{figure}
@@
     \end{center}
-    \caption{Confidence levels from this analysis on the NSI
-    parameters for systematic error and without. The black lines show the 90\% credibility region from~\cite{demidov}.}\label{fig:DC_chisq}
+    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
  \end{figure}
@@
 \begin{align}
-    \chi^2_{joint} = \chi^2_{IC} + \chi^2_{DC} + \chi^2_{P} - \chi^2_{IC,min} - \chi^2_{DC,min} - \chi^2_{P,min}\,
+    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
 \end{align}
-with test statistic $\chi^2_{joint,min}$.
+with test statistic $\chi^2_\text{joint,min}$.
 
@@
  \end{figure}
-At $90\%$ CL:
-PINGU: $-0.046 < \emm < 0.041$
-DC: $-0.045 < \emm < 0.041$
-joint: $-0.038 < \emm < 0.033$
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
-       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
-    \end{center}
-    \caption{Ratio of NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
-    DeepCore (IceCube) MC events are contained.}\label{fig:flux_ratio}
- \end{figure}
+%At $90\%$ CL:
+%PINGU: $-0.046 < \emm < 0.041$
+%DC: $-0.045 < \emm < 0.041$
+%joint: $-0.038 < \emm < 0.033$
+
+%TODO: table with individual and combined chisq values. Discussion on impact of IC on chisq.
 
@@
          \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\Delta m_{31}^2, \theta_{23},\theta_{13}$
+         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
       \end{itemize} &
@@
          \item[$\checkmark$] Data and Monte Carlo from DC 2018
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
          \item[$\checkmark$] 8 z bins from -1 to 1
@@
          \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\Delta m_{31}^2, \theta_{23}$
+         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
          \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
@@
       \end{itemize} &
-    Choubey et. al. PINGU analysis
+    Our DC+PINGU analysis
       \begin{itemize}
          \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\times$] Only consider $\nm$ events
+         \item[$\checkmark$] Tracks and cascades for all flavors
          \vspace{1em} 
-         \item[$\times$] $A_\text{eff}$ and resolution from PINGU Letter of intent
-         \item[$\times$] 27 E bins from 2 to $\SI{101}{\electronvolt^2}$
-         \item[$\times$] 10 z bins from -1 to 0
-         \item[$\checkmark$] Flux normalization uncertainty of 20\%
-         \item[$\times$] Uncertanties in cross-section and spectral index 
-         \item[$\checkmark$] Zenith angle uncertainty of 5\% 
-         \item[$\times$] Priors on $\Delta m_{31}^2, \theta_{23},\theta_{13}$
+         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
+         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
+         \item[$\checkmark$] Flux normalization uncertainty of 25\%
+         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
+         \item[$\checkmark$] No priors on oscillation parameters 
+         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
       \end{itemize} 

### 2021-04-26 src/events/DC/event_processing.py

@@ -119,7 +119,7 @@ def list_of_params_nsi(dicta, dm31_range, th23_range, ett_range, emt_range, eem_
         dict2 = dicta.copy()
         dict2.update(p)
         return dict2
-    dict_list = [update_dict(dicta,{'e_ee':-tt,'e_em':eem,'e_et':eet,'e_mm':-tt,'e_mt':mt,'theta_23':th23, 'dm_31':dm31}) for eet in eet_range for eem in eem_range for mt in emt_range for tt in ett_range for th23 in th23_range for dm31 in dm31_range]
+    dict_list = [update_dict(dicta,{'e_em':eem,'e_et':eet,'e_tt':tt,'e_mt':mt,'theta_23':th23, 'dm_31':dm31}) for eet in eet_range for eem in eem_range for mt in emt_range for tt in ett_range for th23 in th23_range for dm31 in dm31_range]
     return dict_list
 
 def get_param_list(dm31N,th23N, ett, ettN, emt, emtN, eem, eemN, eet, eetN, IO=False):

### 2021-04-26 latex/article/article.tex
update

@@
 
-The oscillation probability $P_{\alpha \beta}$ acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
+The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux at detector level for flavor $\beta$ as 
 \begin{align}\label{eq:propFlux}
@@
 \end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of NSI on both probability
-and flux level, we plot the oscillograms in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
+and flux level, we plot the oscillograms resulting from Eq.\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
 DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
-and DeepCore track events originating from $\nm$ fluxes are contained.
+and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
+is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore, on the other hand, 
+observes multiple fringes of flux surpluses with a factor $\sim 10^1$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
+energy-independent but zenith-sensetive IceCube deficiency.
+
+For the fluxes which drives cascades, we have to resort to the DeepCore detector alone. %TODO: fill more
+Here we see a somewhat weaker signal, this time a zenith-independent deficiency. 
+%TODO: fill with conclusion
 
@@
       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
+      \hspace{1.5cm}
       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
    \end{center}
-   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
+   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. We set $\emt = -0.05$, and all other NSI parameters to zero. 
+   Dotted (dashed) lines show the regions in which 99\% of the 
    DeepCore (IceCube) MC events are contained. \emph{Left panel:} Propagated fluxes of $\ne$ and $\nt$ neutrinos and anti-neutrinos. 
-   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale
+   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale and fix limits
 \end{figure}
@@
 \end{align}
-Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
-simulated events is skewed in energy. To model this bias between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
+As seen in Fig.~\ref{fig:IC_MC_counts}, the energy reconstruction is biased.
+To model this relationship between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
 we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $E^\text{true}$ points of the 99th percentile of each distribution to obtain
@@
     \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
+       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
     \end{center}
@@
       \end{itemize} &
-    Our DC+PINGU analysis
+    This DC+PINGU analysis
       \begin{itemize}

### 2021-04-28 latex/oscillations.tex
update

@@
-\documentclass[twocolumn]{article}
+\documentclass[draft=True]{revtex4-2}
 \input{commands.tex}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
+\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, slashed}
 \usepackage[utf8]{inputenc}
+%\usepackage{hyperref}
 \usepackage{xr-hyper}
-%\usepackage{hyperref}
 \externaldocument{SM}
@@
 \begin{document}
+
 \section{Neutrino Masses and Oscillations}\label{ch:oscillation}
@@
 We now have 
+\begin{align}\label{eq:j_CC3} %TODO: put sums on all above?
+    j^\rho_L &= 2 \sum_\alpha \sum_k U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}
+\end{align}
+Now, the Fourier expansion of the field operator $\bar{\nu}_{k L}$ in Eq.~\ref{eq:j_CC3} contains creation operators $a^\dagger_{\nu_k}$
+of massive neutrinos with mass $m_k$. This means that the summation over the mass index $k$ constructs a flavor neutrino, which interacts with the charged lepton field $\ell_{\a L}$.
+In other words, the charged current generates a flavor neutrino $\na$, which is a superposition of the mass eigenstates 
+$\nu_k$ with weights $U_{\a k}^*$. In the ket-formalism, we express this as
+\begin{align}\label{eq:osc_1}
+    \ket{\na} = \sum_k U^*_{\a k} \ket{\nu_k}\,.
+\end{align}
+It is the mass eigenstates $\ket{\nu_k}$ that are eigenstates of the Hamiltonian, with eigenvalues
+\begin{align}\label{eq:disp}
+    E_k = \sqrt{\vec{p}^2 + m_k^2}\,.
+\end{align}
+The solution to the time-dependent Schrödinger equation 
 \begin{align}
-    j^\rho_L &= 2 U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}
+    i \dv{}{t} \ket{\nu_k(t)} = H\ket{\nu_k(t)}\,,
+\end{align}
+gives us a plane wave evolution to the mass states as 
+\begin{align}
+    \ket{\nu_k(t)} = e^{-iE_kt}\ket{\nu_k}\,.
+\end{align}
+Inserting the plane wave solution into Eq.~\ref{eq:osc_1}, we get 
+\begin{align}\label{eq:nat}
+    \ket{\na(t)} = \sum_k U^*_{\a k} e^{-iE_kt}\ket{\nu_k}\,.
+\end{align}
+Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse? We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
+\begin{align}\label{eq:osc_k}
+    \sum_\a U_{\a k}\ket{\na} &= \sum_{\alpha, j} U_{\a k} U_{\a j}^* \ket{\nu_j} \nonumber \\
+    \sum_\a U_{\a k}\ket{\na} &= \sum_{j} \delta_{kj} \ket{\nu_j} \nonumber \\
+    \sum_\a U_{\a k}\ket{\na} &= \ket{\nu_k}\,,
+\end{align}
+where we have used the unitarity of the leptonic mixing matrix. Eqs.~\ref{eq:osc_1} and \ref{eq:nat} yield 
+\begin{align}
+    \ket{\na(t)} &= \sum_k U^*_{\a k} e^{-iE_kt}\ket{\nu_k} \nonumber \\
+    \ket{\na(t)} &= \sum_k U^*_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
+    \ket{\na(t)} &= \sum_{k,\b} U^*_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
+\end{align}
+The probability of the flavor transition $\na \to \nb$ at time $t$ is $\abs{\bra{\nb}\ket{\na (t)}}^2$:
+\begin{align}
+    P_{\na \to \nb}(t) = \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
 \end{align}
 
-Derivation of neutrino oscillation formula
+We assume the neutrino masses $m_k$ to be extremely small compared to their associated energies $E_k$.
+Thus, $v\approx 1$, and $\abs{\vec{p}} \approx E$ making the energy-dispersion relation of Eq.~\ref{eq:disp} to first order:
+\begin{align}
+    E_k &= \sqrt{\vec{p}^2 + m_k^2} \nonumber \\
+        &= \vec{p}^2\sqrt{1 + \frac{m_k^2}{\vec{p}^2}} \nonumber \\
+        &\approx E + \frac{m_k^2}{2E}
+\end{align}
+Hence, the exponential can be simplified, and simplifying the notation $P_{\na \to \nb}(t) \to P_{\ab}(t)$ we get 
+\begin{align}
+    P_{\ab}(t) = \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)t/2E}\,.
+\end{align}
+
+Now, our approximation $v\approx 1$ implies $x\approx t $, thus
+\begin{align}
+    P_{\ab}(x) &= \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
+                       &= \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E})\,,
+\end{align}
+where we in the last step have defined the \emph{mass squared-difference} $\dm_{kj} = m_k^2 - m_j^2$. Thus, it is impossible
+to measure the mass states $m_k$ through neutrino oscillations, since they depend on the difference between the two squared mass states instead of the
+masses themselves. 
+Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^* = \delta_{\a \b}$ yields 
+\begin{align}
+    \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 = \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^* U_{\b k} U_{\a j} U_{\b j}^*]
+\end{align}
+In this work, we will always assume the mixing matrix $U$ to be real. 
+We thus write 
+\begin{align}\label{eq:Pab}
+    P_{\ab} &= \sum_{k,j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \nonumber \\
+            &\hspace{2em}+ \sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} \nonumber \\
+            & \hspace{3em}+\sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} \nonumber \\
+            &\hspace{3em}+ 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\exp(-i\frac{\dm_{kj}x}{2E})\right] \nonumber \\
+            &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\cos(\frac{\dm_{kj}x}{2E})\right] \nonumber \\
+            &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
+\end{align}
+which is the probability of neutrino vacuum oscillations. %TODO: maybe plot?
+The calculation for antineutrinos yield the same result if one assumes the realness of the mixing matrix.
+
+\subsection{Matter effects}
+\begin{figure}\label{fig:w_and_z}
+    \includegraphics[width=0.1\textwidth]{figures/w-boson.pdf}
+    \hspace{2cm}
+    \includegraphics[width=0.1\textwidth]{figures/z-boson.pdf}
+\end{figure}
+In this work, we are concerned about the interactions with the neutrino and Earth-like matter, i.e. electrons, protons, and neutrons. 
+The possible interactions are shown in Fig. ~\ref{fig:w_and_z}. The left panel shows that the only flavor that can go through charged current (CC) 
+interactions is the electron flavor. This is because the Earth doesn't consist of any muons or tau particles. 
+The right panel shows any neutrino flavor interaction via the neutral current (NC) with Earth-like matter, mediated by the neutral $Z$ boson
+ we see weak forward CC and NC scattering. 
+The interaction mediated by the $W$ boson will give rise to a effective matter potential $V_{CC}$, while
+the $Z$ boson is responsible for $V_{NC}$. Our task is now to find expressions for these.
+
+\subsection{Effective matter potentials}
+
+We start with the effective Hamiltonian for the CC process. The Feynman rules for the left panel give us 
+\begin{align}
+    H = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, e \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, \ne \right]
+\end{align}
+By using the Fierz transformation 
+\begin{align}
+    \mathcal{L}^{V-A}(\psi_1,\psi_2,\psi_3,\psi_4) = \mathcal{L}^{V-A}(\psi_1,\psi_4,\psi_3,\psi_2)\,,
+\end{align}
+we can permute the terms inside the brackets, yielding
+\begin{align}\label{eq:H_fierz}
+    H = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, e \right]\,.
+\end{align}
+Now, lets consider a finite volume $V$ with electron states defined as 
+\begin{align}\label{eq:e_states}
+    \ket{e(p_e,h_e)} = \frac{1}{2E_eV}a_e^{(h_e)\dagger}(p_e)\ket{0}\,,
+\end{align}
+i.e. using the creation operator $a_e^{(h_e)\dagger}(p_e)$ to create electron states from vacuum with momenta $p_e$, energy $E_e$, and helicity $h_e$.
+The density distribution of electrons in $V$ is $f(E_e,T)$, which we normalize to the total number of electrons as we integrate out the momenta $p_e$:
+\begin{align}\label{eq:e_density}
+    \int \dd p_e^3 f(E_e,T) = N_e V = n_e
+\end{align}
+Here, the electron density $N_e$ will ultimately determine the strength of the effective matter potential. 
+To obtain the average effective Hamiltonian, project it on the electron states in Eq.~\ref{eq:e_states} and integrate over the density and sum over the helicities:
+
+\begin{align}\label{eq:avg_H1}
+    \bar H &= \int \dd p_e^3 \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
+           &= \frac{G_F}{\sqrt{2}} \int \dd p_e^3 \bra{e(p_e,h_e)} \left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right]  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \left[\bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x) \right] \ket{e(p_e,h_e)} \nonumber \\
+           &= \frac{G_F}{\sqrt{2}} \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \int \dd p_e^3  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \bra{e(p_e,h_e)} \bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x)   \ket{e(p_e,h_e)}\,.
+\end{align}
+First, calculate the sum using trace technology %TODO: explain this more
+\begin{align}\label{eq:helicity_sum}
+    \frac{1}{2} \sum_{h_e} \bra{e(p_e,h_e)} \bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x)   \ket{e(p_e,h_e)} &= \frac{1}{4E_e V} \sum_{h_e} \bar{u}_e^{h_e}(p_e) \,\gamma_\rho\, (1- \gamma^5)\, u_e^{h_e}(p_e) \nonumber \\
+    &= \frac{1}{4 E_e V} \Trace{\left[ \sum_{h_e} \bar{u}_e^{h_e}(p_e) u_e^{h_e}(p_e) \,\gamma_\rho\, (1- \gamma^5)\, \right]} \nonumber \\
+    &= \frac{1}{4 E_e V} \Trace{\left[ (\slashed{p}_e + m_e ) \,\gamma_\rho\, (1- \gamma^5)\, \right]} \nonumber \\
+    &= \frac{(p_e)_\rho}{E_e V}
+\end{align}
+Eq.~\ref{eq:avg_H1} now becomes 
+\begin{align}\label{eq:avg_H2}
+    \avg{H} &= \frac{G_F}{\sqrt{2}E_e V} \bar\ne \, (1- \gamma^5)\, \ne \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T)\,.
+\end{align}
+Expand the integral, and use the fact that $\vec{p}_e$ is odd:
+\begin{align}
+    \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T) &= \int \dd p_e^3\, f(E_e,T) (\gamma^0 E_e - \vec{p}_e \cdot \vec{gamma}) \nonumber \\
+                                              &= \int \dd p_e^3\, f(E_e,T) \gamma^0 E_e \nonumber \\
+                                              &= \gamma_0 E_e N_e V\,.
+\end{align}
+Inserting this into Eq.~\ref{eq:avg_H2}, we have
+\begin{align}
+    \avg{H} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
+            &= \sqrt{2}G_F N_e \bar{\nu}_{Le} \gamma^0 \nu_{Le}\,,
+\end{align}
+where the projection operator $(1- \gamma^5)$ ensures that only the left-hand compontent of the neutrino fields interact weakly. Thus 
+\begin{align}\label{V_CC1}
+    V_{CC} = \sqrt{2}G_F N_e
+\end{align}
+
+For neutral current, we replace the electron field $e(x)$ in Eq.~\ref{eq:H_fierz} by the fermion field $f(x)$, and the projection operator 
+$(1-\gamma^5)$ with $(g_V^f - g_A^f\gamma^5)$. Again, the $\gamma^5$ will cause the spacial component of $p_f$ to disappear after integration, and the 
+only difference between the average effective Hamiltonian for the neutral current is then the factor $g_V^f$:
+\begin{align}
+    V^f_{NC} = \sqrt{2}G_F N_A g_V^f\,.
+\end{align}
+Summing over the fermions, and assuming electrical neutrality and equal abundance of protons and neutrons, we have
+\begin{align}
+    V_{NC} &= \sum_{f \in {e,p,n}} V^f_{NC} \nonumber \\
+           &= \sqrt{2}G_F N_A \sum_{f \in {e,p,n}} g_V^f \nonumber \\
+           &= \sqrt{2}G_F N_A\left[ -\frac{1}{2}+2\sin^2{(\theta_W)} + \frac{1}{2}-2\sin^2{(\theta_W)} -\frac{1}{2} \right] \nonumber \\
+           &= -\frac{1}  {\sqrt{2}} G_F N_e\,,
+\end{align}
+where the electrical neutrality condition allows us to simply sum the vectorial couplings together, cancelling the electron and proton contributions (and hence, also the mixing angle dependence).
+\subsection{Matter oscillations}
+Since only $\ne$ undergo CC interactions, the $V_{CC}$ potential is zero for all other flavors. However, since all flavors, undergo NC interactions the total matter potential in matrix form is:
+\begin{align}
+    V = \begin{bmatrix}
+        V_{CC} + V_{NC} & 0 & 0 \\
+        0 & V_{NC} & 0 \\
+        0 & 0 & V_{NC} \\
+    \end{bmatrix}
+\end{align}
 %\bibliographystyle{apalike}

### 2021-04-28 src/events/DC/event_processing.py

@@ -178,6 +178,8 @@ def is_precomputed_nsi(pid,ndim, dict, check=False):
                     else:
                         raise FileNotFoundError(f'P{flavor_from}{flavor_to} {ndim}gen for pid {pid}, dm={dict["dm_31"]}, th23={dict["theta_23"]}, e_mm={dict["e_mm"]},e_mt={dict["e_mt"]}, not found')
                 return True
+
+                
 def get_best_fit(deltachi, p_range, cl):
     from scipy import interpolate
     deltachi = deltachi.reshape(-1)

### 2021-04-28 test/test.py

@@ -1,1 +1,0 @@
-from probability.functions 

### 2021-04-28 latex/oscillations.tex
update

@@
 The solution to the time-dependent Schrödinger equation 
-\begin{align}
-    i \dv{}{t} \ket{\nu_k(t)} = H\ket{\nu_k(t)}\,,
+\begin{align}\label{eq:TDSE}
+    i \dv{}{t} \ket{\nu_k(t)} = H_0\ket{\nu_k(t)}\,,
 \end{align}
-gives us a plane wave evolution to the mass states as 
+where $H_0$ is the Hamiltonian and the subscript signifies that we are in vacuum.
+
+The solution to Eq.~\ref{eq:TDSE} gives ut the time evolution
+in the form of plane wave solutions: 
 \begin{align}
@@
 Thus, $v\approx 1$, and $\abs{\vec{p}} \approx E$ making the energy-dispersion relation of Eq.~\ref{eq:disp} to first order:
-\begin{align}
+\begin{align}\label{eq:ultra_rel}
     E_k &= \sqrt{\vec{p}^2 + m_k^2} \nonumber \\
@@
 \end{align}
-where we in the last step have defined the \emph{mass squared-difference} $\dm_{kj} = m_k^2 - m_j^2$. Thus, it is impossible
-to measure the mass states $m_k$ through neutrino oscillations, since they depend on the difference between the two squared mass states instead of the
-masses themselves. 
+where we in the last step have defined the \emph{mass squared-difference} $\dm_{kj} = m_k^2 - m_j^2$. Since the oscillation probability depends on this quantity
+rather than the individual masses, it is impossible
+to measure the mass states $m_k$ through neutrino oscillations.
 Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^* = \delta_{\a \b}$ yields 
@@
 \begin{align}
-    H = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, e \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, \ne \right]
+    H^{CC} = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, e \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, \ne \right]
 \end{align}
@@
 \begin{align}\label{eq:H_fierz}
-    H = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, e \right]\,.
+    H^{CC} = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, e \right]\,.
 \end{align}
@@
 \begin{align}\label{eq:avg_H1}
-    \bar H &= \int \dd p_e^3 \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
+    \bar{H}^{CC} &= \int \dd p_e^3 \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
            &= \frac{G_F}{\sqrt{2}} \int \dd p_e^3 \bra{e(p_e,h_e)} \left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right]  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \left[\bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x) \right] \ket{e(p_e,h_e)} \nonumber \\
@@
     &= \frac{1}{4 E_e V} \Trace{\left[ (\slashed{p}_e + m_e ) \,\gamma_\rho\, (1- \gamma^5)\, \right]} \nonumber \\
-    &= \frac{(p_e)_\rho}{E_e V}
+    &= \frac{(p_e)_\rho}{E_e V}\,.
 \end{align}
@@
 \begin{align}\label{eq:avg_H2}
-    \avg{H} &= \frac{G_F}{\sqrt{2}E_e V} \bar\ne \, (1- \gamma^5)\, \ne \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T)\,.
+    \avg{H^{CC}} &= \frac{G_F}{\sqrt{2}E_e V} \bar\ne \, (1- \gamma^5)\, \ne \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T)\,.
 \end{align}
@@
 \begin{align}
-    \avg{H} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
+    \avg{H^{CC}} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
             &= \sqrt{2}G_F N_e \bar{\nu}_{Le} \gamma^0 \nu_{Le}\,,
 \end{align}
-where the projection operator $(1- \gamma^5)$ ensures that only the left-hand compontent of the neutrino fields interact weakly. Thus 
-\begin{align}\label{V_CC1}
-    V_{CC} = \sqrt{2}G_F N_e
+where the projection operator $(1- \gamma^5)$ ensures that only the left-hand compontent of the neutrino fields interact weakly. Thus,
+\begin{align}\label{eq:V_CC1}
+    V_{CC} = \sqrt{2}G_F N_e\,, \quad H^{CC}\ket{\nu_k} = V_{CC}\ket{\nu_k}\,.
 \end{align}
+Here we see a crucial difference between the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H^{CC}$, namely
+that the CC (and NC) interactions happen in the flavor basis rather than in the mass basis. In other words,
+neutrinos propagate in their mass eigenstates, but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
+determines if the flavor eigenstate has oscillated or not. Thus, the expressions involving the 
+matter potential does not need to be transformed by the PMNS matrix.
 
@@
 \subsection{Matter oscillations}
-Since only $\ne$ undergo CC interactions, the $V_{CC}$ potential is zero for all other flavors. However, since all flavors, undergo NC interactions the total matter potential in matrix form is:
-\begin{align}
+Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors.
+However, since all flavors undergo NC interactions the total matter potential in matrix form is:
+\begin{align}\label{V_matrix}
     V = \begin{bmatrix}
@@
         0 & 0 & V_{NC} \\
-    \end{bmatrix}
+    \end{bmatrix} = V_{CC}\, \delta_{\alpha e} + V_{NC}\,.
+\end{align}
+
+Just as in Eq.~\ref{eq:TDSE}, we start with a Hamiltonian that solves the time-dependent Schrödinger equation. This time, let the Hamiltonian be 
+\begin{align}
+    H = H_0 + H_{I}\,,
+\end{align}
+where $H_0$ is the Hamiltonian in vacuum, and $H_{I}$ is our interaction Hamiltonian associated with our matter potentials.
+Let the wavefunction that describes the $\nu_\a \to \nu_\b$ transition be 
+\begin{align}
+    \bra{\nu_\b}\ket{\nu_\a (t)}\,,
+\end{align}
+i.e.~the evolution of the state of a neutrino emitted at $t =0$ with flavor $\alpha$ to flavor $\beta$ at time $t$.
+
+Now using Eq.~\ref{eq:osc_1} and Eq.~\ref{eq:V_CC1}, we are ready to see what form our Hamiltonians take.
+Let us start with the vaccum Hamiltonian $H_0$, and act on its Schrödinger equation with $\bra{\nu_\b}\,$:
+\begin{align}
+    i \dv{}{t}\ket{\nu_\a (t)} = H_0\ket{\nu_\a (t)} \implies i \dv{}{t}\psi_{\a\b} = \bra{\nu_\b}H_0\ket{\nu_\a (t)}\,.
+\end{align}
+Reminding ourselves that the vacuum Hamiltonian $H_0$ has eigenstates in the mass basis, we write the following expression where 
+use the relations ~\ref{eq:osc_1} and ~\ref{eq:osc_k} to switch between the flavor and mass basis with the PMNS elements:
+\begin{align}
+    \bra{\nu_\b} H_0 &= \sum_k U_{\b k} \bra{\nu_k}H_0 \nonumber \\
+                     &= \sum_k U_{\b k} E_k \bra{\nu_k} \nonumber \\
+                     &= \sum_\eta \sum_k U_{\b k} E_k U^*_{\eta k} \bra{\nu_\eta}\,.
+\end{align}
+Thus,
+\begin{align}
+    \bra{\nu_\b}H_0\ket{\nu_\a (t)} &= \sum_\eta \sum_k U_{\b k} E_k U^*_{\eta k} \bra{\nu_\eta}\ket{\nu_\a (t)} \nonumber \\
+                                    &= \sum_\eta \sum_k U_{\b k} E_k U^*_{\eta k} \psi_{\a\eta}(t)\,.
+\end{align}
+Using the ultrarelativistic approximation from Eq.~\ref{eq:ultra_rel}:
+\begin{align}
+    \sum_\eta \sum_k U_{\b k} E_k U^*_{\eta k} \psi_{\a\eta}(t) &= \sum_\eta \sum_k U_{\b k} \left(p + \frac{m^2_k}{2E}\right) U^*_{\eta k} \psi_{\a\eta}(x) \nonumber \\
+    &= \sum_\eta \sum_k U_{\b k} \left(p + \frac{m^2_k}{2E}\right) U^*_{\eta k} \psi_{\a\eta}(x)\,.
+\end{align}
+Use the fact that $\sum_k m_k^2 = \sum_k m_1^2 + m^2_k - m^2_1 = m_1^2 + \sum_k \dm_{k1}$ to pull out common terms out of the summation:
+\begin{align}\label{eq:t1}
+    \sum_\eta \sum_k U_{\b k} \left(p + \frac{m^2_k}{2E}\right) U^*_{\eta k} \psi_{\a\eta}(x) &= \sum_\eta \sum_k U_{\b k} \left(p + \frac{m^2_1}{2E} + \frac{\dm_{k1}}{2E}\right) U^*_{\eta k} \psi_{\a\eta}(x) \nonumber \\
+    &= \sum_\eta\sum_k \left(p + \frac{m^2_1}{2E}\right) U_{\b k} U^*_{\eta k} \psi_{\a\eta}(x) + \sum_\eta\sum_k U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} \psi_{\a\eta}(x)\,.
+\end{align}
+Unitarity gives $ \sum_k U_{\b k} U^*_{\eta k} = \delta_{\eta\b}$, and the first term in the last step of Eq.~\ref{t1} becomes
+\begin{align}
+    \sum_\eta \left(p + \frac{m^2_1}{2E}\right) \delta_{\beta \eta} \psi_{\a\eta}(x)
+    =& \left(p + \frac{m^2_1}{2E}\right) \psi_{\a\b}(x)\,.
+\end{align}
+This is a phase common to all states, which does not affect the probability since it can be rotated away.
+Our treatment of the interaction Hamiltonian is similar except for the fact that its eigenstates lie in the flavor basis, conviniently allowing us
+to letting it act directly on the flavor eigenstates:
+\begin{align}
+    \bra{\nu_\b}H_I &= V_\beta \bra{\nu_\b} \nonumber\\
+                    &= \delta_{\b\eta} V_\beta \bra{\nu_\eta}\,.
 \end{align}  

### 2021-04-28 src/events/make_events.py
update

@@ -64,7 +64,7 @@ if __name__ == '__main__':
     print('eem:', eem_range)
     print('eet:', eet_range)
     param_dict = nufit_params_nsi_IO if args.IO else nufit_params_nsi
-
+    ordering = 'IO' if args.IO else 'NO'
     param_list = list_of_params_nsi(param_dict, dm31_range, th23_range, ett_range, emt_range, eem_range, eet_range)
     
     #data = [(p) for p in param_list]
@@ -73,15 +73,15 @@ if __name__ == '__main__':
         H1_events_list = process_map(compute_events, param_list)
 
         #p.close()
-        pickle.dump(np.array(H1_events_list),open(f'./pre_computed/H1_PINGU_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
+        pickle.dump(np.array(H1_events_list),open(f'./pre_computed/H1_{ordering}_PINGU_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
     elif args.DC:
         #p = Pool()
         H1_events_list = process_map(compute_events, param_list)
         #p.close()
-        pickle.dump(np.array(H1_events_list),open(f'./pre_computed/H1_DC_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
+        pickle.dump(np.array(H1_events_list),open(f'./pre_computed/H1_{ordering}_DC_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
     if args.IC:
         data = [(0.99, 13,p, False,False, [False, 0, 0],True, True,3) for p in param_list]
         #p = Pool()
         H1_events_list = process_map(IC_events, data)
         #p.close()
-        pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N13_{len(dm31_range)}x{len(th23_range)}x{len(emt_range)}.p','wb'))
+        pickle.dump(H1_events_list,open(f'./pre_computed/H1_{ordering}_IC_N13_{len(dm31_range)}x{len(th23_range)}x{len(emt_range)}.p','wb'))

### 2021-04-28 src/events/make_events.py
update

@@ -70,7 +70,7 @@ if __name__ == '__main__':
     #data = [(p) for p in param_list]
     if args.PINGU:
         #p = Pool()
-        H1_events_list = process_map(compute_events, param_list)
+        H1_events_list = process_map(compute_events, param_list, chunksize=5)
 
         #p.close()
         pickle.dump(np.array(H1_events_list),open(f'./pre_computed/H1_{ordering}_PINGU_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))

### 2021-04-29 thesis/tex/nsiTheory.tex
update

\documentclass[draft=True]{thesis}
\input{commands}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}

\begin{document}
\section{How NSIs alter the matter potential}
Up until now, we have only considered neutrino interactions with electrons, protons, and neutrons. Now we extend this to include we can extend this to include 
the up and down quarks which are present in the Earth as the fundamental components of neutrons and protons. 
Consider interactions beyond the Standard Model through the following Lagrangians,
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$.

We have no independent sensitivity for the neither chirality nor flavor type of $\epsilon^X$, so we sum over these and study the effective matter NSI parameter
 $\epsilon_{\ab}$:
\begin{align}
    \epsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\ab}\,.
\end{align}
Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
we get $N_u/N_e \simeq U_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
\begin{align}
    \epsilon_{\ab} =  \sum_X [\epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})]
\end{align}
Now, $\epsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix. In Eq.~\ref{eq:NSIH}, $A_{CC}\text{diag}(1,0,0)$ is our 
familiar matter potential from the Standard Model. There is also our new term, $A_{CC} \epsilon$, which contains the components $\epsilon_{\a\b}$:
\begin{align}\label{eq:NSIH}
    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\text{diag}(1,0,0) + A_{CC} \epsilon \right] \nonumber \\
      &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}
      \begin{pmatrix}
          1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
          \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
          \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
      \end{pmatrix} \right]\,.
\end{align} 
In the limit $\epsilon_{\ab} \to 0$, we recover the standard interaction Hamiltonian from Eq.~\ref{eq:H_3gen}.
We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ will make the NSI violate 
lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
\begin{align}
    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.

We have two more modifications to the matrix $\epsilon$. First, all terms of the Hamiltonian must of course be Hermitian, thus
\begin{align}
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
    \end{pmatrix} =
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
    \end{pmatrix}\,.
\end{align}
Now we have reduced the possible number of NSI parameters from 9 down to 6. Moreover, it is common to subtract $\emm$ from the diagonal, which
we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
probabilities. So just as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
Our NSI potential matrix now takes the form 
\begin{align}
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
    \end{pmatrix} 
    - \epsilon_{\mu\mu}
    \begin{pmatrix}
        1 & 0 & 0 \\
        0 & 1 & 0 \\
        0 & 0 & 1 
    \end{pmatrix}
     &= \begin{pmatrix}
        \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
    \end{pmatrix} \nonumber \\
    &= \begin{pmatrix}
        \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
    \end{pmatrix}\,,
\end{align}
where $\ep = \ett - \emm$.

\section{Non-standard interactions in IceCube}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$ directly or 
indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon{\a\a}$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting implication. %TODO: fill
In Fig.~\ref{fig:IC_NSI_probs}, we plot $\Pmm$ and $\Pamam$ for 3 cases of $\ep$ and $\emt$ each. As is clear from the 
left panels, the value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, as we expected. Hence, we will not be able
to say anything about $\ett$ in our study. The right panels show an interesting relationship between the sign of the NSI parameter 
and the neutrino type. $\Pmm$ with positive $\ett$ is the same as $\Pamam$ with negative $\ett$. Looking at the form of the matter potential, 
this is something that we should expect. In the standard interaction framework, we distinguish between neutrinos and antineutrinos by flipping the sign 
of the CC potential. Since the NSI potential has the same form, any sign flipping of the NSI potential will have the same effect as 
having an antineutrino.

\begin{figure}\label{fig:IC_NSI_probs}
    \begin{center}
    \includegraphics[width=1\textwidth, height=0.3\textheight]{figures/IC_NSI_probs.pdf}
    \caption{\emph{Top panels: }$\nm$ survival probability for different cases of the two NSI parameters $\ett$ and $\emt$
    \emph{Bottom panels: }$\anm$ survival probability for different cases of the two NSI parameters $\ett$ and $\emt$.
    In all plots, \ztrue = -1.}
    \end{center}
\end{figure}
\end{document}

### 2021-04-29 thesis/tex/oscillations.tex
update

--- 2021-04-28 latex/oscillations.tex
@@
-\documentclass[draft=True]{revtex4-2}
-\input{commands.tex}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, slashed}
+\documentclass[draft=True]{thesis}
+\usepackage{graphicx, slashed}
 \usepackage[utf8]{inputenc}
@@
 \externaldocument{SM}
-
+\input{commands}
 \begin{document}
@@
 \section{Neutrino Masses and Oscillations}\label{ch:oscillation}
+\subsection{Neutrino mixing and the PMNS matrix}
 As we saw in Eq.~\ref{eq:j_CC}
@@
 \end{align}
-Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$
+Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$. We will refer to the matrix $U$ built by the components $U{k \alpha}$ as the
+Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix.%TODO: source
 Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$.
@@
 \begin{align}\label{eq:j_CC3} %TODO: put sums on all above?
-    j^\rho_L &= 2 \sum_\alpha \sum_k U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}
+    j^\rho_L &= 2 \sum_\alpha \sum_k U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}\,.
 \end{align}
+%TODO: add segue
+\subsection{Neutrino oscillations}
+Since we now know how the neutrino mass and flavor eigenstates combine (namely, through the PMNS matrix $U$), and have an expression for the flavor interaction with 
+the neutrinos charged lepton partner, we are now ready to study the flavor oscillations themselves.
+
 Now, the Fourier expansion of the field operator $\bar{\nu}_{k L}$ in Eq.~\ref{eq:j_CC3} contains creation operators $a^\dagger_{\nu_k}$
@@
 \subsection{Matter effects}
-\begin{figure}\label{fig:w_and_z}
-    \includegraphics[width=0.1\textwidth]{figures/w-boson.pdf}
+\begin{figure}
+    \includegraphics[width=0.2\textwidth]{figures/w-boson.pdf} 
     \hspace{2cm}
-    \includegraphics[width=0.1\textwidth]{figures/z-boson.pdf}
+    \includegraphics[width=0.23\textwidth]{figures/z-boson.pdf}
+    \caption{\emph{Left panel:} Charged current weak interaction between an electron neutrino and an electron,
+    mediated by either a $W^+$ or $W^-$ boson. \emph{Right panel:} Neutral current weak interaction between a neutrino of any flavor and a Earth-like fermion,
+    mediated by a neutral $Z$ boson.}
+    \label{fig:w_and_z}
 \end{figure}
-In this work, we are concerned about the interactions with the neutrino and Earth-like matter, i.e. electrons, protons, and neutrons. 
-The possible interactions are shown in Fig. ~\ref{fig:w_and_z}. The left panel shows that the only flavor that can go through charged current (CC) 
+In this work, we are concerned about the interactions with the neutrino and Earth-like matter, i.e.~electrons, protons, and neutrons. 
+The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can go through charged current (CC) 
 interactions is the electron flavor. This is because the Earth doesn't consist of any muons or tau particles. 
-The right panel shows any neutrino flavor interaction via the neutral current (NC) with Earth-like matter, mediated by the neutral $Z$ boson
- we see weak forward CC and NC scattering. 
+The right panel shows any neutrino flavor interaction via the neutral current (NC) with Earth-like matter\footnote{The Earth is entirely composed
+of electrons, protons, and neutrons.
+Thus, the fundamental particles composing Earth are electrons, and up and down quarks.
+We refer to this as \emph{Earth-like matter}.}, mediated by the neutral $Z$ boson
 The interaction mediated by the $W$ boson will give rise to a effective matter potential $V_{CC}$, while
@@
 However, since all flavors undergo NC interactions the total matter potential in matrix form is:
-\begin{align}\label{V_matrix}
+\begin{align}\label{eq:V_matrix}
     V = \begin{bmatrix}
@@
 \end{align}
-Use the fact that $\sum_k m_k^2 = \sum_k m_1^2 + m^2_k - m^2_1 = m_1^2 + \sum_k \dm_{k1}$ to pull out common terms out of the summation:
+Use the fact that $\sum_k m_k^2 =  \sum m_1^2 +_k m^2_k - m^2_1 =\sum_k m_1^2 +  \dm_{k1}$ to pull out common terms out of the summation:
 \begin{align}\label{eq:t1}
@@
 \end{align}
-This is a phase common to all states, which does not affect the probability since it can be rotated away.
+
 Our treatment of the interaction Hamiltonian is similar except for the fact that its eigenstates lie in the flavor basis, conviniently allowing us
@@
 \begin{align}
-    \bra{\nu_\b}H_I &= V_\beta \bra{\nu_\b} \nonumber\\
+    \bra{\nu_\b}H_I &= V_\beta \bra{\nu_\b} \nonumber \\
                     &= \delta_{\b\eta} V_\beta \bra{\nu_\eta}\,.
 \end{align}
-%\bibliographystyle{apalike}
-%\bibliography{ref}
+Using Eq.~\ref{eq:V_matrix}, we rewrite this as
+\begin{align}\label{eq:V_rewrite}
+    \delta_{\b\eta} V_\beta \bra{\nu_\eta} &= \delta_{\b\eta} (V_{CC}\delta_{\beta e} + V_{NC}) \bra{\nu_\eta} \nonumber \\
+                                           &= V_{CC}\delta_{\b\eta}\delta_{\beta e} \bra{\nu_\eta} + V_{NC}\bra{\nu_\beta} \nonumber \\
+    \implies \bra{\nu_\b}H_I\ket{\nu_\a}   &= V_{CC}\delta_{\b\eta}\delta_{\beta e} \bra{\nu_\eta}\ket{\nu_\a} + V_{NC}\bra{\nu_\beta}\ket{\nu_\a} \nonumber \\
+                                           &= V_{CC}\delta_{\b\eta}\delta_{\beta e} \psi_{\a\eta} + V_{NC}\psi_{\a\b}
+\end{align}
+Now, combining Eq.~\ref{eq:t1} and Eq.~\ref{eq:V_rewrite}, we have for the full Hamiltonian
+\begin{align}
+    \bra{\nu_\b}H\ket{\nu_\a (x)} &= \left(p + \frac{m^2_1}{2E} + V_{NC}\right) \psi_{\a\b}(x) + \sum_\eta\sum_k \left(U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} + V_{CC}\delta_{\b\eta}\delta_{\eta e} \right) \psi_{\a\eta}(x)
+\end{align}
+In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  which does not affect the probability since it is a common termt to all flavor states. It can be rotated away.
+Thus
+\begin{align}\label{eq:components}
+    \bra{\nu_\b}H\ket{\nu_\a (x)} &= \sum_\eta\sum_k \left(U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} + V_{CC}\delta_{\b\eta}\delta_{\eta e}\right) \psi_{\a\eta}(x) \nonumber \\
+                                  &= i \dv{}{x}\psi_{\a\b}(x)\,.
+\end{align}
+If we form the vector 
+\begin{align}
+    \Psi_\a = \begin{pmatrix}
+        \psi_{\a e} \\
+        \psi_{\a \mu} \\
+        \psi_{\a \tau}
+    \end{pmatrix}\,,
+\end{align}
+we can write the Schrödinger equation on matrix form ($i\dv{}{x}\Psi_\a = H_F \Psi_\a$) and compare it with Eq.~\ref{eq:components} to see that the flavor Hamiltonian takes the form 
+\begin{align}\label{eq:H_3gen}
+    H_F &= \frac{1}{2E}(U M^2 U^\dagger + A) \nonumber \\
+        &= \frac{1}{2E}\left[U \begin{pmatrix}
+            0 & 0 & 0 \\
+            0 & \dm_{21} & 0 \\
+            0 & 0 & \dm_{31}
+        \end{pmatrix} U^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
+            1 & 0 & 0 \\
+            0 & 0 & 0 \\
+            0 & 0 & 0
+        \end{pmatrix}\,. 
+\end{align}
+This is the three-flavor neutrino oscillation Hamiltonian that we will solve numerically to obtain the evolution of $\Psi_\a$, whose squared components
+are the probabilities
+\begin{align}
+    P_\alpha = \abs{\Psi_a}^2 &=\begin{pmatrix}
+        \abs{\psi_{\a e}}^2 \\
+        \abs{\psi_{\a \mu}}^{2} \\
+        \abs{\psi_{\a \tau}}^{2}
+    \end{pmatrix} \nonumber \\
+    &=\begin{pmatrix}
+        P_{\a e} \\
+        P_{\a \mu} \\
+        P_{\a \tau}
+    \end{pmatrix} 
+\end{align}
+
 \end{document}

### 2021-04-29 plotter.py

@@ -214,8 +214,13 @@ def nsi_flux_oscillogram(E_range, z_range, params, only_m=True):
 
 
 def save(fig, name):
-    fig.savefig(f'latex/article/figures/{name}.pdf')
+    fig.savefig(f'article/figures/{name}.pdf')
     from subprocess import call 
-    _ = call('pdfcrop latex/article/figures/{name}.pdf latex/article/figures/{name}.pdf')
+    _ = call('pdfcrop article/figures/{name}.pdf article/figures/{name}.pdf')
+
+def savethesis(fig, name):
+    fig.savefig(f'thesis/tex/figures/{name}.pdf')
+    from subprocess import call 
+    _ = call('pdfcrop thesis/tex/figures/{name}.pdf thesis/tex/figures/{name}.pdf')
 if __name__ == '__main__':
     pass

### 2021-04-30 thesis/tex/ICtheory.tex
update

\documentclass[draft=True]{thesis}
\usepackage{graphicx, slashed, siunitx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\input{commands}
\begin{document}

\section{Event reconstruction}
After an event has occurred, the IceCube algorithms process the data coming from the detector to \emph{reconstruct} the event. This means that, given the parameters recorded by the detector, what are their "true" values?
We are interested in two variables: the energy and the direction. Each event is tagged with a probable energy and zenith angle, called the recostructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
The collaboration then uses numerous sophisticated methods to backtrack the reconstructed parameters to the true parameters. So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true and reconstructed energy and zenith angle. The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the determination of that neutrino's "actual" flux and cross-section (because this is what nature sees).

How do we then translate between the reconstructed and true parameters? In this work, we are using two different methods, which are based on the form of data available to us.

\section{IceCube event count}\label{ch:ICmethod}
%TODO: show IC MC data

The flux comes from \cite{hondapaper} %TODO: talk about flux
The flux data is binned in $\ztrue$ and has the following form

\begin{tabular}{lrrrrrrr}
    %\toprule
           $\Etrue$ [\si{\GeV}] &        $\phi_\mu$ &     $\phi_\bar{\mu}$ &        $\phi_e$ &     $\phi_{\bar{e}}$ &  $\ztrue_{min}$ &  $\ztrue_{max}$\\
    %\midrule
       27825.594022 &  6.060061e-12 &  3.167883e-12 &  1.558607e-13 &  1.038747e-13 &   -0.2 &   -0.1 \\
      247707.635599 &  5.940855e-16 &  2.923931e-16 &  1.364937e-17 &  8.115912e-18 &   -0.7 &   -0.6 \\
         22.387000 &  3.328100e-02 &  2.781700e-02 &  9.565800e-03 &  7.149400e-03 &   -0.3 &   -0.2 \\
      432876.128108 &  5.185841e-17 &  2.320702e-17 &  1.456761e-18 &  9.828299e-19 &   -1.1 &   -1.0 \\
       64280.731173 &  1.582403e-13 &  8.095293e-14 &  3.480179e-15 &  2.211758e-15 &   -0.4 &   -0.3 \\
    %\bottomrule
\end{tabular}

The fluxes are averaged over azimuthal direction and over solar minimun/maximum. The units of the fluxes are given as \si{\GeV^-1 \metre^-2 \second^-1 \steradian^-1}. 
We note that the fluxes for $\nt$ and $\nu_\bar{\tau}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. Thus, we never have to use probabilities on the form 
$P_{\tau \beta}$, since we have no incoming $\nu_\tau$.

After interpolating this data, we can plot the raw data together with its interpolated values.
%TODO: flux interpolated figure.

As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact in the ice to form their charged leptons. We now are interested in the effective area, i.e.~the detector area that the lepton "sees".
The effective area, $\Aeff$, depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section. Fortunately, the binned $\Aeff$ is provided to us by the ICeCube collaboration~\cite{ICaeff}.
The data file has the following form

\begin{tabular}{lrrrrr}
    %\toprule
    $\Etrue_{min}$ [\si{\GeV}] &     $\Etrue_{max}$ [\si{\GeV}]&   $\ztrue_{min}$ &   $\ztrue_{max}$ &     $\Aeff$ [\si{\metre\squared}] \\
    %\midrule
         251.2 &      316.2 &  -0.92 &  -0.91 &   0.0174 \\
      794300.0 &  1000000.0 &  -0.80 &  -0.79 &  69.3600 \\
        3981.0 &     5012.0 &  -0.78 &  -0.77 &   3.1490 \\
        1585.0 &     1995.0 &  -0.07 &  -0.06 &   0.4659 \\
        398.1 &      501.2 &  -0.73 &  -0.72 &   0.0555 \\
    %\bottomrule
    \end{tabular}
Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_\bar{\mu}$. Thus, it is not flavor dependent.
Just as with the fluxes, we interpolate this in $\Etrue,\ztrue$ and show the result %TODO aeff interpolation

So now we have the physical quantities in the true parameters. But as we discussed, we need a way to translate this into the reconstructed parameters that the detector gives us. We will call the relationship between 
$\Ereco$ and $\Etrue$ the energy resolution function, and the relationshop between $\zreco$ and $\ztrue$ the zenith resolution function. We assume the relationship to follow a logarithmic Gaussian distribution, giving it the form 
\begin{align}\label{eq:gaussian}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
The parameters of the Gaussian are $\sigma_{x^r}(x^t)$ and $\mu(x^t)$, which are functions of the true parameters. By multiplying the Gaussian in Eq.~\ref{eq:gaussian}, we are reweighing the values by the 
probability density of that point. This process is also called \emph{smearing} because it effectively spreads out the data around a certain point.

So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publically released by the 
collaboration has all the ingredients that we need. %TODO: source.
In Table %TODO: add
we see a snippet of how it looks like.

First, we let $\zreco = \ztrue$ for all values. The angular resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
Thus, we only need to concern ourselves with the energy resolution.
In Fig.~\ref{fig:IC_MC_gpr}, we have plotted all event counts found in the MC file, over 8 million. However, this is too much data to process efficiently, with many outliers that ultimately don't weigh in 
that much in the final event count. To resolve this, we have opted to train a Gaussian process regressor on the dataset, from which we can extract the predicted mean and standard deviation for a point.
When doing this over $\Ereco$, we sample $\Etrue$ in the 99\%th percentile around the predicted mean. We then obtain the shaded band shown in Fig.~\ref{fig:IC_MC_gpr}. %TODO add plot with Etrue vs prob dens

The event rate for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
\end{align}
where $T$ is the live time of the detector.

\begin{figure}[!tb]\label{fig:IC_MC_gpr}
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}

\end{document}

### 2021-04-30 src/events/make_events.py
update

@@ -9,8 +9,10 @@ import pandas as pd
 from PINGU.importer import *
 from PINGU.processer import *
 from DC.event_processing import * # DC.event_processing has all we need. 
-from PINGU.main import get_all_events as PINGU_events
-from DC.main import get_all_events as DC_events
+from PINGU.main import get_all_events as PINGU_all_events
+from DC.main import get_all_events as DC_all_events
+from PINGU.main import get_events as PINGU_events
+from DC.main import get_events as DC_events
 from IC.main import sim_events as IC_events
 from functions import nufit_params_nsi, nufit_params_nsi_IO
 from tqdm import tqdm
@@ -41,12 +43,23 @@ parser.add_argument('-PINGU', action='store_true')
 args = parser.parse_args()
 
 
-def compute_events(params):
+def compute_events(arg_tuple):
+    i,j,params = arg_tuple
     if args.PINGU:
         result = PINGU_events(params,nsi=True,save=False)
     elif args.DC:
         result = DC_events(params,nsi=True,save=False)
     return result
+
+def precompute_probs(args_tuple):
+    i,j,params = args_tuple
+    if args.PINGU:
+        res_track = PINGU_events(Ebin=i,zbin=j,params=params,pid=1,nsi=True, save=False)
+        res_cascade =PINGU_events(Ebin=i,zbin=j,params=params,pid=0,nsi=True, save=False)
+    elif args.DC:
+        res_track = DC_events(Ebin=i,zbin=j,params=params,pid=1,nsi=True, no_osc=False, save=False)
+        res_cascade =DC_events(Ebin=i,zbin=j,params=params,pid=0,nsi=True, no_osc=False, save=False)
+    return np.array([res_cascade, res_track])
 
 if __name__ == '__main__':
     assert args.PINGU or args.DC or args.IC
@@ -66,17 +79,19 @@ if __name__ == '__main__':
     param_dict = nufit_params_nsi_IO if args.IO else nufit_params_nsi
     ordering = 'IO' if args.IO else 'NO'
     param_list = list_of_params_nsi(param_dict, dm31_range, th23_range, ett_range, emt_range, eem_range, eet_range)
+    param_tuple = [(i,j,p) for p in param_list for i in range(8) for j in range(8)]
     
     #data = [(p) for p in param_list]
     if args.PINGU:
         #p = Pool()
[…]

### 2021-04-30 article/article.tex

--- 2021-04-26 latex/article/article.tex
@@
 \renewcommand{\ne}{\nu_e}
+\newcommand{\Ereco}{E^{reco}}
+\newcommand{\Etrue}{E^{true}}
 \newcommand{\nm}{\nu_\mu}
@@
 As seen in Fig.~\ref{fig:IC_MC_counts}, the energy reconstruction is biased.
-To model this relationship between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
-we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $E^\text{true}$ points of the 99th percentile of each distribution to obtain
-the limits of $E^\text{true}$ at which to integrate over.
+To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
+we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
+the limits of $\Etrue$ at which to integrate over.
 We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.

### 2021-05-03 thesis/tex/ICintro.tex
update

\documentclass[draft=True]{thesis}
\usepackage{graphicx, slashed, siunitx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\input{commands}
\begin{document}
We always observe neutrinos indirectly through their associated charged lepton. Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
interaction is then deduced. This deduction is obviously imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors handeled by the ICecube collaboration. They are of Cherenkov type, which means that they detect 
the charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
%TODO: text about pid
\begin{figure}\label{fig:events}
    \includegraphics[width=0.5\textwidth]{figures/cascade_event.pdf}\caption{Event classified as cascade}
    \includegraphics[width=0.5\textwidth]{figures/track_event.pdf}\caption{Event classified as track}
\end{figure}

To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
%TODO: pic of cherenkov light/dom?

The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than other.
8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single digit \si{\GeV}. Due to 
this part being situated deep within the ice, it is referred to DeepCore. DeepCore will be treated as a separate and independent detector from the rest, which
retains the name IceCube. A view of the current setup can be seen in Fig.~\ref{fig:array}. In this work, we consider DeepCore data between \SIrange{5.6}{56}{\GeV} and IceCube data in the range \SIrange{0.5}{10}{\TeV}.
\begin{figure}\label{fig:array}
    \includegraphics[width=0.5\textwidth]{figures/icecube2.png}\caption{View of the full IceCube array}
\end{figure}

In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The "Precision IceCube Next Generation Upgrade" is an upgrade that will 
supplement DeepCore, i.e. boosing the capabilites of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
IceCube and DeepCore bounds. 
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}

### 2021-05-03 thesis/tex/nsiTheory.tex
update

@@
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$ directly or 
-indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon{\a\a}$ will directly adjust the matter potential felt 
-by flavor $\a$. The off-diagonal terms have a more interesting implication. %TODO: fill
+indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
+by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,
+we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions.
+Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
+of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since the NSI parameters are 6, and the PMNS
+matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix.
+
+As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$ and $\emm$ or $\ett$ the most suitable
+NSI parameters to constrain.
+
 In Fig.~\ref{fig:IC_NSI_probs}, we plot $\Pmm$ and $\Pamam$ for 3 cases of $\ep$ and $\emt$ each. As is clear from the 

### 2021-05-03 thesis/tex/oscillations.tex
update

@@
 
+In this work, we will be using the best-fit values from~\cite{nufit},
+\begin{align}\label{eq:nufitparams}
+    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
+    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+\end{align}
+with the exception of the CP-violating phase $\delta_\text{CP}$ which we always set to zero for simplicity. The PMNS matrix then has the numerical values 
+\begin{align}\label{eq:Uvalues}
+    U = \begin{pmatrix}
+        U_{e e} & U_{e\mu} & U_{e\tau} \\
+        U_{\mu e} & U_{\mu \mu} & U_{\mu \tau} \\
+        U_{\tau e} & U_{\tau \mu} & U_{\tau \tau}
+    \end{pmatrix} 
+    = \begin{pmatrix}
+        0.825 & 0.545 & 0.149 \\
+        -0.455 & 0.485 & 0.746 \\
+        0.334 & -0.684 & 0.649
+    \end{pmatrix} \,.
+\end{align}
+In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
+suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. We will see that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
+the most abundant. This means we will be able to constrain any parameters relating to $\nm \to \nt$ oscillations stringently.
+
 \end{document}

### 2021-05-03 src/data/DC/processer.py

@@ -227,3 +227,21 @@ def normalization_factors(no_osc_tracks, no_osc_cascades):
 
 if __name__ == '__main__':
     pass
+    '''
+no_osc = np.array([get_all_events(params=param_list[0], pid=0, nsi=True, no_osc=True),get_all_events(params=param_list[0], pid=1, nsi=True, no_osc=True)])
+no_osc_paper = np.array([no_osc2018_DC(0)[1].values,no_osc2018_DC(1)[1].values])
+H0_paper = np.array([pd.read_csv('./src/data/files/DC/2018/cascade_H0.csv', header=None)[1].values,pd.read_csv('./src/data/files/DC/2018/track_H0.csv', header=None)[1].values])
+events = np.array([get_hist(events2018_DC().query(f'pid==0'), 'count_events'),get_hist(events2018_DC().query(f'pid==1'), 'count_events')])
+background = np.array([get_hist(events2018_DC().query(f'pid==0'), 'count_background'), get_hist(events2018_DC().query(f'pid==1'), 'count_background')])
+best_fit_contamination = 0.055/(np.sum(background,axis=(1,2))/np.sum(events,axis=(1,2))) #table 1 DC2017
+
+data = np.sum(events,axis=2)
+
+H0_factors = H0_paper / np.sum(H0,axis=2)
+noosc_factors = (no_osc_paper - back_factor.reshape(-1,1)*np.sum(background,axis=2)) / (np.sum(no_osc,axis=2)*livetime) #can laos use best_fit_contamination here
+
+# Normalize NSI hypothesis
+H1_nonorm = H1 #No normalization
+H1_norm_H0 = H1 * H0_factors[None,:,None,:] #Norm against H0
+H1_norm_noosc = H1*noosc_factors[None,:,None,:] # Norm against no oscillation
+'''

### 2021-05-03 src/data/PINGU/processer.py

@@ -19,8 +19,6 @@ zbins_2018 = [-1., -0.75, -0.5 , -0.25,  0., 0.25, 0.5, 0.75, 1.]
 
 
 def get_probabilities_PINGU(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,pid,ndim, nsi):
-    if not nsi: #Use best fit to generate 'data'
-        param_dict = nufit_params_nsi
     hashed_param_name = sha256(param_dict)
     if anti:
         flavor_from = 'a' + flavor_from
@@ -41,8 +39,6 @@ def get_probabilities_PINGU(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,
     return res
 
 def generate_probabilities_PINGU(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,param_dict,anti,pid, ndim=4, nsi=True, save=True):
-    if not nsi: #Use best fit to generate 'data'. nufit_params_nsi has all epsilon=0
-        param_dict = nufit_params_nsi
     prob = np.array([P_num(flavor_from=flavor_from, E=E_range[i], ndim = ndim, anti=anti,params=param_dict,zenith=z, nsi=nsi)[mass_dict[flavor_to],-1] for i,z in enumerate(z_range)]).reshape(-1,1)
     if save:
         hashed_param_name = sha256(param_dict)

### 2021-05-03 src/events/make_events.py

@@ -1,28 +1,19 @@
-import sys,os
+import sys, pickle, argparse
+from tqdm.contrib.concurrent import process_map
+import numpy as np
 if __name__ == '__main__':
-    #os.chdir('../')
     sys.path.append('./src/data')
     sys.path.append('./src/events')
     sys.path.append('./src/probability')
-import numpy as np
-import pandas as pd
-from PINGU.importer import *
-from PINGU.processer import *
-from DC.event_processing import * # DC.event_processing has all we need. 
-from PINGU.main import get_all_events as PINGU_all_events
-from DC.main import get_all_events as DC_all_events
+from DC.event_processing import get_param_list, list_of_params_nsi
 from PINGU.main import get_events as PINGU_events
 from DC.main import get_events as DC_events
 from IC.main import sim_events as IC_events
 from functions import nufit_params_nsi, nufit_params_nsi_IO
-from tqdm import tqdm
-import pickle
-import argparse
-from tqdm.contrib.concurrent import process_map
-parser = argparse.ArgumentParser()
 
-parser.add_argument('-dm31N', default=10, type=int)
-parser.add_argument('-th23N', default=10, type=int)
+parser = argparse.ArgumentParser()
+parser.add_argument('-dm31N', default=1, type=int)
+parser.add_argument('-th23N', default=1, type=int)
 
 parser.add_argument('-ett', default=5e-2, type=float)
 parser.add_argument('-ettN', default=1, type=int)
@@ -43,19 +34,11 @@ parser.add_argument('-PINGU', action='store_true')
 args = parser.parse_args()
 
 
-def compute_events(arg_tuple):
-    i,j,params = arg_tuple
-    if args.PINGU:
-        result = PINGU_events(params,nsi=True,save=False)
-    elif args.DC:
-        result = DC_events(params,nsi=True,save=False)
-    return result
-
 def precompute_probs(args_tuple):
     i,j,params = args_tuple
     if args.PINGU:
-        res_track = PINGU_events(Ebin=i,zbin=j,params=params,pid=1,nsi=True, save=False)
-        res_cascade =PINGU_events(Ebin=i,zbin=j,params=params,pid=0,nsi=True, save=False)
[…]

### 2021-05-04 thesis/tex/ICtheory.tex
update

@@
-\documentclass[draft=True]{thesis}
-\usepackage{graphicx, slashed, siunitx}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
+\documentclass{thesis}
+\usepackage[margin=0.5in]{geometry}
 \input{commands}
 \begin{document}
+\begin{figure}[t]\label{fig:flux_aeff}
+    \includegraphics[width=0.5\textwidth]{figures/flux.pdf}\hspace{-1cm}
+    \includegraphics[width=0.5\textwidth]{figures/aeff.pdf}
+    \vspace{-2.5cm}\caption{\emph{Left panel:} Interpolated South Pole atmospheric flux with data from~\cite{hondaArticle}.
+    \emph{Right panel:} Interpolated IceCube effective area with data from~\cite{ICaeff}.}
+\end{figure}
+
+\section{Atmospheric neutrino flux}
+The flux comes from \cite{hondaArticle} %TODO: talk about flux
+The flux data is binned in $\ztrue$ and a selection is shown in Table~\ref{table:flux}. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
+The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
+from the table for clarity. 
+We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. 
+Thus, we never have to use probabilities on the form 
+$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.
+
+Interpolating the data yields makes us capable of returning all four necessary fluxes for a given true energy and true zenith.
+The result is shown in Fig.~\ref{fig:flux_aeff}.
+
+\begin{table}[h]\label{table:flux}
+    \begin{center}
+        \begin{tabular}{lcccccc}
+            \hline \hline
+            $\Etrue$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\ztrue_{min}$ &$\ztrue_{max}$\\
+            \hline
+            27825 &  \SI{6.06e-12}{} &  \SI{3.17e-12}{} &  \SI{1.56e-13}{} &  \SI{1.04e-13}{} &   -0.2 &   -0.1 \\
+            247707 &  \SI{5.94e-16}{} &  \SI{2.92e-16}{} &  \SI{1.36e-17}{} &  \SI{8.12e-18}{} &   -0.7 &   -0.6 \\
+                22 &  \SI{3.33e-02}{} &  \SI{2.78e-02}{} &  \SI{9.57e-03}{} & \SI{7.15e-03}{} &   -0.3 &   -0.2 \\
+            432876 &  \SI{5.19e-17}{} &  \SI{2.32e-17}{} &  \SI{1.46e-18}{} & \SI{9.83e-19}{} &   -1.1 &   -1.0 \\
+            64280 &  \SI{1.58e-13}{} &  \SI{8.10e-14}{} &  \SI{3.49e-15}{} &  \SI{2.21e-15}{} &   -0.4 &   -0.3 \\
+            \hline
+        \end{tabular}
+    \end{center}
+    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}
+\end{table}
 
@@
 \section{IceCube event count}\label{ch:ICmethod}
-%TODO: show IC MC data
-
-The flux comes from \cite{hondapaper} %TODO: talk about flux
-The flux data is binned in $\ztrue$ and has the following form
-
-\begin{tabular}{lrrrrrrr}
-    %\toprule
-           $\Etrue$ [\si{\GeV}] &        $\phi_\mu$ &     $\phi_\bar{\mu}$ &        $\phi_e$ &     $\phi_{\bar{e}}$ &  $\ztrue_{min}$ &  $\ztrue_{max}$\\
-    %\midrule
-       27825.594022 &  6.060061e-12 &  3.167883e-12 &  1.558607e-13 &  1.038747e-13 &   -0.2 &   -0.1 \\
-      247707.635599 &  5.940855e-16 &  2.923931e-16 &  1.364937e-17 &  8.115912e-18 &   -0.7 &   -0.6 \\
-         22.387000 &  3.328100e-02 &  2.781700e-02 &  9.565800e-03 &  7.149400e-03 &   -0.3 &   -0.2 \\
-      432876.128108 &  5.185841e-17 &  2.320702e-17 &  1.456761e-18 &  9.828299e-19 &   -1.1 &   -1.0 \\
-       64280.731173 &  1.582403e-13 &  8.095293e-14 &  3.480179e-15 &  2.211758e-15 &   -0.4 &   -0.3 \\
-    %\bottomrule
-\end{tabular}
-
-The fluxes are averaged over azimuthal direction and over solar minimun/maximum. The units of the fluxes are given as \si{\GeV^-1 \metre^-2 \second^-1 \steradian^-1}. 
-We note that the fluxes for $\nt$ and $\nu_\bar{\tau}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. Thus, we never have to use probabilities on the form 
-$P_{\tau \beta}$, since we have no incoming $\nu_\tau$.
-
-After interpolating this data, we can plot the raw data together with its interpolated values.
-%TODO: flux interpolated figure.
-
 As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact in the ice to form their charged leptons.
@@
 The effective area, $\Aeff$, depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section.
-Fortunately, the binned $\Aeff$ is provided to us by the ICeCube collaboration~\cite{ICaeff}.
+Fortunately, the binned $\Aeff$ is provided to us by the collaboration~\cite{ICaeff}.
 The data file has the following form
 
+\begin{table}\label{table:aeff}
     \begin{tabular}{lrrrrr}
-    %\toprule
+        \hline \hline
         $\Etrue_{min}$ [\si{\GeV}] &     $\Etrue_{max}$ [\si{\GeV}]&   $\ztrue_{min}$ &   $\ztrue_{max}$ &     $\Aeff$ [\si{\metre\squared}] \\
-    %\midrule
-         251.2 &      316.2 &  -0.92 &  -0.91 &   0.0174 \\
-      794300.0 &  1000000.0 &  -0.80 &  -0.79 &  69.3600 \\
-        3981.0 &     5012.0 &  -0.78 &  -0.77 &   3.1490 \\
-        1585.0 &     1995.0 &  -0.07 &  -0.06 &   0.4659 \\
-        398.1 &      501.2 &  -0.73 &  -0.72 &   0.0555 \\
-    %\bottomrule
+        \hline
+             251 &      316 &  -0.92 &  -0.91 &   0.0174 \\
+          794300 &  1000000 &  -0.80 &  -0.79 &  69.3600 \\
+            3981 &     5012 &  -0.78 &  -0.77 &   3.1490 \\
+            1585 &     1995 &  -0.07 &  -0.06 &   0.4659 \\
+            398 &      501 &  -0.73 &  -0.72 &   0.0555 \\
+        \hline
         \end{tabular}
-Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_\bar{\mu}$. Thus, it is not flavor dependent.
+    \caption{IceCube effective area from~\cite{ICaeff}}
+\end{table}
+
+Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$. Thus, it is not flavor dependent.
 Just as with the fluxes, we interpolate this in $\Etrue,\ztrue$ and show the result %TODO aeff interpolation
@@
 So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publically released by the 
-collaboration has all the ingredients that we need. %TODO: source.
-In Table %TODO: add
-we see a snippet of how it looks like.
+collaboration has all the ingredients that we need~\cite{IC2016}. In Table.~\ref{table:IC_MC} we show a selection of the data.
+The "pdg" column refers to the Monte Carlo particle classification, where 13 is the tag for $\nm$, while -13 refers
+to an $\anm$. Here we note a crucial property of the IceCube dataset that will impact our analysis: the MC released by the collaboration
+only includes simulated muon events.
+
+\begin{table}\label{table:IC_MC}
+    \begin{tabular}{lrrrrr}
+        \hline \hline
+        pdg &      $\Ereco$ [\si{\GeV}] &     $\zreco$ &       $\Etrue$ [\si{\GeV}] &     $\ztrue$ \\
+        \hline
+         13 &  1665 & -0.645884 &    592 & -0.653421 \\
+         13 &   587 & -0.373241 &    342 & -0.424979 \\
+        -13 &  1431 & -0.177786 &   1169 & -0.189949 \\
+        -13 &   831 & -0.807226 &   1071 & -0.805559 \\
+         13 &   988 & -0.370746 &   1861 & -0.367922 \\
+         \hline
+  \end{tabular}
+  \caption{A selection of the data found in~\ref{IC2016}}
+\end{table}
 
@@
  \end{figure}
-
+\bibliographystyle{nature}
+\bibliography{ref.bib}
 \end{document}

### 2021-05-04 thesis/tex/nsiTheory.tex
update

@@
-\documentclass[draft=True]{thesis}
+\documentclass{thesis}
+\usepackage[margin=0.5in]{geometry}
 \input{commands}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
+\usepackage{siunitx, graphicx}
 \usepackage[utf8]{inputenc}
@@
 \section{Non-standard interactions in IceCube}
-In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$ directly or 
-indirectly. Since all standard matter potentials are diagonal, the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
+In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
+the IceCube data is avaibable in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have settled down.
+
+Since all standard matter potentials are diagonal, 
+the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
 by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,
@@
 Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
-of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since the NSI parameters are 6, and the PMNS
-matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix.
+of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since we have 6 NSI parameters, and the PMNS
+matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
+two of the three mixing angles, making them much more dependent on each other.
 
-As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$ and $\emm$ or $\ett$ the most suitable
-NSI parameters to constrain.
+As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
+NSI parameters to constrain from muon events. As we will see, $\eem$ is also a candidate, alebit a weaker one.
 
-In Fig.~\ref{fig:IC_NSI_probs}, we plot $\Pmm$ and $\Pamam$ for 3 cases of $\ep$ and $\emt$ each. As is clear from the 
-left panels, the value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, as we expected. Hence, we will not be able
-to say anything about $\ett$ in our study. The right panels show an interesting relationship between the sign of the NSI parameter 
-and the neutrino type. $\Pmm$ with positive $\ett$ is the same as $\Pamam$ with negative $\ett$. Looking at the form of the matter potential, 
-this is something that we should expect. In the standard interaction framework, we distinguish between neutrinos and antineutrinos by flipping the sign 
-of the CC potential. Since the NSI potential has the same form, any sign flipping of the NSI potential will have the same effect as 
-having an antineutrino.
+In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
+for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
+amplitude nor frequency of the probabilities. Instead, it seems to strech or compress the oscillations. Since the 
+only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
+$\nm$ with positive $\epsilon_{\a\b}$ is identical to the probability for $\anm$ with negative $\epsilon_{\a\b}$. Thus, the dashed line 
+in the right panel not only shows the survival probability for $\anm$ with $\emt=0.02$, but also the survival probability for $\nm$ with $\emt=-0.02$.
+Hence, we note that $\emt > 0$ stretches (compresses) $\Pmm$ for neutrinos (antineutrinos), while $\emt < 0$ compresses (stretches) $\Pmm$ for neutrinos (antineutrinos).
 
-\begin{figure}\label{fig:IC_NSI_probs}
-    \begin{center}
-    \includegraphics[width=1\textwidth, height=0.3\textheight]{figures/IC_NSI_probs.pdf}
-    \caption{\emph{Top panels: }$\nm$ survival probability for different cases of the two NSI parameters $\ett$ and $\emt$
-    \emph{Bottom panels: }$\anm$ survival probability for different cases of the two NSI parameters $\ett$ and $\emt$.
-    In all plots, \ztrue = -1.}
+The value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
+to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
+we see that even though we let $\ett$ take 2.5 times the value of $\emt$, its effect on $\Pmm$ is smaller.
+The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent
+constraint due to the weakness of the effect compared to $\emt$.
+
+Thus, we will use IceCube to constrain $\emt$ only.
+
+Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
+In ~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
+in the DeepCore region of rapid oscillations, where mixing is more violent. 
+\begin{figure}\label{fig:emt_ett_probs}
+    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
+        \includegraphics[width=0.45\textwidth]{figures/emt_probs.pdf}
+        \includegraphics[width=0.45\textwidth]{figures/ett_probs.pdf}
+        \caption{\emph{Left panel:} Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero.
+        \emph{Right panel:} Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero.}
     \end{center}
 \end{figure}
+
+\begin{figure}\label{fig:eem_eet_probs}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figures/eem_probs.pdf}
+        \includegraphics[width=0.45\textwidth]{figures/eet_probs.pdf}
+        \caption{Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$\emph{Left panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero.
+        \emph{Right panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero.}
+    \end{center}
+\end{figure}
+
+\section{Non-standard interactions in DeepCore and PINGU}
+Now we repeat our proability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
+we have rapid oscillations, which means that "indirect" modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
+will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
+many oscillations have settled down.
+
+Another feature of our DeepCore study includes the fact that we now have access to cascade events, in which $\ne$ and $\nt$ are more abundant. %TODO:show this?
+Thus, we are no longer constrained to the $\mu$ channel alone, but we can now find interesting features in the other channels too. However, we 
+remember that the $\nm$ flux is still the most abundant. %TODO: link to plot comparison of m and e flux.
+
+Fig.~\ref{fig:emt_ett_probs} shows that $\emt$ affects both $\Pmm$ and $\Pamam$ over the whole energy range. Since 
+IceCube also sees this, we hope to be able to boost the constraining of $\emt$ by combining the two experiments.
+
+Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
+a weaker resonance dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.
+
+$\eem$ in Fig.~\ref{fig:eem_eet_probs} shows weak resonance dampening for both $\nm$ and $\anm$.
+
+For $\eet$, we see a similar resonance dampening in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
+see the $\eet$ effect in DeepCore/PINGU, but remember that we now have the option to look at the other flavor channels.
+
+Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
+a clear difference when turning on $\eet$.
+%TODO: clean up above and expand a bit.
+\begin{figure}\label{fig:Pee_eet_probs}
+    \begin{center}
+        \includegraphics[width=0.6\textwidth]{figures/Pee_eet_probs.pdf}
+        \caption{Electron neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero.}
+    \end{center}
+\end{figure}
+
+We summarize our findings in Table~\ref{table:nsi}
+\begin{table}
+    \begin{center}
+    \begin{tabular}{lccc}
+            \hline \hline & & \multicolumn{2}{c} {\text { Visibility }} \\
+            \cline { 3 - 4 } \text {Parameter} & Range & \text { IC } & \text {DC } \\
+            \hline
+            $\ett$ &$\pm 0.05 $ & $\times$ & \checkmark \\
+            $\emt$ &$\pm 0.02 $& \checkmark & \checkmark \\
+            $\eem$ &$\pm 0.2 $& \checkmark & \checkmark \\
+            $\eet$ &$\pm 0.2 $& $\times$ & \checkmark \\
+            \hline
+        \label{table:nsi}
+    \end{tabular}
+    \end{center}
+    \caption{Table of NSI parameters and their ranges considered in this study, along with visibility off
+    their signal in IceCube (IC) and DeepCore/PINGU (DC).}
+\end{table}
+
 \end{document}

### 2021-05-04 thesis/tex/oscillations.tex
update

@@
 \documentclass[draft=True]{thesis}
+\usepackage[margin=0.5in]{geometry}
 \usepackage{graphicx, slashed}
@@
 In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
-suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. We will see that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
-the most abundant. This means we will be able to constrain any parameters relating to $\nm \to \nt$ oscillations stringently.
+suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
+the most abundant. This means we will be able to stringently constrain parameters relating to $\nm \to \nt$ oscillations.
 

### 2021-05-05 thesis/tex/DCtheory.tex
update

--- 2021-04-26 latex/article/article.tex
@@
-\documentclass[draft=True]{revtex4-2}
-\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
-\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
-\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
-\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
-\newcommand{\eet}{\epsilon_{e\tau}}
-\newcommand{\eem}{\epsilon_{e\mu}}
-\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
-\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
-\renewcommand{\ne}{\nu_e}
-\newcommand{\nm}{\nu_\mu}
-\newcommand{\nt}{\nu_\tau}
-\newcommand{\ane}{\bar\nu_e}
-\newcommand{\anm}{\bar\nu_\mu}
-\newcommand{\ant}{\bar\nu_\tau}
-\newcommand{\dm}{\Delta m^2_{31}}
-\newcommand{\sth}{\sin^2(2\theta_{23})}
-
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
+\documentclass[draft=True]{thesis}
+\usepackage[margin=0.5in]{geometry}
+\usepackage{graphicx, slashed, siunitx}
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref}
+\usepackage{xr-hyper}
+\input{commands}
 \begin{document}
-\section{Methodology}
-The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
-Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. %TODO: add more here?
-
-The oscillation probability $P_{\alpha \beta}$ acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
-\begin{align}\label{eq:propFlux}
-    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
-\end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of NSI on both probability
-and flux level, we plot the oscillograms in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
-DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
-and DeepCore track events originating from $\nm$ fluxes are contained.
-
-\begin{figure}[!tb]
-   \begin{center}
-      \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
-      \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
-   \end{center}
-   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
-   DeepCore (IceCube) MC events are contained. \emph{Left panel:} Propagated fluxes of $\ne$ and $\nt$ neutrinos and anti-neutrinos. 
-   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale
-\end{figure}
-
-\subsection{IceCube}\label{ch:ICmethod}
-The event rate for each bin reads
-\begin{align}\label{eq:ICevents}
-    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
-    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
-\end{align}
-where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$.
-We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}.
-$R(x^r,x^t)$ is a resolution function,
-which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
-\begin{align}
-    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
-\end{align}
-Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
-simulated events is skewed in energy. To model this bias between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
-we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $E^\text{true}$ points of the 99th percentile of each distribution to obtain
-the limits of $E^\text{true}$ at which to integrate over.
-We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
-The data is from the IC86 sterile analysis~\cite{IC2020}.
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
-    \end{center}
-    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}.
-Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
- \end{figure}
-
-\subsection{DeepCore}\label{ch:DCmethod}
+\section{DeepCore}
 In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
@@
 number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
-
-\begin{figure}[!tb]
-   \begin{center}
-      \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
-      \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
-   \end{center}
-   \caption{Expected pulls of predicted event numbers for DeepCore and PINGU after 3 years. We compare the NSI event count with $\emt=-0.05$
-    to the standard interaction count}\label{fig:event_pulls} %TODO: remake these with clearer titles and better labels
-\end{figure}
-
-\subsection{PINGU}\label{ch:PINGUmethod}
+\section{PINGU}
 The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}.
@@
 \end{align}
-
-\section{Results}
-For our analyses, we define our $\chi^2$ as
-\begin{align} \label{eq:ICchisq}
-    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
-    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
-    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
-\end{align}
-where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
-$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
-We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}.
-The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
-
-For IceCube, the event count takes the form
-\begin{align}
-    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
-\end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents} Here, we allow the event distribution to rotate around the median zenith of $-0.5$.
-
-For DeepCore and PINGU, the event count takes the form
-\begin{align}
-    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
-\end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
-The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,.
-For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
-For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
-muon background estimate~\cite{DC2019data}.
-
-First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
-which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_ett.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_emt.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eem.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eet.pdf}
-    \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all NSI 
-    parameters not shown in each plot are set to zero.}\label{fig:PINGU_3D}
- \end{figure}
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
-    \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
- \end{figure}
-
-For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
-\begin{align}
-    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
-\end{align}
-with test statistic $\chi^2_\text{joint,min}$.
-
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/emm_deltachi.pdf}
-    \end{center}
-    \caption{}\label{fig:emm_deltachi}
- \end{figure}
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
-    \end{center}
-    \caption{}\label{fig:emm_emp_contour}
- \end{figure}
-%At $90\%$ CL:
-%PINGU: $-0.046 < \emm < 0.041$
-%DC: $-0.045 < \emm < 0.041$
-%joint: $-0.038 < \emm < 0.033$
-
-%TODO: table with individual and combined chisq values. Discussion on impact of IC on chisq.
-
- \newpage
-\begin{tabular}{p{55mm}p{55mm}p{55mm}}
-   DeepCore (2017)
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\times$] Only look at tracks and $\emt$
-         \vspace{1em}  
-         \item[$\times$] DC Monte Carlo from an older dataset 
-         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\times$] 8 z bins from -1 to 0 
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
-      \end{itemize} &
-    Demidov (2020) DC analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
-         \item[$\checkmark$] Data and Monte Carlo from DC 2018
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 z bins from -1 to 1
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
-         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
-         \item[$\times$] Uncertainty on hadron production in atmosphere
-         \item[$\times$] Uncertainty on neutrino nucleon cross section 
-      \end{itemize} &
-    Our DC+PINGU analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Tracks and cascades for all flavors
-         \vspace{1em} 
-         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
-         \item[$\checkmark$] Flux normalization uncertainty of 25\%
-         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
-         \item[$\checkmark$] No priors on oscillation parameters 
-         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
-      \end{itemize} 
-\end{tabular}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{article}
+\bibliographystyle{nature}
+\bibliography{ref.bib}
 \end{document}

### 2021-05-05 thesis/tex/ICintro.tex
update

@@
-\documentclass[draft=True]{thesis}
-\usepackage{graphicx, slashed, siunitx}
+\documentclass{thesis}
+\usepackage[margin=0.5in]{geometry}
+\usepackage{graphicx, slashed, siunitx, subcaption}
 \usepackage[utf8]{inputenc}
@@
 \begin{document}
+\section{Neutrino detection}
 We always observe neutrinos indirectly through their associated charged lepton. Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
@@
 
-In this work, we only study the detectors handeled by the ICecube collaboration. They are of Cherenkov type, which means that they detect 
-the charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
-%TODO: text about pid
+In this work, we only study the detectors handeled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
+the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice.
+
+If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
+Cherenkov light. This event is referred to as a cascade. The neutral current interactions involves quarks, which recoils and procudes
+showers of hadrons. Also, charged current $\ne$ interactions also produce cascades. A cascade event 
+is shown in Fig.~\ref{fig:events_cascade}.
+
+If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
+as they go. This event is referred to as a track, and are often due to muon charged current interactions. A track event 
+is shown in Fig.~\ref{fig:events_track}.
+
 \begin{figure}\label{fig:events}
-    \includegraphics[width=0.5\textwidth]{figures/cascade_event.pdf}\caption{Event classified as cascade}
-    \includegraphics[width=0.5\textwidth]{figures/track_event.pdf}\caption{Event classified as track}
+    \begin{center}
+        \begin{subfigure}{0.4\textwidth}
+            \centering
+            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
+            \caption{Event classified as cascade}  
+            \label{fig:events_cascade}
+          \end{subfigure}
+        \begin{subfigure}{0.4\textwidth}
+            \centering
+            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
+            \caption{Event classified as track} 
+            \label{fig:events_track}
+        \end{subfigure}
+        \caption{The two event types distinguished in the IceCube detector.}
+    \end{center}
 \end{figure}
@@
 not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
-IceCube and DeepCore bounds. 
+IceCube and DeepCore bounds. The PINGU simulations have the same structure as the DeepCore data, so any analysis referring to DeepCore will
+also apply to PINGU except where noted. However, we treat the PINGU detector as independent of the DeepCore experiment.
 \bibliographystyle{nature}

### 2021-05-05 thesis/tex/ICtheory.tex
update

@@
 \section{Atmospheric neutrino flux}
-The flux comes from \cite{hondaArticle} %TODO: talk about flux
-The flux data is binned in $\ztrue$ and a selection is shown in Table~\ref{table:flux}. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
+Atmospheric neutrinos originates from cosmic rays composed of protons interacting with nuclei in the atmosphere.
+These interactions ultimately produces pions, which decay as 
+\begin{align}\label{eq:pion}
+    \pi^+ &\to \mu^+ + \nm\,, \quad \pi^- \ to \mu^- + \anm \nonumber \\
+    \pi^+ &\to e^+ + \ne\,, \quad \pi^- \ to e^- + \ane\,.
+\end{align}
+In the muonic decay channel, muons are emitted which will be detected by the IceCube detector. A part of the 
+uncorrelated systematic error comes from this \emph{muon background}, i.e. events misclassified as muons from 
+$\nm$ interactions rather than from pion decay. Moreover, the atmospheric flux is often associated with a large error.
+In this work, we will use a flux normalization error of 24\%, and a zenith slope error of 4\%. In more sophisticated 
+models, one can also include the pion to kaon flux uncertainty.
+
+The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}
+The flux data is binned in $\ztrue$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
 The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
 from the table for clarity. 
-We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. 
-Thus, we never have to use probabilities on the form 
+We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. Kaons can decay into neutral pions, which in turn 
+can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities on the form 
 $P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.
@@
     \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
+       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
     \end{center}

### 2021-05-05 thesis/tex/nsiResults.tex
update

--- 2021-04-26 latex/article/article.tex
@@
-\documentclass[draft=True]{revtex4-2}
-\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
-\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
-\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
-\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
-\newcommand{\eet}{\epsilon_{e\tau}}
-\newcommand{\eem}{\epsilon_{e\mu}}
-\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
-\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
-\renewcommand{\ne}{\nu_e}
-\newcommand{\nm}{\nu_\mu}
-\newcommand{\nt}{\nu_\tau}
-\newcommand{\ane}{\bar\nu_e}
-\newcommand{\anm}{\bar\nu_\mu}
-\newcommand{\ant}{\bar\nu_\tau}
-\newcommand{\dm}{\Delta m^2_{31}}
-\newcommand{\sth}{\sin^2(2\theta_{23})}
-
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
+\documentclass[draft=True]{thesis}
+\usepackage[margin=0.5in]{geometry}
+\usepackage{graphicx, slashed, siunitx}
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref}
+\usepackage{xr-hyper}
+\input{commands}
 \begin{document}
-\section{Methodology}
-The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
-Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. %TODO: add more here?
-
-The oscillation probability $P_{\alpha \beta}$ acts as a weight, yielding the propagated flux at detector level for flavor $\beta$ as 
-\begin{align}\label{eq:propFlux}
-    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
-\end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of NSI on both probability
-and flux level, we plot the oscillograms in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
-DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
-and DeepCore track events originating from $\nm$ fluxes are contained.
-
-\begin{figure}[!tb]
-   \begin{center}
-      \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
-      \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
-   \end{center}
-   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
-   DeepCore (IceCube) MC events are contained. \emph{Left panel:} Propagated fluxes of $\ne$ and $\nt$ neutrinos and anti-neutrinos. 
-   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale
-\end{figure}
-
-\subsection{IceCube}\label{ch:ICmethod}
-The event rate for each bin reads
-\begin{align}\label{eq:ICevents}
-    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
-    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
-\end{align}
-where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$.
-We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}.
-$R(x^r,x^t)$ is a resolution function,
-which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
-\begin{align}
-    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
-\end{align}
-Assuming no bias in the reconstruction, the mean of the Gaussian can be taken as $\mu(x^t) = x^t$. As seen in Fig.~\ref{fig:IC_MC_counts}, the distribution of 
-simulated events is skewed in energy. To model this bias between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
-we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $E^\text{true}$ points of the 99th percentile of each distribution to obtain
-the limits of $E^\text{true}$ at which to integrate over.
-We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
-The data is from the IC86 sterile analysis~\cite{IC2020}.
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
-    \end{center}
-    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}.
-Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
- \end{figure}
-
-\subsection{DeepCore}\label{ch:DCmethod}
-In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
-IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.
-
-The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
-They are applied as correction factors using the best-fit points from the DeepCore 2019 $\nu_\tau$ appearance 
-analysis~\cite{DC2019tauappearance}.
-
-The data include 14901 track-like events and 26001 cascade-like events, both divided into eight 
-$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{ijk,\beta}$,
-from which we can construct the event count as
-\begin{align}\label{eq:MCevents}
-    N_{ijk} &= C_{ijk}\sum_{\beta}w_{ijk,\beta} \phi_\beta^\text{det}\,,
-\end{align}
-where $C_{k\beta}$ is the correction factor from the detector systematic uncertainty and $\phi_\beta^\text{det}$ is defined as Eq.~\ref{eq:propFlux}.
-We have now substituted the effect of the Gaussian smearing
-by treating the reconstructed and true quantities as a migration matrix.
-
-The oscillation parameters used on our DeepCore simulations are from the
-best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\dm$ and $\theta_{23}$.
-
-We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
-assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
-number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
-
-\begin{figure}[!tb]
-   \begin{center}
-      \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
-      \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
-   \end{center}
-   \caption{Expected pulls of predicted event numbers for DeepCore and PINGU after 3 years. We compare the NSI event count with $\emt=-0.05$
-    to the standard interaction count}\label{fig:event_pulls} %TODO: remake these with clearer titles and better labels
-\end{figure}
-
-\subsection{PINGU}\label{ch:PINGUmethod}
-The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}.
-We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
-As with the DeepCore data, the PINGU MC is divided into eight 
-$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
-We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
-
-\begin{align}\label{eq:PINGUparams}
-    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
-    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
-\end{align}
-
-\section{Results}
+\section{$\chi^2$ minimization}
 For our analyses, we define our $\chi^2$ as
@@
 muon background estimate~\cite{DC2019data}.
-
-First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
-which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_ett.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_emt.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eem.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eet.pdf}
-    \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all NSI 
-    parameters not shown in each plot are set to zero.}\label{fig:PINGU_3D}
- \end{figure}
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
-    \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
- \end{figure}
-
-For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
-\begin{align}
-    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
-\end{align}
-with test statistic $\chi^2_\text{joint,min}$.
-
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/emm_deltachi.pdf}
-    \end{center}
-    \caption{}\label{fig:emm_deltachi}
- \end{figure}
-
- \begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
-    \end{center}
-    \caption{}\label{fig:emm_emp_contour}
- \end{figure}
-%At $90\%$ CL:
-%PINGU: $-0.046 < \emm < 0.041$
-%DC: $-0.045 < \emm < 0.041$
-%joint: $-0.038 < \emm < 0.033$
-
-%TODO: table with individual and combined chisq values. Discussion on impact of IC on chisq.
-
- \newpage
-\begin{tabular}{p{55mm}p{55mm}p{55mm}}
-   DeepCore (2017)
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\times$] Only look at tracks and $\emt$
-         \vspace{1em}  
-         \item[$\times$] DC Monte Carlo from an older dataset 
-         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\times$] 8 z bins from -1 to 0 
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
-      \end{itemize} &
-    Demidov (2020) DC analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
-         \item[$\checkmark$] Data and Monte Carlo from DC 2018
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 z bins from -1 to 1
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
-         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
-         \item[$\times$] Uncertainty on hadron production in atmosphere
-         \item[$\times$] Uncertainty on neutrino nucleon cross section 
-      \end{itemize} &
-    Our DC+PINGU analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Tracks and cascades for all flavors
-         \vspace{1em} 
-         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
-         \item[$\checkmark$] Flux normalization uncertainty of 25\%
-         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
-         \item[$\checkmark$] No priors on oscillation parameters 
-         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
-      \end{itemize} 
-\end{tabular}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{article}
 \end{document}

### 2021-05-05 src/events/make_events.py

@@ -68,14 +68,14 @@ if __name__ == '__main__':
         H1 = np.array(H1_events_list)
         H1 = H1.reshape(len(param_list),1,8,8) #second axis is pid
         #H1 = np.swapaxes(H1,1,3) #Put pid on second index
-        H1 = np.swapaxes(H1,2,3) #Swap e and z bins
+        #H1 = np.swapaxes(H1,2,3) #Swap e and z bins
         pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_PINGU_{args.pid}_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
     elif args.DC:
         H1_events_list = process_map(precompute_probs, param_tuple,chunksize=4)
         H1 = np.array(H1_events_list)
         H1 = H1.reshape(len(param_list),1,8,8) #second axis is pid
         #H1 = np.swapaxes(H1,1,3) #Put pid on second index
-        H1 = np.swapaxes(H1,2,3) #Swap e and z bins
+        #H1 = np.swapaxes(H1,2,3) #Swap e and z bins
         pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_DC_{args.pid}_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
     if args.IC:
         data = [(0.99, 13,p, False,False, [False, 0, 0],True, True,3) for p in param_list]

### 2021-05-05 article/article.tex
update

@@
     \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
+      \includegraphics[width=0.6\linewidth]{figures/DC_3D_NO.pdf}
+      %\includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
+      %\includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
     \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
+    \caption{The expected values of $\Delta \chi^2$ after three years of DC data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+    parameters other than the one displayed in each panel are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D}
  \end{figure}
@@
 
+\begin{table}
+   \begin{center}
+   \begin{tabular}{lcccc}
+           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
+           \cline { 3 - 5 } Parameter & 90\% CL & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \hline
+           $\ett$ & -0.028, 0.044 & 2.435 & 47.84 & 0.0125 \\
+           $\emt$ & -0.015, 0.0050 & 2.435 & 43.97 & -0.005 \\
+           $\eem$ & -0.068, 0.070 & 2.435 & 43.97 & 0 \\
+           $\eet$ & -0.072, 0.14 & 2.435 & 43.97  & 0.05 \\
+           \hline
+       \label{table:DC_results}
+   \end{tabular}
+   \end{center}
+   \caption{DeepCore results. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   $\si{\degree}$, respectively.}
+\end{table}
+
+\begin{table}
+   \begin{center}
+      \begin{tabular}{lcccc}
+         \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
+         \cline { 3 - 5 } Parameter & 90\% CL & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+         \hline
+         $\ett$ &-& - & - & -\\
+         $\emt$ &-& - & - & -\\
+         $\eem$ & -0.060, 0.055 & 2.517 & 49.2 & 0 \\
+         $\eet$ & -0.065, 0.072 & 2.517 & 49.2 & 0 \\
+         \hline
+      \label{table:PINGU_results}
+      \end{tabular}
+   \end{center}
+   \caption{PINGU results. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   $\si{\degree}$, respectively.}
+\end{table}
+
+\begin{table}
+   \begin{center}
+   \begin{tabular}{lcccc}
+           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
+           \cline { 3 - 5 } Parameter & 90\% CL & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \hline
+           $\ett$ &-& - & - & -\\
+           $\emt$ &-& - & - & -\\
+           $\eem$ & -0.046, 0.046 \hspace{1cm}& 2.489 & 47.84 & 0 \\
+           $\eet$ & -0.057, 0.028 \hspace{1cm}& 2.489 & 47.84 & 0 \\
+           \hline
+       \label{table:PINGU_results}
+   \end{tabular}
+   \end{center}
+   \caption{Joint results. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   $\si{\degree}$, respectively.}
+\end{table}
+
 \bibliographystyle{elsarticle-num}

### 2021-05-05 src/events/DC/event_processing.py

@@ -187,5 +187,49 @@ def get_best_fit(deltachi, p_range, cl):
     left = interpolate.interp1d(deltachi[0:half],p_range[0:half])(chi2.ppf(cl,1))
     right = interpolate.interp1d(deltachi[half:-1],p_range[half:-1])(chi2.ppf(cl,1))
     return np.round(left,3),np.round(right,3)
+
+def get_marginalized_array(H1,dm31_range,th23_range,ett_range,emt_range,eem_range,eet_range, param_list, nsi_param, sigma_a,sigma_b, f):
+    chisq,  best_fit_index = get_deltachi([H for H in H1],0,[sigma_a,sigma_b],f,x0=[1,0])
+
+    reshaped_chisq = chisq.reshape(len(eet_range),
+                                len(eem_range),
+                                len(emt_range), 
+                                len(ett_range), 
+                                len(th23_range), 
+                                len(dm31_range)) #reshaped_chisq[eet,eem,emt,emm,th23,dm31]
+    minimum_oscillation = np.min(reshaped_chisq,axis=(0,1,2,3)).reshape(1,1,1,1,len(th23_range),len(dm31_range)) #Marginalize osc params
+    deltachi = reshaped_chisq - minimum_oscillation
+
+
+    best_eet_index,best_eem_index,best_emt_index,best_ett_index,best_th23_index, best_dm31_index = np.unravel_index(best_fit_index,deltachi.shape)
+    best_dm31, best_th23, best_ett, best_emt, best_eem, best_eet = (dm31_range[best_dm31_index], 
+                                                                    th23_range[best_th23_index],
+                                                                    ett_range[best_ett_index],
+                                                                    emt_range[best_emt_index],
+                                                                    eem_range[best_eem_index],
+                                                                    eet_range[best_eet_index])
+    best_fit_params = param_list[best_fit_index]
+    assert best_fit_params['dm_31'] == best_dm31 
+    assert best_fit_params['theta_23'] == best_th23
+    assert best_fit_params['e_tt'] == best_ett
+    assert best_fit_params['e_mt'] == best_emt
+    assert best_fit_params['e_em'] == best_eem
+    assert best_fit_params['e_et'] == best_eet
+
+    marginalized_deltachi = deltachi[:,:,:,:,best_th23_index,best_dm31_index].T # marginalized_deltachi[ett,emt,eem,eet]
[…]

### 2021-05-05 src/events/PINGU/event_processing.py

@@ -139,5 +139,48 @@ def is_precomputed_nsi(pid,ndim, dict, check=False):
                     else:
                         raise FileNotFoundError(f'P{flavor_from}{flavor_to} {ndim}gen for pid {pid}, dm={dict["dm_41"]}, s24={np.sin(2*dict["theta_24"])**2}, e_mm={dict["e_mm"]},e_mt={dict["e_mt"]}, not found')
                 return True
+def get_marginalized_array(H1,H0,dm31_range,th23_range,ett_range,emt_range,eem_range,eet_range, param_list, nsi_param, sigma_a,sigma_b, f):
+    chisq,  best_fit_index = get_deltachi([H for H in H1],H0,0,[sigma_a,sigma_b],f,x0=[1,0])
+
+    reshaped_chisq = chisq.reshape(len(eet_range),
+                                len(eem_range),
+                                len(emt_range), 
+                                len(ett_range), 
+                                len(th23_range), 
+                                len(dm31_range)) #reshaped_chisq[eet,eem,emt,emm,th23,dm31]
+    minimum_oscillation = np.min(reshaped_chisq,axis=(0,1,2,3)).reshape(1,1,1,1,len(th23_range),len(dm31_range)) #Marginalize osc params
+    deltachi = reshaped_chisq - minimum_oscillation
+
+
+    best_eet_index,best_eem_index,best_emt_index,best_ett_index,best_th23_index, best_dm31_index = np.unravel_index(best_fit_index,deltachi.shape)
+    best_dm31, best_th23, best_ett, best_emt, best_eem, best_eet = (dm31_range[best_dm31_index], 
+                                                                    th23_range[best_th23_index],
+                                                                    ett_range[best_ett_index],
+                                                                    emt_range[best_emt_index],
+                                                                    eem_range[best_eem_index],
+                                                                    eet_range[best_eet_index])
+    best_fit_params = param_list[best_fit_index]
+    assert best_fit_params['dm_31'] == best_dm31 
+    assert best_fit_params['theta_23'] == best_th23
+    assert best_fit_params['e_tt'] == best_ett
+    assert best_fit_params['e_mt'] == best_emt
+    assert best_fit_params['e_em'] == best_eem
+    assert best_fit_params['e_et'] == best_eet
+
[…]

### 2021-05-06 article/article.tex
update

--- 2021-04-30 article/article.tex
@@
 
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
+\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
 \usepackage[utf8]{inputenc}
@@
 Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. %TODO: add more here?
+production height of 15 km and an Earth radius of 6371 km. %TODO: add more here? no neutrino absorption
 
@@
 
-We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
-assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
+We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
+assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
 number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
@@
 For our analyses, we define our $\chi^2$ as
-\begin{align} \label{eq:ICchisq}
+\begin{align} \label{eq:chisq}
     \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
@@
 \end{align}
-where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
+where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
 $N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
@@
    \begin{center}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_ett.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_emt.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eem.pdf}
-       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eet.pdf}
+      \begin{subfigure}{0.4\textwidth}
+         \includegraphics[width=1\linewidth]{figures/PINGU_3D_NO.pdf}
+         \label{fig:PINGU_3D_NO}
+         \caption{PINGU}
+      \end{subfigure}
+      \begin{subfigure}{0.4\textwidth}
+         \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
+         \label{fig:PINGU_3D_NO}
+         \caption{DeepCore}
+      \end{subfigure}
     \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all NSI 
-    parameters not shown in each plot are set to zero.}\label{fig:PINGU_3D}
+    \caption{Minimization of the $\Delta \chi^2$ defined in Eq.~\ref{eq:chisq} after three years of data.
+    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+    parameters other than the one displayed in each panel are set to zero.}\label{fig:3D_NO}
  \end{figure}
 
- \begin{figure}[!tb]
+ \begin{table}
    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
-       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
+   \begin{tabular}{lcccc}
+           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
+           \cline { 3 - 5 } Parameter & 90\% CL\hspace{1cm} & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
+           $\ett$ & -0.028, 0.044\hspace{1cm} & 2.435 & 47.84 & 0.0125 \\
+           $\emt$ & -0.015, 0.0050\hspace{1cm} & 2.435 & 43.97 & -0.005 \\
+           $\eem$ & -0.068, 0.070\hspace{1cm} & 2.435 & 43.97 & 0 \\
+           $\eet$ & -0.072, 0.14\hspace{1cm} & 2.435 & 43.97  & 0.05 \\\\
+           \multicolumn{3}{c} {\hspace{2.5cm} PINGU } \\
+           $\ett$ & -0.036, -\hspace{1cm} & 2.517 & 49.2 & 0 \\
+           $\emt$ & -0.0076, 0.0085\hspace{1cm} & 2.517 & 49.2 & 0\\
+           $\eem$ & -0.060, 0.055\hspace{1cm} & 2.517 & 49.2 & 0 \\
+           $\eet$ & -0.065, 0.072\hspace{1cm} & 2.517 & 49.2 & 0 \\
+           \hline
+           \hline
+       \label{table:DC_PINGU_results}
+   \end{tabular}
    \end{center}
-    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
- \end{figure}
+   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   degrees, respectively.}
+\end{table}
 
 For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
-\begin{align}
+\begin{align}\label{eq:joint_chisq}
     \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
@@
     \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/emm_deltachi.pdf}
+       \includegraphics[width=0.4\linewidth]{figures/joint_3D_NO.pdf}
     \end{center}
-    \caption{}\label{fig:emm_deltachi}
+    \caption{Minimization of the joint $\chi^2$ from Eq.~\ref{fig:joint_chisq} using the $\Delta \chi^2$ shown in Fig.~\ref{fig:3D_NO}}
+    \label{fig:joint_3D}
  \end{figure}
 
- \begin{figure}[!tb]
+ \begin{table}
    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
+   \begin{tabular}{lcccc}
+           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
+           \cline { 3 - 5 } Parameter & 90\% CL\hspace{1cm} & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \hline
+           $\ett$ & -0.029, 0.0473\hspace{1cm} & 2.489 & 47.84 & 0.0125\\
+           $\emt$ & -0.0063, 0.0050\hspace{1cm} & 2.489 & 47.84 & 0\\
+           $\eem$ & -0.046, 0.046 \hspace{1cm} & 2.489 & 47.84 & 0 \\
+           $\eet$ & -0.057, 0.028 \hspace{1cm} & 2.489 & 47.84 & 0 \\
+           \hline
+       \label{table:joint_results}
+   \end{tabular}
    \end{center}
-    \caption{}\label{fig:emm_emp_contour}
- \end{figure}
-%At $90\%$ CL:
-%PINGU: $-0.046 < \emm < 0.041$
-%DC: $-0.045 < \emm < 0.041$
-%joint: $-0.038 < \emm < 0.033$
+   \caption{Joint results from $\chi^2_\{text}$ defined in Eq.~\ref{eq:joint_chisq}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   degrees, respectively.}
+\end{table}
 
-%TODO: table with individual and combined chisq values. Discussion on impact of IC on chisq.
+%TODO:  Discussion on impact of IC on chisq.?
 

### 2021-05-06 src/events/DC/event_processing.py

@@ -180,13 +180,13 @@ def is_precomputed_nsi(pid,ndim, dict, check=False):
                 return True
 
                 
-def get_best_fit(deltachi, p_range, cl):
+def get_best_fit(deltachi, p_range, cl):#TODO: make better
     from scipy import interpolate
     deltachi = deltachi.reshape(-1)
     half = int(len(p_range)/2)
     left = interpolate.interp1d(deltachi[0:half],p_range[0:half])(chi2.ppf(cl,1))
     right = interpolate.interp1d(deltachi[half:-1],p_range[half:-1])(chi2.ppf(cl,1))
-    return np.round(left,3),np.round(right,3)
+    return np.round(left,4),np.round(right,4)
 
 def get_marginalized_array(H1,dm31_range,th23_range,ett_range,emt_range,eem_range,eet_range, param_list, nsi_param, sigma_a,sigma_b, f):
     chisq,  best_fit_index = get_deltachi([H for H in H1],0,[sigma_a,sigma_b],f,x0=[1,0])

### 2021-05-06 src/events/make_events.py

@@ -8,7 +8,7 @@ if __name__ == '__main__':
 from DC.event_processing import get_param_list, list_of_params_nsi
 from PINGU.main import get_events as PINGU_events
 from DC.main import get_events as DC_events
-from IC.main import sim_events as IC_events
+from IC.main import get_events as IC_events
 from functions import nufit_params_nsi, nufit_params_nsi_IO
 
 parser = argparse.ArgumentParser()
@@ -36,12 +36,17 @@ args = parser.parse_args()
 
 
 def precompute_probs(args_tuple):
-    i,j,params,pid = args_tuple
     if args.PINGU:
+        i,j,params,pid = args_tuple
         res = PINGU_events(Ebin=i,zbin=j,params=params,pid=pid,nsi=True, save=False)
     elif args.DC:
+        i,j,params,pid = args_tuple
         res = DC_events(Ebin=i,zbin=j,params=params,pid=pid,nsi=True, no_osc=False, save=False)
+    elif args.IC:
+        i,j,a, N,p, spectral,null, tau,ndim = args_tuple
+        res = IC_events(E_index=i, z_index=j, alpha=a, npoints=N, params=p, spectral_shift_parameters=spectral, null=null, tau=tau, ndim=ndim)
     return np.array(res)
+
 
 if __name__ == '__main__':
     assert args.PINGU or args.DC or args.IC
@@ -78,6 +83,7 @@ if __name__ == '__main__':
         #H1 = np.swapaxes(H1,2,3) #Swap e and z bins
         pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_DC_{args.pid}_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
     if args.IC:
-        data = [(0.99, 13,p, False,False, [False, 0, 0],True, True,3) for p in param_list]
-        H1_events_list = process_map(IC_events, data)
+        data = [(i,j,0.99, 13,p, [False, 0, 0],False, True,3) for p in param_list for i in range(13) for j in range(20)]
+        H1_events_list = process_map(precompute_probs, data,chunksize=4)
+        H1_events_list = H1_events_list.reshape(len(param_list),13,20)
         pickle.dump(H1_events_list,open(f'./pre_computed/H1_{ordering}_IC_N13_{len(dm31_range)}x{len(th23_range)}x{len(emt_range)}.p','wb'))

### 2021-05-06 src/events/make_events.py
update

@@ -84,6 +84,6 @@ if __name__ == '__main__':
         pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_DC_{args.pid}_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
     if args.IC:
         data = [(i,j,0.99, 13,p, [False, 0, 0],False, True,3) for p in param_list for i in range(13) for j in range(20)]
-        H1_events_list = process_map(precompute_probs, data,chunksize=4)
+        H1_events_list = process_map(precompute_probs, data,chunksize=20)
         H1_events_list = H1_events_list.reshape(len(param_list),13,20)
         pickle.dump(H1_events_list,open(f'./pre_computed/H1_{ordering}_IC_N13_{len(dm31_range)}x{len(th23_range)}x{len(emt_range)}.p','wb'))

### 2021-05-06 src/data/IC/processer.py
update

@@ -176,25 +176,26 @@ def get_probabilities(flavor_from, flavor_to, Ebin, zbin, param_dict,anti,N,ndim
     f.close()
     return res
 
-def generate_probabilities(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,params,anti,N, ndim=4, nsi=False):
+def generate_probabilities(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,params,anti,N, ndim=4, nsi=False, save=True):
     prob = np.array([wrapper([flavor_from, E_range,z, anti, params, ndim, nsi])[mass_dict[flavor_to]] for z in z_range])
-    hashed_param_name = sha256(params)
-    if anti:
-        flavor_from = 'a' + flavor_from
-        flavor_to = 'a' + flavor_to
-    f = h5py.File(f'./pre_computed/IC/E{E_bin}z{z_bin}.hdf5', 'a')
-    try:
-        dset = f.create_dataset(f'{ndim}gen/P{flavor_from}{flavor_to}/{N}/{hashed_param_name}', data=prob, chunks=True)
-        for key in params.keys():
-            dset.attrs[key] = params[key]
-        f.close()
-    except RuntimeError:
-        print(f'{ndim}gen/P{flavor_from}{flavor_to}/{N}/{hashed_param_name} already exists, skipping')
-        f.close()
-        return prob
-    if E_bin == 5 and z_bin == 5 and flavor_from == 'am' and flavor_to == 'am':
-        with open(f'./pre_computed/IC/hashed_params.csv','a') as fd:
-            fd.write(f'{params};{hashed_param_name}\n')
+    if save:
+        hashed_param_name = sha256(params)
+        if anti:
+            flavor_from = 'a' + flavor_from
+            flavor_to = 'a' + flavor_to
+        f = h5py.File(f'./pre_computed/IC/E{E_bin}z{z_bin}.hdf5', 'a')
+        try:
+            dset = f.create_dataset(f'{ndim}gen/P{flavor_from}{flavor_to}/{N}/{hashed_param_name}', data=prob, chunks=True)
+            for key in params.keys():
+                dset.attrs[key] = params[key]
+            f.close()
+        except RuntimeError:
+            print(f'{ndim}gen/P{flavor_from}{flavor_to}/{N}/{hashed_param_name} already exists, skipping')
+            f.close()
+            return prob
[…]

### 2021-05-06 src/events/IC/main.py

@@ -50,28 +50,28 @@ def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shif
         try:
             Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
         except KeyError:
-            Pmm = generate_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim)
+            Pmm = generate_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim, save=False)
             #gather_specific_prob('Pmm',npoints,E_index,z_index,update=True,ndim=ndim)
             #Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
 
         try:
             P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         except KeyError:
-            P_amam = generate_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim)
+            P_amam = generate_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim, save=False)
             #gather_specific_prob('Pamam',npoints,E_index,z_index,update=True,ndim=ndim)
             #P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         
         try:
             Pem = get_probabilities('e', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
         except KeyError:
-            Pem = generate_probabilities('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim)
+            Pem = generate_probabilities('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim, save=False)
             #gather_specific_prob('Pem',npoints,E_index,z_index,update=True,ndim=ndim)
             #Pem = get_probabilities('e', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
 
         try:
             P_aeam = get_probabilities('e', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         except KeyError:
-            P_aeam=generate_probabilities('e','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim)
+            P_aeam=generate_probabilities('e','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim, save=False)
[…]

### 2021-05-06 article/article.tex
update

@@
 \begin{document}
-\section{Methodology}
+\section{Detector formalism}
 The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
@@
 where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
-and flux level, we plot the oscillograms resulting from Eq.\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
+and flux level, we plot the oscillograms resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
 DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
 and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
-is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore, on the other hand, 
-observes multiple fringes of flux surpluses with a factor $\sim 10^1$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
+is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore on the other hand, 
+observes multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
 energy-independent but zenith-sensetive IceCube deficiency.
@@
    \begin{center}
-      \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
+      \includegraphics[width=0.35\linewidth]{figures/cascade_flux_ratio.pdf}
       \hspace{1.5cm}
-      \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
+      \includegraphics[width=0.35\linewidth]{figures/track_flux_ratio.pdf}
    \end{center}
@@
 \begin{align}\label{eq:ICevents}
-    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
-    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
+   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}  A^\text{eff} R(E^r,E^t)
+   \dd E^t\,,
 \end{align}
-where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$.
-We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}.
-$R(x^r,x^t)$ is a resolution function,
+where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
 which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
@@
 the limits of $\Etrue$ at which to integrate over.
-We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
-The data is from the IC86 sterile analysis~\cite{IC2020}.
+We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.
+The data is from the 86 string sterile analysis~\cite{IC2020}.
 \begin{figure}[!tb]
@@
 \begin{align}\label{eq:MCevents}
-    N_{ijk} &= C_{ijk}\sum_{\beta}w_{ijk,\beta} \phi_\beta^\text{det}\,,
+    N_{ijk} &= C_{ijk}\sum_{\beta}w_{ijk,\beta}\, \phi_\beta^\text{det}\,,
 \end{align}
@@
 We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
-assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
+assuming standard (non-standard) interactions in Fig.~\ref{fig:DC_event_pulls}. This gives the normalized difference in the
 number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
 
-\begin{figure}[!tb]
+\begin{figure}[t]
    \begin{center}
-      \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
-      \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
+      \begin{subfigure}{0.49\textwidth}
+         \includegraphics[width=1\textwidth]{figures/PINGU_event_pulls.pdf}
+         \caption{PINGU}\label{fig:PINGU_event_pulls}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+         \includegraphics[width=1\textwidth]{figures/DC_event_pulls.pdf}
+         \caption{DeepCore}\label{fig:DC_event_pulls}
+      \end{subfigure}
    \end{center}
-   \caption{Expected pulls of predicted event numbers for DeepCore and PINGU after 3 years. We compare the NSI event count with $\emt=-0.05$
-    to the standard interaction count}\label{fig:event_pulls} %TODO: remake these with clearer titles and better labels
+   \caption{Expected pulls of predicted event numbers for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.05$
+    to the standard interaction count}\label{fig:event_pulls} 
+    %TODO: remake these with clearer titles and better labels, and reduce spacing between casc/tracks
+    %also, consider normalizing color scheme to one single for both.
 \end{figure}
@@
 As with the DeepCore data, the PINGU MC is divided into eight 
-$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
-We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
+$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. Just as with DeepCore, 
+we plot the events pulls for cascades and tracks in Fig.~\ref{fig:PINGU_event_pulls}. %TODO:talk about this
+We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
 
@@
 \section{Results}
+%Short intro
+\subsection{Methodology}
 For our analyses, we define our $\chi^2$ as
@@
 \end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents} Here, we allow the event distribution to rotate around the median zenith of $-0.5$.
+with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.
 
-For DeepCore and PINGU, the event count takes the form
+For DeepCore and PINGU, and the event count takes the form
 \begin{align}
@@
 The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
-For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+Since the median zenith is $\zreco = 0$ for DeepCore and PINGU, we allow the event count to rotate around zero.
+For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. %TODO: and take ... %.
 For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
-muon background estimate~\cite{DC2019data}.
+muon background estimate~\cite{DC2019data}. %TODO segue
 
+\subsection{Constraining the NSI parameters}
 First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
 which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
+After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
+confidence levels and best-fit points in Table.~\ref{table:DC_PINGU_results}.
 
@@
          \includegraphics[width=1\linewidth]{figures/PINGU_3D_NO.pdf}
-         \label{fig:PINGU_3D_NO}
-         \caption{PINGU}
+         \caption{PINGU}\label{fig:PINGU_3D_NO}
       \end{subfigure}
+      \hspace{1cm}
       \begin{subfigure}{0.4\textwidth}
          \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
-         \label{fig:PINGU_3D_NO}
-         \caption{DeepCore}
+         \caption{DeepCore}\label{fig:DC_3D_NO}
       \end{subfigure}
@@
     $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than the one displayed in each panel are set to zero.}\label{fig:3D_NO}
+    parameters other than the one shown in each panel are fixed to zero.}\label{fig:3D_NO}
  \end{figure}
@@
            \hline
-       \label{table:DC_PINGU_results}
    \end{tabular}
@@
    \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
-   degrees, respectively.}
+   degrees, respectively.}\label{table:DC_PINGU_results}
 \end{table}
 
+Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
+the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
+the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in our joint analysis,
+since PINGU has stronger statistics than DeepCore, and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
+
+%TODO: segue to joint
 For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
@@
 \end{align}
-with test statistic $\chi^2_\text{joint,min}$.
+with test statistic $\chi^2_\text{joint,min}$. The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Table~\ref{table:joint_results}.
 
-\begin{figure}[!tb]
+\begin{figure}[t]
     \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/joint_3D_NO.pdf}
+       \includegraphics[width=0.9\linewidth]{figures/joint_3D_NO.pdf}
     \end{center}
-    \caption{Minimization of the joint $\chi^2$ from Eq.~\ref{fig:joint_chisq} using the $\Delta \chi^2$ shown in Fig.~\ref{fig:3D_NO}}
+    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
     \label{fig:joint_3D}
@@
            \hline
-       \label{table:joint_results}
    \end{tabular}
    \end{center}
-   \caption{Joint results from $\chi^2_\{text}$ defined in Eq.~\ref{eq:joint_chisq}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
-   degrees, respectively.}
+   \caption{Joint results from $\chi^2_\text{joint}$ defined in Eq.~\ref{eq:joint_chisq}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   degrees, respectively}
+   \label{table:joint_results}
 \end{table}

### 2021-05-07 article/article.tex
update

@@
 \begin{document}
+%TODO: nsi intro, clear about factor 3
 \section{Detector formalism}
@@
    \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale and fix limits
-\end{figure}
+\end{figure}% smaller emt and no log. clarify that IC is missing in left panel. clarify
+%that energy region within dotted line, use as few words as possible. Normalize color scale. check green-yellow cmap
 
@@
 the limits of $\Etrue$ at which to integrate over.
-We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.
+We have no angular resolution function since the angle resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.
 The data is from the 86 string sterile analysis~\cite{IC2020}.
-\begin{figure}[!tb]
-    \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
-    \end{center}
-    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}.
-Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
- \end{figure}
 
@@
    \end{center}
-   \caption{Expected pulls of predicted event numbers for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.05$
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.05$
     to the standard interaction count}\label{fig:event_pulls} 
@@
     %also, consider normalizing color scheme to one single for both.
+    %remove cos>0.
 \end{figure}
@@
 The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
-
+% Make clear distinction of different sigma syst here.
 For IceCube, the event count takes the form
@@
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
-confidence levels and best-fit points in Table.~\ref{table:DC_PINGU_results}.
+confidence levels in Table.~\ref{table:DC_PINGU_results} and best-fit points in Table ~\ref{table:bestfit}.
 
@@
  \end{figure}
-
+%TODO:explain emt assymetry. dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
+%TODO: ploit contour for ett-emt
  \begin{table}
    \begin{center}
-   \begin{tabular}{lcccc}
-           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
-           \cline { 3 - 5 } Parameter & 90\% CL\hspace{1cm} & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+   \begin{tabular}{lcc}
+           \hline \hline \\
+           Parameter & 90\% CL\hspace{1cm} & $3\sigma$  \\
            \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
-           $\ett$ & -0.028, 0.044\hspace{1cm} & 2.435 & 47.84 & 0.0125 \\
-           $\emt$ & -0.015, 0.0050\hspace{1cm} & 2.435 & 43.97 & -0.005 \\
-           $\eem$ & -0.068, 0.070\hspace{1cm} & 2.435 & 43.97 & 0 \\
-           $\eet$ & -0.072, 0.14\hspace{1cm} & 2.435 & 43.97  & 0.05 \\\\
+           $\ett$ & [-0.028, 0.044]\hspace{1cm} & \\
+           $\emt$ & [-0.015, 0.0050]\hspace{1cm} & \\
+           $\eem$ & [-0.068, 0.070]\hspace{1cm} & \\
+           $\eet$ & [-0.072, 0.14]\hspace{1cm} & \\\\
            \multicolumn{3}{c} {\hspace{2.5cm} PINGU } \\
-           $\ett$ & -0.036, -\hspace{1cm} & 2.517 & 49.2 & 0 \\
-           $\emt$ & -0.0076, 0.0085\hspace{1cm} & 2.517 & 49.2 & 0\\
-           $\eem$ & -0.060, 0.055\hspace{1cm} & 2.517 & 49.2 & 0 \\
-           $\eet$ & -0.065, 0.072\hspace{1cm} & 2.517 & 49.2 & 0 \\
+           $\ett$ & [-0.036, -]\hspace{1cm} & \\
+           $\emt$ & [-0.0076, 0.0085]\hspace{1cm} & \\
+           $\eem$ & [-0.060, 0.055]\hspace{1cm} &  \\
+           $\eet$ & [-0.065, 0.072]\hspace{1cm} &  \\\\
+           \multicolumn{3}{c} {\hspace{2.5cm} DeepCore + PINGU } \\
+           $\ett$ & [-0.029, 0.0473]\hspace{1cm} & \\
+           $\emt$ & [-0.0063, 0.0050]\hspace{1cm} & \\
+           $\eem$ & [-0.046, 0.046] \hspace{1cm} & \\
+           $\eet$ & [-0.057, 0.028] \hspace{1cm} &  \\
            \hline
@@
    \end{center}
-   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
-   degrees, respectively.}\label{table:DC_PINGU_results}
+   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
 \end{table}
 
+\begin{table}
+   \begin{center}
+   \begin{tabular}{lccc}
+           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
+           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
+           $\ett$ &  2.435 & 47.84 & 0.0125 \\
+           $\emt$ &  2.435 & 43.97 & -0.005 \\
+           $\eem$ &  2.435 & 43.97 & 0 \\
+           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
+           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
+           $\emt$ &  - & - & - \\
+           \hline
+           \hline
+   \end{tabular}
+   \end{center}
+   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   degrees, respectively.}\label{table:bestfit}
+\end{table}
+%TODO:  include ranges for different f.
+%make log table with secyions of dc, p, ic, dc+p
 Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
@@
 \end{align}
-with test statistic $\chi^2_\text{joint,min}$. The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Table~\ref{table:joint_results}.
+with test statistic $\chi^2_\text{joint,min}$. The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Table~\ref{table:DC_PINGU_results}.
 
@@
  \end{figure}
-
- \begin{table}
-   \begin{center}
-   \begin{tabular}{lcccc}
-           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
-           \cline { 3 - 5 } Parameter & 90\% CL\hspace{1cm} & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
-           \hline
-           $\ett$ & -0.029, 0.0473\hspace{1cm} & 2.489 & 47.84 & 0.0125\\
-           $\emt$ & -0.0063, 0.0050\hspace{1cm} & 2.489 & 47.84 & 0\\
-           $\eem$ & -0.046, 0.046 \hspace{1cm} & 2.489 & 47.84 & 0 \\
-           $\eet$ & -0.057, 0.028 \hspace{1cm} & 2.489 & 47.84 & 0 \\
-           \hline
-   \end{tabular}
-   \end{center}
-   \caption{Joint results from $\chi^2_\text{joint}$ defined in Eq.~\ref{eq:joint_chisq}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
-   degrees, respectively}
-   \label{table:joint_results}
-\end{table}
+%TODO: make 2x2. lines are too hin, colors are ugly. use spline smoothing.
 
 %TODO:  Discussion on impact of IC on chisq.?
+
+%TODO: subsection about comparison between different papers. 
+\bibliographystyle{elsarticle-num}
+\bibliography{article}
 
@@
 \end{tabular}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{article}
 \end{document}

### 2021-05-07 src/events/make_events.py

@@ -85,5 +85,5 @@ if __name__ == '__main__':
     if args.IC:
         data = [(i,j,0.99, 13,p, [False, 0, 0],False, True,3) for p in param_list for i in range(13) for j in range(20)]
         H1_events_list = process_map(precompute_probs, data,chunksize=20)
-        H1_events_list = H1_events_list.reshape(len(param_list),13,20)
+        H1_events_list = np.array(H1_events_list).reshape(len(param_list),13,20)
         pickle.dump(H1_events_list,open(f'./pre_computed/H1_{ordering}_IC_N13_{len(dm31_range)}x{len(th23_range)}x{len(emt_range)}.p','wb'))

### 2021-05-10 article/article.tex
update

@@
    \begin{center}
-      \begin{subfigure}{0.49\textwidth}
-         \includegraphics[width=1\textwidth]{figures/PINGU_event_pulls.pdf}
-         \caption{PINGU}\label{fig:PINGU_event_pulls}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-         \includegraphics[width=1\textwidth]{figures/DC_event_pulls.pdf}
-         \caption{DeepCore}\label{fig:DC_event_pulls}
-      \end{subfigure}
+         \includegraphics[width=0.9\textwidth]{figures/event_pulls.pdf}
    \end{center}
-   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.05$
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
     to the standard interaction count}\label{fig:event_pulls} 
-    %TODO: remake these with clearer titles and better labels, and reduce spacing between casc/tracks
-    %also, consider normalizing color scheme to one single for both.
-    %remove cos>0.
 \end{figure}
@@
            \hline \hline \\
-           Parameter & 90\% CL\hspace{1cm} & $3\sigma$  \\
-           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
-           $\ett$ & [-0.028, 0.044]\hspace{1cm} & \\
-           $\emt$ & [-0.015, 0.0050]\hspace{1cm} & \\
-           $\eem$ & [-0.068, 0.070]\hspace{1cm} & \\
-           $\eet$ & [-0.072, 0.14]\hspace{1cm} & \\\\
-           \multicolumn{3}{c} {\hspace{2.5cm} PINGU } \\
-           $\ett$ & [-0.036, -]\hspace{1cm} & \\
-           $\emt$ & [-0.0076, 0.0085]\hspace{1cm} & \\
-           $\eem$ & [-0.060, 0.055]\hspace{1cm} &  \\
-           $\eet$ & [-0.065, 0.072]\hspace{1cm} &  \\\\
-           \multicolumn{3}{c} {\hspace{2.5cm} DeepCore + PINGU } \\
-           $\ett$ & [-0.029, 0.0473]\hspace{1cm} & \\
-           $\emt$ & [-0.0063, 0.0050]\hspace{1cm} & \\
-           $\eem$ & [-0.046, 0.046] \hspace{1cm} & \\
-           $\eet$ & [-0.057, 0.028] \hspace{1cm} &  \\
+           Parameter & 90\% CL & $3\sigma$  \\
+           \hline \multicolumn{3}{c} {\hspace{1.5cm} DeepCore }  \\[0.1em]
+           $\ett$ & [-0.029, 0.044]\hspace{1cm} & [-, -] \\
+           $\emt$ & [-0.015, 0.005]\hspace{1cm} & [-, 0.015] \\
+           $\eem$ & [-0.072, 0.075]\hspace{1cm} & [-0.132, 0.127]\\
+           $\eet$ & [-0.074, 0.141]\hspace{1cm} & [-0.174, 0.2  ]\\\\
+           \multicolumn{3}{c} {\hspace{1.5cm} PINGU } \\
+           $\ett$ & [-0.033, -]\hspace{1cm} & [-0.048, -] \\
+           $\emt$ & [-0.007, 0.007]\hspace{1cm} & [-0.011, 0.013] \\
+           $\eem$ & [-0.062, 0.057]\hspace{1cm} & [-0.122, 0.103] \\
+           $\eet$ & [-0.069, 0.077]\hspace{1cm} & [-0.121, 0.133] \\\\
+           \multicolumn{3}{c} {\hspace{1.5cm} DeepCore + PINGU } \\
+           $\ett$ & [-0.028, 0.043]\hspace{1cm} & [-0.043, -]\\
+           $\emt$ & [-0.007, 0.005]\hspace{1cm} & [-0.011, 0.01] \\
+           $\eem$ & [-0.048, 0.048] \hspace{1cm} & [-0.09, 0.085]\\
+           $\eet$ & [-0.054, 0.072] \hspace{1cm} & [-0.101, 0.118] \\
            \hline
@@
  \end{figure}
-%TODO: make 2x2. lines are too hin, colors are ugly. use spline smoothing.
 

### 2021-05-11 article/article.tex
update

@@
 energy-independent but zenith-sensetive IceCube deficiency.
-
+%TODO: check values above after final plot of flux ratios
 For the fluxes which drives cascades, we have to resort to the DeepCore detector alone. %TODO: fill more
@@
    \end{center}
-   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. We set $\emt = -0.05$, and all other NSI parameters to zero. 
-   Dotted (dashed) lines show the regions in which 99\% of the 
-   DeepCore (IceCube) MC events are contained. \emph{Left panel:} Propagated fluxes of $\ne$ and $\nt$ neutrinos and anti-neutrinos. 
-   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale and fix limits
-\end{figure}% smaller emt and no log. clarify that IC is missing in left panel. clarify
-%that energy region within dotted line, use as few words as possible. Normalize color scale. check green-yellow cmap
+   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
+   Within the dotted (dashed) lines, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
+   a dashed region is omitted in the left panel.}
+\end{figure}%Done, run code in nsi.ipynb. need high emt and log to show both cascade and track features at the same time.
+%otherwise, the cascade ratio overpowers the track one.
 
@@
 \end{align}
-As seen in Fig.~\ref{fig:IC_MC_counts}, the energy reconstruction is biased.
+However, the energy reconstruction is biased~\cite{weaverEvidenceAstrophysicalMuon}, which means that we don't make the assumption that $\mu(E^t) =E^r$.
 To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
@@
 We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
-assuming standard (non-standard) interactions in Fig.~\ref{fig:DC_event_pulls}. This gives the normalized difference in the
+assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
 number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
-
-\begin{figure}[t]
-   \begin{center}
-         \includegraphics[width=0.9\textwidth]{figures/event_pulls.pdf}
-   \end{center}
-   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
-    to the standard interaction count}\label{fig:event_pulls} 
-\end{figure}
 
@@
 $\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. Just as with DeepCore, 
-we plot the events pulls for cascades and tracks in Fig.~\ref{fig:PINGU_event_pulls}. %TODO:talk about this
+we plot the events pulls for cascades and tracks in Fig.~\ref{fig:event_pulls}. %TODO:talk about this
 We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
@@
    \begin{center}
-      \begin{subfigure}{0.4\textwidth}
-         \includegraphics[width=1\linewidth]{figures/PINGU_3D_NO.pdf}
-         \caption{PINGU}\label{fig:PINGU_3D_NO}
+      \begin{subfigure}{0.45\textwidth}
+         \includegraphics[width=1\linewidth]{figures/joint_3D_NO.pdf}
+         \caption{Normal ordering}\label{fig:joint_3D}
       \end{subfigure}
-      \hspace{1cm}
+      \hspace{0cm}
       \begin{subfigure}{0.4\textwidth}
@@
     \end{center}
-    \caption{Minimization of the $\Delta \chi^2$ defined in Eq.~\ref{eq:chisq} after three years of data.
+    \caption{Expected $\Delta \chi^2$ after three years of data.
     $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
@@
 with test statistic $\chi^2_\text{joint,min}$. The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Table~\ref{table:DC_PINGU_results}.
+\newpage
 
@@
    \begin{center}
-       \includegraphics[width=0.9\linewidth]{figures/joint_3D_NO.pdf}
+      \begin{subfigure}{0.38\textwidth}
+         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
+         \caption{PINGU}\label{fig:PINGU_event_pulls}
+      \end{subfigure}
+      \begin{subfigure}{0.4\textwidth}
+         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
+         \caption{DeepCore}\label{fig:DC_event_pulls}
+      \end{subfigure}
     \end{center}
-    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
-    \label{fig:joint_3D}
- \end{figure}
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
+    to the standard interaction count}\label{fig:event_pulls} 
+\end{figure}%TODO: redo these with same emt as flux_ratio?
 
+% \begin{figure}[b]
+%    \begin{center}
+%       \includegraphics[width=0.2\linewidth]{figures/joint_3D_NO.pdf}
+%    \end{center}
+%    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
+%    \label{fig:joint_3D}
+% \end{figure}
 %TODO:  Discussion on impact of IC on chisq.?

### 2021-05-11 src/events/DC/event_processing.py

@@ -122,7 +122,11 @@ def list_of_params_nsi(dicta, dm31_range, th23_range, ett_range, emt_range, eem_
     dict_list = [update_dict(dicta,{'e_em':eem,'e_et':eet,'e_tt':tt,'e_mt':mt,'theta_23':th23, 'dm_31':dm31}) for eet in eet_range for eem in eem_range for mt in emt_range for tt in ett_range for th23 in th23_range for dm31 in dm31_range]
     return dict_list
 
-def get_param_list(dm31N,th23N, ett, ettN, emt, emtN, eem, eemN, eet, eetN, IO=False):
+def get_param_list(dm31N,th23N, ett_tuple, emt_tuple, eem_tuple, eet_tuple, IO=False):
+    ettFrom, ettTo, ettN = ett_tuple
+    emtFrom, emtTo, emtN = emt_tuple
+    eemFrom, eemTo, eemN = eem_tuple
+    eetFrom, eetTo, eetN = eet_tuple
     if IO is False:
         dm31_range = np.linspace(2.435e-3,2.598e-3,dm31N-1)
         th23_range = np.linspace(40.1*np.pi/180,51.7*np.pi/180,th23N-1)
@@ -130,11 +134,11 @@ def get_param_list(dm31N,th23N, ett, ettN, emt, emtN, eem, eemN, eet, eetN, IO=F
         dm31_range = np.linspace(-2.581e-3 - 8.04e-5, -2.414e-3 + 8.04e-5, dm31N-1)
         th23_range = np.linspace(40.3*np.pi/180, 51.8*np.pi/180, th23N-1)
     
-    ett_range = np.linspace(-ett,ett,ettN-1)
-    emt_range = np.linspace(-emt,emt,emtN-1)
+    ett_range = np.linspace(ettFrom,ettTo,ettN-1)
+    emt_range = np.linspace(emtFrom,emtTo,emtN-1)
 
-    eem_range = np.linspace(-eem,eem,eemN-1)
-    eet_range = np.linspace(-eet,eet,eetN-1)
+    eem_range = np.linspace(eemFrom,eemTo,eemN-1)
+    eet_range = np.linspace(eetFrom,eetTo,eetN-1)
 
     
     if IO:

### 2021-05-11 src/events/make_events.py

@@ -15,14 +15,18 @@ parser = argparse.ArgumentParser()
 parser.add_argument('-dm31N', default=1, type=int)
 parser.add_argument('-th23N', default=1, type=int)
 
-parser.add_argument('-ett', default=5e-2, type=float)
+parser.add_argument('-ettFrom', default=-7e-2, type=float)
+parser.add_argument('-ettTo', default=7e-2, type=float)
 parser.add_argument('-ettN', default=1, type=int)
-parser.add_argument('-emt', default=2e-2, type=float)
+parser.add_argument('-emtFrom', default=-2e-2, type=float)
+parser.add_argument('-emtTo', default=2e-2, type=float)
 parser.add_argument('-emtN', default=1, type=int)
 
-parser.add_argument('-eem', default=2e-1, type=float)
+parser.add_argument('-eemFrom', default=-2.5e-1, type=float)
+parser.add_argument('-eemTo', default=2.5e-1, type=float)
 parser.add_argument('-eemN', default=1, type=int)
-parser.add_argument('-eet', default=2e-1, type=float)
+parser.add_argument('-eetFrom', default=-2.5e-1, type=float)
+parser.add_argument('-eetTo', default=2.5e-1, type=float)
 parser.add_argument('-eetN', default=1, type=int)
 
 parser.add_argument('-s', default = 0, type=int)
@@ -51,10 +55,10 @@ def precompute_probs(args_tuple):
 if __name__ == '__main__':
     assert args.PINGU or args.DC or args.IC
     dm31_range, th23_range,ett_range, emt_range, eem_range, eet_range = get_param_list(args.dm31N, args.th23N, 
-                                                                                       args.ett, args.ettN, 
-                                                                                       args.emt, args.emtN, 
-                                                                                       args.eem, args.eemN, 
-                                                                                       args.eet, args.eetN, 
+                                                                                       (args.ettFrom, args.ettTo, args.ettN), 
+                                                                                       (args.emtFrom, args.emtTo,args.emtN), 
+                                                                                       (args.eemFrom, args.eemTo,args.eemN), 
+                                                                                       (args.eetFrom, args.eetTo,args.eetN), 
                                                                                        args.IO)
     print('dm:', dm31_range)
     print('th:', th23_range)

### 2021-05-11 article/article.tex
update

@@
    \begin{center}
-      \includegraphics[width=0.35\linewidth]{figures/cascade_flux_ratio.pdf}
-      \hspace{1.5cm}
-      \includegraphics[width=0.35\linewidth]{figures/track_flux_ratio.pdf}
+      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
    \end{center}
@@
    a dashed region is omitted in the left panel.}
-\end{figure}%Done, run code in nsi.ipynb. need high emt and log to show both cascade and track features at the same time.
+\end{figure}%TODO:redo with more than 100x100. need high emt and log to show both cascade and track features at the same time.
 %otherwise, the cascade ratio overpowers the track one.
@@
       \end{subfigure}
-      \hspace{0cm}
-      \begin{subfigure}{0.4\textwidth}
-         \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
-         \caption{DeepCore}\label{fig:DC_3D_NO}
-      \end{subfigure}
     \end{center}
@@
  \end{figure}
-%TODO:explain emt assymetry. dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
+%TODO: dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
+
+% \begin{figure}[!tb]%TODO: redo this with P+/P-
+% \begin{center}
+%    \includegraphics[width=0.7\linewidth]{figures/Pmm_asymmetry.pdf}
+% \end{center}
+% \caption{Expected $\Delta \chi^2$ after three years of data.
+%    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+%    parameters other than the one shown in each panel are fixed to zero.}\label{fig:Pmm_asymmetry}
+% \end{figure}
+
+We can explain the asymmetry by looking looking at the oscillogram of the ratio $P(\emt^-)/P(\emt^+)$ in Fig.~\ref{fig:Pmm_asymmetry}, which is the $P_{\mu\mu}$ survival probability
+given $\emt =-0.05$ divided by $P_{\mu\mu}$ for $\emt=0.05$. Muon events are the most abundant in IceCube and DeepCore/PINGU, and it suffices to study
+$P_{\mu\mu}$ to explain the asymmetry. We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (pink area),
+while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in the flux ratio plot, this muon survival abundance 
+is indeed preserved at flux level.
+
+\begin{figure}[!tb]
+   \begin{center}
+      \includegraphics[width=0.5\linewidth]{figures/emt_events.pdf}
+   \end{center}
+   \caption{The best-fit event count ratio at each detector for negative and positive $\emt$. PINGU shows promising 
+   of distinguishing the sign of $\emt$, but favoring $\emt < 0$ while DeepCore has higher statistics for $\emt>0$ and a poor
+   distinction for $\emt<0$}\label{fig:emt_events}%TODO: improve caption?
+ \end{figure}
+As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event count for $\emt=-0.02$ outnumber the event count with $\emt =0.05$ for
+all bins except one, giving a high $\Delta \chi^2$ on both sides and slightly higher for $\emt=-0.02$. DeepCore on the other hand, 
+has no bins where the event count for $\emt=-0.02$ surpasses the event count for $\emt=+0.02$, giving weak statistics for the negative side.
+
 %TODO: ploit contour for ett-emt

### 2021-05-11 article/notebooks/nsi.py
update

@@ -1,0 +1,79 @@
+import sys,os
+os.chdir('../../')
+sys.path.append('./src/data')
+sys.path.append('./src/events')
+sys.path.append('./src/probability')
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+import pandas as pd
+from subprocess import call
+from IC.importer import *
+from IC.processer import *
+from IC.main import sim_events, list_of_params
+from functions import nufit_params_nsi
+from plotter import P_over_E_parameter, nsi_oscillogram, nsi_flux_oscillogram
+from scipy.stats import chi2
+from IC.event_processing import *
+import pickle
+from matplotlib.colors import CenteredNorm
+from multiprocessing import Pool
+from plotter import save, savethesis
+plt.rcParams['figure.figsize'] = [8, 4]
+plt.rcParams['figure.dpi'] = 100
+matplotlib.rc('text', usetex=True)
+matplotlib.rc('text.latex', preamble=r'\usepackage{amsmath}')
+np.set_printoptions(linewidth=200)
+
+IC_range = np.logspace(np.log10(500),4,50)
+DC_range = np.logspace(np.log10(5.6),np.log10(56),50)
+#ett_range = [-0.1,0,0.1]#np.linspace(-1e-1,1e-1,3)
+emm_range = [-1e-1,0,1e-1]#np.linspace(-1e-1,1e-1,3)
+emt_range = [-5e-2,0,5e-2]
+params = nufit_params_nsi.copy()
+anti=True
+s24_range = [0.032]
+params.update({'theta_24': np.arcsin(np.sqrt(0.032))/2, 'dm_41':0.93, 'theta_34': np.arcsin(np.sqrt(0))/2})
+emm_params = list_of_params_nsi(params, s24_range, emm_range)
+emt_params = list_of_params_nsi(params, s24_range, [0],emt_range)
+both_params = list_of_params_nsi(params, s24_range, emm_range,emt_range)
+zenith = -1
+
+z_range = np.linspace(-1,0,500)
+all_range = np.logspace(np.log10(1),5.1,500)
+#P_emm_IC = np.array(nsi_oscillogram(IC_range, z_range, emm_params[0]))
[…]

### 2021-05-14 article/article.tex
update

@@
 %TODO: nsi intro, clear about factor 3
+\section{Formalism}
+\begin{align}
+   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
+\end{align}
+NC denotes the neutral current interaction with 
+$f \in \{e,u,d\}$.
+
+For chirality $X \in \{L,R\}$, the NSI Hamiltonian takes the form 
+\begin{align}
+   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}
+\end{align}
+
+We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these and normalize the fermion number density $n_f$ by
+the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
+so $n_u/n_e \simeq n_d/n_e \simeq 3$.
+The effective matter NSI parameters now take the form
+\begin{align} \label{eq:epsilon}
+    \epsilon_{\alpha\beta} &= \sum_X \sum_f \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
+                           &= \epsilon_{\alpha\beta}^{eV} + 3\epsilon_{\alpha\beta}^{uV} + 3\epsilon_{\alpha\beta}^{dV}
+\end{align}
+We note that our definition of $\epsilon_{\alpha\beta}$ differs from some texts, where the quark number density is used to normalize
+the parameters\cite{deepcoreNSI}.
+
+With the matter potential $V = \sqrt{2}G_F n_e$, we write
+\begin{align} \label{eq:H_NSI}
+   H &= \frac{1}{2E} UM^2U^\dagger + V\,
+   \begin{bmatrix}
+      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
+      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
+      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
+  \end{bmatrix}\,,
+\end{align}
+where we have assumed the components of the NSI matrix to be real.
+
 \section{Detector formalism}
@@
 Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. %TODO: add more here? no neutrino absorption
+production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
+%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?
 
@@
 \subsection{IceCube}\label{ch:ICmethod}
-The event rate for each bin reads
+We obtain the data from the IC-86 sterile data release~\cite{IC2020}. The event rate for each bin reads
 \begin{align}\label{eq:ICevents}
@@
 the limits of $\Etrue$ at which to integrate over.
-We have no angular resolution function since the angle resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.
-The data is from the 86 string sterile analysis~\cite{IC2020}.
+We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.
 
@@
 
-We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
-assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
-number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
+We plot the normalized event difference $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
+assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.
 
@@
 %Short intro
-\subsection{Methodology}
+\subsection{Methodology}\label{sec:method}
 For our analyses, we define our $\chi^2$ as
@@
 The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
-% Make clear distinction of different sigma syst here.
 For IceCube, the event count takes the form
@@
 Since the median zenith is $\zreco = 0$ for DeepCore and PINGU, we allow the event count to rotate around zero.
-For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. %TODO: and take ... %.
-For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
+
+We treat the uncorrelated systematic uncertanties differently for each detector.
+For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+We consider (best) worst-case scenarios in IceCube assuming
+$(f=5\%)$, $f=15\%$. For PINGU, we use the same form but instead assume $f=0\%$ and $f=5\%$ for the best and worst-cases respecively. %TODO: maybe source/justification for these values?
+For DeepCore, we use the provided systematic error distribution which accounts for uncertanties in the finite MC statistics and in the data-driven 
 muon background estimate~\cite{DC2019data}.  %TODO segue
@@
 %TODO: ploit contour for ett-emt
+{\renewcommand{\arraystretch}{1.3}
  \begin{table}
    \begin{center}
-   \begin{tabular}{lcc}
+   \begin{tabular}{lcccc}
       \hline \hline \\
-           Parameter & 90\% CL & $3\sigma$  \\
-           \hline \multicolumn{3}{c} {\hspace{1.5cm} DeepCore }  \\[0.1em]
-           $\ett$ & [-0.029, 0.044]\hspace{1cm} & [-, -] \\
-           $\emt$ & [-0.015, 0.005]\hspace{1cm} & [-, 0.015] \\
-           $\eem$ & [-0.072, 0.075]\hspace{1cm} & [-0.132, 0.127]\\
-           $\eet$ & [-0.074, 0.141]\hspace{1cm} & [-0.174, 0.2  ]\\\\
-           \multicolumn{3}{c} {\hspace{1.5cm} PINGU } \\
-           $\ett$ & [-0.033, -]\hspace{1cm} & [-0.048, -] \\
-           $\emt$ & [-0.007, 0.007]\hspace{1cm} & [-0.011, 0.013] \\
-           $\eem$ & [-0.062, 0.057]\hspace{1cm} & [-0.122, 0.103] \\
-           $\eet$ & [-0.069, 0.077]\hspace{1cm} & [-0.121, 0.133] \\\\
-           \multicolumn{3}{c} {\hspace{1.5cm} DeepCore + PINGU } \\
-           $\ett$ & [-0.028, 0.043]\hspace{1cm} & [-0.043, -]\\
-           $\emt$ & [-0.007, 0.005]\hspace{1cm} & [-0.011, 0.01] \\
-           $\eem$ & [-0.048, 0.048] \hspace{1cm} & [-0.09, 0.085]\\
-           $\eet$ & [-0.054, 0.072] \hspace{1cm} & [-0.101, 0.118] \\
+      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{4}{c}{IceCube}  \\
+      $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
+      & \multicolumn{4}{c}{DeepCore}  \\[0.3em]
+      $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
+      $\emt$ & [-0.015, 0.0048] & [-, 0.015]& [-0.015, 0.0048] & [-, 0.015] \\
+      $\eem$ & [-0.072, 0.075] & [-0.132, 0.127]& [-0.072, 0.075] & [-0.132, 0.127]\\
+      $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
+      &\multicolumn{4}{c}{IceCube + DeepCore}  \\
+      $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
       \hline
@@
    \end{center}
-   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
+   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
+   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:IC_DC_results}
+\end{table}
+\begin{table}
+   \begin{tabular}{lcccc}
+      \hline \hline \\
+      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{4}{c}{PINGU} \\
+      $\ett$ & [-0.0326, -] & [-0.0482, ] & [-0.0371, -] & [-, -] \\
+      $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
+      $\eem$ & [-0.062, 0.057] & [-0.122, 0.103] & [-0.1057, 0.0799] & [-0.198, 0.141]\\
+      $\eet$ & [-0.069, 0.077] & [-0.121, 0.133] & [-0.1072, 0.1022] & [-0.1805, 0.1633]\\\\
+      & \multicolumn{4}{c}{DeepCore + PINGU} \\
+      $\ett$ & [-0.028, 0.043] & [-0.043, -] & [-0.0285,  0.0423] & [-0.0447, -]\\
+      $\emt$ & [-0.0067, 0.0049] & [-0.0109,  0.0101] & [-0.0049, 0.0086] & [-0.0098, 0.0146]\\
+      $\eem$ & [-0.048, 0.048]  & [-0.090, 0.085] & [-0.0721, 0.0503] & [-0.1262, 0.0931]\\
+      $\eet$ & [-0.053, 0.072]  & [-0.101, 0.118] & [-0.0901, 0.0624] & [-0.1491, 0.1168]\\\\
+      & \multicolumn{4}{c}{IceCube + DeepCore + PINGU}  \\
+      $\emt$ & [-0.0088,  0.003 ] & [-0.0128, 0.0081] & [-0.01, 0.0028] & [-0.0145, 0.0087]\\
+      \hline
+      \hline
+   \end{tabular}
+   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
+   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:PINGU_joint_results}
 \end{table}
@@
            \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
-           $\emt$ &  - & - & - \\
+           $\emt$ &  2.435 & 51.70 & 0 \\
+           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
+           $\emt$ &  2.517 & 43.97 & -0.01 \\
            \hline
@@
 %TODO: subsection about comparison between different papers.
+
+\begin{figure}
+   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
+\end{figure}
+\begin{figure}
+   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f5.pdf}
+\end{figure}
 \bibliographystyle{elsarticle-num}

### 2021-05-14 thesis/tex/nsiTheory.tex
update

@@
 Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
-we get $N_u/N_e \simeq U_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
+we get $N_u/N_e \simeq N_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
 \begin{align}

### 2021-05-17 article/article.tex
update

@@
 \begin{document}
-%TODO: nsi intro, clear about factor 3
 \section{Formalism}
+Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions with 
+matter fermions not considered in the Standard Model. We consider matter NSIs arising from the neutral current NSIs, which exclude production 
+and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
 \begin{align}
@@
 \end{align}
-NC denotes the neutral current interaction with 
-$f \in \{e,u,d\}$.
+where NC denotes the neutral current interaction with 
+$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.
 
-For chirality $X \in \{L,R\}$, the NSI Hamiltonian takes the form 
+For chirality $X$, the NSI Hamiltonian takes the form 
 \begin{align}
@@
 
-We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these and normalize the fermion number density $n_f$ by
+We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these to obtain the vector part as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
+Moreover, we normalize the fermion number density $n_f$ by
 the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
-so $n_u/n_e \simeq n_d/n_e \simeq 3$.
-The effective matter NSI parameters now take the form
+so we use the relations $n_u/n_e \simeq n_d/n_e \simeq 3$.
+The effective NSI parameters in matter now take the form
 \begin{align} \label{eq:epsilon}
-    \epsilon_{\alpha\beta} &= \sum_X \sum_f \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
+    \epsilon_{\alpha\beta} &= \sum_{f,X} \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                            &= \epsilon_{\alpha\beta}^{eV} + 3\epsilon_{\alpha\beta}^{uV} + 3\epsilon_{\alpha\beta}^{dV}
@@
 where we have assumed the components of the NSI matrix to be real.
+To see the effect of a NSI, we have plotted a probability difference in the low energy range in Fig.~\ref{fig:Pmm_asymmetry}, and study
+the flux ratio in Fig.~\ref{fig:flux_ratio}.
 
@@
 where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
-and flux level, we plot the oscillograms resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
+and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
 DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
@@
 
-\begin{figure}[!tb]
+\begin{figure}[!tb]\label{fig:flux_ratio}
    \begin{center}
@@
    a dashed region is omitted in the left panel.}
-\end{figure}%TODO:redo with more than 100x100. need high emt and log to show both cascade and track features at the same time.
+\end{figure}% need high emt and log to show both cascade and track features at the same time.
 %otherwise, the cascade ratio overpowers the track one.
@@
 \section{Results}
-%Short intro
+In this section, we present the results from the experiments alone, as well as jointly. 
 \subsection{Methodology}\label{sec:method}
@@
 The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
-Since the median zenith is $\zreco = 0$ for DeepCore and PINGU, we allow the event count to rotate around zero.
+For DeepCore and PINGU, the median zenith angle is $\zreco = 0$, we allow the event count to rotate around this point.
 
@@
 For DeepCore, we use the provided systematic error distribution which accounts for uncertanties in the finite MC statistics and in the data-driven 
-muon background estimate~\cite{DC2019data}.  %TODO segue
+muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
+{\renewcommand{\arraystretch}{1.2}
+\begin{table}
+   \begin{tabular}{lcc}
+      \hline \hline
+      Experiment & Worst case & Best case \\
+      \hline
+      IceCube & $15\%$ & $5\%$ \\
+      DeepCore & - & - \\
+      PINGU & $5\%$ & $0\%$ \\
+      \hline \hline
+   \end{tabular}
+   \caption{Definition of the worst and best case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
+   We do not consider different DeepCore scenarios because the systematic error distribution there is already given in the data release~\cite{DC2019data}.}\label{table:syst_errors}
+\end{table}
 
@@
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
-confidence levels in Table.~\ref{table:DC_PINGU_results} and best-fit points in Table ~\ref{table:bestfit}.
+confidence levels in Table.~\ref{table:IC_DC_results} for DeepCore and IceCube, and best-fit points in Table ~\ref{table:bestfit}.
 
@@
 
-% \begin{figure}[!tb]%TODO: redo this with P+/P-
-% \begin{center}
-%    \includegraphics[width=0.7\linewidth]{figures/Pmm_asymmetry.pdf}
-% \end{center}
-% \caption{Expected $\Delta \chi^2$ after three years of data.
-%    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-%    parameters other than the one shown in each panel are fixed to zero.}\label{fig:Pmm_asymmetry}
-% \end{figure}
-
-We can explain the asymmetry by looking looking at the oscillogram of the ratio $P(\emt^-)/P(\emt^+)$ in Fig.~\ref{fig:Pmm_asymmetry}, which is the $P_{\mu\mu}$ survival probability
-given $\emt =-0.05$ divided by $P_{\mu\mu}$ for $\emt=0.05$. Muon events are the most abundant in IceCube and DeepCore/PINGU, and it suffices to study
-$P_{\mu\mu}$ to explain the asymmetry. We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (pink area),
-while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in the flux ratio plot, this muon survival abundance 
+To see the effect of a NSI at probability level, we plot the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
+$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}.
+We can explain the asymmetry in  by looking looking at the oscillogram.
+Muon events are the most abundant DeepCore/PINGU, and it suffices to study $P_{\mu\mu}$ to explain the asymmetry.
+We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
+while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratios}, this muon survival abundance 
 is indeed preserved at flux level.
@@
 \begin{center}
-      \includegraphics[width=0.5\linewidth]{figures/emt_events.pdf}
+   \includegraphics[width=0.4\linewidth]{figures/Pmm_asymmetry.pdf}
 \end{center}
-   \caption{The best-fit event count ratio at each detector for negative and positive $\emt$. PINGU shows promising 
-   of distinguishing the sign of $\emt$, but favoring $\emt < 0$ while DeepCore has higher statistics for $\emt>0$ and a poor
-   distinction for $\emt<0$}\label{fig:emt_events}%TODO: improve caption?
+\caption{The ratio $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.05$ in the DeepCore/PINGU energy range.
+Negative $\emt$ has the strongest signal, as the thin blue
+region stemming from $\emt = 0.05$ is less prominent than the red regions from $\emt=-0.05$.}\label{fig:Pmm_asymmetry}
 \end{figure}
-As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event count for $\emt=-0.02$ outnumber the event count with $\emt =0.05$ for
-all bins except one, giving a high $\Delta \chi^2$ on both sides and slightly higher for $\emt=-0.02$. DeepCore on the other hand, 
-has no bins where the event count for $\emt=-0.02$ surpasses the event count for $\emt=+0.02$, giving weak statistics for the negative side.
+\begin{figure}[!tb]
+   \begin{center}
+      \includegraphics[width=0.4\linewidth]{figures/emt_events.pdf}
+   \end{center}
+   \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$.}\label{fig:emt_events}%TODO: improve caption?
+ \end{figure}
+As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$.
+DeepCore on the other hand,
+has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side.
+
+Comparing Fig.~\ref{fig:emt_events} with the flux ratios in Fig.~\ref{fig:flux_ratio}, we see that the reconstruction of PINGU is
+superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})}$ (which is in reconstructed quantities) more closely matches the flux ratio $\log{(\phi_{NSI}/\phi_{SI})}$ (which is in true quantities).
+This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes.
 
@@
    \begin{tabular}{lcccc}
-      \hline \hline \\
+      \hline \hline
       Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
@@
    \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
-   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:IC_DC_results}
+   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}}\label{table:IC_DC_results}
 \end{table}
@@
    \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
-   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:PINGU_joint_results}
+   the systematic uncertainty scenarios considered as in Table.~\ref{table:syst_errors}}\label{table:PINGU_joint_results}
 \end{table}
@@
 \end{table}
-%TODO:  include ranges for different f.
-%make log table with secyions of dc, p, ic, dc+p
 Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 

### 2021-05-17 article/article.tex
update

@@
 \section{Formalism}
-Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions with 
-matter fermions not considered in the Standard Model. We consider matter NSIs arising from the neutral current NSIs, which exclude production 
+Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
+We consider matter NSIs arising from the neutral current NSIs, which exclude production 
 and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
@@
 
-We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these to obtain the vector part as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
+We have no independent sensitivity for the chirality of $\epsilon^{fX}$, so we sum over these to obtain the vectorial parameter as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
 Moreover, we normalize the fermion number density $n_f$ by
@@
 \end{align}
-where we have assumed the components of the NSI matrix to be real.
-To see the effect of a NSI, we have plotted a probability difference in the low energy range in Fig.~\ref{fig:Pmm_asymmetry}, and study
-the flux ratio in Fig.~\ref{fig:flux_ratio}.
+where we have assumed the components of the NSI matrix to be real. In Fig.~\ref{fig:flux_ratio}, we study
+the flux ratio arising from the introduction of the NSI parameter $\emt$.
+Fig.~\ref{fig:Pmm_asymmetry} shows the difference $P_{\mu\mu}(\emt>0) - P_{\mu\mu}(\emt<0)$ in the low \si{\GeV} energy range.
+%TODO: maybe plot P_NSI - P_SI instead.
 
 \section{Detector formalism}
-The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
+The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth by solving the 
 Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
@@
 
-The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux at detector level for flavor $\beta$ as 
+The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
 \begin{align}\label{eq:propFlux}
@@
 and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
-is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore on the other hand, 
-observes multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
+is a energy-independent flux deficiency with a factor of $\sim \sqrt{10}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
+is exposed to multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
 energy-independent but zenith-sensetive IceCube deficiency.
 %TODO: check values above after final plot of flux ratios
-For the fluxes which drives cascades, we have to resort to the DeepCore detector alone. %TODO: fill more
-Here we see a somewhat weaker signal, this time a zenith-independent deficiency. 
-%TODO: fill with conclusion
+In IceCube, we will only consier muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
+Here we see a somewhat weaker signal, this time a zenith-independent deficiency. Where we earlier had surpluses with a factor $\sim 10$, we now have deficienies in the order of $\sim \sqrt{10}$.
 
-\begin{figure}[!tb]\label{fig:flux_ratio}
+The muonic flux not only carries the largest $\emt$ effect, it is also more abundant than the $\ne$ flux. Thus, we expect to recieve highest statistics from $\mu$-related NSI parameters,
+thus constraining them the strongest. $\epsilon_{\alpha\beta}$ which are only indirectly weakly dependent on the $\mu$ channel will have the weakest bounds. This could be improved
+by considering cascade events in IceCube, thus opening up the $e$ and $\tau$ channels there.
+
+\begin{figure}[!tb]
    \begin{center}
@@
    \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
-   Within the dotted (dashed) lines, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
-   a dashed region is omitted in the left panel.}
+   Within the dotted (dashed) boundaries, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
+   a dashed region is omitted in the left panel.}\label{fig:flux_ratio}
 \end{figure}% need high emt and log to show both cascade and track features at the same time.
@@
 \subsection{IceCube}\label{ch:ICmethod}
-We obtain the data from the IC-86 sterile data release~\cite{IC2020}. The event rate for each bin reads
+We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which was collected over 8 years. The event rate for each bin reads
 \begin{align}\label{eq:ICevents}
-   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}  A^\text{eff} R(E^r,E^t)
+   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}(E^t,\theta^t)  A^\text{eff}(E^t) R(E^r,E^t)
    \dd E^t\,,
@@
 \end{align}
-However, the energy reconstruction is biased~\cite{weaverEvidenceAstrophysicalMuon}, which means that we don't make the assumption that $\mu(E^t) =E^r$.
-To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
+However, the energy reconstruction is biased, which means that we don't make the assumption that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
+To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo~\cite{IC2016}, from which
 we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
-the limits of $\Etrue$ at which to integrate over.
-We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.
+the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
+events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
 
 \subsection{DeepCore}\label{ch:DCmethod}
-In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
+We use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
 IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.
 
-The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
+The detector systematics include ice absorption and scattering, as well as overall, lateral, and head-on optical efficiencies of the DOMs. 
 They are applied as correction factors using the best-fit points from the DeepCore 2019 $\nu_\tau$ appearance 
@@
 The data include 14901 track-like events and 26001 cascade-like events, both divided into eight 
-$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{ijk,\beta}$,
+$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{ijk,\beta}$
 from which we can construct the event count as
@@
 best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\dm$ and $\theta_{23}$.
+marginalize over $\dm$ and $\theta_{23}$ between their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
 
@@
 assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.
+%TODO:conclusion from this?
 
@@
 The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}.
-We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
-As with the DeepCore data, the PINGU MC is divided into eight 
-$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. Just as with DeepCore, 
-we plot the events pulls for cascades and tracks in Fig.~\ref{fig:event_pulls}. %TODO:talk about this
+We use the public Monte Carlo~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error.
+As with the DeepCore Monte Carlo, the PINGU Monte Carlo is divided into eight 
+$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
+We plot the normalized event differences $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for cascades and tracks in Fig.~\ref{fig:event_pulls}. %TODO:talk about this
 We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
@@
    \caption{Definition of the worst and best case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
-   We do not consider different DeepCore scenarios because the systematic error distribution there is already given in the data release~\cite{DC2019data}.}\label{table:syst_errors}
+   We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
 \end{table}
@@
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
-confidence levels in Table.~\ref{table:IC_DC_results} for DeepCore and IceCube, and best-fit points in Table ~\ref{table:bestfit}.
+confidence levels in Table.~\ref{table:IC_DC_results}, and best-fit points in Table ~\ref{table:bestfit}.
 
@@
          \includegraphics[width=1\linewidth]{figures/joint_3D_NO.pdf}
-         \caption{Normal ordering}\label{fig:joint_3D}
+         \caption{PINGU and DeepCore best case scenario, with their joint $\Delta \chi^2$ in black.}\label{fig:joint_3D}
       \end{subfigure}
+      \begin{subfigure}{0.45\textwidth}
+         \vspace{1em}
+         \includegraphics[width=1\linewidth, height=0.32\textheight]{figures/PID_3D_emt.pdf}
+         \caption{\emph{Top panel:} IceCube $\emt$ result with two combinations of $\Delta \chi^2$.
+                  \emph{Bottom panel:} $\Delta \chi^2$ regions for best and worst case scenarios as defined in Table~\ref{table:syst_errors}.}\label{fig:IC_3D}
+      \end{subfigure}
+    \caption{Expected $\Delta \chi^2$ at PINGU, DeepCore, and IceCube.
+    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+    parameters other than the one shown in each panel are fixed to zero. IceCube tracks only reveal $\emt$, and are displayed separately in the right panel.}\label{fig:3D_NO}
    \end{center}
-    \caption{Expected $\Delta \chi^2$ after three years of data.
-    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than the one shown in each panel are fixed to zero.}\label{fig:3D_NO}
 \end{figure}
@@
 
-To see the effect of a NSI at probability level, we plot the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
-$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}.
-We can explain the asymmetry in  by looking looking at the oscillogram.
-Muon events are the most abundant DeepCore/PINGU, and it suffices to study $P_{\mu\mu}$ to explain the asymmetry.
+We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:joint_3D}, especially in $\emt$ and $\eet$.%TODO: make better
+We investigate this for $\emt$ by plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
+%TODO: check that this is what is plotted.
+$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
 We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
-while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratios}, this muon survival abundance 
-is indeed preserved at flux level.
+while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
+is indeed preserved at flux level. So the flux for $\emt>0$ is higher than the flux for $\emt<0$. Is this still true at event level, i-.e after reconstruction? 
+As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$.
+DeepCore on the other hand,
+has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
+$\emt$ asymmetry stems from the lower statistics for $\emt< 0 $ at probability level, which is then preserved through the flux and finally the reconstruction. %TODO: fill more conclusion?
 
 \begin{figure}[!tb]
-\begin{center}
    \includegraphics[width=0.4\linewidth]{figures/Pmm_asymmetry.pdf}
-\end{center}
    \caption{The ratio $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.05$ in the DeepCore/PINGU energy range.
@@
 region stemming from $\emt = 0.05$ is less prominent than the red regions from $\emt=-0.05$.}\label{fig:Pmm_asymmetry}
+\end{figure}%TODO: maybe plot P_nsi - p_si?
+\begin{figure}[!tb]
+   \includegraphics[width=0.7\linewidth]{figures/emt_events.pdf}
+   \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$. IceCube only observes a small surplus of events for $\emt=-0.01$ compared to 
+   DeepCore and PINGU due to the weak NSI effect at high \si{\GeV} energies.}\label{fig:emt_events}%TODO: improve caption?
  \end{figure}
-\begin{figure}[!tb]
-   \begin{center}
-      \includegraphics[width=0.4\linewidth]{figures/emt_events.pdf}
-   \end{center}
-   \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$.}\label{fig:emt_events}%TODO: improve caption?
- \end{figure}
-As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$.
-DeepCore on the other hand,
-has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side.
 
@@
 superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})}$ (which is in reconstructed quantities) more closely matches the flux ratio $\log{(\phi_{NSI}/\phi_{SI})}$ (which is in true quantities).
-This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes.
+This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes while PINGU still has the $N^-_{NSI}$ surplus below \SI{10}{\GeV}.
 
-%TODO: ploit contour for ett-emt
 {\renewcommand{\arraystretch}{1.3}
@@
       $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
-      & \multicolumn{4}{c}{DeepCore}  \\[0.3em]
+      & \multicolumn{4}{c}{DeepCore}\\ [0.3em]
       $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
@@
       $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
-      &\multicolumn{4}{c}{IceCube + DeepCore}  \\
+      &\multicolumn{4}{c}{IceCube + DeepCore}\\
       $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
@@
    \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
-   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}}\label{table:IC_DC_results}
+   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
 \end{table}
@@
    \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
-   the systematic uncertainty scenarios considered as in Table.~\ref{table:syst_errors}}\label{table:PINGU_joint_results}
+   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
 \end{table}
@@
 \end{table}
-Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
-the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
-the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in our joint analysis,
-since PINGU has stronger statistics than DeepCore, and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
+Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.
+This is because the `data' we generated during
+the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
 
-%TODO: segue to joint
 For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
 \begin{align}\label{eq:joint_chisq}
-    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
+    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
 \end{align}
-with test statistic $\chi^2_\text{joint,min}$. The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Table~\ref{table:DC_PINGU_results}.
+with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
+The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
 \newpage

### 2021-05-18 article/article.tex
update

@@
 is exposed to multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
-energy-independent but zenith-sensetive IceCube deficiency.
+energy-independent but zenith-sensitive IceCube deficiency.
 %TODO: check values above after final plot of flux ratios
-In IceCube, we will only consier muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
-Here we see a somewhat weaker signal, this time a zenith-independent deficiency. Where we earlier had surpluses with a factor $\sim 10$, we now have deficienies in the order of $\sim \sqrt{10}$.
+In IceCube, we will only consider muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
+Here we see a somewhat weaker signal, this time a zenith-independent deficiency. Where we earlier had surpluses with a factor $\sim 10$, we now have deficiencies in the order of $\sim \sqrt{10}$.
 
-The muonic flux not only carries the largest $\emt$ effect, it is also more abundant than the $\ne$ flux. Thus, we expect to recieve highest statistics from $\mu$-related NSI parameters,
+The muonic flux not only carries the largest $\emt$ effect, but it is also more abundant than the $\ne$ flux. Thus, we expect to receive the highest statistics from $\mu$-related NSI parameters,
 thus constraining them the strongest. $\epsilon_{\alpha\beta}$ which are only indirectly weakly dependent on the $\mu$ channel will have the weakest bounds. This could be improved
@@
    a dashed region is omitted in the left panel.}\label{fig:flux_ratio}
-\end{figure}% need high emt and log to show both cascade and track features at the same time.
+\end{figure}%TODO: fix cbar need high emt and log to show both cascade and track features at the same time.
 %otherwise, the cascade ratio overpowers the track one.
@@
 \end{align}
-However, the energy reconstruction is biased, which means that we don't make the assumption that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
+However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
 To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo~\cite{IC2016}, from which
@@
 
-We plot the normalized event difference $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
-assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.
+% We plot the normalized event difference $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
+% assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.
 %TODO:conclusion from this?
@@
 \subsection{PINGU}\label{ch:PINGUmethod}
-The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}.
-We use the public Monte Carlo~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error.
+The methodology behind the PINGU simulations is the same as with our DeepCore study~\ref{ch:DCmethod}. We use the public Monte Carlo~\cite{PINGUdata}, 
+which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+However, since no detector systematics is yet modeled for PINGU, the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error.
 As with the DeepCore Monte Carlo, the PINGU Monte Carlo is divided into eight 
@@
 with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
-The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
+The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
 For DeepCore and PINGU, the median zenith angle is $\zreco = 0$, we allow the event count to rotate around this point.
@@
 For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
-We consider (best) worst-case scenarios in IceCube assuming
-$(f=5\%)$, $f=15\%$. For PINGU, we use the same form but instead assume $f=0\%$ and $f=5\%$ for the best and worst-cases respecively. %TODO: maybe source/justification for these values?
-For DeepCore, we use the provided systematic error distribution which accounts for uncertanties in the finite MC statistics and in the data-driven 
+We consider best, normal, and worst-case scenarios in IceCube assuming
+$f=5\%$, $7.5\%$, and $f=15\%$ respectively. For PINGU, we use the same form but instead assume $f=0\%$, $3\%$, and $f=5\%$. %TODO: maybe source/justification for these values?
+For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
 muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
@@
 \begin{table}
-   \begin{tabular}{lcc}
+   \begin{tabular}{lccc}
       \hline \hline
-      Experiment & Worst case & Best case \\
+      Experiment & Worst case & Normal case & Best case \\
       \hline
-      IceCube & $15\%$ & $5\%$ \\
-      DeepCore & - & - \\
-      PINGU & $5\%$ & $0\%$ \\
+      IceCube & $15\%$ & $10\%$ & $5\%$ \\
+      PINGU & $5\%$ & $3\%$ & $0\%$ \\
       \hline \hline
@@
 which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
-After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
-confidence levels in Table.~\ref{table:IC_DC_results}, and best-fit points in Table ~\ref{table:bestfit}.
+After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:joint_3D}. We record the 
+confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.
 
-\begin{figure}[!tb]
+\begin{figure}
    \begin{center}
-      \begin{subfigure}{0.45\textwidth}
-         \includegraphics[width=1\linewidth]{figures/joint_3D_NO.pdf}
-         \caption{PINGU and DeepCore best case scenario, with their joint $\Delta \chi^2$ in black.}\label{fig:joint_3D}
-      \end{subfigure}
-      \begin{subfigure}{0.45\textwidth}
-         \vspace{1em}
-         \includegraphics[width=1\linewidth, height=0.32\textheight]{figures/PID_3D_emt.pdf}
-         \caption{\emph{Top panel:} IceCube $\emt$ result with two combinations of $\Delta \chi^2$.
-                  \emph{Bottom panel:} $\Delta \chi^2$ regions for best and worst case scenarios as defined in Table~\ref{table:syst_errors}.}\label{fig:IC_3D}
-      \end{subfigure}
-    \caption{Expected $\Delta \chi^2$ at PINGU, DeepCore, and IceCube.
+      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
+      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+      parameters other than the one shown are fixed to zero. 
+      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:joint_3D}
+   \end{center}
+\end{figure} 
+\begin{figure}
+   \begin{center} 
+      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
+      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
     $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than the one shown in each panel are fixed to zero. IceCube tracks only reveal $\emt$, and are displayed separately in the right panel.}\label{fig:3D_NO}
+    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
    \end{center}
@@
 while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
-is indeed preserved at flux level. So the flux for $\emt>0$ is higher than the flux for $\emt<0$. Is this still true at event level, i-.e after reconstruction? 
+is indeed preserved at flux level. So the flux for $\emt>0$ is higher than the flux for $\emt<0$. Is this still true at event level, i.e. after reconstruction? 
 As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$.
@@
 
-\begin{figure}[!tb]
-   \includegraphics[width=0.4\linewidth]{figures/Pmm_asymmetry.pdf}
-   \caption{The ratio $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.05$ in the DeepCore/PINGU energy range.
-Negative $\emt$ has the strongest signal, as the thin blue
-region stemming from $\emt = 0.05$ is less prominent than the red regions from $\emt=-0.05$.}\label{fig:Pmm_asymmetry}
-\end{figure}%TODO: maybe plot P_nsi - p_si?
-\begin{figure}[!tb]
-   \includegraphics[width=0.7\linewidth]{figures/emt_events.pdf}
+\begin{figure}
+   \begin{subfigure}{0.25\textwidth}
+      \includegraphics[width=1\linewidth]{figures/Pmm_asymmetry.pdf}%TODO: redo for emt=0.01
+      \caption{$P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.05$ in the DeepCore/PINGU energy range.}\label{fig:Pmm_asymmetry}
+   \end{subfigure}
+   \begin{subfigure}{0.6\textwidth}
+      \includegraphics[width=1\linewidth]{figures/emt_events.pdf}
    \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$. IceCube only observes a small surplus of events for $\emt=-0.01$ compared to 
    DeepCore and PINGU due to the weak NSI effect at high \si{\GeV} energies.}\label{fig:emt_events}%TODO: improve caption?
+   \end{subfigure}
+   \caption{Probability difference and best-fit event count. Negative $\emt$ has the strongest signal, as the thin blue 
+   region stemming from $\emt = 0.05$ is less prominent than the red regions from $\emt=-0.05$.}
 \end{figure}
@@
    \end{center}
-   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
+   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst-case refers to 
    the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
@@
       \hline & \multicolumn{4}{c}{PINGU} \\
-      $\ett$ & [-0.0326, -] & [-0.0482, ] & [-0.0371, -] & [-, -] \\
+      $\ett$ & [-0.0326, -] & [-0.0482, -] & [-0.0371, -] & [-, -] \\
       $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
@@
    \end{tabular}
-   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
+   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refer to 
    the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
@@
 This is because the `data' we generated during
-the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
 since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

### 2021-05-18 src/events/make_events.py

@@ -18,15 +18,15 @@ parser.add_argument('-th23N', default=1, type=int)
 parser.add_argument('-ettFrom', default=-7e-2, type=float)
 parser.add_argument('-ettTo', default=7e-2, type=float)
 parser.add_argument('-ettN', default=1, type=int)
-parser.add_argument('-emtFrom', default=-2e-2, type=float)
-parser.add_argument('-emtTo', default=2e-2, type=float)
+parser.add_argument('-emtFrom', default=-3e-2, type=float)
+parser.add_argument('-emtTo', default=3e-2, type=float)
 parser.add_argument('-emtN', default=1, type=int)
 
-parser.add_argument('-eemFrom', default=-2.5e-1, type=float)
-parser.add_argument('-eemTo', default=2.5e-1, type=float)
+parser.add_argument('-eemFrom', default=-3e-1, type=float)
+parser.add_argument('-eemTo', default=3e-1, type=float)
 parser.add_argument('-eemN', default=1, type=int)
-parser.add_argument('-eetFrom', default=-2.5e-1, type=float)
-parser.add_argument('-eetTo', default=2.5e-1, type=float)
+parser.add_argument('-eetFrom', default=-3e-1, type=float)
+parser.add_argument('-eetTo', default=3e-1, type=float)
 parser.add_argument('-eetN', default=1, type=int)
 
 parser.add_argument('-s', default = 0, type=int)

### 2021-05-19 article/article.tex
update

@@
    a dashed region is omitted in the left panel.}\label{fig:flux_ratio}
-\end{figure}%TODO: fix cbar need high emt and log to show both cascade and track features at the same time.
-%otherwise, the cascade ratio overpowers the track one.
+\end{figure}%TODO: make prettier cmap
 
@@
       parameters other than the one shown are fixed to zero. 
-      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:joint_3D}
+      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:3D_NO}
    \end{center}
@@
    \begin{center}
-   \begin{tabular}{lcccc}
+   \begin{tabular}{lcccccc}
       \hline \hline
-      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
-      \hline & \multicolumn{4}{c}{IceCube}  \\
-      $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
-      & \multicolumn{4}{c}{DeepCore}\\ [0.3em]
-      $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
-      $\emt$ & [-0.015, 0.0048] & [-, 0.015]& [-0.015, 0.0048] & [-, 0.015] \\
-      $\eem$ & [-0.072, 0.075] & [-0.132, 0.127]& [-0.072, 0.075] & [-0.132, 0.127]\\
-      $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
-      &\multicolumn{4}{c}{IceCube + DeepCore}\\
-      $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
+      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{6}{c}{IceCube}  \\
+      $\epsilon_{\mu\tau}$  &   [-0.01, 0.009] &  [-0.015, 0.014] &  [-0.013, 0.012] &  [-0.019, 0.018] &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
+      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
+      $\epsilon_{\tau\tau}$ &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] \\
+      $\epsilon_{\mu\tau}$  &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] \\
+      $\epsilon_{e\mu}$     &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] \\
+      $\epsilon_{e\tau}$    &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] \\\\
+      &\multicolumn{6}{c}{IceCube + DeepCore}\\
+      $\epsilon_{\mu\tau}$  &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] \\
       \hline
@@
    \end{center}
-   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst-case refers to 
+   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
    the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
@@
 \begin{table}
-   \begin{tabular}{lcccc}
+   \begin{tabular}{lcccccc}
       \hline \hline
-      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
-      \hline & \multicolumn{4}{c}{PINGU} \\
-      $\ett$ & [-0.0326, -] & [-0.0482, -] & [-0.0371, -] & [-, -] \\
-      $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
-      $\eem$ & [-0.062, 0.057] & [-0.122, 0.103] & [-0.1057, 0.0799] & [-0.198, 0.141]\\
-      $\eet$ & [-0.069, 0.077] & [-0.121, 0.133] & [-0.1072, 0.1022] & [-0.1805, 0.1633]\\\\
-      & \multicolumn{4}{c}{DeepCore + PINGU} \\
-      $\ett$ & [-0.028, 0.043] & [-0.043, -] & [-0.0285,  0.0423] & [-0.0447, -]\\
-      $\emt$ & [-0.0067, 0.0049] & [-0.0109,  0.0101] & [-0.0049, 0.0086] & [-0.0098, 0.0146]\\
-      $\eem$ & [-0.048, 0.048]  & [-0.090, 0.085] & [-0.0721, 0.0503] & [-0.1262, 0.0931]\\
-      $\eet$ & [-0.053, 0.072]  & [-0.101, 0.118] & [-0.0901, 0.0624] & [-0.1491, 0.1168]\\\\
-      & \multicolumn{4}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ & [-0.0088,  0.003 ] & [-0.0128, 0.0081] & [-0.01, 0.0028] & [-0.0145, 0.0087]\\
+      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{6}{c}{PINGU} \\
+      $\epsilon_{\tau\tau}$ &  [-0.033, 0.057] &         [-0.048] &  [-0.034, 0.059] &         [-0.051] &  [-0.037, 0.062] &         [-0.055] \\
+      $\epsilon_{\mu\tau}$  &  [-0.007, 0.007] &  [-0.011, 0.013] &  [-0.007, 0.008] &  [-0.012, 0.014] &  [-0.008, 0.009] &  [-0.014, 0.016] \\
+      $\epsilon_{e\mu}$     &  [-0.062, 0.057] &  [-0.122, 0.104] &  [-0.081, 0.067] &   [-0.162, 0.12] &   [-0.106, 0.08] &  [-0.199, 0.141] \\
+      $\epsilon_{e\tau}$    &   [-0.07, 0.077] &   [-0.12, 0.133] &  [-0.086, 0.089] &   [-0.15, 0.148] &  [-0.107, 0.102] &  [-0.182, 0.164] \\\\
+      & \multicolumn{6}{c}{DeepCore + PINGU} \\
+      $\epsilon_{\tau\tau}$ &   [-0.033, 0.05] &  [-0.048, 0.065] &  [-0.033, 0.052] &   [-0.05, 0.067] &  [-0.035, 0.051] &  [-0.052, 0.068] \\
+      $\epsilon_{\mu\tau}$  &  [-0.007, 0.006] &  [-0.011, 0.012] &  [-0.007, 0.006] &  [-0.012, 0.012] &  [-0.004, 0.011] &   [-0.01, 0.017] \\
+      $\epsilon_{e\mu}$     &  [-0.057, 0.052] &  [-0.107, 0.095] &   [-0.067, 0.06] &  [-0.127, 0.107] &  [-0.097, 0.056] &   [-0.165, 0.11] \\
+      $\epsilon_{e\tau}$    &  [-0.063, 0.075] &  [-0.113, 0.128] &  [-0.074, 0.086] &  [-0.136, 0.142] &  [-0.115, 0.065] &  [-0.184, 0.131] \\\\
+      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
+      $\epsilon_{\mu\tau}$  &  [-0.009, 0.004] &  [-0.013, 0.009] &  [-0.009, 0.004] &   [-0.014, 0.01] &  [-0.008, 0.007] &  [-0.012, 0.013] \\
       \hline
@@
    \end{tabular}
-   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refer to 
+   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
    the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
@@
     to the standard interaction count}\label{fig:event_pulls} 
-\end{figure}%TODO: redo these with same emt as flux_ratio?
-
-% \begin{figure}[b]
-%    \begin{center}
-%       \includegraphics[width=0.2\linewidth]{figures/joint_3D_NO.pdf}
-%    \end{center}
-%    \caption{Expected joint $\Delta \chi^2$ from Eq.~\ref{eq:joint_chisq} for normal ordering.}
-%    \label{fig:joint_3D}
-% \end{figure}
-%TODO:  Discussion on impact of IC on chisq.?
+\end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better
 

### 2021-05-19 article/notebooks/nsi.py

@@ -23,7 +23,7 @@ IC_range = np.logspace(np.log10(500),4,50)
 DC_range = np.logspace(np.log10(5.6),np.log10(56),50)
 #ett_range = [-0.1,0,0.1]#np.linspace(-1e-1,1e-1,3)
 emm_range = [-1e-1,0,1e-1]#np.linspace(-1e-1,1e-1,3)
-emt_range = [-5e-2,0,5e-2]
+emt_range = [-1e-2,0,1e-2]
 params = nufit_params_nsi.copy()
 anti=True
 s24_range = [0.032]
@@ -48,7 +48,7 @@ pickle.dump(P_emt_IC_cascade, open('P_emt_IC_cascade.p','wb'))
 '''
 
 z_range = np.linspace(-1,0,500)
-E_range = np.logspace(0,2,500)
+E_range = np.logspace(0,np.log10(60),500)
 
 Pex_neg, Pmx_neg, Paeax_neg,Pamax_neg = nsi_oscillogram(E_range=E_range, z_range=z_range, params= emt_params[0])
 Pex_pos, Pmx_pos, Paeax_pos,Pamax_pos = nsi_oscillogram(E_range=E_range, z_range=z_range, params= emt_params[2])

### 2021-05-20 article/article.tex
update

@@
 \end{align}
-where we have assumed the components of the NSI matrix to be real. In Fig.~\ref{fig:flux_ratio}, we study
-the flux ratio arising from the introduction of the NSI parameter $\emt$.
-Fig.~\ref{fig:Pmm_asymmetry} shows the difference $P_{\mu\mu}(\emt>0) - P_{\mu\mu}(\emt<0)$ in the low \si{\GeV} energy range.
-%TODO: maybe plot P_NSI - P_SI instead.
+where we have assumed the components of the NSI matrix to be real.
+
+In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} area. Any NSI parameter involving $\mu$ or $\tau$ will dampen this resonance,
+with some also shifting the probability in the \SI{100}{\GeV} stationary region.
+This `double effect' of both resonance dampening and shifting happens in two cases: either when the parameter shares one channel with a survival probabilitywe have a survival probability
+(i.e. $P_{\mu\mu}$ and $\eem$), or when the sectors align (i.e. $\emt$ for $P_{\mu\tau}$). The only exception to this rule is for $P_{\tau\tau}$, 
+which due to its near-maximal mixing with the $\mu$ channel displays dampening for $\eem$ even though they share no channel directly. We illustrate
+the three different effects in Fig.~\ref{fig:nsi_probs}.
+
+Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the GeV range. Thus, the only impact that 
+the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
+are met. So except for $P_{ee}$ where the probability is high, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
+Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
+while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by  $\epsilon_{\alpha\beta}$. Any probabilities $P_{e\beta}$ will
+only see a shift in the stationary region, while the two other channels undergo either resonance dampening, or the `double effect'.
+\begin{figure}
+   \includegraphics[width=0.8\textwidth]{figures/nsi_probs.pdf}
+   \caption{The three different effects that the off-diagonal NSI parameters have in the \si{\GeV} range.}\label{fig:nsi_probs}
+\end{figure}
 

### 2021-05-24 article/article.tex
update

--- 2021-05-19 article/article.tex
@@
 \begin{document}
-\section{Formalism}
+\section{Formalism of non-standard interactions}
 Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
@@
 \end{align}
-where we have assumed the components of the NSI matrix to be real. In Fig.~\ref{fig:flux_ratio}, we study
-the flux ratio arising from the introduction of the NSI parameter $\emt$.
-Fig.~\ref{fig:Pmm_asymmetry} shows the difference $P_{\mu\mu}(\emt>0) - P_{\mu\mu}(\emt<0)$ in the low \si{\GeV} energy range.
-%TODO: maybe plot P_NSI - P_SI instead.
+where we have assumed the components of the NSI matrix to be real.
+
+\subsection{Probability effects in the GeV range}
+In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
+with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
+This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
+(e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
+which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
+the three different effects in Fig.~\ref{fig:nsi_probs}.
+
+Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
+the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
+are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
+Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
+while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
+%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
+\begin{figure}
+   \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
+   \caption{The three different effects that the off-diagonal NSI parameters have in the \si{\GeV} range.}\label{fig:nsi_probs}
+\end{figure}
 
@@
 The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth by solving the 
-Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
+Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}.
+The Earth density profile is taken from the PREM~\cite{PREM}.
+The baseline for a given trajectory is determined using an average neutrino
 production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
@@
 and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
-is a energy-independent flux deficiency with a factor of $\sim \sqrt{10}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
-is exposed to multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
+is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
+is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
 energy-independent but zenith-sensitive IceCube deficiency.
@@
 In IceCube, we will only consider muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
-Here we see a somewhat weaker signal, this time a zenith-independent deficiency. Where we earlier had surpluses with a factor $\sim 10$, we now have deficiencies in the order of $\sim \sqrt{10}$.
+Here we see a somewhat weaker signal, this time a zenith-independent deficiency.
+Where we earlier had surpluses with a factor in the order of $\sim 10$, we now have deficiencies in the order of $\sim 10^{0.5}$.
 
@@
 However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
-To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo~\cite{IC2016}, from which
+To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
 we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
 the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
-events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
+events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.
 
@@
 \subsection{Methodology}\label{sec:method}
+%TODO a sentence about simplicity
 For our analyses, we define our $\chi^2$ as
@@
 
-We treat the uncorrelated systematic uncertanties differently for each detector.
-For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
-We consider best, normal, and worst-case scenarios in IceCube assuming
-$f=5\%$, $7.5\%$, and $f=15\%$ respectively. For PINGU, we use the same form but instead assume $f=0\%$, $3\%$, and $f=5\%$. %TODO: maybe source/justification for these values?
+We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+We consider best, normal, and worst-case scenarios in IceCube using
+$f=5\%$, $7.5\%$, and $f=15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $f=5\%$. %TODO: maybe source/justification for these values?
 For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
@@
       \hline \hline
-      Experiment & Worst case & Normal case & Best case \\
+      Experiment & Best case & Baseline & Worst case \\
       \hline
-      IceCube & $15\%$ & $10\%$ & $5\%$ \\
-      PINGU & $5\%$ & $3\%$ & $0\%$ \\
+      IceCube & $5\%$ & $10\%$ & $15\%$ \\
+      PINGU & $0\%$ & $3\%$ & $5\%$ \\
       \hline \hline
    \end{tabular}
-   \caption{Definition of the worst and best case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
+   \caption{Definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
    We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
@@
 which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
-After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:joint_3D}. We record the 
+After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:joint_3D_NO}. We record the 
 confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.
@@
       \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-      parameters other than the one shown are fixed to zero. 
-      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:3D_NO}
+      parameters not shown in each panel are fixed to zero. 
+      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}.}\label{fig:3D_NO}
    \end{center}
@@
    \begin{center} 
-      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
+      \includegraphics[width=0.6\textwidth]{figures/PID_3D_emt.pdf}
       \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
@@
 \end{figure}
-%TODO: dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?
 
-We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:joint_3D}, especially in $\emt$ and $\eet$.%TODO: make better
+We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:3D_NO}, especially in $\emt$ and $\eet$.%TODO: make better
 We investigate this for $\emt$ by plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
@@
 \end{table}
-Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.
-This is because the `data' we generated during
-the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
-since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
 
@@
 The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.
+This is because the `data' we generated during
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
 \newpage

### 2021-05-24 src/events/DC/event_processing.py

@@ -122,6 +122,29 @@ def list_of_params_nsi(dicta, dm31_range, th23_range, ett_range, emt_range, eem_
     dict_list = [update_dict(dicta,{'e_em':eem,'e_et':eet,'e_tt':tt,'e_mt':mt,'theta_23':th23, 'dm_31':dm31}) for eet in eet_range for eem in eem_range for mt in emt_range for tt in ett_range for th23 in th23_range for dm31 in dm31_range]
     return dict_list
 
+def marginalize(chisq,dm31_range, th23_range, ett_range, emt_range, eem_range, eet_range):
+    from scipy.integrate import simps 
+    best_fit_index = chisq.argmin()
+    reshaped_chisq = chisq.reshape(len(eet_range),len(eem_range),len(emt_range),len(ett_range), len(th23_range), len(dm31_range))
+    N = len(th23_range)*len(dm31_range)
+    if len(th23_range) > 1 and len(dm31_range) > 1:
+        marginalized_chisq = simps(simps(reshaped_chisq))/N #Integrate out oscillation parameters and "normalize"
+    else:
+        marginalized_chisq = reshaped_chisq[:,:,:,:,0,0]
+    best_eet_index, best_eem_index, best_emt_index, best_ett_index, best_th23_index, best_dm31_index = np.unravel_index(best_fit_index,reshaped_chisq.shape)
+    
+    deltachi = marginalized_chisq - marginalized_chisq.min()
+    return deltachi, best_dm31_index, best_th23_index, best_ett_index, best_emt_index, best_eem_index, best_eet_index
+
+def marginalize_one(deltachi, axis):
+    '''
+    Assumes 3 axes with same length
+    '''
+    from scipy.integrate import simps 
+    N = deltachi.shape[axis]
+    marginalized_chisq = simps(deltachi, axis=axis)/N #Integrate out oscillation parameters
+    return marginalized_chisq - marginalized_chisq.min()
+
 def get_param_list(dm31N,th23N, ett_tuple, emt_tuple, eem_tuple, eet_tuple, IO=False):
     ettFrom, ettTo, ettN = ett_tuple
     emtFrom, emtTo, emtN = emt_tuple

### 2021-05-25 article/article.tex
update

@@
       \hline & \multicolumn{6}{c}{IceCube}  \\
-      $\epsilon_{\mu\tau}$  &   [-0.01, 0.009] &  [-0.015, 0.014] &  [-0.013, 0.012] &  [-0.019, 0.018] &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
+      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
       & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
-      $\epsilon_{\tau\tau}$ &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] \\
-      $\epsilon_{\mu\tau}$  &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] \\
-      $\epsilon_{e\mu}$     &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] \\
-      $\epsilon_{e\tau}$    &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] \\\\
+      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] &  [-0.046, 0.054] &         [-0.065] &  [-0.049, 0.057] &          [-0.07] \\
+      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\
+      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] &  [-0.11, 0.094] &  [-0.20, 0.16] &   [-0.14, 0.11] &   [-0.23, 0.18] \\
+      $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] &   [-0.10, 0.11] &  [-0.19, 0.18] &  [-0.13, 0.13] &  [-0.23, 0.12] \\\\
       &\multicolumn{6}{c}{IceCube + DeepCore}\\
-      $\epsilon_{\mu\tau}$  &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] \\
+      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
       \hline
@@
       \hline & \multicolumn{6}{c}{PINGU} \\
-      $\epsilon_{\tau\tau}$ &  [-0.033, 0.057] &         [-0.048] &  [-0.034, 0.059] &         [-0.051] &  [-0.037, 0.062] &         [-0.055] \\
-      $\epsilon_{\mu\tau}$  &  [-0.007, 0.007] &  [-0.011, 0.013] &  [-0.007, 0.008] &  [-0.012, 0.014] &  [-0.008, 0.009] &  [-0.014, 0.016] \\
-      $\epsilon_{e\mu}$     &  [-0.062, 0.057] &  [-0.122, 0.104] &  [-0.081, 0.067] &   [-0.162, 0.12] &   [-0.106, 0.08] &  [-0.199, 0.141] \\
-      $\epsilon_{e\tau}$    &   [-0.07, 0.077] &   [-0.12, 0.133] &  [-0.086, 0.089] &   [-0.15, 0.148] &  [-0.107, 0.102] &  [-0.182, 0.164] \\\\
+      $\ett$ &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] \\
+      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
+      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
       & \multicolumn{6}{c}{DeepCore + PINGU} \\
-      $\epsilon_{\tau\tau}$ &   [-0.033, 0.05] &  [-0.048, 0.065] &  [-0.033, 0.052] &   [-0.05, 0.067] &  [-0.035, 0.051] &  [-0.052, 0.068] \\
-      $\epsilon_{\mu\tau}$  &  [-0.007, 0.006] &  [-0.011, 0.012] &  [-0.007, 0.006] &  [-0.012, 0.012] &  [-0.004, 0.011] &   [-0.01, 0.017] \\
-      $\epsilon_{e\mu}$     &  [-0.057, 0.052] &  [-0.107, 0.095] &   [-0.067, 0.06] &  [-0.127, 0.107] &  [-0.097, 0.056] &   [-0.165, 0.11] \\
-      $\epsilon_{e\tau}$    &  [-0.063, 0.075] &  [-0.113, 0.128] &  [-0.074, 0.086] &  [-0.136, 0.142] &  [-0.115, 0.065] &  [-0.184, 0.131] \\\\
+      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] &  [-0.038, 0.048] &  [-0.058, 0.067] &   [-0.039, 0.05] &          [-0.06] \\
+      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] &  [-0.071, 0.086] &  [-0.149, 0.141] &  [-0.082, 0.097] &  [-0.17, 0.16] \\
+      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] &  [-0.061, 0.103] &  [-0.131, 0.155] &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
       & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
-      $\epsilon_{\mu\tau}$  &  [-0.009, 0.004] &  [-0.013, 0.009] &  [-0.009, 0.004] &   [-0.014, 0.01] &  [-0.008, 0.007] &  [-0.012, 0.013] \\
+      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
       \hline

### 2021-05-25 src/events/DC/event_processing.py

@@ -207,13 +207,6 @@ def is_precomputed_nsi(pid,ndim, dict, check=False):
                 return True
 
                 
-def get_best_fit(deltachi, p_range, cl):#TODO: make better
-    from scipy import interpolate
-    deltachi = deltachi.reshape(-1)
-    half = int(len(p_range)/2)
-    left = interpolate.interp1d(deltachi[0:half],p_range[0:half])(chi2.ppf(cl,1))
-    right = interpolate.interp1d(deltachi[half:-1],p_range[half:-1])(chi2.ppf(cl,1))
-    return np.round(left,4),np.round(right,4)
 
 def get_marginalized_array(H1,dm31_range,th23_range,ett_range,emt_range,eem_range,eet_range, param_list, nsi_param, sigma_a,sigma_b, f):
     chisq,  best_fit_index = get_deltachi([H for H in H1],0,[sigma_a,sigma_b],f,x0=[1,0])

### 2021-05-25 article/notebooks/nsi.py
update

@@ -34,19 +34,17 @@ both_params = list_of_params_nsi(params, s24_range, emm_range,emt_range)
 zenith = -1
 
 
-'''
+
 z_range = np.linspace(-1,0,500)
 IC_range = np.logspace(np.log10(500),4,5)
 all_range = np.logspace(np.log10(1),5.1,500)
 #P_emm_IC = np.array(nsi_oscillogram(IC_range, z_range, emm_params[0]))
-#P_emt_IC_track= np.array(nsi_flux_oscillogram(all_range, z_range, emt_params[0], only_m=True))
+P_emt_IC_track= np.array(nsi_flux_oscillogram(all_range, z_range, emt_params[0]))
 #P_emt_IC_cascade= np.array(nsi_flux_oscillogram(all_range, z_range, emt_params[0], only_m=False))
-P_emt_IC_track = pickle.load(open('./pre_computed/P_emt_IC_track.p','rb'))
-P_emt_IC_cascade = pickle.load(open('./pre_computed/P_emt_IC_cascade.p','rb'))
 pickle.dump(P_emt_IC_track, open('P_emt_IC_track.p','wb'))
-pickle.dump(P_emt_IC_cascade, open('P_emt_IC_cascade.p','wb'))
-'''
+#pickle.dump(P_emt_IC_cascade, open('P_emt_IC_cascade.p','wb'))
 
+'''
 z_range = np.linspace(-1,0,500)
 E_range = np.logspace(0,np.log10(60),500)
 
@@ -56,3 +54,4 @@ Pex_pos, Pmx_pos, Paeax_pos,Pamax_pos = nsi_oscillogram(E_range=E_range, z_range
 
 pickle.dump(Pmx_neg, open('Pmx_neg.p','wb'))
 pickle.dump(Pmx_pos, open('Pmx_pos.p','wb'))
+'''

### 2021-05-25 src/plotter.py

@@ -164,7 +164,7 @@ def flux_oscillogram(E_range, z_range, params, nsi=False):
     return 1-flux_final/flux_initial
 
 
-def nsi_flux_oscillogram(E_range, z_range, params, only_m=True):
+def nsi_flux_oscillogram(E_range, z_range, params):
     '''
     Returns (flux_final/flux_initial, flux_bar_final/flux_bar_initial, flux_both_final/flux_both_initial)
     for either only Pxm flux (only_m is True), or for only Pxe+Pxt flux (only_m is False)
@@ -196,21 +196,26 @@ def nsi_flux_oscillogram(E_range, z_range, params, only_m=True):
     flux_mbar = get_flux('mbar',E_mesh,z_mesh,interp_flux)
     flux_ebar = get_flux('ebar',E_mesh,z_mesh,interp_flux)
 
-    if only_m:
-        flux_final =  flux_m*Pmx[1] + flux_e*Pex[1]
-        flux_final_nsi = flux_m*Pmx_nsi[1] + flux_e*Pex_nsi[1]
+    #maybe clean up
+    flux_final_m =  flux_m*Pmx[1] + flux_e*Pex[1]
+    flux_final_m_nsi = flux_m*Pmx_nsi[1] + flux_e*Pex_nsi[1]
 
-        flux_final_bar =  flux_mbar*Pamax[1] + flux_ebar*Paeax[1]
-        flux_final_nsi_bar = flux_mbar*Pamax_nsi[1] + flux_ebar*Paeax_nsi[1]
+    flux_final_m_bar =  flux_mbar*Pamax[1] + flux_ebar*Paeax[1]
+    flux_final_m_nsi_bar = flux_mbar*Pamax_nsi[1] + flux_ebar*Paeax_nsi[1]
     
-    else:
-        flux_final =  flux_m*(Pmx[0] + Pmx[2]) + flux_e*(Pex[0] + Pex[2])
-        flux_final_nsi = flux_m*(Pmx_nsi[0] + Pmx_nsi[2]) + flux_e*(Pex_nsi[0] + Pex_nsi[2])
+    flux_final_e =  flux_m*(Pmx[0] ) + flux_e*(Pex[0])
+    flux_final_e_nsi = flux_m*(Pmx_nsi[0]) + flux_e*(Pex_nsi[0])
 
[…]

### 2021-05-25 article/article.tex
update

@@
 where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
-and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
-DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
-and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
+and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we plot the flux in region in which 99\% of the 
+DeepCore track events originating from $\nm$ fluxes are contained. In the right panel, we show the same but with IceCube events. We see that the only clear signal discernible to the IceCube detector
 is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
@@
 %TODO: check values above after final plot of flux ratios
-In IceCube, we will only consider muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
-Here we see a somewhat weaker signal, this time a zenith-independent deficiency.
-Where we earlier had surpluses with a factor in the order of $\sim 10$, we now have deficiencies in the order of $\sim 10^{0.5}$.
 
@@
    \end{center}
-   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
-   Within the dotted (dashed) boundaries, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
-   a dashed region is omitted in the left panel.}\label{fig:flux_ratio}
+   \caption{Ratio of detector NSI to SI atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes expressed as $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
+   We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
+   Left (right) panel shows the flux ratio in the energy range in which 99\% of the DeepCore (IceCube) events are contained.
+   }\label{fig:flux_ratio}
 \end{figure}%TODO: make prettier cmap
@@
 \end{align}
-where $C_{k\beta}$ is the correction factor from the detector systematic uncertainty and $\phi_\beta^\text{det}$ is defined as Eq.~\ref{eq:propFlux}.
+where $C_{ijk}$ is the correction factor from the detector systematic uncertainty and $\phi_\beta^\text{det}$ is defined as Eq.~\ref{eq:propFlux}.
 We have now substituted the effect of the Gaussian smearing
@@
 We consider best, normal, and worst-case scenarios in IceCube using
-$f=5\%$, $7.5\%$, and $f=15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $f=5\%$. %TODO: maybe source/justification for these values?
+$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$. %TODO: maybe source/justification for these values?
 For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
@@
 which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
-After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:joint_3D_NO}. We record the 
+After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
 confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.
@@
 %TODO: check that this is what is plotted.
-$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
-We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
-while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
-is indeed preserved at flux level. So the flux for $\emt>0$ is higher than the flux for $\emt<0$. Is this still true at event level, i.e. after reconstruction? 
-As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$.
+$\epsilon^\pm_{\mu\tau} = \pm 0.01$ in Fig.~\ref{fig:Pmm_asymmetry}.
+Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
+Let $P^\pm$ denote $P_{\mu\mu}(\epsilon^\pm_{\mu\tau})$. 
+We see see that $\emt^+$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
+while $\emt^-$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
+is indeed preserved at flux level. So the flux for $\emt^+$ is higher than the flux for $\emt^-$. Is this still true at event level, i.e. after reconstruction? 
+As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt^-$.
 DeepCore on the other hand,
-has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
-$\emt$ asymmetry stems from the lower statistics for $\emt< 0 $ at probability level, which is then preserved through the flux and finally the reconstruction. %TODO: fill more conclusion?
+has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
+$\emt$ asymmetry stems from the lower statistics for negative $\emt$ at probability level, which is then propagated through the flux and finally affects the reconstruction.
+%TODO: fill more conclusion?
 
@@
    \begin{subfigure}{0.25\textwidth}   
-      \includegraphics[width=1\linewidth]{figures/Pmm_asymmetry.pdf}%TODO: redo for emt=0.01
-      \caption{$P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.05$ in the DeepCore/PINGU energy range.}\label{fig:Pmm_asymmetry}
+      \includegraphics[width=1\linewidth]{figures/Pmm_asymmetry.pdf}%TODO: redo for emt=0.01x
+      \caption{$P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.01$}\label{fig:Pmm_asymmetry}
    \end{subfigure}
@@
    \caption{Probability difference and best-fit event count. Negative $\emt$ has the strongest signal, as the thin blue 
-   region stemming from $\emt = 0.05$ is less prominent than the red regions from $\emt=-0.05$.}
+   region stemming from $\emt = 0.01$ is less prominent than the red regions from $\emt=-0.01$.}
 \end{figure}
@@
 with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
-The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+The results are shown in Fig.~\ref{fig:IC_NO} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
 Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.

### 2021-05-25 article/notebooks/nsi.py

@@ -37,8 +37,8 @@ zenith = -1
 
 
 z_range = np.linspace(-1,0,500)
-IC_range = np.logspace(np.log10(284),np.log10(103821),500)
-DC_range = np.logspace(np.log10(1.9),np.log10(210),500)
+IC_range = np.logspace(np.log10(284),np.log10(103821),500) #get_Etrue(model, 3,0.995,0.995,E_index=0)[0][0] #get_Etrue(model, 3,0.995,0.995,E_index=12)[0][2]
+DC_range = np.logspace(np.log10(1.9),np.log10(210),500) # MC2018_DC().query('pid==1').query('abs(pdg) == 14').query('reco_energy == reco_energy.min()')['true_energy'].quantile(0.005)
 
 flux_emt_IC_track= np.array(nsi_flux_oscillogram(IC_range, z_range, emt_strong_params[0]))
 flux_emt_DC_track= np.array(nsi_flux_oscillogram(DC_range, z_range, emt_strong_params[0]))

### 2021-05-26 article/article.tex
update

@@
 
-\subsection{Probability effects in the GeV range}
+To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
+The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
+production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption. After this, we are
+ready to study the NSI effect on probability level.
+%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?
+
+\subsection{Non-standard effects in the GeV-TeV range}\label{sec:nsiEffects}
+Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
+However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
+Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.
+
 In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
@@
    \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
-   \caption{The three different effects that the off-diagonal NSI parameters have in the \si{\GeV} range.}\label{fig:nsi_probs}
-\end{figure}
+   \caption{The three different effects that the off-diagonal NSI parameters have in 
+   the \si{\GeV} range. To schematically elucidate the NSI effect, we plot the summed probabilities for both neutrinos and 
+   antineutrinos.}\label{fig:nsi_probs}
+\end{figure}%TODO: change plot ylabels
 
-\section{Detector formalism}
-The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth by solving the 
-Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}.
-The Earth density profile is taken from the PREM~\cite{PREM}.
-The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
-%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?
-
+To study the NSI flux effect, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
 The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
@@
 \end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
-and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we plot the flux in region in which 99\% of the 
-DeepCore track events originating from $\nm$ fluxes are contained. In the right panel, we show the same but with IceCube events. We see that the only clear signal discernible to the IceCube detector
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ at flux level, 
+we plot in Fig.~\ref{fig:flux_ratio} the quantity $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$, 
+where all fluxes are propagated to detector level by Eq.~\ref{eq:propFlux}. 
+In the left panel, we plot the flux in region in which 99\% of the 
+DeepCore track events originating from $\nm + \anm$ fluxes are contained.
+In the right panel, we show the same but with IceCube events.
+We see that the only clear signal discernible to the IceCube detector
 is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
@@
 
+\section{Detector formalism}
 \subsection{IceCube}\label{ch:ICmethod}
@@
 
-% We plot the normalized event difference $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
-% assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.
-%TODO:conclusion from this?
-
 \subsection{PINGU}\label{ch:PINGUmethod}
@@
 \section{Results}
-In this section, we present the results from the experiments alone, as well as jointly. 
-\subsection{Methodology}\label{sec:method}
-%TODO a sentence about simplicity
+At the reconstructed event level, we note that the $\emt$ features discussed in Sec.~\ref{sec:nsiEffects} display themselves differently in each detector.
+We investigate this for $\emt$ by in Fig.~\ref{fig:Pmm_asymmetry} plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
+%TODO: check that this is what is plotted.
+$\epsilon^\pm_{\mu\tau} = \pm 0.01$.
+Comparing Fig.~\ref{fig:Pmm_asymmetry} with the flux ratios in Fig.~\ref{fig:emt_events}, we see that the reconstruction of PINGU is
+superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})} = \log{N^+_{NSI}} - \log{N^-_{NSI}}$ (in reconstructed quantities) 
+more closely matches the probability difference $P^+-P^-$ (in true quantities).
+This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes while PINGU preserves the $N^-_{NSI}$ surplus below \SI{10}{\GeV}.
+
+Now we turn to the effect of $\emt$. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ in this way to explain the $\emt$ features. 
+First, let $P^\pm$ denote $P_{\mu\mu}(\epsilon^\pm_{\mu\tau})$. 
+We see see that $\emt^+$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
+while $\emt^-$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
+is indeed preserved at flux level. So the flux for $\emt^+$ is higher than the flux for $\emt^-$. Is this still true at event level, i.e. after reconstruction? 
+As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, which will give a high statistics on both sides of $\emt=0$, slightly favoring $\emt^-$.
+DeepCore on the other hand, has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, 
+giving weaker statistics for the negative side. Thus, we conclude that we will see a $\emt$ \si{GeV}-asymmetry stemming from the lower statistics 
+for negative $\emt$ at probability level, which is then propagated through the flux and finally affects the reconstruction. %TODO: fill more conclusion?
+
+\begin{figure}
+   \begin{subfigure}{0.25\textwidth}   
+      \includegraphics[width=1\linewidth]{figures/Pmm_asymmetry.pdf}%TODO: redo for emt=0.01x
+      \caption{$P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.01$}\label{fig:Pmm_asymmetry}
+   \end{subfigure}
+   \begin{subfigure}{0.6\textwidth}
+      \includegraphics[width=1\linewidth]{figures/emt_events.pdf}
+   \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$. IceCube only observes a small surplus of events for $\emt=-0.01$ compared to 
+   DeepCore and PINGU due to the weak NSI effect at high \si{\GeV} energies.}\label{fig:emt_events}%TODO: improve caption?
+   \end{subfigure}
+   \caption{Probability difference and best-fit event count. Negative $\emt$ has the strongest signal, as the thin blue 
+   region stemming from $\emt = 0.01$ is less prominent than the red regions from $\emt=-0.01$.}
+\end{figure}
+
+\subsection{Constraining the NSI parameters}\label{sec:method}
+In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
 For our analyses, we define our $\chi^2$ as
@@
 
-\subsection{Constraining the NSI parameters}
-First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
+For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
+\begin{align}\label{eq:joint_chisq}
+    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
+\end{align}
+with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
+
+Now, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
 which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
-After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
-confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.
+After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}.
+The results are shown in Fig.~\ref{fig:IC_NO} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+
+Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.
+This is because the `data' we generated during
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
 
@@
 \end{figure}
-
-We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:3D_NO}, especially in $\emt$ and $\eet$.%TODO: make better
-We investigate this for $\emt$ by plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
-%TODO: check that this is what is plotted.
-$\epsilon^\pm_{\mu\tau} = \pm 0.01$ in Fig.~\ref{fig:Pmm_asymmetry}.
-Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
-Let $P^\pm$ denote $P_{\mu\mu}(\epsilon^\pm_{\mu\tau})$. 
-We see see that $\emt^+$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
-while $\emt^-$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
-is indeed preserved at flux level. So the flux for $\emt^+$ is higher than the flux for $\emt^-$. Is this still true at event level, i.e. after reconstruction? 
-As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt^-$.
-DeepCore on the other hand,
-has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
-$\emt$ asymmetry stems from the lower statistics for negative $\emt$ at probability level, which is then propagated through the flux and finally affects the reconstruction.
-%TODO: fill more conclusion?
-
-\begin{figure}
-   \begin{subfigure}{0.25\textwidth}   
-      \includegraphics[width=1\linewidth]{figures/Pmm_asymmetry.pdf}%TODO: redo for emt=0.01x
-      \caption{$P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.01$}\label{fig:Pmm_asymmetry}
-   \end{subfigure}
-   \begin{subfigure}{0.6\textwidth}
-      \includegraphics[width=1\linewidth]{figures/emt_events.pdf}
-   \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$. IceCube only observes a small surplus of events for $\emt=-0.01$ compared to 
-   DeepCore and PINGU due to the weak NSI effect at high \si{\GeV} energies.}\label{fig:emt_events}%TODO: improve caption?
-   \end{subfigure}
-   \caption{Probability difference and best-fit event count. Negative $\emt$ has the strongest signal, as the thin blue 
-   region stemming from $\emt = 0.01$ is less prominent than the red regions from $\emt=-0.01$.}
-\end{figure}
-
-Comparing Fig.~\ref{fig:emt_events} with the flux ratios in Fig.~\ref{fig:flux_ratio}, we see that the reconstruction of PINGU is
-superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})}$ (which is in reconstructed quantities) more closely matches the flux ratio $\log{(\phi_{NSI}/\phi_{SI})}$ (which is in true quantities).
-This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes while PINGU still has the $N^-_{NSI}$ surplus below \SI{10}{\GeV}.
 
@@
 \end{table}
-
-For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
-\begin{align}\label{eq:joint_chisq}
-    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
-\end{align}
-with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
-The results are shown in Fig.~\ref{fig:IC_NO} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
-Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.
-This is because the `data' we generated during
-the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
-since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
 \newpage

### 2021-05-26 src/events/make_events.py

@@ -60,6 +60,7 @@ if __name__ == '__main__':
                                                                                        (args.eemFrom, args.eemTo,args.eemN), 
                                                                                        (args.eetFrom, args.eetTo,args.eetN), 
                                                                                        args.IO)
+    dm31_range =  np.array_split(dm31_range,args.sT)[args.s]
     print('dm:', dm31_range)
     print('th:', th23_range)
     print('ett:', ett_range)
@@ -76,7 +77,8 @@ if __name__ == '__main__':
         H1 = np.array(H1_events_list)
         H1 = H1.reshape(len(param_list),1,8,8) #second axis is pid
 
-        pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_PINGU_{args.pid}_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))  
+        #pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_PINGU_{args.pid}_{len(dm31_range)}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))
+        pickle.dump(H1,open(f'./pre_computed/H1_{ordering}_PINGU_{args.pid}_{args.s}x{len(th23_range)}x{len(ett_range)}x{len(emt_range)}x{len(eem_range)}x{len(eet_range)}.p','wb'))  
     elif args.DC:
         H1_events_list = process_map(precompute_probs, param_tuple,chunksize=4)
         H1 = np.array(H1_events_list)

### 2021-05-26 thesis/tex/ICtheory.tex
update

@@
 To resolve this, we have opted to train a Gaussian process regressor on the dataset, from which we can extract the predicted mean and standard deviation for a point.
-When doing this over $\Ereco$, we sample $\Etrue$ in the 99\%th percentile around the predicted mean.
+When doing this over $\Ereco$, we sample $\Etrue$ in the 99th percentile around the predicted mean.
 We then obtain the shaded band shown in Fig.~\ref{fig:IC_MC_gpr}.
@@
 where $T$ is the live time of the detector.
+Now this expression handles the Gaussian smearing, but we are not provided systematic error sources, DOM efficiencies, and many more nuisance parameters.
+To correct this,
+we will aim to come as close as possible to the IceCube Monte Carlo, and then normalize with it.
+That way, we know that our null hypotheses will align while we are free to form additional hypotheses with different
+physics parameters. The binned Monte Carlo events that IceCube used as their null hypothesis in the 2020 sterile analysis is shown in %TODO:MC vs myMC fig.
 
@@
  \end{figure}
+
+The latest available data collected and processed by the collaboration contains 305,735 muon track events, collected over eight years~\cite{IC2020}. 
+\newpage
 \bibliographystyle{nature}

### 2021-05-26 thesis/tex/sterileTheory.tex
update

\documentclass{article}
\input{commands}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, subcaption}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{xr-hyper}
%\externaldocument{sterile}

\begin{document}
\section{The Sterile State}\label{sec:anomalies}
In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}. The anomaly was consistent with a fourth
neutrino state with $\dm[41] > \SI{0.03}{\eV \squared}$. Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
$\ne$ events too. Together with the so-called reactor and gallium analomalies, there were indications that both appearance and disappearance
anomalies might be remedied by a fourth mass state.

However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species, so this fourth mass state can't be interacting weakly.
We now distinguish between the three original neutrino flavors ($e$, $\mu$, and $\tau$) and the new fourth flavor ($s$) by calling the former \emph{active} neutrinos
and the latter \emph{sterile}. The experiments listed above indicate that the mass-squared difference of the sterile neutrino is in the \si{\eV} scale, while the two others
are three and five magnitudes smaller. To remind us of this difference, we write $3+1$, since the sterile state proposed is a lot more massive than the active states. Models
with different hierachies might be written as $1+2+1$ or $1+3$, but many of them are ruled out by cosmological constraints and will not be considered here. %TODO:source

The inclusion of the sterile neutrino in the Hamiltonian is straightforward. We extend the PMNS matrix to incorporate the new flavor and mass eigenstates: 
\begin{align}
    U_{4gen} =
    \begin{pmatrix}
    U_{e1} & U_{e2} & U_{e3} & U_{e4} \\
    U_{\mu1} & U_{\mu2} & U_{\mu3} & U_{\mu4} \\
    U_{\tau1} & U_{\tau2} & U_{\tau3} & U_{\tau4} \\
    U_{s1} & U_{s2} & U_{s3} & U_{s4}
    \end{pmatrix}\,,
\end{align}
where a common parametrization of the PMNS matrix is 
\begin{align}\label{eq:U4gen_param}
    U_{4gen} = R_{34}R_{24}R_{14}U_{3gen}\,.
\end{align}
The mass matrix extends analogously:
\begin{align}\label{eq:dm4gen}
    M^2_{4gen} =
    \begin{pmatrix}
        0 & 0 & 0 & 0\\
        0 & \dm_{21} & 0  & 0 \\
        0 & 0 & \dm_{31} & 0 \\
        0 & 0 & 0 & \dm_{41} \\
    \end{pmatrix}\,.
\end{align}

Now,the interaction with matter requires a careful reconsideration of the matter potential. We start of with the unaltered potential matrix. 
Just as with the PMNS matrix, we extend this to $4\times4$:
\begin{align}\label{eq:Vsterile1}
    \begin{pmatrix}
        V_{CC} + V_{NC} & 0 & 0 & 0 \\
        0 &V_{NC} & 0 & 0 \\
        0 & 0 & V_{NC} & 0 \\
        0 & 0 & 0 & 0 
    \end{pmatrix}\,.
\end{align}
Now we need to include the terms that describes the matter potential felt by the sterile flavor state. Recalling our discussion above, we remind ourselves that the sterile neutrino by definition
does not participate in any interaction\footnote{The exception to this is of course gravity. The sterile neutrino is not massless.}. Thus, all potential terms involving the sterile state are zero. 
In other words, the potential matrix in Eq.~\ref{eq:Vsterile1} is complete, save for the usual subtraction by a constant identity matrix:

\begin{align}\label{eq:Vsterile}
    V_{4gen} &=
    \begin{pmatrix}
        V_{CC} + V_{NC} & 0 & 0 & 0 \\
        0 &V_{NC} & 0 & 0 \\
        0 & 0 & V_{NC} & 0 \\
        0 & 0 & 0 & 0 
    \end{pmatrix} - V_{NC}\begin{pmatrix}
        1 & 0 & 0 & 0 \\
        0 &1 & 0 & 0 \\
        0 & 0 & 1 & 0 \\
        0 & 0 & 0 & 1 
    \end{pmatrix}
    = \begin{pmatrix}
        V_{CC} & 0 & 0 & 0 \\
        0 &0 & 0 & 0 \\
        0 & 0 & 0 & 0 \\
        0 & 0 & 0 & -V_{NC}
    \end{pmatrix} \nonumber \\
    &=\sqrt{2}G_F N_e\begin{pmatrix}
        1 & 0 & 0 & 0 \\
        0 &0 & 0 & 0 \\
        0 & 0 & 0 & 0 \\
        0 & 0 & 0 & -1/2
    \end{pmatrix}\,.
\end{align}
where we have assumed electrical neutrality in the last step, yielding $N_e = N_n$.

Thus, the final Hamiltonian with a fourth sterile neutrino is 
\begin{align}\label{eq:H_4gen}
    H_{4gen} &= \frac{1}{2E}\left[U \begin{pmatrix}
            0 & 0 & 0 & 0\\
            0 & \dm_{21} & 0  & 0 \\
            0 & 0 & \dm_{31} & 0 \\
            0 & 0 & 0 & \dm_{41} \\
        \end{pmatrix} U^\dagger\right] + \sqrt{2}G_F N_e 
        \begin{pmatrix}
            1 & 0 & 0 & 0 \\
            0 & 0 & 0 & 0 \\
            0 & 0 & 0 & 0 \\
            0 & 0 & 0 & -1/2
        \end{pmatrix}\,. 
\end{align}

Now, looking at Eqs.~\ref{eq:U4gen_param} and~\ref{eq:dm4gen}, we see that we have introduced four new parameters: $\dm[41]$, $\theta_{14}$
, $\theta_{24}$, $\theta_{34}$.

\section{Sterile Signals}
Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the $\bar\mu \bar\mu$ sector, shown in Fig.~\ref{fig:sterile_resonance}.

\begin{figure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{figures/sterile_resonance.pdf}
        \caption{$\Pamam$ disappearance}\label{fig:sterile_resonance}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{figures/resonance_shift.pdf}
        \caption{$\Pamam$ disappearance}\label{fig:resonance_shift}
    \end{subfigure}
\end{figure}

So for a \si{\eV}-scale sterile neutrino and a non-zero $\theta_{24}$, we expect a \si{\TeV} $\anm$ disappearance.
The resonance dip is affected by the value of $\dm[41]$ and $\theta_{24}$ as shown in Fig.~\ref{fig:resonance_shift}.
We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength.

\newpage
\bibliographystyle{elsarticle-num}
\bibliography{ref}
\end{document}

### 2021-05-26 src/events/IC/event_processing.py

@@ -237,6 +237,14 @@ def list_of_params_nsi(dicta,s24_range, emm_range, emt_range=None):
     else:
         dict_list = [update_dict(dicta,{'e_mm':mm,'e_mt':mt,'theta_24':np.arcsin(np.sqrt(s24))/2}) for mt in emt_range for mm in emm_range for s24 in s24_range]
     return dict_list
+
+def list_of_params(dicta,dm41_range, s24_range):
+    def update_dict(dict,p):
+        dict2 = dict.copy()
+        dict2.update(p)
+        return dict2
+    dict_list = [update_dict(dicta,{'dm_41':dm,'theta_24':np.arcsin(np.sqrt(s24))/2}) for dm in dm41_range for s24 in s24_range]
+    return dict_list
 def return_precomputed_nsi(N,ndim,params, nsi=False):
     params= np.array(params)
     precomputed_list = np.array([is_precomputed_nsi(N,ndim, p, check=False) for p in params])

### 2021-05-26 thesis/tex/sterileResults.tex
update

--- 2021-05-26 thesis/tex/sterileTheory.tex
@@
-\documentclass{article}
+\documentclass{thesis}
+\usepackage[margin=0.5in]{geometry}
 \input{commands}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, subcaption}
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{xr-hyper}
-%\externaldocument{sterile}
 
 \begin{document}
-\section{The Sterile State}\label{sec:anomalies}
-In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}. The anomaly was consistent with a fourth
-neutrino state with $\dm[41] > \SI{0.03}{\eV \squared}$. Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
-$\ne$ events too. Together with the so-called reactor and gallium analomalies, there were indications that both appearance and disappearance
-anomalies might be remedied by a fourth mass state.
 
-However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species, so this fourth mass state can't be interacting weakly.
-We now distinguish between the three original neutrino flavors ($e$, $\mu$, and $\tau$) and the new fourth flavor ($s$) by calling the former \emph{active} neutrinos
-and the latter \emph{sterile}. The experiments listed above indicate that the mass-squared difference of the sterile neutrino is in the \si{\eV} scale, while the two others
-are three and five magnitudes smaller. To remind us of this difference, we write $3+1$, since the sterile state proposed is a lot more massive than the active states. Models
-with different hierachies might be written as $1+2+1$ or $1+3$, but many of them are ruled out by cosmological constraints and will not be considered here. %TODO:source
-
-The inclusion of the sterile neutrino in the Hamiltonian is straightforward. We extend the PMNS matrix to incorporate the new flavor and mass eigenstates: 
-\begin{align}
-    U_{4gen} =
-    \begin{pmatrix}
-    U_{e1} & U_{e2} & U_{e3} & U_{e4} \\
-    U_{\mu1} & U_{\mu2} & U_{\mu3} & U_{\mu4} \\
-    U_{\tau1} & U_{\tau2} & U_{\tau3} & U_{\tau4} \\
-    U_{s1} & U_{s2} & U_{s3} & U_{s4}
-    \end{pmatrix}\,,
-\end{align}
-where a common parametrization of the PMNS matrix is 
-\begin{align}\label{eq:U4gen_param}
-    U_{4gen} = R_{34}R_{24}R_{14}U_{3gen}\,.
-\end{align}
-The mass matrix extends analogously:
-\begin{align}\label{eq:dm4gen}
-    M^2_{4gen} =
-    \begin{pmatrix}
-        0 & 0 & 0 & 0\\
-        0 & \dm_{21} & 0  & 0 \\
-        0 & 0 & \dm_{31} & 0 \\
-        0 & 0 & 0 & \dm_{41} \\
-    \end{pmatrix}\,.
-\end{align}
-
-Now,the interaction with matter requires a careful reconsideration of the matter potential. We start of with the unaltered potential matrix. 
-Just as with the PMNS matrix, we extend this to $4\times4$:
-\begin{align}\label{eq:Vsterile1}
-    \begin{pmatrix}
-        V_{CC} + V_{NC} & 0 & 0 & 0 \\
-        0 &V_{NC} & 0 & 0 \\
-        0 & 0 & V_{NC} & 0 \\
-        0 & 0 & 0 & 0 
-    \end{pmatrix}\,.
-\end{align}
-Now we need to include the terms that describes the matter potential felt by the sterile flavor state. Recalling our discussion above, we remind ourselves that the sterile neutrino by definition
-does not participate in any interaction\footnote{The exception to this is of course gravity. The sterile neutrino is not massless.}. Thus, all potential terms involving the sterile state are zero. 
-In other words, the potential matrix in Eq.~\ref{eq:Vsterile1} is complete, save for the usual subtraction by a constant identity matrix:
-
-\begin{align}\label{eq:Vsterile}
-    V_{4gen} &=
-    \begin{pmatrix}
-        V_{CC} + V_{NC} & 0 & 0 & 0 \\
-        0 &V_{NC} & 0 & 0 \\
-        0 & 0 & V_{NC} & 0 \\
-        0 & 0 & 0 & 0 
-    \end{pmatrix} - V_{NC}\begin{pmatrix}
-        1 & 0 & 0 & 0 \\
-        0 &1 & 0 & 0 \\
-        0 & 0 & 1 & 0 \\
-        0 & 0 & 0 & 1 
-    \end{pmatrix}
-    = \begin{pmatrix}
-        V_{CC} & 0 & 0 & 0 \\
-        0 &0 & 0 & 0 \\
-        0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & -V_{NC}
-    \end{pmatrix} \nonumber \\
-    &=\sqrt{2}G_F N_e\begin{pmatrix}
-        1 & 0 & 0 & 0 \\
-        0 &0 & 0 & 0 \\
-        0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & -1/2
-    \end{pmatrix}\,.
-\end{align}
-where we have assumed electrical neutrality in the last step, yielding $N_e = N_n$.
-
-Thus, the final Hamiltonian with a fourth sterile neutrino is 
-\begin{align}\label{eq:H_4gen}
-    H_{4gen} &= \frac{1}{2E}\left[U \begin{pmatrix}
-            0 & 0 & 0 & 0\\
-            0 & \dm_{21} & 0  & 0 \\
-            0 & 0 & \dm_{31} & 0 \\
-            0 & 0 & 0 & \dm_{41} \\
-        \end{pmatrix} U^\dagger\right] + \sqrt{2}G_F N_e 
-        \begin{pmatrix}
-            1 & 0 & 0 & 0 \\
-            0 & 0 & 0 & 0 \\
-            0 & 0 & 0 & 0 \\
-            0 & 0 & 0 & -1/2
-        \end{pmatrix}\,. 
-\end{align}
-
-Now, looking at Eqs.~\ref{eq:U4gen_param} and~\ref{eq:dm4gen}, we see that we have introduced four new parameters: $\dm[41]$, $\theta_{14}$
-, $\theta_{24}$, $\theta_{34}$.
-
-\section{Sterile Signals}
-Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
-we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
-which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the $\bar\mu \bar\mu$ sector, shown in Fig.~\ref{fig:sterile_resonance}.
-
-\begin{figure}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=1\linewidth]{figures/sterile_resonance.pdf}
-        \caption{$\Pamam$ disappearance}\label{fig:sterile_resonance}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=1\linewidth]{figures/resonance_shift.pdf}
-        \caption{$\Pamam$ disappearance}\label{fig:resonance_shift}
-    \end{subfigure}
-\end{figure}
-
-So for a \si{\eV}-scale sterile neutrino and a non-zero $\theta_{24}$, we expect a \si{\TeV} $\anm$ disappearance.
-The resonance dip is affected by the value of $\dm[41]$ and $\theta_{24}$ as shown in Fig.~\ref{fig:resonance_shift}.
-We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength.
-
-\newpage
-\bibliographystyle{elsarticle-num}
-\bibliography{ref}
 \end{document}

### 2021-05-27 src/events/IC/make_events.py
update

@@ -5,84 +5,47 @@ if __name__ == '__main__':
     sys.path.append('./src/events')
     sys.path.append('./src/probability')
 import numpy as np
-import pandas as pd
 from IC.importer import *
 from IC.processer import *
 from IC.event_processing import *
-from DC.event_processing import list_of_params_nsi
 from IC.main import sim_events
-from functions import nufit_params_nsi, nufit_params_nsi_IO
+from functions import ic_params
 import pickle
 import argparse
 parser = argparse.ArgumentParser()
-parser.add_argument('-dm31From', default=2.489, type=float)
-parser.add_argument('-dm31To', default=2.543, type=float)
-parser.add_argument('-dm31N', default=10, type=int)
+parser.add_argument('-dm41From', default=0.01, type=float)
+parser.add_argument('-dm41To', default=10, type=float)
+parser.add_argument('-dm41N', default=10, type=int)
 
-parser.add_argument('-th23From', default=48*np.pi/180, type=float)
-parser.add_argument('-th23To', default=50.1*np.pi/180, type=float)
-parser.add_argument('-th23N', default=10, type=int)
+parser.add_argument('-s24From', default=0.01, type=float)
+parser.add_argument('-s24To', default=1, type=float)
+parser.add_argument('-s24N', default=10, type=int)
 
-parser.add_argument('-emm', default=1e-1, type=float)
-parser.add_argument('-emmN', default=10, type=int)
-parser.add_argument('-emt', default=1e-2, type=float)
-parser.add_argument('-emtN', default=10, type=int)
 parser.add_argument('-s', default = 0, type=int)
 parser.add_argument('-sT', default = 1, type=int)
-parser.add_argument('-nonsi', action='store_false')
-parser.add_argument('-IO', action='store_true')
 parser.add_argument('-N', default=13, type=int)
 args = parser.parse_args()
 
 if __name__ == '__main__':
     alpha = 0.99
     gamma=0
-    if args.IO is False:
-        dm31_range = np.linspace(args.dm31From*1e-3,args.dm31To*1e-3,args.dm31N-1)
-    else: #Nufit gives dm32 for IO, so convert the values and bounds to dm31 explicitly here
[…]

### 2021-05-27 src/events/IC/make_sterile_events.py
update

@@ -1,17 +1,15 @@
-import sys,os
-if __name__ == '__main__':
-    #os.chdir('../')
-    sys.path.append('./src/data')
-    sys.path.append('./src/events')
-    sys.path.append('./src/probability')
+import sys
+sys.path.append('./src/events')
+sys.path.append('./src/probability')
+sys.path.append('./src/data')
 import numpy as np
-from IC.importer import *
-from IC.processer import *
-from IC.event_processing import *
-from IC.main import sim_events
-from functions import ic_params
 import pickle
 import argparse
+
+from IC.main import get_events
+from IC.event_processing import list_of_params
+from functions import ic_params
+
 parser = argparse.ArgumentParser()
 parser.add_argument('-dm41From', default=0.01, type=float)
 parser.add_argument('-dm41To', default=10, type=float)
@@ -45,7 +43,7 @@ if __name__ == '__main__':
 
     from multiprocessing import Pool
     p = Pool()
-    data = [(alpha, args.N,p, False,False, [False, np.median(1), gamma],False, False,4) for p in param_list]
-    H1_events_list = p.starmap(sim_events, data)
+    data = [(i,j,0.99, args.N,p, [False, 0, 0],False, False,False,4) for p in param_list for i in range(13) for j in range(20)]
+    H1_events_list = p.starmap(get_events, data)
     p.close()
     pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s42_range)}.p','wb'))

### 2021-05-27 thesis/tex/sterileResults.tex
update

@@
 \begin{document}
+\section{Monte Carlo normalization}
+Independent researchers outside of the IceCube collaboration will not be able to more persicely
+simulate the detector. The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this 
+section is to come as close as we can to their Monte Carlo simulations. After we are confident that 
+our code displays the same overall features as the ´offical', we normalize our results $N_{ij}^\text{sim}$ as 
+\begin{align}\label{eq:MC_norm}
+    N_{ij}^\text{corr} = \frac{N_{ij}^\text{null}}{N_{ij}^\text{MC}}\,.
+\end{align}
+For each bin $i,j$, we then obtain a correction factor which contains information that we are unable
+to obtain or sufficiently incorporate. One example of such information is the systematic errors of the DOMs.
+Recent IceCube data releases do not include such information. Since the systematic errors are affecting the 
+event count on a bin-by-bin basis, they can in theory drastically modify the binned results. Another example of
+an error source what will be remedied by this method is the flux. We are using a fairly simple model of the atmospheric 
+flux that excludes prompt flux. The IceCube collaboration use several different flux models which are initialized 
+by a parametrization of the cosmic ray flux.\footnote{Included in the cosmic ray models are e.g. the pion to kaon 
+ratio, which are often used as a nuisance parameter. By not being able to include this in our error analysis, our method will 
+be limited to only consider the overall flux normalization, rather than the components that produce the flux in the first place.}
+%TODO: maybe rambling?
+
+In Fig.~\ref{fig:IC_MC_norm}, we present the Icecube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
+with our null hypothesis times a constant factor.  We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
+correction factors of Eq.~\ref{eq:MC_norm}. We now arrive to our final event count
+\begin{align}\label{eq:Nth}
+    N_{ij} &= \frac{N_{ij}^\text{null}}{N_{ij}^\text{MC}} T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
+    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
+\end{align}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/IC_MC_norm.pdf}
+    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as ´Null' in the plots.}\label{fig:IC_MC_norm}
+\end{figure}
+
+\section{Sterile hypothesis}
+With the null normalized, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
+First, let us see how the collected data from Fig.~\ref{fig:IC_data} deviates from the predicted $3\nu$ oscillations.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/IC_rates.pdf}
+    \caption{}\label{fig:IC_rates}
+\end{figure}
+Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
+for neutrinos close to double-digit \si{\TeV} values. In zenith, the data only deviates $\pm 1\%$. Recalling the \si{\TeV} disappearance from 
+Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at $4 \si{TeV}$. Thus, we expect the best fitting 
+sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
+that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.
+
+\section{$\chi^2$}
+For our analyses, we define our $\chi^2$ as
+\begin{align} \label{eq:chisq}
+    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ij} \frac{\left(N^\text{th}-N^\text{data}\right)_{ij}^{2}}
+    {\left(\sigma^\text{data}_{ij}\right)^{2} + \left(\sigma^\text{syst}_{ij}\right)^{2}}+ 
+    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
+\end{align}
+where we minimize over the model parameters $\hat{\theta} \in \{\dm[41], \theta_{24}\}$, the penalty terms $\alpha$ and $\beta$.
+$N_{ij}^\text{th}$ is the expected number of events from theory, and $N_{ij}^\text{data}$ is the observed number of events in that bin. 
+We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
+The observed event number has an associated Poissonian uncertainty $\sigma_{ij}^\text{data} = \sqrt{N_{ij}^\text{data}}$.
+For IceCube, the event count takes the form
+\begin{align}
+    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
+\end{align}
+with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}. Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.
 

### 2021-05-27 src/events/IC/make_sterile_events.py

@@ -46,4 +46,4 @@ if __name__ == '__main__':
     data = [(i,j,0.99, args.N,p, [False, 0, 0],False, False,False,4) for p in param_list for i in range(13) for j in range(20)]
     H1_events_list = p.starmap(get_events, data)
     p.close()
-    pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s42_range)}.p','wb'))
+    pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}.p','wb'))

### 2021-05-27 thesis/tex/sterileResults.tex
update

@@
 
-\section{$\chi^2$}
+\section{$\chi^2$ minimization}
 For our analyses, we define our $\chi^2$ as
@@
 \end{align}
-with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}. Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.
+with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}.
+Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate with angle $\beta$ around the median zenith angle of $\zreco = -0.5$.
+We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a percentage of our own choosing,
+typically a value between 0 and 20 \%.
 
+The minimization of Eq.~\ref{eq:chisq} simply returns a value for each set of model parameters. We use this value to quantify to what extent
+our theoretical simulations $N^\text{th}_{ij}$ agree with the data $N^\text{data}_{ij}$ within the error bounds provided by $\sigma_a,\sigma_b,$ and $f$.
+We then select the set of $\chi^2$ values which are the smallest and our allowed parameters are then their associated $\hat{\theta}$.
+From the $\chi^2$-distribution, one can show that the $90\%$ confidence level has a value of $2.71$ for two degrees of freedom. When slicing through the 
+two-dimensional grid of $\chi^2$ at this level, we then obtain a contour plot that tells us what regions are within our $90 \%$ and what regions are not.
+
+Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
 \end{document}

### 2021-05-27 src/plotter.py

@@ -91,6 +91,18 @@ def plot_P_E_params(x,P, ax,flavor_to='m',colors=None,legend_name='', legend_val
 def wrap(flavor_from, E, zenith, ndim, anti,params,nsi):
     return P_num_over_E(flavor_from=flavor_from, E=E, zenith=zenith, ndim = ndim,anti=anti,params=params, nsi=nsi)
 
+def wrap_param(p_list):
+    flavor_from, E, zenith, ndim, anti,params,nsi = p_list
+    return P_over_E_parameter(flavor_from, params, E, zenith=zenith, ndim = ndim,anti=anti, nsi=nsi)
+
+def _oscillogram_no_pool(p_list):
+    '''
+    p = [flavor_from, E, zenith, ndim, anti, params]
+    '''
+    res = list(map(wrap_param, p_list))
+    Pxm = np.array(res)[:,:,1,:]
+    return np.swapaxes(Pxm, 1,2)
+
 def _oscillogram(p_list):
     '''
     p = [flavor_from, E, zenith, ndim, anti, params]
@@ -141,22 +153,22 @@ def flux_oscillogram(E_range, z_range, params, nsi=False):
     '''
     Returns 1-flux_final/flux_initial for Pxm
     '''
-    lista_mbar = [('m', E_range, z, 3, True, params,False) for z in z_range]
-    lista_ebar = [('e', E_range, z, 3, True, params,False) for z in z_range]
-    lista_m = [('m', E_range, z, 3, False, params,False) for z in z_range]
-    lista_e = [('e', E_range, z, 3, False, params,False) for z in z_range]
-    Pmm = _oscillogram(lista_m)
-    Pem = _oscillogram(lista_e)
-    Pamam = _oscillogram(lista_mbar)
-    Paeam = _oscillogram(lista_ebar)
+    lista_mbar = [('m', E_range, z, 4, True, params,nsi) for z in z_range]
+    lista_ebar = [('e', E_range, z, 4, True, params,nsi) for z in z_range]
+    lista_m = [('m', E_range, z, 4, False, params,nsi) for z in z_range]
+    lista_e = [('e', E_range, z, 4, False, params,nsi) for z in z_range]
+    Pmm = _oscillogram_no_pool(lista_m)
+    Pem = _oscillogram_no_pool(lista_e)
[…]

### 2021-05-27 thesis/notebooks/sterile_parameter.py

@@ -1,0 +1,19 @@
+import sys,os
+sys.path.append('./src/')
+sys.path.append('./src/data')
+sys.path.append('./src/events')
+sys.path.append('./src/probability')
+import numpy as np
+import pickle
+from functions import ic_params
+from plotter import flux_oscillogram
+from IC.event_processing import list_of_params
+
+if __name__ == '__main__':
+    E_range = np.logspace(2,5,1)
+    z_range= np.linspace(-1,0,1)
+    dm_range = np.logspace(-1,2,1)
+    s24_range = np.logspace(-2,0,1)
+    params = list_of_params(ic_params, dm_range,s24_range)
+    res = flux_oscillogram(E_range, z_range, params, nsi=False)
+    pickle.dump(res,open('./pre_computed/sterile_animation.p','wb'))

### 2021-05-27 thesis/notebooks/sterile_parameter.py
update

@@ -10,10 +10,10 @@ from plotter import flux_oscillogram
 from IC.event_processing import list_of_params
 
 if __name__ == '__main__':
-    E_range = np.logspace(2,5,1)
-    z_range= np.linspace(-1,0,1)
+    E_range = np.logspace(2,5,200)
+    z_range= np.linspace(-1,0,200)
     dm_range = np.logspace(-1,2,1)
-    s24_range = np.logspace(-2,0,1)
+    s24_range = np.logspace(-2,0,100)
     params = list_of_params(ic_params, dm_range,s24_range)
     res = flux_oscillogram(E_range, z_range, params, nsi=False)
     pickle.dump(res,open('./pre_computed/sterile_animation.p','wb'))

### 2021-05-28 article/article.tex
update

@@
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}.
-The results are shown in Fig.~\ref{fig:IC_NO} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
 
@@
     \end{center}
-   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years. We compare the NSI event count with $\emt=-0.01$
-    to the standard interaction count}\label{fig:event_pulls} 
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}\label{fig:event_pulls} 
 \end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better

### 2021-05-28 src/events/IC/main.py

@@ -47,46 +47,46 @@ def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shif
         flux_mbar = get_flux('mbar',Et_mesh,zr_mesh,interp_flux)
 
     if not null:
-        try:
-            Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
-        except KeyError:
-            Pmm = generate_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim,nsi=nsi, save=False)
+        #try:
+        #    Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
+        #except KeyError:
+        Pmm = generate_probabilities('m','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim,nsi=nsi, save=False)
             #gather_specific_prob('Pmm',npoints,E_index,z_index,update=True,ndim=ndim)
             #Pmm = get_probabilities('m', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
 
-        try:
-            P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
-        except KeyError:
-            P_amam = generate_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim,nsi=nsi, save=False)
+        #try:
+        #    P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
+        #except KeyError:
+        P_amam = generate_probabilities('m','m',Et,zr,E_index, z_index, params,True,npoints,ndim=ndim,nsi=nsi, save=False)
             #gather_specific_prob('Pamam',npoints,E_index,z_index,update=True,ndim=ndim)
             #P_amam = get_probabilities('m', 'm', E_index,z_index,params,True,npoints,ndim=ndim)
         
-        try:
-            Pem = get_probabilities('e', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
-        except KeyError:
-            Pem = generate_probabilities('e','m',Et,zr,E_index, z_index, params,False,npoints,ndim=ndim,nsi=nsi, save=False)
+        #try:
+        #   Pem = get_probabilities('e', 'm', E_index,z_index,params,False,npoints,ndim=ndim)
+        #except KeyError:
[…]

### 2021-05-28 src/events/IC/make_sterile_events.py

@@ -43,7 +43,8 @@ if __name__ == '__main__':
 
     from multiprocessing import Pool
     p = Pool()
-    data = [(i,j,0.99, args.N,p, [False, 0, 0],False, False,False,4) for p in param_list for i in range(13) for j in range(20)]
+    data = [(i,j,alpha, args.N,p, [False, 0, 0],False, False,False,4) for p in param_list for i in range(13) for j in range(20)]
     H1_events_list = p.starmap(get_events, data)
     p.close()
+    H1_events_list = np.array(H1_events_list).reshape(len(dm41_range)*len(s24_range),13,20)
     pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}.p','wb'))

### 2021-05-28 thesis/notebooks/sterile_parameter.py

@@ -12,8 +12,9 @@ from IC.event_processing import list_of_params
 if __name__ == '__main__':
     E_range = np.logspace(2,5,200)
     z_range= np.linspace(-1,0,200)
-    dm_range = np.logspace(-1,2,1)
-    s24_range = np.logspace(-2,0,100)
+    dm_range = np.logspace(-2,1,1)
+    s24_range = np.logspace(-2,0,1)
     params = list_of_params(ic_params, dm_range,s24_range)
-    res = flux_oscillogram(E_range, z_range, params, nsi=False)
-    pickle.dump(res,open('./pre_computed/sterile_animation.p','wb'))
+    print(params)
+    #res = flux_oscillogram(E_range, z_range, params, nsi=False)
+    #pickle.dump(res,open('./pre_computed/sterile_animation.p','wb'))

### 2021-05-28 thesis/tex/oscillations.tex
update

@@
-\documentclass[draft=True]{thesis}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{graphicx, slashed}
-\usepackage[utf8]{inputenc}
-%\usepackage{hyperref}
-\usepackage{xr-hyper}
-\externaldocument{SM}
-\input{commands}
-\begin{document}
+%\input{commands}
+%\begin{document}
 
-\section{Neutrino Masses and Oscillations}\label{ch:oscillation}
-\subsection{Neutrino mixing and the PMNS matrix}
+\section{Neutrino Mixing}\label{ch:oscillation}
+%TODO: small intro about PMNS and justification of oscillations
+\subsection{Mass Generation}
 As we saw in Eq.~\ref{eq:j_CC}
@@
 It has the usual properties of the conventional left-handed neutrino such as hypercharge and color zero.
-Moreover, since the electroweak gauge group $\t{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, it transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
+Moreover, since the electroweak gauge group $\text{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, it transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
 This neutrino is \emph{sterile} since it doesn't participate any of the SM interactions.
@@
 \end{align}
-Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$. We will refer to the matrix $U$ built by the components $U{k \alpha}$ as the
-Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix.%TODO: source
+
 Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$. 
+Thus, neutrino interactions still conserve lepton number.
 However, the Higgs-lepton Yukawa Lagrangian 
@@
 There is no transformation that leaves both the interaction and kinetic Lagrangian invariant.
+
+Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$. We will refer to the matrix $U$ built by the components $U_{k \alpha}$ as the
+Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix. %TODO: source
 We now have 
@@
 %TODO: add segue
-\subsection{Neutrino oscillations}
-Since we now know how the neutrino mass and flavor eigenstates combine (namely, through the PMNS matrix $U$), and have an expression for the flavor interaction with 
-the neutrinos charged lepton partner, we are now ready to study the flavor oscillations themselves.
+\subsection{Neutrino Propagation}
+Since we now know how the neutrino mass and flavor eigenstates combine, and have an expression for the flavor interaction with 
+the neutrino's charged lepton partner, we are now ready to study the flavor oscillations themselves.
 
-Now, the Fourier expansion of the field operator $\bar{\nu}_{k L}$ in Eq.~\ref{eq:j_CC3} contains creation operators $a^\dagger_{\nu_k}$
+Now, the Fourier expansion of the field operator $\bar{\nu}_{k L}$ in the current of Eq.~\ref{eq:j_CC3} contains creation operators $a^\dagger_{\nu_k}$
 of massive neutrinos with mass $m_k$. This means that the summation over the mass index $k$ constructs a flavor neutrino, which interacts with the charged lepton field $\ell_{\a L}$.
@@
 \end{align}
-Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse? We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
+Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse?
+ We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
 \begin{align}\label{eq:osc_k}
@@
 We assume the neutrino masses $m_k$ to be extremely small compared to their associated energies $E_k$. 
-Thus, $v\approx 1$, and $\abs{\vec{p}} \approx E$ making the energy-dispersion relation of Eq.~\ref{eq:disp} to first order:
+Thus, $v\sim 1$, and $\abs{\vec{p}} \sim E$ making the energy-dispersion relation of Eq.~\ref{eq:disp} to first order:
 \begin{align}\label{eq:ultra_rel}
@@
 We thus write 
-\begin{align}\label{eq:Pab}
+\begin{align}\label{eq:Pab}%TODO: shorten?
     P_{\ab} &= \sum_{k,j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
@@
 
-\subsection{Matter effects}
+\subsection{Effective Matter Potentials}
+
 \begin{figure}
-    \includegraphics[width=0.2\textwidth]{figures/w-boson.pdf} 
-    \hspace{2cm}
-    \includegraphics[width=0.23\textwidth]{figures/z-boson.pdf}
-    \caption{\emph{Left panel:} Charged current weak interaction between an electron neutrino and an electron,
-    mediated by either a $W^+$ or $W^-$ boson. \emph{Right panel:} Neutral current weak interaction between a neutrino of any flavor and a Earth-like fermion,
+    \centering
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=1\textwidth]{figures/w-boson.pdf} 
+        \caption{Charged current weak interaction between an electron neutrino and an electron,
+        mediated by either a $W^+$ or $W^-$ boson.}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=1\textwidth]{figures/z-boson.pdf} 
+        \caption{Neutral current weak interaction between a neutrino of any flavor and a Earth-like fermion,
         mediated by a neutral $Z$ boson.}
-    \label{fig:w_and_z}
+    \end{subfigure}%TODO: they are different sizes
+    \caption{Feyman diagrams showing the two interactions that neutrinos participate in according to the Standard Model.}\label{fig:w_and_z}
 \end{figure}
@@
 the $Z$ boson is responsible for $V_{NC}$. Our task is now to find expressions for these.
-
-\subsection{Effective matter potentials}
 
@@
 \begin{align}
-    \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T) &= \int \dd p_e^3\, f(E_e,T) (\gamma^0 E_e - \vec{p}_e \cdot \vec{gamma}) \nonumber \\
+    \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T) &= \int \dd p_e^3\, f(E_e,T) (\gamma^0 E_e - \vec{p}_e \cdot \vec{\gamma}) \nonumber \\
                                               &= \int \dd p_e^3\, f(E_e,T) \gamma^0 E_e \nonumber \\
@@
     V_{CC} = \sqrt{2}G_F N_e\,, \quad H^{CC}\ket{\nu_k} = V_{CC}\ket{\nu_k}\,.
-\end{align}
+\end{align}%TODO: write H_{CC} instead
 Here we see a crucial difference between the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H^{CC}$, namely
@@
 \end{align}
-where the electrical neutrality condition allows us to simply sum the vectorial couplings together, cancelling the electron and proton contributions (and hence, also the mixing angle dependence).
-\subsection{Matter oscillations}
+where the electrical neutrality condition allows us to simply sum the vectorial couplings together, cancelling the electron and proton contributions (and hence, also the Weinberg angle dependence).
+
+\subsection*{Matter oscillations}
 Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors.
@@
 \end{align}
-Unitarity gives $ \sum_k U_{\b k} U^*_{\eta k} = \delta_{\eta\b}$, and the first term in the last step of Eq.~\ref{t1} becomes
+Unitarity gives $ \sum_k U_{\b k} U^*_{\eta k} = \delta_{\eta\b}$, and the first term in the last step of Eq.~\ref{eq:t1} becomes
 \begin{align}
@@
 \end{align}
-we can write the Schrödinger equation on matrix form ($i\dv{}{x}\Psi_\a = H_F \Psi_\a$) and compare it with Eq.~\ref{eq:components} to see that the flavor Hamiltonian takes the form 
+we can write the Schrödinger equation on matrix form ($i \dv{}{x}\Psi_\a = H_F \Psi_\a$) and compare it with Eq.~\ref{eq:components} to see that the flavor Hamiltonian takes the form 
 \begin{align}\label{eq:H_3gen}
@@
         \end{pmatrix}\,. 
-\end{align}
+\end{align}%TODO: this is equal to the analytic expression for n_e=0
 This is the three-flavor neutrino oscillation Hamiltonian that we will solve numerically to obtain the evolution of $\Psi_\a$, whose squared components
@@
     U = \begin{pmatrix}
-        U_{e e} & U_{e\mu} & U_{e\tau} \\
-        U_{\mu e} & U_{\mu \mu} & U_{\mu \tau} \\
-        U_{\tau e} & U_{\tau \mu} & U_{\tau \tau}
+        U_{e 1} & U_{e2} & U_{e3} \\
+        U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
+        U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
     \end{pmatrix} 
@@
 the most abundant. This means we will be able to stringently constrain parameters relating to $\nm \to \nt$ oscillations. 
+%TODO: write more about smallness of Ue3 and write about parametrization of U. maybe about su2
 
-\end{document}
+%\end{document}

### 2021-05-28 thesis/tex/sterileTheory.tex
update

@@
-\documentclass{article}
-\input{commands}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, subcaption}
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{xr-hyper}
-%\externaldocument{sterile}
+% \documentclass{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \usepackage{subcaption}
+% \input{commands}
 
-\begin{document}
+% \begin{document}
 \section{The Sterile State}\label{sec:anomalies}
@@
 
+\subsection{The Hamiltonian}
 The inclusion of the sterile neutrino in the Hamiltonian is straightforward. We extend the PMNS matrix to incorporate the new flavor and mass eigenstates: 
@@
 
-Now,the interaction with matter requires a careful reconsideration of the matter potential. We start of with the unaltered potential matrix. 
+Now, the interaction with matter requires a careful reconsideration of the matter potential. We start of with the unaltered potential matrix. 
 Just as with the PMNS matrix, we extend this to $4\times4$:
@@
 
-\section{Sterile Signals}
+\subsection{Sterile Signals}
 Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
@@
 \begin{figure}
+    \centering
     \begin{subfigure}{0.45\textwidth}
@@
     \end{subfigure}
-\end{figure}
+\end{figure} %TODO: better captions
 
@@
 We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
+%TODO: more? mention that Pmm=1 at TeV for 3+0
 
-\newpage
-\bibliographystyle{elsarticle-num}
-\bibliography{ref}
-\end{document}
+% \newpage
+% \bibliographystyle{elsarticle-num}
+% \bibliography{ref}
+% \end{document}

### 2021-05-28 thesis/tex/DCtheory.tex
update

@@
-\documentclass[draft=True]{thesis}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{graphicx, slashed, siunitx}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
-\input{commands}
-\begin{document}
-\section{DeepCore}
+% \documentclass[draft=True]{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \usepackage{graphicx, slashed, siunitx}
+% \usepackage[utf8]{inputenc}
+% \usepackage{xr-hyper}
+% \input{commands}
+% \begin{document}
+\section{DeepCore}\label{ch:DCmethod}
 In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
@@
 \section{PINGU}
-The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}.
-We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+The methodology behind the PINGU simulations are the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
 However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
-As with the DeepCore data, the PINGU MC is divided into eight 
+As with the DeepCore data, the PINGU Monte Carlo is divided into eight 
 $\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
@@
 \end{align}
-\bibliographystyle{nature}
-\bibliography{ref.bib}
-\end{document}
+% \bibliographystyle{nature}
+% \bibliography{ref.bib}
+% \end{document}

### 2021-05-28 thesis/tex/ICintro.tex
update

@@
-\documentclass{thesis}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{graphicx, slashed, siunitx, subcaption}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
-\input{commands}
-\begin{document}
+% \documentclass{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \usepackage{graphicx, slashed, siunitx, subcaption}
+% \usepackage[utf8]{inputenc}
+% \usepackage{xr-hyper}
+% \input{commands}
+% \begin{document}
 \section{Neutrino detection}
@@
 \begin{figure}\label{fig:array}
-    \includegraphics[width=0.5\textwidth]{figures/icecube2.png}\caption{View of the full IceCube array}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/icecube2.png}
+    \caption{View of the full IceCube array}
 \end{figure}
 
-In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The "Precision IceCube Next Generation Upgrade" is an upgrade that will 
+In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The `Precision IceCube Next Generation Upgrade' is an upgrade that will 
 supplement DeepCore, i.e. boosing the capabilites of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
@@
 also apply to PINGU except where noted. However, we treat the PINGU detector as independent of the DeepCore experiment.
-\bibliographystyle{nature}
-\bibliography{ref.bib}
-\end{document}
+
+\begin{figure}[t]\label{fig:flux_aeff}
+    \includegraphics[width=0.5\textwidth]{figures/flux.pdf}\hspace{-1cm}
+    \includegraphics[width=0.5\textwidth]{figures/aeff.pdf}
+    \vspace{-2.5cm}\caption{\emph{Left panel:} Interpolated South Pole atmospheric flux with data from~\cite{hondaArticle}.
+    \emph{Right panel:} Interpolated IceCube effective area with data from~\cite{ICaeff}.}
+\end{figure}
+
+\subsection{Atmospheric neutrino flux}
+Atmospheric neutrinos originates from cosmic rays composed of protons interacting with nuclei in the atmosphere.
+These interactions ultimately produces pions, which decay as 
+\begin{align}\label{eq:pion}
+    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
+    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
+\end{align}
+In the muonic decay channel, muons are emitted which will be detected by the IceCube detector. A part of the 
+uncorrelated systematic error comes from this \emph{muon background}, i.e. events misclassified as muons from 
+$\nm$ interactions rather than from pion decay. Moreover, the atmospheric flux is often associated with a large error.
+In this work, we will use a flux normalization error of 24\%, and a zenith slope error of 4\%~\cite{hondapaper}.
+
+The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}
+The flux data is binned in $\ztrue$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
+The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
+from the table for clarity. 
+We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. Kaons can decay into neutral pions, which in turn 
+can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities on the form 
+$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.
+
+Interpolating the data yields makes us capable of returning all four necessary fluxes for a given true energy and true zenith.
+The result is shown in Fig.~\ref{fig:flux_aeff}.
+
+\begin{table}[h]\label{table:flux}
+    \begin{center}
+        \begin{tabular}{lcccccc}
+            \hline \hline
+            $\Etrue$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\ztrue$\\\\
+            \hline
+            27825 &  \SI{6.06e-12}{} &  \SI{3.17e-12}{} &  \SI{1.56e-13}{} &  \SI{1.04e-13}{} &   [-0.2, -0.1] \\
+            247707 &  \SI{5.94e-16}{} &  \SI{2.92e-16}{} &  \SI{1.36e-17}{} &  \SI{8.12e-18}{} &   [-0.7, -0.6] \\
+                22 &  \SI{3.33e-02}{} &  \SI{2.78e-02}{} &  \SI{9.57e-03}{} & \SI{7.15e-03}{} &   [-0.3, -0.2] \\
+            432876 &  \SI{5.19e-17}{} &  \SI{2.32e-17}{} &  \SI{1.46e-18}{} & \SI{9.83e-19}{} &   [-1.1, -1.0] \\
+            64280 &  \SI{1.58e-13}{} &  \SI{8.10e-14}{} &  \SI{3.49e-15}{} &  \SI{2.21e-15}{} &   [-0.4, -0.3] \\
+            \hline \hline
+        \end{tabular}
+    \end{center}
+    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}
+\end{table}
+
+\subsection{Event reconstruction}
+After an event has occurred, the IceCube algorithms process the data coming from the detector to \emph{reconstruct} the event.
+This means that, given the parameters recorded by the detector, what are their "true" values?
+We are interested in two variables: the energy and the direction.
+Each event is tagged with a probable energy and zenith angle, called the recostructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
+The collaboration then uses numerous sophisticated methods to backtrack the reconstructed parameters to the true parameters.
+So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true and reconstructed energy and zenith angle.
+The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the determination of that neutrino's "actual" flux and cross-section (because this is what nature sees).
+
+How do we then translate between the reconstructed and true parameters?
+In this work, we are using two different methods, which are based on the form of data available to us.
+They will be outlined in Sec.\ref{ch:ICmethod} and Sec.~\ref{ch:DCmethod}.
+
+% \bibliographystyle{nature}
+% \bibliography{ref.bib}
+% \end{document}

### 2021-05-28 thesis/tex/ICtheory.tex
update

@@
-\documentclass{thesis}
-\usepackage[margin=0.5in]{geometry}
-\input{commands}
-\begin{document}
-\begin{figure}[t]\label{fig:flux_aeff}
-    \includegraphics[width=0.5\textwidth]{figures/flux.pdf}\hspace{-1cm}
-    \includegraphics[width=0.5\textwidth]{figures/aeff.pdf}
-    \vspace{-2.5cm}\caption{\emph{Left panel:} Interpolated South Pole atmospheric flux with data from~\cite{hondaArticle}.
-    \emph{Right panel:} Interpolated IceCube effective area with data from~\cite{ICaeff}.}
-\end{figure}
+% \documentclass{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \input{commands}
+% \begin{document}
 
-\section{Atmospheric neutrino flux}
-Atmospheric neutrinos originates from cosmic rays composed of protons interacting with nuclei in the atmosphere.
-These interactions ultimately produces pions, which decay as 
-\begin{align}\label{eq:pion}
-    \pi^+ &\to \mu^+ + \nm\,, \quad \pi^- \ to \mu^- + \anm \nonumber \\
-    \pi^+ &\to e^+ + \ne\,, \quad \pi^- \ to e^- + \ane\,.
-\end{align}
-In the muonic decay channel, muons are emitted which will be detected by the IceCube detector. A part of the 
-uncorrelated systematic error comes from this \emph{muon background}, i.e. events misclassified as muons from 
-$\nm$ interactions rather than from pion decay. Moreover, the atmospheric flux is often associated with a large error.
-In this work, we will use a flux normalization error of 24\%, and a zenith slope error of 4\%. In more sophisticated 
-models, one can also include the pion to kaon flux uncertainty.
-
-The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}
-The flux data is binned in $\ztrue$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
-The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
-from the table for clarity. 
-We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. Kaons can decay into neutral pions, which in turn 
-can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities on the form 
-$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.
-
-Interpolating the data yields makes us capable of returning all four necessary fluxes for a given true energy and true zenith.
-The result is shown in Fig.~\ref{fig:flux_aeff}.
-
-\begin{table}[h]\label{table:flux}
-    \begin{center}
-        \begin{tabular}{lcccccc}
-            \hline \hline
-            $\Etrue$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\ztrue_{min}$ &$\ztrue_{max}$\\
-            \hline
-            27825 &  \SI{6.06e-12}{} &  \SI{3.17e-12}{} &  \SI{1.56e-13}{} &  \SI{1.04e-13}{} &   -0.2 &   -0.1 \\
-            247707 &  \SI{5.94e-16}{} &  \SI{2.92e-16}{} &  \SI{1.36e-17}{} &  \SI{8.12e-18}{} &   -0.7 &   -0.6 \\
-                22 &  \SI{3.33e-02}{} &  \SI{2.78e-02}{} &  \SI{9.57e-03}{} & \SI{7.15e-03}{} &   -0.3 &   -0.2 \\
-            432876 &  \SI{5.19e-17}{} &  \SI{2.32e-17}{} &  \SI{1.46e-18}{} & \SI{9.83e-19}{} &   -1.1 &   -1.0 \\
-            64280 &  \SI{1.58e-13}{} &  \SI{8.10e-14}{} &  \SI{3.49e-15}{} &  \SI{2.21e-15}{} &   -0.4 &   -0.3 \\
-            \hline
-        \end{tabular}
-    \end{center}
-    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}
-\end{table}
-
-\section{Event reconstruction}
-After an event has occurred, the IceCube algorithms process the data coming from the detector to \emph{reconstruct} the event.
-This means that, given the parameters recorded by the detector, what are their "true" values?
-We are interested in two variables: the energy and the direction.
-Each event is tagged with a probable energy and zenith angle, called the recostructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
-The collaboration then uses numerous sophisticated methods to backtrack the reconstructed parameters to the true parameters.
-So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true and reconstructed energy and zenith angle.
-The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the determination of that neutrino's "actual" flux and cross-section (because this is what nature sees).
-
-How do we then translate between the reconstructed and true parameters? In this work, we are using two different methods, which are based on the form of data available to us.
-
-\section{IceCube event count}\label{ch:ICmethod}
-As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact in the ice to form their charged leptons.
-We now are interested in the effective area, i.e.~the detector area that the lepton "sees".
-The effective area, $\Aeff$, depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section.
+\section{IceCube}\label{ch:ICmethod}
+As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact with charged lepton in the ice. We now are interested in the effective area $\Aeff$, 
+i.e.~the cross-section of the detector that the lepton is exposed to.
+$\Aeff$ depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section.
 Fortunately, the binned $\Aeff$ is provided to us by the collaboration~\cite{ICaeff}.
@@
 
-\begin{table}\label{table:aeff}
+\begin{table}[h]\label{table:aeff}
+    \centering
     \begin{tabular}{lrrrrr}
@@
             398 &      501 &  -0.73 &  -0.72 &   0.0555 \\
-        \hline
+        \hline \hline
         \end{tabular}
-    \caption{IceCube effective area from~\cite{ICaeff}}
+    \caption{IceCube-86 effective area from~\cite{ICaeff}}
 \end{table}
 
-Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$. Thus, it is not flavor dependent.
+Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$.
 Just as with the fluxes, we interpolate this in $\Etrue,\ztrue$ and show the result %TODO aeff interpolation
@@
 
-\begin{table}\label{table:IC_MC}
+\begin{table}[h]\label{table:IC_MC}
+    \centering
     \begin{tabular}{lrrrrr}
@@
          13 &   988 & -0.370746 &   1861 & -0.367922 \\
-         \hline
+         \hline \hline
   \end{tabular}
@@
 \begin{align}\label{eq:ICevents}
-    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
-    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
+    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
+    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
+    \,,
 \end{align}
@@
 
-\begin{figure}[!tb]\label{fig:IC_MC_gpr}
+\begin{figure}[!tb]
     \begin{center}
@@
     \end{center}
-    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}.
-Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
+    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}.
+    Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.}\label{fig:IC_MC_gpr}
  \end{figure}
@@
 The latest available data collected and processed by the collaboration contains 305,735 muon track events, collected over eight years~\cite{IC2020}. 
-\newpage
-\bibliographystyle{nature}
-\bibliography{ref.bib}
-\end{document}
+%The data has 13 logarithmically spaced bins in $\Ereco \in \[500,9976\] \si{GeV}$, and 20 linear bins in $\zreco \in \[-1,0\]$. The data is shown in Fig.~\ref{fig:IC_data}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/IC_data.pdf}
+    \caption{IceCube track events from~\cite{IC2020}}\label{fig:IC_data}
+\end{figure}
+
+\subsection*{Monte Carlo normalization}
+Independent researchers outside of the IceCube collaboration will not be able to more persicely
+simulate the detector. The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this 
+section is to come as close as we can to their Monte Carlo simulations. After we are confident that 
+our code displays the same overall features as the `offical', we normalize our results $N_{ij}^\text{sim}$ as 
+\begin{align}\label{eq:MC_norm}
+    N_{ij} = \frac{N_{ij}^\text{null}}{N_{ij}^\text{MC}} N_{ij}^\text{sim}\,.
+\end{align}
+For each bin $i,j$, we then obtain a correction factor which contains information that we are unable
+to obtain or sufficiently incorporate. One example of such information is the systematic errors of the DOMs.
+Recent IceCube data releases do not include such information. Since the systematic errors are affecting the 
+event count on a bin-by-bin basis, they can in theory drastically modify the binned results. Another example of
+an error source what will be remedied by this method is the flux. We are using a fairly simple model of the atmospheric 
+flux that excludes prompt flux. The IceCube collaboration use several different flux models which are initialized 
+by a parametrization of the cosmic ray flux.\footnote{Included in the cosmic ray models are e.g. the pion to kaon 
+ratio, which are often used as a nuisance parameter. By not being able to include this in our error analysis, our method will 
+be limited to only consider the overall flux normalization, rather than the components that produce the flux in the first place.}
+%TODO: maybe rambling?
+
+In Fig.~\ref{fig:IC_MC_norm}, we present the Icecube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
+with our null hypothesis times a constant factor.  We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
+correction factors of Eq.~\ref{eq:MC_norm}. We now arrive to our final event count
+\begin{align}\label{eq:Nth}
+    N_{ij} &= \frac{N_{ij}^\text{null}}{N_{ij}^\text{MC}} T \sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
+    \int_{E^t_{min}}^{E^t_{max}} R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta\, \dd E^t
+    \,,
+\end{align}
+with $E^t_{min}$, $E^t_{max}$, and $R(E^r,E^t)$ taken from the Gaussian process regressor.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/IC_MC_norm.pdf}
+    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as ´Null' in the plots.}\label{fig:IC_MC_norm}
+\end{figure} 
+%TODO:fill more
+% \newpage
+% \bibliographystyle{nature}
+% \bibliography{ref.bib}
+% \end{document}

### 2021-05-28 thesis/tex/SM.tex
update

--- 2021-03-24 latex/SM.tex
@@
-\documentclass[twocolumn]{article}
-\input{commands.tex}
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
-%\externaldocument{sterile}
+% \input{commands}
 
-\begin{document}
+% \begin{document}
 \section{The Standard Model}\label{ch:SM}
@@
 Each vector boson has one corresponding generator in the group that describes the force. 
-The strong charge is mediated by eight gluons, which correspond to the eight generators of $\t{SU}(3)_C$.
-The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$ and the massless boson $\gamma$, which constitute the generators of $\t{SU}(2)_L$.
-Finally, the massless gauge boson, the photon, is the generator of $\t{U}(1)_Y$.
+The strong charge is mediated by eight gluons, which correspond to the eight generators of $\text{SU}(3)_C$. 
+The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$ and the massless boson $\gamma$, 
+which constitute the generators of $\text{SU}(2)_L$. Finally, the massless gauge boson, the photon, is the generator of $\text{U}(1)_Y$. 
 Together, these groups make up the local symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
 This symmetry group determines the form of the three coupling constants of nature, whose numerical values but be experimentally derived. 
-Thus, the vector bosons are wholly constrained by the symmetry group.
-However, the scalar bosons and fermions are free as long as they belong to representations of the symmetry group.
+Thus, the vector bosons are wholly constrained by the symmetry group. However, the scalar bosons and fermions are free as long as they
+ belong to representations of the symmetry group.
 
 The subscript of each group denotes by which mechanism that force is mediated.
-The gluons mediate the strong force through interactions of color, $C$.
-The weak force only sees left-handed particles, $L$.
+The gluons mediate the strong force through interactions of color, emphasized with subscript $C$.
+The weak force only sees left-handed particles,
+which we distinguish wityh the subscript $L$.
 And the electroweak interaction that a particle undergoes is determined by its hypercharge, $Y$.
@@
 \end{align}
-where each fermion field and matrix have an implied $L$ subscript which was dropped for clarity.
+where each fermion field and matrix have an implied $L$ subscript, which was dropped for clarity.
 The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$.
@@
 The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. 
-%\bibliographystyle{apalike}
-%\bibliography{ref}
-\end{document}
+%TODO:more here about SM and lepton mixing?
+% \bibliographystyle{apalike}
+% \bibliography{ref}
+% \end{document}

### 2021-05-28 thesis/tex/nsiResults.tex
update

@@
-\documentclass[draft=True]{thesis}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{graphicx, slashed, siunitx}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
-\input{commands}
-\begin{document}
-\section{$\chi^2$ minimization}
-For our analyses, we define our $\chi^2$ as
-\begin{align} \label{eq:ICchisq}
-    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
-    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
+% \documentclass[draft=True]{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \usepackage{graphicx, slashed, siunitx}
+% \usepackage[utf8]{inputenc}
+% \usepackage{xr-hyper}
+% \input{commands}
+% \begin{document}
+\section{Non-standard Interactions}
+\subsection{$\chi^2$ minimization}
+The $\chi^2$ takes the same form as in Eq.~\ref{eq:chisq}, namely 
+\begin{align} \label{eq:chisq2}
+    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ij} \frac{\left(N^\text{th}-N^\text{data}\right)_{ij}^{2}}
+    {\left(\sigma^\text{data}_{ij}\right)^{2} + \left(\sigma^\text{syst}_{ij}\right)^{2}}+ 
     \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
 \end{align}
-where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
-$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
-We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}.
-The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
-
-For IceCube, the event count takes the form
+Just as with the sterile analysis, the IceCube event count takes the form 
 \begin{align}
-    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
+    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,.
 \end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents} Here, we allow the event distribution to rotate around the median zenith of $-0.5$.
-
-For DeepCore and PINGU, the event count takes the form
+For DeepCore and PINGU however, the event count takes the form
 \begin{align}
@@
 muon background estimate~\cite{DC2019data}.
-\end{document}
+\subsection{Constraining Parameters}
+% \end{document}

### 2021-05-28 thesis/tex/nsiTheory.tex
update

@@
-\documentclass{thesis}
-\usepackage[margin=0.5in]{geometry}
-\input{commands}
-\usepackage{siunitx, graphicx}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
+% \documentclass{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \input{commands}
+% \usepackage{siunitx, graphicx}
+% \usepackage[utf8]{inputenc}
+% \usepackage{xr-hyper}
 
-\begin{document}
-\section{How NSIs alter the matter potential}
+% \begin{document}
+\section{Non-standard interactions}
+%TODO: moreintro. incompleteness of SM
+Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
+\begin{align}
+    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
+\end{align} 
+in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
+two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
+we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.
+
+\subsection{Altering the Matter Potential}
 Up until now, we have only considered neutrino interactions with electrons, protons, and neutrons. Now we extend this to include we can extend this to include 
@@
 any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
-Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
-\begin{align}
-    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
-\end{align} 
-in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
-two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
-we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.
 
@@
 
-\section{Non-standard interactions in IceCube}
+\subsection{NSIs in IceCube}
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
@@
 Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
-In ~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
+In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
 in the DeepCore region of rapid oscillations, where mixing is more violent. 
@@
 
-\section{Non-standard interactions in DeepCore and PINGU}
+\subsection{NSIs in DeepCore and PINGU}
 Now we repeat our proability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
@@
 
-\end{document}
+% \end{document}

### 2021-05-28 thesis/tex/sterileResults.tex
update

--- 2021-05-26 thesis/tex/sterileResults.tex
@@
-\documentclass{thesis}
-\usepackage[margin=0.5in]{geometry}
-\input{commands}
+% \documentclass{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \input{commands}
 
-\begin{document}
+% \begin{document}
+\section{The Sterile Hypothesis}
+With the null ($3\nu$ hypothesis) normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
+First, let us see how the collected data from Fig.~\ref{fig:IC_data} deviates from the predicted $3\nu$ oscillations.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/IC_rates.pdf}
+    \caption{}\label{fig:IC_rates}
+\end{figure}
+Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
+for neutrinos close to double-digit \si{\TeV} values. In zenith, the data only deviates $\pm 1\%$. Recalling the \si{\TeV} disappearance from 
+Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. Thus, we expect the best fitting 
+sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
+that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.
 
-\end{document}
+\subsection{$\chi^2$ minimization}
+For our analyses, we define our $\chi^2$ as
+\begin{align} \label{eq:chisq}
+    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ij} \frac{\left(N^\text{th}-N^\text{data}\right)_{ij}^{2}}
+    {\left(\sigma^\text{data}_{ij}\right)^{2} + \left(\sigma^\text{syst}_{ij}\right)^{2}}+ 
+    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
+\end{align}
+where we minimize over the model parameters $\hat{\theta}$, the penalty terms $\alpha$ and $\beta$.
+$N_{ij}^\text{th}$ is the expected number of events from theory, and $N_{ij}^\text{data}$ is the observed number of events in that bin. 
+We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
+The observed event number has an associated Poissonian uncertainty $\sigma_{ij}^\text{data} = \sqrt{N_{ij}^\text{data}}$.
+For IceCube, the event count takes the form
+\begin{align}
+    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
+\end{align}
+with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}.
+Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate with angle $\beta$ around the median zenith angle of $\zreco = -0.5$.
+We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a percentage of our own choosing,
+typically a value between 0 and 20 \%.
+
+The minimization of Eq.~\ref{eq:chisq} simply returns a value for each set of model parameters. We use this value to quantify to what extent
+our theoretical simulations $N^\text{th}_{ij}$ agree with the data $N^\text{data}_{ij}$ within the error bounds provided by $\sigma_a,\sigma_b,$ and $f$.
+We then select the set of $\chi^2$ values which are the smallest and our allowed parameters are then their associated $\hat{\theta}$.
+We then translate the $\chi^2$ distribution by subtracting the best-fit point, and analyze $\Delta \chi^2 = \chi^2 - \chi^2_{min}$.
+From the $\chi^2$-distribution, one can show that the $90\%$ confidence level has a value of $2.71$ for two degrees of freedom. When slicing through the 
+two-dimensional grid of $\Delta \chi^2$ at this level, we then obtain a contour plot that tells us what regions are within our $90 \%$ and what regions are not.
+
+\subsection{Sterile Mass and Mixing}
+Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
+Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the sterile hypothesis.
+The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
+$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO:double check these
+The contour plot shown in Fig.~\ref{fig:s24_contour} divides the parameter space into two regions.
+To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
+those parameter pairs can be excluded at a certain confidence level.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/final_rate_plot.pdf}
+    \caption{}\label{fig:final_rate_plot}%TODO: update
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/s24_contour.pdf}
+    \caption{}\label{fig:s24_contour}%TODO: update
+\end{figure}
+%\end{document}

### 2021-05-28 src/events/IC/event_processing.py

@@ -41,7 +41,7 @@ Ereco_full = 500*10**np.linspace(0.0,1.3,14)
 Ereco_full_midpoints = Ereco_full[0:-1] +np.diff(Ereco_full)/2 #For scatter plot
 
 Ereco = Ereco_full[EFrom:ETo+1]
-Ereco_midpoints= Ereco_full_midpoints[3:14]
+Ereco_midpoints= Ereco_full_midpoints[EFrom:ETo+1]
 
 zreco_full = np.linspace(-1,0,21)
 zreco_full_midpoints = zreco_full[0:-1] +np.diff(zreco_full)/2 #For scatter plot
@@ -74,6 +74,10 @@ def count_plots(H1,H0):
     fig, ax = plt.subplots(2,2, sharex='col', squeeze=True,gridspec_kw={'width_ratios': [3, 3], 'height_ratios':[3,1]}, figsize=(12,8))
     ax = ax.flatten()
 
+    label_size = 15
+    tick_size = 15
+    legend_size=13
+
     ax[0].scatter(Ereco_midpoints, IC_per_E, label='IC data', s=10, color='black', zorder=10)
     ax[0].step(Ereco, H1_per_E_hist, label='Sterile',lw=3, where='post', color='blue')
     ax[0].step(Ereco, H0_per_E_hist, label='Null',   lw=1.5, where='post', color='red')
@@ -92,23 +96,28 @@ def count_plots(H1,H0):
 
 
     ax[0].set_xlim((Ereco.min(),Ereco.max()))
-    ax[0].set_ylabel('Counts')
+    ax[0].set_ylabel('Counts', fontsize=label_size)
     ax[0].set_xscale('log')
     ax[0].set_yscale('log')
 
     ax[2].set_xscale('log')
-    ax[2].set_xlabel(r'$E_\mu^{reco}$ [GeV]')
-    ax[2].set_ylabel('Ratio to Null')
+    ax[2].set_xlabel(r'$E^{reco}$ [GeV]', fontsize=label_size)
+    ax[2].set_ylabel('Ratio to Null', fontsize=label_size)
     ax[2].grid(True,which='both', axis='both', alpha=0.3)
 
     ax[3].set_xlim((zreco.min(),zreco.max()))
     ax[3].set_ylim(ax[2].get_ylim())
     ax[3].grid(True,which='both', axis='both', alpha=0.3)
-    ax[3].set_xlabel(r'$\cos{(\theta^{reco}_z)}$')
[…]

### 2021-05-31 thesis/tex/SM.tex
update

@@
-% \input{commands}
-
-% \begin{document}
+% \input{commands}\begin{document}
 \section{The Standard Model}\label{ch:SM}
-In order to describe the three forces of nature, we gather the mediators of each force -- the vector gauge bosons -- into gauge groups. 
-Each vector boson has one corresponding generator in the group that describes the force. 
+In order to describe the three forces of nature, we gather the mediators of each force -- the vector bosons -- into gauge groups. 
+Each vector boson has one corresponding generator, the set of which constitutes the group.
 The strong charge is mediated by eight gluons, which correspond to the eight generators of $\text{SU}(3)_C$. 
 The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$ and the massless boson $\gamma$, 
-which constitute the generators of $\text{SU}(2)_L$. Finally, the massless gauge boson, the photon, is the generator of $\text{U}(1)_Y$. 
-Together, these groups make up the local symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
-This symmetry group determines the form of the three coupling constants of nature, whose numerical values but be experimentally derived. 
-Thus, the vector bosons are wholly constrained by the symmetry group. However, the scalar bosons and fermions are free as long as they
- belong to representations of the symmetry group.
+which constitute the generators of $\text{SU}(2)_L$. Finally, the massless gauge boson, the photon, has a representation which is the generator of $\text{U}(1)_Y$.
 
@@
 The weak force only sees left-handed particles,
-which we distinguish wityh the subscript $L$.
+which we distinguish with the subscript $L$.
 And the electroweak interaction that a particle undergoes is determined by its hypercharge, $Y$.
-For example, the quarks all have a nonzero color and (hyper)charge, so they participate in the strong and electromagnetic interactions.
-If a given quark is left-handed, it will also feel the weak interaction.
+For example, the quarks all have a nonzero color and hypercharge,
+so they participate in the strong and electromagnetic interactions.
+If a quark is left-handed, it will also feel the weak interaction.
 The neutrinos on the other hand have neither charge nor color, so they are insivible to both the strong and electromagnetic force.
 
+Together, these groups make up the local symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
+This symmetry group determines the form of the three coupling constants of nature, whose numerical values must be experimentally measured. 
+Since the vector bosons are represented by the generators, they are wholly constrained by the symmetry group.
+However, the scalar bosons\footnote{The Standard Model only has one scalar boson: the Higgs boson.} and fermions are free as long as they
+belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. In this work,
+we will use this leniency to make drastic modifications to the Standard Model and examine to which extent they might be falsifiable.
+
 \subsection{Lepton mixing}
+In this section, we will see how the neutrinos interact with the charged leptons, which is the first stepping stone in our journey.
+
 In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
@@
 The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$.
-However, since we still operate under the SM framework, $\nu_\alpha$ is still massless, since no flavor rotation $V_{L}^{\ell \dagger}$ can make massless fields massive.
-
-The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. 
-%TODO:more here about SM and lepton mixing?
+However,
+$\nu_\alpha$ is still massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
+%TODO:more here about SM and lepton mixing? maybe about mass/massless particles. why does SM predict massless neutrinos, and 
+%what implications does it have?
 % \bibliographystyle{apalike}

### 2021-05-31 thesis/tex/oscillations.tex
update

@@
-%\input{commands}
-%\begin{document}
+% \input{commands}\begin{document}
 
@@
 \subsection{Mass Generation}
-As we saw in Eq.~\ref{eq:j_CC}
-, the neutrino fields $\nu_\alpha$ only couple to the associated lepton fields $\ell_\alpha$, conserving the lepton number $L_\alpha$.
-We will now introduce two separate extensions to this part of the Standard Model.
+We consider a right-handed neutrino field, $\nu_R$.
+It has the usual properties of the conventional left-handed neutrino such as hypercharge and color zero.
+Moreover, since the electroweak gauge group $\text{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
+This neutrino field is \emph{sterile} since it doesn't participate any of the SM interactions.
 
-We introduce a right-handed neutrino field, $\nu_R$.
-It has the usual properties of the conventional left-handed neutrino such as hypercharge and color zero.
-Moreover, since the electroweak gauge group $\text{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, it transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
-This neutrino is \emph{sterile} since it doesn't participate any of the SM interactions.
-
-We extend the SM by adding a right-handed component to the Higgs-lepton Yukawa Lagrangian from Eq.~\ref{eq:YukawaLagrangian} with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ ,
-
+We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa Lagrangian from Eq.~\ref{eq:YukawaLagrangian}
 \begin{align}
@@
 \end{align}
-Similar to how we diagonalized the lepton Yukawa couplings $Y_{\alpha \beta}^{\prime \ell}$ in Eq.~~\ref{eq:leptonYukawaDiag}, we diagonalize $Y_{\alpha \beta}^{\prime \nu}$ as
+Similar to how we diagonalized the lepton Yukawa couplings $Y_{\alpha \beta}^{\prime \ell}$ in Eq.~\ref{eq:leptonYukawaDiag}, we diagonalize $Y_{\alpha \beta}^{\prime \nu}$ as
 \begin{align}
@@
 \end{align}
-The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and expanding the Higgs VEV into the fields gives us
+The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and expanding the Higgs vacuum expectation value $v$ into the fields gives us
 \begin{align}
@@
 \begin{align}\label{eq:j_CC3} %TODO: put sums on all above?
-    j^\rho_L &= 2 \sum_\alpha \sum_k U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}\,.
+    j^\rho_L &= 2 \sum_\alpha \sum_k U^\dagger_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}\,.
 \end{align}
-%TODO: add segue
+
+What form does this new matrix $U$ take? By construction, it provides the unitary transformation between the flavor and mass bases.
+Any unitary $3\times3$ matrix can be parametrized using three mixing angles and six phases. However, not all phases affect the 
+charged and weak currents and are thus not observable. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
+leaving only one physical phase for us to measure. Thus we are down to four degrees of freedom in the three dimensional case: three mixing angles
+of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$.
+
+We construct the PMNS matrix using the rotation matrixes from $SO(3)$ as
+\begin{align}
+    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12} \nonumber \\
+      & = 
+    \begin{pmatrix}{ccc}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
+\begin{pmatrix}{ccc}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
+\begin{pmatrix}{ccc}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}\,.
+\end{align}
+
+The term $\delta_\text{CP}$ determines the degree of charge-parity violation. In this work, we will assume CP invariance by always
+setting $\delta_{CP} = \SI{0}{\degree}$. Thus,
+
+\begin{align}
+    U &=
+    \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
+\begin{pmatrix}c_{13} & 0 & s_{13} \\ 0 & 1 & 0 \\ -s_{13}  & 0 & c_{13}\end{pmatrix}
+\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix} \nonumber \\
+    &= 
+    \begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} \\ 
+        -s_{12} c_{23}-c_{12} s_{23} s_{13} & c_{12} c_{23}-s_{12} s_{23} s_{13} & s_{23} c_{13} \\ 
+        s_{12} s_{23}-c_{12} c_{23} s_{13}  & -c_{12} s_{23}-s_{12} c_{23} s_{13} & c_{23} c_{13}
+    \end{pmatrix}\,.
+\end{align}
+
+In this work, we will be using the best-fit values from~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$. The $90\% $ CL values are
+\begin{align}\label{eq:nufitparams}
+    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+\end{align}
+The PMNS matrix is then real, with numerical values 
+\begin{align}\label{eq:Uvalues}
+    U = \begin{pmatrix}
+        U_{e 1} & U_{e2} & U_{e3} \\
+        U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
+        U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
+    \end{pmatrix} 
+    = \begin{pmatrix}
+        0.825 & 0.545 & 0.149 \\
+        -0.455 & 0.485 & 0.746 \\
+        0.334 & -0.684 & 0.649
+    \end{pmatrix} \,.
+\end{align}
+In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
+suggesting that $\nm$ primarily mixes into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
+the most abundant. This means we will be able to stringently constrain parameters relating to $\mu\tau$ mixing.
+
 \subsection{Neutrino Propagation}
@@
 In other words, the charged current generates a flavor neutrino $\na$, which is a superposition of the mass eigenstates 
-$\nu_k$ with weights $U_{\a k}^*$. In the ket-formalism, we express this as
+$\nu_k$ with weights $U_{\a k}^\dagger$. In the ket-formalism, we express this as
 \begin{align}\label{eq:osc_1}
-    \ket{\na} = \sum_k U^*_{\a k} \ket{\nu_k}\,.
+    \ket{\na} = \sum_k U^\dagger_{\a k} \ket{\nu_k}\,.
 \end{align}
@@
 \begin{align}\label{eq:nat}
-    \ket{\na(t)} = \sum_k U^*_{\a k} e^{-iE_kt}\ket{\nu_k}\,.
+    \ket{\na(t)} = \sum_k U^\dagger_{\a k} e^{-iE_kt}\ket{\nu_k}\,.
 \end{align}
@@
 \begin{align}\label{eq:osc_k}
-    \sum_\a U_{\a k}\ket{\na} &= \sum_{\alpha, j} U_{\a k} U_{\a j}^* \ket{\nu_j} \nonumber \\
+    \sum_\a U_{\a k}\ket{\na} &= \sum_{\alpha, j} U_{\a k} U_{\a j}^\dagger \ket{\nu_j} \nonumber \\
     \sum_\a U_{\a k}\ket{\na} &= \sum_{j} \delta_{kj} \ket{\nu_j} \nonumber \\
@@
 \begin{align}
-    \ket{\na(t)} &= \sum_k U^*_{\a k} e^{-iE_kt}\ket{\nu_k} \nonumber \\
-    \ket{\na(t)} &= \sum_k U^*_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
-    \ket{\na(t)} &= \sum_{k,\b} U^*_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
+    \ket{\na(t)} &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\ket{\nu_k} \nonumber \\
+    \ket{\na(t)} &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
+    \ket{\na(t)} &= \sum_{k,\b} U^\dagger_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
 \end{align}
@@
 \begin{align}
-    P_{\na \to \nb}(t) = \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
+    P_{\na \to \nb}(t) = \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
 \end{align}
@@
 \begin{align}
-    P_{\ab}(t) = \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)t/2E}\,.
+    P_{\ab}(t) = \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)t/2E}\,.
 \end{align}
@@
 \begin{align}
-    P_{\ab}(x) &= \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
-                       &= \sum_{k,j} U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E})\,,
+    P_{\ab}(x) &= \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
+                       &= \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E})\,,
 \end{align}
@@
 rather than the individual masses, it is impossible
-to measure the mass states $m_k$ through neutrino oscillations.
-Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^* = \delta_{\a \b}$ yields 
+to measure the mass $m_k$ through neutrino oscillations.
+Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^\dagger = \delta_{\a \b}$ yields 
 \begin{align}
-    \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 = \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^* U_{\b k} U_{\a j} U_{\b j}^*]
+    \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 = \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^\dagger U_{\b k} U_{\a j} U_{\b j}^\dagger]
 \end{align}
-In this work, we will always assume the mixing matrix $U$ to be real. 
-We thus write 
+
+Since we take the PMNS matrix to be real and thus Hermitian, we drop the complex transpose in the following calculation. We have
 \begin{align}\label{eq:Pab}%TODO: shorten?
@@
 which is the probability of neutrino vacuum oscillations. %TODO: maybe plot?
-The calculation for antineutrinos yield the same result if one assumes the realness of the mixing matrix.
+The calculation for antineutrinos yield the same result if one continues to assume the Hermicity of the mixing matrix.
+
+For our purposes, the probabilities in Eq.~\ref{eq:Pab} are rather uninteresting, since they are only valid in vacuum.
+Despite this fact, this form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
+determine the amplitude of the oscillations, while the mass-squared differences together with the ratio $L/E$ determine the 
+frequency.
 
@@
 \begin{align}
-    H^{CC} = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, e \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, \ne \right]
+    H_{CC} = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, e \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, \ne \right]
 \end{align}
@@
 \begin{align}\label{eq:H_fierz}
-    H^{CC} = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, e \right]\,.
+    H_{CC} = \frac{G_F}{\sqrt{2}}\left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right] \left[\bar e \,\gamma_\rho\, (1- \gamma^5)\, e \right]\,.
 \end{align}
@@
 \begin{align}\label{eq:avg_H1}
-    \bar{H}^{CC} &= \int \dd p_e^3 \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
+    \avg{H_{CC}} &= \int \dd p_e^3 \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
            &= \frac{G_F}{\sqrt{2}} \int \dd p_e^3 \bra{e(p_e,h_e)} \left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right]  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \left[\bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x) \right] \ket{e(p_e,h_e)} \nonumber \\
@@
 \begin{align}\label{eq:avg_H2}
-    \avg{H^{CC}} &= \frac{G_F}{\sqrt{2}E_e V} \bar\ne \, (1- \gamma^5)\, \ne \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T)\,.
+    \avg{H_{CC}} &= \frac{G_F}{\sqrt{2}E_e V} \bar\ne \, (1- \gamma^5)\, \ne \int \dd p_e^3\, \slashed{p}_e\, f(E_e,T)\,.
 \end{align}
@@
 \begin{align}
-    \avg{H^{CC}} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
+    \avg{H_{CC}} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
             &= \sqrt{2}G_F N_e \bar{\nu}_{Le} \gamma^0 \nu_{Le}\,,
 \end{align}
-where the projection operator $(1- \gamma^5)$ ensures that only the left-hand compontent of the neutrino fields interact weakly. Thus,
+where the projection operator $(1- \gamma^5)$ in the first line ensures that only the left-hand compontent of the neutrino fields interact. Thus,
 \begin{align}\label{eq:V_CC1}
-    V_{CC} = \sqrt{2}G_F N_e\,, \quad H^{CC}\ket{\nu_k} = V_{CC}\ket{\nu_k}\,.
-\end{align}%TODO: write H_{CC} instead
-Here we see a crucial difference between the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H^{CC}$, namely
-that the CC (and NC) interactions happen in the flavor basis rather than in the mass basis. In other words,
+    V_{CC} = \sqrt{2}G_F N_e\,, \quad H_{CC}\ket{\nu_k} = V_{CC}\ket{\nu_k}\,.
+\end{align}
+Here we see a crucial difference between the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H_{CC}$, namely
+that the CC interactions happen in the flavor basis rather than in the mass basis\footnote{A similar calculation for the NC reveals the same fact:
+neutrinos interact in the flavor basis.}. In other words,
 neutrinos propagate in their mass eigenstates, but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
-determines if the flavor eigenstate has oscillated or not. Thus, the expressions involving the 
-matter potential does not need to be transformed by the PMNS matrix.
+determines if the flavor eigenstate has oscillated or not. The interactions still conserve lepton number, but the kinetic Lagrangian will not.
 
@@
 Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors.
-However, since all flavors undergo NC interactions the total matter potential in matrix form is:
+However, since all flavors undergo NC interactions the total matter potential in matrix form is
 \begin{align}\label{eq:V_matrix}
@@
 
-In this work, we will be using the best-fit values from~\cite{nufit},
-\begin{align}\label{eq:nufitparams}
-    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \Delta m^2_{31} =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
-    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+For $N_e = 0$, i.e. in vacuum, these probabilities are identical to the ones that we analytically derived in Eq.~\ref{eq:Pab}.
+For $N_e \neq 0$, we have closed form solutions, but they are not considered further here.
+
+We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
+symmetric piecewise polynomials for the Earth density in \si{\gram \cm^3} shown in the left panel of Fig.~\ref{fig:potential}.
+We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary, and will be visible in our 
+oscillations.
+
+Using a value of $Y=0.5$ electron per nucleon, we express the matter potential as
+\begin{align}
+    V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
+           &= \SI{3.8e-23}{\eV\, \gram \cm^{-3}}\,,
 \end{align}
-with the exception of the CP-violating phase $\delta_\text{CP}$ which we always set to zero for simplicity. The PMNS matrix then has the numerical values 
-\begin{align}\label{eq:Uvalues}
-    U = \begin{pmatrix}
-        U_{e 1} & U_{e2} & U_{e3} \\
-        U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
-        U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
-    \end{pmatrix} 
-    = \begin{pmatrix}
-        0.825 & 0.545 & 0.149 \\
-        -0.455 & 0.485 & 0.746 \\
-        0.334 & -0.684 & 0.649
-    \end{pmatrix} \,.
-\end{align}
-In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
-suggesting that $\nm$ primarily oscillates into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
-the most abundant. This means we will be able to stringently constrain parameters relating to $\nm \to \nt$ oscillations. 
-%TODO: write more about smallness of Ue3 and write about parametrization of U. maybe about su2
+a low number due to the smallness of $G_F$. This is plotted in the right panel of Fig.~\ref{fig:potential}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/potential.pdf}
+    \caption{\emph{Left panel:} Earth density asa function of distance from the core from the PREM~\cite{PREM}.
+    \emph{Right panel:} $V_{CC}$ using the PREM density 0.5 electrons per nucleon.}\label{fig:potential}
+\end{figure}
 
-%\end{document}
+Now, solving the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_3gen} with the matter potential from the PREM,
+we obtain the nine combinations of probabilities through the Earth diameter. We note that due to our assumption of CP-invariance
+(and thus, T-invariance), the probabilities $P_{\a\b}$ and $P_{\b\a}$ are identically equivalent. The result for \si{\GeV} neutrinos 
+is shown in Fig.~\ref{fig:oscillations}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
+    \caption{}\label{fig:oscillations}
+\end{figure}
+
+Now we need to incorporate the \emph{zenith angle}, defined as the angle between the neutrino direction of travel and south.
+This way, neutrinos traveling through the entire diameter of the Earth up through the South Pole are defined as `up-going', while
+neutrinos that start at the South Pole are `down-going'. We will refer to the quantity $\cos{(\theta_z)}$ as the \emph{zenith}, while
+$\theta_z$ is the \emph{zenith angle}.
+
+Since we are interested in the matter effects, we reserve our IceCube study to up-going neutrinos, i.e. neutrinos with
+zenith $-1<= \cos{(\theta_z)}<=0$. We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
+allowing us to fully see the Earth matter effect on the oscillations in full. This is shown in Fig.~\ref{fig:oscillograms}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/oscillograms.pdf}
+    \caption{Oscillograms showing neutrino oscillations for all flavors in E-$\cos(\theta_z)$ space.}\label{fig:oscillograms}%TODO: redo finer
+\end{figure}%TODO: remake with finer
+
+The core-mantle boundary from Fig.\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.
+
+% \end{document}

### 2021-05-31 thesis/tex/sterileTheory.tex
update

@@
-% \documentclass{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \usepackage{subcaption}
-% \input{commands}
-
-% \begin{document}
+% \input{commands}\begin{document}
 \section{The Sterile State}\label{sec:anomalies}
@@
 we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
-which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the $\bar\mu \bar\mu$ sector, shown in Fig.~\ref{fig:sterile_resonance}.
+which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the for $P_{\anm\anm}$, shown in Fig.~\ref{fig:sterile_resonance}.
 
@@
 We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
-%TODO: more? mention that Pmm=1 at TeV for 3+0
+TODO: more? mention that Pmm=1 at TeV for 3+0
 
-% \newpage
-% \bibliographystyle{elsarticle-num}
-% \bibliography{ref}
-% \end{document}
+% \newpage\bibliographystyle{elsarticle-num}\bibliography{ref}\end{document}

### 2021-05-31 src/plotter.py

@@ -240,4 +240,4 @@ def savethesis(fig, name):
     from subprocess import call 
     _ = call('pdfcrop thesis/tex/figures/{name}.pdf thesis/tex/figures/{name}.pdf')
 if __name__ == '__main__':
-    pass
+    an_plots()

### 2021-05-31 src/probability/functions.py

@@ -287,11 +287,13 @@ def rho_earth(r):# lä 1306.2903 och 0612285 ocg kuo
     Calculates the density in g/cm-3 of the point at a distance r in km from the Earth's center using data from PREM https://www.cfa.harvard.edu/~lzeng/papers/PREM.pdf
     Returns the density in gm/cm-3
     '''
-    if r == r_earth + 1: #Neutrino doesn't traverse Earth
-        return 0.0
+    
     if not np.isscalar(r): #If r is array, return list of densities.
         return [rho_earth(item) for item in r]
     
+    if r == r_earth + 1: #Neutrino doesn't traverse Earth
+        return 0.0
+
     x = r / r_earth #Normalized Earth radius in km
     if 0 <= r < 1221.5:
         return 13.0885 - 8.8381*x**2
@@ -408,7 +410,4 @@ def integrate(array,method='simps',*args):
     elif np.ndim(array) == 4:
         return simps(simps(simps(simps(array,args[0]),args[1]),args[2]),args[3])
 if __name__ == '__main__':
-    import matplotlib.pyplot as plt
-    z = 1
-    print(baseline(np.pi - np.arccos(z)))
-    print(get_radial_distance(500, np.pi - np.arccos(z)))
+    print(np.sqrt(2) * GF * 0.5 * N_A * 1 * (1/GeVtocm1)**3)

### 2021-06-01 thesis/tex/SM.tex
update

@@
 Each vector boson has one corresponding generator, the set of which constitutes the group.
-The strong charge is mediated by eight gluons, which correspond to the eight generators of $\text{SU}(3)_C$. 
+The strong charge is mediated by eight massless gluons, which correspond to the eight generators of $\text{SU}(3)_C$. 
 The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$ and the massless boson $\gamma$, 
-which constitute the generators of $\text{SU}(2)_L$. Finally, the massless gauge boson, the photon, has a representation which is the generator of $\text{U}(1)_Y$.
+which constitute the generators of $\text{SU}(2)_L$ and $\text{U}(1)_Y$.
 
@@
 However, the scalar bosons\footnote{The Standard Model only has one scalar boson: the Higgs boson.} and fermions are free as long as they
-belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. In this work,
-we will use this leniency to make drastic modifications to the Standard Model and examine to which extent they might be falsifiable.
+belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. Even the
+number of fermions must be experimentally derived. In this work,
+we will use this leniency to make drastic modifications to the Standard Model fermions and examine to which extent these theories might be falsifiable.
 
 \subsection{Lepton mixing}
-In this section, we will see how the neutrinos interact with the charged leptons, which is the first stepping stone in our journey.
+In this section, we will see how the neutral leptons -- the neutrinos -- interact with the charged leptons, 
+which is the first stepping stone in our journey.
 
@@
 \end{align}
-has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the lepton masses being non-definite.
+has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the charged lepton masses being non-definite.
 This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
@@
 \end{align}
-This procedure give the lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass.
-However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo.
-The leptonic charged weak current now takes the form
+This procedure give the charged lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. 
+However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
 \begin{align}
@@
 \end{align}
-where each fermion field and matrix have an implied $L$ subscript, which was dropped for clarity.
+where each lepton field and matrix have an implied $L$ subscript, which was dropped for clarity.
 The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$.
 However,
-$\nu_\alpha$ is still massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
+$\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive. In the next section,
+we shall make our first extension of the Standard Model, by introducing neutrino masses.
 %TODO:more here about SM and lepton mixing? maybe about mass/massless particles. why does SM predict massless neutrinos, and 

### 2021-06-01 thesis/tex/oscillations.tex
update

@@
-% \input{commands}\begin{document}
+\input{commands}
+\begin{document}
 
@@
 \end{align}
-Thus, this extension to the SM generates neutrino masses by the Higgs mechanism, in the same fashion as with the charged leptons and the quarks:
+Thus, this extension to the SM generates neutrino masses at electroweak symmetry breaking by the Higgs mechanism with mass terms
 \begin{align}
-    m_k = \frac{y_k^\nu v}{\sqrt{2}}
+    m_k = \frac{y_k^\nu v}{\sqrt{2}}\,.
 \end{align}
 
+\subsection*{The PMNS matrix}
 Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
@@
 in Eq.~\ref{eq:L_H} violates lepton number conservation since it couples the charged lepton flavor $\alpha$ to the neutrino mass eigenstate $k$, which is a superposition of flavors. 
-There is no transformation that leaves both the interaction and kinetic Lagrangian invariant.
+There is no transformation that leaves both the interaction and kinetic Lagrangian invariant, thus violating this symmetry.
 
@@
       & = 
-    \begin{pmatrix}{ccc}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
-\begin{pmatrix}{ccc}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
-\begin{pmatrix}{ccc}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}\,.
+    \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
+\begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
+\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}\,.
 \end{align}
-
 The term $\delta_\text{CP}$ determines the degree of charge-parity violation. In this work, we will assume CP invariance by always
@@
 \end{align}
-In our study, we will only use atmospheric neutrinos, of which $\nm$ are the most abundant. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
+In our study, we will only use neutrinos originating from conventional cosmic ray interactions in the atmosphere. 
+In this so-called atmospheric neutrinos, $\nm$ are the most abundant, while the $\nt$ flux is neglible. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
 suggesting that $\nm$ primarily mixes into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
@@
 \end{align}
-
 Now, our approximation $v\approx 1$ implies $x\approx t $, thus
@@
 \end{align}
-
 Since we take the PMNS matrix to be real and thus Hermitian, we drop the complex transpose in the following calculation. We have
@@
 The calculation for antineutrinos yield the same result if one continues to assume the Hermicity of the mixing matrix. 
+In Fig.~\ref{fig:vac_osc}, we show the energy spectra of these oscillations in the low \si{\GeV} range for neutrinos that travel \SI{12000}{\km}\footnote{This baseline
+is approximately the Earth diameter, and will be the maximum travel distance which we will use later on.}.
+In the left-most panel, we see a supressed $\nu_\mu \to e$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
+numerical values of the mixing matrix in Eq.~\ref{Uvalues}.
+\si{\GeV} oscillations are driven by the $\dm[31]$ mass-squared difference. Hence, the most important mixing matrix 
+elements for $P_{\a\b}$ are $U_{\a3}, U_{\a1}$ and $U_{\b3}, U_{\b1}$. The smallness of $U_{e3}$ then supresses the
+amplitude of $\Pme$.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/vac_osc.pdf}
+    \caption{$\nm$ vacuum oscillations from Eq.~\ref{eq:Pab}}\label{fig:vac_osc}
+\end{figure}
 
@@
     \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=1\textwidth]{figures/w-boson.pdf} 
+        \includegraphics[width=0.9\textwidth]{figures/w-boson.pdf} 
         \caption{Charged current weak interaction between an electron neutrino and an electron,
@@
 \end{align}
-
 Just as in Eq.~\ref{eq:TDSE}, we start with a Hamiltonian that solves the time-dependent Schrödinger equation. This time, let the Hamiltonian be 
@@
 Reminding ourselves that the vacuum Hamiltonian $H_0$ has eigenstates in the mass basis, we write the following expression where 
-use the relations ~\ref{eq:osc_1} and ~\ref{eq:osc_k} to switch between the flavor and mass basis with the PMNS elements:
+use the relations Eq.~\ref{eq:osc_1} and Eq.~\ref{eq:osc_k} to switch between the flavor and mass basis with the PMNS elements:
 \begin{align}
@@
         \end{pmatrix}\,. 
-\end{align}%TODO: this is equal to the analytic expression for n_e=0
+\end{align}
 This is the three-flavor neutrino oscillation Hamiltonian that we will solve numerically to obtain the evolution of $\Psi_\a$, whose squared components
@@
 For $N_e = 0$, i.e. in vacuum, these probabilities are identical to the ones that we analytically derived in Eq.~\ref{eq:Pab}.
-For $N_e \neq 0$, we have closed form solutions, but they are not considered further here.
+For matter oscillations with $N_e \neq 0$, we do have closed form solutions, but they are not considered further here.
 
@@
     \caption{\emph{Left panel:} Earth density asa function of distance from the core from the PREM~\cite{PREM}.
-    \emph{Right panel:} $V_{CC}$ using the PREM density 0.5 electrons per nucleon.}\label{fig:potential}
+    \emph{Right panel:} $V_{CC}$ using the PREM density and 1/2 electrons per nucleon.}\label{fig:potential}
 \end{figure}
@@
 This way, neutrinos traveling through the entire diameter of the Earth up through the South Pole are defined as `up-going', while
-neutrinos that start at the South Pole are `down-going'. We will refer to the quantity $\cos{(\theta_z)}$ as the \emph{zenith}, while
-$\theta_z$ is the \emph{zenith angle}.
-
+neutrinos that start at the South Pole are `down-going'. We will mostly work with the quantity $\cos{(\theta_z)}$.
 Since we are interested in the matter effects, we reserve our IceCube study to up-going neutrinos, i.e. neutrinos with
-zenith $-1<= \cos{(\theta_z)}<=0$. We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
+zenith angle $-1<= \cos{(\theta_z)}<=0$. We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
 allowing us to fully see the Earth matter effect on the oscillations in full. This is shown in Fig.~\ref{fig:oscillograms}.
@@
 \end{figure}%TODO: remake with finer
-
 The core-mantle boundary from Fig.\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.
 
-% \end{document}
+\end{document}

### 2021-06-01 thesis/tex/sterileTheory.tex
update

@@
 \section{The Sterile State}\label{sec:anomalies}
-In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}. The anomaly was consistent with a fourth
-neutrino state with $\dm[41] > \SI{0.03}{\eV \squared}$. Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
-$\ne$ events too. Together with the so-called reactor and gallium analomalies, there were indications that both appearance and disappearance
-anomalies might be remedied by a fourth mass state.
+In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}.  
+Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
+$\ne$ events too. Together with the so-called reactor and gallium anomalies, these reports suggested 
+that the three massive neutrino framework could be amended.
+By introducing a fourth heavy mass state $\nu_4$, both appearance and disappeareance anomalies could be minimally accomodated.
 
-However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species, so this fourth mass state can't be interacting weakly.
-We now distinguish between the three original neutrino flavors ($e$, $\mu$, and $\tau$) and the new fourth flavor ($s$) by calling the former \emph{active} neutrinos
-and the latter \emph{sterile}. The experiments listed above indicate that the mass-squared difference of the sterile neutrino is in the \si{\eV} scale, while the two others
-are three and five magnitudes smaller. To remind us of this difference, we write $3+1$, since the sterile state proposed is a lot more massive than the active states. Models
-with different hierachies might be written as $1+2+1$ or $1+3$, but many of them are ruled out by cosmological constraints and will not be considered here. %TODO:source
+However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species, 
+so this fourth mass state cannot be interacting weakly.
+We now distinguish between the three original neutrino flavors ($e$, $\mu$, and $\tau$) and the new fourth 
+flavor ($s$) by calling the former \emph{active} neutrinos
+and the latter \emph{sterile}. The experiments listed above indicate that the mass-squared difference of the 
+sterile neutrino is in the \si{\eV} scale, while the two others
+are three and five magnitudes smaller. To remind us of this difference, we write $3+1$, since the sterile state 
+proposed is a lot more massive than the active states. Models
+with different hierachies might be written as $1+2+1$ or $1+3$, but many of them are ruled out by cosmological 
+observations and will not be considered here. %TODO:source
+
+In this chapter, we will use the matter-enhanced resonant oscillations assuming the 3+1 framework,
+and probe it the using the $\nm$ disappearance signature.
 
 \subsection{The Hamiltonian}
-The inclusion of the sterile neutrino in the Hamiltonian is straightforward. We extend the PMNS matrix to incorporate the new flavor and mass eigenstates: 
+The inclusion of the sterile state in the Hamiltonian is straightforward. We extend the PMNS matrix to incorporate the new flavor and mass eigenstates: 
 \begin{align}
@@
 \end{align}
-where a common parametrization of the PMNS matrix is 
+where a common parametrization of this new mixing matrix is 
 \begin{align}\label{eq:U4gen_param}
@@
     \end{pmatrix}
-    = \begin{pmatrix}
-        V_{CC} & 0 & 0 & 0 \\
+    = \sqrt{2}G_F\begin{pmatrix}
+        N_e & 0 & 0 & 0 \\
         0 &0 & 0 & 0 \\
         0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & -V_{NC}
+        0 & 0 & 0 & -N_n/2
     \end{pmatrix} \nonumber \\
@@
 We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
-TODO: more? mention that Pmm=1 at TeV for 3+0
+%TODO: more? mention that Pmm=1 at TeV for 3+0
 

### 2021-06-01 src/probability/analytical.py

@@ -1,12 +1,12 @@
 import numpy as np
-from functions import V,dm, mass_dict,theta,param_dict,GeV2tokm1,get_radial_distance,r_earth
+from functions import V,dm, mass_dict,theta,param_dict,GeV2tokm1,U_3,r_earth, nufit_params_nsi
         
 def P_an(flavor_from, flavor_to, param, E=None, L=None,  param_min=None, param_max=None, material='vac',earth_start = 0, ndim = 3, anti=False, theta_i=0, npoints=500, params=param_dict):
     '''
     Returns the analytical probability as an array for a collection of L[m/km] and E[MeV/GeV]
     '''
     if param == 'E':
-        E = np.linspace(param_min, param_max, npoints)
+        E = np.logspace(np.log10(param_min), np.log10(param_max), npoints)
         assert(L is not None)
     elif param == 'L':
         L = np.linspace(param_min, param_max, npoints)
@@ -19,25 +19,23 @@ def P_an(flavor_from, flavor_to, param, E=None, L=None,  param_min=None, param_m
 
     if ndim == 2:
         probs = [P_two(alpha, beta, E, L =ell, theta_i=theta_i ,param=param,earth_start=earth_start, anti=anti, material=material, params=param_dict) for ell in L]
-        return L, np.array(probs)
+        return np.array(probs)
     else:
         if param == 'E':
-            probs = [P_n(alpha, beta, E=en, L =L, param='E', imag_sign=imag_sign, ndim=ndim, params=param_dict, theta_i=theta_i, material=material) for en in E]
-            return E, np.array(probs)
+            probs = [P_n(alpha, beta, E=en, L =L, ndim=ndim, params=param_dict) for en in E]
+            return np.array(probs)
         elif param == 'L':
-            probs = [P_n(alpha, beta, E=E, L =ell, param='L', imag_sign=imag_sign, ndim=ndim, params=param_dict,theta_i=theta_i,material=material) for ell in L]
-            return L, np.array(probs)
+            probs = [P_n(alpha, beta, E=E, L =ell, ndim=ndim, params=param_dict) for ell in L]
+            return np.array(probs)
 
 
-def P_n(flavor_from,  flavor_to, E, ndim, L=2*r_earth, params=param_dict): 
+def P_n(alpha,  beta, E, ndim, L=2*r_earth, params=param_dict): 
     '''
[…]

### 2021-06-07 thesis/tex/DCtheory.tex
update

@@
 
-We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
-assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
-number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
 \section{PINGU}
@@
 $\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
-We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
+We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
 

### 2021-06-07 thesis/tex/SM.tex
update

@@
 
-Together, these groups make up the local symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
+Together, these groups make up the local (gauge) symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
 This symmetry group determines the form of the three coupling constants of nature, whose numerical values must be experimentally measured. 
-Since the vector bosons are represented by the generators, they are wholly constrained by the symmetry group.
-However, the scalar bosons\footnote{The Standard Model only has one scalar boson: the Higgs boson.} and fermions are free as long as they
+Since the vector bosons are represented by the generators, they are wholly constrained by the symmetry group. However, the scalar bosons and fermions are free as long as they
 belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. Even the
@@
 \subsection{Lepton mixing}
-In this section, we will see how the neutral leptons -- the neutrinos -- interact with the charged leptons, 
-which is the first stepping stone in our journey.
-
-In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
+Now we shall see how the charged leptons interact with the chargeless neutrinos.
+Consider how charged leptons interact with the Higgs field. In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
 \begin{align}
@@
 However,
-$\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive. In the next section,
-we shall make our first extension of the Standard Model, by introducing neutrino masses.
+$\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
 %TODO:more here about SM and lepton mixing? maybe about mass/massless particles. why does SM predict massless neutrinos, and 

### 2021-06-07 thesis/tex/nsiTheory.tex
update

@@
 % \begin{document}
-\section{Non-standard interactions}
+\section{Non-Standard Interactions}
+We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
+osillations forces us to amend it. We have no reason to believe that the Standard Model 
+gauge group is the complete picture. Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
+spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with ompletely different
+properties might be responsible for the Standard Model that we know. In this sense, the Standard Model might be considered 
+an effective low energy theory, which is yiels impressive results in some areas, but failing in others. In fact, 
+just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
+another broken symmetry resulting in the Standard Model gauge group.
+
 %TODO: moreintro. incompleteness of SM
-Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
+Following the discussion in~\cite{tommyNSI}, the new parameters $\epsilon$ have the scale
 \begin{align}
-    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
+    \epsilon \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
 \end{align} 
-in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
-two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
-we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.
+in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
+two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above electroweak scale, 
+we then predict that the parameters contribute with at most a factor of $10^{-2}$ to the standard matter effect, decreasing quadratically.
 
 \subsection{Altering the Matter Potential}
-Up until now, we have only considered neutrino interactions with electrons, protons, and neutrons. Now we extend this to include we can extend this to include 
-the up and down quarks which are present in the Earth as the fundamental components of neutrons and protons. 
-Consider interactions beyond the Standard Model through the following Lagrangians,
+Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.
+Following the approach of the Standard Model that the group generators uniquely determine the gauge bosons, a different gauge
+theory will have different interactions than those we presently know. We call these interactions non-standard interactions (NSI).
+We can phenomenologically allow these interactions to include the up and down quarks which are present 
+in the Earth as the fundamental components of neutrons and protons, 
+parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
+We write the Lagrangians
 \begin{align*}
@@
 where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
-$f \in \{e,u,d\}$.
+$f \in \{e,u,d\}$. The CC NSI effect affects neutrino production and detection, and will not be considered here. NC NSI affect the matter potential, 
+and is thus of interest to us.
 
@@
 \begin{align}
-    \epsilon_{\ab} =  \sum_X [\epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})]
+    \epsilon_{\ab} =  \sum_X \epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})
 \end{align}
@@
 \end{align}
-Now we have reduced the possible number of NSI parameters from 9 down to 6. Moreover, it is common to subtract $\emm$ from the diagonal, which
-we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
-probabilities. So just as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
-Our NSI potential matrix now takes the form 
-\begin{align}
-    \begin{pmatrix}
-        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
-        \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
-        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
-    \end{pmatrix} 
-    - \epsilon_{\mu\mu}
-    \begin{pmatrix}
-        1 & 0 & 0 \\
-        0 & 1 & 0 \\
-        0 & 0 & 1 
-    \end{pmatrix}
-     &= \begin{pmatrix}
-        \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
-        \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
-        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
-    \end{pmatrix} \nonumber \\
-    &= \begin{pmatrix}
-        \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
-        \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
-        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
-    \end{pmatrix}\,,
-\end{align}
-where $\ep = \ett - \emm$.
+Now we have reduced the possible number of NSI parameters from 9 down to 6.
+
+% Moreover, it is common to subtract $\emm$ from the diagonal, which
+% we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
+% probabilities. So just as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
+% Our NSI potential matrix now takes the form 
+% \begin{align}
+%     \begin{pmatrix}
+%         \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
+%         \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
+%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
+%     \end{pmatrix} 
+%     - \epsilon_{\mu\mu}
+%     \begin{pmatrix}
+%         1 & 0 & 0 \\
+%         0 & 1 & 0 \\
+%         0 & 0 & 1 
+%     \end{pmatrix}
+%      &= \begin{pmatrix}
+%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
+%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
+%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
+%     \end{pmatrix} \nonumber \\
+%     &= \begin{pmatrix}
+%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
+%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
+%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
+%     \end{pmatrix}\,,
+% \end{align}
+% where $\ep = \ett - \emm$.
 
@@
 a clear difference when turning on $\eet$.
+
+We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
+assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
+number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
 %TODO: clean up above and expand a bit.
@@
 
-We summarize our findings in Table~\ref{table:nsi}
-\begin{table}
-    \begin{center}
-    \begin{tabular}{lccc}
-            \hline \hline & & \multicolumn{2}{c} {\text { Visibility }} \\
-            \cline { 3 - 4 } \text {Parameter} & Range & \text { IC } & \text {DC } \\
-            \hline
-            $\ett$ &$\pm 0.05 $ & $\times$ & \checkmark \\
-            $\emt$ &$\pm 0.02 $& \checkmark & \checkmark \\
-            $\eem$ &$\pm 0.2 $& \checkmark & \checkmark \\
-            $\eet$ &$\pm 0.2 $& $\times$ & \checkmark \\
-            \hline
-        \label{table:nsi}
-    \end{tabular}
-    \end{center}
-    \caption{Table of NSI parameters and their ranges considered in this study, along with visibility off
-    their signal in IceCube (IC) and DeepCore/PINGU (DC).}
-\end{table}
-
 % \end{document}

### 2021-06-07 thesis/tex/oscillations.tex
update

@@
-\input{commands}
-\begin{document}
+% \input{commands}
+% \begin{document}
 
 \section{Neutrino Mixing}\label{ch:oscillation}
-%TODO: small intro about PMNS and justification of oscillations
-\subsection{Mass Generation}
-We consider a right-handed neutrino field, $\nu_R$.
-It has the usual properties of the conventional left-handed neutrino such as hypercharge and color zero.
-Moreover, since the electroweak gauge group $\text{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
+
+%\subsection{Mass Generation}
+In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermions right and left-handed components.
+All neutrinos are left-handed and all antineutrinos are right-handed. Thus, neutrinos are massless since they do not undergo the Higgs mechanism.
+Additionally, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
+generated at loop level because any such attempt will violate the total lepton number by two units.
+In order to keep our theory renormalizable, we have one option left: introducing additional fermions.
+
+We consider a right-handed neutrino field, $\nu_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
+left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the SM symmetry 
+group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
 This neutrino field is \emph{sterile} since it doesn't participate any of the SM interactions.
@@
 
-\subsection*{The PMNS matrix}
+\subsection{The mixing matrix}
 Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
@@
 
-\subsection{Effective Matter Potentials}
+\subsection{Effective Potentials}
 
@@
 
-\subsection*{Matter oscillations}
+\subsection{Matter Oscillations}
 Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors.

### 2021-06-07 thesis/tex/sterileResults.tex
update

@@
 \section{The Sterile Hypothesis}
-With the null ($3\nu$ hypothesis) normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
+With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
 First, let us see how the collected data from Fig.~\ref{fig:IC_data} deviates from the predicted $3\nu$ oscillations.
@@
 
-\subsection{$\chi^2$ minimization}
+\subsection{\texorpdfstring{$\chi^2$}{Chi-squared} Minimization}
 For our analyses, we define our $\chi^2$ as

### 2021-06-07 thesis/tex/sterileTheory.tex
update

@@
-% \input{commands}\begin{document}
+%\input{commands}
+%\begin{document}
 \section{The Sterile State}\label{sec:anomalies}
@@
 
-However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species, 
-so this fourth mass state cannot be interacting weakly.
+However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species\footnote{
+    Direct measurements of the invisible $Z$ decay yields $N=2.92 \pm 0.05$\cite{pdg}.
+}, 
+so this fourth mass state cannot be interacting weakly. In other words, it needs to transform as a
+singlet under the broken gauge group $SU(2)_L \times U(1)_{EM}$.
 We now distinguish between the three original neutrino flavors ($e$, $\mu$, and $\tau$) and the new fourth 
-flavor ($s$) by calling the former \emph{active} neutrinos
-and the latter \emph{sterile}. The experiments listed above indicate that the mass-squared difference of the 
-sterile neutrino is in the \si{\eV} scale, while the two others
+flavor by calling the former \emph{active} neutrinos
+and the latter \emph{sterile} due to its non-interacting behavior.
+
+The experiments listed above indicate that the mass-squared difference of the 
+sterile neutrino is in the \si{\eV\squared} scale, while the two others
 are three and five magnitudes smaller. To remind us of this difference, we write $3+1$, since the sterile state 
-proposed is a lot more massive than the active states. Models
-with different hierachies might be written as $1+2+1$ or $1+3$, but many of them are ruled out by cosmological 
-observations and will not be considered here. %TODO:source
+proposed is a lot more massive than the active states.
 
-In this chapter, we will use the matter-enhanced resonant oscillations assuming the 3+1 framework,
-and probe it the using the $\nm$ disappearance signature.
+Two neutrino physics parameters probed by CMB lensing observations are the effective number of neutrinos
+$N_\text{eff}$, and the sum of neutrino masses $\sum m_i$. 
+The 2018 results from the Planck Collaboration in~\cite{planck2018} constrain the parameters to 
+\begin{align}
+    N_\text{eff} = 2.96^{+0.34}_{-0.33}\,, \quad \sum m_i < \SI{0.12}{\eV} \quad (95\%)\,,
+\end{align}
+consistent with the Standard Model with oscillations\footnote{Of course, the 
+Standard Model \emph{without} neutrino masses dictates $N_\text{eff} = 3$ and $\sum m_i \equiv 0$.} prediction of $N_\text{eff} = 3.045$ degrees~\cite{desalas2016}.
+Assuming the Planck data, one thermalized sterile neutrino $(N_\text{eff} = 4)$ is excluded at $6\sigma$. 
+Thus, thermalized sterile 
+neutrinos are strongly in tension with cosmological observations if one does not consider some special mechanism.
+So if a fourth neutrino species is present in nature, it will have ramifications not only on neutrino physics itself, but on
+our understanding of the CMB aswell.
 
@@
 
-% \newpage\bibliographystyle{elsarticle-num}\bibliography{ref}\end{document}
+%\newpage\bibliographystyle{elsarticle-num}\bibliography{ref}\end{document}

### 2021-06-07 thesis/tex/oscillations.tex
update

@@
 \section{Neutrino Mixing}\label{ch:oscillation}
+In 1998, the Super-Kamiokande collaboration detected a $\nm$ deficit that could not be explained by any other mechanism
+than the conversion muon neutrinos to electron neutrinos. This was the first conclusive evidence of a $\nm \to \ne$ oscillation.
+The most interesting conclusion from the observation of neutrino flavor oscillations is the equivalence between oscillations and neutrino mass, 
+with the latter being identically zero acording to the Standard Model. Thus, we are required to extend the Standard Model to incorporate neutrino 
+masses and hence, neutrino oscillations.
 
-%\subsection{Mass Generation}
+\subsection{Mass Generation}
 In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermions right and left-handed components.
@@
 generated at loop level because any such attempt will violate the total lepton number by two units.
-In order to keep our theory renormalizable, we have one option left: introducing additional fermions.
+In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing additional fermions.
 
@@
 
-We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa Lagrangian from Eq.~\ref{eq:YukawaLagrangian}
+We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa Lagrangian 
 \begin{align}
-    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]
+    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,.
 \end{align}
-Similar to how we diagonalized the lepton Yukawa couplings $Y_{\alpha \beta}^{\prime \ell}$ in Eq.~\ref{eq:leptonYukawaDiag}, we diagonalize $Y_{\alpha \beta}^{\prime \nu}$ as
+Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, with the former resulting in the charged lepton masses being non-definite.
+This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$.
+Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, since no flavor rotation can make massless fields massive.
+
 \begin{align}
@@
 \end{align}
-Now we introduce a crucial difference between the properties of the charged lepton and the neutrino fields.
+Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
 While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
@@
 The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
-This is commonly introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
+This fact is introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
 
@@
     \mathcal{L}_{H} &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}\right.
-\nonumber \\
-    &\hspace{5.7em}+\left. \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}
+    + \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
     &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
@@
 \end{align}
-By construction, $Y^\ell_{\alpha \beta}$ and $Y^\nu_{kj}$ are diagonal, so we write them as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as
+By construction, $Y^\ell$ and $Y^\nu$ are diagonal, so we write their omponents as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
 \begin{align}\label{eq:L_H}
@@
 \end{align}
-
-Now, the Dirac neutrino field is
+Now, by the introduction of the sterile field $\nu_R$, the Dirac neutrino field is
 \begin{align}
@@
 \end{align}
-Thus, this extension to the SM generates neutrino masses at electroweak symmetry breaking by the Higgs mechanism with mass terms
+Thus, this extension to the SM generates by the Higgs mechanism neutrino masses with terms
 \begin{align}
-    m_k = \frac{y_k^\nu v}{\sqrt{2}}\,.
+    m_k = \frac{y_k^\nu v}{\sqrt{2}}\,,
 \end{align}
-
-\subsection{The mixing matrix}
-Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
+where the Yukawa couplings $y^\nu_k$ needs to be experimentally determined.
+\subsection{The Mixing Matrix}
+Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the expression for the weak charged current, we get
 \begin{align}\label{eq:j_CC2}
@@
 \end{align}
-
 Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$. 
@@
 Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$. We will refer to the matrix $U$ built by the components $U_{k \alpha}$ as the
-Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix. %TODO: source
+Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix~\cite{pontecorvo1957,maki1962}. %TODO: source
 We now have 
@@
 In our study, we will only use neutrinos originating from conventional cosmic ray interactions in the atmosphere. 
-In this so-called atmospheric neutrinos, $\nm$ are the most abundant, while the $\nt$ flux is neglible. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
+In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is neglible. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
 suggesting that $\nm$ primarily mixes into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
@@
     P_{\ab} &= \sum_{k,j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \nonumber \\
-            &\hspace{2em}+ \sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} \nonumber \\
-            & \hspace{3em}+\sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} \nonumber \\
-            &\hspace{3em}+ 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} +\sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} + 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
             &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\exp(-i\frac{\dm_{kj}x}{2E})\right] \nonumber \\
@@
 which is the probability of neutrino vacuum oscillations. %TODO: maybe plot?
-The calculation for antineutrinos yield the same result if one continues to assume the Hermicity of the mixing matrix. 
+The calculation for antineutrinos yield the same result if one continues to assume the realness of the mixing matrix. 
 In Fig.~\ref{fig:vac_osc}, we show the energy spectra of these oscillations in the low \si{\GeV} range for neutrinos that travel \SI{12000}{\km}\footnote{This baseline
@@
 In the left-most panel, we see a supressed $\nu_\mu \to e$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
-numerical values of the mixing matrix in Eq.~\ref{Uvalues}.
+numerical values of the mixing matrix in Eq.~\ref{eq:Uvalues}.
 \si{\GeV} oscillations are driven by the $\dm[31]$ mass-squared difference. Hence, the most important mixing matrix 
@@
     \avg{H_{CC}} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
-            &= \sqrt{2}G_F N_e \bar{\nu}_{Le} \gamma^0 \nu_{Le}\,,
+            &= \sqrt{2}G_F N_e \bar{\nu}_{eE} \gamma^0 \nu_{eL}\,,
 \end{align}
@@
 \end{align}
-In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  which does not affect the probability since it is a common termt to all flavor states. It can be rotated away.
+In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  which does not affect the probability since it is a common term to all flavor states. It can be rotated away.
 Thus
@@
     \includegraphics[width=0.7\textwidth]{figures/potential.pdf}
-    \caption{\emph{Left panel:} Earth density asa function of distance from the core from the PREM~\cite{PREM}.
+    \caption{\emph{Left panel:} The spherically symmetric Earth density according to PREM~\cite{PREM}, as of distance from the core.
     \emph{Right panel:} $V_{CC}$ using the PREM density and 1/2 electrons per nucleon.}\label{fig:potential}

### 2021-06-07 thesis/tex/sterileTheory.tex
update

@@
 However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species\footnote{
-    Direct measurements of the invisible $Z$ decay yields $N=2.92 \pm 0.05$\cite{pdg}.
+    Direct measurements of the invisible $Z$ decay yields $N=2.92 \pm 0.05$~\cite{pdg}.
 }, 

### 2021-06-08 thesis/tex/ICintro.tex
update

@@
 the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
-
 If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
@@
 is shown in Fig.~\ref{fig:events_cascade}.
-
 If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
@@
 
-\subsection{Atmospheric neutrino flux}
+\subsection{Atmospheric Neutrino Flux}
 Atmospheric neutrinos originates from cosmic rays composed of protons interacting with nuclei in the atmosphere.
@@
 $P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux. 
-
 Interpolating the data yields makes us capable of returning all four necessary fluxes for a given true energy and true zenith.
@@
 
-\subsection{Event reconstruction}
+\subsection{Event Reconstruction}
 After an event has occurred, the IceCube algorithms process the data coming from the detector to \emph{reconstruct} the event.
@@
 So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true and reconstructed energy and zenith angle.
-The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the determination of that neutrino's "actual" flux and cross-section (because this is what nature sees).
+The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the
+determination of that neutrino's `actual' flux and cross-section (because this is what Nature sees).
 

### 2021-06-08 thesis/tex/SM.tex
update

@@
 % \input{commands}\begin{document}
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/SM_figure.pdf}
+\end{figure}
 \section{The Standard Model}\label{ch:SM}
-In order to describe the three forces of nature, we gather the mediators of each force -- the vector bosons -- into gauge groups. 
+In order to describe the three quantizable forces of nature, we gather the mediators of each force -- the vector bosons -- into local (gauge) symmetry groups. 
 Each vector boson has one corresponding generator, the set of which constitutes the group.
 The strong charge is mediated by eight massless gluons, which correspond to the eight generators of $\text{SU}(3)_C$. 
-The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$ and the massless boson $\gamma$, 
+The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$, and the massless photon $\gamma$, 
 which constitute the generators of $\text{SU}(2)_L$ and $\text{U}(1)_Y$.
@@
 which we distinguish with the subscript $L$.
-And the electroweak interaction that a particle undergoes is determined by its hypercharge, $Y$.
+And the electroweak interaction that a particle undergoes is determined by its hypercharge $Y$.
 For example, the quarks all have a nonzero color and hypercharge,
-so they participate in the strong and electromagnetic interactions.
-If a quark is left-handed, it will also feel the weak interaction.
-The neutrinos on the other hand have neither charge nor color, so they are insivible to both the strong and electromagnetic force.
+so they participate in the strong and electromagnetic interactions. If a quark is left-handed, it will also feel the weak interaction. The neutrinos on the other hand, have neither charge nor color, 
+so they are insivible to both the strong and electromagnetic force. We express this by letting their fields transform as singlets under those symmetry groups.
 
-Together, these groups make up the local (gauge) symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
-This symmetry group determines the form of the three coupling constants of nature, whose numerical values must be experimentally measured. 
-Since the vector bosons are represented by the generators, they are wholly constrained by the symmetry group. However, the scalar bosons and fermions are free as long as they
+Together, these three interactions make up the Standard Model gauge group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
+This determines the form of the three coupling constants, but which numerical values must be experimentally measured. 
+Since the vector bosons are represented by the generators, they are uniquely determined by the symmetry group. However, the scalar boson(s) and fermions are free as long as they
 belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. Even the
-number of fermions must be experimentally derived. In this work,
-we will use this leniency to make drastic modifications to the Standard Model fermions and examine to which extent these theories might be falsifiable.
+number of fermions must be experimentally verified and can be altered from a phenomenological standpoint. In this work,
+we will use this leniency to make drastic modifications to the Standard Model fermions and examine to which extent 
+these modifications might be supported by experimental evidence.
 
-\subsection{Lepton mixing}
-Now we shall see how the charged leptons interact with the chargeless neutrinos.
-Consider how charged leptons interact with the Higgs field. In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
-\begin{align}
-    \label{eq:YukawaLagrangian}
-    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
-\end{align}
-has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the charged lepton masses being non-definite.
+% \subsection{Lepton mixing}
+% Now we shall see how the charged leptons interact with the chargeless neutrinos.
+% Consider how charged leptons interact with the Higgs field. In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
+% \begin{align}
+%     \label{eq:YukawaLagrangian}
+%     \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
+% \end{align}
+% has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the charged lepton masses being non-definite.
 This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
-\begin{align}\label{eq:leptonYukawaDiag}
-    V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
-\end{align}
-This procedure give the charged lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. 
-However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
-\begin{align}
-    \label{eq:j_CC}
-    j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
-             &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
-             &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
-\end{align}
-where each lepton field and matrix have an implied $L$ subscript, which was dropped for clarity.
+% \begin{align}\label{eq:leptonYukawaDiag}
+%     V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
+% \end{align}
+% This procedure give the charged lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. 
+% However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
+% \begin{align}
+%     \label{eq:j_CC}
+%     j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
+%              &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
+%              &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
+% \end{align}
+% where each lepton field and matrix have an implied $L$ subscript, which was dropped for clarity.
 The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$.
 However,
-$\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
-%TODO:more here about SM and lepton mixing? maybe about mass/massless particles. why does SM predict massless neutrinos, and 
-%what implications does it have?
+% $\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
 % \bibliographystyle{apalike}

### 2021-06-08 thesis/tex/introduction.tex
update

\chapter{Introduction}
There is no reason for us to believe that our current knowledge in particle physics is complete.
The most successful framework -- the Standard Model -- has notable shortcomings. Neither does it 
explain why there is something rather than nothing, nor does it give a candidate for dark matter\footnote{In the Standard Model,
matter and antimatter come in pairs of one particle and one antiparticle. When interacting,
antimatter \emph{annihilates} the matter, resulting in pure light. Since the universe exists,
there must have been more matter than antimatter at the Big Bang. %TODO: check and make better
Dark matter is heavy matter which does not interact
with electromagnetic radiation, and is thus ´invisible' to us. 
No such particle exists in the Standard Model.}.

To make matters even worse, three of the massless particles in the Standard Model do have mass.
In this thesis we focus on the said particles, the neutrinos, and propose extensions to the Standard Model
related to the neutrinos. We then compare the effects of these extensions with collected data to see 
if our new theory more closely describes Nature or not.

Ultimately, the purpose of this excursion is to guide future research where to uncover more accurate theories.
Traces of this grander theory will be present as breadcrumbs in Nature, we just need to know where 
and how carefully to look.

\section{Outline}
This thesis is outlined as follows. In Chapter~\ref{ch:osc}, we briefly review the most relevant parts 
of the Standard Model that will be relevant for our extensions of it. Then we present the evidence and 
subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel physics prize, 
along with the modifications to the Standard Model needed to accomodate the discovery. The 
reader is then introduced to a standard but detailed derivation of the neutrino mixing matrix
and oscillation Hamiltonian, including the matter 
effects stemming from charged and neutral current weak interactions within the Earth.

In Chapter~\ref{ch:ic}, we present an experimental procedure which can be used to observe signals from neutrinos originating
from cosmic ray interactions in the atmosphere of the Earth. Furthermore, we introduce the reader to 
the two present Antarctic neutrino detectors: IceCube and DeepCore. We also give a brief summary 
about a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which 
we will use as a forecast in our analysis.

Chapter~\ref{ch:theory} consists of two parts. In Section~\ref{sec:anomalies}, we 
introduce a new particle: the sterile neutrino. We present how neutrino oscillations are
modified by this hypothesized fourth neutrino, and how these modifications would appear in IceCube if 
the particle is present in Nature. In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside,
and instead turn to the interactions between neutrinos and the Earth. We again amend the Standard Model by 
considering exotic interactions from a higher energy theory, manifesting themselves as sub-leading modifications 
to the matter potential. These new interactions are not present in the Standard Model and are thus called 
non-standard interactions (NSI).

Finally, Chapter~\ref{ch:results} contains the result from our two separate extensions of the Standard Model.
In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with
literature. In Section~\ref{sec:nsiResults}, we present new constrained bounds on the NSI parameters by 
combining our results for IceCube, DeepCore, and PINGU.

### 2021-06-08 thesis/tex/nsiTheory.tex
update

@@
 % \begin{document}
-\section{Non-Standard Interactions}
-We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
-osillations forces us to amend it. We have no reason to believe that the Standard Model 
-gauge group is the complete picture. Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
-spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with ompletely different
-properties might be responsible for the Standard Model that we know. In this sense, the Standard Model might be considered 
-an effective low energy theory, which is yiels impressive results in some areas, but failing in others. In fact, 
+\section{Non-Standard Interactions}\label{sec:nsiTheory}
+We have no reason to believe that the Standard Model 
+gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
+osillations forces us to amend it. 
+Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
+spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
+properties might undergo a similar spontaneous symmetry break at high energies, 
+producing at lower energies the Standard Model that we know. In fact, 
 just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
 another broken symmetry resulting in the Standard Model gauge group.
+In this sense, the Standard Model might be considered 
+an effective low energy theory, which is yiels impressive results in some areas, but failing in others.
 
-%TODO: moreintro. incompleteness of SM
-Following the discussion in~\cite{tommyNSI}, the new parameters $\epsilon$ have the scale
+Compared to other fermions, the lightness of neutrino masses along with their sparse SM interactions might 
+indicate that these particles provide the best starting point for us to probe new physics, in which 
+other neutrino interactions might occur~\cite{gavela2009}. We call these interactions non-standard interactions (NSI).
+
+Following the approach of the Standard Model that the group generators uniquely determine the gauge bosons, a different gauge
+theory will have different interactions than those we presently know. These new interactions can be parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
+Following the discussion in~\cite{tommyNSI}, the six-dimensional NSI parameters $\epsilon$ have the scale
 \begin{align}
@@
 in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
-two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above electroweak scale, 
+two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory above electroweak scale, 
 we then predict that the parameters contribute with at most a factor of $10^{-2}$ to the standard matter effect, decreasing quadratically.
@@
 Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.
-Following the approach of the Standard Model that the group generators uniquely determine the gauge bosons, a different gauge
-theory will have different interactions than those we presently know. We call these interactions non-standard interactions (NSI).
 We can phenomenologically allow these interactions to include the up and down quarks which are present 
-in the Earth as the fundamental components of neutrons and protons, 
-parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
-We write the Lagrangians
+in the Earth as the fundamental components of neutrons and protons, as seen in the Lagrangians
 \begin{align*}
@@
 where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
-$f \in \{e,u,d\}$. The CC NSI effect affects neutrino production and detection, and will not be considered here. NC NSI affect the matter potential, 
+$f \in \{e,u,d\}$. The CC NSI effect affects neutrino production and detection, and will not be considered further. NC NSI affect the matter potential, 
 and is thus of interest to us.
@@
 \begin{align}\label{eq:NSIH}
-    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\text{diag}(1,0,0) + A_{CC} \epsilon \right] \nonumber \\
+    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\,\text{diag}(1,0,0) + A_{CC}\, \epsilon \right] \nonumber \\
       &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}
@@
 
-\subsection{NSIs in IceCube}
+\subsection{IceCube Signal}
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
@@
 in the DeepCore region of rapid oscillations, where mixing is more violent. 
-\begin{figure}\label{fig:emt_ett_probs}
+\begin{figure}
     \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
-        \includegraphics[width=0.45\textwidth]{figures/emt_probs.pdf}
-        \includegraphics[width=0.45\textwidth]{figures/ett_probs.pdf}
+        \includegraphics[width=0.49\textwidth]{figures/emt_probs.pdf}
+        \includegraphics[width=0.49\textwidth]{figures/ett_probs.pdf}
         \caption{\emph{Left panel:} Muon neutrino and antineutrino survival probabilities for
@@
         $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero.}
+        \label{fig:emt_ett_probs}
     \end{center}
@@
 
-\begin{figure}\label{fig:eem_eet_probs}
+\begin{figure}
     \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/eem_probs.pdf}
-        \includegraphics[width=0.45\textwidth]{figures/eet_probs.pdf}
+        \includegraphics[width=0.49\textwidth]{figures/eem_probs.pdf}
+        \includegraphics[width=0.49\textwidth]{figures/eet_probs.pdf}
         \caption{Muon neutrino and antineutrino survival probabilities for
@@
         \emph{Right panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero.}
+        \label{fig:eem_eet_probs}
     \end{center}
@@
 
-\subsection{NSIs in DeepCore and PINGU}
+\subsection{DeepCore and PINGU Signals}
 Now we repeat our proability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
@@
 %TODO: clean up above and expand a bit.
-\begin{figure}\label{fig:Pee_eet_probs}
+\begin{figure}
     \begin{center}
-        \includegraphics[width=0.6\textwidth]{figures/Pee_eet_probs.pdf}
+        \includegraphics[width=0.8\textwidth]{figures/Pee_eet_probs.pdf}
         \caption{Electron neutrino and antineutrino survival probabilities for
         $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero.}
+        \label{fig:Pee_eet_probs}
     \end{center}

### 2021-06-08 thesis/tex/oscillations.tex
update

@@
 We consider a right-handed neutrino field, $\nu_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
-left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the SM symmetry 
+left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the Standard Model symmetry 
 group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
-This neutrino field is \emph{sterile} since it doesn't participate any of the SM interactions.
+This neutrino field is \emph{sterile} since it doesn't participate any of the Standard Model interactions.
 

### 2021-06-08 thesis/tex/sterileResults.tex
update

@@
 % \begin{document}
-\section{The Sterile Hypothesis}
+\section{The Sterile Hypothesis}\label{sec:sterileResults}
 With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.

### 2021-06-08 thesis/tex/introduction.tex
update

@@
 In this thesis we focus on the said particles, the neutrinos, and propose extensions to the Standard Model
-related to the neutrinos. We then compare the effects of these extensions with collected data to see 
+related to them. We then compare the effects of these extensions with collected data to see 
 if our new theory more closely describes Nature or not.
@@
 
-In Chapter~\ref{ch:ic}, we present an experimental procedure which can be used to observe signals from neutrinos originating
+In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating
 from cosmic ray interactions in the atmosphere of the Earth. Furthermore, we introduce the reader to 

### 2021-06-08 thesis/tex/oscillations.tex
update

@@
 Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, with the former resulting in the charged lepton masses being non-definite. 
-This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$.
-Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, since no flavor rotation can make massless fields massive.
-
+This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$ as
 \begin{align}
@@
 \end{align}
+Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, since no flavor rotation can make massless fields massive.
 Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.

### 2021-06-16 thesis/tex/ICtheory.tex
update

@@
 an error source what will be remedied by this method is the flux. We are using a fairly simple model of the atmospheric 
-flux that excludes prompt flux. The IceCube collaboration use several different flux models which are initialized 
+flux that excludes atmospheric prompt and astrophysical fluxes. The IceCube collaboration use several different flux models which are initialized 
 by a parametrization of the cosmic ray flux.\footnote{Included in the cosmic ray models are e.g. the pion to kaon 
@@
 be limited to only consider the overall flux normalization, rather than the components that produce the flux in the first place.}
-%TODO: maybe rambling?
 
@@
 \end{figure} 
-%TODO:fill more
+Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.
 % \newpage

### 2021-06-16 thesis/tex/introduction.tex
update

@@
 there must have been more matter than antimatter at the Big Bang. %TODO: check and make better
-Dark matter is heavy matter which does not interact
-with electromagnetic radiation, and is thus ´invisible' to us. 
+Dark matter is heavy matter which does not interact with electromagnetic radiation.
 No such particle exists in the Standard Model.}.
 
-To make matters even worse, three of the massless particles in the Standard Model do have mass.
-In this thesis we focus on the said particles, the neutrinos, and propose extensions to the Standard Model
-related to them. We then compare the effects of these extensions with collected data to see 
-if our new theory more closely describes Nature or not.
+To make matters even worse, three of the massive particles are massless in the Standard Model.
+In this thesis, we focus on the said particles -- the neutrinos -- and propose extensions to the Standard Model related to them. 
+We then compare the effects of these extensions with collected data to see if our new theory more closely describes Nature or not.
 
 Ultimately, the purpose of this excursion is to guide future research where to uncover more accurate theories.
-Traces of this grander theory will be present as breadcrumbs in Nature, we just need to know where 
-and how carefully to look.
+Traces of this grander theory will be present as breadcrumbs scattered in Nature. We just need to know where and how carefully to look.
 
 \section{Outline}
-This thesis is outlined as follows. In Chapter~\ref{ch:osc}, we briefly review the most relevant parts 
-of the Standard Model that will be relevant for our extensions of it. Then we present the evidence and 
-subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel physics prize, 
-along with the modifications to the Standard Model needed to accomodate the discovery. The 
-reader is then introduced to a standard but detailed derivation of the neutrino mixing matrix
-and oscillation Hamiltonian, including the matter 
-effects stemming from charged and neutral current weak interactions within the Earth.
+This thesis is outlined as follows. In Chapter~\ref{ch:osc}, we briefly review the most relevant parts of the Standard Model that will be relevant for our extensions of it.
+Then we present the evidence and subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel physics prize, along with the modifications to the Standard Model needed to accommodate the discovery.
+The reader is then introduced to a standard but detailed derivation of the neutrino mixing matrix and oscillation Hamiltonian, including the matter effects stemming from charged and neutral current weak interactions within the Earth.
 
-In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating
-from cosmic ray interactions in the atmosphere of the Earth. Furthermore, we introduce the reader to 
-the two present Antarctic neutrino detectors: IceCube and DeepCore. We also give a brief summary 
-about a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which 
-we will use as a forecast in our analysis.
+In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating from cosmic ray interactions in the atmosphere of the Earth. 
+Furthermore, present the two present Antarctic neutrino detectors: IceCube and DeepCore.
+We also summarize a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which we will use as a forecast in our analysis.
 
-Chapter~\ref{ch:theory} consists of two parts. In Section~\ref{sec:anomalies}, we 
-introduce a new particle: the sterile neutrino. We present how neutrino oscillations are
-modified by this hypothesized fourth neutrino, and how these modifications would appear in IceCube if 
-the particle is present in Nature. In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside,
-and instead turn to the interactions between neutrinos and the Earth. We again amend the Standard Model by 
-considering exotic interactions from a higher energy theory, manifesting themselves as sub-leading modifications 
-to the matter potential. These new interactions are not present in the Standard Model and are thus called 
-non-standard interactions (NSI).
+Chapter~\ref{ch:theory} consists of two parts. In Section~\ref{sec:anomalies}, we introduce a new particle: the sterile neutrino. 
+We present how neutrino oscillations are modified by this hypothesized fourth neutrino and how these modifications would appear in IceCube if the particle is present in Nature. 
+In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside and instead turn to the interactions between neutrinos and the Earth. 
+We again amend the Standard Model by considering exotic interactions from a higher energy theory, manifesting themselves as sub-leading modifications to the matter potential. 
+Since these new interactions are not present in the Standard Model, we call them non-standard interactions (NSI).
 
 Finally, Chapter~\ref{ch:results} contains the result from our two separate extensions of the Standard Model.
-In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with
-literature. In Section~\ref{sec:nsiResults}, we present new constrained bounds on the NSI parameters by 
-combining our results for IceCube, DeepCore, and PINGU.
+In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with literature. 
+In Section~\ref{sec:nsiResults}, we present new constrained bounds on the NSI parameters by combining our results for IceCube, DeepCore, and PINGU.

### 2021-06-16 thesis/tex/nsiTheory.tex
update

@@
 indicate that these particles provide the best starting point for us to probe new physics, in which 
-other neutrino interactions might occur~\cite{gavela2009}. We call these interactions non-standard interactions (NSI).
+exotic neutrino interactions might occur~\cite{gavela2009}. We call these interactions non-standard interactions (NSI) in order to 
+distinguish them from the `standard' interactions of the Standard Model.
 
@@
 theory will have different interactions than those we presently know. These new interactions can be parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
-Following the discussion in~\cite{tommyNSI}, the six-dimensional NSI parameters $\epsilon$ have the scale
+Following the discussion in~\cite{tommyNSI}, we see that the NSI parameters $\epsilon$ resulting from six-dimensional operators have the scale
 \begin{align}
@@
 Now we repeat our proability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
-we have rapid oscillations, which means that "indirect" modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
+we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
 will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
@@
 
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=0.8\textwidth]{figures/DC_event_pulls.pdf}
+        \caption{Plots of the quantity $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$, displaying which 
+        reconstructed bins the NSI signal is most clear.}
+        \label{fig:event_pulls}
+    \end{center}
+\end{figure}
+%TODO: talk a bit about this. Compare cascades to tracks
+
 % \end{document}

### 2021-06-16 thesis/tex/oscillations.tex
update

@@
 \subsection{Mass Generation}
-In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermions right and left-handed components.
+In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
 All neutrinos are left-handed and all antineutrinos are right-handed. Thus, neutrinos are massless since they do not undergo the Higgs mechanism.
@@
 \end{align}
-First, calculate the sum using trace technology %TODO: explain this more
+First, calculate the sum using trace technology
 \begin{align}\label{eq:helicity_sum}
@@
     V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
-           &= \SI{3.8e-23}{\eV\, \gram \cm^{-3}}\,,
+           &= \SI{3.8e-23}{\eV \gram \cm^{-3}}\,,
 \end{align}

### 2021-06-16 thesis/tex/sterileTheory.tex
update

@@
 sterile neutrino is in the \si{\eV\squared} scale, while the two others
-are three and five magnitudes smaller. To remind us of this difference, we write $3+1$, since the sterile state 
+are three and five magnitudes smaller. To remind us of this hierarchy, we write $3+1$, since the sterile state 
 proposed is a lot more massive than the active states.
@@
 Now, looking at Eqs.~\ref{eq:U4gen_param} and~\ref{eq:dm4gen}, we see that we have introduced four new parameters: $\dm[41]$, $\theta_{14}$
-, $\theta_{24}$, $\theta_{34}$.
+, $\theta_{24}$, $\theta_{34}$. In our analysis, we reduce the number of parameters by only considering $\dm[41]$ and $\theta_{24}$, which are 
+the most important for the $\nm$ oscillations. In fact, one can close the $e$ channel by letting $\theta_{14} = 0$ in the \si{\GeV} to \si{\TeV} range, thus 
+using a two-flavor neutrino approximation. This is not done in this work.
 
@@
     \centering
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.35\textwidth}
         \includegraphics[width=1\linewidth]{figures/sterile_resonance.pdf}
-        \caption{$\Pamam$ disappearance}\label{fig:sterile_resonance}
+        \caption{$\Pamam$ resonant disappearance}\label{fig:sterile_resonance}
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.69\textwidth}
         \includegraphics[width=1\linewidth]{figures/resonance_shift.pdf}
-        \caption{$\Pamam$ disappearance}\label{fig:resonance_shift}
+        \caption{Shifting and amplification of the resonance by altering $\dm[41]$ and $\theta_{24}$, respectively.}\label{fig:resonance_shift}
     \end{subfigure}
-\end{figure} %TODO: better captions
+\end{figure}
 
@@
 We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
-%TODO: more? mention that Pmm=1 at TeV for 3+0
+In the $3+0$ scenario, $\Pamam = 1$ in this range. Thus, if we are able to see a $\anm$ disappearance in the \si{\TeV} region,
+we are in a good position to argue for a \si{\eV} scale $\dm[41]$.
 

### 2021-06-16 src/events/DC/event_processing.py

@@ -129,16 +129,19 @@ def marginalize(chisq,dm31_range, th23_range, ett_range, emt_range, eem_range, e
     N = len(th23_range)*len(dm31_range)
     if len(th23_range) > 1 and len(dm31_range) > 1:
         marginalized_chisq = simps(simps(reshaped_chisq))/N #Integrate out oscillation parameters and "normalize"
+    elif len(th23_range) > 1 and len(dm31_range) == 1:
+        marginalized_chisq = simps(reshaped_chisq, axis=4)/N #Integrate out oscillation parameters and "normalize"
     else:
         marginalized_chisq = reshaped_chisq[:,:,:,:,0,0]
     best_eet_index, best_eem_index, best_emt_index, best_ett_index, best_th23_index, best_dm31_index = np.unravel_index(best_fit_index,reshaped_chisq.shape)
     
     deltachi = marginalized_chisq - marginalized_chisq.min()
-    return deltachi, best_dm31_index, best_th23_index, best_ett_index, best_emt_index, best_eem_index, best_eet_index
+    return deltachi.T, best_dm31_index, best_th23_index, best_ett_index, best_emt_index, best_eem_index, best_eet_index
 
 def marginalize_one(deltachi, axis):
     '''
-    Assumes 3 axes with same length
+    Assumes 3 axes with same length.
+    Integrates out the axis specified and returns deltachi
     '''
     from scipy.integrate import simps 
     N = deltachi.shape[axis]

### 2021-06-16 src/events/IC/make_sterile_events.py

@@ -37,7 +37,7 @@ if __name__ == '__main__':
     param_list = list_of_params(params, dm41_range, s24_range)
 
 
-    print(f'Precomputing IO IC events for dm41({dm41_range.min()},{dm41_range.max()},{len(dm41_range)}),',
+    print(f'Precomputing NO IC events for dm41({dm41_range.min()},{dm41_range.max()},{len(dm41_range)}),',
             f's24({s24_range.min()},{s24_range.max()},{len(s24_range)})')
 
 

### 2021-06-17 src/events/IC/make_sterile_events.py
update

@@ -12,10 +12,10 @@ from functions import ic_params
 
 parser = argparse.ArgumentParser()
 parser.add_argument('-dm41From', default=0.01, type=float)
-parser.add_argument('-dm41To', default=10, type=float)
+parser.add_argument('-dm41To', default=2, type=float)
 parser.add_argument('-dm41N', default=10, type=int)
 
-parser.add_argument('-s24From', default=0.01, type=float)
+parser.add_argument('-s24From', default=0.005, type=float)
 parser.add_argument('-s24To', default=1, type=float)
 parser.add_argument('-s24N', default=10, type=int)
 
@@ -44,12 +44,7 @@ if __name__ == '__main__':
     from multiprocessing import Pool
     p = Pool()
     data = [(i,j,alpha, args.N,p, [False, 0, 0],False, False,False,4) for p in param_list for i in range(13) for j in range(20)]
-    #H1_events_list = p.starmap(get_events, data)
-    #p.close()
-    #H1_events_list = np.array(H1_events_list).reshape(len(dm41_range)*len(s24_range),13,20)
-    #pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}.p','wb'))
-    data = [(i,j,alpha, args.N,params, [False, 0, 0],True, False,False,4) for i in range(13) for j in range(20)]
-    H0_events_list = p.starmap(get_events, data)
+    H1_events_list = p.starmap(get_events, data)
     p.close()
-    H0_events_list = np.array(H0_events_list).reshape(1,13,20)
-    pickle.dump(H0_events_list,open(f'./pre_computed/H0_IC_N{args.N}.p','wb'))
+    H1_events_list = np.array(H1_events_list).reshape(len(dm41_range)*len(s24_range),13,20)
+    pickle.dump(H1_events_list,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}.p','wb'))

### 2021-06-17 thesis/tex/sterileResults.tex
update

@@
 Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate with angle $\beta$ around the median zenith angle of $\zreco = -0.5$.
-We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a percentage of our own choosing,
-typically a value between 0 and 20 \%.
+We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a percentage of our own choosing.
 
@@
 those parameter pairs can be excluded at a certain confidence level.
+
+By tuning the scaling $f$ of the uncorrelated systematic error, we can shift the contour. We extract the contour from the 
+IceCube sterile analysis~\cite{IC2020}, and compare in Fig.~\ref{fig:error_tuning}. We see that the contour in the 
+higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensetive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
+remains fixed. We put $f=35\%$ and compare our results to the Giunti et al.~\cite{gariazzoUpdatedGlobalAnalysis2017} in Fig.~\ref{fig:s24_contour}.
+Here, we see that our lower fixed region between \SIrange{1e-1}{1}{\eV\squared} is closer to the IceCube result than Giunti et al, but that 
+our contour slightly diverges above \SI{1}{\eV\squared}. 
 \begin{figure}
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/final_rate_plot.pdf}
-    \caption{}\label{fig:final_rate_plot}%TODO: update
+    \includegraphics[width=0.8\textwidth]{figures/s24_error_tuning.pdf}
+    \caption{The 90\% CL contour with two different systematic error scalings, compared 
+    with the official IceCube result from~\cite{IC2020}}\label{fig:error_tuning}
 \end{figure}
@@
     \includegraphics[width=0.8\textwidth]{figures/s24_contour.pdf}
-    \caption{}\label{fig:s24_contour}%TODO: update
+    \caption{The 90\% CL contour using $f=35\%$, compared with the official IceCube result from~\cite{IC2020}
+    and the result from~\cite{gariazzoUpdatedGlobalAnalysis2017}}\label{fig:s24_contour}
 \end{figure}
+
+We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit sterile hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
+sterile hypothesis compares to data.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/final_rate_plot.pdf}
+    \caption{The predicted binned event count assuming our best-fit sterile hypothesis, compared with the 
+    null and data.}\label{fig:final_rate_plot}
+\end{figure}
+
 %\end{document}

### 2021-06-23 thesis/tex/nsiTheory.tex
update

@@
 
-Compared to other fermions, the lightness of neutrino masses along with their sparse SM interactions might 
+Compared to other fermions, the lightness of neutrino masses\footnote{The extreme lightness might be explained 
+by a mass generation at a higher order theory.} along with their sparse SM interactions might 
 indicate that these particles provide the best starting point for us to probe new physics, in which 
@@
 
-% Moreover, it is common to subtract $\emm$ from the diagonal, which
+By combining oscillation data and neutrino-nucleon scattering at the COHERENT experiment, 90 \% CL ranges of some of 
+the NSI parameters were constrained in~\cite{coherent} to
+\begin{align}\label{eq:coherentbounds}
+    -0.090 < &\ett < 0.38 \nonumber \\
+    -0.01 < &\emt < 0.009 \nonumber \\
+    -0.073 < &\eem < 0.044 \nonumber \\
+    -0.15 < &\eet < 0.13\,.
+\end{align}
+
 % we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
-% probabilities. So just as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
+% probabilities. So jusb t as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
 % Our NSI potential matrix now takes the form 
-% \begin{align}
+% {µmmb m  m mb  mb  mbb  mb bmMoreover, it is common to subtract $\emm$ from the diagonal, which
+% \begin{align} m mmb
 %     \begin{pmatrix}
@@
 Since all standard matter potentials are diagonal, 
-the elements $\epsilon_{\a\b}, \a = \b$ will directly adjust the matter potential felt 
+the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
 by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,

### 2021-06-24 thesis/tex/introduction.tex
update

@@
 antimatter \emph{annihilates} the matter, resulting in pure light. Since the universe exists,
-there must have been more matter than antimatter at the Big Bang. %TODO: check and make better
+there must have been more matter than antimatter at the Big Bang. This baryon asymmetry is unexplained in the Standard 
+Model.
 Dark matter is heavy matter which does not interact with electromagnetic radiation.
 No such particle exists in the Standard Model.}.
-
-To make matters even worse, three of the massive particles are massless in the Standard Model.
+To make matters even worse, three of the massless particles have been observed to have mass.
 In this thesis, we focus on the said particles -- the neutrinos -- and propose extensions to the Standard Model related to them. 

### 2021-06-24 thesis/tex/oscillations.tex
update

@@
 In 1998, the Super-Kamiokande collaboration detected a $\nm$ deficit that could not be explained by any other mechanism
-than the conversion muon neutrinos to electron neutrinos. This was the first conclusive evidence of a $\nm \to \ne$ oscillation.
+than the conversion of muon neutrinos to electron neutrinos. This was the first conclusive evidence of a $\nm \to \ne$ oscillation.
 The most interesting conclusion from the observation of neutrino flavor oscillations is the equivalence between oscillations and neutrino mass, 
 with the latter being identically zero acording to the Standard Model. Thus, we are required to extend the Standard Model to incorporate neutrino 
-masses and hence, neutrino oscillations.
+masses before we discuss the neutrino oscillations themselves.
 
@@
     \sum_\a U_{\a k}\ket{\na} &= \sum_{\alpha, j} U_{\a k} U_{\a j}^\dagger \ket{\nu_j} \nonumber \\
-    \sum_\a U_{\a k}\ket{\na} &= \sum_{j} \delta_{kj} \ket{\nu_j} \nonumber \\
-    \sum_\a U_{\a k}\ket{\na} &= \ket{\nu_k}\,,
+                              &= \sum_{j} \delta_{kj} \ket{\nu_j} \nonumber \\
+                              &= \ket{\nu_k}\,,
 \end{align}
@@
     \ket{\na(t)} &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\ket{\nu_k} \nonumber \\
-    \ket{\na(t)} &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
-    \ket{\na(t)} &= \sum_{k,\b} U^\dagger_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
+                 &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
+                 &= \sum_{k,\b} U^\dagger_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
 \end{align}
@@
             &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\exp(-i\frac{\dm_{kj}x}{2E})\right] \nonumber \\
-            &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\cos(\frac{\dm_{kj}x}{2E})\right] \nonumber \\
+            %&= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\cos(\frac{\dm_{kj}x}{2E})\right] \nonumber \\
             &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
 \end{align}
-which is the probability of neutrino vacuum oscillations. %TODO: maybe plot?
+which is the probability of neutrino vacuum oscillations.
 The calculation for antineutrinos yield the same result if one continues to assume the realness of the mixing matrix. 
@@
 is approximately the Earth diameter, and will be the maximum travel distance which we will use later on.}.
-In the left-most panel, we see a supressed $\nu_\mu \to e$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
+In the left-most panel, we see a supressed $\nm \to \ne$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
 numerical values of the mixing matrix in Eq.~\ref{eq:Uvalues}.
@@
 \begin{align}\label{eq:e_states}
-    \ket{e(p_e,h_e)} = \frac{1}{2E_eV}a_e^{(h_e)\dagger}(p_e)\ket{0}\,,
+    \ket{e(p_e,h_e)} = \frac{1}{2E_eV}\, a_e^{(h_e)\dagger}(p_e)\ket{0}\,,
 \end{align}
@@
 \begin{align}\label{eq:avg_H1}
-    \avg{H_{CC}} &= \int \dd p_e^3 \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
+    \avg{H_{CC}} &= \int \dd p_e^3\, \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
            &= \frac{G_F}{\sqrt{2}} \int \dd p_e^3 \bra{e(p_e,h_e)} \left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right]  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \left[\bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x) \right] \ket{e(p_e,h_e)} \nonumber \\
@@
         0 & 0 & V_{NC} \\
-    \end{bmatrix} = V_{CC}\, \delta_{\alpha e} + V_{NC}\,.
+    \end{bmatrix} = V_{CC}\, \delta_{\alpha e}\mathbb{1} + V_{NC}\mathbb{1}\,.
 \end{align}
@@
 where $H_0$ is the Hamiltonian in vacuum, and $H_{I}$ is our interaction Hamiltonian associated with our matter potentials.
-Let the wavefunction that describes the $\nu_\a \to \nu_\b$ transition be 
+Let the wavefunction that describes the $\nu_\a \to \nu_\b$ transition be denoted as
 \begin{align}
-    \bra{\nu_\b}\ket{\nu_\a (t)}\,,
+    \psi_{\a\b}(t) = \bra{\nu_\b}\ket{\nu_\a (t)}\,,
 \end{align}
@@
 \end{align}
-Using Eq.~\ref{eq:V_matrix}, we rewrite this as
+Using Eq.~\ref{eq:V_matrix} in component form, we rewrite this as
 \begin{align}\label{eq:V_rewrite}
@@
 \end{align}
-In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  which does not affect the probability since it is a common term to all flavor states. It can be rotated away.
+In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  is a common term to all flavor states, and does not affect the probability. It can be rotated away.
 Thus

### 2021-06-24 thesis/tex/sterileTheory.tex
update

@@
 In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}.  
-Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
+Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but observed an excess in the
 $\ne$ events too. Together with the so-called reactor and gallium anomalies, these reports suggested 
@@
 By introducing a fourth heavy mass state $\nu_4$, both appearance and disappeareance anomalies could be minimally accomodated.
-
 However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species\footnote{
@@
 \subsection{The Hamiltonian}
-The inclusion of the sterile state in the Hamiltonian is straightforward. We extend the PMNS matrix to incorporate the new flavor and mass eigenstates: 
+The inclusion of the sterile state in the Hamiltonian is straightforward. We extend the PMNS matrix
+with terms for the mixing between the new flavor $(U_{si})$ and mass $(U_{\a 4})$ eigenstates:
 \begin{align}
@@
 \end{align}
+This parametrization does not affect the physics, but determines the structure of the mixing angles.
+
 The mass matrix extends analogously:
@@
 
-Now, the interaction with matter requires a careful reconsideration of the matter potential. We start of with the unaltered potential matrix. 
+Now, the interaction with matter requires a careful reconsideration of the matter potential. We start off with the unaltered potential matrix from Eq.~\ref{eq:V_matrix}. 
 Just as with the PMNS matrix, we extend this to $4\times4$:
@@
 does not participate in any interaction\footnote{The exception to this is of course gravity. The sterile neutrino is not massless.}. Thus, all potential terms involving the sterile state are zero. 
-In other words, the potential matrix in Eq.~\ref{eq:Vsterile1} is complete, save for the usual subtraction by a constant identity matrix:
+In other words, the potential matrix in Eq.~\ref{eq:Vsterile1} is complete, save for the usual subtraction by a constant times the identity matrix:
 

### 2021-07-29 presentation/manus.tex
update

\documentclass{article}
\begin{document}
There is no reason for us to believe that our current knowledge in particle physics is complete. The most
successful framework – the Standard Model – has notable shortcomings. It doesn't explain dark matter.
Neither does it explain why the universe didn't get annihilated by anti-matter at the Big Bang.
To make matters
even worse, three of the massless particles have been observed to have mass. In this thesis, we focus on
the said particles – the neutrinos – and propose extensions to the Standard Model related to them. We
then compare the effects of these extensions with collected data to see if our new theory more closely
describes Nature or not.
Ultimately, the purpose of this excursion is to guide future research where to uncover more accurate
theories. Traces of this grander theory will be present as breadcrumbs scattered in Nature. We just need
to know where and how carefully to look.

In order to describe the three quantizable forces (interactions) of nature, we gather the mediators of each force – the
vector bosons – into local symmetry groups called gauge groups. Each vector boson has one corresponding generator,
the set of which constitutes the group. The strong charge is mediated by eight massless gluons, which
correspond to the eight independent generators of SU(3). The weak charge is mediated by the three massive gauge
bosons W and Z, and the massless photon γ, which constitute the generators of SU(2) and U(1).
The subscript of each group denotes by which mechanism that force is mediated. The gluons mediate
the strong force through interactions of color, emphasized with subscript C. The weak force only sees
left-handed particles, which we distinguish with the subscript L. And the electroweak interaction that
a particle undergoes is determined by its hypercharge Y. For example, the quarks all have a nonzero
color and hypercharge, so they participate in the strong and electromagnetic interactions. If a quark is
left-handed, it will also feel the weak interaction. The neutrinos on the other hand, have neither charge
nor color, so they are insivible to both the strong and electromagnetic force. We express this by letting
their fields transform as singlets under those SU(3) and U(1).
Together, these three interactions make up the Standard Model gauge group SU(3)_C × SU(2)_L ×
U(1)_Y.

TODO: NEUTRINO OSCILLATIONS AND MATTER EFFECTS

We always observe neutrinos indirectly through their associated charged lepton. Regardless of the type
of interaction (charged current via the W boson, or neutral current via the Z), a charged lepton exits
with altered properties. The lepton is then detected, and the properties of the neutrino involved in the
interaction is then deduced. This deduction is obviously imperfect.

TODO: ABOUT ICECUBE
In this work, we only study the detectors handeled by the IceCube collaboration.
They are of
Cherenkov type, which means that they detect the secondary charged lepton by its emitted Cherenkov
light, produced from its travel through the Antarctic ice. If the charged leptons interact heavily with the
ice, they will travel a short distance and emit a localized flash of Cherenkov light. This event is referred
to as a cascade.
If the charged leptons don’t interact as much in the ice, they penetrate a larger part of it,
emitting light and tertiary particles as they go. This event is referred to as a track, and are often due to
muon charged current interactions.
After an event has occurred, the IceCube algorithms process the data coming from the detector to
reconstruct the event. This means that, given the parameters recorded by the detector, what are their
”true” values? We are interested in two variables: the energy and the direction. Each event is tagged with
a probable energy and zenith angle, called the recostructed parameters Ereco and cos (θrecoz), which are
the parameters according to the DOMs. The collaboration then uses numerous sophisticated methods to
backtrack the reconstructed parameters to the true parameters. So a charged lepton hits the DOMs, and
we ultimately end up with the associated neutrino’s true and reconstructed energy and zenith angle. The
reconstructed parameters are what we are using to analyze the data (because this is what the detector
actually sees), while the true parameters are used in the determination of that neutrino’s ‘actual’ flux
and cross-section (because this is what Nature sees).

As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact with
charged lepton in the ice. We now are interested in the effective area Aeff, i.e. the cross-section of the
detector that the lepton is exposed to. Aeff depends on several parameters, some of them being detector
physical volume, Etrue, cos(θtruez) and the neutrino cross-section.

So now we have the physical quantities in the true parameters. But as we discussed, we need a way to
translate this into the reconstructed parameters that the detector gives us. We will call the relationship
between Ereco and Etrue the energy resolution function, and the relationshop between cos (θrecoz) and
cos (θtruez) the zenith resolution function. We assume the relationship to follow a logarithmic Gaussian
distribution, giving it the form ....

So how do we then obtain the parameters needed to construct the Gaussian?
The collaboration frequently releases their own simulated data files, which we refer to the IceCube Monte Carlo.
In the files, we can see the connection between the true and reconstructed parameters. We use this to train a Gaussian
Process Regressor.
TODO: ABOUT GPR

Independent researchers outside of the IceCube collaboration will not be able to more persicely simulate
the detector. The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this
section is to come as close as we can to their Monte Carlo simulations. After we are confident that our
code displays the same overall features as the ‘offical’, we normalize our results to it.
For each bin i, j, we then obtain a correction factor which contains information that we are unable to
obtain or sufficiently incorporate. One example of such information is the systematic errors of the DOMs.
Recent IceCube data releases do not include such information. Since the systematic errors are affecting
the event count on a bin-by-bin basis, they can in theory drastically modify the binned results. Another
example of an error source what will be remedied by this method is the flux. We are using a fairly simple
model of the atmospheric flux that excludes atmospheric prompt and astrophysical fluxes. The IceCube
collaboration use several different flux models which are initialized by a parametrization of the cosmic
ray flux. Included in the cosmic ray models are e.g. the pion to kaon ratio, which are often used as a nuisance parameter. By not
being able to include this in our error analysis, our method will be limited to only consider the overall flux normalization,
rather than the components that produce the flux in the first place.

In 1996, the LSND experiment reported an excess of ¯νe events from an ¯νµ beam [17]. Nine years later,
MiniBooNE not only reproduced the ¯νe anomaly, but observed an excess in the νe events too. Together
with the so-called reactor and gallium anomalies, these reports suggested that the three massive neutrino
framework could be amended.
By introducing a fourth heavy mass state ν4 at eV scale, both appearance and
disappeareance anomalies could be minimally accomodated. However, we know from the decay width
of the Z boson that it only can interact with three flavor species1, so this fourth mass state cannot be
interacting weakly. In other words, it needs to transform as a singlet under the broken gauge group
SU(2)L × U(1)EM. We now distinguish between the three original neutrino flavors (e, µ, and τ) and the
new fourth flavor by calling the former active neutrinos and the latter sterile due to its non-interacting
behavior.

Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing
angle θi4 is non-zero, we allow the sterile mass state to mix with the active state i. The most interesting
case is when θ24 ̸= 0, which for ∆m2
41 ∼ eV2 gives rise to a resonant disappeareance in the for P¯νµ¯νµ

We have no reason to believe that the Standard Model gauge group is the complete picture. We have
already seen how the failure of the Standard Model to predict neutrino masses and flavor osillations forces
us to amend it. Just as the electroweak theory SU(2)L × U(1)Y is spontaneously broken to U(1)EM,
a higher order theory at a different energy scale with completely different properties might undergo a
similar spontaneous symmetry break at high energies, producing at lower energies the Standard Model
that we know. In fact, just as the fermion masses originate from the electroweak symmetry breaking,
the neutrino masses might be generated from another broken symmetry resulting in the Standard Model
gauge group. In this sense, the Standard Model might be considered an effective low energy theory,
which is yiels impressive results in some areas, but failing in others.

Compared to other fermions, the lightness of neutrino masses4 along with their sparse SM interactions
might indicate that these particles provide the best starting point for us to probe new physics, in which
exotic neutrino interactions might occur [21]. We call these interactions non-standard interactions (NSI)
in order to distinguish them from the ‘standard’ interactions of the Standard Model.
Following the approach of the Standard Model that the group generators uniquely determine the gauge
bosons, a different gauge theory will have different interactions than those we presently know. These
new interactions can be parametrized as model-independent four-fermion effective operators [22, 23].
Following the discussion in [24], we see that the NSI parameters ϵ resulting from six-dimensional operators
have the scale ...

Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.
We can phenomenologically allow these interactions to include the up and down quarks which are present
in the Earth as the fundamental components of neutrons and protons.
The CC NSI effect affects neutrino production and
detection, and will not be considered here. NC NSI affect the matter potential, and is thus of interest
to us.

Off-iagonal NSI parameters constitute new sources of flavor violation, while diagonal elements represent 
flavor nonuniversality.

In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any
theory which does not modify Pαµ. Moreover, the IceCube data is avaibable in the range 500 GeV to
10 TeV range, where any rapid oscillations have settled down.

\end{document}

### 2021-07-29 thesis/tex/ICtheory.tex
update

@@
 i.e.~the cross-section of the detector that the lepton is exposed to.
-$\Aeff$ depends on several parameters, some of them being detector physical volume, $\Etrue$,$\ztrue$ and the neutrino cross-section.
+$\Aeff$ depends on several parameters, some of them being detector physical volume, $\Etrue$, $\ztrue$ and the neutrino cross-section.
 Fortunately, the binned $\Aeff$ is provided to us by the collaboration~\cite{ICaeff}.
@@
 Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$.
-Just as with the fluxes, we interpolate this in $\Etrue,\ztrue$ and show the result %TODO aeff interpolation
+Just as with the fluxes, we interpolate this in $\Etrue$, $\ztrue$ and show the result %TODO aeff interpolation
 
@@
     \includegraphics[width=0.8\linewidth]{figures/IC_data.pdf}
-    \caption{IceCube track events from~\cite{IC2020}}\label{fig:IC_data}
+    \caption{IceCube track events from~\cite{IC2020}.}\label{fig:IC_data}
 \end{figure}
@@
 \subsection*{Monte Carlo normalization}
-Independent researchers outside of the IceCube collaboration will not be able to more persicely
+Independent researchers outside of the IceCube collaboration will not be able to more percisely
 simulate the detector. The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this 
@@
     \includegraphics[width=0.8\linewidth]{figures/IC_MC_norm.pdf}
-    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as ´Null' in the plots.}\label{fig:IC_MC_norm}
+    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
 \end{figure} 

### 2021-07-29 thesis/tex/nsiTheory.tex
update

@@
 the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
-by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as the open up matter interactions across flavors. Remember, in the Standard model,
-we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions.
+by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
+we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
+the off-diagonal elements constitute new soures of flavor violation.
 Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently

### 2021-07-29 thesis/tex/sterileTheory.tex
update

@@
 we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
-which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the for $P_{\anm\anm}$, shown in Fig.~\ref{fig:sterile_resonance}.
+which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the for $P_{\bar{\mu}\bar{\mu}}$, shown in Fig.~\ref{fig:sterile_resonance}.
 

### 2021-07-29 src/data/IC/importer.py

@@ -263,5 +263,7 @@ def fit_flux(flux_df,zmin):
     y_new_ebar = model_ebar.predict(np.log10(x_new.reshape(-1,1)))
 
     return pd.DataFrame(np.transpose([x_new, 10**y_new_m, 10**y_new_mbar, 10**y_new_e, 10**y_new_ebar, zmin*np.ones(100), (zmin + 0.1)*np.ones(100)]),columns=['GeV', 'm_flux','mbar_flux','e_flux', 'ebar_flux', 'z_min','z_max'])
+
+
 if __name__ == '__main__':
     get_flux_factor()

### 2021-07-29 src/data/IC/processer.py

@@ -27,15 +27,6 @@ def get_flux(flavor,E,z,df):
         raise KeyError('NYI for tau flux')
     return np.abs(flux_avg) 
 
-
-def get_aeff_dc(E,interpolator):
-    try:
-        return interpolator(np.log10(E))
-    except ValueError: #extrapolate
-        y1 = interpolator(1.13)
-        y2 = interpolator(1.2)
-        return (y2-y1)/(1.2-1.13) * np.log10(E)
-
 def interpolate_aeff(recompute):
     if recompute:
         df = get_aeff_df()
@@ -197,46 +188,6 @@ def generate_probabilities(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,p
             with open(f'./pre_computed/IC/hashed_params.csv','a') as fd:
                 fd.write(f'{params};{hashed_param_name}\n')
     return prob
-
-
-def get_probabilitiesOLD(flavor_from, flavor_to, E_bin,z_bin,params,anti,N, ndim=4):
-    '''
-    Name of resulting .npy is the sha256 hash of the parameter dictionary used to generate the probablities.
-    '''
-
-    hashed_param_name = sha256(params) #Get hash of parm dict to be used as filename
-    if anti:
-        file_dir = f'./pre_computed/{ndim}gen/Pa{flavor_from}a{flavor_to}/{N}/'
-    else:
-        file_dir = f'./pre_computed/{ndim}gen/P{flavor_from}{flavor_to}/{N}/'
-    df = pickle.load(open(f'{file_dir}E{E_bin}z{z_bin}.p','rb'))
-    res = df[hashed_param_name][f'E{E_bin}z{z_bin}']
-    return res
-
-def generate_probabilitiesOLD(flavor_from, flavor_to, E_range,z_range,E_bin,z_bin,params,anti,N, ndim=4, nsi=False):
-    '''
-    Name of resulting .csv is the sha256 hash of the parameter dictionary used to generate the probablities.
-    '''
-
-    filename = sha256(params) #Get hash of parm dict to be used as filename
-    if anti:
-        file_dir = f'./pre_computed/{ndim}gen/Pa{flavor_from}a{flavor_to}/{N}/E{E_bin}z{z_bin}/'
-    else:
-        file_dir = f'./pre_computed/{ndim}gen/P{flavor_from}{flavor_to}/{N}/E{E_bin}z{z_bin}/'
[…]

### 2021-07-29 src/events/DC/event_processing.py

@@ -128,9 +128,9 @@ def marginalize(chisq,dm31_range, th23_range, ett_range, emt_range, eem_range, e
     reshaped_chisq = chisq.reshape(len(eet_range),len(eem_range),len(emt_range),len(ett_range), len(th23_range), len(dm31_range))
     N = len(th23_range)*len(dm31_range)
     if len(th23_range) > 1 and len(dm31_range) > 1:
-        marginalized_chisq = simps(simps(reshaped_chisq))/N #Integrate out oscillation parameters and "normalize"
+        marginalized_chisq = marginalize_one(marginalize_one(reshaped_chisq, dm31_range, 5), th23_range, 4)
     elif len(th23_range) > 1 and len(dm31_range) == 1:
-        marginalized_chisq = simps(reshaped_chisq, axis=4)/N #Integrate out oscillation parameters and "normalize"
+        marginalized_chisq = marginalize_one(reshaped_chisq, th23_range, axis=4)
     else:
         marginalized_chisq = reshaped_chisq[:,:,:,:,0,0]
     best_eet_index, best_eem_index, best_emt_index, best_ett_index, best_th23_index, best_dm31_index = np.unravel_index(best_fit_index,reshaped_chisq.shape)
@@ -138,15 +138,16 @@ def marginalize(chisq,dm31_range, th23_range, ett_range, emt_range, eem_range, e
     deltachi = marginalized_chisq - marginalized_chisq.min()
     return deltachi.T, best_dm31_index, best_th23_index, best_ett_index, best_emt_index, best_eem_index, best_eet_index
 
-def marginalize_one(deltachi, axis):
+def marginalize_one(y, x_range, axis):
     '''
     Assumes 3 axes with same length.
-    Integrates out the axis specified and returns deltachi
+    Integrates out the axis specified and returns
     '''
     from scipy.integrate import simps 
-    N = deltachi.shape[axis]
-    marginalized_chisq = simps(deltachi, axis=axis)/N #Integrate out oscillation parameters
-    return marginalized_chisq - marginalized_chisq.min()
+    N = y.shape[axis]
+    marginalized_chisq = simps(y = y, axis=axis)/N
+    #marginalized_chisq = simps(y = y, x = x_range, axis=axis)*N
+    return marginalized_chisq
 
 def get_param_list(dm31N,th23N, ett_tuple, emt_tuple, eem_tuple, eet_tuple, IO=False):
     ettFrom, ettTo, ettN = ett_tuple

### 2021-07-29 src/events/IC/event_processing.py

@@ -1,16 +1,13 @@
-import sys,os
+import sys
 if __name__ == '__main__':
-    os.chdir('../../')
     sys.path.append('./src/data')
     sys.path.append('./src/events')
     sys.path.append('./src/probability')
 import numpy as np
 import matplotlib.pyplot as plt
-import matplotlib
 import pandas as pd
 from IC.importer import *
 from IC.processer import *
-from IC.main import sim_events, list_of_params, ic_params
 from functions import perform_chisq
 from scipy.stats import chi2
 
@@ -171,34 +168,6 @@ def normalize_bin_by_bin(simulated_events, MC = True, MC_old=False, correct_flux
     return np.array(normalization)
 
 
-def is_precomputed(N,ndim, dict, check=False, quick=True):
-    for anti in [True,False]:
-        for flavor_from in ['e','m']:
-            flavor_to  = 'm'
-            try:
-                if quick:
-                    get_probabilities(flavor_from, flavor_to, 5,5,dict,anti,N,ndim)
-                else:
-                    for Ebin in range(3,13):
-                        for zbin in range(0,20):
-                            get_probabilities(flavor_from, flavor_to, Ebin,zbin,dict,anti,N,ndim)
-            except (FileNotFoundError,KeyError):
-                if check:
-                    return False
-                else:
-                    if quick:
-                        raise FileNotFoundError(f'P{flavor_from}{flavor_to}, for N={N}, dm={dict["dm_41"]}, s24={np.sin(2*dict["theta_24"])**2}, s34={np.sin(2*dict["theta_34"])**2}, not found')
-                    else:
-                        raise FileNotFoundError(f'P{flavor_from}{flavor_to}, E{Ebin}z{zbin} for N={N}, dm={dict["dm_41"]}, s24={np.sin(2*dict["theta_24"])**2}, s34={np.sin(2*dict["theta_34"])**2}, not found')
-            return True
-
-def return_precomputed(N,ndim,params, nsi=False, quick=True):
-    params= np.array(params)
-    precomputed_list = np.array([is_precomputed(N,ndim, p, check=True,quick=quick) for p in params])
-    mask = precomputed_list == True
-    computed_params = params[mask]
-    return computed_params
-
 def normalize_events(H0_events,H1_events_list,z_bins):
[…]

### 2021-07-29 src/events/IC/main.py

@@ -1,40 +1,52 @@
-import sys,os
+import sys
 if __name__ == '__main__':
-    #os.chdir('../../')
     sys.path.append('./src/probability')
     sys.path.append('./src/data')
 import numpy as np
-from IC.processer import get_flux, generate_probabilities, get_probabilities, get_Etrue, get_interpolators,generate_probabilitiesOLD
+from IC.processer import get_flux, generate_probabilities, get_Etrue, get_interpolators
 from IC.importer import *
 from multiprocessing import Pool
 from functions import ic_params, integrate
-import time
 from scipy.stats import lognorm
 
 
-def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shift_parameters=[False, 2e3, 0.02], null=False, tau=False, nsi=False, ndim=4):
+def get_events(E_index, z_index, alpha, npoints, params=ic_params, spectral_shift_parameters=[False, 2e3, 0.02], null=False, tau=False, nsi=False, ndim=4, gen2=False):
     '''
-    Assume zr == zt, and thus the zenith resolution function is 1.
+    Gets the number of events (N_ij) in IceCube for E_index and z_index.
+    alpha: the percentile from which to sample true points from. 0.99 is recommended. Higher alpha needs flux for lower and higher energies.
+    npoints: the number of points in which to integrate over. Recommended values between 13 and 19.
+    params: dictionary with oscillation parameters
+    spectral_shift_parameters: list with 3 elements. If first is True, use spectral shifting. Second element is pivot point, third is delta gamma (shift).
+    null: If True, take P_amam == 1 (no sterile hypothesis)
+    tau: if True, use decayed tauons (17.39% BR) and include in final probability.
+    nsi: If True, construct Hamiltonian assuming NSI as specified in params.
+    ndim: Number of neutrino generations (active AND sterile)
+    gen2: If True, multiply Aeff by 5 to simulate Icecube Gen2
     '''
+
     E_buckets = 500*10**(np.linspace(0.0,1.3,14)) #log-binned in steps of 0.1 from 500 GeV to 500*1e1.3 GeV
     z_buckets = np.linspace(-1,0,21)
 
[…]

### 2021-07-29 src/probability/functions.py

@@ -410,4 +410,4 @@ def integrate(array,method='simps',*args):
     elif np.ndim(array) == 4:
         return simps(simps(simps(simps(array,args[0]),args[1]),args[2]),args[3])
 if __name__ == '__main__':
-    print(np.sqrt(2) * GF * 0.5 * N_A * 1 * (1/GeVtocm1)**3)
+    print(U_4(params=ic_params))

### 2021-07-29 src/probability/numerical.py

@@ -149,7 +149,7 @@ def P_num(flavor_from, flavor_to=None,ndim = 3, E=None,L_max=None,vacuum=False,a
     return np.abs(solver.y)**2
 
 
-def P_num_over_E(flavor_from, E, flavor_to=None, L=2*r_earth, zenith=-1,earth_start = 0, ndim = 3,vacuum=False, eval_at=None,anti=False,params=param_dict, material='earth', nsi=False,tols=(1e-3,1e-6)):
+def P_num_over_E(flavor_from, E, flavor_to=None, L=2*r_earth, zenith=-1, ndim = 3,vacuum=False, eval_at=None,anti=False,params=param_dict, material='earth', nsi=False,tols=(1e-3,1e-6)):
     '''
     Returns the range of energies and the list of all flavour oscillation probabilities. Uses a single core
     '''

### 2021-07-31 article/article.tex
update

@@
 \documentclass[draft=True]{revtex4-2}
-\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
-\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
+\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
+\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{T})}}}
 \newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
@@
 \renewcommand{\ne}{\nu_e}
-\newcommand{\Ereco}{E^{reco}}
-\newcommand{\Etrue}{E^{true}}
+\newcommand{\Ereco}{E^{R}}
+\newcommand{\Etrue}{E^{T}}
 \newcommand{\nm}{\nu_\mu}
@@
     \epsilon_{\alpha\beta} &= \sum_{f,X} \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
-                           &= \epsilon_{\alpha\beta}^{eV} + 3\epsilon_{\alpha\beta}^{uV} + 3\epsilon_{\alpha\beta}^{dV}
+                           &= \epsilon_{\alpha\beta}^{eV} + 3\,\epsilon_{\alpha\beta}^{uV} + 3\,\epsilon_{\alpha\beta}^{dV}
 \end{align}
-We note that our definition of $\epsilon_{\alpha\beta}$ differs from some texts, where the quark number density is used to normalize
-the parameters\cite{deepcoreNSI}.
+We note that our definition of $\epsilon_{\alpha\beta}$ differs from e.g. \cite{deepcoreNSI}, where the quark number density is used to normalize
+the parameters.
 
@@
 
-\subsection{Non-standard effects in the GeV-TeV range}\label{sec:nsiEffects}
+\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
 Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
@@
 
+\subsection{NSI phenomenology at flux level}\label{sec:nsiFluxEffects}
 To study the NSI flux effect, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
@@
 \subsection{IceCube}\label{ch:ICmethod}
-We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which was collected over 8 years. The event rate for each bin reads
+We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which contain muon track events collected over 8 years. 
+The reconstructed energy $\Ereco$ is logarithmically binned between \SI{500}{\GeV} to \SI{9976}{\GeV}, totalling 13 bins (index $i$).
+The reconstructed cosine-zenith $\zreco$ is linearly binned between $-1$ and $0$ in 20 bins (index $j$).
+
+The event count for each bin reads
 \begin{align}\label{eq:ICevents}
-   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}(E^t,\theta^t)  A^\text{eff}(E^t) R(E^r,E^t)
-   \dd E^t\,,
+   N_{ij} &= T\sum_\beta \int_{(\zreco)_j}^{(\zreco)_{j+1}} \dd \zreco \int_{\Ereco_{i}}^{\Ereco_{i+1}} \dd \Ereco \int_0^\pi R(\theta^R,\theta^T) \dd \ztrue \int_0^\infty \phi_\beta^\text{det}(\Etrue,\theta^R)  A^\text{eff}(\Etrue) R(\Ereco,\Etrue)
+   \dd \Etrue\,,
 \end{align}
-where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
-which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
+where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area obtained from~\cite{ICaeff}, in which $A^\text{eff}$ has been averaged over neutrinos and 
+anti-neutrinos. $R(x^R,x^T)$ is a resolution function, 
+which is responsible for the smearing between the reconstructed and true parameters $x^R$ and $x^T$, respectively. We assume a log-normal distribution, giving it the form 
 \begin{align}
-    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
+    R(x^R, x^T) = \frac{1}{\sqrt{2\pi} \sigma_{x^R}x^R} \exp\left[-\frac{(\log x^R-\mu(x^T))^2}{2\sigma_{x^R}^2}\right]\,.
 \end{align}
-However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
+However, the energy reconstruction is biased, which means that we don't assume that $\mu(\Etrue) =\Ereco$~\cite{weaverThesis}. 
 To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
-we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
+we can extract a predicted mean and standard deviation for a given $\Ereco$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
 the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
@@
 The data include 14901 track-like events and 26001 cascade-like events, both divided into eight 
-$ \log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins. Each event has a Monte Carlo weight $w_{ijk,\beta}$
-from which we can construct the event count as
+$ \log_{10}E^{reco} \in [0.75,1.75]$ bins (index $i$), eight $\zreco \in [-1,1]$ bins (index $j$), and two bins for the event classification (index $k$). 
+Each event has a Monte Carlo weight $w_{ijk,\beta}$ from which we can construct the event count as
 \begin{align}\label{eq:MCevents}
@@
 by treating the reconstructed and true quantities as a migration matrix.
-
-The oscillation parameters used on our DeepCore simulations are from the
-best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\dm$ and $\theta_{23}$ between their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
 
@@
 $N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
+
+In our simulations of $N_{ijk}^\text{th}$, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, 
+except for $\dm$ and $\theta_{23}$
+which we let free over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
+
 We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
@@
 \begin{align}
-    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
+    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
 \end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.
+with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median cosine-zenith of $\zreco = -0.5$.
 
@@
 The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
-For DeepCore and PINGU, the median zenith angle is $\zreco = 0$, we allow the event count to rotate around this point.
+For DeepCore and PINGU, the median cosine-zenith is $\zreco = 0$, and we allow the event count to rotate around this point.
 
@@
 
-Now, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
-which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}.

### 2021-07-31 src/events/make_sterile_events.py

@@ -22,6 +22,7 @@ parser.add_argument('-s24N', default=10, type=int)
 parser.add_argument('-s', default = 0, type=int)
 parser.add_argument('-sT', default = 1, type=int)
 parser.add_argument('-N', default=13, type=int)
+parser.add_argument('-s34', action='store_true')
 args = parser.parse_args()
 
 if __name__ == '__main__':
@@ -33,12 +34,13 @@ if __name__ == '__main__':
 
     params = ic_params.copy()
 
-
-    param_list = list_of_params(params, dm41_range, s24_range)
+    param_list = list_of_params(params, dm41_range, s24_range, s24_eq_s34=args.s34)
 
 
     print(f'Precomputing NO IC events for dm41({dm41_range.min()},{dm41_range.max()},{len(dm41_range)}),',
             f's24({s24_range.min()},{s24_range.max()},{len(s24_range)})')
+    if args.s34:
+            print('Putting s24 = s34')
 
 
     from multiprocessing import Pool
@@ -47,4 +49,9 @@ if __name__ == '__main__':
     H1_events_list = p.starmap(get_events, data)
     p.close()
     H1_events = np.array(H1_events_list).reshape(len(dm41_range)*len(s24_range),13,20)
-    pickle.dump(H1_events,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}.p','wb'))
+    if args.s34:
+        pickle.dump(H1_events,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}_s34.p','wb'))
+    else:
+        pickle.dump(H1_events,open(f'./pre_computed/H1_IC_N{args.N}_{len(dm41_range)}x{len(s24_range)}.p','wb'))
+
+    

### 2021-07-31 src/plotter.py

@@ -56,20 +56,17 @@ def compare_an_nu(flavor_from_list, flavor_to_list, param, material,E=None, L=No
 
 def P_over_E_parameter(flavor_from, param_dict_list, E, zenith = -1, ndim = 3, anti=False, nsi=False, tols=(1e-4,1e-7)):
     '''
-    Returns the range of energies and the list of all flavour oscillation probabilities. Uses all cores locally or on techila (type='local'/'cloud')
+    Returns the range of energies and the list of all flavour oscillation probabilities.
     '''
 
-    args = [(flavor_from, E, None, 2*r_earth, zenith, 0,ndim,False, None, anti, p,'earth',nsi, tols) for p in param_dict_list]
+    args = [(flavor_from, E, None, 2*r_earth, zenith,ndim,False, None, anti, p,'earth',nsi, tols) for p in param_dict_list]
     p = Pool()
     #res = []
     #for p in param_dict_list:
     #    res.append(P_num_over_E_wrapper(p))
     res = p.starmap(P_num_over_E, args)
 
-    P_list = []
-    for i in range(len(param_dict_list)): # Splits result list into x and y
-        P_list.append(res[i])
-    return np.array(P_list)
+    return np.array(res)
 
 
 def plot_P_E_params(x,P, ax,flavor_to='m',colors=None,legend_name='', legend_values='', ylabel='', xlabel='',title=''):

### 2021-08-03 article/article.tex
update

@@
 To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
-The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
-production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption. After this, we are
-ready to study the NSI effect on probability level.
+The Earth density profile is taken from the PREM~\cite{PREM}, and we do not consider neutrino absorption.
+The baseline for a given trajectory is determined using an average neutrino production height of 15 km and an Earth radius of 6371 km.
+Thus, matter oscillations introduce a zenith angle dependence in two areas. Firstly, the matter potential depends on the matter density through the
+neutrino propagates. A neutrino with $\cos{\theta_z} < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
+with $\cos{\theta_z} > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
+After this, we are ready to study the NSI effect on probability level.
 %TODO: add more here? are there more effects than just absoption missing? justify absorption missing?
@@
 \end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ at flux level, 
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
+To illustrate the impact of $\emt$ at flux level, 
 we plot in Fig.~\ref{fig:flux_ratio} the quantity $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$, 
 where all fluxes are propagated to detector level by Eq.~\ref{eq:propFlux}. 
-In the left panel, we plot the flux in region in which 99\% of the 
-DeepCore track events originating from $\nm + \anm$ fluxes are contained.
-In the right panel, we show the same but with IceCube events.
-We see that the only clear signal discernible to the IceCube detector
+In the left (right) panel, we plot the flux in region in which 99\% of the 
+DeepCore (IceCube) track events originating from $\nm + \anm$ fluxes are contained. We see that the only clear signal discernible to the IceCube detector
 is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
@@
    We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
-   Left (right) panel shows the flux ratio in the energy range in which 99\% of the DeepCore (IceCube) events are contained.
+   Left (right) panel shows the flux ratio in the energy range in which 99\% of the simulated DeepCore (IceCube) events are contained.
    }\label{fig:flux_ratio}
@@
 \section{Detector formalism}
+The IceCube Neutrino Observatory is a gigaton Cherenkov detector located within Antarctic ice near the Geographic 
+South Pole. It consists of 5160 individual digital optical modules situated on 86 strings, which detect Cherenkov light emitted by charged leptons
+from neutrino events. We distinguish between two interaction topologies: track- and cascade-like events. Track-like events originate mainly
+from muons originating from $\nm$ CC interactions, while cascades predominantly consist of electromagnetic and hadronic showers.
+
+DeepCore is a dense sub-array whithin the standard IceCube array, which allows us to observe neutrino interactions down to a few GeV~\cite{DC2021}.
+Due to its lower energy threshold compared with IceCube, DeepCore has previously been used to study NSI effects in this more discernible range\cite{DC2021,deepcoreNSI}.
+
+PINGU is a proposed 26 string in-fill array to IceCube, consisting of optical modules of similar nature~\cite{PINGUletter}. While porposed to mainly shed light on 
+neutrino mass ordering, PINGU will be able to probe NSI parameters aswell.  
 \subsection{IceCube}\label{ch:ICmethod}
+
 We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which contain muon track events collected over 8 years. 
-The reconstructed energy $\Ereco$ is logarithmically binned between \SI{500}{\GeV} to \SI{9976}{\GeV}, totalling 13 bins (index $i$).
+In the data, the reconstructed energy $\Ereco$ is logarithmically binned between \SI{500}{\GeV} to \SI{9976}{\GeV}, totalling 13 bins (index $i$).
 The reconstructed cosine-zenith $\zreco$ is linearly binned between $-1$ and $0$ in 20 bins (index $j$).
@@
 \end{align}
-However, the energy reconstruction is biased, which means that we don't assume that $\mu(\Etrue) =\Ereco$~\cite{weaverThesis}. 
-To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
-we can extract a predicted mean and standard deviation for a given $\Ereco$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
-the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
+However, the energy reconstruction is biased, meaning that the most probable reconstructed energy for a given true energy is not the same due to 
+systematic differences~\cite{weaverThesis}. Thus, we don't assume that $\mu(\Etrue) =\Ereco$. 
+To model this relationship between $\Etrue$ and $\Ereco$, we fit a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
+we can extract a predicted mean and standard deviation for a given $\Ereco$. We then take the $\Etrue$ points of the 99th percentile of each reconstructed
+distribution to obtain the $\Etrue$ limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
 events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.
@@
 The data include 14901 track-like events and 26001 cascade-like events, both divided into eight 
-$ \log_{10}E^{reco} \in [0.75,1.75]$ bins (index $i$), eight $\zreco \in [-1,1]$ bins (index $j$), and two bins for the event classification (index $k$). 
+$ \log_{10}\Ereco \in [0.75,1.75]$ bins (index $i$), eight $\zreco \in [-1,1]$ bins (index $j$), and two bins for the event classification (index $k$). 
 Each event has a Monte Carlo weight $w_{ijk,\beta}$ from which we can construct the event count as
@@
 where $C_{ijk}$ is the correction factor from the detector systematic uncertainty and $\phi_\beta^\text{det}$ is defined as Eq.~\ref{eq:propFlux}. 
-We have now substituted the effect of the Gaussian smearing
-by treating the reconstructed and true quantities as a migration matrix.
+We have now substituted the effect of the Gaussian smearing by treating the reconstructed and true quantities as a migration matrix.
 
@@
 which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modeled for PINGU, the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error.
+However, since no detector systematics is yet modeled for PINGU, we take the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error,
+which we can scale at will.
 As with the DeepCore Monte Carlo, the PINGU Monte Carlo is divided into eight 
-$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
+$\log_{10}\Ereco \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
 We plot the normalized event differences $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for cascades and tracks in Fig.~\ref{fig:event_pulls}. %TODO:talk about this
@@
 \section{Results}
-At the reconstructed event level, we note that the $\emt$ features discussed in Sec.~\ref{sec:nsiEffects} display themselves differently in each detector.
+At the reconstructed event level, we note that the $\emt$ features discussed in Sec.~\ref{sec:nsiFluxEffects} display themselves differently in each detector.
 We investigate this for $\emt$ by in Fig.~\ref{fig:Pmm_asymmetry} plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
@@
 
-\subsection{Constraining the NSI parameters}\label{sec:method}
+\subsection{Constraining the NSI parameters}\label{sec:constraining}
 In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
@@
 except for $\dm$ and $\theta_{23}$
-which we let free over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
+which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
 
@@
    \end{tabular}
-   \caption{Definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
+   \caption{Our definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
    We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}

### 2021-09-08 thesis/tex/oscillations.tex
update

@@
 We construct the PMNS matrix using the rotation matrixes from $SO(3)$ as
-\begin{align}
+\begin{align}\label{PMNS_def}
     U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12} \nonumber \\
@@
 \begin{align}
-    P_{\na \to \nb}(t) = \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
+    P_{\na \to \nb}(t) = \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
 \end{align}
@@
 
+\subsection{Two neutrino mixing}
+By working in the limit where one of the neutrino masses can be neglected, 
+we can reduce the complexity of the analytical solution of neutrino oscillation.
+We now only consider the mixing between two neutrino flavors, say between $\ne, \nm$, and $\nu_1, \nu_2$.
+In other words, we let $\dm[31] = 0$.
+
+The three-neutrino oscillation Hamiltonian from Eq.~\eqref{eq:H_3gen} %TODO: derive this
+now reduces to 
+\begin{align}
+    H_F &= \frac{1}{2E}(U M^2 U^\dagger + A) \nonumber \\
+        &= \frac{1}{2E}\left[U \begin{pmatrix}
+            0 & 0 & 0 \\
+            0 & \dm_{21} & 0 \\
+            0 & 0 & 0
+        \end{pmatrix} U^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
+            1 & 0 & 0 \\
+            0 & 0 & 0 \\
+            0 & 0 & 0
+        \end{pmatrix}\,. 
+\end{align}
+The rotation matrices $R_{ij}$ that constitute $U$ according to Eq.~\eqref{PMNS_def} can be simplified.
+The rotation $R_{13}$ will not affect our mass matrix, since the former acts in the $1-3$ plane, and the latter sits in the $1-2$ plane.
+Thus, the reduced mass matrix $\mathcal{M}_{12}$ commutes with $R_{13}$.
+Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathcal{M}_{12}$.
+Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
+\begin{align}
+    \commutator{R_{ij}}{R_{kl}} = R_{ij}R_{kl} - R_{kl}R_{ij} = 0\,.
+\end{align}
+Thus,
+\begin{align}
+    U \mathcal{M}_{12} U^\dagger &=
+    R_{23}R_{13}R_{12} \mathcal{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
+    &= R_{12}R_{23}R_{13} \mathcal{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
+    &= R_{12}\mathcal{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
+\end{align}
+And due to the fact that the rotation matrices are unitary,
+\begin{align}
+    R\,R^\dagger = \mathcal{I}\,,
+\end{align}
+we have that 
+\begin{align}
+    U \mathcal{M}_{12} U^\dagger &= R_{12}\mathcal{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
+    &= R_{12}\mathcal{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
+    &= R_{12}\mathcal{M}_{12}  R_{12}^\dagger\,.
+\end{align}
+We have now completely removed the dependence of the mixing angle between the $\nu_1$ and $\nu_3$ mass eigenstates, $\theta_{13}$, and the dependece of the mixing angle between the $\nu_2$ and $\nu_3$ mass eigenstates, $\theta_{23}$.
+We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
+
+\begin{align}
+    U &= R_{12}
+\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix} 
+\end{align}
+
+Let us return to the Hamiltonian with our two-neutrino mixing matrix. We have 
+\begin{align}
+    H_F
+        &= \frac{1}{2E}\left[R_{12} \begin{pmatrix}
+            0 & 0 & 0 \\
+            0 & \dm_{21} & 0 \\
+            0 & 0 & 0
+        \end{pmatrix} R_{12}^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
+            1 & 0 & 0 \\
+            0 & 0 & 0 \\
+            0 & 0 & 0
+        \end{pmatrix} \nonumber \\
+        &= \frac{1}{2E}\left[\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}  \begin{pmatrix}
+            0 & 0 & 0 \\
+            0 & \dm_{21} & 0 \\
+            0 & 0 & 0
+        \end{pmatrix} \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e \begin{pmatrix}
+            1 & 0 & 0 \\
+            0 & 0 & 0 \\
+            0 & 0 & 0
+        \end{pmatrix}\,. 
+\end{align}
+
+We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the final two-neutrino Hamiltonian:
+
+\begin{align}
+    H_F
+        &= \frac{1}{2E}\left[
+            \begin{pmatrix}
+                c_{12} & s_{12} \\ 
+                -s_{12} & c_{12} \\ 
+            \end{pmatrix}  
+            \begin{pmatrix}
+            0 & 0 \\
+            0 & \dm_{21}
+        \end{pmatrix} 
+        \begin{pmatrix}
+            c_{12} & s_{12}\\ 
+            -s_{12} & c_{12} \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e 
+            \begin{pmatrix}
+            1 & 0 \\
+            0 & 0 \\
+        \end{pmatrix} \nonumber \\
+        &= 
+        \frac{1}{2E}\left[
+            \begin{pmatrix}
+                0 & \dm_{21} s_{12} \\ 
+                0 & \dm_{21} c_{12} \\ 
+            \end{pmatrix}  
+        \begin{pmatrix}
+            c_{12} & -s_{12}\\ 
+            s_{12} & c_{12} \end{pmatrix} \right] + \sqrt{2}G_F N_e 
+            \begin{pmatrix}
+            1 & 0 \\
+            0 & 0 \\
+        \end{pmatrix} \nonumber \\
+        &= 
+        \frac{1}{2E}\left[
+            \begin{pmatrix}
+                s_{12}^2 + \sqrt{2}G_F N_e & \dm_{21} s_{12}c_{12} \\ 
+                \dm_{21} s_{12}c_{12} & \dm_{21} c_{12}^2 \\ 
+            \end{pmatrix}  \right]
+\end{align}
+%TODO: complete trig simplification
+
+This matrix has eigenvalues which we identify as the effective two-neutrino squared-mass difference $(\dm[21])^M$. They are
+
+\begin{align}\label{eq:eff_dm}
+    \pm (\dm[21])^M = \pm \sqrt{(\dm[21] \cos{(2\theta_{12}) - \sqrt{2}G_F N_e})^2 + (\dm[21]\sin{(2\theta_{12})})^2}
+\end{align}
+
+The matrix is diagonalized by the usual rotation matrix $R_{12}$, but with a different rotation angle. This now introduces the effective two-neutrino mixing angle $\theta_{12}^M$:
+
+\begin{align}
+    U^M &= R_{12}^M = R_{12}(\theta_{12}^M)\,.
+\end{align}
+$U^M$ diagonalizes $H_F$ if and only if
+
+\begin{align}\label{eq:eff_theta}
+    \tan{(2\theta_{12}^M)} = \frac{\tan{(2\theta_{12})}}{1- \frac{\sqrt{2}G_F N_e}{\dm[21]\cos{(2\theta_{12})}}}\,.
+\end{align}
+
+Now assume that the matter density is sufficiently smooth along the trajectory $x$, that is $\dd \theta_M / \dd x \approx 0$.
+In its diagonalized form, the Schrödinger equation with two-neutrino Hamiltonian can be solved with this assuption.
+The solutions are the regular neutrino vacuum oscillations of Eq.~\eqref{eq:Pab} using $\theta[13] = \theta[23] =0$, but with the effective parameters of Eqs.~\eqref{eq:eff_dm,eq:eff_theta}.
+That is
+%TODO:maybe expand eq below or solve above explicitly?
+\begin{align}
+    P_{e\mu}^M(x) = \sin^2(2\theta_{12}^M))\sin^2(\frac{\dm[21]x}{4E})
+\end{align}
+
+\subsection{Earth propagation}
+
 We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically

### 2021-09-09 article/article.tex
update

@@
 \subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
-Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
-However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
-Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.
+% Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
+% However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
+% Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.
 
-In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
-with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
-This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
-(e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
-which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
-the three different effects in Fig.~\ref{fig:nsi_probs}.
+% In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
+% with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
+% This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
+% (e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
+% which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
+% the three different effects in Fig.~\ref{fig:nsi_probs}.
 
-Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
-the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
-are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
-Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
-while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
+% Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
+% the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
+% are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
+% Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
+% while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
 %TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
 \begin{figure}
-   \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
-   \caption{The three different effects that the off-diagonal NSI parameters have in 
-   the \si{\GeV} range. To schematically elucidate the NSI effect, we plot the summed probabilities for both neutrinos and 
-   antineutrinos.}\label{fig:nsi_probs}
-\end{figure}%TODO: change plot ylabels
+   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
+   \caption{}\label{fig:nsi_probs}
+\end{figure}
 

### 2021-09-09 thesis/tex/nsiResults.tex
update

--- 2021-05-05 thesis/tex/nsiResults.tex
@@
-\documentclass[draft=True]{thesis}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{graphicx, slashed, siunitx}
-\usepackage[utf8]{inputenc}
-\usepackage{xr-hyper}
-\input{commands}
-\begin{document}
-\section{$\chi^2$ minimization}
+% \documentclass[draft=True]{thesis}
+% \usepackage[margin=0.5in]{geometry}
+% \usepackage{graphicx, slashed, siunitx}
+% \usepackage[utf8]{inputenc}
+% \usepackage{xr-hyper}
+% \input{commands}
+% \begin{document}
+\section{Non-Standard Interactions}\label{sec:nsiResults}
+\subsection{Constraining the NSI parameters}\label{sec:constraining}
+In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
 For our analyses, we define our $\chi^2$ as
-\begin{align} \label{eq:ICchisq}
+\begin{align} \label{eq:chisq}
     \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
@@
 \end{align}
-where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
+where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
 $N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
+
+In our simulations of $N_{ijk}^\text{th}$, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, 
+except for $\dm$ and $\theta_{23}$
+which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
+
 We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
 The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
-
 For IceCube, the event count takes the form
 \begin{align}
-    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
+    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
 \end{align}
-with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents} Here, we allow the event distribution to rotate around the median zenith of $-0.5$.
+with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median cosine-zenith of $\zreco = -0.5$.
 
-For DeepCore and PINGU, the event count takes the form
+For DeepCore and PINGU, and the event count takes the form
 \begin{align}
@@
 with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
-The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,.
-For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
-For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
-muon background estimate~\cite{DC2019data}.
+The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
+For DeepCore and PINGU, the median cosine-zenith is $\zreco = 0$, and we allow the event count to rotate around this point.
+
+We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+We consider best, normal, and worst-case scenarios in IceCube using
+$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$. %TODO: maybe source/justification for these values?
+For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
+muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
+{\renewcommand{\arraystretch}{1.2}
+\begin{table}
+   \begin{tabular}{lccc}
+      \hline \hline
+      Experiment & Best case & Baseline & Worst case \\
+      \hline
+      IceCube & $5\%$ & $10\%$ & $15\%$ \\
+      PINGU & $0\%$ & $3\%$ & $5\%$ \\
+      \hline \hline
+   \end{tabular}
+   \caption{Our definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
+   We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
+\end{table}
+
+For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
+\begin{align}\label{eq:joint_chisq}
+    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
+\end{align}
+with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
+
+After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
+The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+
+Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero.
+This is because the `data' we generated during
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
+
+\begin{figure}
+   \begin{center}
+      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
+      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+      parameters not shown in each panel are fixed to zero. 
+      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}.}\label{fig:3D_NO}
+   \end{center}
+\end{figure} 
+\begin{figure}
+   \begin{center} 
+      \includegraphics[width=0.6\textwidth]{figures/PID_3D_emt.pdf}
+      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
+    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
+   \end{center}
+\end{figure}
+
+{\renewcommand{\arraystretch}{1.3}
+ \begin{table}
+   \begin{center}
+   \begin{tabular}{lcccccc}
+      \hline \hline
+      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{6}{c}{IceCube}  \\
+      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
+      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
+      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] &  [-0.046, 0.054] &         [-0.065] &  [-0.049, 0.057] &          [-0.07] \\
+      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\
+      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] &  [-0.11, 0.094] &  [-0.20, 0.16] &   [-0.14, 0.11] &   [-0.23, 0.18] \\
+      $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] &   [-0.10, 0.11] &  [-0.19, 0.18] &  [-0.13, 0.13] &  [-0.23, 0.12] \\\\
+      &\multicolumn{6}{c}{IceCube + DeepCore}\\
+      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
+      \hline
+      \hline
+   \end{tabular}
+   \end{center}
+   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
+   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
+\end{table}
+\begin{table}
+   \begin{tabular}{lcccccc}
+      \hline \hline
+      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{6}{c}{PINGU} \\
+      $\ett$ &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] \\
+      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
+      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      & \multicolumn{6}{c}{DeepCore + PINGU} \\
+      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] &  [-0.038, 0.048] &  [-0.058, 0.067] &   [-0.039, 0.05] &          [-0.06] \\
+      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] &  [-0.071, 0.086] &  [-0.149, 0.141] &  [-0.082, 0.097] &  [-0.17, 0.16] \\
+      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] &  [-0.061, 0.103] &  [-0.131, 0.155] &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
+      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
+      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+      \hline
+      \hline
+   \end{tabular}
+   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
+   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
+\end{table}
+
+\begin{table}
+   \begin{center}
+   \begin{tabular}{lccc}
+           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
+           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
+           $\ett$ &  2.435 & 47.84 & 0.0125 \\
+           $\emt$ &  2.435 & 43.97 & -0.005 \\
+           $\eem$ &  2.435 & 43.97 & 0 \\
+           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
+           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
+           $\emt$ &  2.435 & 51.70 & 0 \\
+           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
+           $\emt$ &  2.517 & 43.97 & -0.01 \\
+           \hline
+           \hline
+   \end{tabular}
+   \end{center}
+   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   degrees, respectively.}\label{table:bestfit}
+\end{table}
+\newpage
+
+ \begin{figure}[t]
+   \begin{center}
+      \begin{subfigure}{0.38\textwidth}
+         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
+         \caption{PINGU}\label{fig:PINGU_event_pulls}
+      \end{subfigure}
+      \begin{subfigure}{0.4\textwidth}
+         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
+         \caption{DeepCore}\label{fig:DC_event_pulls}
+      \end{subfigure}
+    \end{center}
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}\label{fig:event_pulls} 
+\end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better
+
+%TODO: subsection about comparison between different papers.
+
+\begin{figure}
+   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
+\end{figure}
+\begin{figure}
+   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f5.pdf}
+\end{figure}
+\bibliographystyle{elsarticle-num}
+\bibliography{article}
+
+\newpage
+\begin{tabular}{p{55mm}p{55mm}p{55mm}}
+   DeepCore (2017)
+      \begin{itemize}
+         \item[$\checkmark$] Honda atmospheric fluxes
+         \item[$\times$] Only look at tracks and $\emt$
+         \vspace{1em}  
+         \item[$\times$] DC Monte Carlo from an older dataset 
+         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+         \item[$\times$] 8 z bins from -1 to 0 
+         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
+         \item[$\times$] Prior on spectral index
+         \item[$\times$] No zenith angle normalization
+         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
+      \end{itemize} &
+    Demidov (2020) DC analysis
+      \begin{itemize}
+         \item[$\checkmark$] Honda atmospheric fluxes
+         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
+         \item[$\checkmark$] Data and Monte Carlo from DC 2018
+         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
+         \item[$\checkmark$] 8 z bins from -1 to 1
+         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
+         \item[$\times$] Prior on spectral index
+         \item[$\times$] No zenith angle normalization
+         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
+         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
+         \item[$\times$] Uncertainty on hadron production in atmosphere
+         \item[$\times$] Uncertainty on neutrino nucleon cross section 
+      \end{itemize} &
+    This DC+PINGU analysis
+      \begin{itemize}
+         \item[$\checkmark$] Honda atmospheric fluxes
+         \item[$\checkmark$] Tracks and cascades for all flavors
+         \vspace{1em} 
+         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
+         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
+         \item[$\checkmark$] Flux normalization uncertainty of 25\%
+         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
+         \item[$\checkmark$] No priors on oscillation parameters 
+         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
+      \end{itemize} 
+\end{tabular}
 \end{document}
+
+% \end{document}

### 2021-09-11 thesis/tex/SM.tex
update

@@
 Each vector boson has one corresponding generator, the set of which constitutes the group.
-The strong charge is mediated by eight massless gluons, which correspond to the eight generators of $\text{SU}(3)_C$. 
+The strong charge is mediated by eight massless gluons, which correspond to the eight independent generators of $\text{SU}(3)_C$. 
 The weak charge is mediated by the three massive gauge bosons $W^\pm$ and $Z$, and the massless photon $\gamma$, 
@@
 
-The subscript of each group denotes by which mechanism that force is mediated.
-The gluons mediate the strong force through interactions of color, emphasized with subscript $C$.
-The weak force only sees left-handed particles,
-which we distinguish with the subscript $L$.
-And the electroweak interaction that a particle undergoes is determined by its hypercharge $Y$.
-For example, the quarks all have a nonzero color and hypercharge,
-so they participate in the strong and electromagnetic interactions. If a quark is left-handed, it will also feel the weak interaction. The neutrinos on the other hand, have neither charge nor color, 
+The subscript of each group denotes by which mechanism that force is mediated. The gluons mediate the strong force through interactions of color,
+emphasized with subscript $C$. The weak force only sees left-handed particles, 
+which we distinguish with the subscript $L$. And the electroweak interaction that a particle undergoes is determined by its hypercharge $Y$. 
+For example, the quarks all have a non-zero color and non-zero hypercharge, 
+so they participate in the strong and electromagnetic interactions. If a quark is left-handed, it will also feel the weak interaction. 
+The neutrinos on the other hand, have neither charge nor color, 
 so they are insivible to both the strong and electromagnetic force. We express this by letting their fields transform as singlets under those symmetry groups.
@@
 Together, these three interactions make up the Standard Model gauge group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
-This determines the form of the three coupling constants, but which numerical values must be experimentally measured. 
+This determines the form of the three coupling constants, which numerical values must be experimentally measured. 
 Since the vector bosons are represented by the generators, they are uniquely determined by the symmetry group. However, the scalar boson(s) and fermions are free as long as they
@@
 number of fermions must be experimentally verified and can be altered from a phenomenological standpoint. In this work,
-we will use this leniency to make drastic modifications to the Standard Model fermions and examine to which extent 
-these modifications might be supported by experimental evidence.
+we will use this leniency to introduce a new particle and examine to which extent 
+these modifications might be supported by experimental evidence. Moreover, we will examine the possibility of adding a new completely new force to the Standard Model.
+As then follows from our discussion above, this means that we will add a symmetry group and thus also at least one more vector boson.
 
+%TODO: write about convervation laws
 % \subsection{Lepton mixing}

### 2021-09-11 thesis/tex/oscillations.tex
update

@@
 \section{Neutrino Mixing}\label{ch:oscillation}
-In 1998, the Super-Kamiokande collaboration detected a $\nm$ deficit that could not be explained by any other mechanism
-than the conversion of muon neutrinos to electron neutrinos. This was the first conclusive evidence of a $\nm \to \ne$ oscillation.
-The most interesting conclusion from the observation of neutrino flavor oscillations is the equivalence between oscillations and neutrino mass, 
-with the latter being identically zero acording to the Standard Model. Thus, we are required to extend the Standard Model to incorporate neutrino 
+Japan 1998. The Super-Kamiokande experiment detects a $\nm$ deficit that could not be explained by any other mechanism
+than the conversion of muon neutrinos to electron neutrinos. This was the first conclusive evidence of a completely new physics phenomenon: neutrino flavor
+oscillations. An implication of the observation of oscillations is neutrino mass, 
+which is identically zero acording to the Standard Model. Thus, we are required to extend the Standard Model to incorporate neutrino 
 masses before we discuss the neutrino oscillations themselves.
@@
 In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
-All neutrinos are left-handed and all antineutrinos are right-handed. Thus, neutrinos are massless since they do not undergo the Higgs mechanism.
+All neutrinos are left-handed and all antineutrinos are right-handed. Thus, they do not pick up a Yukawa coupling, 
+and will not undergo the Higgs mechanism, which leaves them massless.
 Additionally, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
 generated at loop level because any such attempt will violate the total lepton number by two units.
-In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing additional fermions.
+In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing right-handed neutrinos and left-handed antineutrinos.
 
@@
 \end{align}
-Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, since no flavor rotation can make massless fields massive.
+Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
+since no flavor rotation can make massless fields massive.
 Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
@@
 The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
-This fact is introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
+This fact is denoted as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
 
@@
 \end{align}
-By construction, $Y^\ell$ and $Y^\nu$ are diagonal, so we write their omponents as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
+By construction, $Y^\ell$ and $Y^\nu$ are diagonal, so we write their components as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
 \begin{align}\label{eq:L_H}
@@
 \end{align}
-The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and expanding the Higgs vacuum expectation value $v$ into the fields gives us
+The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and multiplying the Higgs vacuum expectation value $v$ into the fields gives us
 \begin{align}
@@
 Any unitary $3\times3$ matrix can be parametrized using three mixing angles and six phases. However, not all phases affect the 
-charged and weak currents and are thus not observable. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
-leaving only one physical phase for us to measure. Thus we are down to four degrees of freedom in the three dimensional case: three mixing angles
-of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$.
+charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
+leaving only one physical phase for us to measure. We are now down to four degrees of freedom in the three dimensional case: three mixing angles
+of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$. The mixing angle $\theta_{ij}$ specifies 
+the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate. The physical interpretation of
+a mixing angle is then the degree of which the $\nu_i$ eigenstate mixes with the $\nu_j$ eigenstate. A non-zero mixing angle will then 
+cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates that we allowed to mix. %TODO: nua = nu1 + nu2
 
@@
 \end{align}
-The term $\delta_\text{CP}$ determines the degree of charge-parity violation. In this work, we will assume CP invariance by always
+The term $\delta_\text{CP}$ determines the degree of charge-parity violation. In this work, we will always assume CP invariance for simplicity by
 setting $\delta_{CP} = \SI{0}{\degree}$. Thus,
@@
 \end{align}
-The PMNS matrix is then real, with numerical values 
+Our neglect of the issue of CP invariance leaves the PMNS matrix real, with numerical values 
 \begin{align}\label{eq:Uvalues}
@@
 In our study, we will only use neutrinos originating from conventional cosmic ray interactions in the atmosphere. 
-In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is neglible. We see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
+In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is neglible. From Eq.~\eqref{eq:Uvalues}, w
+e see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
 suggesting that $\nm$ primarily mixes into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
@@
 \end{align}
-where $H_0$ is the Hamiltonian and the subscript signifies that we are in vacuum.
+where $H_0$ is the vacuum Hamiltonian.
 
@@
 \end{align}
-Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse?
- We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
+Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse?We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
 \begin{align}\label{eq:osc_k}
@@
 \end{align}
-where we in the last step have defined the \emph{mass squared-difference} $\dm_{kj} = m_k^2 - m_j^2$. Since the oscillation probability depends on this quantity
-rather than the individual masses, it is impossible
-to measure the mass $m_k$ through neutrino oscillations.
+where we in the last step have defined the \emph{mass-squared difference} $\dm_{kj} = m_k^2 - m_j^2$. Since the oscillation probability depends on this quantity
+rather than the individual masses, it is impossible to measure the mass $m_k$ through neutrino oscillations.
 Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^\dagger = \delta_{\a \b}$ yields 
@@
 
-For our purposes, the probabilities in Eq.~\ref{eq:Pab} are rather uninteresting, since they are only valid in vacuum.
-Despite this fact, this form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
+this form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
 determine the amplitude of the oscillations, while the mass-squared differences together with the ratio $L/E$ determine the 
-frequency.
+frequency. So in vacuum, the mixing angles only influence the oscillation amplitude, while the energy, trajectory, and masses of
+the neutrinos only influence the oscillation frequency.
 
@@
     \end{subfigure}%TODO: they are different sizes
-    \caption{Feyman diagrams showing the two interactions that neutrinos participate in according to the Standard Model.}\label{fig:w_and_z}
+    \caption{Feymann diagrams showing the two interactions that neutrinos participate in according to the Standard Model.}\label{fig:w_and_z}
 \end{figure}
 In this work, we are concerned about the interactions with the neutrino and Earth-like matter, i.e.~electrons, protons, and neutrons. 
-The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can go through charged current (CC) 
-interactions is the electron flavor. This is because the Earth doesn't consist of any muons or tau particles. 
+The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can undergo charged current (CC) 
+interactions is the electron flavor. This is because the CC interaction requires a neutrino with flavor $\alpha$ to interact with its charged lepton 
+partner $\alpha$. Since the Earth doesn't consist of any muons or tau particles, the $\nu_\mu$ and $\nu_\tau$ have no charged leptons to undergo CC interactions with. 
 The right panel shows any neutrino flavor interaction via the neutral current (NC) with Earth-like matter\footnote{The Earth is entirely composed
@@
 neutrinos propagate in their mass eigenstates, but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
-determines if the flavor eigenstate has oscillated or not. The interactions still conserve lepton number, but the kinetic Lagrangian will not.
+determines if the flavor eigenstate has oscillated or not. The interactions still conserve lepton number since the interaction Lagrangian does,
+but the kinetic Lagrangian will not. Hence, neutrinos violate lepton number convervation during propagation.
 
-For neutral current, we replace the electron field $e(x)$ in Eq.~\ref{eq:H_fierz} by the fermion field $f(x)$, and the projection operator 
+For neutral current, we replace the electron field $e(x)$ in Eq.~\ref{eq:H_fierz} by the more general fermion field $f(x)$, and the projection operator 
 $(1-\gamma^5)$ with $(g_V^f - g_A^f\gamma^5)$. Again, the $\gamma^5$ will cause the spacial component of $p_f$ to disappear after integration, and the 
@@
 \end{align}
-where the electrical neutrality condition allows us to simply sum the vectorial couplings together, cancelling the electron and proton contributions (and hence, also the Weinberg angle dependence).
+where the electrical neutrality condition allows us to simply sum the vectorial couplings together, cancelling the electron and proton contributions (and hence, also the $\theta_W$ dependence).
+
+We now see that both matter potentials, regardless if the interaction is of type charged or neutral, is only dependent on the eletron density in the medium, $N_e$ times a constant.
+So to calculate the matter oscillations in an eletrically neutral medium with equal abundance of protons and neutrons, we are only required to consider the matter density of the medium.
 
@@
 Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors. 
-However, since all flavors undergo NC interactions the total matter potential in matrix form is
+However, since all flavors undergo NC interactions the total matter potential in the flavor basis is
 \begin{align}\label{eq:V_matrix}
@@
 
-Our treatment of the interaction Hamiltonian is similar except for the fact that its eigenstates lie in the flavor basis, conviniently allowing us
+Our treatment of the interaction Hamiltonian is similar except for the fact that its eigenstates lie in the flavor basis, conveniently allowing us
 to letting it act directly on the flavor eigenstates:
@@
 we can reduce the complexity of the analytical solution of neutrino oscillation. 
-We now only consider the mixing between two neutrino flavors, say between $\ne, \nm$, and $\nu_1, \nu_2$.
-In other words, we let $\dm[31] = 0$.
+We now only consider the mixing between two neutrino flavors, say between $\ne, \nm$, and $\nu_1, \nu_2$. In other words, we let $\dm[31] = 0$.
 
@@
 In its diagonalized form, the Schrödinger equation with two-neutrino Hamiltonian can be solved with this assuption. 
-The solutions are the regular neutrino vacuum oscillations of Eq.~\eqref{eq:Pab} using $\theta[13] = \theta[23] =0$, but with the effective parameters of Eqs.~\eqref{eq:eff_dm,eq:eff_theta}.
-That is
+The solutions are the regular neutrino vacuum oscillations of Eq.~\eqref{eq:Pab} using $\theta[13] = \theta[23] =0$, but with the effective parameters of Eqs.~\eqref{eq:eff_dm,eq:eff_theta}. That is
 %TODO:maybe expand eq below or solve above explicitly?
@@
 \end{align}
+
+While two-neutrino flavor oscillation can only be assumed to hold in regions where mixing into the third flavor can be considered neglible,
+the fact that the mixing angle in matter depends on the squared-mass difference, and vice versa, gives us an interesting conclusion which is 
+still valid for the full three neutrino oscillations. We previously saw that the oscillation amplitudes were entirely dependant on
+the mixing angles, and the oscillation frequencies entirely dependant on the squared-mass difference along with energy, and trajectory. After 
+introducing the matter potentials, we now see that the matter effect mixes the mixing matrix elements together with the masses.
+%TODO: maybe 2 vs 3 plot
 

### 2021-09-13 thesis/tex/ICintro.tex
update

@@
 \section{Neutrino detection}
-We always observe neutrinos indirectly through their associated charged lepton. Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
+We always observe neutrinos indirectly through their associated charged lepton. 
+Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
 via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
-interaction is then deduced. This deduction is obviously imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.
+interaction is then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.
 
@@
 into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
-%TODO: pic of cherenkov light/dom?
 
@@
     \includegraphics[width=0.5\textwidth]{figures/icecube2.png}
-    \caption{View of the full IceCube array}
+    \caption{View of the full IceCube array, with the Eiffel tower for scale.}
 \end{figure}
@@
 not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
-IceCube and DeepCore bounds. The PINGU simulations have the same structure as the DeepCore data, so any analysis referring to DeepCore will
-also apply to PINGU except where noted. However, we treat the PINGU detector as independent of the DeepCore experiment.
+results from IceCube and DeepCore. The PINGU simulations have the same structure as the DeepCore data, so our analysis referring to DeepCore will
+also apply to PINGU except where noted. However, we treat the PINGU detector as independent of the other experiments.
 
-\begin{figure}[t]\label{fig:flux_aeff}
-    \includegraphics[width=0.5\textwidth]{figures/flux.pdf}\hspace{-1cm}
-    \includegraphics[width=0.5\textwidth]{figures/aeff.pdf}
-    \vspace{-2.5cm}\caption{\emph{Left panel:} Interpolated South Pole atmospheric flux with data from~\cite{hondaArticle}.
-    \emph{Right panel:} Interpolated IceCube effective area with data from~\cite{ICaeff}.}
+\begin{figure}[t]\label{fig:flux}
+    \includegraphics[width=0.7\textwidth]{figures/flux.pdf}
+    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a near-neglible 
+    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.
 \end{figure}
@@
 \subsection{Atmospheric Neutrino Flux}
-Atmospheric neutrinos originates from cosmic rays composed of protons interacting with nuclei in the atmosphere.
+Atmospheric neutrinos originates from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
 These interactions ultimately produces pions, which decay as 
@@
 \end{align}
-In the muonic decay channel, muons are emitted which will be detected by the IceCube detector. A part of the 
-uncorrelated systematic error comes from this \emph{muon background}, i.e. events misclassified as muons from 
-$\nm$ interactions rather than from pion decay. Moreover, the atmospheric flux is often associated with a large error.
+In the muonic decay channel, muons are emitted which will be detected by the IceCube detector.
+The detector's experience an uncorrelated systematic error, which comes from this \emph{muon background}, 
+i.e. events misclassified as muons from 
+$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
+For IceCube events, we will scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
+expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
+to be neglible~\cite{PINGUletter}.
+Moreover, the atmospheric flux itself is often associated with a large error.
 In this work, we will use a flux normalization error of 24\%, and a zenith slope error of 4\%~\cite{hondapaper}.
 
-The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}
-The flux data is binned in $\ztrue$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
+The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
+The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
 The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
@@
 can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities on the form 
-$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux. 
-Interpolating the data yields makes us capable of returning all four necessary fluxes for a given true energy and true zenith.
-The result is shown in Fig.~\ref{fig:flux_aeff}.
+$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
+Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
+The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. This is due to the 
+very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
+large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
+small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
+equal. First, the difference in the density profiles introduces wildly different matter effects. 
+Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{20}{\km}
+overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs. 
+The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
 
@@
             \hline \hline
-            $\Etrue$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\ztrue$\\\\
+            $E$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\cos(\theta_z)$\\\\
             \hline
@@
 This means that, given the parameters recorded by the detector, what are their "true" values?
-We are interested in two variables: the energy and the direction.
-Each event is tagged with a probable energy and zenith angle, called the recostructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
+We are interested in two variables: the energy and the direction. Each event is tagged with a probable energy and zenith angle, 
+called the recostructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
 The collaboration then uses numerous sophisticated methods to backtrack the reconstructed parameters to the true parameters. 
-So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true and reconstructed energy and zenith angle.
+So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true energy and zenith angle, $\Etrue$ and $\ztrue$. 
 The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the 
@@
 In this work, we are using two different methods, which are based on the form of data available to us. 
-They will be outlined in Sec.\ref{ch:ICmethod} and Sec.~\ref{ch:DCmethod}.
+They will be outlined in Sec.~\ref{ch:ICmethod} and Sec.~\ref{ch:DCmethod}.
 

### 2021-09-13 thesis/tex/ICtheory.tex
update

@@
         \end{tabular}
-    \caption{IceCube-86 effective area from~\cite{ICaeff}}
+    \caption{IceCube-86 effective area from~\cite{ICaeff}.}
 \end{table}
@@
 Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$.
-Just as with the fluxes, we interpolate this in $\Etrue$, $\ztrue$ and show the result %TODO aeff interpolation
+Just as with the fluxes, we interpolate this in $\Etrue$, $\ztrue$ and show the result in Fig.~\ref{fig:aeff}
+Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area of which the array the neutrinos are exposed to.
+While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than 
+the flux itself. Energy-wise, the situation here is completely reverse. Increasing with energy, the effective area of the detector
+approaches its geometrical area of \SI{1e6}{\metre^2}, but is still only in the single digit range at \si{\TeV} energies.
+
+\begin{figure}[t]\label{fig:aeff}
+    \includegraphics[width=0.7\textwidth]{figures/aeff.pdf}
+    \caption{Interpolated IceCube effective area with data from~\cite{ICaeff}.}
+\end{figure}
 

### 2021-09-13 thesis/tex/oscillations.tex
update

@@
 we obtain the nine combinations of probabilities through the Earth diameter. We note that due to our assumption of CP-invariance
-(and thus, T-invariance), the probabilities $P_{\a\b}$ and $P_{\b\a}$ are identically equivalent. The result for \si{\GeV} neutrinos 
+(and thus, T-invariance), the probabilities $P_{\a\b}$ and $P_{\b\a}$ are equivalent. The result for \si{\GeV} neutrinos 
 is shown in Fig.~\ref{fig:oscillations}.
@@
 
-Now we need to incorporate the \emph{zenith angle}, defined as the angle between the neutrino direction of travel and south.
+Now we need to incorporate the \emph{zenith angle}, here defined as the angle between the neutrino direction of travel and south.
 This way, neutrinos traveling through the entire diameter of the Earth up through the South Pole are defined as `up-going', while
 neutrinos that start at the South Pole are `down-going'. We will mostly work with the quantity $\cos{(\theta_z)}$.
-Since we are interested in the matter effects, we reserve our IceCube study to up-going neutrinos, i.e. neutrinos with
-zenith angle $-1<= \cos{(\theta_z)}<=0$. We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
+Since we are interested in the matter effects, some studies are only looking at up-going neutrinos, i.e. neutrinos with
+zenith angle $-1 \le \cos{(\theta_z)} \le 0$. However, while down-going neutrinos don't experience matter oscillations (and hardly even vacuum
+oscillations due to the short baseline), they can be included to reduce systematic errors.
+We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
 allowing us to fully see the Earth matter effect on the oscillations in full. This is shown in Fig.~\ref{fig:oscillograms}.

### 2021-09-13 thesis/tex/DCtheory.tex
update

@@
 \begin{align}\label{eq:PINGUparams}
-    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
+    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm[31] =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
     &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.

### 2021-09-13 thesis/tex/ICintro.tex
update

@@
     \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a near-neglible 
-    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.
+    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}
 \end{figure}
@@
 Moreover, the atmospheric flux itself is often associated with a large error.
-In this work, we will use a flux normalization error of 24\%, and a zenith slope error of 4\%~\cite{hondapaper}.
+In this work, we will use a flux normalization error of 25\%, and a zenith slope error of 5\%~\cite{hondapaper}.
 
@@
 The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
+
+So now we have
 

### 2021-09-13 thesis/tex/ICtheory.tex
update

@@
 
-\begin{table}[h]\label{table:aeff}
+\begin{table}[ht]
     \centering
@@
     \caption{IceCube-86 effective area from~\cite{ICaeff}.}
+    \label{table:aeff}
 \end{table}
@@
 While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than 
-the flux itself. Energy-wise, the situation here is completely reverse. Increasing with energy, the effective area of the detector
+the flux itself. Energy-wise, the situation here is completely reverse from the flux. Increasing with energy, the effective area of the detector
 approaches its geometrical area of \SI{1e6}{\metre^2}, but is still only in the single digit range at \si{\TeV} energies.
 
-\begin{figure}[t]\label{fig:aeff}
+\begin{figure}[ht]
     \includegraphics[width=0.7\textwidth]{figures/aeff.pdf}
     \caption{Interpolated IceCube effective area with data from~\cite{ICaeff}.}
+    \label{fig:aeff}
 \end{figure}
@@
 So now we have the physical quantities in the true parameters. 
-But as we discussed, we need a way to translate this into the reconstructed parameters that the detector gives us.
-We will call the relationship between
+But as we discussed, we need a way to translate this into the reconstructed parameters that the detector gives us. We will call the relationship between 
 $\Ereco$ and $\Etrue$ the energy resolution function, and the relationshop between $\zreco$ and $\ztrue$ the zenith resolution function. 
@@
 
-\begin{table}[h]\label{table:IC_MC}
+\begin{table}[ht]
     \centering
@@
   \caption{A selection of the data found in~\ref{IC2016}}
+  \label{table:IC_MC}
 \end{table}
@@
 where $T$ is the live time of the detector.
-Now this expression handles the Gaussian smearing, but we are not provided systematic error sources, DOM efficiencies, and many more nuisance parameters.
+Now this expression handles the Gaussian smearing, but we are not provided systematic error sources, DOM efficiencies, and other nuisance parameters.
 To correct this,
@@
 That way, we know that our null hypotheses will align while we are free to form additional hypotheses with different
-physics parameters. The binned Monte Carlo events that IceCube used as their null hypothesis in the 2020 sterile analysis is shown in %TODO:MC vs myMC fig.
+physics parameters. %The binned Monte Carlo events that IceCube used as their null hypothesis in the 2020 sterile analysis is shown in %TODO:MC vs myMC fig.
 
-\begin{figure}[!tb]
+\begin{figure}[ht]
     \begin{center}
-       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
+       \includegraphics[width=0.7\linewidth]{figures/IC_MC_gpr.pdf}
     \end{center}
     \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}.
-    Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.}\label{fig:IC_MC_gpr}
+    Color indicates the frequency of each simulated point.
+    Shaded area shows the 99th percentile limits predicted by the regressor trained on this set. It is within this band 
+    that then will sample the $\Etrue$ values for each $\Ereco$.}\label{fig:IC_MC_gpr}
  \end{figure}
@@
 The latest available data collected and processed by the collaboration contains 305,735 muon track events, collected over eight years~\cite{IC2020}. 
-%The data has 13 logarithmically spaced bins in $\Ereco \in \[500,9976\] \si{GeV}$, and 20 linear bins in $\zreco \in \[-1,0\]$. The data is shown in Fig.~\ref{fig:IC_data}.
+The data has 13 logarithmically spaced bins in $\Ereco \in [500,9976]$ \si{\GeV}, and 20 linear bins in $\zreco \in [-1,0]$. The data is shown in Fig.~\ref{fig:IC_data}.
 
-\begin{figure}
+\begin{figure}[ht]
     \centering
@@
 with $E^t_{min}$, $E^t_{max}$, and $R(E^r,E^t)$ taken from the Gaussian process regressor.
-\begin{figure}
+\begin{figure}[ht]
     \centering

### 2021-09-14 thesis/tex/ICtheory.tex
update

@@
 \section{IceCube}\label{ch:ICmethod}
-As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact with charged lepton in the ice. We now are interested in the effective area $\Aeff$, 
-i.e.~the cross-section of the detector that the lepton is exposed to.
-$\Aeff$ depends on several parameters, some of them being detector physical volume, $\Etrue$, $\ztrue$ and the neutrino cross-section. 
+As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact with charged leptons in the ice.
+The charged lepton then emits the Cherenkov light that is detected by the array.
+We now are interested in the effective area $\Aeff$, 
+i.e.~the cross-sectional area of the detector that the lepton is exposed to.
+$\Aeff$ depends on several parameters, some of them being detector physical volume, $\Etrue$, $\ztrue$, and the particle type. 
 Fortunately, the binned $\Aeff$ is provided to us by the collaboration~\cite{ICaeff}.
-The data file has the following form
+An excerpt from this data is shown in Table~\ref{table:aeff}.
 
@@
 
-Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$.
-Just as with the fluxes, we interpolate this in $\Etrue$, $\ztrue$ and show the result in Fig.~\ref{fig:aeff}
-Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area of which the array the neutrinos are exposed to.
-While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than 
-the flux itself. Energy-wise, the situation here is completely reverse from the flux. Increasing with energy, the effective area of the detector
-approaches its geometrical area of \SI{1e6}{\metre^2}, but is still only in the single digit range at \si{\TeV} energies.
+Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will on average, experience the same $\Aeff$ in our model. 
+Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
+Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the neutrinos are exposed to.
+While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself.
+Energy-wise, the situation here is completely reverse from the flux.
+Increasing with energy, the effective area of the detector
+approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
 
-\begin{figure}[ht]
-    \includegraphics[width=0.7\textwidth]{figures/aeff.pdf}
+\begin{figure}[ht]%TODO: fix whitespace
+    \centering
+    \includegraphics[scale=0.6]{figures/aeff.pdf}
     \caption{Interpolated IceCube effective area with data from~\cite{ICaeff}.}
@@
 But as we discussed, we need a way to translate this into the reconstructed parameters that the detector gives us. We will call the relationship between 
-$\Ereco$ and $\Etrue$ the energy resolution function, and the relationshop between $\zreco$ and $\ztrue$ the zenith resolution function. 
+$\Ereco$ and $\Etrue$ the energy resolution function, and the relationship between $\zreco$ and $\ztrue$ the zenith resolution function. 
 We assume the relationship to follow a logarithmic Gaussian distribution, giving it the form 
@@
 \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.8\linewidth]{figures/IC_data.pdf}
+    %\centering
+    \hspace{-2cm}
+    \includegraphics[scale=0.4]{figures/IC_data.pdf}
     \caption{IceCube track events from~\cite{IC2020}.}\label{fig:IC_data}
@@
 \subsection*{Monte Carlo normalization}
-Independent researchers outside of the IceCube collaboration will not be able to more percisely
+Independent researchers outside of the IceCube collaboration will not be able to more precisely
 simulate the detector. The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this 
@@
 \end{align}
-For each bin $i,j$, we then obtain a correction factor which contains information that we are unable
+For each bin $i,j$, we then obtain a correction factor that contains information that we are unable
 to obtain or sufficiently incorporate. One example of such information is the systematic errors of the DOMs.
@@
 event count on a bin-by-bin basis, they can in theory drastically modify the binned results. Another example of
-an error source what will be remedied by this method is the flux. We are using a fairly simple model of the atmospheric 
-flux that excludes atmospheric prompt and astrophysical fluxes. The IceCube collaboration use several different flux models which are initialized 
+an error source that will be remedied by this method is the flux. We are using a fairly simple model of the atmospheric 
+flux that excludes atmospheric prompt and astrophysical fluxes. The IceCube collaboration uses several different flux models which are initialized 
 by a parametrization of the cosmic ray flux.\footnote{Included in the cosmic ray models are e.g. the pion to kaon 
@@
 \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.8\linewidth]{figures/IC_MC_norm.pdf}
-    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
+    \begin{centering}
+    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
+    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots. We 
+    see a large deviation for high zenith values, but since these neutrinos have traversed less matter and have a smaller baseline, we deem this to be acceptable.}\label{fig:IC_MC_norm}
+    \end{centering}
 \end{figure} 

### 2021-09-14 article/article.tex
update

@@
 
-DeepCore is a dense sub-array whithin the standard IceCube array, which allows us to observe neutrino interactions down to a few GeV~\cite{DC2021}.
+DeepCore is a dense sub-array within the standard IceCube array, which allows us to observe neutrino interactions down to a few GeV~\cite{DC2021}.
 Due to its lower energy threshold compared with IceCube, DeepCore has previously been used to study NSI effects in this more discernible range\cite{DC2021,deepcoreNSI}.
 
-PINGU is a proposed 26 string in-fill array to IceCube, consisting of optical modules of similar nature~\cite{PINGUletter}. While porposed to mainly shed light on 
-neutrino mass ordering, PINGU will be able to probe NSI parameters aswell.  
+PINGU is a proposed 26 string in-fill array to IceCube, consisting of optical modules of similar nature~\cite{PINGUletter}. While proposed to mainly shed light on 
+neutrino mass ordering, PINGU will be able to probe NSI parameters as well.  
 \subsection{IceCube}\label{ch:ICmethod}
 
-We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which contain muon track events collected over 8 years. 
+We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which contains muon track events collected over 8 years. 
 In the data, the reconstructed energy $\Ereco$ is logarithmically binned between \SI{500}{\GeV} to \SI{9976}{\GeV}, totalling 13 bins (index $i$).
@@
 As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, which will give a high statistics on both sides of $\emt=0$, slightly favoring $\emt^-$.
-DeepCore on the other hand, has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, 
+DeepCore on the other hand has fewer bins where the event count for $\emt^-$ surpasses the event count for $\emt^+$, 
 giving weaker statistics for the negative side. Thus, we conclude that we will see a $\emt$ \si{GeV}-asymmetry stemming from the lower statistics 

### 2021-09-14 thesis/tex/DCtheory.tex
update

@@
 best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\dm$ and $\theta_{23}$.
+marginalize over $\dm[31]$ and $\theta_{23}$.
 

### 2021-09-14 thesis/tex/ICintro.tex
update

@@
 via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
-interaction is then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.
+interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.
 
-In this work, we only study the detectors handeled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
+In this work, we only study the detectors handled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
 the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
 If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
-Cherenkov light. This event is referred to as a cascade. The neutral current interactions involves quarks, which recoils and procudes
+Cherenkov light. This event is referred to as a cascade. The neutral current interactions involve quarks, which recoils and produces
 showers of hadrons. Also, charged current $\ne$ interactions also produce cascades. A cascade event 
@@
 If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
-as they go. This event is referred to as a track, and are often due to muon charged current interactions. A track event 
+as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
 is shown in Fig.~\ref{fig:events_track}.
@@
 
-The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than other.
-8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single digit \si{\GeV}. Due to 
+The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than others.
+8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}. Due to 
 this part being situated deep within the ice, it is referred to DeepCore. DeepCore will be treated as a separate and independent detector from the rest, which
@@
 In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The `Precision IceCube Next Generation Upgrade' is an upgrade that will 
-supplement DeepCore, i.e. boosing the capabilites of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
+supplement DeepCore, i.e. boosing the capabilities of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
 not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
@@
 
-\begin{figure}[t]\label{fig:flux}
-    \includegraphics[width=0.7\textwidth]{figures/flux.pdf}
-    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a near-neglible 
-    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}
-\end{figure}
-
 \subsection{Atmospheric Neutrino Flux}
-Atmospheric neutrinos originates from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
+Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
 These interactions ultimately produces pions, which decay as 
@@
 The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
-The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
+The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
 The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
@@
 We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. Kaons can decay into neutral pions, which in turn 
-can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities on the form 
+can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities in the form 
 $P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
@@
 equal. First, the difference in the density profiles introduces wildly different matter effects. 
-Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{20}{\km}
-overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs. 
+Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
+overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
 The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
-
-So now we have
 
@@
 
+\begin{figure}[t]\label{fig:flux}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
+    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a near-neglible 
+    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}
+\end{figure}
+
+We propagate the atmospheric neutrino flux $\phi_\alpha^\text{atm}(E,\theta_z)$ through the Earth.
+The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
+\begin{align}\label{eq:propFlux}
+    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
+\end{align}
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
+
 \subsection{Event Reconstruction}
 After an event has occurred, the IceCube algorithms process the data coming from the detector to \emph{reconstruct} the event. 
-This means that, given the parameters recorded by the detector, what are their "true" values?
-We are interested in two variables: the energy and the direction. Each event is tagged with a probable energy and zenith angle, 
-called the recostructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
+This means that, given the parameters recorded by the detector, what are their `true' values?
+We are interested in two variables: energy and direction. Each event is tagged with a probable energy and zenith angle, 
+called the reconstructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
 The collaboration then uses numerous sophisticated methods to backtrack the reconstructed parameters to the true parameters. 
 So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true energy and zenith angle, $\Etrue$ and $\ztrue$. 
-The reconstructed parameters are what we are using to analyze the data (because this is what the detector actually sees), while the true parameters are used in the 
+The reconstructed parameters are what we are using to analyze the data (because this is what the detector sees), while the true parameters are used in the 
 determination of that neutrino's `actual' flux and cross-section (because this is what Nature sees).

### 2021-09-14 thesis/tex/nsiResults.tex
update

@@
-% \documentclass[draft=True]{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \usepackage{graphicx, slashed, siunitx}
-% \usepackage[utf8]{inputenc}
-% \usepackage{xr-hyper}
-% \input{commands}
-% \begin{document}
 \section{Non-Standard Interactions}\label{sec:nsiResults}
@@
 For our analyses, we define our $\chi^2$ as
-\begin{align} \label{eq:chisq}
+\begin{align}\label{eq:chisq_NSI}
     \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
@@
 except for $\dm$ and $\theta_{23}$
-which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
+which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV\squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
 
-We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
+We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.05$ as the zenith angle slope error~\cite{hondapaper}. 
 The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
@@
 For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
-muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
+muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.
 {\renewcommand{\arraystretch}{1.2}
 \begin{table}
+   \centering
    \begin{tabular}{lccc}
@@
 This is because the `data' we generated during
-the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
 since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
@@
    \begin{center}
-      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
-      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+      \includegraphics[width=0.8\textwidth]{figures/joint_3D_NO.pdf}
+      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon.
+$\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI
       parameters not shown in each panel are fixed to zero. 
-      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}.}\label{fig:3D_NO}
+      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
    \end{center}
@@
    \begin{center} 
-      \includegraphics[width=0.6\textwidth]{figures/PID_3D_emt.pdf}
-      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
-    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
+      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
+      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
+    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
    \end{center}
@@
 
-{\renewcommand{\arraystretch}{1.3}
+%TODO: PINGU values are the same. Fill in empty values
+{\renewcommand{\arraystretch}{1.0}
  \begin{table}
    \begin{center}
-   \begin{tabular}{lcccccc}
-      \hline \hline
-      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
-      \hline & \multicolumn{6}{c}{IceCube}  \\
-      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
-      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
-      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] &  [-0.046, 0.054] &         [-0.065] &  [-0.049, 0.057] &          [-0.07] \\
-      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\
-      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] &  [-0.11, 0.094] &  [-0.20, 0.16] &   [-0.14, 0.11] &   [-0.23, 0.18] \\
-      $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] &   [-0.10, 0.11] &  [-0.19, 0.18] &  [-0.13, 0.13] &  [-0.23, 0.12] \\\\
-      &\multicolumn{6}{c}{IceCube + DeepCore}\\
-      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
+      \begin{tabular}{lcc}
          \hline
+         Parameter & Best 90\% CL & Best $3\sigma$\\
+         \hline & \multicolumn{2}{c}{IceCube}  \\
+         $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017]  \\\\
+         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
+         $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
+         $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] \\
+         $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] \\
+         $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] \\\\
+         &\multicolumn{2}{c}{IceCube + DeepCore} \\
+         $\emt$ &  [-0.029, 0.007] &          [0.026] \\
+         \hline
+         \vspace{2em}
+      \end{tabular}
+      \begin{tabular}{lcc}
+         \hline
+         Parameter & Baseline 90\% CL & Baseline $3\sigma$ \\
+         \hline & \multicolumn{2}{c}{IceCube}  \\
+         $\emt$ &  [-0.009, 0.01] &  [-0.015, 0.018]  \\\\
+         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
+         $\ett$ &    [-0.046, 0.054] &         [-0.065]  \\
+         $\emt$ &     [-0.009, 0.01] &  [-0.015, 0.018]  \\
+         $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16]    \\
+         $\eet$ &    [-0.10, 0.11] &  [-0.19, 0.18]  \\\\
+         &\multicolumn{2}{c}{IceCube + DeepCore}\\
+         $\emt$ &   [-0.029, 0.007] &          [0.026] \\
+         \hline
+         \vspace{2em}
+      \end{tabular}
+      \begin{tabular}{lcc}
+         \hline
+         Parameter & Worst 90\% CL & Worst $3\sigma$\\
+         \hline & \multicolumn{2}{c}{IceCube}  \\
+         $\emt$ &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
+         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
+         $\ett$ &    [-0.049, 0.057] &          [-0.07] \\
+         $\emt$ &     [-0.01, 0.011] &   [-0.017, 0.02] \\
+         $\eem$ &   [-0.14, 0.11] &   [-0.23, 0.18] \\
+         $\eet$ &   [-0.13, 0.13] &  [-0.23, 0.12] \\\\
+         &\multicolumn{2}{c}{IceCube + DeepCore}\\
+         $\emt$ &   [-0.029, 0.007] &          [0.026] \\
          \hline
       \end{tabular}
+      \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}.
+$\dm[31]$ and $\theta_{23}$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
+Best, baseline, and worst refer to
+      the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
    \end{center}
-   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
-   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
 \end{table}
+
 \begin{table}
-   \begin{tabular}{lcccccc}
-      \hline \hline
-      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
-      \hline & \multicolumn{6}{c}{PINGU} \\
-      $\ett$ &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] \\
-      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
-      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] \\
-      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
-      & \multicolumn{6}{c}{DeepCore + PINGU} \\
-      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] &  [-0.038, 0.048] &  [-0.058, 0.067] &   [-0.039, 0.05] &          [-0.06] \\
-      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
-      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] &  [-0.071, 0.086] &  [-0.149, 0.141] &  [-0.082, 0.097] &  [-0.17, 0.16] \\
-      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] &  [-0.061, 0.103] &  [-0.131, 0.155] &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
-      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+   \centering
+   \begin{tabular}{lcc}
       \hline
+      Parameter & Best 90\% CL & Best $3\sigma$\\
+      \hline & \multicolumn{2}{c}{PINGU} \\
+      $\ett$ &  [-0.054, 0.067] &               [] \\
+      $\emt$ &  [-0.029, 0.007] &          [0.026] \\
+      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      & \multicolumn{2}{c}{DeepCore + PINGU} \\
+      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
+      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] \\
+      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] \\
+      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] \\\\
+      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
+      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013]  \\
+      \hline
+      \vspace{0.5em}
+   \end{tabular}
+   \begin{tabular}{lcc}
+      \hline 
+      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
+      \hline & \multicolumn{2}{c}{PINGU} \\
+      $\ett$ &   [-0.054, 0.067] &               []\\
+      $\emt$  &  [-0.029, 0.007] &          [0.026]  \\
+      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
+      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      & \multicolumn{2}{c}{DeepCore + PINGU} \\
+      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
+      $\emt$ &    [-0.01, 0.006] &  [-0.016, 0.014] \\
+      $\eem$ &    [-0.071, 0.086] &  [-0.149, 0.141]  \\
+      $\eet$ &   [-0.061, 0.103] &  [-0.131, 0.155] \\\\
+      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
+      $\emt$ &   [-0.01, 0.006] &  [-0.016, 0.014] \\
+      \hline
+      \vspace{0.5em}
+   \end{tabular}
+   \begin{tabular}{lcc}
+      \hline 
+      Parameter & Worst 90\% CL & Worst $3\sigma$\\
+      \hline & \multicolumn{2}{c}{PINGU} \\
+      $\ett$ &    [-0.054, 0.067] &               [] \\
+      $\emt$ &    [-0.029, 0.007] &          [0.026] \\
+      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      & \multicolumn{2}{c}{DeepCore + PINGU} \\
+      $\ett$ &     [-0.039, 0.05] &          [-0.06] \\
+      $\emt$ &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
+      $\eet$ &   [-0.067, 0.11] &  [-0.15, 0.17] \\\\
+      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
+      $\emt$ &   [-0.011, 0.007] &  [-0.017, 0.015] \\
       \hline
    \end{tabular}
-   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
+   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.
+$\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
+   Best, baseline, and worst refer to 
    the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
 \end{table}
+
+%TODO: compare results
 
@@
    \end{center}
-   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+   \caption{Best fit points for $\dm[31]$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
    degrees, respectively.}\label{table:bestfit}
@@
     \end{center}
-   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}\label{fig:event_pulls} 
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
 \end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better
 
-%TODO: subsection about comparison between different papers.
+There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI.
+For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation.
+The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry.
+So ideally, we would simulate a grid where all NSI parameters are allowed to vary, but this is not feasible.
+Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$.
+We let $\ett=0$ because we saw that it did not influence the other parameters.
+We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}.
+We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical.
+Hence, we can see that no relationship exists between them.
+With $\eet - \eem$, however, the contours are assuming a different shape.
+The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
 
@@
    \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
+   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
+   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out.}\label{fig:PINGU_2D}
 \end{figure}
-\begin{figure}
-   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f5.pdf}
-\end{figure}
-\bibliographystyle{elsarticle-num}
-\bibliography{article}
-
-\newpage
-\begin{tabular}{p{55mm}p{55mm}p{55mm}}
-   DeepCore (2017)
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\times$] Only look at tracks and $\emt$
-         \vspace{1em}  
-         \item[$\times$] DC Monte Carlo from an older dataset 
-         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\times$] 8 z bins from -1 to 0 
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
-      \end{itemize} &
-    Demidov (2020) DC analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
-         \item[$\checkmark$] Data and Monte Carlo from DC 2018
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 z bins from -1 to 1
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
-         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
-         \item[$\times$] Uncertainty on hadron production in atmosphere
-         \item[$\times$] Uncertainty on neutrino nucleon cross section 
-      \end{itemize} &
-    This DC+PINGU analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Tracks and cascades for all flavors
-         \vspace{1em} 
-         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
-         \item[$\checkmark$] Flux normalization uncertainty of 25\%
-         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
-         \item[$\checkmark$] No priors on oscillation parameters 
-         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
-      \end{itemize} 
-\end{tabular}
-\end{document}
-
-% \end{document}

### 2021-09-14 thesis/tex/DCtheory.tex
update

@@
 \section{PINGU}
-The methodology behind the PINGU simulations are the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
+The methodology behind the PINGU simulations is the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+However, since no detector systematics is yet modeled for PINGU, the correction factors $C_{ijk}$ are all unity.
 As with the DeepCore data, the PINGU Monte Carlo is divided into eight 

### 2021-09-14 thesis/tex/ICintro.tex
update

@@
 In this work, we consider DeepCore data between \SIrange{5.6}{56}{\GeV} and IceCube data in the range \SIrange{0.5}{10}{\TeV}.
-\begin{figure}\label{fig:array}
+\begin{figure}
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/icecube2.png}
-    \caption{View of the full IceCube array, with the Eiffel tower for scale.}
+    \includegraphics[width=0.8\textwidth]{figures/icecube2.png}
+    \caption{View of the full IceCube array, with the Eiffel tower for scale.}\label{fig:array}
 \end{figure}
@@
 In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The `Precision IceCube Next Generation Upgrade' is an upgrade that will 
-supplement DeepCore, i.e. boosing the capabilities of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
+supplement DeepCore, i.e. boosting the capabilities of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
 not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
@@
 
-\begin{table}[h]\label{table:flux}
+\begin{table}[h]
     \begin{center}
@@
     \end{center}
-    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}
+    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}\label{table:flux}
 \end{table}
 
-\begin{figure}[t]\label{fig:flux}
+\begin{figure}[t]
     \centering
@@
     \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a near-neglible 
-    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}
+    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
 \end{figure}

### 2021-09-14 thesis/tex/nsiTheory.tex
update

@@
 gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
-osillations forces us to amend it. 
+oscillations force us to amend it. 
 Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
@@
 In this sense, the Standard Model might be considered 
-an effective low energy theory, which is yiels impressive results in some areas, but failing in others.
+an effective low energy theory, which is yields impressive results in some areas, but failing in others.
 
-Compared to other fermions, the lightness of neutrino masses\footnote{The extreme lightness might be explained 
-by a mass generation at a higher order theory.} along with their sparse SM interactions might 
-indicate that these particles provide the best starting point for us to probe new physics, in which 
-exotic neutrino interactions might occur~\cite{gavela2009}. We call these interactions non-standard interactions (NSI) in order to 
+Compared to other fermions, the lightness of neutrino masses\footnote{The extreme lightness might be explained by a mass generation at a higher order theory.} along with their sparse SM interactions might
+indicate that these particles provide the best starting point for us to probe new physics, in which exotic neutrino interactions might occur~\cite{gavela2009}.
+We call these interactions non-standard interactions (NSI) in order to
 distinguish them from the `standard' interactions of the Standard Model.
@@
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
-the IceCube data is avaibable in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have settled down.
+the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have settled down.
 
@@
 by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
-we are restriced to weak interactions that conserve lepton number. However, a off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
-the off-diagonal elements constitute new soures of flavor violation.
+we are restricted to weak interactions that conserve lepton number. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
+the off-diagonal elements constitute new sources of flavor violation.
 Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
-of the mixing matrix. Thus, we can in theory boost a flavor transition which is supressed by the mixing matrix. Moreover, since we have 6 NSI parameters, and the PMNS
+of the mixing matrix. Thus, we can in theory boost a flavor transition that is suppressed by the mixing matrix. Moreover, since we have 6 NSI parameters, and the PMNS
 matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
@@
 As discussed in Eq.~\ref{eq:Uvalues}, the atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
-NSI parameters to constrain from muon events. As we will see, $\eem$ is also a candidate, alebit a weaker one.
+NSI parameters to constrain from muon events. As we will see, $\eem$ is also a candidate, albeit a weaker one.
 
@@
 for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
-amplitude nor frequency of the probabilities. Instead, it seems to strech or compress the oscillations. Since the 
+amplitude nor frequency of the probabilities. Instead, it seems to stretch or compress the oscillations. Since the 
 only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
@@
 
-The value of $\ett$ does not affect neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
+The value of $\ett$ affects neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
 to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
@@
     \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
-        \includegraphics[width=0.49\textwidth]{figures/emt_probs.pdf}
-        \includegraphics[width=0.49\textwidth]{figures/ett_probs.pdf}
-        \caption{\emph{Left panel:} Muon neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero.
-        \emph{Right panel:} Muon neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero.}
+        \includegraphics[width=0.9\textwidth]{figures/emt_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/ett_probs.pdf}
+        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\emt = 0.02$.
+All other NSI parameters are fixed to zero.
+In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$.
+At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
+        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\ett = 0.05$.
+All other NSI parameters are fixed to zero.
+$\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study.
+However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
         \label{fig:emt_ett_probs}
@@
     \begin{center}
-        \includegraphics[width=0.49\textwidth]{figures/eem_probs.pdf}
-        \includegraphics[width=0.49\textwidth]{figures/eet_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/eem_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/eet_probs.pdf}
         \caption{Muon neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$\emph{Left panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero.
-        \emph{Right panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero.}
+        $\ztrue = -1$.
+\emph{Top panel:} $\eem = 0.2$.
+All other NSI parameters are fixed to zero.
+Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}.
+At \si{\TeV}, the probability is shifted down, just as with $\emt$.
+        \emph{Bottom panel:} $\eet = 0.2$.
+All other NSI parameters are fixed to zero.
+Here, we see a very weak shifting and a $\nm$ dampening at low \si{\GeV}, and again, no visible effect at \si{TeV} energies.
+}
         \label{fig:eem_eet_probs}
@@
 \subsection{DeepCore and PINGU Signals}
-Now we repeat our proability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
+Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
 we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
@@
     \begin{center}
-        \includegraphics[width=0.8\textwidth]{figures/Pee_eet_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
         \caption{Electron neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero.}
+        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. Compared to the $\nm$ and $\anm$ plots, here we see a strong difference across the whole energy range.}
         \label{fig:Pee_eet_probs}
@@
 \end{figure}
-%TODO: talk a bit about this. Compare cascades to tracks
+
+Now we will compare the probability plots with the final event counts in DeepCore.
+It is not enough to only study the effect at probability level, since that is in true quantities.
+Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets smeared away in the reconstruction, and not showing up at all in the data.
+In general, features showing at probability level are often washed out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.
+
+The top right panel shows a surplus of DeepCore track events at \SIrange{20}{30}{\GeV} for through-going neutrinos when we turn on $\ett$.
+This is what we expected from the bottom right panel in Fig.~\ref{fig:emt_ett_probs}, where we saw that we had an increase in $\anm$ survival probability at \SIrange{20}{40}{\GeV}.
+
+The third right panel shows the expected event pull for $\eem$.
+Comparing with the probabilities in Fig.~\ref{fig:eem_eet_probs}, we see that the surplus of the $\anm$ survival in the \SIrange{20}{30}{\GeV} and the deficit above \SI{40}{\GeV} is intact, while the \SI{10}{\GeV} $\nm$ deficit is completely washed out.
 

### 2021-09-14 thesis/tex/oscillations.tex
update

@@
 oscillations. An implication of the observation of oscillations is neutrino mass, 
-which is identically zero acording to the Standard Model. Thus, we are required to extend the Standard Model to incorporate neutrino 
+which is identically zero according to the Standard Model. Thus, we are required to extend the Standard Model to incorporate neutrino 
 masses before we discuss the neutrino oscillations themselves.
@@
 group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
-This neutrino field is \emph{sterile} since it doesn't participate any of the Standard Model interactions.
+This neutrino field is \emph{sterile} since it doesn't participate in any of the Standard Model interactions.
 
@@
 \end{align}
-Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
+Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
 since no flavor rotation can make massless fields massive.
@@
 While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
-This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement of neutrino flavor eigenstates to have a definite mass. 
+This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement for neutrino flavor eigenstates to have a definite mass. 
 The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
@@
 leaving only one physical phase for us to measure. We are now down to four degrees of freedom in the three dimensional case: three mixing angles
-of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$. The mixing angle $\theta_{ij}$ specifies 
-the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate. The physical interpretation of
-a mixing angle is then the degree of which the $\nu_i$ eigenstate mixes with the $\nu_j$ eigenstate. A non-zero mixing angle will then 
+of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$.
+The mixing angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate.
+The physical interpretation of
+a mixing angle is then the degree to which the $\nu_i$ eigenstate mixes with the $\nu_j$ eigenstate. A non-zero mixing angle will then 
 cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates that we allowed to mix. %TODO: nua = nu1 + nu2
@@
 In our study, we will only use neutrinos originating from conventional cosmic ray interactions in the atmosphere. 
-In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is neglible. From Eq.~\eqref{eq:Uvalues}, w
+In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is negligible. From Eq.~\eqref{eq:Uvalues}, w
 e see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
@@
 amplitude of $\Pme$.
-\begin{figure}
-    \centering
+\begin{figure}[!h]
+    \begin{center}
     \includegraphics[width=0.9\textwidth]{figures/vac_osc.pdf}
     \caption{$\nm$ vacuum oscillations from Eq.~\ref{eq:Pab}}\label{fig:vac_osc}
+    \end{center}
 \end{figure}
@@
     \begin{subfigure}{0.3\textwidth}
+        \vspace{1em}
         \includegraphics[width=1\textwidth]{figures/z-boson.pdf} 
@@
         mediated by a neutral $Z$ boson.}
-    \end{subfigure}%TODO: they are different sizes
+    \end{subfigure}
     \caption{Feymann diagrams showing the two interactions that neutrinos participate in according to the Standard Model.}\label{fig:w_and_z}
@@
 The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can undergo charged current (CC) 
-interactions is the electron flavor. This is because the CC interaction requires a neutrino with flavor $\alpha$ to interact with its charged lepton 
+interactions are the electron flavor. This is because the CC interaction requires a neutrino with flavor $\alpha$ to interact with its charged lepton 
 partner $\alpha$. Since the Earth doesn't consist of any muons or tau particles, the $\nu_\mu$ and $\nu_\tau$ have no charged leptons to undergo CC interactions with. 
@@
 To obtain the average effective Hamiltonian, project it on the electron states in Eq.~\ref{eq:e_states} and integrate over the density and sum over the helicities:
-
 \begin{align}\label{eq:avg_H1}
-    \avg{H_{CC}} &= \int \dd p_e^3\, \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
-           &= \frac{G_F}{\sqrt{2}} \int \dd p_e^3 \bra{e(p_e,h_e)} \left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right]  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \left[\bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x) \right] \ket{e(p_e,h_e)} \nonumber \\
-           &= \frac{G_F}{\sqrt{2}} \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \int \dd p_e^3  f(E_e,T) \times \frac{1}{2} \sum_{h_e} \bra{e(p_e,h_e)} \bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x)   \ket{e(p_e,h_e)}\,.
+    \avg{H_{CC}} &= \int \dd p_e^3\, \bra{e(p_e,h_e)} \times \frac{1}{2} \sum_{h_e} H_{CC}   f(E_e,T) \ket{e(p_e,h_e)} \nonumber \\
+           &= \frac{G_F}{\sqrt{2}} \int \dd p_e^3 \bra{e(p_e,h_e)} \left[ \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \right]  f(E_e,T) \nonumber \\
+           &\hspace{2cm}\times \frac{1}{2} \sum_{h_e} \left[\bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x) \right] \ket{e(p_e,h_e)} \nonumber \\
+           &= \frac{G_F}{\sqrt{2}} \bar\ne \gamma^\rho\, (1- \gamma^5)\, \ne \int \dd p_e^3  f(E_e,T) \nonumber \\
+           &\hspace{2cm} \times \frac{1}{2} \sum_{h_e} \bra{e(p_e,h_e)} \bar e(x) \,\gamma_\rho\, (1- \gamma^5)\, e(x)   \ket{e(p_e,h_e)}\,.
 \end{align}
@@
 neutrinos interact in the flavor basis.}. In other words,
-neutrinos propagate in their mass eigenstates, but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
+neutrinos propagate in their mass eigenstates but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
 determines if the flavor eigenstate has oscillated or not. The interactions still conserve lepton number since the interaction Lagrangian does,
@@
 
-We now see that both matter potentials, regardless if the interaction is of type charged or neutral, is only dependent on the eletron density in the medium, $N_e$ times a constant.
-So to calculate the matter oscillations in an eletrically neutral medium with equal abundance of protons and neutrons, we are only required to consider the matter density of the medium.
+We now see that both matter potentials, regardless of the interaction is of type charged or neutral, are only dependent on the electron density in the medium, $N_e$ times a constant.
+So to calculate the matter oscillations in an electrically neutral medium with an equal abundance of protons and neutrons, we are only required to consider the matter density of the medium.
 
@@
         0 & 0 & V_{NC} \\
-    \end{bmatrix} = V_{CC}\, \delta_{\alpha e}\mathbb{1} + V_{NC}\mathbb{1}\,.
+    \end{bmatrix} = V_{CC}\, \delta_{\alpha e}\mathbb{I} + V_{NC}\mathbb{I}\,.
 \end{align}
@@
 i.e.~the evolution of the state of a neutrino emitted at $t =0$ with flavor $\alpha$ to flavor $\beta$ at time $t$.
-
 Now using Eq.~\ref{eq:osc_1} and Eq.~\ref{eq:V_CC1}, we are ready to see what form our Hamiltonians take.
@@
     \sum_\eta \sum_k U_{\b k} \left(p + \frac{m^2_k}{2E}\right) U^*_{\eta k} \psi_{\a\eta}(x) &= \sum_\eta \sum_k U_{\b k} \left(p + \frac{m^2_1}{2E} + \frac{\dm_{k1}}{2E}\right) U^*_{\eta k} \psi_{\a\eta}(x) \nonumber \\
-    &= \sum_\eta\sum_k \left(p + \frac{m^2_1}{2E}\right) U_{\b k} U^*_{\eta k} \psi_{\a\eta}(x) + \sum_\eta\sum_k U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} \psi_{\a\eta}(x)\,.
+    &= \sum_\eta\sum_k \left(p + \frac{m^2_1}{2E}\right) U_{\b k} U^*_{\eta k} \psi_{\a\eta}(x) \nonumber \\
+    &+ \sum_\eta\sum_k U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} \psi_{\a\eta}(x)\,.
 \end{align}
@@
 
+Eq.~\ref{eq:eff_theta} has a pole at %TODO: write more
+\begin{align}
+    N_e^* &= \frac{\dm[21]\cos(2\theta_{12})}{\sqrt{2}G_F}\,.
+\end{align}
+Expressing the electron density $N_e^*$ in terms of matter density $\rho^*$, electron number per nucleon $Y$, and Avogadro's constant $N_A$, we obtain
+\begin{align}
+    \rho^* &= \frac{\dm[21]\cos(2\theta_{12})}{\sqrt{2}G_F Y N_A}\,.
+\end{align}
+
 Now assume that the matter density is sufficiently smooth along the trajectory $x$, that is $\dd \theta_M / \dd x \approx 0$.
 In its diagonalized form, the Schrödinger equation with two-neutrino Hamiltonian can be solved with this assuption. 
-The solutions are the regular neutrino vacuum oscillations of Eq.~\eqref{eq:Pab} using $\theta[13] = \theta[23] =0$, but with the effective parameters of Eqs.~\eqref{eq:eff_dm,eq:eff_theta}. That is
+The solutions are the regular neutrino vacuum oscillations of Eq.~\ref{eq:Pab} using $\theta_{13} = \theta_{23} =0$, but with the effective parameters of Eqs.~(\ref{eq:eff_dm},~\ref{eq:eff_theta}).
+That is
 %TODO:maybe expand eq below or solve above explicitly?
 \begin{align}
-    P_{e\mu}^M(x) = \sin^2(2\theta_{12}^M))\sin^2(\frac{\dm[21]x}{4E})
+    P_{e\mu}^M(x) = \sin^2(2\theta_{12}^M)\sin^2\left(\frac{\dm[21]x}{4E}\right)\,.
 \end{align}
 
-While two-neutrino flavor oscillation can only be assumed to hold in regions where mixing into the third flavor can be considered neglible,
+While two-neutrino flavor oscillation can only be assumed to hold in regions where mixing into the third flavor can be considered negligible,
 the fact that the mixing angle in matter depends on the squared-mass difference, and vice versa, gives us an interesting conclusion which is 
 still valid for the full three neutrino oscillations. We previously saw that the oscillation amplitudes were entirely dependant on
-the mixing angles, and the oscillation frequencies entirely dependant on the squared-mass difference along with energy, and trajectory. After 
+the mixing angles, and the oscillation frequencies were entirely dependant on the squared-mass difference along with energy, and trajectory. After 
 introducing the matter potentials, we now see that the matter effect mixes the mixing matrix elements together with the masses.
@@
 \subsection{Earth propagation}
-
 We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
-symmetric piecewise polynomials for the Earth density in \si{\gram \cm^3} shown in the left panel of Fig.~\ref{fig:potential}.
-We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary, and will be visible in our 
+symmetric piecewise polynomials for the Earth density in \si{\gram\cm^3} shown in the left panel of Fig.~\ref{fig:potential}.
+We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
 oscillations.
@@
     V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
-           &= \SI{3.8e-23}{\eV \gram \cm^{-3}}\,,
+           &= \SI{3.8e-23}{\eV} \times \rho\,,
 \end{align}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{figures/potential.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/potential.pdf}
     \caption{\emph{Left panel:} The spherically symmetric Earth density according to PREM~\cite{PREM}, as of distance from the core.
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{figures/oscillograms.pdf}
-    \caption{Oscillograms showing neutrino oscillations for all flavors in E-$\cos(\theta_z)$ space.}\label{fig:oscillograms}%TODO: redo finer
+    \includegraphics[width=0.9\textwidth]{figures/oscillograms.pdf}
+    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space.
+Note the panels are symmetric about the diagonal panels, i.e.
+$P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0$.
+The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer
 \end{figure}%TODO: remake with finer
-The core-mantle boundary from Fig.\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.
 

### 2021-09-14 thesis/tex/sterileResults.tex
update

@@
     \includegraphics[width=0.8\textwidth]{figures/IC_rates.pdf}
-    \caption{}\label{fig:IC_rates}
+    \caption{How the null hypothesis compares to the IceCube data from~\cite{IC2020}.}\label{fig:IC_rates}
 \end{figure}
 Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
-for neutrinos close to double-digit \si{\TeV} values. In zenith, the data only deviates $\pm 1\%$. Recalling the \si{\TeV} disappearance from 
+for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$. Recalling the \si{\TeV} disappearance from 
 Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. Thus, we expect the best fitting 
@@
 $N_{ij}^\text{th}$ is the expected number of events from theory, and $N_{ij}^\text{data}$ is the observed number of events in that bin. 
-We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
+We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.05$ as the zenith angle slope error~\cite{hondapaper}. 
 The observed event number has an associated Poissonian uncertainty $\sigma_{ij}^\text{data} = \sqrt{N_{ij}^\text{data}}$.
@@
 Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate with angle $\beta$ around the median zenith angle of $\zreco = -0.5$.
-We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a percentage of our own choosing.
+We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a factor of our own choosing.
 
@@
 From the $\chi^2$-distribution, one can show that the $90\%$ confidence level has a value of $2.71$ for two degrees of freedom. When slicing through the 
-two-dimensional grid of $\Delta \chi^2$ at this level, we then obtain a contour plot that tells us what regions are within our $90 \%$ and what regions are not.
+two-dimensional grid of $\Delta \chi^2$ at this level, we then obtain a contour plot that tells us what parameter values are within our $90 \%$ confidence level and what regions are not.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/final_rate_plot.pdf}
+    \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
     \caption{The predicted binned event count assuming our best-fit sterile hypothesis, compared with the 

### 2021-09-14 thesis/tex/sterileTheory.tex
update

@@
 In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}.  
-Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but observed an excess in the
+Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly but observed an excess in the
 $\ne$ events too. Together with the so-called reactor and gallium anomalies, these reports suggested 
 that the three massive neutrino framework could be amended.
-By introducing a fourth heavy mass state $\nu_4$, both appearance and disappeareance anomalies could be minimally accomodated.
+By introducing a fourth heavy mass state $\nu_4$, both appearance and disappearance anomalies could be minimally accommodated.
 However, we know from the decay width of the $Z$ boson that it only can interact with three flavor species\footnote{
@@
 are three and five magnitudes smaller. To remind us of this hierarchy, we write $3+1$, since the sterile state 
-proposed is a lot more massive than the active states.
+proposed is heavier than the active states.
 
@@
         0 & 0 & 0 & 1 
-    \end{pmatrix}
-    = \sqrt{2}G_F\begin{pmatrix}
+    \end{pmatrix} \nonumber \\
+    &= \sqrt{2}G_F\begin{pmatrix}
         N_e & 0 & 0 & 0 \\
@@
 where we have assumed electrical neutrality in the last step, yielding $N_e = N_n$.
-
 Thus, the final Hamiltonian with a fourth sterile neutrino is 
@@
 , $\theta_{24}$, $\theta_{34}$. In our analysis, we reduce the number of parameters by only considering $\dm[41]$ and $\theta_{24}$, which are 
-the most important for the $\nm$ oscillations. In fact, one can close the $e$ channel by letting $\theta_{14} = 0$ in the \si{\GeV} to \si{\TeV} range, thus 
-using a two-flavor neutrino approximation. This is not done in this work.
+the most important for the $\nm$ oscillations. In fact, one can supress the $e$ channel by letting $\theta_{14} = 0$ in the \si{\GeV} to \si{\TeV} range, thus 
+using a two-flavor neutrino approximation.
 
@@
     \centering
-    \begin{subfigure}{0.35\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \includegraphics[width=1\linewidth]{figures/sterile_resonance.pdf}
@@
     \end{subfigure}
-    \begin{subfigure}{0.69\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \includegraphics[width=1\linewidth]{figures/resonance_shift.pdf}
@@
 In the $3+0$ scenario, $\Pamam = 1$ in this range. Thus, if we are able to see a $\anm$ disappearance in the \si{\TeV} region,
-we are in a good position to argue for a \si{\eV} scale $\dm[41]$.
+we are in a good position to argue for a \si{\eV^2} scale $\dm[41]$.
 

### 2021-09-15 thesis/tex/ICintro.tex
update

@@
 from the table for clarity. 
-We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. Kaons can decay into neutral pions, which in turn 
+We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons can decay into neutral pions, which in turn 
 can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities in the form 
@@
             \hline \hline
-            $E$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\cos(\theta_z)$\\\\
+            $E$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\cos(\theta_z)$\\
             \hline
@@
 called the reconstructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
-The collaboration then uses numerous sophisticated methods to backtrack the reconstructed parameters to the true parameters. 
+The collaboration then uses numerous methods to backtrack the reconstructed parameters to approximate the true parameters. 
 So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true energy and zenith angle, $\Etrue$ and $\ztrue$. 

### 2021-09-15 thesis/tex/ICtheory.tex
update

@@
 Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
-Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the neutrinos are exposed to.
+Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the leptons are exposed to.
 While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself.
 Energy-wise, the situation here is completely reverse from the flux.
-Increasing with energy, the effective area of the detector
-approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
+Increasing with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
 
@@
 \begin{figure}[ht]
-    %\centering
-    \hspace{-2cm}
+    \centering
     \includegraphics[scale=0.4]{figures/IC_data.pdf}
@@
 section is to come as close as we can to their Monte Carlo simulations. After we are confident that 
-our code displays the same overall features as the `offical', we normalize our results $N_{ij}^\text{sim}$ as 
+our code displays the same overall features as the `official', we normalize our results $N_{ij}^\text{sim}$ as 
 \begin{align}\label{eq:MC_norm}
@@
     \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
-    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots. We 
-    see a large deviation for high zenith values, but since these neutrinos have traversed less matter and have a smaller baseline, we deem this to be acceptable.}\label{fig:IC_MC_norm}
+    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
     \end{centering}

### 2021-09-15 thesis/tex/introduction.tex
update

--- 2021-06-16 thesis/tex/introduction.tex
@@
 The most successful framework -- the Standard Model -- has notable shortcomings. Neither does it 
-explain why there is something rather than nothing, nor does it give a candidate for dark matter\footnote{In the Standard Model,
+explain why there is something rather than nothing\footnote{In the Standard Model,
 matter and antimatter come in pairs of one particle and one antiparticle. When interacting,
-antimatter \emph{annihilates} the matter, resulting in pure light. Since the universe exists,
-there must have been more matter than antimatter at the Big Bang. %TODO: check and make better
-Dark matter is heavy matter which does not interact with electromagnetic radiation.
+antimatter \emph{annihilates} the matter, resulting in pure light. Since the universe today contains matter,
+there must have been more matter than antimatter at the Big Bang. This baryon asymmetry is unexplained in the Standard 
+Model.}, nor does it give a candidate for dark matter
+\footnote{Dark matter is heavy matter which does not interact with electromagnetic radiation.
 No such particle exists in the Standard Model.}.
-
-To make matters even worse, three of the massive particles are massless in the Standard Model.
+To make matters even worse, three of the particles which are massless according to the Standard Model have been observed to have mass.
 In this thesis, we focus on the said particles -- the neutrinos -- and propose extensions to the Standard Model related to them. 

### 2021-09-15 thesis/tex/oscillations.tex
update

@@
 Japan 1998. The Super-Kamiokande experiment detects a $\nm$ deficit that could not be explained by any other mechanism
-than the conversion of muon neutrinos to electron neutrinos. This was the first conclusive evidence of a completely new physics phenomenon: neutrino flavor
+than the conversion of muon neutrinos to electron neutrinos~\cite{sk1998}. This was the first conclusive evidence of a completely new physics phenomenon: neutrino flavor
 oscillations. An implication of the observation of oscillations is neutrino mass, 
@@
 In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
-All neutrinos are left-handed and all antineutrinos are right-handed. Thus, they do not pick up a Yukawa coupling, 
+All neutrinos are left-handed and all antineutrinos are right-handed~\cite{giunti}. Thus, they do not pick up a Yukawa coupling, 
 and will not undergo the Higgs mechanism, which leaves them massless.
@@
 \begin{align}
-    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,.
+    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,,
 \end{align}
+where $v$ is the Higgs vacuum expectation value, $H$ the Higgs field, $\ell_{\alpha L}^\prime (\ell_{\beta R}^\prime)$ the left (right) handed charged lepton field with non-definite masses.
+$Y_{\alpha \beta}^{\prime \ell}$ are the charged lepton Yukawa couplings, and $\nu^\prime_{\alpha L}(\nu^\prime_{\beta R})$ are the left (right) handed neutrino fields .
 Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, with the former resulting in the charged lepton masses being non-definite. 
@@
 
-Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$. We will refer to the matrix $U$ built by the components $U_{k \alpha}$ as the
-Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix~\cite{pontecorvo1957,maki1962}. %TODO: source
+Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$.
+We will refer to the matrix $U$ built by the components $U_{k \alpha}$ as the (neutrino) mixing matrix.
+It can also be referred to as the
+Pontecorvo-Maki-Nakagawa-Sakata (PMNS) matrix~\cite{pontecorvo1957,maki1962}.
 We now have 
@@
 The physical interpretation of
-a mixing angle is then the degree to which the $\nu_i$ eigenstate mixes with the $\nu_j$ eigenstate. A non-zero mixing angle will then 
-cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates that we allowed to mix. %TODO: nua = nu1 + nu2
+a mixing angle is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate. A non-zero mixing angle will then 
+cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates that we allowed to mix. More on this in Section~\ref{sec:prop}.
 
-We construct the PMNS matrix using the rotation matrixes from $SO(3)$ as
+We construct the PMNS matrix using the rotation matrices from $SO(3)$ as
 \begin{align}\label{PMNS_def}
@@
 
-In this work, we will be using the best-fit values from~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$. The $90\% $ CL values are
+In this work, we will be using the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$. The $90\% $ CL values are
 \begin{align}\label{eq:nufitparams}
@@
 In our study, we will only use neutrinos originating from conventional cosmic ray interactions in the atmosphere. 
-In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is negligible. From Eq.~\eqref{eq:Uvalues}, w
-e see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
+In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is negligible. From Eq.~\eqref{eq:Uvalues}, we see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
 suggesting that $\nm$ primarily mixes into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
-the most abundant. This means we will be able to stringently constrain parameters relating to $\mu\tau$ mixing.
+the most abundant.
 
-\subsection{Neutrino Propagation}
-Since we now know how the neutrino mass and flavor eigenstates combine, and have an expression for the flavor interaction with 
+\subsection{Neutrino Propagation}\label{sec:prop}
+Since we now know how the neutrino mass and flavor eigenstates combine and have an expression for the flavor interaction with 
 the neutrino's charged lepton partner, we are now ready to study the flavor oscillations themselves.
@@
 Now, the Fourier expansion of the field operator $\bar{\nu}_{k L}$ in the current of Eq.~\ref{eq:j_CC3} contains creation operators $a^\dagger_{\nu_k}$
-of massive neutrinos with mass $m_k$. This means that the summation over the mass index $k$ constructs a flavor neutrino, which interacts with the charged lepton field $\ell_{\a L}$.
+of massive neutrinos with mass $m_k$~\cite{giunti}.
+This means that the summation over the mass index $k$ with the mixing matrix elements constructs a flavor neutrino, which interacts with the charged lepton field $\ell_{\a L}$.
 In other words, the charged current generates a flavor neutrino $\na$, which is a superposition of the mass eigenstates 
@@
 where $H_0$ is the vacuum Hamiltonian. 
-
 The solution to Eq.~\ref{eq:TDSE} gives ut the time evolution
@@
 \end{align}
-Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse?We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
+Now we know how to evolve and combine the mass eigenstates to form a flavor eigenstate, but how about the reverse? We swap the index $k\to j$ in Eq.~\ref{eq:osc_1} and multiply by $U_{\a k}$:
 \begin{align}\label{eq:osc_k}
@@
 \begin{align}
-    P_{\na \to \nb}(t) = \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
+    P_{\na \to \nb}(t) &= {\bra{\nb}\ket{\na (t)}}^2\sum_{k,j} \nonumber \\
+    &= U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
 \end{align}
@@
 We assume the neutrino masses $m_k$ to be extremely small compared to their associated energies $E_k$. 
-Thus, $v\sim 1$, and $\abs{\vec{p}} \sim E$ making the energy-dispersion relation of Eq.~\ref{eq:disp} to first order:
+Thus, $v\approx 1$, and $\abs{\vec{p}} \approx E$ making the energy-dispersion relation of Eq.~\ref{eq:disp} to first order:
 \begin{align}\label{eq:ultra_rel}
@@
     \includegraphics[width=0.9\textwidth]{figures/vac_osc.pdf}
-    \caption{$\nm$ vacuum oscillations from Eq.~\ref{eq:Pab}}\label{fig:vac_osc}
+    \caption{$\nm$ vacuum oscillations from Eq.~\ref{eq:Pab}
+    for $\nm$ neutrinos travelling 12 000 km.}\label{fig:vac_osc}
     \end{center}
 \end{figure}
-
-this form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
+This form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
 determine the amplitude of the oscillations, while the mass-squared differences together with the ratio $L/E$ determine the 
@@
     \end{subfigure}
-    \caption{Feymann diagrams showing the two interactions that neutrinos participate in according to the Standard Model.}\label{fig:w_and_z}
+    \caption{Feymann diagrams showing neutrinos participating in the two types of weak interactions according to the Standard Model.}\label{fig:w_and_z}
 \end{figure}
@@
 We refer to this as \emph{Earth-like matter}.}, mediated by the neutral $Z$ boson
-The interaction mediated by the $W$ boson will give rise to a effective matter potential $V_{CC}$, while
+The interaction mediated by the $W$ boson will give rise to an effective matter potential $V_{CC}$, while
 the $Z$ boson is responsible for $V_{NC}$. Our task is now to find expressions for these.
@@
 
-For neutral current, we replace the electron field $e(x)$ in Eq.~\ref{eq:H_fierz} by the more general fermion field $f(x)$, and the projection operator 
+For neutral current, we replace the electron field $e(x)$ in Eq.~\ref{eq:H_fierz} by the more general fermion field $f(x)$, and the chiral projection operator 
 $(1-\gamma^5)$ with $(g_V^f - g_A^f\gamma^5)$. Again, the $\gamma^5$ will cause the spacial component of $p_f$ to disappear after integration, and the 
@@
 The rotation $R_{13}$ will not affect our mass matrix, since the former acts in the $1-3$ plane, and the latter sits in the $1-2$ plane.
-Thus, the reduced mass matrix $\mathcal{M}_{12}$ commutes with $R_{13}$.
-Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathcal{M}_{12}$.
+Thus, the reduced mass matrix $\mathbb{M}_{12}$ commutes with $R_{13}$.
+Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathbb{M}_{12}$.
 Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
@@
 \begin{align}
-    U \mathcal{M}_{12} U^\dagger &=
-    R_{23}R_{13}R_{12} \mathcal{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
-    &= R_{12}R_{23}R_{13} \mathcal{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
-    &= R_{12}\mathcal{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
+    U \mathbb{M}_{12} U^\dagger &=
+    R_{23}R_{13}R_{12} \mathbb{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
+    &= R_{12}R_{23}R_{13} \mathbb{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
+    &= R_{12}\mathbb{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
 \end{align}
@@
 \begin{align}
-    R\,R^\dagger = \mathcal{I}\,,
+    R\,R^\dagger = \mathbb{I}\,,
 \end{align}
@@
 \begin{align}
-    U \mathcal{M}_{12} U^\dagger &= R_{12}\mathcal{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
-    &= R_{12}\mathcal{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
-    &= R_{12}\mathcal{M}_{12}  R_{12}^\dagger\,.
+    U \mathbb{M}_{12} U^\dagger &= R_{12}\mathbb{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
+    &= R_{12}\mathbb{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
+    &= R_{12}\mathbb{M}_{12}  R_{12}^\dagger\,.
 \end{align}
@@
 
-We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the final two-neutrino Hamiltonian:
+We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form, and start simplifying:
 
@@
         &= 
-        \frac{1}{2E}\left[
+        \frac{1}{2E}
             \begin{pmatrix}
-                s_{12}^2 + \sqrt{2}G_F N_e & \dm_{21} s_{12}c_{12} \\ 
+                \dm_{21} s_{12}^2 & \dm_{21} s_{12}c_{12} \\ 
                 \dm_{21} s_{12}c_{12} & \dm_{21} c_{12}^2 \\ 
-            \end{pmatrix}  \right]
+            \end{pmatrix} + \sqrt{2}G_F N_e 
+            \begin{pmatrix}
+            1 & 0 \\
+            0 & 0 \\
+        \end{pmatrix} \nonumber \\
+            &= 
+        \frac{1}{4E}
+            \begin{pmatrix}
+                \dm_{21} (1-\cos(2\theta_{12}))& \dm_{21}  \sin(2\theta_{12}) \\ 
+                \dm_{21}  \sin(2\theta_{12}) & \dm_{21} (1+\cos(2\theta_{12})) \\ 
+            \end{pmatrix} + \sqrt{2}G_F N_e 
+            \begin{pmatrix}
+            1 & 0 \\
+            0 & 0 \\
+        \end{pmatrix}
 \end{align}
-%TODO: complete trig simplification
-
+Just as we did with Eq.~\ref{eq:components}, we can subtract a term proportional to the identity matrix without affecting the underlying physics. Thus, we subtract
+\begin{align}
+    \frac{\dm[21]}{4E} - \frac{1}{2}\sqrt{2}G_F N_e
+\end{align}
+times the identity from the Hamiltonian, obtaining the final two-neutrino Hamiltonian
+\begin{align}
+    H_F &= \frac{1}{4E}
+    \begin{pmatrix}
+        -\dm_{21} \cos(2\theta_{12}) & \dm_{21}  \sin(2\theta_{12}) \\ 
+        \dm_{21}  \sin(2\theta_{12}) & \dm_{21} \cos(2\theta_{12}) \\ 
+    \end{pmatrix} + \frac{1}{2}\sqrt{2}G_F N_e 
+    \begin{pmatrix}
+    1 & 0 \\
+    0 & -1 \\
+    \end{pmatrix} \nonumber \\
+    &= \frac{1}{4E}
+    \begin{pmatrix}
+        -\dm_{21} \cos(2\theta_{12}) + \sqrt{2}G_F N_e  & \dm_{21}  \sin(2\theta_{12}) \\ 
+        \dm_{21}  \sin(2\theta_{12}) & \dm_{21} \cos(2\theta_{12}) - \sqrt{2}G_F N_e  \\ 
+    \end{pmatrix}
+\end{align}
 This matrix has eigenvalues which we identify as the effective two-neutrino squared-mass difference $(\dm[21])^M$. They are
@@
 \begin{align}\label{eq:eff_dm}
-    \pm (\dm[21])^M = \pm \sqrt{(\dm[21] \cos{(2\theta_{12}) - \sqrt{2}G_F N_e})^2 + (\dm[21]\sin{(2\theta_{12})})^2}
+    \pm (\dm[21])^M = \pm \sqrt{(\dm[21] \cos{(2\theta_{12}) - 2\sqrt{2}G_F N_e E})^2 + (\dm[21]\sin{(2\theta_{12})})^2}
 \end{align}
@@
 \begin{align}\label{eq:eff_theta}
-    \tan{(2\theta_{12}^M)} = \frac{\tan{(2\theta_{12})}}{1- \frac{\sqrt{2}G_F N_e}{\dm[21]\cos{(2\theta_{12})}}}\,.
+    \tan{(2\theta_{12}^M)} = \frac{\tan{(2\theta_{12})}}{1- \frac{2\sqrt{2}G_F N_e E}{\dm[21]\cos{(2\theta_{12})}}}\,.
 \end{align}
-
 Eq.~\ref{eq:eff_theta} has a pole at %TODO: write more
 \begin{align}
-    N_e^* &= \frac{\dm[21]\cos(2\theta_{12})}{\sqrt{2}G_F}\,.
+    E^* &= \frac{\dm[21]\cos(2\theta_{12})}{2\sqrt{2}G_F N_e}\,.
 \end{align}
-Expressing the electron density $N_e^*$ in terms of matter density $\rho^*$, electron number per nucleon $Y$, and Avogadro's constant $N_A$, we obtain
-\begin{align}
-    \rho^* &= \frac{\dm[21]\cos(2\theta_{12})}{\sqrt{2}G_F Y N_A}\,.
-\end{align}
+So at a certain electron density, a neutrino with energy $E^*$ will experience a resonance in the matter mixing angle.
+This phenomenon is called MSW resonance after Mikheev, Smirnov, and Wolfenstein.
+At this point, $\tan{(2\theta_{12}^M)} \to \infty$, which is equivalent to the matter mixing angle $\theta_{12}^M$ assuming its maximal value, $\pi/4$.
+Thus, the MSW resonance can cause maximal mixing between two flavors.
 
-Now assume that the matter density is sufficiently smooth along the trajectory $x$, that is $\dd \theta_M / \dd x \approx 0$.
-In its diagonalized form, the Schrödinger equation with two-neutrino Hamiltonian can be solved with this assuption. 
+Now assume that the matter density is sufficiently constant along a trajectory $x$, that is $\dd \theta_M / \dd x \approx 0$.
+In its diagonalized form, the Schrödinger equation with two-neutrino Hamiltonian can be solved with this assumption. 
 The solutions are the regular neutrino vacuum oscillations of Eq.~\ref{eq:Pab} using $\theta_{13} = \theta_{23} =0$, but with the effective parameters of Eqs.~(\ref{eq:eff_dm},~\ref{eq:eff_theta}).
 That is
-%TODO:maybe expand eq below or solve above explicitly?
+
 \begin{align}
-    P_{e\mu}^M(x) = \sin^2(2\theta_{12}^M)\sin^2\left(\frac{\dm[21]x}{4E}\right)\,.
+    P_{e\mu}^M = \sin^2(2\theta_{12}^M)\sin^2\left(\frac{\dm[21]L}{4E}\right)\,.
 \end{align}
@@
 the mixing angles, and the oscillation frequencies were entirely dependant on the squared-mass difference along with energy, and trajectory. After 
-introducing the matter potentials, we now see that the matter effect mixes the mixing matrix elements together with the masses.
+introducing the matter potentials, we now see that the matter effect mixes the mixing matrix elements with the masses and the energy. 
 %TODO: maybe 2 vs 3 plot

### 2021-09-15 thesis/tex/sterileResults.tex
update

@@
 for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$. Recalling the \si{\TeV} disappearance from 
-Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. Thus, we expect the best fitting 
-sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
-that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.
+Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. 
+%Thus, we expect the best fitting 
+%sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
+%that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.
 
@@
 higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensetive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
-remains fixed. We put $f=35\%$ and compare our results to the Giunti et al.~\cite{gariazzoUpdatedGlobalAnalysis2017} in Fig.~\ref{fig:s24_contour}.
-Here, we see that our lower fixed region between \SIrange{1e-1}{1}{\eV\squared} is closer to the IceCube result than Giunti et al, but that 
-our contour slightly diverges above \SI{1}{\eV\squared}. 
+remains fixed. %We put $f=35\%$ and compare our results to the Giunti et al.~\cite{gariazzoUpdatedGlobalAnalysis2017} in Fig.~\ref{fig:s24_contour}. %TODO fix
+%Here, we see that our lower fixed region between \SIrange{1e-1}{1}{\eV\squared} is closer to the IceCube result than Giunti et al, but that 
+%our contour slightly diverges above \SI{1}{\eV\squared}. 
 \begin{figure}
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/s24_error_tuning.pdf}
+    \includegraphics[scale=0.58]{figures/s24_error_tuning.pdf}
     \caption{The 90\% CL contour with two different systematic error scalings, compared 
-    with the official IceCube result from~\cite{IC2020}}\label{fig:error_tuning}
+    with the official IceCube result from~\cite{IC2020}.}\label{fig:error_tuning}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/s24_contour.pdf}
-    \caption{The 90\% CL contour using $f=35\%$, compared with the official IceCube result from~\cite{IC2020}
-    and the result from~\cite{gariazzoUpdatedGlobalAnalysis2017}}\label{fig:s24_contour}    
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.8\textwidth]{figures/s24_contour.pdf}
+%    \caption{The 90\% CL contour using $f=35\%$, compared with the official IceCube result from~\cite{IC2020}
+%    %and the result from~\cite{gariazzoUpdatedGlobalAnalysis2017}
+%    }\label{fig:s24_contour}    
+%\end{figure} %TODO fix
 

### 2021-09-15 src/probability/functions.py

@@ -410,4 +410,4 @@ def integrate(array,method='simps',*args):
     elif np.ndim(array) == 4:
         return simps(simps(simps(simps(array,args[0]),args[1]),args[2]),args[3])
 if __name__ == '__main__':
-    print(U_4(params=ic_params))
+    print(dc_params['dm_21']*1e-18*np.cos(2*dc_params['theta_12']) /(2*np.sqrt(2) * GF * 0.5 * N_A * 1 * (1/GeVtocm1)**3))

### 2021-11-13 thesis/tex/SM.tex
update
Corrected

@@
     \centering
-    \includegraphics[width=0.7\textwidth]{figures/SM_figure.pdf}
+    \includegraphics[width=0.8\textwidth]{figures/SM_figure.pdf}
 \end{figure}
-\section{The Standard Model}\label{ch:SM}
+\section{The Standard Model}\label{ch:SM} %TODO: expand
 In order to describe the three quantizable forces of nature, we gather the mediators of each force -- the vector bosons -- into local (gauge) symmetry groups. 
@@
 so they participate in the strong and electromagnetic interactions. If a quark is left-handed, it will also feel the weak interaction. 
-The neutrinos on the other hand, have neither charge nor color, 
-so they are insivible to both the strong and electromagnetic force. We express this by letting their fields transform as singlets under those symmetry groups.
+The neutrinos, on the other hand, have neither charge nor color, 
+so they are invisible to both the strong and electromagnetic force. We express this by letting their fields transform as singlets under those symmetry groups.
 
+\subsection{Beyond the Standard Model}
 Together, these three interactions make up the Standard Model gauge group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
@@
 Since the vector bosons are represented by the generators, they are uniquely determined by the symmetry group. However, the scalar boson(s) and fermions are free as long as they
-belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. Even the
+belong to representations of the symmetry group.
+By this construction, modifications to fermions rather than bosons are generally easier to make, allowing us to propose amendments to the model.
+Even the
 number of fermions must be experimentally verified and can be altered from a phenomenological standpoint. In this work,
 we will use this leniency to introduce a new particle and examine to which extent 
-these modifications might be supported by experimental evidence. Moreover, we will examine the possibility of adding a new completely new force to the Standard Model.
-As then follows from our discussion above, this means that we will add a symmetry group and thus also at least one more vector boson.
+these modifications might be supported by experimental evidence.
+Moreover, we will examine the possibility of adding a new completely new force, which manifests itself as modifications to the neutrino-matter interactions.
 
-%TODO: write about convervation laws
-% \subsection{Lepton mixing}
-% Now we shall see how the charged leptons interact with the chargeless neutrinos.
-% Consider how charged leptons interact with the Higgs field. In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
-% \begin{align}
-%     \label{eq:YukawaLagrangian}
-%     \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
-% \end{align}
-% has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the charged lepton masses being non-definite.
-This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
-% \begin{align}\label{eq:leptonYukawaDiag}
-%     V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
-% \end{align}
-% This procedure give the charged lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. 
-% However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
-% \begin{align}
-%     \label{eq:j_CC}
-%     j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
-%              &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
-%              &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
-% \end{align}
-% where each lepton field and matrix have an implied $L$ subscript, which was dropped for clarity.
-The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$.
-However,
-% $\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
-% \bibliographystyle{apalike}
-% \bibliography{ref}
-% \end{document}
+\section{Mass Generation}
+In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
+All neutrinos are left-handed and all antineutrinos are right-handed~\cite{giunti}. Thus, they do not pick up a Yukawa coupling, 
+and will not undergo the Higgs mechanism, which leaves them massless.
+Additionally, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
+generated at loop level because any such attempt will violate the total lepton number by two units.
+In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing right-handed neutrinos and left-handed antineutrinos.
+
+We consider a right-handed neutrino field, $\nu_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
+left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the Standard Model symmetry 
+group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
+
+%TODO: write eq for lepton doublet
+
+We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa part of the interaction Lagrangian
+\begin{align} % TODO: its not a Lorentz scalar, there has to be a bar somewhere. Is it incorrect?
+    \mathcal{L}_{int} \subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,,
+\end{align}
+where $v$ is the Higgs vacuum expectation value, $H$ the Higgs field, $\ell_{\alpha L}^\prime (\ell_{\beta R}^\prime)$ the left (right) handed charged lepton field.
+$Y_{\alpha \beta}^{\prime \ell}$ are the charged lepton Yukawa couplings, and $\nu^\prime_{\alpha L}(\nu^\prime_{\beta R})$ are the left (right) handed neutrino fields .
+Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal. 
+%TODO: Y  is not symmetric. We need to do a bi-unitary transformation. If you are not sure, just drop this.
+%We need two diagonalizations here
+This can be remedied by diagonalizing $Y^{\prime \nu}$ with a unitary matrix $V^\nu$ as
+\begin{align}
+    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
+\end{align}
+Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
+since no flavor rotation can make massless fields massive.
+Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
+While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
+This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement for neutrino flavor eigenstates to have a definite mass. 
+The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
+This fact is denoted as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
+
+So, let the neutrino field in the mass basis have components with Latin numerals to distinguish them from the flavour components, i.e 
+\begin{align}\label{eq:nu_rotation} 
+    \nu_{k} =  V_{k\beta}^{\nu \dagger} \nu_{\beta}^\prime\,.
+\end{align}
+The diagonalized Lagrangian now takes the form 
+\begin{align}
+    \mathcal{L}_{int} &\subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}
+    + \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]
+\end{align}
+By construction, $Y^\ell$ and $Y^\nu$ are diagonal, so we write their components as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
+\begin{align}\label{eq:L_H}
+    \mathcal{L}_{int} 
+    &\subseteq-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell} \delta_{\alpha \beta} \ell_{\beta R} + \bar{\nu}_{k L} y_{k}^{\nu} \delta_{k j} \nu_{j R}\right] \nonumber \\
+    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell}  \ell_{\alpha R} + \bar{\nu}_{k L} y_{k}^{\nu} \nu_{k R}\right] \nonumber \\
+    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}  \bar{\ell}_{\alpha L}\ell_{\alpha R} +  y_{k}^{\nu}\bar{\nu}_{k L} \nu_{k R}\right] 
+\end{align}
+Now, by the introduction of the right-handed field $\nu_R$, the Dirac neutrino field is
+\begin{align}
+    \nu_k = \nu_{kL} + \nu_{kR}\,.
+\end{align}
+Multiplying $\nu_k$ with its conjugate $\bar{\nu}_k$, we get 
+\begin{align}
+    \bar{\nu}_k \nu_k 
+    & = \bar{\nu}_{k L} \nu_{k L} +\bar{\nu}_{k R}\nu_{k L} + \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k R} \nonumber \\
+    & = \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k L} \nonumber \\
+    & = \bar{\nu}_{k L}\nu_{k R} + \t{h.c.}
+\end{align}
+The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and multiplying the Higgs vacuum expectation value $v$ into the fields gives us
+\begin{align}
+    \mathcal{L}_{H} 
+    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}   \bar{\ell}_\alpha \ell_\alpha  +  y_{k}^{\nu} \bar{\nu}_k \nu_k \right] \nonumber \\
+    &=- \frac{y_{\alpha}^{\ell} v}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha   -  \frac{ y_{k}^{\nu} v}{\sqrt{2}} \bar{\nu}_k \nu_k  - \frac{y_{\alpha}^{\ell}}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha H  -  \frac{ y_{k}^{\nu}}{\sqrt{2}} \bar{\nu}_k \nu_k H\,.
+\end{align}
+Thus, this extension to the SM generates by the Higgs mechanism neutrino masses with terms
+\begin{align}
+    m_k = \frac{y_k^\nu v}{\sqrt{2}}\,,
+\end{align}
+where the Yukawa couplings $y^\nu_k$ needs to be experimentally determined.

### 2021-11-13 thesis/tex/oscillations.tex
Corrected

@@
 
-\subsection{Mass Generation}
-In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
-All neutrinos are left-handed and all antineutrinos are right-handed~\cite{giunti}. Thus, they do not pick up a Yukawa coupling, 
-and will not undergo the Higgs mechanism, which leaves them massless.
-Additionally, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
-generated at loop level because any such attempt will violate the total lepton number by two units.
-In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing right-handed neutrinos and left-handed antineutrinos.
-
-We consider a right-handed neutrino field, $\nu_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
-left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the Standard Model symmetry 
-group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
-This neutrino field is \emph{sterile} since it doesn't participate in any of the Standard Model interactions.
-
-We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa Lagrangian 
-\begin{align}
-    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,,
-\end{align}
-where $v$ is the Higgs vacuum expectation value, $H$ the Higgs field, $\ell_{\alpha L}^\prime (\ell_{\beta R}^\prime)$ the left (right) handed charged lepton field with non-definite masses.
-$Y_{\alpha \beta}^{\prime \ell}$ are the charged lepton Yukawa couplings, and $\nu^\prime_{\alpha L}(\nu^\prime_{\beta R})$ are the left (right) handed neutrino fields .
-Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, with the former resulting in the charged lepton masses being non-definite. 
-This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$ as
-\begin{align}
-    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
-\end{align}
-Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
-since no flavor rotation can make massless fields massive.
-Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
-While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
-This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement for neutrino flavor eigenstates to have a definite mass. 
-The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
-This fact is denoted as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
-
-So, let the neutrino field with chriality $X$ be denoted $\nu_X$, with components having Latin numerals to distinguish them from the flavour components, i.e 
-\begin{align}\label{eq:nu_rotation}
-    \nu_{k X} =  V_{k\beta X}^{\nu \dagger} \nu_{\beta X}^\prime\,.
-\end{align}
-The diagonalized Lagrangian now takes the form 
-\begin{align}
-    \mathcal{L}_{H} &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}
-    + \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]
-\end{align}
-By construction, $Y^\ell$ and $Y^\nu$ are diagonal, so we write their components as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
-\begin{align}\label{eq:L_H}
-    \mathcal{L}_{H} 
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell} \delta_{\alpha \beta} \ell_{\beta R} + \bar{\nu}_{k L} y_{k}^{\nu} \delta_{k j} \nu_{j R}\right] \nonumber \\
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell}  \ell_{\alpha R} + \bar{\nu}_{k L} y_{k}^{\nu} \nu_{k R}\right] \nonumber \\
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}  \bar{\ell}_{\alpha L}\ell_{\alpha R} +  y_{k}^{\nu}\bar{\nu}_{k L} \nu_{k R}\right] 
-\end{align}
-Now, by the introduction of the sterile field $\nu_R$, the Dirac neutrino field is
-\begin{align}
-    \nu_k = \nu_{kL} + \nu_{kR}\,.
-\end{align}
-Multiplying $\nu_k$ with its conjugate $\bar{\nu}_k$, we get 
-\begin{align}
-    \bar{\nu}_k \nu_k 
-    & = \bar{\nu}_{k L} \nu_{k L} +\bar{\nu}_{k R}\nu_{k L} + \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k R} \nonumber \\
-    & = \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k L} \nonumber \\
-    & = \bar{\nu}_{k L}\nu_{k R} + \t{h.c.}
-\end{align}
-The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and multiplying the Higgs vacuum expectation value $v$ into the fields gives us
-\begin{align}
-    \mathcal{L}_{H} 
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}   \bar{\ell}_\alpha \ell_\alpha  +  y_{k}^{\nu} \bar{\nu}_k \nu_k \right] \nonumber \\
-    &=- \frac{y_{\alpha}^{\ell} v}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha   -  \frac{ y_{k}^{\nu} v}{\sqrt{2}} \bar{\nu}_k \nu_k  - \frac{y_{\alpha}^{\ell}}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha H  -  \frac{ y_{k}^{\nu}}{\sqrt{2}} \bar{\nu}_k \nu_k H\,.
-\end{align}
-Thus, this extension to the SM generates by the Higgs mechanism neutrino masses with terms
-\begin{align}
-    m_k = \frac{y_k^\nu v}{\sqrt{2}}\,,
-\end{align}
-where the Yukawa couplings $y^\nu_k$ needs to be experimentally determined.
 \subsection{The Mixing Matrix}
@@
 We now have 
-\begin{align}\label{eq:j_CC3} %TODO: put sums on all above?
+\begin{align}\label{eq:j_CC3}
     j^\rho_L &= 2 \sum_\alpha \sum_k U^\dagger_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}\,.
@@
 leaving only one physical phase for us to measure. We are now down to four degrees of freedom in the three dimensional case: three mixing angles
+%TODO: Look CKM wikipedia, good explanation.
+Mention that it is not guaranteed that the mixing matrix that we only have one phase.
+We could Have three due to Dirac/majorana.
+Majorana phases are not relevant for oscillations because oscillations are not violating lepton number, but include them in PMNS.
 of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$.
@@
 
-We construct the PMNS matrix using the rotation matrices from $SO(3)$ as
+We construct the PMNS matrix using a standard parametrization as
 \begin{align}\label{PMNS_def}
@@
 \begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
-\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}\,.
-\end{align}
-The term $\delta_\text{CP}$ determines the degree of charge-parity violation. In this work, we will always assume CP invariance for simplicity by
-setting $\delta_{CP} = \SI{0}{\degree}$. Thus,
-
-\begin{align}
-    U &=
-    \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
-\begin{pmatrix}c_{13} & 0 & s_{13} \\ 0 & 1 & 0 \\ -s_{13}  & 0 & c_{13}\end{pmatrix}
 \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix} \nonumber \\
-    &= 
-    \begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} \\ 
+ %TODO: add dcp
+ &=\begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} \\ 
         -s_{12} c_{23}-c_{12} s_{23} s_{13} & c_{12} c_{23}-s_{12} s_{23} s_{13} & s_{23} c_{13} \\ 
         s_{12} s_{23}-c_{12} c_{23} s_{13}  & -c_{12} s_{23}-s_{12} c_{23} s_{13} & c_{23} c_{13}
-    \end{pmatrix}\,.
-\end{align}
-
-In this work, we will be using the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$. The $90\% $ CL values are
-\begin{align}\label{eq:nufitparams}
-    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
-\end{align}
-Our neglect of the issue of CP invariance leaves the PMNS matrix real, with numerical values 
-\begin{align}\label{eq:Uvalues}
-    U = \begin{pmatrix}
+    \end{pmatrix} \nonumber \\
+&= \begin{pmatrix}
   U_{e 1} & U_{e2} & U_{e3} \\
@@
    U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
-    \end{pmatrix} 
-    = \begin{pmatrix}
-        0.825 & 0.545 & 0.149 \\
-        -0.455 & 0.485 & 0.746 \\
-        0.334 & -0.684 & 0.649
-    \end{pmatrix} \,.
+\end{pmatrix}\,.
 \end{align}
-In our study, we will only use neutrinos originating from conventional cosmic ray interactions in the atmosphere. 
-In this so-called atmospheric neutrino flux, $\nm$ are the most abundant, while the $\nt$ flux is negligible. From Eq.~\eqref{eq:Uvalues}, we see that $U_{\mu\tau}$ is the largest $U_{\mu\beta}$ term,
-suggesting that $\nm$ primarily mixes into $\nt$, at least in vacuum. It turns out that matter effects indeed preserves this ordering, making the $\nm \to \nt$ transition
-the most abundant.
 
@@
 
-Now, the Fourier expansion of the field operator $\bar{\nu}_{k L}$ in the current of Eq.~\ref{eq:j_CC3} contains creation operators $a^\dagger_{\nu_k}$
-of massive neutrinos with mass $m_k$~\cite{giunti}.
-This means that the summation over the mass index $k$ with the mixing matrix elements constructs a flavor neutrino, which interacts with the charged lepton field $\ell_{\a L}$.
+From the expression for the weak charged current in~\ref{eq:j_CC3}, we see that the summation over the mass index $k$ with the mixing matrix elements constructs a flavor neutrino, which interacts with the charged lepton field $\ell_{\a L}$.
 In other words, the charged current generates a flavor neutrino $\na$, which is a superposition of the mass eigenstates 
@@
 \begin{align}
-    P_{\na \to \nb}(t) &= {\bra{\nb}\ket{\na (t)}}^2\sum_{k,j} \nonumber \\
-    &= U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
+    P_{\na \to \nb}(t) &= \sum_{k,j} {\bra{\nb}\ket{\na (t)}}^2 \nonumber \\
+    &= \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(E_k-E_j)t}\,.
 \end{align}
@@
 \begin{align}\label{eq:ultra_rel}
-    E_k &= \sqrt{\vec{p}^2 + m_k^2} \nonumber \\
-        &= \vec{p}^2\sqrt{1 + \frac{m_k^2}{\vec{p}^2}} \nonumber \\
+    E_k &= \sqrt{{\vec{p}}^2 + m_k^2} \nonumber \\
+        &= {\vec{p}}^2\sqrt{1 + \frac{m_k^2}{\vec{p}^2}} \nonumber \\
         &\approx E + \frac{m_k^2}{2E}
@@
 \begin{align}
-    P_{\ab}(t) = \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)t/2E}\,.
+    %TODO: check abs
+    P_{\ab}(t) = \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)t/2E}\,.
 \end{align}
@@
 \begin{align}
-    P_{\ab}(x) &= \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
-                       &= \sum_{k,j} U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E})\,,
+    P_{\ab}(x) &= \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
+                       &= \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E})\,,
 \end{align}
 where we in the last step have defined the \emph{mass-squared difference} $\dm_{kj} = m_k^2 - m_j^2$. Since the oscillation probability depends on this quantity
-rather than the individual masses, it is impossible to measure the mass $m_k$ through neutrino oscillations. 
+rather than the individual masses, it is impossible to measure the absolute mass $m_k$ through neutrino oscillations. We have
+to rely on other types of experiments to get us at least one absolute mass, from which we then can calculate the remaining.
 Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^\dagger = \delta_{\a \b}$ yields 
@@
 \end{align}
-Since we take the PMNS matrix to be real and thus Hermitian, we drop the complex transpose in the following calculation. We have
-\begin{align}\label{eq:Pab}%TODO: shorten?
+%TODO: include dcp
+We have
+\begin{align}\label{eq:Pab} 
+    %TODO: include dcp and don't write so many lines
     P_{\ab} &= \sum_{k,j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
@@
 The calculation for antineutrinos yield the same result if one continues to assume the realness of the mixing matrix.
-In Fig.~\ref{fig:vac_osc}, we show the energy spectra of these oscillations in the low \si{\GeV} range for neutrinos that travel \SI{12000}{\km}\footnote{This baseline
+
+Experimental measurements show that $\theta_{13}$ is the smallest of the mixing angles~\cite{nufit}, causing 
+$\nm$ to primarily mix into $\nt$. The mixing matrix from~\ref{PMNS_def} takes the values
+\begin{align}\label{eq:Uvalues}
+   U = \begin{pmatrix}
+       U_{e 1} & U_{e2} & U_{e3} \\
+       U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
+       U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
+   \end{pmatrix} 
+   = \begin{pmatrix}
+       0.825 & 0.545 & 0.149 \\
+       -0.455 & 0.485 & 0.746 \\
+       0.334 & -0.684 & 0.649
+   \end{pmatrix} \,,
+\end{align}
+which use to we plot the $P_{\mu \beta}$ probabilities in Fig.~\ref{fig:vac_osc}.
+Here, we show the energy spectra of these oscillations in the low \si{\GeV} range for neutrinos that travel \SI{12000}{\km}\footnote{This baseline
 is approximately the Earth diameter, and will be the maximum travel distance which we will use later on.}.
@@
 numerical values of the mixing matrix in Eq.~\ref{eq:Uvalues}.
-\si{\GeV} oscillations are driven by the $\dm[31]$ mass-squared difference. Hence, the most important mixing matrix 
-elements for $P_{\a\b}$ are $U_{\a3}, U_{\a1}$ and $U_{\b3}, U_{\b1}$. The smallness of $U_{e3}$ then supresses the
-amplitude of $\Pme$.
+The smallness of $U_{e3}$ reduces the effect of $\dm[21]$ mass-squared difference,
+allowing $\dm[31]$ to drive the oscillations. 
+The most important mixing matrix 
+elements for $P_{\a\b}$ are $U_{\a3}, U_{\a1}$ and $U_{\b3}, U_{\b1}$. %TODO: write whole 4 product here
+%instead of U,U and U,U
+
 \begin{figure}[!h]
+    %TODO: write pme, pmm, pmt in titles, bigger ticks
     \begin{center}
-    \includegraphics[width=0.9\textwidth]{figures/vac_osc.pdf}
-    \caption{$\nm$ vacuum oscillations from Eq.~\ref{eq:Pab}
-    for $\nm$ neutrinos travelling 12 000 km.}\label{fig:vac_osc}
+    \includegraphics[width=1\textwidth]{figures/vac_osc.pdf}
+    \caption{Probabilities of $\nm$ oscillations travelling 12 000 km in vaccum.}\label{fig:vac_osc}
     \end{center}
@@
 
-\subsection{Effective Potentials}
+\subsection{Neutrino Oscillations in Matter}
 
@@
         \includegraphics[width=1\textwidth]{figures/z-boson.pdf} 
-        \caption{Neutral current weak interaction between a neutrino of any flavor and a Earth-like fermion,
+        \caption{Neutral current weak interaction between a neutrino of any flavor and an electron, proton, or neutron,
         mediated by a neutral $Z$ boson.}
@@
 \end{figure}
-In this work, we are concerned about the interactions with the neutrino and Earth-like matter, i.e.~electrons, protons, and neutrons. 
+So far we have discussed neutrinos travelling in vacuum. Now we will concern ourselves with neutrino oscillations in matter.
 The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can undergo charged current (CC) 
@@
 partner $\alpha$. Since the Earth doesn't consist of any muons or tau particles, the $\nu_\mu$ and $\nu_\tau$ have no charged leptons to undergo CC interactions with. 
-The right panel shows any neutrino flavor interaction via the neutral current (NC) with Earth-like matter\footnote{The Earth is entirely composed
-of electrons, protons, and neutrons.
-Thus, the fundamental particles composing Earth are electrons, and up and down quarks.
-We refer to this as \emph{Earth-like matter}.}, mediated by the neutral $Z$ boson
+The right panel shows any neutrino flavor interaction via the neutral current (NC) with matter, mediated by the neutral $Z$ boson. The Earth is entirely composed
+of electrons, protons, and neutrons. Thus, the fundamental particles composing Earth are electrons, and up and down quarks. These are the 
+fermions relevant for our matter oscillations. 
 The interaction mediated by the $W$ boson will give rise to an effective matter potential $V_{CC}$, while
-the $Z$ boson is responsible for $V_{NC}$. Our task is now to find expressions for these.
+the $Z$ boson is responsible for $V_{NC}$.
 

### 2021-11-16 thesis/tex/ICintro.tex
update

@@
-% \documentclass{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \usepackage{graphicx, slashed, siunitx, subcaption}
-% \usepackage[utf8]{inputenc}
-% \usepackage{xr-hyper}
-% \input{commands}
-% \begin{document}
 \section{Neutrino detection}
+%TODO: Write down detection process. This section should be written carefully. 
+% Specify the guys going into NC and CC. 
+% First line only true for CC
+% In next lines ,detail the detection process (interaction with detector matter osv). 
+% Specify which are occurring in tracks and cascades.
 We always observe neutrinos indirectly through their associated charged lepton. 
@@
 the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
+To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
+into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
+
+The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than others.
+8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}.
+This detector is referred to DeepCore.
+DeepCore will be treated as a separate and independent detector from the rest, which
+retains the name IceCube.
+A view of the current setup can be seen in Fig.~\ref{fig:array}.
+In this work, we consider DeepCore data between \SIrange{5.6}{56}{\GeV} and IceCube data in the range \SIrange{0.5}{10}{\TeV}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/icecube2.png}
+    \caption{View of the full IceCube array, with the Eiffel tower for scale.}\label{fig:array}
+\end{figure}
+
 If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
@@
 is shown in Fig.~\ref{fig:events_cascade}.
+% S wanted to remove below. Why?
 If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
@@
 is shown in Fig.~\ref{fig:events_track}. 
+%TODO: numbers on how often^. Write about which particles appear where
 
@@
 
-To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
-into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
-
-The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than others.
-8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}. Due to 
-this part being situated deep within the ice, it is referred to DeepCore. DeepCore will be treated as a separate and independent detector from the rest, which
-retains the name IceCube.
-A view of the current setup can be seen in Fig.~\ref{fig:array}.
-In this work, we consider DeepCore data between \SIrange{5.6}{56}{\GeV} and IceCube data in the range \SIrange{0.5}{10}{\TeV}.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/icecube2.png}
-    \caption{View of the full IceCube array, with the Eiffel tower for scale.}\label{fig:array}
-\end{figure}
-
 In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The `Precision IceCube Next Generation Upgrade' is an upgrade that will 
@@
 These interactions ultimately produces pions, which decay as 
-\begin{align}\label{eq:pion}
+\begin{align}\label{eq:pion} %Incorrect. Add muon decays
     &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
@@
 In the muonic decay channel, muons are emitted which will be detected by the IceCube detector.
-The detector's experience an uncorrelated systematic error, which comes from this \emph{muon background}, 
-i.e. events misclassified as muons from 
-$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
-For IceCube events, we will scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
-expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
-to be neglible~\cite{PINGUletter}.
-Moreover, the atmospheric flux itself is often associated with a large error.
-In this work, we will use a flux normalization error of 25\%, and a zenith slope error of 5\%~\cite{hondapaper}.
 
@@
 from the table for clarity. 
-We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons can decay into neutral pions, which in turn 
-can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities in the form 
+We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
 $P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
@@
     \centering
+    %TODO: rework
     \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
-    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a near-neglible 
+    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
     zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
@@
 
-\subsection{Event Reconstruction}
-After an event has occurred, the IceCube algorithms process the data coming from the detector to \emph{reconstruct} the event. 
+\subsection{True and Recontstructed Parameters}
+After an event has occurred, the IceCube collaboration \emph{reconstruct} the event. 
 This means that, given the parameters recorded by the detector, what are their `true' values?
@@
 called the reconstructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
-The collaboration then uses numerous methods to backtrack the reconstructed parameters to approximate the true parameters. 
+In other words, the collaboration uses the recorded data to backtrack the event, using the reconstructed parameters to approximate the true parameters. 
 So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true energy and zenith angle, $\Etrue$ and $\ztrue$. 

### 2021-11-16 thesis/tex/ICtheory.tex
Corrected
update

@@
 The charged lepton then emits the Cherenkov light that is detected by the array.
+We construct the event rate for each bin as
+\begin{align}\label{eq:ICevents}
+    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
+    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
+    \,,
+\end{align}
+where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\theta_z^r$ the reconstructed 
+zenith angle, i.e. the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle, i.e. the actual direction of the incoming neutrino. 
+$E^r$ is the reconstructed energy, binned with index $j$. $R(\theta^r,\theta^t)$ is a zenith resolution function 
+that describes the relationship with the reconstructed and true zenith angles, specific to the 86-string configuration of IceCube.
+$R(E^r,E^t)$ is an energy resolution function 
+that describes the relationship with the reconstructed and true energies. $\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
+in accordance with Eq.~\ref{eq:propFlux}.
+
 We now are interested in the effective area $\Aeff$, 
@@
   \end{tabular}
-  \caption{A selection of the data found in~\ref{IC2016}}
+  \caption{A selection of the data found in~\cite{IC2016}}
   \label{table:IC_MC}
@@
 
-The event rate for each bin reads
-\begin{align}\label{eq:ICevents}
-    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
-    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
-    \,,
-\end{align}
-where $T$ is the live time of the detector.
-Now this expression handles the Gaussian smearing, but we are not provided systematic error sources, DOM efficiencies, and other nuisance parameters.
-To correct this,
+Now, Eq.~\ref{eq:ICevents} handles the Gaussian smearing, but we are not provided systematic error sources, DOM efficiencies, and other nuisance parameters. To correct this,
 we will aim to come as close as possible to the IceCube Monte Carlo, and then normalize with it.
@@
 In Fig.~\ref{fig:IC_MC_norm}, we present the Icecube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
-with our null hypothesis times a constant factor.  We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
+with our null hypothesis times a constant factor. 
+We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0$ for simplicity. The values used are
+\begin{align}\label{eq:nufitparams}
+    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+\end{align}
+
+We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
 correction factors of Eq.~\ref{eq:MC_norm}. We now arrive to our final event count

### 2021-11-16 thesis/tex/nsiResults.tex
update

@@
 \section{Non-Standard Interactions}\label{sec:nsiResults}
+%TODO: add
 \subsection{Constraining the NSI parameters}\label{sec:constraining}
@@
 
+%TODO: check that below flows
 For DeepCore and PINGU, and the event count takes the form
@@
 with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
+The detector's experience an uncorrelated systematic error, which comes from this \emph{muon background}, 
+i.e. events misclassified as muons from 
+$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
+For IceCube events, we scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
+expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
+to be neglible~\cite{PINGUletter}.
 The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
@@
    \begin{center}
-      \includegraphics[width=0.8\textwidth]{figures/joint_3D_NO.pdf}
+      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
       \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon.
@@
       \hline
-      \vspace{0.5em}
+      %\vspace{0.5em}
    \end{tabular}
@@
 For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation.
-The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry.
-So ideally, we would simulate a grid where all NSI parameters are allowed to vary, but this is not feasible.
+The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
+but this is not feasible.
 Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$.
@@
 \begin{figure}
-   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
+   \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
    \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two

### 2021-11-16 thesis/tex/nsiTheory.tex
update

@@
 All other NSI parameters are fixed to zero.
-Here, we see a very weak shifting and a $\nm$ dampening at low \si{\GeV}, and again, no visible effect at \si{TeV} energies.
+Here, we see a very weak shifting and a $\nm$ weaker dip at low \si{\GeV}, and again, no visible effect at \si{TeV} energies.
 }
@@
 Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
-a weaker resonance dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.
+a shallower dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.
 
-$\eem$ in Fig.~\ref{fig:eem_eet_probs} shows weak resonance dampening for both $\nm$ and $\anm$.
+$\eem$ in Fig.~\ref{fig:eem_eet_probs} causes a weaker dip for both $\nm$ and $\anm$.
 
-For $\eet$, we see a similar resonance dampening in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
+For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
 see the $\eet$ effect in DeepCore/PINGU, but remember that we now have the option to look at the other flavor channels.

### 2021-11-16 thesis/tex/oscillations.tex
update

@@
 is approximately the Earth diameter, and will be the maximum travel distance which we will use later on.}.
-In the left-most panel, we see a supressed $\nm \to \ne$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
+In the left-most panel, we see a suppressed $\nm \to \ne$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
 numerical values of the mixing matrix in Eq.~\ref{eq:Uvalues}.
@@
 \end{figure}
-So far we have discussed neutrinos travelling in vacuum. Now we will concern ourselves with neutrino oscillations in matter.
+So far we have discussed neutrinos traveling in vacuum. Now we will concern ourselves with neutrino oscillations in matter.
 The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can undergo charged current (CC) 
@@
 of electrons, protons, and neutrons. Thus, the fundamental particles composing Earth are electrons, and up and down quarks. These are the
-fermions relevant for our matter oscillations. 
+fermions relevant for our matter oscillations. In these two diagrams, we see that the CC interactions happen in the flavor basis rather than in the mass basis. In other words,
+neutrinos propagate in their mass eigenstates but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
+determines if the flavor eigenstate has oscillated or not.
+
 The interaction mediated by the $W$ boson will give rise to an effective matter potential $V_{CC}$, while
@@
     \avg{H_{CC}} &= \frac{G_F N_e}{\sqrt{2}} \bar{\nu}_e \, (1- \gamma^5)\, \ne \gamma_0 \nonumber \\
-            &= \sqrt{2}G_F N_e \bar{\nu}_{eE} \gamma^0 \nu_{eL}\,,
+            &= \sqrt{2}G_F N_e \bar{\nu}_{eR} \gamma^0 \nu_{eL}\,,
 \end{align}
-where the projection operator $(1- \gamma^5)$ in the first line ensures that only the left-hand compontent of the neutrino fields interact. Thus,
+where the projection operator $(1- \gamma^5)$ in the first line ensures that only the left-hand compontent of the neutrino fields interact.
+Here we see a crucial difference that we expected: comparing the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H_{CC}$ shows us 
+that by this construction, CC interactions occur in the flavor basis.
+
+The effective 
+potential that the electron neutrino experiences is then
 \begin{align}\label{eq:V_CC1}
-    V_{CC} = \sqrt{2}G_F N_e\,, \quad H_{CC}\ket{\nu_k} = V_{CC}\ket{\nu_k}\,.
+    V_{CC} = \sqrt{2}G_F N_e\,.
 \end{align}
-Here we see a crucial difference between the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H_{CC}$, namely
-that the CC interactions happen in the flavor basis rather than in the mass basis\footnote{A similar calculation for the NC reveals the same fact:
-neutrinos interact in the flavor basis.}. In other words,
-neutrinos propagate in their mass eigenstates but interact in their flavor eigenstate. The mixing of mass eigenstates during propagation
-determines if the flavor eigenstate has oscillated or not. The interactions still conserve lepton number since the interaction Lagrangian does,
-but the kinetic Lagrangian will not. Hence, neutrinos violate lepton number convervation during propagation.
 
@@
 
-\subsection{Matter Oscillations}
 Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors. 
@@
 Just as in Eq.~\ref{eq:TDSE}, we start with a Hamiltonian that solves the time-dependent Schrödinger equation. This time, let the Hamiltonian be 
-\begin{align}
+\begin{align}\label{eq:H_full}
     H = H_0 + H_{I}\,,
@@
 where $H_0$ is the Hamiltonian in vacuum, and $H_{I}$ is our interaction Hamiltonian associated with our matter potentials.
-Let the wavefunction that describes the $\nu_\a \to \nu_\b$ transition be denoted as
+Let the amplitude for the $\nu_\a \to \nu_\b$ transition be denoted as
 \begin{align}
@@
 Let us start with the vaccum Hamiltonian $H_0$, and act on its Schrödinger equation with $\bra{\nu_\b}\,$:
-\begin{align}
+\begin{align}\label{eq:TDSE_H0}
     i \dv{}{t}\ket{\nu_\a (t)} = H_0\ket{\nu_\a (t)} \implies i \dv{}{t}\psi_{\a\b} = \bra{\nu_\b}H_0\ket{\nu_\a (t)}\,.
 \end{align}
+Eq.~\ref{eq:TDSE_H0} with the full Hamiltonian from Eq.~\ref{eq:H_full} is what we will numerically solve for the three neutrino picture
+for neutrino oscillations in matter.
+
+\subsection{Three Neutrino Picture}
 Reminding ourselves that the vacuum Hamiltonian $H_0$ has eigenstates in the mass basis, we write the following expression where 
@@
 
-\subsection{Two neutrino mixing}
+\subsection{Two Neutrino Picture Solution}
 By working in the limit where one of the neutrino masses can be neglected, 
-we can reduce the complexity of the analytical solution of neutrino oscillation. 
+we can reduce the complexity of the neutrino oscillations and obtain tractable analytical 
+expressions. 
 We now only consider the mixing between two neutrino flavors, say between $\ne, \nm$, and $\nu_1, \nu_2$. In other words, we let $\dm[31] = 0$.
@@
 We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
-
 \begin{align}
@@
 Now we need to incorporate the \emph{zenith angle}, here defined as the angle between the neutrino direction of travel and south.
-This way, neutrinos traveling through the entire diameter of the Earth up through the South Pole are defined as `up-going', while
-neutrinos that start at the South Pole are `down-going'. We will mostly work with the quantity $\cos{(\theta_z)}$.
+This way, neutrinos traveling through the entire diameter of the Earth are defined as `up-going', while
+neutrinos that directly over-head are `down-going'. We will mostly work with the quantity $\cos{(\theta_z)}$.
 Since we are interested in the matter effects, some studies are only looking at up-going neutrinos, i.e. neutrinos with

### 2021-11-16 thesis/tex/sterileTheory.tex
update

@@
 so this fourth mass state cannot be interacting weakly. In other words, it needs to transform as a
-singlet under the broken gauge group $SU(2)_L \times U(1)_{EM}$.
+singlet under the gauge symmetry group $SU(2)_L \times U(1)_{Y}$.
 We now distinguish between the three original neutrino flavors ($e$, $\mu$, and $\tau$) and the new fourth 
@@
 
-\subsection{Sterile Signals}
-Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
+\subsection{Effect of Sterile Neutrino on Probabilities}
+Since the new, sterile, neutrino does not interact weakly, how do we know if it's there? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
 we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 

### 2021-11-16 thesis/tex/nsiTheory.tex
update

@@
 
-\subsection{Altering the Matter Potential}
+\subsection{Non-Standard Effects on Neutrino Matter Interactions}
 Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.

### 2021-11-18 thesis/tex/SM.tex
update

@@
 \end{figure}
-\section{The Standard Model}\label{ch:SM} %TODO: expand
+\section{The Standard Model}\label{ch:SM}
 In order to describe the three quantizable forces of nature, we gather the mediators of each force -- the vector bosons -- into local (gauge) symmetry groups. 
@@
 In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
-All neutrinos are left-handed and all antineutrinos are right-handed~\cite{giunti}. Thus, they do not pick up a Yukawa coupling, 
+All neutrinos are left-handed and all antineutrinos are right-handed~\cite{giunti}. This observational fact is reflected in the 
+left-handed lepton doublet and right-handed lepton singlet
+
+\begin{align}
+    L^\prime_{\alpha L} = \begin{pmatrix}
+            \nu^\prime_{\alpha L} \\
+        \alpha^\prime_{L} 
+    \end{pmatrix}\,, \quad
+    \ell^\prime_{\alpha R} =
+    \alpha^\prime_{R} \,,            
+\end{align}
+where $\alpha \in \{e,\mu,\tau\}$, and the primes denotes that the fields do not have definite masses.
+The essential part here is that $\nu^\prime_{\alpha R}$ is missing from the right-handed lepton singlet.
+Thus, the neutrino fields do not pick up a Yukawa coupling, 
 and will not undergo the Higgs mechanism, which leaves them massless.
-Additionally, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
+Moreover, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
 generated at loop level because any such attempt will violate the total lepton number by two units.
-In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing right-handed neutrinos and left-handed antineutrinos.
+In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing right-handed neutrino and left-handed antineutrino fields.
 
-We consider a right-handed neutrino field, $\nu_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
+We consider a right-handed neutrino field, $\nu^\prime_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
 left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the Standard Model symmetry 
@@
 
-%TODO: write eq for lepton doublet
-
 We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa part of the interaction Lagrangian
-\begin{align} % TODO: its not a Lorentz scalar, there has to be a bar somewhere. Is it incorrect?
-    \mathcal{L}_{int} \subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,,
+\begin{align} 
+    \mathcal{L}_{int} \subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[ \bar{\ell}^{\prime}_{\alpha L} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \bar{\nu}_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,,
 \end{align}
-where $v$ is the Higgs vacuum expectation value, $H$ the Higgs field, $\ell_{\alpha L}^\prime (\ell_{\beta R}^\prime)$ the left (right) handed charged lepton field.
+where $v$ is the Higgs vacuum expectation value, $H$ the Higgs field, $\ell_{\alpha L}^\prime (\ell_{\beta R}^\prime)$ the left (right) handed charged lepton field, and summation over the lepton indices $\alpha,\beta$ is implied.
 $Y_{\alpha \beta}^{\prime \ell}$ are the charged lepton Yukawa couplings, and $\nu^\prime_{\alpha L}(\nu^\prime_{\beta R})$ are the left (right) handed neutrino fields .
-Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal. 
-%TODO: Y  is not symmetric. We need to do a bi-unitary transformation. If you are not sure, just drop this.
-%We need two diagonalizations here
-This can be remedied by diagonalizing $Y^{\prime \nu}$ with a unitary matrix $V^\nu$ as
+Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, as emphasized with their prime. 
+This can be remedied by diagonalizing $Y^{\prime \ell}$  with a biunitary transformation
 \begin{align}
-    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
+    V_{ L}^{\ell \dagger} Y^{\prime \ell} V_{ R}^{\ell}=Y^{\ell} \,.
 \end{align}
+where $V^\ell_L$ and $V^\ell_R$ are two unitary matrices.
 Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
@@
 \begin{align}
-    \mathcal{L}_{int} &\subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}
-    + \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
+    \mathcal{L}_{int} &\subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \bar{\nu}_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}
+    + \bar{\nu}_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
+    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
     &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]

### 2021-11-18 thesis/tex/nsiResults.tex
update

@@
 where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
-$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
+$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
+and $k$ denotes the event-type bin, i.e. track or cascade. 
+$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
+incertainty.
 
@@
 with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median cosine-zenith of $\zreco = -0.5$. 
+The event index $k$ is omitted since we only have track events for IceCube.
 
-%TODO: check that below flows
 For DeepCore and PINGU, and the event count takes the form
@@
 with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
-The detector's experience an uncorrelated systematic error, which comes from this \emph{muon background}, 
+The detectors experience an uncorrelated systematic error, which comes from the muon background, 
 i.e. events misclassified as muons from 
@@
 
-We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ij}^\text{syst} = f\sqrt{N_{ij}^\text{data}}$.
 We consider best, normal, and worst-case scenarios in IceCube using
-$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$. %TODO: maybe source/justification for these values?
+$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$.
 For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 

### 2021-11-18 thesis/tex/oscillations.tex
update

@@
 
-What form does this new matrix $U$ take? By construction, it provides the unitary transformation between the flavor and mass bases.
-Any unitary $3\times3$ matrix can be parametrized using three mixing angles and six phases. However, not all phases affect the 
+We construct the PMNS matrix by parametrizing it as as
+\begin{align}\label{PMNS_def}
+    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12} \nonumber \\
+     &= \begin{pmatrix}
+        U_{e 1} & U_{e2} & U_{e3} \\
+         U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
+         U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
+      \end{pmatrix} \nonumber \\
+      & = \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
+\begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
+\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix} \nonumber \\
+ &=\begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 
+        -s_{12} c_{23}-c_{12} s_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{12} c_{23}-s_{12} s_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & s_{23} c_{13} \\ 
+        s_{12} s_{23}-c_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}}  & -c_{12} s_{23}-s_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{23} c_{13}
+    \end{pmatrix}\,,
+\end{align}
+where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \delta_\mathrm{CP} \leq 2\pi$
+
+By construction, it provides the unitary transformation between the flavor and mass bases.
+Any unitary $3\times3$ matrix can be parametrized using three angles and six phases. However, not all phases affect the 
 charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
-leaving only one physical phase for us to measure. We are now down to four degrees of freedom in the three dimensional case: three mixing angles
+leaving only one physical phase for us to measure. We are now down to four degrees of freedom in the three dimensional case: three angles
 %TODO: Look CKM wikipedia, good explanation.
@@
 Majorana phases are not relevant for oscillations because oscillations are not violating lepton number, but include them in PMNS.
-of the form $\sin{(\theta_{ij})}/\cos{(\theta_{ij})} = s_{ij}/c_{ij}$, and one phase of the form $e^{i\delta}$.
-The mixing angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate.
+of the form $s_{ij}, c_{ij}$, and one phase of the form $e^{i\delta}$.
+The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate.
 The physical interpretation of
-a mixing angle is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate. A non-zero mixing angle will then 
-cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates that we allowed to mix. More on this in Section~\ref{sec:prop}.
-
-We construct the PMNS matrix using a standard parametrization as
-\begin{align}\label{PMNS_def}
-    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12} \nonumber \\
-      & = 
-    \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
-\begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
-\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix} \nonumber \\
- %TODO: add dcp
- &=\begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} \\ 
-        -s_{12} c_{23}-c_{12} s_{23} s_{13} & c_{12} c_{23}-s_{12} s_{23} s_{13} & s_{23} c_{13} \\ 
-        s_{12} s_{23}-c_{12} c_{23} s_{13}  & -c_{12} s_{23}-s_{12} c_{23} s_{13} & c_{23} c_{13}
-    \end{pmatrix} \nonumber \\
-&= \begin{pmatrix}
-  U_{e 1} & U_{e2} & U_{e3} \\
-   U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
-   U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
-\end{pmatrix}\,.
-\end{align}
+a mixing angle is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate. Thus we refer to $\theta_{ij}$ as the mixing angles. A non-zero mixing angle will then 
+cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates $\nu_i$ that we allowed to mix. More on this in Section~\ref{sec:prop}.
 
@@
 \begin{align}
-    \bra{\nu_\b}H\ket{\nu_\a (x)} &= \left(p + \frac{m^2_1}{2E} + V_{NC}\right) \psi_{\a\b}(x) + \sum_\eta\sum_k \left(U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} + V_{CC}\delta_{\b\eta}\delta_{\eta e} \right) \psi_{\a\eta}(x)
+    \bra{\nu_\b}H\ket{\nu_\a (x)} &= \left(p + \frac{m^2_1}{2E} + V_{NC}\right) \psi_{\a\b}(x) \nonumber \\
+                                  &+ \sum_\eta\sum_k \left(U_{\b k} \frac{\dm_{k1}}{2E} U^*_{\eta k} + V_{CC}\delta_{\b\eta}\delta_{\eta e} \right) \psi_{\a\eta}(x)
 \end{align}
@@
 expressions. 
-We now only consider the mixing between two neutrino flavors, say between $\ne, \nm$, and $\nu_1, \nu_2$. In other words, we let $\dm[31] = 0$.
+We now only consider the mixing between two neutrino flavors, say between $\ne, \nm$, and $\nu_1, \nu_2$. In other words, we let $\dm[31] = 0$. For simplicity, let $\delta_{CP} = 0$.
 

### 2021-11-21 thesis/tex/nsiResults.tex
update

@@
-\section{Non-Standard Interactions}\label{sec:nsiResults}
-%TODO: add
-\subsection{Constraining the NSI parameters}\label{sec:constraining}
+\section{Constraining the NSI parameters}\label{sec:constraining}
 In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.

### 2021-11-21 thesis/tex/oscillations.tex
update

@@
-% \input{commands}
-% \begin{document}
-
 \section{Neutrino Mixing}\label{ch:oscillation}
@@
 \begin{align}\label{PMNS_def}
-    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12} \nonumber \\
+    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12}P_{Maj} \nonumber \\
      &= \begin{pmatrix}
@@
 \begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
-\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix} \nonumber \\
+\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}
+\begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda{2}} & 0 \\ 0 & 0 & e^{i \lambda{3}}\end{pmatrix}
+\nonumber \\
  &=\begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 
@@
         s_{12} s_{23}-c_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}}  & -c_{12} s_{23}-s_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{23} c_{13}
-    \end{pmatrix}\,,
+    \end{pmatrix}
+    \begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda{2}} & 0 \\ 0 & 0 & e^{i \lambda{3}}\end{pmatrix}\,,
 \end{align}
-where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \delta_\mathrm{CP} \leq 2\pi$
+where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \lambda{i},\delta_\mathrm{CP} \leq 2\pi$.
 
@@
 charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
-leaving only one physical phase for us to measure. We are now down to four degrees of freedom in the three dimensional case: three angles
-%TODO: Look CKM wikipedia, good explanation.
-Mention that it is not guaranteed that the mixing matrix that we only have one phase.
-We could Have three due to Dirac/majorana.
-Majorana phases are not relevant for oscillations because oscillations are not violating lepton number, but include them in PMNS.
-of the form $s_{ij}, c_{ij}$, and one phase of the form $e^{i\delta}$.
+leaving only one physical phase for us to measure: one term in the form of a Dirac CP-violating phase $\delta_\mathrm{CP}$.
+However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
+Thus, we include two Majorana phases $\lambda{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
+Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number.
+
+We are now down to six degrees of freedom in the three dimensional case: three angles
+of the form $s_{ij}, c_{ij}$, and three phase of the form $e^{i\delta_\mathrm{CP}}$ and $e^{\lambda{i}}$.
 The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate.
@@
 \begin{align}
-    P_{\na \to \nb}(t) &= \sum_{k,j} {\bra{\nb}\ket{\na (t)}}^2 \nonumber \\
-    &= \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(E_k-E_j)t}\,.
+    P_{\na \to \nb}(t) &= \sum_{k,j} \abs{{\bra{\nb}\ket{\na (t)}}}^2 \nonumber \\
+    &= U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
 \end{align}
@@
 \begin{align}
-    %TODO: check abs
     P_{\ab}(t) = \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)t/2E}\,.
@@
 \end{align}
-%TODO: include dcp
 We have
 \begin{align}\label{eq:Pab} 
-    %TODO: include dcp and don't write so many lines
-    P_{\ab} &= \sum_{k,j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} +\sum_{k \neq j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &= \delta_{\a \b} - 2 \sum_{k>j}U_{\a k} U_{\b k} U_{\b j} U_{\a j} + 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\exp(-i\frac{\dm_{kj}x}{2E})\right] \nonumber \\
+    P_{\ab} &= \sum_{k,j} \abs{U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \sum_{k \neq j} \abs{U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^\dagger U_{\b k} U_{\a j} U_{\b j}^\dagger] +\sum_{k \neq j} \abs{U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            %&= \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^\dagger U_{\b k} U_{\a j} U_{\b j}^\dagger] + 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            %&= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\exp(-i\frac{\dm_{kj}x}{2E})\right] \nonumber \\
             %&= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\cos(\frac{\dm_{kj}x}{2E})\right] \nonumber \\
-            &= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
+            &= \delta_{\a \b} - 4\sum_{k > j} \Re[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)} \nonumber \\
+            &\hspace{1.2cm}+ 2\sum_{k > j} \Im[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
 \end{align}
 which is the probability of neutrino vacuum oscillations.
-The calculation for antineutrinos yield the same result if one continues to assume the realness of the mixing matrix.
+A similar calculation for antineutrinos yield  
+\begin{align}\label{eq:Pab} 
+    P_{\ab} 
+            &= \delta_{\a \b} - 4\sum_{k > j} \Re[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)} \nonumber \\
+            &\hspace{1.2cm}- 2\sum_{k > j} \Im[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
+\end{align}
 
 Experimental measurements show that $\theta_{13}$ is the smallest of the mixing angles~\cite{nufit}, causing 
-$\nm$ to primarily mix into $\nt$. The mixing matrix from~\ref{PMNS_def} takes the values
+$\nm$ to primarily mix into $\nt$. Using values from~\cite{nufit}, but taking $\delta_\mathrm{CP} = 0$ for simplicity,
+the mixing matrix from~\ref{PMNS_def} takes the values
 \begin{align}\label{eq:Uvalues}
@@
 
-The three-neutrino oscillation Hamiltonian from Eq.~\eqref{eq:H_3gen} %TODO: derive this
+The three-neutrino oscillation Hamiltonian from Eq.~\eqref{eq:H_3gen}
 now reduces to 
@@
 introducing the matter potentials, we now see that the matter effect mixes the mixing matrix elements with the masses and the energy.
-%TODO: maybe 2 vs 3 plot
 

### 2021-11-21 thesis/tex/ICtheory.tex
update

@@
 
-In Fig.~\ref{fig:IC_MC_norm}, we present the Icecube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
+In Fig.~\ref{fig:IC_MC_norm}, we present the IceCube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
 with our null hypothesis times a constant factor. 

### 2021-11-24 thesis/tex/nsiTheory.tex
update

@@
 In the limit $\epsilon_{\ab} \to 0$, we recover the standard interaction Hamiltonian from Eq.~\ref{eq:H_3gen}.
-We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ will make the NSI violate 
-lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
+We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ contribute
+to neutrino mixing, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
 any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
@@
 
-Another feature of our DeepCore study includes the fact that we now have access to cascade events, in which $\ne$ and $\nt$ are more abundant. %TODO:show this?
+Another feature of our DeepCore study includes the fact that we now have access to cascade events, in which $\ne$ and $\nt$ are more abundant.
 Thus, we are no longer constrained to the $\mu$ channel alone, but we can now find interesting features in the other channels too. However, we 
-remember that the $\nm$ flux is still the most abundant. %TODO: link to plot comparison of m and e flux.
+remember that the $\nm$ flux is still the most abundant.
 
@@
 number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
-%TODO: clean up above and expand a bit.
+
 \begin{figure}

### 2021-11-24 thesis/tex/oscillations.tex

@@
 We are now down to six degrees of freedom in the three dimensional case: three angles
-of the form $s_{ij}, c_{ij}$, and three phase of the form $e^{i\delta_\mathrm{CP}}$ and $e^{\lambda{i}}$.
+of the form $s_{ij}, c_{ij}$, and three phase of the form $e^{i\delta_\mathrm{CP}}$ and $e^{i\lambda_{i}}$.
 The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate.
@@
 In other words, the charged current generates a flavor neutrino $\na$, which is a superposition of the mass eigenstates 
-$\nu_k$ with weights $U_{\a k}^\dagger$. In the ket-formalism, we express this as
+$\nu_k$ with weights $U_{\a k}^*$. In the ket-formalism, we express this as
 \begin{align}\label{eq:osc_1}
-    \ket{\na} = \sum_k U^\dagger_{\a k} \ket{\nu_k}\,.
+    \ket{\na} = \sum_k U^*_{\a k} \ket{\nu_k}\,.
 \end{align}
@@
 \begin{align}\label{eq:nat}
-    \ket{\na(t)} = \sum_k U^\dagger_{\a k} e^{-iE_kt}\ket{\nu_k}\,.
+    \ket{\na(t)} = \sum_k U^*_{\a k} e^{-iE_kt}\ket{\nu_k}\,.
 \end{align}
@@
 \begin{align}\label{eq:osc_k}
-    \sum_\a U_{\a k}\ket{\na} &= \sum_{\alpha, j} U_{\a k} U_{\a j}^\dagger \ket{\nu_j} \nonumber \\
+    \sum_\a U_{\a k}\ket{\na} &= \sum_{\alpha, j} U_{\a k} U_{\a j}^* \ket{\nu_j} \nonumber \\
                               &= \sum_{j} \delta_{kj} \ket{\nu_j} \nonumber \\
@@
 \begin{align}
-    \ket{\na(t)} &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\ket{\nu_k} \nonumber \\
-                 &= \sum_k U^\dagger_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
-                 &= \sum_{k,\b} U^\dagger_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
+    \ket{\na(t)} &= \sum_k U^*_{\a k} e^{-iE_kt}\ket{\nu_k} \nonumber \\
+                 &= \sum_k U^*_{\a k} e^{-iE_kt}\left(\sum_\b U_{\b k}\ket{\nb}\right) \nonumber \\
+                 &= \sum_{k,\b} U^*_{\a k}U_{\b k} e^{-iE_kt} \ket{\nb}\,.
 \end{align}
@@
     P_{\na \to \nb}(t) &= \sum_{k,j} \abs{{\bra{\nb}\ket{\na (t)}}}^2 \nonumber \\
-    &= U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
+    &= U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j} e^{-i(E_k-E_j)t}\,.
 \end{align}
@@
 \begin{align}
-    P_{\ab}(t) = \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)t/2E}\,.
+    P_{\ab}(t) = \sum_{k,j} \abs{U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)t/2E}\,.
 \end{align}
@@
 \begin{align}
-    P_{\ab}(x) &= \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
-                       &= \sum_{k,j} \abs{U^\dagger_{\a k}U_{\b k}U^\dagger_{\b j}U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E})\,,
+    P_{\ab}(x) &= \sum_{k,j} \abs{U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j}} e^{-i(m_k^2-m_j^2)x/2E} \nonumber \\
+                       &= \sum_{k,j} \abs{U^*_{\a k}U_{\b k}U^*_{\b j}U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E})\,,
 \end{align}
@@
 to rely on other types of experiments to get us at least one absolute mass, from which we then can calculate the remaining.
-Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^\dagger = \delta_{\a \b}$ yields 
+Squaring the unitarity condition $\sum_k U_{\a k}U_{\b k}^* = \delta_{\a \b}$ yields 
 \begin{align}
-    \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 = \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^\dagger U_{\b k} U_{\a j} U_{\b j}^\dagger]
+    \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 = \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^* U_{\b k} U_{\a j} U_{\b j}^*]
 \end{align}
@@
 \begin{align}\label{eq:Pab} 
-    P_{\ab} &= \sum_{k,j} \abs{U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \sum_{k \neq j} \abs{U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            &= \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^\dagger U_{\b k} U_{\a j} U_{\b j}^\dagger] +\sum_{k \neq j} \abs{U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
-            %&= \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^\dagger U_{\b k} U_{\a j} U_{\b j}^\dagger] + 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+    P_{\ab} &= \sum_{k,j} \abs{U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &=  \sum_k \abs{U_{\a k}}^2\abs{U_{\b k}}^2 + \sum_{k \neq j} \abs{U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            &= \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^* U_{\b k} U_{\a j} U_{\b j}^*] +\sum_{k \neq j} \abs{U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
+            %&= \delta_{\a \b} - 2 \sum_{k>j}\Re[U_{\a k}^* U_{\b k} U_{\a j} U_{\b j}^*] + 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \exp(-i\frac{\dm_{kj}x}{2E}) \nonumber \\
             %&= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\exp(-i\frac{\dm_{kj}x}{2E})\right] \nonumber \\
             %&= \delta_{\a \b} - 2\sum_{k > j} U_{\a k}U_{\b k}U_{\b j}U_{\a j} \left[1-\cos(\frac{\dm_{kj}x}{2E})\right] \nonumber \\
-            &= \delta_{\a \b} - 4\sum_{k > j} \Re[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)} \nonumber \\
-            &\hspace{1.2cm}+ 2\sum_{k > j} \Im[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
+            &= \delta_{\a \b} - 4\sum_{k > j} \Re[U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}] \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)} \nonumber \\
+            &\hspace{1.2cm}+ 2\sum_{k > j} \Im[U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}] \sin{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
 \end{align}
@@
 A similar calculation for antineutrinos yield  
-\begin{align}\label{eq:Pab} 
+\begin{align}
     P_{\ab} 
-            &= \delta_{\a \b} - 4\sum_{k > j} \Re[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)} \nonumber \\
-            &\hspace{1.2cm}- 2\sum_{k > j} \Im[U_{\a k} ^ \dagger U_{\b k}U_{\b j}^\dagger U_{\a j}] \sin{\left(\frac{\dm_{kj}x}{4E}\right)}\,,
+            &= \delta_{\a \b} - 4\sum_{k > j} \Re[U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}] \sin^2{\left(\frac{\dm_{kj}x}{4E}\right)} \nonumber \\
+            &\hspace{1.2cm}- 2\sum_{k > j} \Im[U_{\a k} ^ * U_{\b k}U_{\b j}^* U_{\a j}] \sin{\left(\frac{\dm_{kj}x}{4E}\right)}\,.
 \end{align}
+
+This form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
+determine the amplitude of the oscillations, while the mass-squared differences together with the ratio $L/E$ determine the
+frequency. So in vacuum, the mixing angles only influence the oscillation amplitude, while the energy, trajectory, and masses of
+the neutrinos only influence the oscillation frequency.
 
@@
 The smallness of $U_{e3}$ reduces the effect of $\dm[21]$ mass-squared difference,
-allowing $\dm[31]$ to drive the oscillations. 
-The most important mixing matrix 
-elements for $P_{\a\b}$ are $U_{\a3}, U_{\a1}$ and $U_{\b3}, U_{\b1}$. %TODO: write whole 4 product here
-%instead of U,U and U,U
+allowing $\dm[31]$ to drive the oscillations. Thus, 
+The most important mixing matrix elements for $P_{\a\b}$ are the ones appearing in the term with $\dm[31]$:
+namely the product $U_{\a3}^*U_{\b3} U_{\b1}^*U_{\a1}$.
 
 \begin{figure}[!h]
-    %TODO: write pme, pmm, pmt in titles, bigger ticks
     \begin{center}
     \includegraphics[width=1\textwidth]{figures/vac_osc.pdf}
-    \caption{Probabilities of $\nm$ oscillations travelling 12 000 km in vaccum.}\label{fig:vac_osc}
+    \caption{Probabilities of $\nm$ oscillations after travelling 12 000 km in vaccum.}\label{fig:vac_osc}
     \end{center}
 \end{figure}
-This form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
-determine the amplitude of the oscillations, while the mass-squared differences together with the ratio $L/E$ determine the
-frequency. So in vacuum, the mixing angles only influence the oscillation amplitude, while the energy, trajectory, and masses of
-the neutrinos only influence the oscillation frequency.
 

### 2021-11-24 thesis/tex/ICintro.tex
update
added muon decays

@@
 % Specify which are occurring in tracks and cascades.
-We always observe neutrinos indirectly through their associated charged lepton. 
+We always observe neutrinos indirectly.
 Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
-via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
+via the $Z$), a fermion (which is not another neutrino) exits with altered properties. This fermion is then directly or indirectly detected, 
+and the properties of the neutrino involved in the 
 interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.
 
-In this work, we only study the detectors handled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
-the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
-To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
-into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
+In this work, we only study the detectors buried within the Antarctic ice by the IceCube collaboration. 
+They are of Cherenkov type, which means that they detect 
+a charged lepton by its emitted Cherenkov light, produced from its travel through the ice. 
+In the case of CC interactions, this charged lepton is directly involved in the interaction with the neutrino, either as 
+both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic CC interaction.
+In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
+from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.
 
-The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than others.
-8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}.
-This detector is referred to DeepCore.
-DeepCore will be treated as a separate and independent detector from the rest, which
-retains the name IceCube.
-A view of the current setup can be seen in Fig.~\ref{fig:array}.
-In this work, we consider DeepCore data between \SIrange{5.6}{56}{\GeV} and IceCube data in the range \SIrange{0.5}{10}{\TeV}.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/icecube2.png}
-    \caption{View of the full IceCube array, with the Eiffel tower for scale.}\label{fig:array}
-\end{figure}
+If the secondary particles interact heavily with the ice, they will only travel a short distance before decaying 
+into the shower which emit a localized flash of Cherenkov light. This event is referred to as a cascade.
+NC interactions tend to be classified as cascades due to the production of a localized hadronic shower
+However, CC $\ne$ interactions can also produce a similar localized flash of Cherenkov light, causing them to also contribute 
+to the cascade events. A cascade event 
+is shown in Fig.~\ref{fig:events_cascade}.
 
-If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
-Cherenkov light. This event is referred to as a cascade. The neutral current interactions involve quarks, which recoils and produces
-showers of hadrons. Also, charged current $\ne$ interactions also produce cascades. A cascade event 
-is shown in Fig.~\ref{fig:events_cascade}.
-% S wanted to remove below. Why?
 If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
@@
 is shown in Fig.~\ref{fig:events_track}.
-%TODO: numbers on how often^. Write about which particles appear where
+
+So NC interactions and CC $\ne$ interactions are usually classified as cascades, while CC $\nm$ interactions are usually tagged 
+as a track. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
+of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
+information in Table~\ref{table:events}, containting classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.
+
+\begin{table}[h]
+    \begin{center}
+        \begin{tabular}{lcccccc}
+            \hline \hline
+            Interaction &Track &Cascade\\
+            \hline
+            CC $\ne$ & 30\%& 70\% \\
+            CC $\nm$ & 70\%&30\% \\
+            CC $\nt$ & 29\%& 71\%\\
+            NC $\nu$ & 24\%& 76\%\\
+            \hline \hline
+        \end{tabular}
+    \end{center}
+    \caption{The neutrino event classification at \SI{56}{\GeV} from `Sample B' in~\cite{DC2019tauappearance}}\label{table:events}
+\end{table}
 
@@
 
+To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
+into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
+
+The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than others.
+8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}.
+This detector is referred to DeepCore.
+DeepCore will be treated as a separate and independent detector from the rest, which
+retains the name IceCube.
+A view of the current setup can be seen in Fig.~\ref{fig:array}.
+In this work, we consider DeepCore data between \SIrange{5.6}{56}{\GeV} and IceCube data in the range \SIrange{0.5}{10}{\TeV}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/icecube2.png}
+    \caption{View of the full IceCube array, with the Eiffel tower for scale.}\label{fig:array}
+\end{figure}
+
 In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The `Precision IceCube Next Generation Upgrade' is an upgrade that will 
@@
 These interactions ultimately produces pions, which decay as 
-\begin{align}\label{eq:pion} %Incorrect. Add muon decays
+\begin{align}\label{eq:pion}
     &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
@@
 \end{align}
-In the muonic decay channel, muons are emitted which will be detected by the IceCube detector.
+The heavy muon ($m_\mu \approx 200m_e$) decays further:
+\begin{align}
+    &\mu^+ \to e^+ + \ne + \anm\,, \quad \mu^- \to e^- + \ane + \nm\,,
+\end{align}
+producing even more neutrinos.
 
@@
     \centering
-    %TODO: rework
     \includegraphics[width=0.9\textwidth]{figures/flux.pdf}

### 2021-11-24 thesis/tex/ICtheory.tex
update

@@
 We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
-correction factors of Eq.~\ref{eq:MC_norm}. We now arrive to our final event count
-\begin{align}\label{eq:Nth}
-    N_{ij} &= \frac{N_{ij}^\text{null}}{N_{ij}^\text{MC}} T \sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
-    \int_{E^t_{min}}^{E^t_{max}} R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta\, \dd E^t
-    \,,
-\end{align}
-with $E^t_{min}$, $E^t_{max}$, and $R(E^r,E^t)$ taken from the Gaussian process regressor.
+correction factors of Eq.~\ref{eq:MC_norm}.
 \begin{figure}[ht]

### 2021-11-24 thesis/tex/ICintro.tex
update

@@
 \section{Neutrino detection}
-%TODO: Write down detection process. This section should be written carefully. 
-% Specify the guys going into NC and CC. 
-% First line only true for CC
-% In next lines ,detail the detection process (interaction with detector matter osv). 
-% Specify which are occurring in tracks and cascades.
+\begin{figure}\label{fig:events}
+    \begin{center}
+        \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
+            \caption{Event classified as cascade}  
+            \label{fig:events_cascade}
+          \end{subfigure}
+        \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
+            \caption{Event classified as track} 
+            \label{fig:events_track}
+        \end{subfigure}
+        \caption{The two event types distinguished in the IceCube detector.}
+    \end{center}
+\end{figure}
 We always observe neutrinos indirectly.
 Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
-via the $Z$), a fermion (which is not another neutrino) exits with altered properties. This fermion is then directly or indirectly detected, 
+via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
+gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
+This fermion is then directly or indirectly detected, 
 and the properties of the neutrino involved in the 
@@
 They are of Cherenkov type, which means that they detect 
-a charged lepton by its emitted Cherenkov light, produced from its travel through the ice. 
-In the case of CC interactions, this charged lepton is directly involved in the interaction with the neutrino, either as 
-both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic CC interaction.
+a fermion by its emitted Cherenkov light, produced from its travel through the ice. 
+In the case of CC interactions, this fermion is directly involved in the interaction with the neutrino, either as 
+both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic interaction.
 In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
@@
 \end{table}
-
-\begin{figure}\label{fig:events}
-    \begin{center}
-        \begin{subfigure}{0.4\textwidth}
-            \centering
-            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
-            \caption{Event classified as cascade}  
-            \label{fig:events_cascade}
-          \end{subfigure}
-        \begin{subfigure}{0.4\textwidth}
-            \centering
-            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
-            \caption{Event classified as track} 
-            \label{fig:events_track}
-        \end{subfigure}
-        \caption{The two event types distinguished in the IceCube detector.}
-    \end{center}
-\end{figure}
 

### 2021-12-10 thesis/tex/ICintro.tex
update

--- 2021-11-16 thesis/tex/ICintro.tex
@@
 \section{Neutrino detection}
-%TODO: Write down detection process. This section should be written carefully. 
-% Specify the guys going into NC and CC. 
-% First line only true for CC
-% In next lines ,detail the detection process (interaction with detector matter osv). 
-% Specify which are occurring in tracks and cascades.
 We always observe neutrinos indirectly through their associated charged lepton. 
@@
 interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}. 
-
+% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
 In this work, we only study the detectors handled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
@@
 These interactions ultimately produces pions, which decay as 
-\begin{align}\label{eq:pion} %Incorrect. Add muon decays
+\begin{align}\label{eq:pion} %TODO: Incorrect. Add muon decays
     &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
@@
 Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
-The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. This is due to the 
-very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
-large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
-small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
-equal. First, the difference in the density profiles introduces wildly different matter effects. 
-Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
-overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
+The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. 
+% This is due to the 
+% very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
+% large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
+% small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
+% equal. 
+% First, the difference in the density profiles introduces wildly different matter effects. 
+% Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
+% overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
 The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
@@
 
-\subsection{True and Recontstructed Parameters}
+\subsection{True and Reconstructed Parameters}
 After an event has occurred, the IceCube collaboration \emph{reconstruct} the event. 
@@
 They will be outlined in Sec.~\ref{ch:ICmethod} and Sec.~\ref{ch:DCmethod}.
-
-% \bibliographystyle{nature}
-% \bibliography{ref.bib}
-% \end{document}

### 2021-12-10 thesis/tex/conclusion.tex
update

\chapter{Conclusion}\label{ch:conc}
TBD
% TODO Conclusion:
% We produced the conclusion plots, and ic is insensitive to any impact if th34.
% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
% Include effect on system uncertainty on PINGU. Compare with other measurements. Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.

### 2021-12-10 thesis/tex/nsiResults.tex
update

@@
 \section{Constraining the NSI parameters}\label{sec:constraining}
+%TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
 In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
@@
 since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
-
+% TODO: Write a few lines about the plots 5.4 and 5.5
 \begin{figure}
@@
 
-%TODO: compare results
+%TODO: compare results, fix tables
 
@@
    \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
-\end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better
-
+\end{figure}
+%TODO 5.6 is small, fix labels
+%TODO:  Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
 There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI.

### 2021-12-10 thesis/tex/nsiTheory.tex
update

@@
 \begin{align}\label{eq:coherentbounds}
-    -0.090 < &\ett < 0.38 \nonumber \\
-    -0.01 < &\emt < 0.009 \nonumber \\
-    -0.073 < &\eem < 0.044 \nonumber \\
-    -0.15 < &\eet < 0.13\,.
+    -0.090 < &\,\ett < 0.38 \nonumber \\
+    -0.01 < &\,\emt < 0.009 \nonumber \\
+    -0.073 < &\,\eem < 0.044 \nonumber \\
+    -0.15 < &\,\eet < 0.13\,.
 \end{align}
-
-% we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
-% probabilities. So jusb t as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
-% Our NSI potential matrix now takes the form 
-% {µmmb m  m mb  mb  mbb  mb bmMoreover, it is common to subtract $\emm$ from the diagonal, which
-% \begin{align} m mmb
-%     \begin{pmatrix}
-%         \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
-%         \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
-%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
-%     \end{pmatrix} 
-%     - \epsilon_{\mu\mu}
-%     \begin{pmatrix}
-%         1 & 0 & 0 \\
-%         0 & 1 & 0 \\
-%         0 & 0 & 1 
-%     \end{pmatrix}
-%      &= \begin{pmatrix}
-%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
-%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
-%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
-%     \end{pmatrix} \nonumber \\
-%     &= \begin{pmatrix}
-%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
-%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
-%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
-%     \end{pmatrix}\,,
-% \end{align}
-% where $\ep = \ett - \emm$.
 
@@
 by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
-we are restricted to weak interactions that conserve lepton number. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
+we are restricted to weak interactions that conserve lepton flavor. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
 the off-diagonal elements constitute new sources of flavor violation.
 Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
-of the mixing matrix. Thus, we can in theory boost a flavor transition that is suppressed by the mixing matrix. Moreover, since we have 6 NSI parameters, and the PMNS
+of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
+possibility of additional interactions that can cause the flavor change. Moreover, since we have 6 NSI parameters, and the PMNS
 matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
@@
     \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
-        \includegraphics[width=0.9\textwidth]{figures/emt_probs.pdf}
-        \includegraphics[width=0.9\textwidth]{figures/ett_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
         \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for

### 2021-12-10 thesis/tex/oscillations.tex
update

@@
 \end{align}
-Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$. 
-Thus, neutrino interactions still conserve lepton number.
-However, the Higgs-lepton Yukawa Lagrangian 
-in Eq.~\ref{eq:L_H} violates lepton number conservation since it couples the charged lepton flavor $\alpha$ to the neutrino mass eigenstate $k$, which is a superposition of flavors. 
-There is no transformation that leaves both the interaction and kinetic Lagrangian invariant, thus violating this symmetry.
 
@@
 \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}
-\begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda{2}} & 0 \\ 0 & 0 & e^{i \lambda{3}}\end{pmatrix}
+\begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda_{2}} & 0 \\ 0 & 0 & e^{i \lambda_{3}}\end{pmatrix}
 \nonumber \\
@@
     \end{pmatrix}
-    \begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda{2}} & 0 \\ 0 & 0 & e^{i \lambda{3}}\end{pmatrix}\,,
+    \begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda_{2}} & 0 \\ 0 & 0 & e^{i \lambda_{3}}\end{pmatrix}\,,
 \end{align}
-where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \lambda{i},\delta_\mathrm{CP} \leq 2\pi$.
+where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \lambda_{i},\delta_\mathrm{CP} \leq 2\pi$.
 
@@
 However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
-Thus, we include two Majorana phases $\lambda{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
+Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
 Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number.
@@
 \end{align}
-The rotation matrices $R_{ij}$ that constitute $U$ according to Eq.~\eqref{PMNS_def} can be simplified.
+% The rotation matrices $R_{ij}$ that constitute $U$ according to Eq.~\eqref{PMNS_def} can be simplified.
 The rotation $R_{13}$ will not affect our mass matrix, since the former acts in the $1-3$ plane, and the latter sits in the $1-2$ plane.
@@
 Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathbb{M}_{12}$.
-Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
-\begin{align}
-    \commutator{R_{ij}}{R_{kl}} = R_{ij}R_{kl} - R_{kl}R_{ij} = 0\,.
-\end{align}
-Thus,
-\begin{align}
-    U \mathbb{M}_{12} U^\dagger &=
-    R_{23}R_{13}R_{12} \mathbb{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
-    &= R_{12}R_{23}R_{13} \mathbb{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
-    &= R_{12}\mathbb{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
-\end{align}
-And due to the fact that the rotation matrices are unitary,
-\begin{align}
-    R\,R^\dagger = \mathbb{I}\,,
-\end{align}
-we have that 
-\begin{align}
-    U \mathbb{M}_{12} U^\dagger &= R_{12}\mathbb{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
-    &= R_{12}\mathbb{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
-    &= R_{12}\mathbb{M}_{12}  R_{12}^\dagger\,.
-\end{align}
-We have now completely removed the dependence of the mixing angle between the $\nu_1$ and $\nu_3$ mass eigenstates, $\theta_{13}$, and the dependece of the mixing angle between the $\nu_2$ and $\nu_3$ mass eigenstates, $\theta_{23}$.
-We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
-\begin{align}
-    U &= R_{12}
-\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix} 
-\end{align}
+% Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
+% \begin{align}
+%     \commutator{R_{ij}}{R_{kl}} = R_{ij}R_{kl} - R_{kl}R_{ij} = 0\,.
+% \end{align}
+% Thus,
+% \begin{align}
+%     U \mathbb{M}_{12} U^\dagger &=
+%     R_{23}R_{13}R_{12} \mathbb{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
+%     &= R_{12}R_{23}R_{13} \mathbb{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
+%     &= R_{12}\mathbb{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
+% \end{align}
+% And due to the fact that the rotation matrices are unitary,
+% \begin{align}
+%     R\,R^\dagger = \mathbb{I}\,,
+% \end{align}
+% we have that 
+% \begin{align}
+%     U \mathbb{M}_{12} U^\dagger &= R_{12}\mathbb{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
+%     &= R_{12}\mathbb{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
+%     &= R_{12}\mathbb{M}_{12}  R_{12}^\dagger\,.
+% \end{align}
+% We have now completely removed the dependence of the mixing angle between the $\nu_1$ and $\nu_3$ mass eigenstates, $\theta_{13}$, and the dependece of the mixing angle between the $\nu_2$ and $\nu_3$ mass eigenstates, $\theta_{23}$.
+% We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
+% \begin{align}
+%     U &= R_{12}
+% \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix} 
+% \end{align}
 
-Let us return to the Hamiltonian with our two-neutrino mixing matrix. We have 
-\begin{align}
-    H_F
-        &= \frac{1}{2E}\left[R_{12} \begin{pmatrix}
-            0 & 0 & 0 \\
-            0 & \dm_{21} & 0 \\
-            0 & 0 & 0
-        \end{pmatrix} R_{12}^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
-            1 & 0 & 0 \\
-            0 & 0 & 0 \\
-            0 & 0 & 0
-        \end{pmatrix} \nonumber \\
-        &= \frac{1}{2E}\left[\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}  \begin{pmatrix}
-            0 & 0 & 0 \\
-            0 & \dm_{21} & 0 \\
-            0 & 0 & 0
-        \end{pmatrix} \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e \begin{pmatrix}
-            1 & 0 & 0 \\
-            0 & 0 & 0 \\
-            0 & 0 & 0
-        \end{pmatrix}\,. 
-\end{align}
-
+% Let us return to the Hamiltonian with our two-neutrino mixing matrix. We have 
+% \begin{align}
+%     H_F
+%         &= \frac{1}{2E}\left[R_{12} \begin{pmatrix}
+%             0 & 0 & 0 \\
+%             0 & \dm_{21} & 0 \\
+%             0 & 0 & 0
+%         \end{pmatrix} R_{12}^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
+%             1 & 0 & 0 \\
+%             0 & 0 & 0 \\
+%             0 & 0 & 0
+%         \end{pmatrix} \nonumber \\
+%         &= \frac{1}{2E}\left[\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}  \begin{pmatrix}
+%             0 & 0 & 0 \\
+%             0 & \dm_{21} & 0 \\
+%             0 & 0 & 0
+%         \end{pmatrix} \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e \begin{pmatrix}
+%             1 & 0 & 0 \\
+%             0 & 0 & 0 \\
+%             0 & 0 & 0
+%         \end{pmatrix}\,. 
+% \end{align}
+% TODO: segue into 2gen
 We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form, and start simplifying:
@@
 We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
-symmetric piecewise polynomials for the Earth density in \si{\gram\cm^3} shown in the left panel of Fig.~\ref{fig:potential}.
+symmetric piecewise polynomials for the Earth density in \si{\gram\cm^-3} shown in the left panel of Fig.~\ref{fig:potential}.
 We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
@@
 \begin{figure}
+    %TODO: labels
     \centering
@@
 \begin{figure}
+    %TODO: labels, caption. Include osc params used. Mention value of L if missing.
+    % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
     \centering

### 2021-12-10 thesis/tex/sterileResults.tex
update

@@
 \section{The Sterile Hypothesis}\label{sec:sterileResults}
+% TODO Ch 5.1 write that we didn’t include deep core because resonance doesn’t appear there (in footnote).
+Refer to figures that show that resonance in TeV.
+We bring Deepcore back in the next section.
 With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
@@
 $\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO:double check these
-The contour plot shown in Fig.~\ref{fig:s24_contour} divides the parameter space into two regions.
+The contour plot shown in Fig.~\ref{fig:error_tuning} divides the parameter space into two regions.
 To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
@@
 \begin{figure}
+    %TODO: Fig 5.3 mention what is written in the legend. 
     \centering
@@
 \end{figure}
-
+%TODO: Mention that we see from this that the simulations are consistent with 3+0 with deviations in 6%. Fix label sizes. 
+% Include figure on theta34 and say that IC can’t distinguish it.
 %\end{document}

### 2021-12-10 thesis/tex/ICintro.tex

--- 2021-11-24 thesis/tex/ICintro.tex
@@
 \end{figure}
+% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
 We always observe neutrinos indirectly.

### 2021-12-10 thesis/tex/introduction.tex
Corrected

@@
 In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating from cosmic ray interactions in the atmosphere of the Earth. 
-Furthermore, present the two present Antarctic neutrino detectors: IceCube and DeepCore.
+Furthermore, two Antarctic neutrino detectors are introduced: IceCube and DeepCore.
 We also summarize a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which we will use as a forecast in our analysis.
@@
 In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with literature. 
-In Section~\ref{sec:nsiResults}, we present new constrained bounds on the NSI parameters by combining our results for IceCube, DeepCore, and PINGU.
+In Section~\ref{sec:constraining}, we present new constrained bounds on the NSI parameters by combining our results for IceCube, DeepCore, and PINGU.

### 2021-12-11 thesis/tex/ICintro.tex
Lots of changes!!

@@
-\section{Neutrino detection}
+\section{Atmospheric Neutrino Flux}
+Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
+These interactions ultimately produces pions, which decay as 
+\begin{align}\label{eq:pion}
+    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
+    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
+\end{align}
+The heavy muon ($m_\mu \approx 200m_e$) decays further:
+\begin{align}
+    &\mu^+ \to e^+ + \ne + \anm\,, \quad \mu^- \to e^- + \ane + \nm\,,
+\end{align}
+producing even more neutrinos.
+
+The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
+The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
+The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
+from the table for clarity. 
+We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
+$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
+Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
+The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. 
+% This is due to the 
+% very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
+% large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
+% small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
+% equal. 
+% First, the difference in the density profiles introduces wildly different matter effects. 
+% Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
+% overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
+The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
+
+\begin{table}[h]
+    \begin{center}
+        \begin{tabular}{lcccccc}
+            \hline \hline
+            $E$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\cos(\theta_z)$\\
+            \hline
+            27825 &  \SI{6.06e-12}{} &  \SI{3.17e-12}{} &  \SI{1.56e-13}{} &  \SI{1.04e-13}{} &   [-0.2, -0.1] \\
+            247707 &  \SI{5.94e-16}{} &  \SI{2.92e-16}{} &  \SI{1.36e-17}{} &  \SI{8.12e-18}{} &   [-0.7, -0.6] \\
+                22 &  \SI{3.33e-02}{} &  \SI{2.78e-02}{} &  \SI{9.57e-03}{} & \SI{7.15e-03}{} &   [-0.3, -0.2] \\
+            432876 &  \SI{5.19e-17}{} &  \SI{2.32e-17}{} &  \SI{1.46e-18}{} & \SI{9.83e-19}{} &   [-1.1, -1.0] \\
+            64280 &  \SI{1.58e-13}{} &  \SI{8.10e-14}{} &  \SI{3.49e-15}{} &  \SI{2.21e-15}{} &   [-0.4, -0.3] \\
+            \hline \hline
+        \end{tabular}
+    \end{center}
+    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}\label{table:flux}
+\end{table}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
+    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
+    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
+\end{figure}
+
+We propagate the atmospheric neutrino flux $\phi_\alpha^\text{atm}(E,\theta_z)$ through the Earth.
+The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
+\begin{align}\label{eq:propFlux}
+    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
+\end{align}
+where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
+
+\section{Neutrino Detection}
 \begin{figure}\label{fig:events}
@@
 
-\subsection{Atmospheric Neutrino Flux}
-Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
-These interactions ultimately produces pions, which decay as 
-\begin{align}\label{eq:pion}
-    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
-    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
-\end{align}
-The heavy muon ($m_\mu \approx 200m_e$) decays further:
-\begin{align}
-    &\mu^+ \to e^+ + \ne + \anm\,, \quad \mu^- \to e^- + \ane + \nm\,,
-\end{align}
-producing even more neutrinos.
-
-The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
-The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
-The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
-from the table for clarity. 
-We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
-$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
-Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
-The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. 
-% This is due to the 
-% very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
-% large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
-% small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
-% equal. 
-% First, the difference in the density profiles introduces wildly different matter effects. 
-% Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
-% overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
-The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
-
-\begin{table}[h]
-    \begin{center}
-        \begin{tabular}{lcccccc}
-            \hline \hline
-            $E$ [\si{\GeV}] &$\phi_\mu$ &$\phi_{\bar{\mu}}$ &$\phi_e$ &$\phi_{\bar{e}}$ & $\cos(\theta_z)$\\
-            \hline
-            27825 &  \SI{6.06e-12}{} &  \SI{3.17e-12}{} &  \SI{1.56e-13}{} &  \SI{1.04e-13}{} &   [-0.2, -0.1] \\
-            247707 &  \SI{5.94e-16}{} &  \SI{2.92e-16}{} &  \SI{1.36e-17}{} &  \SI{8.12e-18}{} &   [-0.7, -0.6] \\
-                22 &  \SI{3.33e-02}{} &  \SI{2.78e-02}{} &  \SI{9.57e-03}{} & \SI{7.15e-03}{} &   [-0.3, -0.2] \\
-            432876 &  \SI{5.19e-17}{} &  \SI{2.32e-17}{} &  \SI{1.46e-18}{} & \SI{9.83e-19}{} &   [-1.1, -1.0] \\
-            64280 &  \SI{1.58e-13}{} &  \SI{8.10e-14}{} &  \SI{3.49e-15}{} &  \SI{2.21e-15}{} &   [-0.4, -0.3] \\
-            \hline \hline
-        \end{tabular}
-    \end{center}
-    \caption{A selection of processed atmospheric South Pole fluxes from~\cite{hondaData} by Honda et al.~\cite{hondaArticle}.}\label{table:flux}
-\end{table}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
-    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
-    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
-\end{figure}
-
-We propagate the atmospheric neutrino flux $\phi_\alpha^\text{atm}(E,\theta_z)$ through the Earth.
-The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
-\begin{align}\label{eq:propFlux}
-    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
-\end{align}
-where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
-
 \subsection{True and Reconstructed Parameters}

### 2021-12-11 thesis/tex/ICtheory.tex
Lots of changes!!

@@
 Energy-wise, the situation here is completely reverse from the flux.
-Increasing with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
+Increasing linearily with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
 
@@
 %TODO add plot with Etrue vs prob dens
+
+Note that since atmospheric neutrino flux scales as $E^{-2.7}$, the log-normal Gaussian $R(E^r, E^t)$ as $E^{-2}$,
+and the effective area is approximately linear in $E$.
+Thus, the event count in~\ref{eq:ICevents} will be proportional to $E^{-1.7}$. Having almost a quadratic dropoff, the event count as 
+observed by IceCube will be lower and lower as we probe higher energies, severely limiting our confidence in \si{\TeV} analyses due to 
+lower statistical significance.
 
@@
 Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.
-% \newpage
-% \bibliographystyle{nature}
-% \bibliography{ref.bib}
-% \end{document}

### 2021-12-11 thesis/tex/nsiResults.tex
Lots of changes!!

@@
    \begin{center}
-      \begin{subfigure}{0.38\textwidth}
+      \begin{subfigure}{0.47\textwidth}
          \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
@@
       \end{subfigure}
-      \begin{subfigure}{0.4\textwidth}
+      \begin{subfigure}{0.51\textwidth}
          \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
@@
 %TODO 5.6 is small, fix labels
-%TODO:  Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
 There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI.
@@
 The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
+Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
+to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$.
 
@@
    \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
-   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out.}\label{fig:PINGU_2D}
+   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. The values of the standard oscillation parameters 
+   are taken from NuFit~\cite{nufit}.}\label{fig:PINGU_2D}
 \end{figure}

### 2021-12-11 thesis/tex/nsiTheory.tex
Lots of changes!!

@@
-% \documentclass{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \input{commands}
-% \usepackage{siunitx, graphicx}
-% \usepackage[utf8]{inputenc}
-% \usepackage{xr-hyper}
-
-% \begin{document}
 \section{Non-Standard Interactions}\label{sec:nsiTheory}
@@
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
-the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have settled down.
+the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have averaged out.
 
@@
 Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
-In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
+In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
 in the DeepCore region of rapid oscillations, where mixing is more violent. 
@@
 will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
-many oscillations have settled down.
+many oscillations have averaged out.
 

### 2021-12-11 thesis/tex/oscillations.tex
Lots of changes!!

@@
 Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
-Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number.
+Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number, and a Majorana phase would
+violate lepton number by two units.
 
@@
 of the form $s_{ij}, c_{ij}$, and three phase of the form $e^{i\delta_\mathrm{CP}}$ and $e^{i\lambda_{i}}$.
-The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane, allowing an $i$ eigenstate to mix with a $j$ eigenstate.
+The angle $\theta_{ij}$ specifies the amount of rotation in the $i-j$ plane.
 The physical interpretation of
-a mixing angle is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate. Thus we refer to $\theta_{ij}$ as the mixing angles. A non-zero mixing angle will then 
+a mixing matrix element $U_{ij}$ is then the degree to which the $\nu_i$ mass eigenstate mixes with the $\nu_j$ mass eigenstate.
+Thus we refer to $\theta_{ij}$ as the mixing angles.
+A non-zero mixing angle will then
 cause the flavor eigenstate $\nu_\alpha$ to be a superposition of the mass eigenstates $\nu_i$ that we allowed to mix. More on this in Section~\ref{sec:prop}.
@@
 Eq.~\ref{eq:eff_theta} has a pole at %TODO: write more
-\begin{align}
+\begin{align}\label{eq:MSW}
     E^* &= \frac{\dm[21]\cos(2\theta_{12})}{2\sqrt{2}G_F N_e}\,.
@@
 We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
-symmetric piecewise polynomials for the Earth density in \si{\gram\cm^-3} shown in the left panel of Fig.~\ref{fig:potential}.
+symmetric piecewise polynomials for the Earth density in \si{\gram\cm^{-3}} shown in the left panel of Fig.~\ref{fig:potential}.
 We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
@@
 \begin{figure}
-    %TODO: labels, caption. Include osc params used. Mention value of L if missing.
+    %TODO: labels
     % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
@@
     \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
-    \caption{}\label{fig:oscillations}
+    \caption{Neutrino oscillation probabilities after traversing the diameter of the Earth. 
+    Oscillation parameters are taken from NuFit~\cite{nufit} and given in Eq.~\ref{eq:PINGUparams}.}\label{fig:oscillations}
 \end{figure}
@@
 The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer
-\end{figure}%TODO: remake with finer
-
-% \end{document}
+\end{figure}

### 2021-12-11 thesis/tex/sterileTheory.tex
update
Lots of changes!!

@@
 So if a fourth neutrino species is present in nature, it will have ramifications not only on neutrino physics itself, but on
-our understanding of the CMB aswell.
+our understanding of the CMB as well.
 
@@
 , $\theta_{24}$, $\theta_{34}$. In our analysis, we reduce the number of parameters by only considering $\dm[41]$ and $\theta_{24}$, which are 
-the most important for the $\nm$ oscillations. In fact, one can supress the $e$ channel by letting $\theta_{14} = 0$ in the \si{\GeV} to \si{\TeV} range, thus 
-using a two-flavor neutrino approximation.
+the most important for the $\nm$ oscillations.
 
@@
 we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
-which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the for $P_{\bar{\mu}\bar{\mu}}$, shown in Fig.~\ref{fig:sterile_resonance}.
+which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappearance in the for $P_{\bar{\mu}\bar{\mu}}$, shown in Fig.~\ref{fig:sterile_resonance}.
 
@@
     \centering
-    \begin{subfigure}{0.7\textwidth}
         \includegraphics[width=1\linewidth]{figures/sterile_resonance.pdf}
-        \caption{$\Pamam$ resonant disappearance}\label{fig:sterile_resonance}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
+        \caption{Comparing the standard 3+0 hypothesis to the
+        3+1 hypothesis assuming $\dm[41] = \SI{1}{\eV \squared}$ and $\theta_{24} = 0.04$.
+        The former, shown as a blue dashed line, shows no $\anm$ disappearance.
+        The latter, shown as a black solid line, predicts a resonant $\anm$ disappearance at \SI{2.6}{\TeV}.
+        The standard oscillation parameters are taken from NuFit~\cite{nufit}, and the 
+        neutrino has traversed the entire Earth diameter.}\label{fig:sterile_resonance}
+    \end{figure}
+    \begin{figure}
         \includegraphics[width=1\linewidth]{figures/resonance_shift.pdf}
-        \caption{Shifting and amplification of the resonance by altering $\dm[41]$ and $\theta_{24}$, respectively.}\label{fig:resonance_shift}
-    \end{subfigure}
+        \caption{Shifting and amplification of the resonance by altering $\dm[41]$ and $\theta_{24}$, respectively.
+        Left panel has a fixed value of $\theta_[24] = 0.04$ while varying $\dm[41]$ from 0.5 to 3 \si{\TeV^2}.
+        Right panel has a fixed value of $\dm[41] = \SI{1}{\TeV^2}$ while varying $\theta_[24]$ from 0.02 to 0.08.
+        Standard oscillation parameters are taken from NuFit~\cite{nufit}, and shown in Eq.~\ref{eq:PINGUparams}.}\label{fig:resonance_shift}
 \end{figure}
+So for a \si{\eV^2}-scale sterile neutrino and a non-zero $\theta_{24}$, we expect a \si{\TeV} $\anm$ disappearance.
+The resonance dip is affected by the value of $\dm[41]$ and $\theta_{24}$ as shown in Fig.~\ref{fig:resonance_shift}.
+We see how the value of $\dm[41]$ shifts the resonance peak, while the mixing angle amplifies it. 
+In the $3+0$ scenario, $\Pamam = 1$ in this range. Thus, if we are able to see a $\anm$ disappearance in the \si{\TeV} region,
+we are in a good position to argue for an \si{\eV^2}-scale $\dm[41]$.
 
-So for a \si{\eV}-scale sterile neutrino and a non-zero $\theta_{24}$, we expect a \si{\TeV} $\anm$ disappearance.
-The resonance dip is affected by the value of $\dm[41]$ and $\theta_{24}$ as shown in Fig.~\ref{fig:resonance_shift}.
-We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
-In the $3+0$ scenario, $\Pamam = 1$ in this range. Thus, if we are able to see a $\anm$ disappearance in the \si{\TeV} region,
-we are in a good position to argue for a \si{\eV^2} scale $\dm[41]$.
+Keeping in mind that the event count from Eq.~\ref{eq:ICevents} scales as $E^{-1.7}$,
+signals at higher energies will be more difficult to detect. Since higher values of $\dm[41]$ shifts the $\Pamam$ resonance peak to higher 
+energies, high $\dm[41]$ values will be harder to rule out because the event count is already lower, as compared to energies 
+at single-digit \si{\TeV} values. There is then a range of parameters, in which our detector will 
+be able to distinguish between the two hypotheses. Using the two-neutrino approximation\footnote{In this approximation, we only consider mixing between $\nm$ and $\ns$, essentially a `1+1' picture.}, 
+we can rewrite the expression for MSW resonance from Eq.~\ref{eq:MSW} as 
+\begin{align}
+    E^* = \frac{\dm[41] \cos{2\theta_{24}}}{2\sqrt{2} G_F N_e}\,,
+\end{align}
+which for $\dm[41] = \SI{1}{\TeV^2}$ and $\theta_{24} = 0.04$, gives us a resonance at $E^* = \SI{2.58}{\TeV}$, matching the $3+1$ simulation shown in
+Fig.~\ref{fig:sterile_resonance}. From the two-neutrino picture, 
+we see that the resonance peak in the $\anm$ channel scales linearly with $\dm[41]$, while the mixing angle dependence 
+shows up as $\cos{2\theta_{24}}$, which is between 0.987 and 0.999 for the $\theta_[24}$ values considered in Fig.~\ref{fig:resonance_shift}.
+Since our $\theta_{24}$ values considered are so low, the location of the resonance peak is essentially only dependent on the value of $\dm[41]$.
+Thus, we expect a more stringent constraint of low values of $\dm[41]$, regardless of the value of $\theta_{24}$.
 
-%\newpage\bibliographystyle{elsarticle-num}\bibliography{ref}\end{document}
+We also note that lower values of $\theta_{24}$ suppresses the 3+1 signal, making it closer to the $3+0$ hypothesis. 
+Regardless of the value of $\dm[41]$, the $3+1$ hypothesis asymptotically converges to the $3+0$ hypothesis as $\theta_{24} \to 0$.

### 2021-12-11 thesis/tex/DCtheory.tex
update

--- 2021-09-13 thesis/tex/DCtheory.tex
@@
-% \documentclass[draft=True]{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \usepackage{graphicx, slashed, siunitx}
-% \usepackage[utf8]{inputenc}
-% \usepackage{xr-hyper}
-% \input{commands}
-% \begin{document}
 \section{DeepCore}\label{ch:DCmethod}
-In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
-IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.
+In this part, we use the publicly available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
+IceCube collaboration in a $\nu_\mu$ disappearance analysis~\cite{DC2018mudisappearance}.
 
 The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
-They are applied as correction factors using the best-fit points from the DeepCore 2019 $\nu_\tau$ appearance 
+They are applied as correction factors using the best-fit points from the 2019 DeepCore $\nu_\tau$ appearance 
 analysis~\cite{DC2019tauappearance}.
@@
 
-The oscillation parameters used on our DeepCore simulations are from the
-best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
-marginalize over $\dm$ and $\theta_{23}$.
-
 \section{PINGU}
-The methodology behind the PINGU simulations are the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
+The methodology behind the PINGU simulations is the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
 However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
@@
     &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm[31] =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
-    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0^\circ\,.
 \end{align}
-% \bibliographystyle{nature}
-% \bibliography{ref.bib}
-% \end{document}

### 2021-12-11 thesis/tex/ICintro.tex
update

@@
     \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
-    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
+    zenith angle dependence, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
 \end{figure}
@@
 of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
-information in Table~\ref{table:events}, containting classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.
+information in Table~\ref{table:events}, containing classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.
 

### 2021-12-11 thesis/tex/ICtheory.tex
update

@@
 Energy-wise, the situation here is completely reverse from the flux.
-Increasing linearily with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
+Increasing linearly with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
 
@@
 
-So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publically released by the 
+So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publicly released by the 
 collaboration has all the ingredients that we need~\cite{IC2016}. In Table.~\ref{table:IC_MC} we show a selection of the data.
@@
 and the effective area is approximately linear in $E$.
-Thus, the event count in~\ref{eq:ICevents} will be proportional to $E^{-1.7}$. Having almost a quadratic dropoff, the event count as 
+Thus, the event count in~\ref{eq:ICevents} will be proportional to $E^{-1.7}$. Having almost a quadratic drop-off, the event count as 
 observed by IceCube will be lower and lower as we probe higher energies, severely limiting our confidence in \si{\TeV} analyses due to 
@@
     \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}.
-    Color indicates the frequency of each simulated point.
+    The color indicates the frequency of each simulated point.
     Shaded area shows the 99th percentile limits predicted by the regressor trained on this set. It is within this band 
@@
 with our null hypothesis times a constant factor. 
-We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0$ for simplicity. The values used are
+We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0^\circ$ for simplicity. The values used are
 \begin{align}\label{eq:nufitparams}
-    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
+    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0^\circ\,.
 \end{align}
@@
     \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
-    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
+    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in red in the plots.}\label{fig:IC_MC_norm}
     \end{centering}

### 2021-12-11 thesis/tex/nsiResults.tex
update

@@
-\section{Constraining the NSI parameters}\label{sec:constraining}
+\section{The NSI Hypothesis}\label{sec:constraining}
 %TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
@@
 $N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
-incertainty.
+uncertainty.
 
@@
 expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
-to be neglible~\cite{PINGUletter}.
+to be negligible~\cite{PINGUletter}.
 The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
@@
 
-We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ij}^\text{syst} = f\sqrt{N_{ij}^\text{data}}$.
+We treat the uncorrelated systematic uncertainties differently for each detector. For IceCube, we set $\sigma_{ij}^\text{syst} = f\sqrt{N_{ij}^\text{data}}$.
 We consider best, normal, and worst-case scenarios in IceCube using

### 2021-12-11 thesis/tex/nsiTheory.tex
update

@@
 We have no reason to believe that the Standard Model 
-gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
-oscillations force us to amend it. 
+gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and 
+oscillations forces us to amend it. 
 Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
@@
 \end{align} 
-in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
+in \si{\TeV}, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
 two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory above electroweak scale, 
@@
 matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
-two of the three mixing angles, making them much more dependent on each other.
+two of the three mixing angles, making the individual angles more inter-dependent than the NSI parameters, since combinations of them must satisfy the constraints of the matrix elements.
 
@@
 \begin{figure}
-    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
+    \begin{center}
+        %TODO: subplots and fix labels in parahgraph aboveto match them
         \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
@@
 In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$.
-At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
+At \si{\TeV} energies, both probabilities simply get shifted down, resulting in a net reduction of track events.
         \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
@@
 Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets smeared away in the reconstruction, and not showing up at all in the data.
-In general, features showing at probability level are often washed out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.
+In general, features showing at probability level are often averaged out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.
 
@@
 Comparing with the probabilities in Fig.~\ref{fig:eem_eet_probs}, we see that the surplus of the $\anm$ survival in the \SIrange{20}{30}{\GeV} and the deficit above \SI{40}{\GeV} is intact, while the \SI{10}{\GeV} $\nm$ deficit is completely washed out.
-
-% \end{document}

### 2021-12-11 thesis/tex/oscillations.tex
update

@@
     \includegraphics[width=1\textwidth]{figures/vac_osc.pdf}
-    \caption{Probabilities of $\nm$ oscillations after travelling 12 000 km in vaccum.}\label{fig:vac_osc}
+    \caption{Probabilities of $\nm$ oscillations after travelling 12 000 km in vacuum.}\label{fig:vac_osc}
     \end{center}
@@
 \end{align}
-where the projection operator $(1- \gamma^5)$ in the first line ensures that only the left-hand compontent of the neutrino fields interact.
+where the projection operator $(1- \gamma^5)$ in the first line ensures that only the left-hand component of the neutrino fields interact.
 Here we see a crucial difference that we expected: comparing the eigenvectors between the vacuum Hamiltonian defined in Eq.~\ref{eq:osc_1} and $H_{CC}$ shows us 
@@
 \begin{figure}
-    %TODO: labels
     \centering
@@
 \begin{figure}
-    %TODO: labels
     % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
     \centering
-    \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/oscillations.pdf}
     \caption{Neutrino oscillation probabilities after traversing the diameter of the Earth. 
@@
     \includegraphics[width=0.9\textwidth]{figures/oscillograms.pdf}
-    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space.
+    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space using parameters from~\cite{nufit}.
 Note the panels are symmetric about the diagonal panels, i.e.
-$P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0$.
+$P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0^\circ$.
 The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer

### 2021-12-11 thesis/tex/sterileResults.tex
update

--- 2021-09-15 thesis/tex/sterileResults.tex
@@
-% \documentclass{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \input{commands}
-
-% \begin{document}
 \section{The Sterile Hypothesis}\label{sec:sterileResults}
-With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
+With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:MC_norm}, we are now in good shape to study the sterile neutrino effect on the probabilities, and how that compares to data
+\footnote{We do not consider DeepCore nor PINGU in the sterile neutrino analysis because the $\Pamam$ resonance does not appear in the \si{\GeV} region for \si{\eV^2}-scale $\dm[41]$, as shown in Fig.~\ref{fig:sterile_resonance}.
+We bring DeepCore and PINGU back in the next section.}.
 First, let us see how the collected data from Fig.~\ref{fig:IC_data} deviates from the predicted $3\nu$ oscillations.
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/IC_rates.pdf}
-    \caption{How the null hypothesis compares to the IceCube data from~\cite{IC2020}.}\label{fig:IC_rates}
+    \includegraphics[width=1\textwidth]{figures/IC_rates.pdf}
+    \caption{How the IceCube null hypothesis from~\cite{IC2020} compares to their collected data.}\label{fig:IC_rates}
 \end{figure}
 Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
-for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$. Recalling the \si{\TeV} disappearance from 
-Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. 
-%Thus, we expect the best fitting 
-%sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
-%that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.
+for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$.
 
@@
 \end{align}
-with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}.
+with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:MC_norm}.
 Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate with angle $\beta$ around the median zenith angle of $\zreco = -0.5$.
@@
 Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
-Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the sterile hypothesis.
+Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the 3+1 hypothesis.
 The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
-$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO:double check these
-The contour plot shown in Fig.~\ref{fig:s24_contour} divides the parameter space into two regions.
+$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO: double check these
+The contour plot shown in Fig.~\ref{fig:error_tuning} divides the parameter space into two regions.
 To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
@@
 By tuning the scaling $f$ of the uncorrelated systematic error, we can shift the contour. We extract the contour from the 
-IceCube sterile analysis~\cite{IC2020}, and compare in Fig.~\ref{fig:error_tuning}. We see that the contour in the 
-higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensetive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
-remains fixed. %We put $f=35\%$ and compare our results to the Giunti et al.~\cite{gariazzoUpdatedGlobalAnalysis2017} in Fig.~\ref{fig:s24_contour}. %TODO fix
-%Here, we see that our lower fixed region between \SIrange{1e-1}{1}{\eV\squared} is closer to the IceCube result than Giunti et al, but that 
-%our contour slightly diverges above \SI{1}{\eV\squared}. 
+IceCube sterile neutrino analysis~\cite{IC2020}, and compare in Fig.~\ref{fig:error_tuning}. We see that the contour in the 
+higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensitive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
+remains fixed.
 \begin{figure}
@@
 
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.8\textwidth]{figures/s24_contour.pdf}
-%    \caption{The 90\% CL contour using $f=35\%$, compared with the official IceCube result from~\cite{IC2020}
-%    %and the result from~\cite{gariazzoUpdatedGlobalAnalysis2017}
-%    }\label{fig:s24_contour}    
-%\end{figure} %TODO fix
-
-We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit sterile hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
-sterile hypothesis compares to data.
+We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit 3+1 hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
+3+1 hypothesis compares to data.
 \begin{figure}
@@
     \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
-    \caption{The predicted binned event count assuming our best-fit sterile hypothesis, compared with the 
-    null and data.}\label{fig:final_rate_plot}
+    \caption{The predicted binned event count assuming our best-fit 3+1 hypothesis in blue, compared with the 
+    null 3+0 hypothesis in red and data points in black.}\label{fig:final_rate_plot}
 \end{figure}
 
-%\end{document}
+In Fig.~\ref{fig:final_rate_plot}, we see that the simulations are consistent with the 3+0 hypothesis with deviations of 6\% at high single-digit 
+\si{\TeV} energies.
+
+%TODO: Fix label sizes. 
+%TODO: Include figure on theta34 and say that IC can’t distinguish it.

### 2021-12-11 thesis/tex/sterileTheory.tex
update

@@
 
-\subsection{Effect of Sterile Neutrino on Probabilities}
+\subsection{The Probability Effect of a Sterile Neutrino}
 Since the new, sterile, neutrino does not interact weakly, how do we know if it's there? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
@@
 we see that the resonance peak in the $\anm$ channel scales linearly with $\dm[41]$, while the mixing angle dependence 
-shows up as $\cos{2\theta_{24}}$, which is between 0.987 and 0.999 for the $\theta_[24}$ values considered in Fig.~\ref{fig:resonance_shift}.
+shows up as $\cos{2\theta_{24}}$, which is between 0.987 and 0.999 for the $\theta_[24]$ values considered in Fig.~\ref{fig:resonance_shift}.
 Since our $\theta_{24}$ values considered are so low, the location of the resonance peak is essentially only dependent on the value of $\dm[41]$.

### 2021-12-11 thesis/tex/oscillations.tex
update

@@
 
-\subsection{Three Neutrino Picture}
+\subsection{The Three Neutrino Picture}
 Reminding ourselves that the vacuum Hamiltonian $H_0$ has eigenstates in the mass basis, we write the following expression where 
@@
 
-\subsection{Two Neutrino Picture Solution}
+\subsection{Earth Propagation}
+We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
+symmetric piecewise polynomials for the Earth density in \si{\gram\cm^{-3}} shown in the left panel of Fig.~\ref{fig:potential}.
+We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
+oscillations.
+
+Using a value of $Y=0.5$ electron per nucleon, we express the matter potential as
+\begin{align}
+    V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
+           &= \SI{3.8e-23}{\eV} \times \rho\,,
+\end{align}
+a low number due to the smallness of $G_F$. This is plotted in the right panel of Fig.~\ref{fig:potential}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/potential.pdf}
+    \caption{\emph{Left panel:} The spherically symmetric Earth density according to PREM~\cite{PREM}, as of distance from the core.
+    \emph{Right panel:} $V_{CC}$ using the PREM density and 1/2 electrons per nucleon.}\label{fig:potential}
+\end{figure}
+
+Now, solving the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_3gen} with the matter potential from the PREM,
+we obtain the nine combinations of probabilities through the Earth diameter. We note that due to our assumption of CP-invariance
+(and thus, T-invariance), the probabilities $P_{\a\b}$ and $P_{\b\a}$ are equivalent. The result for \si{\GeV} neutrinos 
+is shown in Fig.~\ref{fig:oscillations}.
+
+\begin{figure}
+    % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/oscillations.pdf}
+    \caption{Neutrino oscillation probabilities after traversing the diameter of the Earth. 
+    Oscillation parameters are taken from NuFit~\cite{nufit} and given in Eq.~\ref{eq:PINGUparams}.}\label{fig:oscillations}
+\end{figure}
+
+Now we need to incorporate the \emph{zenith angle}, here defined as the angle between the neutrino direction of travel and south.
+This way, neutrinos traveling through the entire diameter of the Earth are defined as `up-going', while
+neutrinos that directly over-head are `down-going'. We will mostly work with the quantity $\cos{(\theta_z)}$.
+Since we are interested in the matter effects, some studies are only looking at up-going neutrinos, i.e. neutrinos with
+zenith angle $-1 \le \cos{(\theta_z)} \le 0$. However, while down-going neutrinos don't experience matter oscillations (and hardly even vacuum
+oscillations due to the short baseline), they can be included to reduce systematic errors.
+We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
+allowing us to fully see the Earth matter effect on the oscillations in full. This is shown in Fig.~\ref{fig:oscillograms}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/oscillograms.pdf}
+    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space using parameters from~\cite{nufit}.
+Note the panels are symmetric about the diagonal panels, i.e.
+$P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0^\circ$.
+The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/vac_vs_matter.png}
+    \caption{$\nm$ oscillation probabilities after traversing the diameter of the Earth in black, 
+    compared to the vacuum oscillation with the same 
+    baseline in red. 
+    Oscillation parameters are taken from NuFit~\cite{nufit} and given in Eq.~\ref{eq:PINGUparams}.}\label{fig:vac_vs_matter}
+\end{figure}
+
+In Fig.~\ref{fig:vac_vs_matter}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
+traveling 12000 km. The red line is the vacuum oscillation, while the black line is the matter oscillation, traversing through the 
+matter density profile of the Earth. We see that the matter effects are more for some energies, and less for others. At energies 
+above $\SI{10}{\GeV}$, the matter effects are small for $\Pmm$ and $\Pmt$, while they heavily deviate for single-digit \si{\GeV} energies.
+$\Pme$ behaves in a different way, where the matter effects affect the oscillation probability regardless of energy. Here, we start to
+see the convergence as late as $\SI{100}{\GeV}$. Thus, matter effects are most important for energies below $\SI{100}{\GeV}$, for all channels.
+Above these energies, the density profile of the Earth is less relevant, and the Earth is more or less transparent for $\nm$.
+
+\subsection{The Two Neutrino Picture}
 By working in the limit where one of the neutrino masses can be neglected, 
@@
 
-\begin{align}
+\begin{align}\label{eq:2gen}
     P_{e\mu}^M = \sin^2(2\theta_{12}^M)\sin^2\left(\frac{\dm[21]L}{4E}\right)\,.
@@
 
-\subsection{Earth propagation}
-We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
-symmetric piecewise polynomials for the Earth density in \si{\gram\cm^{-3}} shown in the left panel of Fig.~\ref{fig:potential}.
-We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
-oscillations.
-
-Using a value of $Y=0.5$ electron per nucleon, we express the matter potential as
-\begin{align}
-    V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
-           &= \SI{3.8e-23}{\eV} \times \rho\,,
-\end{align}
-a low number due to the smallness of $G_F$. This is plotted in the right panel of Fig.~\ref{fig:potential}
 \begin{figure}
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/potential.pdf}
-    \caption{\emph{Left panel:} The spherically symmetric Earth density according to PREM~\cite{PREM}, as of distance from the core.
-    \emph{Right panel:} $V_{CC}$ using the PREM density and 1/2 electrons per nucleon.}\label{fig:potential}
+    \includegraphics[width=1\textwidth]{figures/2_vs_3.png}
+    \caption{$\nm$ oscillation probabilities after traversing the diameter of the Earth in black, 
+    compared to the two-neutrino picture oscillations with the same 
+    baseline and matter potential in blue. The figure showcases the convergence of the $2\nu$ and $3\nu$ pictures at energies above $\SI{10}{\GeV}$.
+    Oscillation parameters are taken from NuFit~\cite{nufit} and given in Eq.~\ref{eq:PINGUparams}.}\label{fig:2_vs_3}
 \end{figure}
 
-Now, solving the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_3gen} with the matter potential from the PREM,
-we obtain the nine combinations of probabilities through the Earth diameter. We note that due to our assumption of CP-invariance
-(and thus, T-invariance), the probabilities $P_{\a\b}$ and $P_{\b\a}$ are equivalent. The result for \si{\GeV} neutrinos 
-is shown in Fig.~\ref{fig:oscillations}.
+In Fig.~\ref{fig:2_vs_3}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
+traveling 12000 km. The black lines are the probabilities of $\nm$ oscillation, after it has traversing through the diameter of the Earth.
+The red lines are the probabilities of $\nm$ oscillation, but in the two-neutrino picture using Eq.~\ref{eq:2gen}. So in the left-most panel,
+we are only considering the mixing between $\ne$ and $\nm$, completely neglecting $\theta_{13}$ and $\theta_{23}$.
 
-\begin{figure}
-    % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/oscillations.pdf}
-    \caption{Neutrino oscillation probabilities after traversing the diameter of the Earth. 
-    Oscillation parameters are taken from NuFit~\cite{nufit} and given in Eq.~\ref{eq:PINGUparams}.}\label{fig:oscillations}
-\end{figure}
-
-Now we need to incorporate the \emph{zenith angle}, here defined as the angle between the neutrino direction of travel and south.
-This way, neutrinos traveling through the entire diameter of the Earth are defined as `up-going', while
-neutrinos that directly over-head are `down-going'. We will mostly work with the quantity $\cos{(\theta_z)}$.
-Since we are interested in the matter effects, some studies are only looking at up-going neutrinos, i.e. neutrinos with
-zenith angle $-1 \le \cos{(\theta_z)} \le 0$. However, while down-going neutrinos don't experience matter oscillations (and hardly even vacuum
-oscillations due to the short baseline), they can be included to reduce systematic errors.
-We now supplement our probability grid from Fig.~\ref{fig:oscillations} with the zenith dimension,
-allowing us to fully see the Earth matter effect on the oscillations in full. This is shown in Fig.~\ref{fig:oscillograms}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/oscillograms.pdf}
-    \caption{Oscillograms showing neutrino oscillations for all flavors in $E - \cos(\theta_z)$ space using parameters from~\cite{nufit}.
-Note the panels are symmetric about the diagonal panels, i.e.
-$P_{\a\b} = P_{\b\a}$ due to $\delta_{CP} = 0^\circ$.
-The core-mantle boundary from Fig.~\ref{fig:potential} is clearly displayed at $\cos{(\theta_z)} = -0.83$ as a sharp discontinuity for all flavors.}\label{fig:oscillograms}%TODO: redo finer
-\end{figure}
+The pattern is similar to when we compared $3\nu$ matter and vacuum oscillations: at $\SI{10}{\GeV}$, the two pictures converge.
+It is evident that the full $3\nu$ picture is required for single-digit \si{\GeV} energies, and that mixings between all three flavors here are 
+abundant. Increasing with energy, however, the influence of the $\nu_1$ mass eigenstate on the probabilities is reduced.
+Thus, we are able to approximate resonant behavior as described in Eq.~\ref{eq:MSW} above $\SI{100}{\GeV}$ by only considering 
+mixing between two neutrino species. We will utilize this observation later on to study a particular resonance in the \si{\TeV} range.

### 2021-12-11 src/probability/analytical.py
update

@@ -1,5 +1,5 @@
 import numpy as np
-from functions import V,dm, mass_dict,theta,param_dict,GeV2tokm1,U_3,r_earth, nufit_params_nsi
+from functions import V,dm, mass_dict,theta,param_dict,GeV2tokm1,U_3,r_earth, nufit_params_nsi, baseline
         
 def P_an(flavor_from, flavor_to, param, E=None, L=None,  param_min=None, param_max=None, material='vac',earth_start = 0, ndim = 3, anti=False, theta_i=0, npoints=500, params=param_dict):
     '''
@@ -18,7 +18,10 @@ def P_an(flavor_from, flavor_to, param, E=None, L=None,  param_min=None, param_m
     beta = mass_dict[flavor_to]
 
     if ndim == 2:
-        probs = [P_two(alpha, beta, E, L =ell, theta_i=theta_i ,param=param,earth_start=earth_start, anti=anti, material=material, params=param_dict) for ell in L]
+        if param == 'E':
+            probs = [P_two(alpha, beta, E=en, L =L, theta_i=theta_i , material=material, params=param_dict) for en in E]
+        elif param == 'L':
+            probs = [P_two(alpha, beta, E=E, L =ell, theta_i=theta_i , material=material, params=param_dict) for ell in L]
         return np.array(probs)
     else:
         if param == 'E':
@@ -48,14 +51,14 @@ def P_n(alpha,  beta, E, ndim, L=2*r_earth, params=param_dict):
     else:
         return np.sum(P_list)
 
-def P_two(alpha, beta, E, L, param, material, theta_i, earth_start=0, N_n=0, anti=False, params=param_dict):#giunti 9.77
+def P_two(alpha, beta, E, L, material, theta_i, params=param_dict):#giunti 9.77
     flavor_from=mass_dict[alpha]
     flavor_to=mass_dict[beta]
+    r = baseline(theta_i)
+    A = 2*E*V(r, material)[0]
 
-    A = V(E,L,material,theta_i)
-
-    th_M = theta(alpha+1,beta+1, A=A, params=params)
-    dm_M = dm(alpha+1, beta+1, A= A, params=params)
+    th_M = theta(alpha+1,beta+1, params=params)
+    dm_M = dm(alpha+1, beta+1, params=params)
 
     return np.sin(2*th_M)**2 * np.sin(GeV2tokm1*dm_M*L/(4*E))**2
 

### 2021-12-12 thesis/tex/conclusion.tex
updated, and added worse s24 fig

@@
 \chapter{Conclusion}\label{ch:conc}
-TBD
+We were able to simulate the IceCube experiment with 86 strings, with our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig~\ref{fig:IC_MC_norm}. 
+We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_[24]$ in Fig~\ref{fig:error_tuning}.
+We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
+We also investigated the case when $\theta_{24} = \theta{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. This 
+observation makes us conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
+when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to observe 
+an impact of $\theta_{34}$.
+
 % TODO Conclusion:

### 2021-12-12 thesis/tex/nsiResults.tex
updated, and added worse s24 fig

@@
     $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
+    parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
    \end{center}
@@
          \hline & \multicolumn{2}{c}{IceCube}  \\
-         $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017]  \\\\
+         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017]  \\\\
          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
          $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
-         $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] \\
+         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017] \\
          $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] \\
@@
          &\multicolumn{2}{c}{IceCube + DeepCore} \\
-         $\emt$ &  [-0.029, 0.007] &          [0.026] \\
+         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
          \hline
@@
          \hline & \multicolumn{2}{c}{IceCube}  \\
-         $\emt$ &  [-0.009, 0.01] &  [-0.015, 0.018]  \\\\
+         $\emt$ &  [-0.0090, 0.010] &  [-0.015, 0.018]  \\\\
          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
-         $\ett$ &    [-0.046, 0.054] &         [-0.065]  \\
-         $\emt$ &     [-0.009, 0.01] &  [-0.015, 0.018]  \\
+         $\ett$ &    [-0.046, 0.054] &  [-0.065, 0.073]  \\
+         $\emt$ &     [-0.0090, 0.010] &  [-0.015, 0.018]  \\
          $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16]    \\
@@
          &\multicolumn{2}{c}{IceCube + DeepCore}\\
-         $\emt$ &   [-0.029, 0.007] &          [0.026] \\
+         $\emt$ &   [-0.029, 0.0070] & [-0.041, 0.026] \\
          \hline
@@
          \hline & \multicolumn{2}{c}{IceCube}  \\
-         $\emt$ &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
+         $\emt$ &   [-0.010, 0.011] &   [-0.017, 0.020] \\\\
          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
-         $\ett$ &    [-0.049, 0.057] &          [-0.07] \\
-         $\emt$ &     [-0.01, 0.011] &   [-0.017, 0.02] \\
+         $\ett$ &    [-0.049, 0.057] &  [-0.070, 0.078] \\
+         $\emt$ &     [-0.010, 0.011] &   [-0.017, 0.020] \\
          $\eem$ &   [-0.14, 0.11] &   [-0.23, 0.18] \\
@@
          &\multicolumn{2}{c}{IceCube + DeepCore}\\
-         $\emt$ &   [-0.029, 0.007] &          [0.026] \\
+         $\emt$ &   [-0.029, 0.007] & [-0.041, 0.026] \\
          \hline
@@
       \hline & \multicolumn{2}{c}{PINGU} \\
-      $\ett$ &  [-0.054, 0.067] &               [] \\
-      $\emt$ &  [-0.029, 0.007] &          [0.026] \\
+      $\ett$ &  [-0.054, 0.067] & [-0.089, 0.10] \\
+      $\emt$ &  [-0.029, 0.0070] & [-0.041, 0.026] \\
       $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
@@
       $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
-      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] \\
-      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] \\
-      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] \\\\
+      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013] \\
+      $\eem$ &   [-0.060, 0.077] &  [-0.13, 0.13] \\
+      $\eet$ &  [-0.052, 0.095] &  [-0.11, 0.14] \\\\
       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013]  \\
+      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013]  \\
       \hline
@@
       \hline & \multicolumn{2}{c}{PINGU} \\
-      $\ett$ &   [-0.054, 0.067] &               []\\
-      $\emt$  &  [-0.029, 0.007] &          [0.026]  \\
+      $\ett$ &   [-0.054, 0.067] & [-0.089, 0.10]\\
+      $\emt$  &  [-0.029, 0.0070] & [-0.041, 0.026] \\
       $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
@@
       $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
-      $\emt$ &    [-0.01, 0.006] &  [-0.016, 0.014] \\
-      $\eem$ &    [-0.071, 0.086] &  [-0.149, 0.141]  \\
-      $\eet$ &   [-0.061, 0.103] &  [-0.131, 0.155] \\\\
+      $\emt$ &    [-0.010, 0.0060] &  [-0.016, 0.014] \\
+      $\eem$ &    [-0.071, 0.086] &  [-0.15, 0.14]  \\
+      $\eet$ &   [-0.061, 0.10] &  [-0.13, 0.16] \\\\
       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &   [-0.01, 0.006] &  [-0.016, 0.014] \\
+      $\emt$ &   [-0.010, 0.006] &  [-0.016, 0.014] \\
       \hline
@@
       \hline & \multicolumn{2}{c}{PINGU} \\
-      $\ett$ &    [-0.054, 0.067] &               [] \\
-      $\emt$ &    [-0.029, 0.007] &          [0.026] \\
+      $\ett$ &    [-0.054, 0.067] & [-0.089, 0.10] \\
+      $\emt$ &    [-0.029, 0.007] & [-0.041, 0.026] \\
       $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
@@
       & \multicolumn{2}{c}{DeepCore + PINGU} \\
-      $\ett$ &     [-0.039, 0.05] &          [-0.06] \\
-      $\emt$ &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+      $\ett$ &     [-0.039, 0.050] & [-0.06, 0.07] \\
+      $\emt$ &  [-0.011, 0.0070] &  [-0.017, 0.015] \\
       $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
@@
       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &   [-0.011, 0.007] &  [-0.017, 0.015] \\
+      $\emt$ &   [-0.011, 0.0070] &  [-0.017, 0.015] \\
       \hline
@@
 
-%TODO: compare results, fix tables
+%TODO: compare results
 
@@
            \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
-           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+           \cline { 2 - 4 } Parameter & $\dm[31]$ & $\theta_{23}$  & $\epsilon$  \\
            \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
@@
    \begin{center}
-      \begin{subfigure}{0.47\textwidth}
+      \begin{subfigure}{0.44\textwidth}
          \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
@@
       \end{subfigure}
-      \begin{subfigure}{0.51\textwidth}
+      \begin{subfigure}{0.54\textwidth}
          \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
@@
     \end{center}
-   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
+   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years of data. 
+   Each row has only one NSI non-zero parameter, with the first row having $\ett= -0.07$, second $\emt = -0.03$, third $\eem = -0.3$, and fourth $\eet = -0.3$.
+   We clearly see the increased statistics of the PINGU detector, especially in cascade events. The low values of $\ett$ and $\emt$ produce a weak pull in DeepCore,
+   while PINGU can be expected to observe multiple regions of strong pulls for $\emt$, $\eem$, and $\eet$.}\label{fig:event_pulls}
 \end{figure}
+
+We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
+assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
+number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
+
+Now we will compare the probability plots with the final event counts in DeepCore. It is not enough to only study the effect at probability level, since that is in true quantities. 
+Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets averaged out in the reconstruction, and not showing up at all in the data. 
+In general, features showing at probability level are can be 
+averaged out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.
+
+The top right panel shows a surplus of DeepCore track events at \SIrange{20}{30}{\GeV} for through-going neutrinos when we turn on $\ett$.
+This is what we expected from the bottom right panel in Fig.~\ref{fig:emt_ett_probs}, where we saw that we had an increase in $\anm$ survival probability at \SIrange{20}{40}{\GeV}.
+
+The third right panel shows the expected event pull for $\eem$.
+Comparing with the probabilities in Fig.~\ref{fig:eem_eet_probs}, we see that the surplus of the $\anm$ survival in the \SIrange{20}{30}{\GeV} and the deficit above \SI{40}{\GeV} is intact, while the \SI{10}{\GeV} $\nm$ deficit is completely averaged out.
+
 %TODO 5.6 is small, fix labels
 There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI.
-For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation.
-The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
+For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the
+interaction Lagrangian respects lepton flavor conservation. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
 but this is not feasible.
@@
 Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
-to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$.
+to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$. This is consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}, from which we 
+saw that $\eem$ and $\eet$ strongly affect $\Pme$ for single-digit \si{\GeV} energies.
 
@@
    \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
-   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. The values of the standard oscillation parameters 
+   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. We observe an anti-correlation between $\eem$ and $\eet$,
+   consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}.
+   The values of the standard oscillation parameters 
    are taken from NuFit~\cite{nufit}.}\label{fig:PINGU_2D}

### 2021-12-12 thesis/tex/nsiTheory.tex
updated, and added worse s24 fig

@@
     \begin{center}
-        %TODO: subplots and fix labels in parahgraph aboveto match them
-        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
-        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/Pmm_emt_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/Pmm_ett_probs.pdf}
         \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
@@
     \begin{center}
-        \includegraphics[width=0.9\textwidth]{figures/eem_probs.pdf}
-        \includegraphics[width=0.9\textwidth]{figures/eet_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/eem_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/eet_probs.pdf}
         \caption{Muon neutrino and antineutrino survival probabilities for
@@
 For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
-see the $\eet$ effect in DeepCore/PINGU, but remember that we now have the option to look at the other flavor channels.
+see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
+have cascade events for DeepCore and PINGU. If we simulate 
+$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
+Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
+The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
+indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
+we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
+in the $\Pme$ probability. This indicating that the NSI parameters are much more influential at these energies, and that we should be able to 
+constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\textwidth]{figures/eem_eet_prob.pdf}
+    \caption{The quantity $\abs{P_{\mu e}^{NSI} - P_{\mu e}^{SI}}$ when we let $\eem$ and $\eet$ independently vary over
+    the range \{-0.3,0.3\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
+    a promising indication that constriction of $\eem$ and $\eet$ is possible using cascade events at these energies.}\label{fig:eem_eet_prob}
+\end{figure}
 
@@
 a clear difference when turning on $\eet$.
-
-We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
-assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
-number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
 
@@
 \end{figure}
-
-\begin{figure}
-    \begin{center}
-        \includegraphics[width=0.8\textwidth]{figures/DC_event_pulls.pdf}
-        \caption{Plots of the quantity $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$, displaying which 
-        reconstructed bins the NSI signal is most clear.}
-        \label{fig:event_pulls}
-    \end{center}
-\end{figure}
-
-Now we will compare the probability plots with the final event counts in DeepCore.
-It is not enough to only study the effect at probability level, since that is in true quantities.
-Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets smeared away in the reconstruction, and not showing up at all in the data.
-In general, features showing at probability level are often averaged out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.
-
-The top right panel shows a surplus of DeepCore track events at \SIrange{20}{30}{\GeV} for through-going neutrinos when we turn on $\ett$.
-This is what we expected from the bottom right panel in Fig.~\ref{fig:emt_ett_probs}, where we saw that we had an increase in $\anm$ survival probability at \SIrange{20}{40}{\GeV}.
-
-The third right panel shows the expected event pull for $\eem$.
-Comparing with the probabilities in Fig.~\ref{fig:eem_eet_probs}, we see that the surplus of the $\anm$ survival in the \SIrange{20}{30}{\GeV} and the deficit above \SI{40}{\GeV} is intact, while the \SI{10}{\GeV} $\nm$ deficit is completely washed out.

### 2021-12-12 thesis/tex/sterileResults.tex
updated, and added worse s24 fig

@@
 higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensitive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
-remains fixed.
+remains fixed. In both cases, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$
 \begin{figure}
@@
 \si{\TeV} energies.
-
-%TODO: Fix label sizes. 
-%TODO: Include figure on theta34 and say that IC can’t distinguish it.
+Wanting to investigate the effect of $\theta_[34]$, we also simulated the 3+1 hypothesis using $\theta_[24] = \theta_[34]$. However, we did not see 
+a difference in the exclusion regions compared to the regions when $\theta_[34] = 0$. Thus, we conclude that on our work, IceCube was not able to 
+distinguish any effect due to the $\theta_[34]$ parameter.

### 2021-12-12 thesis/tex/conclusion.tex
update

@@
 We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
+Our best-fit parameters were found to be$\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
+a p-value of $33\%$.
 We also investigated the case when $\theta_{24} = \theta{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. This 
@@
 
+In our second part of the work, we put the sterile neutrino completely aside, and turned our focus to non-standard interactions. 
+We included DeepCore in order to both lower the energy range of the data, but also to include cascade events in this range. 
+Additionally, we simulated a proposed upgrade to DeepCore, PINGU, and produced data for it assuming a standard $3+0$ hypothesis with parameters from\cite{nufit}.
+We saw that, on a probability level, in the high energy region of IceCube, NSI effects other than those stemming from $\emt$ are not apparent.
+Moreover, we saw in the $\Pme$ shown in Fig~\ref{fig:eem_eet_prob} that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
+We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions, making us hope to constrain $\emt$ further by 
+a joint analysis.
+In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore, with $\emt$ effects being the weakest 
+due to their low effect on all probability channels in the \si{\GeV} range.
+
 % TODO Conclusion:
-% We produced the conclusion plots, and ic is insensitive to any impact if th34.
 % NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?

### 2021-12-12 thesis/tex/nsiTheory.tex
update

@@
 
+Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
+a clear signal when turning on $\eet$.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
+        \caption{Electron neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\eet = 0.2$.
+All other NSI parameters are fixed to zero.
+Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{eem_eet_probs}.}
+        \label{fig:Pee_eet_probs}
+    \end{center}
+\end{figure}
+
 Fig.~\ref{fig:emt_ett_probs} shows that $\emt$ affects both $\Pmm$ and $\Pamam$ over the whole energy range. Since 
@@
 \end{figure}
-
-Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
-a clear difference when turning on $\eet$.
-
-\begin{figure}
-    \begin{center}
-        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
-        \caption{Electron neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. Compared to the $\nm$ and $\anm$ plots, here we see a strong difference across the whole energy range.}
-        \label{fig:Pee_eet_probs}
-    \end{center}
-\end{figure}

### 2021-12-12 thesis/tex/sterileResults.tex
update

@@
 higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensitive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
-remains fixed. In both cases, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$
+remains fixed. In both cases, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
+a p-value of $33\%$.
 \begin{figure}
@@
     \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
-    \caption{The predicted binned event count assuming our best-fit 3+1 hypothesis in blue, compared with the 
-    null 3+0 hypothesis in red and data points in black.}\label{fig:final_rate_plot}
+    \caption{The predicted binned event count assuming our best-fit 3+1 hypothesis in blue with $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$, compared with the 
+    null 3+0 hypothesis in red and data points from ~\cite{IC2020} in black.}\label{fig:final_rate_plot}
 \end{figure}

### 2021-12-12 thesis/tex/conclusion.tex
update

--- 2021-12-10 thesis/tex/conclusion.tex
@@
 \chapter{Conclusion}\label{ch:conc}
-TBD
-% TODO Conclusion:
-% We produced the conclusion plots, and ic is insensitive to any impact if th34.
-% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
-% Include effect on system uncertainty on PINGU.
-Compare with other measurements.
-Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
-% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.
+We were able to simulate the IceCube experiment with 86 strings, with the event count of our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig.~\ref{fig:IC_MC_norm}. 
+We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_{24}$ in Fig.~\ref{fig:error_tuning}.
+We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
+Our best-fit parameters were found to be $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
+a p-value of $33\%$.
+We also investigated the case when $\theta_{24} = \theta_{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. From this observation, 
+we conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
+when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to better observe 
+an impact of $\theta_{34}$.
+
+In our second part of the work, we put the sterile neutrino completely aside, and turned our focus to non-standard interactions. 
+We included DeepCore in order to both lower the energy range of the data, but also to include cascade events in this range. 
+Additionally, we simulated a proposed upgrade to DeepCore, PINGU, and produced data for it assuming a standard $3+0$ hypothesis with parameters from~\cite{nufit}.
+We saw that, on a probability level, in the high energy region of IceCube, NSI effects other than those stemming from $\emt$ are not apparent.
+Moreover, we saw in the $\Pme$ shown in Fig~\ref{fig:eem_eet_prob} that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
+We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions, making us hope to constrain $\emt$ further by 
+a joint analysis. This suspicion was confirmed in Fig.~\ref{fig:IC_3D} and shown in Eq.~\ref{eq:PID_result}, where we obtained a stringent bound on $\emt$:
+\begin{align}
+    -0.010 <&\, \emt < 0.0060\,,
+ \end{align}
+Thus, we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
+will be able to even further constrain the parameters.
+
+Our parameters obtained from the DeepCore analysis was more stringent than those obtained in~\cite{demidov}, which used the same data sample as us.
+These bounds were found to be 
+\begin{align}
+    -0.054 <&\, \ett < 0.067 \nonumber \\
+    -0.029 <&\, \emt < 0.0070 \nonumber \\
+    -0.12 <&\, \eem < 0.15 \nonumber \\
+    -0.084 <&\, \eet < 0.15\,.
+ \end{align}
+In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore, with $\emt$ effects being the weakest 
+due to their low effect on all probability channels in the \si{\GeV} range. Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side, 
+we can expect the result to be highly dependent on the systematic uncertainty of PINGU.
+
+Finally, we saw that the effect on $\eem$ and $\eet$ on $\Pme$ shown in Fig.~\ref{fig:eem_eet_prob}.
+After setting $\ett=0$ and marginalizing out $\emt$, this effect is expected to propagate through to the event count of PINGU, 
+manifesting as an anti-correlation between the $\eem$ and $\eet$, shown in Fig~\ref{fig:PINGU_2D}. No other pair of NSI parameters were observed to have 
+a significant correlation.

### 2021-12-12 thesis/tex/introduction.tex
update

@@
 there must have been more matter than antimatter at the Big Bang. This baryon asymmetry is unexplained in the Standard 
-Model.}, nor does it give a candidate for dark matter
-\footnote{Dark matter is heavy matter which does not interact with electromagnetic radiation.
+Model.}, nor does it give a candidate for dark matter\footnote{Dark matter is heavy matter which does not interact with electromagnetic radiation.
 No such particle exists in the Standard Model.}.
@@
 This thesis is outlined as follows. In Chapter~\ref{ch:osc}, we briefly review the most relevant parts of the Standard Model that will be relevant for our extensions of it.
-Then we present the evidence and subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel physics prize, along with the modifications to the Standard Model needed to accommodate the discovery.
+Then we present the evidence and subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel prize in physics, along with the modifications to the Standard Model needed to accommodate the discovery.
 The reader is then introduced to a standard but detailed derivation of the neutrino mixing matrix and oscillation Hamiltonian, including the matter effects stemming from charged and neutral current weak interactions within the Earth.

### 2021-12-12 thesis/tex/nsiResults.tex
update

@@
 \section{The NSI Hypothesis}\label{sec:constraining}
-%TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
-In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
+In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$. As we shall see, the impacts of NSI mainly manifesting 
+themselves at \si{\GeV} energies, causing us to bring back DeepCore and PINGU. We will consider the results obtained from these three detectors separately as well as jointly.
+
 For our analyses, we define our $\chi^2$ as
@@
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
-The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
+by the best and worst case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
+no scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.
 
@@
 since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
-% TODO: Write a few lines about the plots 5.4 and 5.5
+Moreover, we see that we can expect PINGU to be sensitive to systematic uncertainty, especially when constraining $\eem$ and $\eet$ from the negative side.
+
 \begin{figure}
@@
       \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
-      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
+      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
     $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
+    parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.
+    The zones contain the three uncertainty scenarios considered, and we see that the inclusion of PINGU is expected 
+    to drastically make the bound on $\emt$ more stringent.
+    }\label{fig:IC_3D}
    \end{center}
@@
 
-%TODO: PINGU values are the same. Fill in empty values
 {\renewcommand{\arraystretch}{1.0}
@@
          \hline & \multicolumn{2}{c}{IceCube}  \\
-         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017]  \\\\
+         $\emt$ &  [-0.012, 0.011] &  [-0.017, 0.016] \\\\
          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
-         $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
-         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017] \\
-         $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] \\
-         $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] \\\\
+         $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
+         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+         $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+         $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
          &\multicolumn{2}{c}{IceCube + DeepCore} \\
-         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+         $\emt$ &  [-0.013, 0.0070] &  [-0.017, 0.013] \\
          \hline
@@
          \hline & \multicolumn{2}{c}{IceCube}  \\
-         $\emt$ &  [-0.0090, 0.010] &  [-0.015, 0.018]  \\\\
+         $\emt$ &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
-         $\ett$ &    [-0.046, 0.054] &  [-0.065, 0.073]  \\
-         $\emt$ &     [-0.0090, 0.010] &  [-0.015, 0.018]  \\
-         $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16]    \\
-         $\eet$ &    [-0.10, 0.11] &  [-0.19, 0.18]  \\\\
+         $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
+         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+         $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+         $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
          &\multicolumn{2}{c}{IceCube + DeepCore}\\
-         $\emt$ &   [-0.029, 0.0070] & [-0.041, 0.026] \\
+         $\emt$ &  [-0.016, 0.0070] &  [-0.022, 0.016] \\
          \hline
@@
          \hline & \multicolumn{2}{c}{IceCube}  \\
-         $\emt$ &   [-0.010, 0.011] &   [-0.017, 0.020] \\\\
+         $\emt$ &  [-0.018, 0.017] &  [-0.025, 0.024] \\\\
          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
-         $\ett$ &    [-0.049, 0.057] &  [-0.070, 0.078] \\
-         $\emt$ &     [-0.010, 0.011] &   [-0.017, 0.020] \\
-         $\eem$ &   [-0.14, 0.11] &   [-0.23, 0.18] \\
-         $\eet$ &   [-0.13, 0.13] &  [-0.23, 0.12] \\\\
+         $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
+         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+         $\eem$ &  [-0.11, 0.15] &  [-0.23, 0.24] \\
+         $\eet$ &   [-0.084, 0.15] &  [-0.188, 0.212] \\\\
          &\multicolumn{2}{c}{IceCube + DeepCore}\\
-         $\emt$ &   [-0.029, 0.007] & [-0.041, 0.026] \\
+         $\emt$ &  [-0.018, 0.0070] &  [-0.024, 0.018] \\
          \hline
@@
       \hline & \multicolumn{2}{c}{PINGU} \\
-      $\ett$ &  [-0.054, 0.067] & [-0.089, 0.10] \\
-      $\emt$ &  [-0.029, 0.0070] & [-0.041, 0.026] \\
-      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
-      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
+      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] \\
+      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.138] \\
+      $\eet$ &  [-0.079, 0.098] &  [-0.148, 0.161] \\\\
       & \multicolumn{2}{c}{DeepCore + PINGU} \\
@@
       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013]  \\
+      $\emt$ &  [-0.0080, 0.0050] &  [-0.012, 0.011] \\
       \hline
@@
       \hline & \multicolumn{2}{c}{PINGU} \\
-      $\ett$ &   [-0.054, 0.067] & [-0.089, 0.10]\\
-      $\emt$  &  [-0.029, 0.0070] & [-0.041, 0.026] \\
-      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
-      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      $\ett$ &  [-0.046, 0.054] &  [-0.065, 0.073] \\
+      $\emt$ &   [-0.0090, 0.010] &  [-0.015, 0.018] \\
+      $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16] \\
+      $\eet$ &   [-0.10, 0.11] &  [-0.19, 0.18] \\\\
       & \multicolumn{2}{c}{DeepCore + PINGU} \\
@@
       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &   [-0.010, 0.006] &  [-0.016, 0.014] \\
+      $\emt$ &  [-0.009, 0.0060] &  [-0.014, 0.012] \\
       \hline
@@
       \hline & \multicolumn{2}{c}{PINGU} \\
-      $\ett$ &    [-0.054, 0.067] & [-0.089, 0.10] \\
-      $\emt$ &    [-0.029, 0.007] & [-0.041, 0.026] \\
-      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
-      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+      $\ett$ &  [-0.049, 0.057] &   [-0.07, 0.078] \\
+      $\emt$ &   [-0.01, 0.011] &   [-0.017, 0.02] \\
+      $\eem$ &   [-0.137, 0.11] &   [-0.228, 0.18] \\
+      $\eet$ &  [-0.132, 0.125] &  [-0.226, 0.196] \\\\
       & \multicolumn{2}{c}{DeepCore + PINGU} \\
-      $\ett$ &     [-0.039, 0.050] & [-0.06, 0.07] \\
+      $\ett$ &   [-0.039, 0.050] &    [-0.060, 0.070] \\
       $\emt$ &  [-0.011, 0.0070] &  [-0.017, 0.015] \\
-      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
+      $\eem$ &  [-0.082, 0.097] &  [-0.168, 0.16] \\
       $\eet$ &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &   [-0.011, 0.0070] &  [-0.017, 0.015] \\
+      $\emt$ &   [-0.010, 0.0060] &  [-0.016, 0.013] \\
       \hline
@@
 \end{table}
-
-%TODO: compare results
 
@@
 \end{table}
+
+We compare our results to a similar analysis performed on the same DeepCore dataset in~\cite{demidov}. In that publication, 
+the constraints found at 90\% CL were 
+\begin{align}\label{eq:demidov}
+   -0.055 <&\, \ett < 0.056 \nonumber \\
+   -0.023 <&\, \emt < 0.016 \nonumber \\
+   -0.21 <&\, \eem < 0.20 \nonumber \\
+   -0.19 <&\, \eet < 0.20\,.
+\end{align}
+Comparing~\ref{eq:demidov} to our results from Table~\ref{table:IC_DC_results} at 90\% CL, namely
+\begin{align}\label{eq:DC_results}
+   -0.054 <&\, \ett < 0.067 \nonumber \\
+   -0.029 <&\, \emt < 0.0070 \nonumber \\
+   -0.12 <&\, \eem < 0.15 \nonumber \\
+   -0.084 <&\, \eet < 0.15\,,
+\end{align}
+we see that our results for $\eem$, $\eet$ are more stringent, while the results for $\emt$ and $\ett$ are similar but more lenient. It is worth noting that the 
+results from~\cite{demidov} are have been obtained by including more systematic uncertainties, such as the spectral index, hadron production, and baryon resonance. 
+However, the overall flux normalization in~\cite{demidov} is 20\%, while we opted for a slightly higher figure of 25\% which could compensate for the exclusion of the 
+statistical uncertainties mentioned.
+
+Using the baseline case of 3\% systematic uncertainty at 90\% CL, we find from Table~\ref{table:PINGU_joint_results}, that our predictions for the proposed PINGU detector are
+\begin{align}\label{eq_P_results}
+   -0.049 <&\, \ett < 0.057 \nonumber \\
+   -0.010 <&\, \emt < 0.011 \nonumber \\
+   -0.137 <&\, \eem < 0.11 \nonumber \\
+   -0.132 <&\, \eet < 0.125\,,
+\end{align}
+which displays an improvement over the DeepCore results in Eq.~\ref{eq:DC_results}, except for $\eet$ which is worse.
+
+Finally, the joint results for $\emt$ using IceCube and DeepCore from~\ref{table:PINGU_joint_results} at 90\% CL are
+\begin{align}\label{eq:ID_result}
+   -0.016 <&\, \emt < 0.0070\,,
+\end{align}
+and when combining IceCube, DeepCore, and PINGU, the 90\% CL constraint on $\emt$ in our baseline scenario is predicted to be
+\begin{align}\label{eq:PID_result}
+   -0.010 <&\, \emt < 0.0060\,,
+\end{align}
+which is more stringent for $\emt>0$ than the result in~\cite{deepcoreNSI}.
 \newpage
@@
 
-%TODO 5.6 is small, fix labels
 There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI.

### 2021-12-12 thesis/tex/nsiTheory.tex
update

@@
 \subsection{IceCube Signal}
+The effect of NSI on the IceCube event count has been previously discussed in~\cite{salvadoNSI, DC2021, nsiFarzan}
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
@@
 \subsection{DeepCore and PINGU Signals}
+The effect of NSI on the DeepCore event count has been previously discussed in~\cite{smirnovNSI}, while the NSI effect 
+in PINGU has been studied in~\cite{choubey2014, ohlsson2013}.
 Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,

### 2021-12-12 thesis/tex/sterileResults.tex
update

@@
 The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
-$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO: double check these
+$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). 
 The contour plot shown in Fig.~\ref{fig:error_tuning} divides the parameter space into two regions.
@@
 \si{\TeV} energies.
-Wanting to investigate the effect of $\theta_[34]$, we also simulated the 3+1 hypothesis using $\theta_[24] = \theta_[34]$. However, we did not see 
-a difference in the exclusion regions compared to the regions when $\theta_[34] = 0$. Thus, we conclude that on our work, IceCube was not able to 
-distinguish any effect due to the $\theta_[34]$ parameter.
+Wanting to investigate the effect of $\theta_{34}$, we also simulated the 3+1 hypothesis using $\theta_{24} = \theta_{34}$. However, we did not see 
+a difference in the exclusion regions compared to the regions when $\theta_{34} = 0$. Thus, we conclude that on our work, IceCube was not able to 
+distinguish any effect due to the $\theta_{34}$ parameter.

### 2021-12-13 thesis/tex/ICintro.tex
update

@@
             \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
-            \caption{Event classified as cascade}  
+            \caption{Event classified as cascade, caused by an interaction in Eq.~\ref{eq:cascade}.}  
             \label{fig:events_cascade}
@@
             \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
-            \caption{Event classified as track} 
+            \caption{Event classified as track, caused by the interaction in Eq.~\ref{eq:track}.} 
             \label{fig:events_track}
@@
 \end{figure}
-% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
 We always observe neutrinos indirectly.
@@
 via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
-gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
-This fermion is then directly or indirectly detected, 
-and the properties of the neutrino involved in the 
-interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.
+gets its flavor and energy changed, as seen in Eq.~\ref{eq:CC} where an 
+incoming neutrino of flavor $\alpha$ scatters of a fermion or hadron $N$, producing a charged lepton $\alpha$,
+and $N^\prime$ with charge changed by one unit. 
+\begin{align}\label{eq:CC}
+    \nu_\alpha + N \to \alpha + N^\prime
+\end{align}
+This fermion is directly involved in the interaction with the neutrino, either as 
+both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic interaction.
+
+In NC interactions, shown in Eq.~\ref{eq:NC}, no flavor change can occur, so the fermion leaves with increased energy.
+The flavor and charge of the fermion or hadron $N$ interacting with the neutrino is unchanged, but energy 
+from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.
+\begin{align}\label{eq:NC}
+    \nu_\alpha + N \to \nu_\alpha + N^\prime
+\end{align}
 
@@
 a fermion by its emitted Cherenkov light, produced from its travel through the ice. 
-In the case of CC interactions, this fermion is directly involved in the interaction with the neutrino, either as 
-both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic interaction.
-In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
-from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.
-
 If the secondary particles interact heavily with the ice, they will only travel a short distance before decaying 
@@
 However, CC $\ne$ interactions can also produce a similar localized flash of Cherenkov light, causing them to also contribute 
-to the cascade events. A cascade event 
-is shown in Fig.~\ref{fig:events_cascade}.
+to the cascade events. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
+of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. A cascade event 
+is shown in Fig.~\ref{fig:events_cascade} and Eq.~\ref{eq:cascade}, shows the possible interactions causing a cascade event.
+Here $N$ denotes an incoming nucleon (consisting of one fermion due to interact with the neutrino), and the resultant $N^\prime$ can be a hadron or
+a hadronic shower.
+\begin{align}\label{eq:cascade}
+    \nu_\alpha + N &\to \nu_\alpha + N^\prime \nonumber \\
+    \nu_e + N &\to e + N^\prime  \nonumber \\
+    \nu_\tau + N &\to \tau + N^\prime\,.
+\end{align}
 
@@
 as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
-is shown in Fig.~\ref{fig:events_track}.
+is shown in Fig.~\ref{fig:events_track}, and and Eq.~\ref{eq:track} shows the possible interactions causing a track event.
+\begin{align}\label{eq:track}
+    \nm + N \to \mu + N^\prime
+\end{align}
 
-So NC interactions and CC $\ne$ interactions are usually classified as cascades, while CC $\nm$ interactions are usually tagged 
-as a track. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
-of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
-information in Table~\ref{table:events}, containing classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.
+So NC interactions and CC $\ne, \nt$ interactions produce cascades, while CC $\nm$ interactions produce tracks. 
+The charged secondary $N^\prime$ is then detected (or, in the case of CC $\nt$, a tertiary shower from the $\tau$ decay), and the properties of the neutrino involved in the 
+interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}. 
+However, the detection of the topologies themselves is also not straightforward, and misclassifications are bound to occur.
+We see this from classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}, from which we summarize the classification 
+information in Table~\ref{table:events}.
 
@@
     \end{center}
-    \caption{The neutrino event classification at \SI{56}{\GeV} from `Sample B' in~\cite{DC2019tauappearance}}\label{table:events}
+    \caption{The neutrino event classification at \SI{56}{\GeV} from `Sample B' in~\cite{DC2019tauappearance}, showing 
+    how simulated events where classified.}\label{table:events}
 \end{table}

### 2021-12-13 thesis/tex/conclusion.tex
update

@@
 \chapter{Conclusion}\label{ch:conc}
-We were able to simulate the IceCube experiment with 86 strings, with the event count of our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig.~\ref{fig:IC_MC_norm}. 
-We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_{24}$ in Fig.~\ref{fig:error_tuning}.
-We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
-Our best-fit parameters were found to be $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
-a p-value of $33\%$.
-We also investigated the case when $\theta_{24} = \theta_{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. From this observation, 
-we conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
+In this thesis, we have discussed the potential of explaining new physics at the IceCube collaboration detectors.
+We started off by introducing the Standard Model in Ch.~\ref{ch:SM}, and noted that it has several shortcomings. We saw that, by adding a right-handed neutrino field,
+neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
+We mentioned the Super-Kamiokande experiment, and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}. In Ch.~\ref{ch:oscillation},
+we saw how the neutrino mixing matrix could be constructed, and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures. Adding a term for matter potential,
+we then arrived at a Hamiltonian that we used in the time-dependent Schrödinger equation to solve for the oscillation probabilities in matter.
+
+In Ch.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile neutrino~\cite{lsnd}.
+We modified the Hamiltonian to incorporate mixing with this new neutrino species, and saw how $\ns$ affects the $\Pamam$ probability, giving us a resonant $\anm$ disappearance.
+We then put the sterile neutrino aside, and introduced Non-Standard Interactions in Ch.\ref{sec:nsiTheory} as an possible example of new physics beyond the Standard Model.
+By assuming general four-fermion effective operators, we allowed the possibility of the neutrinos to interact across flavors through NSI. We then studied the effects of
+NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
+Moreover, we saw in the $\Pme$ that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
+We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions.
+
+In order to test the sterile neutrino hypothesis, we simulated the IceCube detector, configured with 86 strings. Our method was explained in Ch.\ref{ch:ICmethod}, and we only looked at track events. 
+As a result, we were able to in Ch.~\ref{sec:sterileResults} confirm that the $3+0$ hypothesis holds by using a $\chi^2$ test between the data and our simulated event counts. %TODO: p value?
+After simulating event counts for the $3+1$ hypothesis, which includes the sterile neutrino, we were able to find best-fit parameters of 
+$\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
+a p-value of $33\%$. Even though we found a best-fit for two parameters of the sterile neutrino, they are not statistically significant. Hence, we found no evidence of a sterile neutrino in IceCube.
+We also investigated the case when $\theta_{24} = \theta_{34}$, which produced an identical exclusion contour as in the case with $\theta_{34}=0$. From this observation, 
+we concluded that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
 when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to better observe 
-an impact of $\theta_{34}$.
+an impact of $\theta_{34}$. With this knowledge, we then completely left the sterile neutrino behind.
 
-In our second part of the work, we put the sterile neutrino completely aside, and turned our focus to non-standard interactions. 
-We included DeepCore in order to both lower the energy range of the data, but also to include cascade events in this range. 
-Additionally, we simulated a proposed upgrade to DeepCore, PINGU, and produced data for it assuming a standard $3+0$ hypothesis with parameters from~\cite{nufit}.
-We saw that, on a probability level, in the high energy region of IceCube, NSI effects other than those stemming from $\emt$ are not apparent.
-Moreover, we saw in the $\Pme$ shown in Fig~\ref{fig:eem_eet_prob} that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
-We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions, making us hope to constrain $\emt$ further by 
-a joint analysis. This suspicion was confirmed in Fig.~\ref{fig:IC_3D} and shown in Eq.~\ref{eq:PID_result}, where we obtained a stringent bound on $\emt$:
+In Ch.~\ref{sec:constraining}, we moved on to the NSI parameter $\emt$ and its effect events captured by IceCube. 
+Using a $\chi^2$ test, we found that the bound from IceCube on $\emt$ at 90 \% confidence level was 
 \begin{align}
-    -0.010 <&\, \emt < 0.0060\,,
+    -0.015 <\,& \emt < 0.014\,, \quad (90\% \text{ CL})
 \end{align}
-Thus, we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
-will be able to even further constrain the parameters.
+for our `baseline' case of 15\% systematic uncertainty.
 
-Our parameters obtained from the DeepCore analysis was more stringent than those obtained in~\cite{demidov}, which used the same data sample as us.
-These bounds were found to be 
+In Ch.~\ref{ch:DCmethod}, we moved on and explained our method of simulating a second detector, DeepCore
+
+Armed with simulations possible for this detector, we then continued to explore the possibility of NSI, this time including both track and cascade events and a lower energy region.
+Using the $\chi^2$ test defined in Eq.~\ref{eq:chisq_NSI}, we found the following constraints on four NSI parameters at 90\% confidence level:
 \begin{align}
@@
     -0.12 <&\, \eem < 0.15 \nonumber \\
-    -0.084 <&\, \eet < 0.15\,.
+    -0.084 <&\, \eet < 0.15\,. \quad (\text{all at }90\% \text{ CL})
  \end{align}
-In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore, with $\emt$ effects being the weakest 
-due to their low effect on all probability channels in the \si{\GeV} range. Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side, 
+We compared these constraints to literature, and found that the bounds for $\eem$ and $\eet$ were more stringent than those obtained in~\cite{demidov}.
+
+In Ch.~\ref{ch:PINGUmethod} we described our method of simulating a proposed upgrade to the IceCube array: PINGU.
+Since PINGU is not yet live, we produced data for it assuming a standard $3+0$ hypothesis with parameters from~\cite{nufit}.
+
+This suspicion was confirmed in Fig.~\ref{fig:IC_3D} and shown in Eq.~\ref{eq:PID_result}, where we obtained a stringent bound on $\emt$:
+\begin{align}
+    -0.010 <&\, \emt < 0.0060\,,
+ \end{align}
+using our `baseline' case of 3\% systematic uncertainty.
+
+Thus, we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
+will be able to even further constrain the parameters.
+
+In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore. Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side, 
 we can expect the result to be highly dependent on the systematic uncertainty of PINGU.

### 2021-12-13 thesis/tex/nsiTheory.tex
update

@@
 \subsection{IceCube Signal}
-The effect of NSI on the IceCube event count has been previously discussed in~\cite{salvadoNSI, DC2021, nsiFarzan}
+The effect of NSI on the IceCube event count has been previously discussed in~\cite{salvadoNSI, DC2021, nsiFarzan}.
 In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,

### 2021-12-13 thesis/tex/conclusion.tex
Conclusion almost done

@@
 \chapter{Conclusion}\label{ch:conc}
-In this thesis, we have discussed the potential of explaining new physics at the IceCube collaboration detectors.
-We started off by introducing the Standard Model in Ch.~\ref{ch:SM}, and noted that it has several shortcomings. We saw that, by adding a right-handed neutrino field,
+In this thesis, we have discussed the potential of explaining new physics at the detectors handled by the IceCube collaboration.
+We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. We saw that, by adding a right-handed neutrino field,
 neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
-We mentioned the Super-Kamiokande experiment, and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}. In Ch.~\ref{ch:oscillation},
+We mentioned the Super-Kamiokande experiment, and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}. In Sec.~\ref{ch:oscillation},
 we saw how the neutrino mixing matrix could be constructed, and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures. Adding a term for matter potential,
@@
 
-In Ch.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile neutrino~\cite{lsnd}.
+In Sec.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile neutrino~\cite{lsnd}.
 We modified the Hamiltonian to incorporate mixing with this new neutrino species, and saw how $\ns$ affects the $\Pamam$ probability, giving us a resonant $\anm$ disappearance.
-We then put the sterile neutrino aside, and introduced Non-Standard Interactions in Ch.\ref{sec:nsiTheory} as an possible example of new physics beyond the Standard Model.
-By assuming general four-fermion effective operators, we allowed the possibility of the neutrinos to interact across flavors through NSI. We then studied the effects of
-NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
+We then put the sterile neutrino aside, and introduced Non-Standard Interactions in Sec.\ref{sec:nsiTheory} as an possible example of new physics beyond the Standard Model.
+We then studied the effects of NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
 Moreover, we saw in the $\Pme$ that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
@@
 
-In order to test the sterile neutrino hypothesis, we simulated the IceCube detector, configured with 86 strings. Our method was explained in Ch.\ref{ch:ICmethod}, and we only looked at track events. 
-As a result, we were able to in Ch.~\ref{sec:sterileResults} confirm that the $3+0$ hypothesis holds by using a $\chi^2$ test between the data and our simulated event counts. %TODO: p value?
+In order to test the sterile neutrino hypothesis, we simulated the IceCube detector, configured with 86 strings. Our method was explained in Sec.\ref{ch:ICmethod}, and we only looked at track events. 
+As a result, we were able to in Sec.~\ref{sec:sterileResults} confirm that the $3+0$ hypothesis holds by using a $\chi^2$ test between the data and our simulated event counts. %TODO: p value?
 After simulating event counts for the $3+1$ hypothesis, which includes the sterile neutrino, we were able to find best-fit parameters of 
@@
 
-In Ch.~\ref{sec:constraining}, we moved on to the NSI parameter $\emt$ and its effect events captured by IceCube. 
+In Sec.~\ref{sec:constraining}, we moved on to the NSI parameter $\emt$ and its effect events captured by IceCube. 
 Using a $\chi^2$ test, we found that the bound from IceCube on $\emt$ at 90 \% confidence level was 
 \begin{align}
-    -0.015 <\,& \emt < 0.014\,, \quad (90\% \text{ CL})
+    -0.015 <\,& \emt < 0.014\ \quad (90\% \text{ CL})
 \end{align}
-for our `baseline' case of 15\% systematic uncertainty.
+for our `baseline' case of 15\% uncorrelated systematic uncertainty.
 
-In Ch.~\ref{ch:DCmethod}, we moved on and explained our method of simulating a second detector, DeepCore
-
+In Sec.~\ref{ch:DCmethod}, we moved on and explained our method of simulating a second detector, DeepCore.
 Armed with simulations possible for this detector, we then continued to explore the possibility of NSI, this time including both track and cascade events and a lower energy region.
-Using the $\chi^2$ test defined in Eq.~\ref{eq:chisq_NSI}, we found the following constraints on four NSI parameters at 90\% confidence level:
+Using the $\chi^2$ test defined in Eq.~\ref{eq:chisq_NSI} and marginalizing out $\dm[31]$ and $\theta_{23}$, we found the following constraints on the NSI parameters at 90\% confidence level:
 \begin{align}
@@
     -0.12 <&\, \eem < 0.15 \nonumber \\
-    -0.084 <&\, \eet < 0.15\,. \quad (\text{all at }90\% \text{ CL})
+    -0.084 <&\, \eet < 0.15\ \quad (\text{all at }90\% \text{ CL})\,.
  \end{align}
 We compared these constraints to literature, and found that the bounds for $\eem$ and $\eet$ were more stringent than those obtained in~\cite{demidov}.
+Then, we did a joint $\chi^2$ test using simulated events from both IceCube and DeepCore. At 90\% confidence level, the bound of $\emt$ improved to
+\begin{align}
+    -0.016 <&\, \emt < 0.0070\ \quad (90\% \text{ CL})\,.
+ \end{align}
 
-In Ch.~\ref{ch:PINGUmethod} we described our method of simulating a proposed upgrade to the IceCube array: PINGU.
+In Sec.~\ref{ch:PINGUmethod} we described our method of simulating a proposed upgrade to the IceCube array: PINGU.
 Since PINGU is not yet live, we produced data for it assuming a standard $3+0$ hypothesis with parameters from~\cite{nufit}.
+After a $\chi^2$ analysis, we obtained the following constrains on the NSI parameters at 90\% confidence level:
+\begin{align}
+    -0.049 <&\, \ett < 0.057 \nonumber \\
+    -0.010 <&\, \emt < 0.011 \nonumber \\
+    -0.137 <&\, \eem < 0.11 \nonumber \\
+    -0.132 <&\, \eet < 0.125 \quad (\text{all at }90\% \text{ CL})\,.
+ \end{align}
+After that, we did a joint $\chi^2$ analysis combining IceCube, DeepCore and simulated PINGU events to further constrict $\emt$. The bound at 90\% confidence level obtained was
+\begin{align}
+    -0.010 <&\, \emt < 0.0060\,. \quad (90\% \text{ CL})
+ \end{align}
 
-This suspicion was confirmed in Fig.~\ref{fig:IC_3D} and shown in Eq.~\ref{eq:PID_result}, where we obtained a stringent bound on $\emt$:
-\begin{align}
-    -0.010 <&\, \emt < 0.0060\,,
- \end{align}
-using our `baseline' case of 3\% systematic uncertainty.
-
-Thus, we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
+We were then able to draw the conclusion that we we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
 will be able to even further constrain the parameters.
-
-In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore. Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side, 
+We can expect PINGU to be more sensitive to NSI effects than DeepCore.
+Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side,
 we can expect the result to be highly dependent on the systematic uncertainty of PINGU.
 
-Finally, we saw that the effect on $\eem$ and $\eet$ on $\Pme$ shown in Fig.~\ref{fig:eem_eet_prob}.
-After setting $\ett=0$ and marginalizing out $\emt$, this effect is expected to propagate through to the event count of PINGU, 
-manifesting as an anti-correlation between the $\eem$ and $\eet$, shown in Fig~\ref{fig:PINGU_2D}. No other pair of NSI parameters were observed to have 
+Finally, we simulated the event count in PINGU allowing $\emt$, $\eem$, and $\eet$ to vary, setting $\ett=0$.
+After and marginalizing out $\dm[31]$, $\theta_{23}$ and$\emt$, the effect of $\eem$ and $\eet$ we saw on $\Pme$ had indeed propagated through to the event count,
+manifesting as an anti-correlation between the $\eem$ and $\eet$. No other pair of NSI parameters were observed to have 
 a significant correlation.

### 2021-12-13 thesis/tex/nsiResults.tex
Conclusion almost done

@@
 
+\subsection{$\chi^2$ Minimization}\label{sec:nsi_chi2}
 For our analyses, we define our $\chi^2$ as
@@
 
+\subsection{Constraining the NSI parameters}\label{sec:constraining_NSI}
 After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
@@
 Using the baseline case of 3\% systematic uncertainty at 90\% CL, we find from Table~\ref{table:PINGU_joint_results}, that our predictions for the proposed PINGU detector are
-\begin{align}\label{eq_P_results}
+\begin{align}\label{eq:P_results}
    -0.049 <&\, \ett < 0.057 \nonumber \\
@@
 which is more stringent for $\emt>0$ than the result in~\cite{deepcoreNSI}.
-\newpage
 

### 2021-12-14 thesis/tex/abstract.tex
update

\chapter*{Abstract}
\addcontentsline{toc}{section}{Abstract}

The failure of the Standard Model of particle physics to predict neutrino masses forces us to amend it. We have no reason to believe that 
the interactions currently described by the gauge group are the whole picture, nor should we expect that the number of fermions hitherto observed is correct.
In this thesis, we explore two modifications to the Standard Model, and examine whether these amendments are consistent with measured data.
Firstly, we consider the sterile neutrino, which have no interactions described by the Standard Model. We examine the effect of this 
new fermion on the neutrino oscillation probabilities, and present what would be a detectable signal in the \si{\TeV} range.
Secondly, we consider interactions beyond the Standard Model, possibly stemming from a higher-order theory.
We show how the parameters of these Non-Standard Interactions (NSI) can modify the oscillation probabilities, and within which energy range we expect to be able to discern this signal.
We use data from and simulate event counts in two Cherenkov detectors: IceCube and DeepCore. Moreover, we generate data and simulate a proposed upgrade of the DeepCore detector: PINGU. 
Using IceCube track events, we obtain best-fit values $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ for our sterile neutrino hypothesis at 
a p-value of $20\%$, which is not statistically significant. Hence, we found no evidence of a sterile neutrino in IceCube data. 
Moreover, were unable to distinguish a signal from $\theta_{34}$ in our IceCube simulation.
We obtain stringent bounds on the NSI parameters, and compare those to previous results. We show that PINGU is expected to further narrow the bound 
on $\emt$, especially the considering a joint analysis together with IceCube and DeepCore. Finally, we see that an anti-correlation between 
$\eem$ and $\eet$ at probability level was propagated down to event level, which we expect to be observable by PINGU.

\chapter*{Sammanfattning}
\addcontentsline{toc}{section}{Sammanfattning}
Misslyckandet med partikelfysikens s.k. standardmodell att förutsäga neutrinomassor tvingar oss att ändra den. Vi har ingen anledning att tro att
de interaktioner som för närvarande beskrivs av standardmodellens symmetrigrupp är hela bilden, och vi bör inte heller förvänta oss att antalet fermioner som hittils observerats.
I detta examensarbete undersöker vi två modifieringar av standardmodellen och undersöker om dessa ändringar är förenliga med uppmätta data.
Först introducerar vi den sterila neutrinon, som inte har några interaktioner som beskrivs av standardmodellen. Vi undersöker effekten av denna
nya fermion på neutrinoscillationssannolikheterna, och presentera vad som skulle vara en detekterbar signal i \si{\TeV}-området.
Vidare introducerar vi en ny interaktion som vi kallar Icke-Standard Interaktioner (NSI), som möjligen härrör från en högre ordningens teori.
Vi visar hur NSI-parametrarna kan modifiera oscillationssannolikheterna, och inom vilka energiområden vi förväntar oss att urskilja denna signal.

Vi samlar in data från och simulerar två Cherenkov-detektorer: IceCube och DeepCore. Dessutom presenterar vi resultat som vi
kan förvänta sig att se i en kommande uppgradering av DeepCore-detektorn: PINGU.

Vi får resultat som indikerar att den aktuella 3+0-hypotesen överensstämmer med IceCube-data, med bästa anpassningsvärden
$\dm[41] = \SI{0.01}{\eV^2}$ och $\theta_{24} = 0.67 $ med
ett p-värde på $33\%$. Vi kunde inte skilja en signal från $\theta_{34}$.
Vi erhåller stringenta gränser för NSI-parametrarna och jämför dem med tidigare resultat. Vi visar att PINGU förväntas minska gränsen ytterligare
hos $\emt$, särskilt genom att gemensamt analysera resultaten med IceCube och DeepCore. Slutligen ser vi att en anti-korrelation mellan
$\eem$ och $\eet$ på sannolikhetsnivå spreds ner till händelsenivå, vilket kommer att kunna observeras av PINGU.

\chapter*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
The computations were enabled by resources provided by the Swedish
National Infrastructure for Computing (SNIC) at HPC2N, Umeå University
and NSC, Linköping University. The resources were partially funded by the Swedish Research 
Council through grant agreement no. 2018-05973

### 2021-12-14 thesis/tex/conclusion.tex
update

@@
 \chapter{Conclusion}\label{ch:conc}
-In this thesis, we have discussed the potential of explaining new physics at the detectors handled by the IceCube collaboration.
-We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. We saw that, by adding a right-handed neutrino field,
-neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
-We mentioned the Super-Kamiokande experiment, and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}. In Sec.~\ref{ch:oscillation},
-we saw how the neutrino mixing matrix could be constructed, and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures. Adding a term for matter potential,
+In this thesis, we have explored the potential of explaining new physics using detectors handled by the IceCube collaboration.
+We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. 
+We mentioned the Super-Kamiokande experiment, and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}, in direct violation of the Standard Model. 
+We saw that, by adding a right-handed neutrino field, neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
+In Sec.~\ref{ch:oscillation}, we saw how the neutrino mixing matrix could be constructed, and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures.
+Adding a term for matter potential,
 we then arrived at a Hamiltonian that we used in the time-dependent Schrödinger equation to solve for the oscillation probabilities in matter.
 
-In Sec.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile neutrino~\cite{lsnd}.
-We modified the Hamiltonian to incorporate mixing with this new neutrino species, and saw how $\ns$ affects the $\Pamam$ probability, giving us a resonant $\anm$ disappearance.
-We then put the sterile neutrino aside, and introduced Non-Standard Interactions in Sec.\ref{sec:nsiTheory} as an possible example of new physics beyond the Standard Model.
+In Sec.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile, neutrino $\ns$~\cite{lsnd}.
+We modified the Hamiltonian to incorporate mixing with this new neutrino species, and saw how a \si{\eV^2} scale  $\ns$ with $\theta_{24}\neq 0$ affects the $\Pamam$ oscillation probability 
+by giving us a resonant \si{\TeV} $\anm$ disappearance.
+
+We then put the sterile neutrino aside, and introduced Non-Standard Interactions (NSI) in Sec.\ref{sec:nsiTheory} as an possible example of new physics beyond the Standard Model.
 We then studied the effects of NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
-Moreover, we saw in the $\Pme$ that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
+Moreover, we saw in $\Pme$ that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
 We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions.
 
-In order to test the sterile neutrino hypothesis, we simulated the IceCube detector, configured with 86 strings. Our method was explained in Sec.\ref{ch:ICmethod}, and we only looked at track events. 
-As a result, we were able to in Sec.~\ref{sec:sterileResults} confirm that the $3+0$ hypothesis holds by using a $\chi^2$ test between the data and our simulated event counts. %TODO: p value?
-After simulating event counts for the $3+1$ hypothesis, which includes the sterile neutrino, we were able to find best-fit parameters of 
+First, we described our method in testing the sterile neutrino hypothesis (3+1). We simulated the 86 string IceCube detector with track events, explained in Sec.\ref{ch:ICmethod}.
+After simulating event counts in Sec.~\ref{sec:sterileResults} for the $3+1$ hypothesis, we were able to find best-fit parameters of 
 $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
-a p-value of $33\%$. Even though we found a best-fit for two parameters of the sterile neutrino, they are not statistically significant. Hence, we found no evidence of a sterile neutrino in IceCube.
-We also investigated the case when $\theta_{24} = \theta_{34}$, which produced an identical exclusion contour as in the case with $\theta_{34}=0$. From this observation, 
+a p-value of $20\%$.
+Even though we found a best-fit for two parameters of the sterile neutrino, they are not statistically significant.
+Hence, we found no evidence of a sterile neutrino in IceCube data.
+We also investigated the case when $\theta_{24} = \theta_{34}$, which produced an identical contour as in the case with $\theta_{34}=0$. From this observation, 
 we concluded that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
 when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to better observe 
-an impact of $\theta_{34}$. With this knowledge, we then completely left the sterile neutrino behind.
+an impact of $\theta_{34}$. With these results, we then completely left the sterile neutrino behind.
 
@@
 Armed with simulations possible for this detector, we then continued to explore the possibility of NSI, this time including both track and cascade events and a lower energy region.
-Using the $\chi^2$ test defined in Eq.~\ref{eq:chisq_NSI} and marginalizing out $\dm[31]$ and $\theta_{23}$, we found the following constraints on the NSI parameters at 90\% confidence level:
+Using the $\chi^2$ test defined in Eq.~\ref{eq:chisq_NSI} and after marginalizing $\dm[31]$ and $\theta_{23}$ out, we found the following constraints on the NSI parameters at 90\% confidence level:
 \begin{align}
@@
 
-Finally, we simulated the event count in PINGU allowing $\emt$, $\eem$, and $\eet$ to vary, setting $\ett=0$.
-After and marginalizing out $\dm[31]$, $\theta_{23}$ and$\emt$, the effect of $\eem$ and $\eet$ we saw on $\Pme$ had indeed propagated through to the event count,
-manifesting as an anti-correlation between the $\eem$ and $\eet$. No other pair of NSI parameters were observed to have 
+Finally, we simulated the event count in PINGU allowing $\emt$, $\eem$, and $\eet$ to vary, but setting $\ett=0$.
+After and marginalizing out $\dm[31]$, $\theta_{23}$, and $\emt$, we saw that the effect of $\eem$ and $\eet$ on $\Pme$ had indeed propagated through to the event count,
+manifesting as an anti-correlation between the $\eem$ and $\eet$ at both 90\% and $3\sigma$ confidence levels. No other pair of NSI parameters were observed to have 
 a significant correlation.

### 2021-12-14 thesis/tex/abstract.tex
update

@@
 
-The failure of the Standard Model of particle physics to predict neutrino masses forces us to amend it. We have no reason to believe that 
+The failure of the Standard Model of particle physics to predict neutrino masses invites us to amend it. We have no reason to believe that 
 the interactions currently described by the gauge group are the whole picture, nor should we expect that the number of fermions hitherto observed is correct.
-In this thesis, we explore two modifications to the Standard Model, and examine whether these amendments are consistent with measured data.
+In this thesis, we explore two amendments to the Standard Model, and examine whether either of these are consistent with measured data.
+
 Firstly, we consider the sterile neutrino, which have no interactions described by the Standard Model. We examine the effect of this 
-new fermion on the neutrino oscillation probabilities, and present what would be a detectable signal in the \si{\TeV} range.
+new fermion on the neutrino oscillation probabilities, and present what could be a detectable signal in the \si{\TeV} energy range.
 Secondly, we consider interactions beyond the Standard Model, possibly stemming from a higher-order theory.
@@
 We use data from and simulate event counts in two Cherenkov detectors: IceCube and DeepCore. Moreover, we generate data and simulate a proposed upgrade of the DeepCore detector: PINGU.
+
 Using IceCube track events, we obtain best-fit values $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ for our sterile neutrino hypothesis at 
@@
 Moreover, were unable to distinguish a signal from $\theta_{34}$ in our IceCube simulation.
-We obtain stringent bounds on the NSI parameters, and compare those to previous results. We show that PINGU is expected to further narrow the bound 
+We obtain stringent bounds on the NSI parameters, and compare those to previous results in literature. We show that PINGU is expected to further narrow the bound 
 on $\emt$, especially the considering a joint analysis together with IceCube and DeepCore. Finally, we see that an anti-correlation between 

### 2021-12-14 thesis/tex/nsiResults.tex
update

@@
 
-\subsection{$\chi^2$ Minimization}\label{sec:nsi_chi2}
+\subsection{\texorpdfstring{$\chi^2$}{Chi-squared} Minimization}
+\label{sec:nsi_chi2}
 For our analyses, we define our $\chi^2$ as
@@
 In our simulations of $N_{ijk}^\text{th}$, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, 
-except for $\dm$ and $\theta_{23}$
-which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV\squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
+except for $\dm[31]$ and $\theta_{23}$
+which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV\squared} and \SIrange{40.1}{51.7}{\degree}, respectively~\cite{nufit}.
 
@@
 \subsection{Constraining the NSI parameters}\label{sec:constraining_NSI}
-After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
+We let each of the four NSI parameters considered assume a value, while keeping the other three fixed at zero. We consider the following ranges of values for each parameter:
+\begin{align}
+   -0.07 \le &\, \ett \le 0.07 \nonumber \\
+   -0.03 \le &\, \emt \le 0.03 \nonumber \\
+   -0.3 \le &\, \eem \le 0.3 \nonumber \\
+   -0.3 \le &\, \eet \le 0.3 \nonumber \\
+\end{align}
+After the oscillation parameters $\dm[31]$ and $\theta_{23}$ have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
 The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
 by the best and worst case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
-no scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.
+no uncertainty scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.
 

### 2021-12-14 thesis/tex/sterileResults.tex
update

@@
-\section{The Sterile Hypothesis}\label{sec:sterileResults}
+\section{The Sterile Neutrino Hypothesis}\label{sec:sterileResults}
 With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:MC_norm}, we are now in good shape to study the sterile neutrino effect on the probabilities, and how that compares to data
@@
 Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
-for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$.
+for neutrinos at $\SI{10}{\TeV}$ values. In zenith, the data only deviates $\pm 2\%$.
 
@@
 higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensitive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
-remains fixed. In both cases, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
-a p-value of $33\%$.
+remains fixed. Using the case of 15\% uncorrelated systematic error, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
+a p-value of $20\%$. This is not statistically significant, 
+hence we find no evidence for a sterile neutrino within the parameter range $0.01 \le \dm[41] \le \SI{1}{\eV^2}, 0.01\le \sin(2\theta_{24})^2 \le 1$  in IceCube data.
 \begin{figure}
@@
 
-In Fig.~\ref{fig:final_rate_plot}, we see that the simulations are consistent with the 3+0 hypothesis with deviations of 6\% at high single-digit 
-\si{\TeV} energies.
 Wanting to investigate the effect of $\theta_{34}$, we also simulated the 3+1 hypothesis using $\theta_{24} = \theta_{34}$. However, we did not see 
 a difference in the exclusion regions compared to the regions when $\theta_{34} = 0$. Thus, we conclude that on our work, IceCube was not able to 
-distinguish any effect due to the $\theta_{34}$ parameter.
+distinguish any effect due to the $\theta_{34}$ parameter. However, since our dataset only included muon track events in the \SIrange{0.5}{10}{\TeV} range,
+one might be able to expect a larger effect of $\theta_{34}$ if one includes cascade events as well.

### 2021-12-14 thesis/tex/ICtheory.tex
updated, and added worse s24 fig
update

@@
-% \documentclass{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \input{commands}
-% \begin{document}
-
 \section{IceCube}\label{ch:ICmethod}
@@
 collaboration has all the ingredients that we need~\cite{IC2016}. In Table.~\ref{table:IC_MC} we show a selection of the data.
-The "pdg" column refers to the Monte Carlo particle classification, where 13 is the tag for $\nm$, while -13 refers
+The `pdg' column refers to the Monte Carlo particle classification, where 13 is the tag for $\nm$, while -13 refers
 to an $\anm$. Here we note a crucial property of the IceCube dataset that will impact our analysis: the MC released by the collaboration
@@
     \includegraphics[scale=0.4]{figures/IC_data.pdf}
-    \caption{IceCube track events from~\cite{IC2020}.}\label{fig:IC_data}
+    \caption{IceCube track events from~\cite{IC2020}, displaying the $E^{-1.7}$ drop-off in event count.}\label{fig:IC_data}
 \end{figure}
@@
     \begin{centering}
-    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
+    \includegraphics[scale=0.7]{figures/IC_MC_norm.pdf}
     \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in red in the plots.}\label{fig:IC_MC_norm}

### 2021-12-14 thesis/tex/SM.tex
Lots of changes!!
update

@@
-% \input{commands}\begin{document}
 \begin{figure}[!h]
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/SM_figure.pdf}
+    \includegraphics[width=0.95\textwidth]{figures/SM_figure.pdf}
 \end{figure}
@@
 these modifications might be supported by experimental evidence.
-Moreover, we will examine the possibility of adding a new completely new force, which manifests itself as modifications to the neutrino-matter interactions.
+Moreover, we will examine the possibility of adding a new completely new interaction, which manifests itself as modifications to the neutrino-matter interactions.
 
@@
 where $V^\ell_L$ and $V^\ell_R$ are two unitary matrices.
-Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, 
-since no flavor rotation can make massless fields massive.
+Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. 
 Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.

### 2021-12-14 thesis/tex/introduction.tex
update

@@
 
-Chapter~\ref{ch:theory} consists of two parts. In Section~\ref{sec:anomalies}, we introduce a new particle: the sterile neutrino. 
+Chapter~\ref{ch:theory} consists of two parts. In Section~\ref{sec:anomalies}, we consider a particle beyond the Standard Model: the sterile neutrino. 
 We present how neutrino oscillations are modified by this hypothesized fourth neutrino and how these modifications would appear in IceCube if the particle is present in Nature. 
-In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside and instead turn to the interactions between neutrinos and the Earth. 
+In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside and instead turn to the interactions between neutrinos and matter. 
 We again amend the Standard Model by considering exotic interactions from a higher energy theory, manifesting themselves as sub-leading modifications to the matter potential. 
@@
 Finally, Chapter~\ref{ch:results} contains the result from our two separate extensions of the Standard Model.
-In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino and compare those with literature. 
-In Section~\ref{sec:constraining}, we present new constrained bounds on the NSI parameters by combining our results for IceCube, DeepCore, and PINGU.
+In Section~\ref{sec:sterileResults} we present our findings for the sterile neutrino. 
+In Section~\ref{sec:constraining}, we present new constrained bounds on the NSI parameters compare those with literature.

### 2021-12-14 thesis/tex/oscillations.tex
update

@@
 
-We construct the PMNS matrix by parametrizing it as as
+We construct the PMNS matrix by parametrizing it with the rotation matrices $R_{ij}$ and a matrix $P_{Maj}$ as
 \begin{align}\label{PMNS_def}
@@
 However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
-Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
+Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix through $P_{Maj}$.
+These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
 Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number, and a Majorana phase would
@@
 which use to we plot the $P_{\mu \beta}$ probabilities in Fig.~\ref{fig:vac_osc}.
-Here, we show the energy spectra of these oscillations in the low \si{\GeV} range for neutrinos that travel \SI{12000}{\km}\footnote{This baseline
-is approximately the Earth diameter, and will be the maximum travel distance which we will use later on.}.
+Here, we show the energy spectra of these oscillations in the low \si{\GeV} range for neutrinos that travel \SI{12742}{\km}\footnote{This baseline
+is the Earth diameter, and will, apart from the atmosphere, be the maximum travel distance which we will use later on.}.
 In the left-most panel, we see a suppressed $\nm \to \ne$ transition. We can understand this behavior by studying Eq.~\ref{eq:Pab} and the 
@@
     \includegraphics[width=1\textwidth]{figures/vac_osc.pdf}
-    \caption{Probabilities of $\nm$ oscillations after travelling 12 000 km in vacuum.}\label{fig:vac_osc}
+    \caption{Probabilities of $\nm$ oscillations after travelling 12 742 km in vacuum, using parameters from~\cite{nufit}.}\label{fig:vac_osc}
     \end{center}
@@
 In Fig.~\ref{fig:vac_vs_matter}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
-traveling 12000 km. The red line is the vacuum oscillation, while the black line is the matter oscillation, traversing through the 
+traveling 12742 km. The red line is the vacuum oscillation, while the black line is the matter oscillation, traversing through the 
 matter density profile of the Earth. We see that the matter effects are more for some energies, and less for others. At energies 
@@
 % TODO: segue into 2gen
-We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form, and start simplifying:
+We can reduce this down to two dimensions by extracting the upper-left block of all matrices\footnote{Or, following the method of the derivation of the Hamiltonianin the three-
+neutrino picture, take U as one two-dimensional rotation matrix.}. We now have the Hamiltonian in a two-dimensional form, and start simplifying:
 
@@
 In Fig.~\ref{fig:2_vs_3}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
-traveling 12000 km. The black lines are the probabilities of $\nm$ oscillation, after it has traversing through the diameter of the Earth.
+traveling through the entire Earth diameter. The black lines are the probabilities of $\nm$ oscillation, after it has traversing through the diameter of the Earth.
 The red lines are the probabilities of $\nm$ oscillation, but in the two-neutrino picture using Eq.~\ref{eq:2gen}. So in the left-most panel,

### 2021-12-14 thesis/tex/DCtheory.tex
update

@@
 
-The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
+The detector systematics include ice absorption and scattering and overall, lateral, and head-on optical efficiencies of the DOMs. 
 They are applied as correction factors using the best-fit points from the 2019 DeepCore $\nu_\tau$ appearance 
@@
 
-\section{PINGU}
+\section{PINGU}\label{ch:PINGUmethod}
 The methodology behind the PINGU simulations is the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
+However, since no detector systematics is yet modeled for PINGU, the correction factors $C_{ijk}$ are all unity.
 As with the DeepCore data, the PINGU Monte Carlo is divided into eight 
 $\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
-We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
+We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase, which is set to zero for simplicity.
 

### 2021-12-14 thesis/tex/ICintro.tex
update

@@
 % overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
-The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.
+The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this substantial decline in flux.
 
@@
 In NC interactions, shown in Eq.~\ref{eq:NC}, no flavor change can occur, so the fermion leaves with increased energy.
-The flavor and charge of the fermion or hadron $N$ interacting with the neutrino is unchanged, but energy 
+The flavor and charge of the fermion or hadron $N$ interacting with the neutrino are unchanged. However, energy 
 from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.
@@
 a fermion by its emitted Cherenkov light, produced from its travel through the ice. 
-If the secondary particles interact heavily with the ice, they will only travel a short distance before decaying 
-into the shower which emit a localized flash of Cherenkov light. This event is referred to as a cascade.
+If the secondary particles interact heavily with the ice, they will only travel a short distance. They then decay
+into a shower which emits a localized flash of Cherenkov light. This event is referred to as a cascade.
 NC interactions tend to be classified as cascades due to the production of a localized hadronic shower
@@
 
-If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
-as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
+If the charged leptons do not interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
+as they go. This event is called a track and is often due to charged current muon interactions. A track event 
 is shown in Fig.~\ref{fig:events_track}, and and Eq.~\ref{eq:track} shows the possible interactions causing a track event.
@@
 
-To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
+In order to detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
 into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.
@@
 The strings and DOMs are not spaced evenly, making some parts of the detector more sensitive to certain energy ranges than others.
-8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}.
-This detector is referred to DeepCore.
-DeepCore will be treated as a separate and independent detector from the rest, which
+8 strings packed more tightly than the other 78, making that part of the detector sensitive to neutrino energies down to single-digit \si{\GeV}. This detector is referred to DeepCore. 
+DeepCore will be treated as a separate and independent detector from the rest of the array, which
 retains the name IceCube.
@@
 supplement DeepCore, i.e. boosting the capabilities of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
-not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
-results from IceCube and DeepCore. The PINGU simulations have the same structure as the DeepCore data, so our analysis referring to DeepCore will
+unable to use any data from it. However, the collaboration has released preliminary simulations, which we will use. The simulated events 
+are between \SIrange{5.6}{56}{\GeV}, the same range as the DeepCore data.
+The PINGU simulations have the same structure as the DeepCore data, so our analysis referring to DeepCore will
 also apply to PINGU except where noted. However, we treat the PINGU detector as independent of the other experiments.
@@
 After an event has occurred, the IceCube collaboration \emph{reconstruct} the event. 
-This means that, given the parameters recorded by the detector, what are their `true' values?
+Given the parameters recorded by the detector, what are their `true' values?
 We are interested in two variables: energy and direction. Each event is tagged with a probable energy and zenith angle, 

### 2021-12-14 thesis/tex/ICtheory.tex
update

--- 2021-12-11 thesis/tex/ICtheory.tex
@@
-% \documentclass{thesis}
-% \usepackage[margin=0.5in]{geometry}
-% \input{commands}
-% \begin{document}
-
 \section{IceCube}\label{ch:ICmethod}
-As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact with charged leptons in the ice.
-The charged lepton then emits the Cherenkov light that is detected by the array.
+As the neutrinos have propagated the Earth, they arrive at the South Pole, where they interact with charged leptons in the ice. The charged lepton then emits the Cherenkov light detected by the array.
 We construct the event rate for each bin as
@@
 where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\theta_z^r$ the reconstructed 
-zenith angle, i.e. the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle, i.e. the actual direction of the incoming neutrino. 
+zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle, i.e.~the actual direction of the incoming neutrino. 
 $E^r$ is the reconstructed energy, binned with index $j$. $R(\theta^r,\theta^t)$ is a zenith resolution function 
@@
 i.e.~the cross-sectional area of the detector that the lepton is exposed to.
-$\Aeff$ depends on several parameters, some of them being detector physical volume, $\Etrue$, $\ztrue$, and the particle type. 
+$\Aeff$ depends on several parameters, some of them being physical detector volume, $\Etrue$, $\ztrue$, and the particle type. 
 Fortunately, the binned $\Aeff$ is provided to us by the collaboration~\cite{ICaeff}.
@@
 
-Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will on average, experience the same $\Aeff$ in our model. 
+Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will, on average, experience the same $\Aeff$ in our model. 
 Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
@@
 While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself. 
-Energy-wise, the situation here is completely reverse from the flux.
 Increasing linearly with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.
@@
 So now we have the physical quantities in the true parameters. 
-But as we discussed, we need a way to translate this into the reconstructed parameters that the detector gives us. We will call the relationship between 
+As we discussed, we need a way to translate this into the reconstructed parameters that the detector gives us. We will call the relationship between 
 $\Ereco$ and $\Etrue$ the energy resolution function, and the relationship between $\zreco$ and $\ztrue$ the zenith resolution function. 
@@
 The angular resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.
-Thus, we only need to concern ourselves with the energy resolution.
+Thus, we only need to concern ourselves with the energy resolution function.
 In Fig.~\ref{fig:IC_MC_gpr}, we have plotted all event counts found in the MC file, over 8 million.
-However, this is too much data to process efficiently, with many outliers that ultimately don't weigh in
+However, this is too much data to process efficiently, with many outliers that ultimately do not weigh in
 that much in the final event count.
 To resolve this, we have opted to train a Gaussian process regressor on the dataset, from which we can extract the predicted mean and standard deviation for a point.
-When doing this over $\Ereco$, we sample $\Etrue$ in the 99th percentile around the predicted mean.
-We then obtain the shaded band shown in Fig.~\ref{fig:IC_MC_gpr}.
-%TODO add plot with Etrue vs prob dens
+When doing this over $\Ereco$, we sample $\Etrue$ in the 99th percentile around the predicted mean. We then obtain the shaded band shown in Fig.~\ref{fig:IC_MC_gpr}.
 
@@
 That way, we know that our null hypotheses will align while we are free to form additional hypotheses with different
-physics parameters. %The binned Monte Carlo events that IceCube used as their null hypothesis in the 2020 sterile analysis is shown in %TODO:MC vs myMC fig.
+physics parameters.
 
@@
     \includegraphics[scale=0.4]{figures/IC_data.pdf}
-    \caption{IceCube track events from~\cite{IC2020}.}\label{fig:IC_data}
+    \caption{IceCube track events from~\cite{IC2020}, displaying the $E^-{-1.7}$ drop-off in event count.}\label{fig:IC_data}
 \end{figure}
@@
 \subsection*{Monte Carlo normalization}
-Independent researchers outside of the IceCube collaboration will not be able to more precisely
-simulate the detector. The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this 
-section is to come as close as we can to their Monte Carlo simulations. After we are confident that 
+Independent researchers outside of the IceCube collaboration will not be able to simulate the detector more precisely.
+The IceCube Monte Carlo is a complex and proprietary machinery, so our goal in this 
+section is merely to come as close as we can to it. After we are confident that 
 our code displays the same overall features as the `official', we normalize our results $N_{ij}^\text{sim}$ as 
@@
 Recent IceCube data releases do not include such information. Since the systematic errors are affecting the 
-event count on a bin-by-bin basis, they can in theory drastically modify the binned results. Another example of
+event count on a bin-by-bin basis, they can, in theory, drastically modify the binned results. Another example of
 an error source that will be remedied by this method is the flux. We are using a fairly simple model of the atmospheric 
-flux that excludes atmospheric prompt and astrophysical fluxes. The IceCube collaboration uses several different flux models which are initialized 
+flux that excludes atmospheric prompt and astrophysical fluxes. The IceCube collaboration uses several different flux models, which are initialized 
 by a parametrization of the cosmic ray flux.\footnote{Included in the cosmic ray models are e.g. the pion to kaon 
 ratio, which are often used as a nuisance parameter. By not being able to include this in our error analysis, our method will 
-be limited to only consider the overall flux normalization, rather than the components that produce the flux in the first place.}
+be limited to only consider the overall flux normalization rather than the components that produce the flux in the first place.}
 

### 2021-12-14 thesis/tex/SM.tex
update

--- 2021-11-18 thesis/tex/SM.tex
@@
-% \input{commands}\begin{document}
 \begin{figure}[!h]
@@
 In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
-All neutrinos are left-handed and all antineutrinos are right-handed~\cite{giunti}. This observational fact is reflected in the 
+All neutrinos are left-handed, and all antineutrinos are right-handed~\cite{giunti}. This observational fact is reflected in the 
 left-handed lepton doublet and right-handed lepton singlet
@@
 This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement for neutrino flavor eigenstates to have a definite mass. 
-The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
+The flavor of a neutrino is then -- by definition -- the flavor of the associated charged lepton. 
 This fact is denoted as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.

### 2021-12-14 thesis/tex/conclusion.tex
update

@@
 We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. 
-We mentioned the Super-Kamiokande experiment, and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}, in direct violation of the Standard Model. 
+We mentioned the Super-Kamiokande experiment and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}, in direct violation of the Standard Model. 
 We saw that, by adding a right-handed neutrino field, neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
-In Sec.~\ref{ch:oscillation}, we saw how the neutrino mixing matrix could be constructed, and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures.
+In Sec.~\ref{ch:oscillation}, we saw how the neutrino mixing matrix could be constructed and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures.
 Adding a term for matter potential,
@@
 
-We then put the sterile neutrino aside, and introduced Non-Standard Interactions (NSI) in Sec.\ref{sec:nsiTheory} as an possible example of new physics beyond the Standard Model.
+We then put the sterile neutrino aside and introduced Non-Standard Interactions (NSI) in Sec.\ref{sec:nsiTheory} as a possible example of new physics beyond the Standard Model.
 We then studied the effects of NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
@@
 we concluded that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
-when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to better observe 
+when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with the inclusion of cascade events from $\nt$, IceCube could be able to better observe 
 an impact of $\theta_{34}$. With these results, we then completely left the sterile neutrino behind.
@@
  \end{align}
-We compared these constraints to literature, and found that the bounds for $\eem$ and $\eet$ were more stringent than those obtained in~\cite{demidov}.
+We compared these constraints to literature and found that the bounds for $\eem$ and $\eet$ were more stringent than those obtained in~\cite{demidov}.
 Then, we did a joint $\chi^2$ test using simulated events from both IceCube and DeepCore. At 90\% confidence level, the bound of $\emt$ improved to
@@
 
-We were then able to draw the conclusion that we we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
-will be able to even further constrain the parameters.
-We can expect PINGU to be more sensitive to NSI effects than DeepCore.
-Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side,
+We were then able to draw the conclusion that we expect PINGU to successfully be able to observe the impact of NSI.
+Moreover, a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
+will be able to constrain the parameters even further.
+We saw that can expect PINGU to be more sensitive to NSI effects than DeepCore.
+We were also able to see that when constraining $\eem$ and $\eet$ from the negative side,
 we can expect the result to be highly dependent on the systematic uncertainty of PINGU.
 
-Finally, we simulated the event count in PINGU allowing $\emt$, $\eem$, and $\eet$ to vary, but setting $\ett=0$.
+Finally, we simulated the event count in PINGU, allowing $\emt$, $\eem$, and $\eet$ to vary, but setting $\ett=0$.
 After and marginalizing out $\dm[31]$, $\theta_{23}$, and $\emt$, we saw that the effect of $\eem$ and $\eet$ on $\Pme$ had indeed propagated through to the event count,

### 2021-12-14 thesis/tex/introduction.tex
update

--- 2021-12-12 thesis/tex/introduction.tex
@@
 No such particle exists in the Standard Model.}.
-To make matters even worse, three of the particles which are massless according to the Standard Model have been observed to have mass.
+To make matters even worse, three of the particles which are massless according to the Standard Model have been observed to actually have mass.
 In this thesis, we focus on the said particles -- the neutrinos -- and propose extensions to the Standard Model related to them. 
@@
 We present how neutrino oscillations are modified by this hypothesized fourth neutrino and how these modifications would appear in IceCube if the particle is present in Nature. 
-In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside and instead turn to the interactions between neutrinos and the Earth. 
+In Section~\ref{sec:nsiTheory}, we set the sterile neutrino aside altogether and instead turn to the interactions between neutrinos and the Earth. 
 We again amend the Standard Model by considering exotic interactions from a higher energy theory, manifesting themselves as sub-leading modifications to the matter potential. 

### 2021-12-14 thesis/tex/old_abstract.tex
update

--- 2021-12-14 thesis/tex/abstract.tex
@@
 In this thesis, we explore two modifications to the Standard Model, and examine whether these amendments are consistent with measured data.
-Firstly, we consider the sterile neutrino, which have no interactions described by the Standard Model. We examine the effect of this 
+Firstly, we introduce the sterile neutrino, which have no interactions described by the Standard Model. We examine the effect of this 
 new fermion on the neutrino oscillation probabilities, and present what would be a detectable signal in the \si{\TeV} range.
-Secondly, we consider interactions beyond the Standard Model, possibly stemming from a higher-order theory.
-We show how the parameters of these Non-Standard Interactions (NSI) can modify the oscillation probabilities, and within which energy range we expect to be able to discern this signal.
-We use data from and simulate event counts in two Cherenkov detectors: IceCube and DeepCore. Moreover, we generate data and simulate a proposed upgrade of the DeepCore detector: PINGU. 
-Using IceCube track events, we obtain best-fit values $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ for our sterile neutrino hypothesis at 
-a p-value of $20\%$, which is not statistically significant. Hence, we found no evidence of a sterile neutrino in IceCube data. 
-Moreover, were unable to distinguish a signal from $\theta_{34}$ in our IceCube simulation.
+Secondly, we are introducing a new interaction which we call Non-Standard Interactions (NSI), possibly stemming from a higher-order theory. 
+We show how the NSI parameters can modify the oscillation probabilities, and within which energy range we expect to be able to discern this signal.
+
+We are collecting data from and simulating two Cherenkov detectors: IceCube and DeepCore. Moreover, we are presenting results which we 
+can expect to see in a coming upgrade of the DeepCore detector: PINGU.
+
+We obtain results indicating that the current 3+0 hypothesis is consistent with IceCube data, with best-fit values $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ at 
+a p-value of $33\%$. We were unable to distinguish a signal from $\theta_{34}$.
 We obtain stringent bounds on the NSI parameters, and compare those to previous results. We show that PINGU is expected to further narrow the bound 
 on $\emt$, especially the considering a joint analysis together with IceCube and DeepCore. Finally, we see that an anti-correlation between 
-$\eem$ and $\eet$ at probability level was propagated down to event level, which we expect to be observable by PINGU.
+$\eem$ and $\eet$ at probability level was propagated down to event level, which will be observable by PINGU.
 

### 2021-12-14 thesis/tex/oscillations.tex
update

--- 2021-12-11 thesis/tex/oscillations.tex
@@
 
-We construct the PMNS matrix by parametrizing it as as
+We construct the PMNS matrix by parametrizing it as
 \begin{align}\label{PMNS_def}
@@
 Since we now know how the neutrino mass and flavor eigenstates combine and have an expression for the flavor interaction with 
-the neutrino's charged lepton partner, we are now ready to study the flavor oscillations themselves.
+the neutrinos charged lepton partner, we are now ready to study the flavor oscillations themselves.
 
@@
 \end{figure}
-So far we have discussed neutrinos traveling in vacuum. Now we will concern ourselves with neutrino oscillations in matter.
+So far, we have discussed neutrinos traveling in vacuum. Now we will concern ourselves with neutrino oscillations in matter.
 The possible interactions are shown in Fig.~\ref{fig:w_and_z}. The left panel shows that the only flavor that can undergo charged current (CC) 
 interactions are the electron flavor. This is because the CC interaction requires a neutrino with flavor $\alpha$ to interact with its charged lepton
-partner $\alpha$. Since the Earth doesn't consist of any muons or tau particles, the $\nu_\mu$ and $\nu_\tau$ have no charged leptons to undergo CC interactions with. 
+partner $\alpha$. Since the Earth does not consist of any muons or tau particles, the $\nu_\mu$ and $\nu_\tau$ have no charged leptons with which they can undergo CC interactions. 
 The right panel shows any neutrino flavor interaction via the neutral current (NC) with matter, mediated by the neutral $Z$ boson. The Earth is entirely composed
@@
 \end{align}
-In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  is a common term to all flavor states, and does not affect the probability. It can be rotated away.
+In this form, we see that the term $p + \frac{m^2_1}{2E} + V_{NC}$  is a common term to all flavor states and does not affect the probability. It can be rotated away.
 Thus
@@
 For $N_e = 0$, i.e. in vacuum, these probabilities are identical to the ones that we analytically derived in Eq.~\ref{eq:Pab}.
-For matter oscillations with $N_e \neq 0$, we do have closed form solutions, but they are not considered further here.
+For matter oscillations with $N_e \neq 0$, we do have closed-form solutions, but they are not considered further here.
 
@@
 traveling 12000 km. The red line is the vacuum oscillation, while the black line is the matter oscillation, traversing through the 
-matter density profile of the Earth. We see that the matter effects are more for some energies, and less for others. At energies 
+matter density profile of the Earth. We see that the matter effects are more for some energies and less for others. At energies 
 above $\SI{10}{\GeV}$, the matter effects are small for $\Pmm$ and $\Pmt$, while they heavily deviate for single-digit \si{\GeV} energies.
@@
 % TODO: segue into 2gen
-We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form, and start simplifying:
+We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form and start simplifying:
 
@@
 \end{align}
-Eq.~\ref{eq:eff_theta} has a pole at %TODO: write more
+Eq.~\ref{eq:eff_theta} has a pole at
 \begin{align}\label{eq:MSW}
@@
 still valid for the full three neutrino oscillations. We previously saw that the oscillation amplitudes were entirely dependant on
-the mixing angles, and the oscillation frequencies were entirely dependant on the squared-mass difference along with energy, and trajectory. After 
+the mixing angles, and the oscillation frequencies were entirely dependant on the squared-mass difference along with energy and trajectory. After 
 introducing the matter potentials, we now see that the matter effect mixes the mixing matrix elements with the masses and the energy.
@@
 In Fig.~\ref{fig:2_vs_3}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
-traveling 12000 km. The black lines are the probabilities of $\nm$ oscillation, after it has traversing through the diameter of the Earth.
+traveling 12000 km. The black lines are the probabilities of $\nm$ oscillation after it has traversed through the diameter of the Earth.
 The red lines are the probabilities of $\nm$ oscillation, but in the two-neutrino picture using Eq.~\ref{eq:2gen}. So in the left-most panel,
@@
 The pattern is similar to when we compared $3\nu$ matter and vacuum oscillations: at $\SI{10}{\GeV}$, the two pictures converge.
-It is evident that the full $3\nu$ picture is required for single-digit \si{\GeV} energies, and that mixings between all three flavors here are 
+It is evident that the full $3\nu$ picture is required for single-digit \si{\GeV} energies and that mixings between all three flavors here are 
 abundant. Increasing with energy, however, the influence of the $\nu_1$ mass eigenstate on the probabilities is reduced.
 Thus, we are able to approximate resonant behavior as described in Eq.~\ref{eq:MSW} above $\SI{100}{\GeV}$ by only considering 
-mixing between two neutrino species. We will utilize this observation later on to study a particular resonance in the \si{\TeV} range.
+mixing between two neutrino species. We will utilize this observation later on, to study a particular resonance in the \si{\TeV} range.

### 2021-12-14 thesis/tex/sterileResults.tex
update

@@
 our theoretical simulations $N^\text{th}_{ij}$ agree with the data $N^\text{data}_{ij}$ within the error bounds provided by $\sigma_a,\sigma_b,$ and $f$.
-We then select the set of $\chi^2$ values which are the smallest and our allowed parameters are then their associated $\hat{\theta}$.
+We then select the smallest set of $\chi^2$ values, and our allowed parameters are then their associated $\hat{\theta}$.
 We then translate the $\chi^2$ distribution by subtracting the best-fit point, and analyze $\Delta \chi^2 = \chi^2 - \chi^2_{min}$.
@@
 Wanting to investigate the effect of $\theta_{34}$, we also simulated the 3+1 hypothesis using $\theta_{24} = \theta_{34}$. However, we did not see 
-a difference in the exclusion regions compared to the regions when $\theta_{34} = 0$. Thus, we conclude that on our work, IceCube was not able to 
+a difference in the exclusion regions compared to the regions when $\theta_{34} = 0$. Thus, we conclude that in our work, IceCube was not able to 
 distinguish any effect due to the $\theta_{34}$ parameter. However, since our dataset only included muon track events in the \SIrange{0.5}{10}{\TeV} range,

### 2021-12-14 thesis/tex/sterileTheory.tex
update

@@
-%\input{commands}
-%\begin{document}
 \section{The Sterile State}\label{sec:anomalies}
@@
 Keeping in mind that the event count from Eq.~\ref{eq:ICevents} scales as $E^{-1.7}$,
-signals at higher energies will be more difficult to detect. Since higher values of $\dm[41]$ shifts the $\Pamam$ resonance peak to higher 
+signals at higher energies will be more difficult to detect. Since higher values of $\dm[41]$ shift the $\Pamam$ resonance peak to higher 
 energies, high $\dm[41]$ values will be harder to rule out because the event count is already lower, as compared to energies 
-at single-digit \si{\TeV} values. There is then a range of parameters, in which our detector will 
+at single-digit \si{\TeV} values. There is then a range of parameters with which our detector will 
 be able to distinguish between the two hypotheses. Using the two-neutrino approximation\footnote{In this approximation, we only consider mixing between $\nm$ and $\ns$, essentially a `1+1' picture.}, 

### 2021-12-14 thesis/tex/ICtheory.tex

@@
     \includegraphics[scale=0.4]{figures/IC_data.pdf}
-    \caption{IceCube track events from~\cite{IC2020}, displaying the $E^-{-1.7}$ drop-off in event count.}\label{fig:IC_data}
+    \caption{IceCube track events from~\cite{IC2020}, displaying the $E^{-1.7}$ drop-off in event count.}\label{fig:IC_data}
 \end{figure}

### 2021-12-14 thesis/tex/oscillations.tex

@@
 
-We construct the PMNS matrix by parametrizing it as
+We construct the PMNS matrix by parametrizing it with the rotation matrices $R_{ij}$ and a matrix $P_{Maj}$ as
 \begin{align}\label{PMNS_def}
@@
 \end{align}
-
 This form elucidates an important aspect of neutrino oscillations. The mixing matrix elements
@@
 In Fig.~\ref{fig:vac_vs_matter}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
-traveling 12000 km. The red line is the vacuum oscillation, while the black line is the matter oscillation, traversing through the 
-matter density profile of the Earth. We see that the matter effects are more for some energies and less for others. At energies 
+traveling 12742 km. The red line is the vacuum oscillation, while the black line is the matter oscillation, traversing through the 
+matter density profile of the Earth. We see that the matter effects are more for some energies, and less for others. At energies 
 above $\SI{10}{\GeV}$, the matter effects are small for $\Pmm$ and $\Pmt$, while they heavily deviate for single-digit \si{\GeV} energies.
@@
 \end{align}
-% The rotation matrices $R_{ij}$ that constitute $U$ according to Eq.~\eqref{PMNS_def} can be simplified.
-The rotation $R_{13}$ will not affect our mass matrix, since the former acts in the $1-3$ plane, and the latter sits in the $1-2$ plane.
-Thus, the reduced mass matrix $\mathbb{M}_{12}$ commutes with $R_{13}$.
-Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathbb{M}_{12}$.
-% Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
-% \begin{align}
-%     \commutator{R_{ij}}{R_{kl}} = R_{ij}R_{kl} - R_{kl}R_{ij} = 0\,.
-% \end{align}
-% Thus,
-% \begin{align}
-%     U \mathbb{M}_{12} U^\dagger &=
-%     R_{23}R_{13}R_{12} \mathbb{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
-%     &= R_{12}R_{23}R_{13} \mathbb{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
-%     &= R_{12}\mathbb{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
-% \end{align}
-% And due to the fact that the rotation matrices are unitary,
-% \begin{align}
-%     R\,R^\dagger = \mathbb{I}\,,
-% \end{align}
-% we have that 
-% \begin{align}
-%     U \mathbb{M}_{12} U^\dagger &= R_{12}\mathbb{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
-%     &= R_{12}\mathbb{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
-%     &= R_{12}\mathbb{M}_{12}  R_{12}^\dagger\,.
-% \end{align}
-% We have now completely removed the dependence of the mixing angle between the $\nu_1$ and $\nu_3$ mass eigenstates, $\theta_{13}$, and the dependece of the mixing angle between the $\nu_2$ and $\nu_3$ mass eigenstates, $\theta_{23}$.
-% We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
-% \begin{align}
-%     U &= R_{12}
-% \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix} 
-% \end{align}
-
-% Let us return to the Hamiltonian with our two-neutrino mixing matrix. We have 
-% \begin{align}
-%     H_F
-%         &= \frac{1}{2E}\left[R_{12} \begin{pmatrix}
-%             0 & 0 & 0 \\
-%             0 & \dm_{21} & 0 \\
-%             0 & 0 & 0
-%         \end{pmatrix} R_{12}^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
-%             1 & 0 & 0 \\
-%             0 & 0 & 0 \\
-%             0 & 0 & 0
-%         \end{pmatrix} \nonumber \\
-%         &= \frac{1}{2E}\left[\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}  \begin{pmatrix}
-%             0 & 0 & 0 \\
-%             0 & \dm_{21} & 0 \\
-%             0 & 0 & 0
-%         \end{pmatrix} \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e \begin{pmatrix}
-%             1 & 0 & 0 \\
-%             0 & 0 & 0 \\
-%             0 & 0 & 0
-%         \end{pmatrix}\,. 
-% \end{align}
-% TODO: segue into 2gen
-We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form and start simplifying:
+We can reduce this down to two dimensions by extracting the upper-left block of all matrices\footnote{Or, following the method of the derivation of the Hamiltonianin the three-
+neutrino picture, take U as one two-dimensional rotation matrix.}. We now have the Hamiltonian in a two-dimensional form, and start simplifying:
 
@@
 In Fig.~\ref{fig:2_vs_3}, we have plotted the oscillation probabilities for an incoming $\nm$ with \si{\GeV} energy,
-traveling 12000 km. The black lines are the probabilities of $\nm$ oscillation after it has traversed through the diameter of the Earth.
+traveling through the entire Earth diameter. The black lines are the probabilities of $\nm$ oscillation, after it has traversing through the diameter of the Earth.
 The red lines are the probabilities of $\nm$ oscillation, but in the two-neutrino picture using Eq.~\ref{eq:2gen}. So in the left-most panel,

### 2021-12-14 thesis/tex/abstract.tex
update

@@
 
-Firstly, we consider the sterile neutrino, which have no interactions described by the Standard Model. We examine the effect of this 
+Firstly, we consider the sterile neutrino, which has no interactions described by the Standard Model. We examine the effect of this 
 new fermion on the neutrino oscillation probabilities, and present what could be a detectable signal in the \si{\TeV} energy range.
 Secondly, we consider interactions beyond the Standard Model, possibly stemming from a higher-order theory.
-We show how the parameters of these Non-Standard Interactions (NSI) can modify the oscillation probabilities, and within which energy range we expect to be able to discern this signal.
+We show how the parameters of these Non-Standard Interactions (NSI) can modify the oscillation probabilities and within which energy range we expect to discern this signal.
 We use data from and simulate event counts in two Cherenkov detectors: IceCube and DeepCore. Moreover, we generate data and simulate a proposed upgrade of the DeepCore detector: PINGU.
@@
 a p-value of $20\%$, which is not statistically significant. Hence, we found no evidence of a sterile neutrino in IceCube data. 
-Moreover, were unable to distinguish a signal from $\theta_{34}$ in our IceCube simulation.
-We obtain stringent bounds on the NSI parameters, and compare those to previous results in literature. We show that PINGU is expected to further narrow the bound 
-on $\emt$, especially the considering a joint analysis together with IceCube and DeepCore. Finally, we see that an anti-correlation between 
+Moreover, we were unable to distinguish a signal from $\theta_{34}$ in our IceCube simulation.
+We obtain stringent bounds on the NSI parameters and compare those to previous results in literature. We show that PINGU is expected to narrow the bound further 
+on $\emt$, especially by considering a joint analysis with IceCube and DeepCore. Finally, we see that an anti-correlation between 
 $\eem$ and $\eet$ at probability level was propagated down to event level, which we expect to be observable by PINGU.
@@
 \addcontentsline{toc}{section}{Sammanfattning}
-Misslyckandet med partikelfysikens s.k. standardmodell att förutsäga neutrinomassor tvingar oss att ändra den. Vi har ingen anledning att tro att
-de interaktioner som för närvarande beskrivs av standardmodellens symmetrigrupp är hela bilden, och vi bör inte heller förvänta oss att antalet fermioner som hittils observerats.
-I detta examensarbete undersöker vi två modifieringar av standardmodellen och undersöker om dessa ändringar är förenliga med uppmätta data.
+Misslyckandet med partikelfysikens s.k. standardmodell att förutsäga neutrinomassor uppmanar oss att förbättra den. Vi har ingen anledning att tro att
+de interaktioner som för närvarande beskrivs av standardmodellens symmetrigrupp är hela bilden, och inte heller vi bör förvänta oss att antalet fermioner som hittils observerats
+är korrekt.
+I detta examensarbete undersöker vi två förlängningar av standardmodellen och undersöker om dessa är förenliga med uppmätta data.
 Först introducerar vi den sterila neutrinon, som inte har några interaktioner som beskrivs av standardmodellen. Vi undersöker effekten av denna
@@
 Vi visar hur NSI-parametrarna kan modifiera oscillationssannolikheterna, och inom vilka energiområden vi förväntar oss att urskilja denna signal.
+Vi simulerar två Cherenkov-detektorer: IceCube och DeepCore. Dessutom presenterar vi resultat som vi
+kan förvänta oss att se i en föreslagen detektor: PINGU.
 
-Vi samlar in data från och simulerar två Cherenkov-detektorer: IceCube och DeepCore. Dessutom presenterar vi resultat som vi
-kan förvänta sig att se i en kommande uppgradering av DeepCore-detektorn: PINGU.
-
-Vi får resultat som indikerar att den aktuella 3+0-hypotesen överensstämmer med IceCube-data, med bästa anpassningsvärden
-$\dm[41] = \SI{0.01}{\eV^2}$ och $\theta_{24} = 0.67 $ med
-ett p-värde på $33\%$. Vi kunde inte skilja en signal från $\theta_{34}$.
-Vi erhåller stringenta gränser för NSI-parametrarna och jämför dem med tidigare resultat. Vi visar att PINGU förväntas minska gränsen ytterligare
-hos $\emt$, särskilt genom att gemensamt analysera resultaten med IceCube och DeepCore. Slutligen ser vi att en anti-korrelation mellan
-$\eem$ och $\eet$ på sannolikhetsnivå spreds ner till händelsenivå, vilket kommer att kunna observeras av PINGU.
+Genom att analysera spår från muoner i IceCube erhåller vi bästa anpassningsvärden $\dm[41] = \SI{0.01}{\eV^2}$ och $\theta_{24} = 0.67$ för vår sterila neutrinohypotes, med
+ett p-värde på $20\%$, vilket inte är statistiskt signifikant. Därför hittade vi inga bevis på en steril neutrino i IceCube-datat.
+Dessutom kunde vi inte urskilja en signal från $\theta_{34}$ i vår IceCube-simulering.
+Vi uppmäter snäva gränser för NSI-parametrarna och jämför dem med tidigare resultat i litteraturen. Vi visar att PINGU förväntas minska gränsen ytterligare
+på $\emt$, särskilt ifall man utformar en gemensam analys med IceCube och DeepCore. Slutligen ser vi att en anti-korrelation mellan
+$\eem$ och $\eet$ på sannolikhetsnivå spreds ner till händelsenivå, något som vi förväntar oss kan observeras av PINGU.
 
@@
 \addcontentsline{toc}{section}{Acknowledgements}
+First and foremost, I would like to thank my supervisor Prof. Sandhya Choubey for her extensive guidance and support throughout,
+and for the time she dedicated to my project.
+
+Secondly, I'm eternally grateful to everyone who contributed to making me be the person who I am. 
+My friends from KTH,
+mainly Svante, Anders, and Erik for making the final years -- in which I got to know you -- the best. 
+My best friends, Gilbert and Max, with whom I have shared countless of evenings filled with laughter and 
+great conversations. 
+My beloved girlfriend Moa, who I met at the start of this thesis. I have no idea if this would have been possible without you.
+
+Finally, my parents Anders and Helena, and also Ingemar. Thank you for nurturing my curiosity and for your unwavering belief in me.
+
+\vspace{9cm}
 The computations were enabled by resources provided by the Swedish

### 2021-12-14 thesis/tex/conclusion.tex
update

@@
 
-In Sec.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile, neutrino $\ns$~\cite{lsnd}.
+In Sec.~\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile, neutrino $\ns$~\cite{lsnd}.
 We modified the Hamiltonian to incorporate mixing with this new neutrino species, and saw how a \si{\eV^2} scale  $\ns$ with $\theta_{24}\neq 0$ affects the $\Pamam$ oscillation probability 

### 2021-12-14 thesis/tex/abstract.tex
update

@@
 \addcontentsline{toc}{section}{Sammanfattning}
-Misslyckandet med partikelfysikens s.k. standardmodell att förutsäga neutrinomassor uppmanar oss att förbättra den. Vi har ingen anledning att tro att
-de interaktioner som för närvarande beskrivs av standardmodellens symmetrigrupp är hela bilden, och inte heller vi bör förvänta oss att antalet fermioner som hittils observerats
+Misslyckandet med partikelfysikens så kallade standardmodell att förutsäga neutrinomassor uppmanar oss att förbättra den. Vi har ingen anledning att tro att
+de interaktioner som för närvarande beskrivs av standardmodellens symmetrigrupp fullständigt beskriver universum, och inte heller vi bör förvänta oss att antalet fermioner som hittils observerats
 är korrekt.
@@
 Vi simulerar två Cherenkov-detektorer: IceCube och DeepCore. Dessutom presenterar vi resultat som vi
-kan förvänta oss att se i en föreslagen detektor: PINGU.
+kan förvänta oss att se från en föreslagen detektor: PINGU.
 
 Genom att analysera spår från muoner i IceCube erhåller vi bästa anpassningsvärden $\dm[41] = \SI{0.01}{\eV^2}$ och $\theta_{24} = 0.67$ för vår sterila neutrinohypotes, med
-ett p-värde på $20\%$, vilket inte är statistiskt signifikant. Därför hittade vi inga bevis på en steril neutrino i IceCube-datat.
+ett p-värde på $20\%$, vilket inte är statistiskt signifikant. Därmed hittade vi inga bevis på en steril neutrino i IceCube-datat.
 Dessutom kunde vi inte urskilja en signal från $\theta_{34}$ i vår IceCube-simulering.
 Vi uppmäter snäva gränser för NSI-parametrarna och jämför dem med tidigare resultat i litteraturen. Vi visar att PINGU förväntas minska gränsen ytterligare
-på $\emt$, särskilt ifall man utformar en gemensam analys med IceCube och DeepCore. Slutligen ser vi att en anti-korrelation mellan
+hos $\emt$, särskilt ifall man utformar en gemensam analys med IceCube och DeepCore. Slutligen ser vi att en anti-korrelation mellan
 $\eem$ och $\eet$ på sannolikhetsnivå spreds ner till händelsenivå, något som vi förväntar oss kan observeras av PINGU.
@@
 Secondly, I'm eternally grateful to everyone who contributed to making me be the person who I am. 
+My parents Anders and Helena, and also Ingemar. Thank you for nurturing my curiosity and for your unwavering belief in me.
 My friends from KTH,
@@
 great conversations.
-My beloved girlfriend Moa, who I met at the start of this thesis. I have no idea if this would have been possible without you.
 
-Finally, my parents Anders and Helena, and also Ingemar. Thank you for nurturing my curiosity and for your unwavering belief in me.
+Finally, beloved girlfriend Moa, who I met at the start of this thesis. I have no idea if this would have been possible without you.
 

### 2021-12-15 thesis/tex/conclusion.tex
update, and removed files

@@
 We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. 
-We mentioned the Super-Kamiokande experiment and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}, in direct violation of the Standard Model. 
+We mentioned the Super-Kamiokande experiment and that their 1998 result found no other explanation than that $\nm$ oscillated~\cite{sk1998}, in direct violation of the Standard Model. 
 We saw that, by adding a right-handed neutrino field, neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 

### 2021-12-20 thesis/tex/SM.tex
update

@@
 \end{figure}
-\section{The Standard Model}\label{ch:SM}
+\section{The Standard Model. Figure adapted from a diagram made by Carsten Burgard.}\label{ch:SM}
 In order to describe the three quantizable forces of nature, we gather the mediators of each force -- the vector bosons -- into local (gauge) symmetry groups. 
@@
 \section{Mass Generation}
+In the following sections, the presentation is following the outline in~\cite{giunti}.
 In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.

### 2022-06-20 article_v2/tex/SM.tex
article v2

--- 2021-12-14 thesis/tex/SM.tex
@@
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/SM_figure.pdf}
-\end{figure}
 \section{The Standard Model}\label{ch:SM}
@@
 Since the vector bosons are represented by the generators, they are uniquely determined by the symmetry group. However, the scalar boson(s) and fermions are free as long as they
-belong to representations of the symmetry group.
-By this construction, modifications to fermions rather than bosons are generally easier to make, allowing us to propose amendments to the model.
-Even the
-number of fermions must be experimentally verified and can be altered from a phenomenological standpoint. In this work,
-we will use this leniency to introduce a new particle and examine to which extent 
-these modifications might be supported by experimental evidence.
-Moreover, we will examine the possibility of adding a new completely new force, which manifests itself as modifications to the neutrino-matter interactions.
-
-\section{Mass Generation}
-In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermion's right and left-handed components.
-All neutrinos are left-handed, and all antineutrinos are right-handed~\cite{giunti}. This observational fact is reflected in the 
-left-handed lepton doublet and right-handed lepton singlet
-
-\begin{align}
-    L^\prime_{\alpha L} = \begin{pmatrix}
-            \nu^\prime_{\alpha L} \\
-        \alpha^\prime_{L} 
-    \end{pmatrix}\,, \quad
-    \ell^\prime_{\alpha R} =
-    \alpha^\prime_{R} \,,            
-\end{align}
-where $\alpha \in \{e,\mu,\tau\}$, and the primes denotes that the fields do not have definite masses.
-The essential part here is that $\nu^\prime_{\alpha R}$ is missing from the right-handed lepton singlet.
-Thus, the neutrino fields do not pick up a Yukawa coupling, 
-and will not undergo the Higgs mechanism, which leaves them massless.
-Moreover, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
-generated at loop level because any such attempt will violate the total lepton number by two units.
-In order to keep our theory renormalizable, we have one option left if we want to generate neutrino masses: introducing right-handed neutrino and left-handed antineutrino fields.
-
-We consider a right-handed neutrino field, $\nu^\prime_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
-left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the Standard Model symmetry 
-group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$.
-
-We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa part of the interaction Lagrangian
-\begin{align} 
-    \mathcal{L}_{int} \subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[ \bar{\ell}^{\prime}_{\alpha L} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \bar{\nu}_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,,
-\end{align}
-where $v$ is the Higgs vacuum expectation value, $H$ the Higgs field, $\ell_{\alpha L}^\prime (\ell_{\beta R}^\prime)$ the left (right) handed charged lepton field, and summation over the lepton indices $\alpha,\beta$ is implied.
-$Y_{\alpha \beta}^{\prime \ell}$ are the charged lepton Yukawa couplings, and $\nu^\prime_{\alpha L}(\nu^\prime_{\beta R})$ are the left (right) handed neutrino fields .
-Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, as emphasized with their prime. 
-This can be remedied by diagonalizing $Y^{\prime \ell}$  with a biunitary transformation
-\begin{align}
-    V_{ L}^{\ell \dagger} Y^{\prime \ell} V_{ R}^{\ell}=Y^{\ell} \,.
-\end{align}
-where $V^\ell_L$ and $V^\ell_R$ are two unitary matrices.
-Similarly, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. 
-Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
-While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
-This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement for neutrino flavor eigenstates to have a definite mass. 
-The flavor of a neutrino is then -- by definition -- the flavor of the associated charged lepton. 
-This fact is denoted as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
-
-So, let the neutrino field in the mass basis have components with Latin numerals to distinguish them from the flavour components, i.e 
-\begin{align}\label{eq:nu_rotation} 
-    \nu_{k} =  V_{k\beta}^{\nu \dagger} \nu_{\beta}^\prime\,.
-\end{align}
-The diagonalized Lagrangian now takes the form 
-\begin{align}
-    \mathcal{L}_{int} &\subseteq -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \bar{\nu}_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}
-    + \bar{\nu}_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
-    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]
-\end{align}
-By construction, $Y^\ell$ and $Y^\nu$ are diagonal, so we write their components as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
-\begin{align}\label{eq:L_H}
-    \mathcal{L}_{int} 
-    &\subseteq-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell} \delta_{\alpha \beta} \ell_{\beta R} + \bar{\nu}_{k L} y_{k}^{\nu} \delta_{k j} \nu_{j R}\right] \nonumber \\
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell}  \ell_{\alpha R} + \bar{\nu}_{k L} y_{k}^{\nu} \nu_{k R}\right] \nonumber \\
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}  \bar{\ell}_{\alpha L}\ell_{\alpha R} +  y_{k}^{\nu}\bar{\nu}_{k L} \nu_{k R}\right] 
-\end{align}
-Now, by the introduction of the right-handed field $\nu_R$, the Dirac neutrino field is
-\begin{align}
-    \nu_k = \nu_{kL} + \nu_{kR}\,.
-\end{align}
-Multiplying $\nu_k$ with its conjugate $\bar{\nu}_k$, we get 
-\begin{align}
-    \bar{\nu}_k \nu_k 
-    & = \bar{\nu}_{k L} \nu_{k L} +\bar{\nu}_{k R}\nu_{k L} + \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k R} \nonumber \\
-    & = \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k L} \nonumber \\
-    & = \bar{\nu}_{k L}\nu_{k R} + \t{h.c.}
-\end{align}
-The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and multiplying the Higgs vacuum expectation value $v$ into the fields gives us
-\begin{align}
-    \mathcal{L}_{H} 
-    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}   \bar{\ell}_\alpha \ell_\alpha  +  y_{k}^{\nu} \bar{\nu}_k \nu_k \right] \nonumber \\
-    &=- \frac{y_{\alpha}^{\ell} v}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha   -  \frac{ y_{k}^{\nu} v}{\sqrt{2}} \bar{\nu}_k \nu_k  - \frac{y_{\alpha}^{\ell}}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha H  -  \frac{ y_{k}^{\nu}}{\sqrt{2}} \bar{\nu}_k \nu_k H\,.
-\end{align}
-Thus, this extension to the SM generates by the Higgs mechanism neutrino masses with terms
-\begin{align}
-    m_k = \frac{y_k^\nu v}{\sqrt{2}}\,,
-\end{align}
-where the Yukawa couplings $y^\nu_k$ needs to be experimentally determined.
+belong to representations of the symmetry group. By this construction, modifications to fermions rather than bosons are generally easier to make, allowing us to propose amendments to the model. 
+We will use this leniency to will examine the possibility of adding a new completely new interaction, which manifests itself as modifications to the neutrino-matter interactions.

### 2022-06-20 article_v2/tex/abstract.tex
article v2

--- 2021-12-14 thesis/tex/abstract.tex
@@
-\chapter*{Abstract}
+\section*{Abstract}
 \addcontentsline{toc}{section}{Abstract}
 
-The failure of the Standard Model of particle physics to predict neutrino masses invites us to amend it. We have no reason to believe that 
-the interactions currently described by the gauge group are the whole picture, nor should we expect that the number of fermions hitherto observed is correct.
-In this thesis, we explore two amendments to the Standard Model, and examine whether either of these are consistent with measured data.
-
-Firstly, we consider the sterile neutrino, which have no interactions described by the Standard Model. We examine the effect of this 
-new fermion on the neutrino oscillation probabilities, and present what could be a detectable signal in the \si{\TeV} energy range.
-Secondly, we consider interactions beyond the Standard Model, possibly stemming from a higher-order theory.
-We show how the parameters of these Non-Standard Interactions (NSI) can modify the oscillation probabilities, and within which energy range we expect to be able to discern this signal.
+We consider interactions beyond the Standard Model, possibly stemming from a higher-order theory.
+We show how the parameters of these Non-Standard Interactions (NSI) can modify the oscillation probabilities and within which energy range we expect to discern this signal.
 We use data from and simulate event counts in two Cherenkov detectors: IceCube and DeepCore. Moreover, we generate data and simulate a proposed upgrade of the DeepCore detector: PINGU.
 
-Using IceCube track events, we obtain best-fit values $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ for our sterile neutrino hypothesis at 
-a p-value of $20\%$, which is not statistically significant. Hence, we found no evidence of a sterile neutrino in IceCube data. 
-Moreover, were unable to distinguish a signal from $\theta_{34}$ in our IceCube simulation.
-We obtain stringent bounds on the NSI parameters, and compare those to previous results in literature. We show that PINGU is expected to further narrow the bound 
-on $\emt$, especially the considering a joint analysis together with IceCube and DeepCore. Finally, we see that an anti-correlation between 
+We obtain stringent bounds on the NSI parameters and compare those to previous results in literature. We show that PINGU is expected to narrow the bound further 
+on $\emt$, especially by considering a joint analysis with IceCube and DeepCore. Finally, we see that an anti-correlation between 
 $\eem$ and $\eet$ at probability level was propagated down to event level, which we expect to be observable by PINGU.
 
-\chapter*{Sammanfattning}
-\addcontentsline{toc}{section}{Sammanfattning}
-Misslyckandet med partikelfysikens s.k. standardmodell att förutsäga neutrinomassor tvingar oss att ändra den. Vi har ingen anledning att tro att
-de interaktioner som för närvarande beskrivs av standardmodellens symmetrigrupp är hela bilden, och vi bör inte heller förvänta oss att antalet fermioner som hittils observerats.
-I detta examensarbete undersöker vi två modifieringar av standardmodellen och undersöker om dessa ändringar är förenliga med uppmätta data.
-Först introducerar vi den sterila neutrinon, som inte har några interaktioner som beskrivs av standardmodellen. Vi undersöker effekten av denna
-nya fermion på neutrinoscillationssannolikheterna, och presentera vad som skulle vara en detekterbar signal i \si{\TeV}-området.
-Vidare introducerar vi en ny interaktion som vi kallar Icke-Standard Interaktioner (NSI), som möjligen härrör från en högre ordningens teori.
-Vi visar hur NSI-parametrarna kan modifiera oscillationssannolikheterna, och inom vilka energiområden vi förväntar oss att urskilja denna signal.
-
-Vi samlar in data från och simulerar två Cherenkov-detektorer: IceCube och DeepCore. Dessutom presenterar vi resultat som vi
-kan förvänta sig att se i en kommande uppgradering av DeepCore-detektorn: PINGU.
-
-Vi får resultat som indikerar att den aktuella 3+0-hypotesen överensstämmer med IceCube-data, med bästa anpassningsvärden
-$\dm[41] = \SI{0.01}{\eV^2}$ och $\theta_{24} = 0.67 $ med
-ett p-värde på $33\%$. Vi kunde inte skilja en signal från $\theta_{34}$.
-Vi erhåller stringenta gränser för NSI-parametrarna och jämför dem med tidigare resultat. Vi visar att PINGU förväntas minska gränsen ytterligare
-hos $\emt$, särskilt genom att gemensamt analysera resultaten med IceCube och DeepCore. Slutligen ser vi att en anti-korrelation mellan
-$\eem$ och $\eet$ på sannolikhetsnivå spreds ner till händelsenivå, vilket kommer att kunna observeras av PINGU.
-
-\chapter*{Acknowledgements}
-\addcontentsline{toc}{section}{Acknowledgements}
+\section*{Acknowledgements}
 The computations were enabled by resources provided by the Swedish

### 2022-06-20 article_v2/tex/conclusion.tex
article v2

--- 2021-12-14 thesis/tex/conclusion.tex
@@
-\chapter{Conclusion}\label{ch:conc}
-In this thesis, we have explored the potential of explaining new physics using detectors handled by the IceCube collaboration.
-We started off by introducing the Standard Model in Sec.~\ref{ch:SM}, and noted that it has several shortcomings. 
-We mentioned the Super-Kamiokande experiment and that their 1998 result found no other explanation than $\ne \to \nm$ mixing~\cite{sk1998}, in direct violation of the Standard Model. 
-We saw that, by adding a right-handed neutrino field, neutrino masses are generated by the Higgs mechanism, thus enabling neutrino oscillations to occur. 
-In Sec.~\ref{ch:oscillation}, we saw how the neutrino mixing matrix could be constructed and derived formulas describing neutrino oscillations in the two- and three-neutrino pictures.
-Adding a term for matter potential,
-we then arrived at a Hamiltonian that we used in the time-dependent Schrödinger equation to solve for the oscillation probabilities in matter.
-
-In Sec.\ref{sec:anomalies}, we learned that the LSND experiment found an excess in neutrino events that could be explained by a fourth, sterile, neutrino $\ns$~\cite{lsnd}.
-We modified the Hamiltonian to incorporate mixing with this new neutrino species, and saw how a \si{\eV^2} scale  $\ns$ with $\theta_{24}\neq 0$ affects the $\Pamam$ oscillation probability 
-by giving us a resonant \si{\TeV} $\anm$ disappearance.
-
-We then put the sterile neutrino aside and introduced Non-Standard Interactions (NSI) in Sec.\ref{sec:nsiTheory} as a possible example of new physics beyond the Standard Model.
+\section*{Conclusion}\label{ch:conc}
+We introduced Non-Standard Interactions (NSI) in Sec.~\ref{sec:nsiTheory} as a possible example of new physics beyond the Standard Model.
 We then studied the effects of NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
@@
 
-First, we described our method in testing the sterile neutrino hypothesis (3+1). We simulated the 86 string IceCube detector with track events, explained in Sec.\ref{ch:ICmethod}.
-After simulating event counts in Sec.~\ref{sec:sterileResults} for the $3+1$ hypothesis, we were able to find best-fit parameters of 
-$\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
-a p-value of $20\%$.
-Even though we found a best-fit for two parameters of the sterile neutrino, they are not statistically significant.
-Hence, we found no evidence of a sterile neutrino in IceCube data.
-We also investigated the case when $\theta_{24} = \theta_{34}$, which produced an identical contour as in the case with $\theta_{34}=0$. From this observation, 
-we concluded that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
-when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with the inclusion of cascade events from $\nt$, IceCube could be able to better observe 
-an impact of $\theta_{34}$. With these results, we then completely left the sterile neutrino behind.
-
-In Sec.~\ref{sec:constraining}, we moved on to the NSI parameter $\emt$ and its effect events captured by IceCube. 
+We simulated the 86 string IceCube detector with track events, explained in Sec.~\ref{ch:ICmethod}.
+In Sec.~\ref{sec:constraining}, we studied the NSI parameter $\emt$ and its effect events captured by IceCube. 
 Using a $\chi^2$ test, we found that the bound from IceCube on $\emt$ at 90 \% confidence level was 
@@
 In Sec.~\ref{ch:PINGUmethod} we described our method of simulating a proposed upgrade to the IceCube array: PINGU.
-Since PINGU is not yet live, we produced data for it assuming a standard $3+0$ hypothesis with parameters from~\cite{nufit}.
+Since PINGU is not yet live, we produced data for it assuming a standard $3$ neutrino hypothesis with parameters from~\cite{nufit}.
 After a $\chi^2$ analysis, we obtained the following constrains on the NSI parameters at 90\% confidence level:

### 2022-06-20 article_v2/tex/introduction.tex
article v2

--- 2021-12-14 thesis/tex/introduction.tex
@@
 We present how neutrino oscillations are modified by this hypothesized fourth neutrino and how these modifications would appear in IceCube if the particle is present in Nature. 
-In Section~\ref{sec:nsiTheory}, we completely set the sterile neutrino aside and instead turn to the interactions between neutrinos and matter. 
+In Section~\ref{sec:nsiTheory}, we set the sterile neutrino aside altogether and instead turn to the interactions between neutrinos and mattter. 
 We again amend the Standard Model by considering exotic interactions from a higher energy theory, manifesting themselves as sub-leading modifications to the matter potential. 

### 2022-06-20 article_v2/tex/nsiResults.tex
article v2

--- 2021-12-14 thesis/tex/nsiResults.tex
@@
 \section{The NSI Hypothesis}\label{sec:constraining}
-In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$. As we shall see, the impacts of NSI mainly manifesting 
+In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$. As we shall see, the impacts of NSI mainly manifest
 themselves at \si{\GeV} energies, causing us to bring back DeepCore and PINGU. We will consider the results obtained from these three detectors separately as well as jointly.
@@
 The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
-by the best and worst case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
+by the best and worst-case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
 no uncertainty scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.
@@
 This is because the `data' we generated during
-the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses, which include PINGU
 since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
@@
 results from~\cite{demidov} are have been obtained by including more systematic uncertainties, such as the spectral index, hadron production, and baryon resonance. 
-However, the overall flux normalization in~\cite{demidov} is 20\%, while we opted for a slightly higher figure of 25\% which could compensate for the exclusion of the 
+However, the overall flux normalization in~\cite{demidov} is 20\%, while we opted for a slightly higher figure of 25\%, which could compensate for the exclusion of the 
 statistical uncertainties mentioned.
@@
 assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
-number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
+number of expected events at the detector and illustrates the expected sensitivity of DeepCore for the NSI parameters.
 

### 2022-06-20 article_v2/tex/nsiTheory.tex
article v2

--- 2021-12-13 thesis/tex/nsiTheory.tex
@@
 In this sense, the Standard Model might be considered 
-an effective low energy theory, which is yields impressive results in some areas, but failing in others.
+an effective low energy theory, which is yields impressive results in some areas but fails in others.
 
@@
 of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
-possibility of additional interactions that can cause the flavor change. Moreover, since we have 6 NSI parameters, and the PMNS
-matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
-two of the three mixing angles, making the individual angles more inter-dependent than the NSI parameters, since combinations of them must satisfy the constraints of the matrix elements.
+possibility of additional interactions that can cause the flavor change. Moreover, since we have six NSI parameters, and the PMNS
+matrix is parametrized with only three parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
+two of the three mixing angles. This makes the individual angles more inter-dependent than the NSI parameters since combinations of them must satisfy the constraints of the matrix elements.
 
@@
 we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
-will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
+will be more apparent since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
 many oscillations have averaged out.
@@
 All other NSI parameters are fixed to zero.
-Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{eem_eet_probs}.}
+Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{fig:eem_eet_probs}.}
         \label{fig:Pee_eet_probs}
@@
 we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
-in the $\Pme$ probability. This indicating that the NSI parameters are much more influential at these energies, and that we should be able to 
+in the $\Pme$ probability. This indicates that the NSI parameters are much more influential at these energies, and that we should be able to 
 constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.

### 2022-10-22 article/article.tex
update

@@
-\documentclass[draft=True]{revtex4-2}
+\documentclass{article}
 \newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
@@
 \newcommand{\nm}{\nu_\mu}
+\newcommand{\ab}{\alpha\beta}
 \newcommand{\nt}{\nu_\tau}
@@
 
+\newcommand{\Pee}{P_{e  e}}
+\newcommand{\Pem}{P_{e  \mu}}
+\newcommand{\Pet}{P_{e  \tau}}
+
+\newcommand{\Pme}{P_{\mu  e}}
+\newcommand{\Pmm}{P_{\mu\mu}}
+\newcommand{\Pmt}{P_{\mu  \tau}}
+
+\newcommand{\Pte}{P_{P_{\tau e}}}
+\newcommand{\Ptm}{P_{\tau  \mu}}
+\newcommand{\Ptt}{P_{\tau  \tau}}
+
+\newcommand{\Paeae}{P_{\bar{e}  \bar{e}}}
+\newcommand{\Paeam}{P_{\bar{e}  \bar{\mu}}}
+\newcommand{\Paeat}{P_{\bar{e}  \bar{\tau}}}
+
+\newcommand{\Pamae}{P_{\bar{\mu}  \bar{e}}}
+\newcommand{\Pamam}{P_{\bar{\mu}  \bar{\mu}}}
+\newcommand{\Pamat}{P_{\bar{\mu}  \bar{\tau}}}
+
+\newcommand{\Patae}{P_{\bar{\tau}  \bar{e}}}
+\newcommand{\Patam}{P_{\bar{\tau}  \bar{\mu}}}
+\newcommand{\Patat}{P_{\bar{\tau}  \bar{\tau}}}
+
 \usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
@@
 \begin{document}
-\section{Formalism of non-standard interactions}
+\section{Formalism of non-standard interactions}\label{sec:intro} %OK
 Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
@@
 \begin{align} \label{eq:epsilon}
-    \epsilon_{\alpha\beta} &= \sum_{f,X} \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
-                           &= \epsilon_{\alpha\beta}^{eV} + 3\,\epsilon_{\alpha\beta}^{uV} + 3\,\epsilon_{\alpha\beta}^{dV}
+    \epsilon_{\alpha\beta} &= \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
+                           &= \sum_X \epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})
 \end{align}
@@
 After this, we are ready to study the NSI effect on probability level.
-%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?
 
-\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
+\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects} %OK
 % Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
@@
 % while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
-%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
+
+The atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
+NSI parameters to constrain from muon events. As we will see, $\eem$ is also a good candidate to constrain, albeit a weaker one.
+
+In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
+for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
+amplitude nor frequency of the probabilities. Instead, it seems to stretch or compress the oscillations. Since the 
+only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
+$\nm$ with positive $\epsilon_{\alpha\beta}$ is identical to the probability for $\anm$ with negative $\epsilon_{\alpha\beta}$. Thus, the dashed line 
+in the right panel not only shows the survival probability for $\anm$ with $\emt=0.02$, but also the survival probability for $\nm$ with $\emt=-0.02$.
+Hence, we note that $\emt > 0$ stretches (compresses) $\Pmm$ for neutrinos (antineutrinos), while $\emt < 0$ compresses (stretches) $\Pmm$ for neutrinos (antineutrinos).
+
+The value of $\ett$ affects neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
+to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
+we see that even though we let $\ett$ take 2.5 times the value of $\emt$, its effect on $\Pmm$ is smaller.
+The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent
+constraint due to the weakness of the effect compared to $\emt$.
+
+Thus, we will use IceCube to constrain $\emt$ only.
+
+Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
+In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
+in the DeepCore region of rapid oscillations, where mixing is more violent. 
 \begin{figure}
+    \begin{center}
+        \includegraphics[width=0.99\textwidth]{figures/Pmm_emt_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/Pmm_ett_probs.pdf}
+        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\emt = 0.02$.
+All other NSI parameters are fixed to zero.
+In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$.
+At \si{\TeV} energies, both probabilities simply get shifted down, resulting in a net reduction of track events.
+        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\ett = 0.05$.
+All other NSI parameters are fixed to zero.
+$\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study.
+However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
+        \label{fig:emt_ett_probs}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=0.99\textwidth]{figures/eem_probs.pdf}
+        \includegraphics[width=0.99\textwidth]{figures/eet_probs.pdf}
+        \caption{Muon neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$.
+\emph{Top panel:} $\eem = 0.2$.
+All other NSI parameters are fixed to zero.
+Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}.
+At \si{\TeV}, the probability is shifted down, just as with $\emt$.
+        \emph{Bottom panel:} $\eet = 0.2$.
+All other NSI parameters are fixed to zero.
+Here, we see a very weak shifting and a $\nm$ weaker dip at low \si{\GeV}, and again, no visible effect at \si{TeV} energies.
+}
+        \label{fig:eem_eet_probs}
+    \end{center}
+\end{figure}
+
+\begin{figure}% TODO: check if this is redundant
    \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
    \caption{}\label{fig:nsi_probs}
+\end{figure}
+
+The effect of NSI on the DeepCore event count has been previously discussed in~\cite{smirnovNSI}, while the NSI effect 
+in PINGU has been studied in~\cite{choubey2014, ohlsson2013}.
+Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
+we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
+will be more apparent since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
+many oscillations have averaged out.
+
+Another feature of our DeepCore study includes the fact that we now have access to cascade events, in which $\ne$ and $\nt$ are more abundant.
+Thus, we are no longer constrained to the $\mu$ channel alone, but we can now find interesting features in the other channels too. However, we 
+remember that the $\nm$ flux is still the most abundant.
+
+Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
+a clear signal when turning on $\eet$.
+
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
+        \caption{Electron neutrino and antineutrino survival probabilities for
+        $\ztrue = -1$ when $\eet = 0.2$.
+All other NSI parameters are fixed to zero.
+Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{fig:eem_eet_probs}.}
+        \label{fig:Pee_eet_probs}
+    \end{center}
+\end{figure}
+
+Fig.~\ref{fig:emt_ett_probs} shows that $\emt$ affects both $\Pmm$ and $\Pamam$ over the whole energy range. Since 
+IceCube also sees this, we hope to be able to boost the constraining of $\emt$ by combining the two experiments.
+
+Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
+a shallower dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.
+
+$\eem$ in Fig.~\ref{fig:eem_eet_probs} causes a weaker dip for both $\nm$ and $\anm$.
+
+For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
+see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
+have cascade events for DeepCore and PINGU. If we simulate 
+$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
+Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
+The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
+indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
+we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
+in the $\Pme$ probability. This indicates that the NSI parameters are much more influential at these energies, and that we should be able to 
+constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\textwidth]{figures/eem_eet_prob.pdf}
+    \caption{The quantity $\abs{P_{\mu e}^{NSI} - P_{\mu e}^{SI}}$ when we let $\eem$ and $\eet$ independently vary over
+    the range \{-0.3,0.3\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
+    a promising indication that constriction of $\eem$ and $\eet$ is possible using cascade events at these energies.}\label{fig:eem_eet_prob}
 \end{figure}
@@
    }\label{fig:flux_ratio}
-\end{figure}%TODO: make prettier cmap
+\end{figure}
 
-\section{Detector formalism}
+\section{Detector formalism} %OK
 The IceCube Neutrino Observatory is a gigaton Cherenkov detector located within Antarctic ice near the Geographic 
@@
 \begin{align}\label{eq:ICevents}
-   N_{ij} &= T\sum_\beta \int_{(\zreco)_j}^{(\zreco)_{j+1}} \dd \zreco \int_{\Ereco_{i}}^{\Ereco_{i+1}} \dd \Ereco \int_0^\pi R(\theta^R,\theta^T) \dd \ztrue \int_0^\infty \phi_\beta^\text{det}(\Etrue,\theta^R)  A^\text{eff}(\Etrue) R(\Ereco,\Etrue)
-   \dd \Etrue\,,
+    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
+    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
+    \,,
 \end{align}
-where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area obtained from~\cite{ICaeff}, in which $A^\text{eff}$ has been averaged over neutrinos and 
-anti-neutrinos. $R(x^R,x^T)$ is a resolution function, 
-which is responsible for the smearing between the reconstructed and true parameters $x^R$ and $x^T$, respectively. We assume a log-normal distribution, giving it the form 
+where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\theta_z^r$ the reconstructed 
+zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle of the incoming neutrino. 
+$E^r$ is the reconstructed energy, binned with index $j$. $R(\theta^r,\theta^t)$ is a zenith resolution function 
+that describes the relationship with the reconstructed and true zenith angles, specific to the 86-string configuration of IceCube.
+$R(E^r,E^t)$ is an energy resolution function 
+that describes the relationship with the reconstructed and true energies. $\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
+in accordance with Eq.~\ref{eq:propFlux}. The effective area $A^\text{eff}$ is binned and provided to us by the IceCube collaboration~\cite{ICaeff}.
+
+For the energy and zenith resolution functions, we assume a log-normal distribution, giving it the form 
 \begin{align}
-    R(x^R, x^T) = \frac{1}{\sqrt{2\pi} \sigma_{x^R}x^R} \exp\left[-\frac{(\log x^R-\mu(x^T))^2}{2\sigma_{x^R}^2}\right]\,.
+    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
 \end{align}
@@
 
-\subsection{DeepCore}\label{ch:DCmethod}
+\subsection{DeepCore}\label{ch:DCmethod} % OK
 We use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
@@
 
-\subsection{PINGU}\label{ch:PINGUmethod}
+\subsection{PINGU}\label{ch:PINGUmethod} % OK
 The methodology behind the PINGU simulations is the same as with our DeepCore study~\ref{ch:DCmethod}. We use the public Monte Carlo~\cite{PINGUdata}, 
 which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
-However, since no detector systematics is yet modeled for PINGU, we take the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error,
+However, since no detector systematics is yet modeled for PINGU,the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error,
 which we can scale at will.
@@
 $\log_{10}\Ereco \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
-We plot the normalized event differences $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for cascades and tracks in Fig.~\ref{fig:event_pulls}. %TODO:talk about this
+We plot the normalized event differences $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for cascades and tracks in Fig.~\ref{fig:event_pulls}.
 We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.
@@
 
-\subsection{Constraining the NSI parameters}\label{sec:constraining}
+\subsection{Constraining the NSI parameters}\label{sec:constraining} % Might need some shortening
 In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
 For our analyses, we define our $\chi^2$ as
-\begin{align} \label{eq:chisq}
+\begin{align}\label{eq:chisq}
     \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
@@
 where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
-$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.
+$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
+and $k$ denotes the event-type bin, i.e. track or cascade. 
+$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
+uncertainty.
 
 In our simulations of $N_{ijk}^\text{th}$, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, 
-except for $\dm$ and $\theta_{23}$
-which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.
+except for $\dm[31]$ and $\theta_{23}$
+which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV\squared} and \SIrange{40.1}{51.7}{\degree}, respectively~\cite{nufit}.
 
-We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
+We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.05$ as the zenith angle slope error~\cite{hondapaper}. 
 The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
@@
 with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
+The detectors experience an uncorrelated systematic error, which comes from the muon background, 
+i.e. events misclassified as muons from 
+$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
+For IceCube events, we scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
+expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
+to be negligible~\cite{PINGUletter}.
 The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
@@
 
-We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
+We treat the uncorrelated systematic uncertainties differently for each detector. For IceCube, we set $\sigma_{ij}^\text{syst} = f\sqrt{N_{ij}^\text{data}}$.
 We consider best, normal, and worst-case scenarios in IceCube using
-$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$. %TODO: maybe source/justification for these values?
+$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$.
 For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
-muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
+muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.
 {\renewcommand{\arraystretch}{1.2}
 \begin{table}
+   \centering
    \begin{tabular}{lccc}
@@
 
-After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
-The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
+We let each of the four NSI parameters considered assume a value, while keeping the other three fixed at zero. We consider the following ranges of values for each parameter:
+\begin{align}
+   -0.07 \le &\, \ett \le 0.07 \nonumber \\
+   -0.03 \le &\, \emt \le 0.03 \nonumber \\
+   -0.3 \le &\, \eem \le 0.3 \nonumber \\
+   -0.3 \le &\, \eet \le 0.3 \nonumber \\
+\end{align}
+
+After the oscillation parameters $\dm[31]$ and $\theta_{23}$ have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
+The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
+by the best and worst-case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
+no uncertainty scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.
 
@@
 This is because the `data' we generated during
-the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
+the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses, which include PINGU
 since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
+Moreover, we see that we can expect PINGU to be sensitive to systematic uncertainty, especially when constraining $\eem$ and $\eet$ from the negative side.
 
@@
     \begin{center}
-      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
-      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+       \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
+       \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon.
+$\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI
        parameters not shown in each panel are fixed to zero. 
-      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}.}\label{fig:3D_NO}
+       IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
     \end{center}
@@
     \begin{center} 
-      \includegraphics[width=0.6\textwidth]{figures/PID_3D_emt.pdf}
+       \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
        \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
-    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
-    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
+     $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
+     parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.
+     The zones contain the three uncertainty scenarios considered, and we see that the inclusion of PINGU is expected 
+     to drastically make the bound on $\emt$ more stringent.
+     }\label{fig:IC_3D}
     \end{center}
@@
 
-{\renewcommand{\arraystretch}{1.3}
+ {\renewcommand{\arraystretch}{1.0}
   \begin{table}
     \begin{center}
-   \begin{tabular}{lcccccc}
-      \hline \hline
-      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
-      \hline & \multicolumn{6}{c}{IceCube}  \\
-      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
-      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
-      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] &  [-0.046, 0.054] &         [-0.065] &  [-0.049, 0.057] &          [-0.07] \\
-      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\
-      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] &  [-0.11, 0.094] &  [-0.20, 0.16] &   [-0.14, 0.11] &   [-0.23, 0.18] \\
-      $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] &   [-0.10, 0.11] &  [-0.19, 0.18] &  [-0.13, 0.13] &  [-0.23, 0.12] \\\\
-      &\multicolumn{6}{c}{IceCube + DeepCore}\\
-      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
+       \begin{tabular}{lcc}
           \hline
+          Parameter & Best 90\% CL & Best $3\sigma$\\
+          \hline & \multicolumn{2}{c}{IceCube}  \\
+          $\emt$ &  [-0.012, 0.011] &  [-0.017, 0.016] \\\\
+          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
+          $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
+          $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+          $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+          $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+          &\multicolumn{2}{c}{IceCube + DeepCore} \\
+          $\emt$ &  [-0.013, 0.0070] &  [-0.017, 0.013] \\
+          \hline
+          \vspace{2em}
+       \end{tabular}
+       \begin{tabular}{lcc}
+          \hline
+          Parameter & Baseline 90\% CL & Baseline $3\sigma$ \\
+          \hline & \multicolumn{2}{c}{IceCube}  \\
+          $\emt$ &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
+          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
+          $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
+          $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+          $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
+          $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
+          &\multicolumn{2}{c}{IceCube + DeepCore}\\
+          $\emt$ &  [-0.016, 0.0070] &  [-0.022, 0.016] \\
+          \hline
+          \vspace{2em}
+       \end{tabular}
+       \begin{tabular}{lcc}
+          \hline
+          Parameter & Worst 90\% CL & Worst $3\sigma$\\
+          \hline & \multicolumn{2}{c}{IceCube}  \\
+          $\emt$ &  [-0.018, 0.017] &  [-0.025, 0.024] \\\\
+          & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
+          $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
+          $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
+          $\eem$ &  [-0.11, 0.15] &  [-0.23, 0.24] \\
+          $\eet$ &   [-0.084, 0.15] &  [-0.188, 0.212] \\\\
+          &\multicolumn{2}{c}{IceCube + DeepCore}\\
+          $\emt$ &  [-0.018, 0.0070] &  [-0.024, 0.018] \\
           \hline
        \end{tabular}
+       \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}.
+$\dm[31]$ and $\theta_{23}$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
+Best, baseline, and worst refer to
+       the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
     \end{center}
-   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
-   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
  \end{table}
+
  \begin{table}
-   \begin{tabular}{lcccccc}
-      \hline \hline
-      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
-      \hline & \multicolumn{6}{c}{PINGU} \\
-      $\ett$ &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] \\
-      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
-      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] \\
-      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
-      & \multicolumn{6}{c}{DeepCore + PINGU} \\
-      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] &  [-0.038, 0.048] &  [-0.058, 0.067] &   [-0.039, 0.05] &          [-0.06] \\
-      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
-      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] &  [-0.071, 0.086] &  [-0.149, 0.141] &  [-0.082, 0.097] &  [-0.17, 0.16] \\
-      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] &  [-0.061, 0.103] &  [-0.131, 0.155] &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
-      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
-      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
+    \centering
+    \begin{tabular}{lcc}
        \hline
+       Parameter & Best 90\% CL & Best $3\sigma$\\
+       \hline & \multicolumn{2}{c}{PINGU} \\
+       $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
+       $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] \\
+       $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.138] \\
+       $\eet$ &  [-0.079, 0.098] &  [-0.148, 0.161] \\\\
+       & \multicolumn{2}{c}{DeepCore + PINGU} \\
+       $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
+       $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013] \\
+       $\eem$ &   [-0.060, 0.077] &  [-0.13, 0.13] \\
+       $\eet$ &  [-0.052, 0.095] &  [-0.11, 0.14] \\\\
+       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
+       $\emt$ &  [-0.0080, 0.0050] &  [-0.012, 0.011] \\
+       \hline
+       %\vspace{0.5em}
+    \end{tabular}
+    \begin{tabular}{lcc}
+       \hline 
+       Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
+       \hline & \multicolumn{2}{c}{PINGU} \\
+       $\ett$ &  [-0.046, 0.054] &  [-0.065, 0.073] \\
+       $\emt$ &   [-0.0090, 0.010] &  [-0.015, 0.018] \\
+       $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16] \\
+       $\eet$ &   [-0.10, 0.11] &  [-0.19, 0.18] \\\\
+       & \multicolumn{2}{c}{DeepCore + PINGU} \\
+       $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
+       $\emt$ &    [-0.010, 0.0060] &  [-0.016, 0.014] \\
+       $\eem$ &    [-0.071, 0.086] &  [-0.15, 0.14]  \\
+       $\eet$ &   [-0.061, 0.10] &  [-0.13, 0.16] \\\\
+       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
+       $\emt$ &  [-0.009, 0.0060] &  [-0.014, 0.012] \\
+       \hline
+       %\vspace{0.5em}
+    \end{tabular}
+    \begin{tabular}{lcc}
+       \hline 
+       Parameter & Worst 90\% CL & Worst $3\sigma$\\
+       \hline & \multicolumn{2}{c}{PINGU} \\
+       $\ett$ &  [-0.049, 0.057] &   [-0.07, 0.078] \\
+       $\emt$ &   [-0.01, 0.011] &   [-0.017, 0.02] \\
+       $\eem$ &   [-0.137, 0.11] &   [-0.228, 0.18] \\
+       $\eet$ &  [-0.132, 0.125] &  [-0.226, 0.196] \\\\
+       & \multicolumn{2}{c}{DeepCore + PINGU} \\
+       $\ett$ &   [-0.039, 0.050] &    [-0.060, 0.070] \\
+       $\emt$ &  [-0.011, 0.0070] &  [-0.017, 0.015] \\
+       $\eem$ &  [-0.082, 0.097] &  [-0.168, 0.16] \\
+       $\eet$ &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
+       & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
+       $\emt$ &   [-0.010, 0.0060] &  [-0.016, 0.013] \\
        \hline
     \end{tabular}
-   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
+    \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.
+$\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
+    Best, baseline, and worst refer to 
     the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
@@
             \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
-           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
+            \cline { 2 - 4 } Parameter & $\dm[31]$ & $\theta_{23}$  & $\epsilon$  \\
             \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
@@
     \end{center}
-   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
+    \caption{Best fit points for $\dm[31]$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
     degrees, respectively.}\label{table:bestfit}
  \end{table}
-\newpage
+
+ We compare our results to a similar analysis performed on the same DeepCore dataset in~\cite{demidov}. In that publication, 
+ the constraints found at 90\% CL were 
+ \begin{align}\label{eq:demidov}
+    -0.055 <&\, \ett < 0.056 \nonumber \\
+    -0.023 <&\, \emt < 0.016 \nonumber \\
+    -0.21 <&\, \eem < 0.20 \nonumber \\
+    -0.19 <&\, \eet < 0.20\,.
+ \end{align}
+ Comparing~\ref{eq:demidov} to our results from Table~\ref{table:IC_DC_results} at 90\% CL, namely
+ \begin{align}\label{eq:DC_results}
+    -0.054 <&\, \ett < 0.067 \nonumber \\
+    -0.029 <&\, \emt < 0.0070 \nonumber \\
+    -0.12 <&\, \eem < 0.15 \nonumber \\
+    -0.084 <&\, \eet < 0.15\,,
+ \end{align}
+ we see that our results for $\eem$, $\eet$ are more stringent, while the results for $\emt$ and $\ett$ are similar but more lenient. It is worth noting that the 
+ results from~\cite{demidov} are have been obtained by including more systematic uncertainties, such as the spectral index, hadron production, and baryon resonance. 
+ However, the overall flux normalization in~\cite{demidov} is 20\%, while we opted for a slightly higher figure of 25\%, which could compensate for the exclusion of the 
+ statistical uncertainties mentioned.
+
+ Using the baseline case of 3\% systematic uncertainty at 90\% CL, we find from Table~\ref{table:PINGU_joint_results}, that our predictions for the proposed PINGU detector are
+ \begin{align}\label{eq:P_results}
+    -0.049 <&\, \ett < 0.057 \nonumber \\
+    -0.010 <&\, \emt < 0.011 \nonumber \\
+    -0.137 <&\, \eem < 0.11 \nonumber \\
+    -0.132 <&\, \eet < 0.125\,,
+ \end{align}
+ which displays an improvement over the DeepCore results in Eq.~\ref{eq:DC_results}, except for $\eet$ which is worse.
+
+ Finally, the joint results for $\emt$ using IceCube and DeepCore from~\ref{table:PINGU_joint_results} at 90\% CL are
+ \begin{align}\label{eq:ID_result}
+    -0.016 <&\, \emt < 0.0070\,,
+ \end{align}
+ and when combining IceCube, DeepCore, and PINGU, the 90\% CL constraint on $\emt$ in our baseline scenario is predicted to be
+ \begin{align}\label{eq:PID_result}
+    -0.010 <&\, \emt < 0.0060\,,
+ \end{align}
+ which is more stringent for $\emt>0$ than the result in~\cite{deepcoreNSI}.
 
@@
     \begin{center}
-      \begin{subfigure}{0.38\textwidth}
+       \begin{subfigure}{0.44\textwidth}
           \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
@@
        \end{subfigure}
-      \begin{subfigure}{0.4\textwidth}
+       \begin{subfigure}{0.54\textwidth}
           \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
@@
      \end{center}
-   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}\label{fig:event_pulls} 
-\end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better
+    \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years of data. 
+    Each row has only one NSI non-zero parameter, with the first row having $\ett= -0.07$, second $\emt = -0.03$, third $\eem = -0.3$, and fourth $\eet = -0.3$.
+    We clearly see the increased statistics of the PINGU detector, especially in cascade events. The low values of $\ett$ and $\emt$ produce a weak pull in DeepCore,
+    while PINGU can be expected to observe multiple regions of strong pulls for $\emt$, $\eem$, and $\eet$.}\label{fig:event_pulls}
+ \end{figure}
 
-%TODO: subsection about comparison between different papers.
+ We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
+ assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
+ number of expected events at the detector and illustrates the expected sensitivity of DeepCore for the NSI parameters.
+
+ Now we will compare the probability plots with the final event counts in DeepCore. It is not enough to only study the effect at probability level, since that is in true quantities. 
+ Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets averaged out in the reconstruction, and not showing up at all in the data. 
+ In general, features showing at probability level are can be 
+ averaged out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.
+
+ The top right panel shows a surplus of DeepCore track events at \SIrange{20}{30}{\GeV} for through-going neutrinos when we turn on $\ett$.
+This is what we expected from the bottom right panel in Fig.~\ref{fig:emt_ett_probs}, where we saw that we had an increase in $\anm$ survival probability at \SIrange{20}{40}{\GeV}.
+
+ The third right panel shows the expected event pull for $\eem$.
+Comparing with the probabilities in Fig.~\ref{fig:eem_eet_probs}, we see that the surplus of the $\anm$ survival in the \SIrange{20}{30}{\GeV} and the deficit above \SI{40}{\GeV} is intact, while the \SI{10}{\GeV} $\nm$ deficit is completely averaged out.
+
+ There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI.
+So ideally, we would simulate a grid where all NSI parameters are allowed to vary,
+ but this is not feasible.
+Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$.
+We let $\ett=0$ because we saw that it did not influence the other parameters.
+ We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}.
+We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical.
+ Hence, we can see that no relationship exists between them.
+With $\eet - \eem$, however, the contours are assuming a different shape.
+The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
+ Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
+ to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$. This is consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}, from which we 
+ saw that $\eem$ and $\eet$ strongly affect $\Pme$ for single-digit \si{\GeV} energies.
 
  \begin{figure}
-   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
+    \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
+    \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
+    standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. We observe an anti-correlation between $\eem$ and $\eet$,
+    consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}.
+    The values of the standard oscillation parameters 
+    are taken from NuFit~\cite{nufit}.}\label{fig:PINGU_2D}
  \end{figure}
-\begin{figure}
-   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f5.pdf}
-\end{figure}
+
+\subsection{Conclusion}\label{sec:conclusion}
+We introduced Non-Standard Interactions (NSI) in Sec.~\ref{sec:intro} as a possible example of new physics beyond the Standard Model.
+We then studied the effects of NSI on the neutrino oscillation probabilities and saw that NSI effects other than those stemming from $\emt$ are not apparent in the \si{\TeV} region.
+Moreover, we saw in $\Pme$ that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
+We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions.
+
+We simulated the 86 string IceCube detector with track events, explained in Sec.~\ref{ch:ICmethod}.
+In Sec.~\ref{sec:constraining}, we studied the NSI parameter $\emt$ and its effect events captured by IceCube. 
+Using a $\chi^2$ test, we found that the bound from IceCube on $\emt$ at 90 \% confidence level was 
+\begin{align}
+    -0.015 <\,& \emt < 0.014\ \quad (90\% \text{ CL})
+\end{align}
+for our `baseline' case of 15\% uncorrelated systematic uncertainty.
+
+In Sec.~\ref{ch:DCmethod}, we moved on and explained our method of simulating a second detector, DeepCore.
+Armed with simulations possible for this detector, we then continued to explore the possibility of NSI, this time including both track and cascade events and a lower energy region.
+Using the $\chi^2$ test defined in Eq.~\ref{eq:chisq} and after marginalizing $\dm[31]$ and $\theta_{23}$ out, we found the following constraints on the NSI parameters at 90\% confidence level:
+\begin{align}
+    -0.054 <&\, \ett < 0.067 \nonumber \\
+    -0.029 <&\, \emt < 0.0070 \nonumber \\
+    -0.12 <&\, \eem < 0.15 \nonumber \\
+    -0.084 <&\, \eet < 0.15\ \quad (\text{all at }90\% \text{ CL})\,.
+ \end{align}
+We compared these constraints to literature and found that the bounds for $\eem$ and $\eet$ were more stringent than those obtained in~\cite{demidov}.
+Then, we did a joint $\chi^2$ test using simulated events from both IceCube and DeepCore. At 90\% confidence level, the bound of $\emt$ improved to
+\begin{align}
+    -0.016 <&\, \emt < 0.0070\ \quad (90\% \text{ CL})\,.
+ \end{align}
+
+In Sec.~\ref{ch:PINGUmethod} we described our method of simulating a proposed upgrade to the IceCube array: PINGU.
+Since PINGU is not yet live, we produced data for it assuming a standard $3$ neutrino hypothesis with parameters from~\cite{nufit}.
+After a $\chi^2$ analysis, we obtained the following constrains on the NSI parameters at 90\% confidence level:
+\begin{align}
+    -0.049 <&\, \ett < 0.057 \nonumber \\
+    -0.010 <&\, \emt < 0.011 \nonumber \\
+    -0.137 <&\, \eem < 0.11 \nonumber \\
+    -0.132 <&\, \eet < 0.125 \quad (\text{all at }90\% \text{ CL})\,.
+ \end{align}
+After that, we did a joint $\chi^2$ analysis combining IceCube, DeepCore and simulated PINGU events to further constrict $\emt$. The bound at 90\% confidence level obtained was
+\begin{align}
+    -0.010 <&\, \emt < 0.0060\,. \quad (90\% \text{ CL})
+ \end{align}
+
+We were then able to draw the conclusion that we expect PINGU to successfully be able to observe the impact of NSI.
+Moreover, a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
+will be able to constrain the parameters even further.
+We saw that can expect PINGU to be more sensitive to NSI effects than DeepCore.
+We were also able to see that when constraining $\eem$ and $\eet$ from the negative side,
+we can expect the result to be highly dependent on the systematic uncertainty of PINGU.
+
+Finally, we simulated the event count in PINGU, allowing $\emt$, $\eem$, and $\eet$ to vary, but setting $\ett=0$.
+After and marginalizing out $\dm[31]$, $\theta_{23}$, and $\emt$, we saw that the effect of $\eem$ and $\eet$ on $\Pme$ had indeed propagated through to the event count,
+manifesting as an anti-correlation between the $\eem$ and $\eet$ at both 90\% and $3\sigma$ confidence levels. No other pair of NSI parameters were observed to have 
+a significant correlation.
 \bibliographystyle{elsarticle-num}

### 2022-10-23 article/article.tex
update

@@
-\documentclass{article}
+\documentclass{revtex4-2}
+\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
+\usepackage[utf8]{inputenc}
+\usepackage{hyperref}
+
+% True/reconstructed parameters
+\newcommand{\z}{\ensuremath{\cos{(\theta_z)}}}
 \newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
 \newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{T})}}}
+\newcommand{\treco}{\ensuremath{\theta_z^{R}}}
+\newcommand{\ttrue}{\ensuremath{\theta_z^{T}}}
+\newcommand{\xreco}{\ensuremath{x^R}}
+\newcommand{\xtrue}{\ensuremath{x^T}}
+\newcommand{\Ereco}{E^{R}}
+\newcommand{\Etrue}{E^{T}}
+
+% NSI parameters
 \newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
@@
 \newcommand{\ep}{\ensuremath{\epsilon^\prime}}
+
+% Oscillation parameters
+\newcommand{\dm}{\Delta m^2_{31}}
+\newcommand{\sth}{\sin^2(2\theta_{23})}
+
+% Neutrinos
 \renewcommand{\ne}{\nu_e}
-\newcommand{\Ereco}{E^{R}}
-\newcommand{\Etrue}{E^{T}}
 \newcommand{\nm}{\nu_\mu}
@@
 \newcommand{\ant}{\bar\nu_\tau}
-\newcommand{\dm}{\Delta m^2_{31}}
-\newcommand{\sth}{\sin^2(2\theta_{23})}
 
+% Probabilities
 \newcommand{\Pee}{P_{e  e}}
@@
 
-\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
-\usepackage[utf8]{inputenc}
-\usepackage{hyperref}
 \begin{document}
-\section{Formalism of non-standard interactions}\label{sec:intro} %OK
+\section{Formalism of non-standard interactions}\label{sec:intro}
 Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
@@
 \begin{align}
-   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}
+   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}\,,
 \end{align}
-
+where $U$ is the PMNS matrix, $M^2$ the matrix containing matter-squared differences, and $n_f$ the fermion number density
+of fermion $f$.
 We have no independent sensitivity for the chirality of $\epsilon^{fX}$, so we sum over these to obtain the vectorial parameter as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
-Moreover, we normalize the fermion number density $n_f$ by
+Moreover, we normalize $n_f$ by
 the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
@@
 Thus, matter oscillations introduce a zenith angle dependence in two areas. Firstly, the matter potential depends on the matter density through the
-neutrino propagates. A neutrino with $\cos{\theta_z} < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
-with $\cos{\theta_z} > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
+neutrino propagates. A neutrino with indident zenith angle $\theta_z$ having $\z < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
+with $\z > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
 After this, we are ready to study the NSI effect on probability level.
 
-\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects} %OK
+\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
 % Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
@@
 % This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
-% (e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
+% (e.g. $\eem$ and $\Pmm$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
 % which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
@@
 
-The atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
+The atmospheric $\nm \to \nt$ transition is the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
 NSI parameters to constrain from muon events. As we will see, $\eem$ is also a good candidate to constrain, albeit a weaker one.
@@
 In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
-for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
+for neutrinos that traverse the entire Earth diameter (i.e. $\z = -1$). $\emt$ does not dramatically change neither
 amplitude nor frequency of the probabilities. Instead, it seems to stretch or compress the oscillations. Since the 
@@
 The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent
-constraint due to the weakness of the effect compared to $\emt$.
-
-Thus, we will use IceCube to constrain $\emt$ only.
+constraint due to the weakness of the effect compared to $\emt$. Thus, we will use IceCube to constrain $\emt$ only.
 
@@
 in the DeepCore region of rapid oscillations, where mixing is more violent. 
-\begin{figure}
+\begin{figure} %TODO: maybe add shaded region > 500 GeV to signify IC limit
     \begin{center}
-        \includegraphics[width=0.99\textwidth]{figures/Pmm_emt_probs.pdf}
-        \includegraphics[width=0.99\textwidth]{figures/Pmm_ett_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/Pmm_emt_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/Pmm_ett_probs.pdf}
         \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\emt = 0.02$.
+        $\z = -1$ when $\emt = 0.02$.
 All other NSI parameters are fixed to zero.
@@
         \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\ett = 0.05$.
+        $\z = -1$ when $\ett = 0.05$.
 All other NSI parameters are fixed to zero.
@@
 
-\begin{figure}
+\begin{figure} %TODO: maybe add shaded region > 500 GeV to signify IC limit
     \begin{center}
-        \includegraphics[width=0.99\textwidth]{figures/eem_probs.pdf}
-        \includegraphics[width=0.99\textwidth]{figures/eet_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/eem_probs.pdf}
+        \includegraphics[width=0.9\textwidth]{figures/eet_probs.pdf}
         \caption{Muon neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$.
+        $\z = -1$.
 \emph{Top panel:} $\eem = 0.2$.
@@
 
-\begin{figure}% TODO: check if this is redundant
-   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
-   \caption{}\label{fig:nsi_probs}
-\end{figure}
+%\begin{figure} %This one might be redundant with Fig 1 and 2
+%   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
+%   \caption{}\label{fig:nsi_probs}
+%\end{figure}
 
@@
     \begin{center}
-        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
+        \includegraphics[width=0.8\textwidth]{figures/Pee_eet_probs.pdf}
         \caption{Electron neutrino and antineutrino survival probabilities for
-        $\ztrue = -1$ when $\eet = 0.2$.
-All other NSI parameters are fixed to zero.
+        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. 
         Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{fig:eem_eet_probs}.}
@@
 $\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
-Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
+Subtract the regular $\Pme^{SI}$ (i.e, $\Pme$ under standard interactions), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
 The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
@@
     \centering
-    \includegraphics[width=1\textwidth]{figures/eem_eet_prob.pdf}
+    \includegraphics[width=0.99\textwidth]{figures/eem_eet_prob.pdf}
     \caption{The quantity $\abs{P_{\mu e}^{NSI} - P_{\mu e}^{SI}}$ when we let $\eem$ and $\eet$ independently vary over
-    the range \{-0.3,0.3\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
+    the range \{$-0.3$, $0.3$\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
     a promising indication that constriction of $\eem$ and $\eet$ is possible using cascade events at these energies.}\label{fig:eem_eet_prob}
@@
 \subsection{NSI phenomenology at flux level}\label{sec:nsiFluxEffects}
-To study the NSI flux effect, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
+To study the impact of NSI on the flux, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
 The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
@@
 DeepCore (IceCube) track events originating from $\nm + \anm$ fluxes are contained. We see that the only clear signal discernible to the IceCube detector
-is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
+is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\z < -0.87$. DeepCore on the other hand, 
 is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
@@
 
-\begin{figure}[!tb]
+\begin{figure}[!tb] %TODO: remove "true" in zenith x axis label?
    \begin{center}
-      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
+      \includegraphics[width=0.99\linewidth]{figures/flux_ratio.pdf}
    \end{center}
-   \caption{Ratio of detector NSI to SI atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes expressed as $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
-   We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
+   \caption{Ratio of atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes at detector level, expressed as the logarithm of $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
+   For the NSI fluxes $\phi^\text{NSI}$, we set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. For the SI fluxes $\phi^\text{SI}$, all $\epsilon_{\alpha\beta} = 0$.
    Left (right) panel shows the flux ratio in the energy range in which 99\% of the simulated DeepCore (IceCube) events are contained.
@@
 \begin{align}\label{eq:ICevents}
-    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
-    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
+    N_{ij} = T \sum_\beta &\int_{(\zreco)_i}^{(\zreco)_{i+1}} \dd \zreco \int_{\Ereco_{j}}^{\Ereco_{j+1}} \dd \Ereco \times \nonumber \\
+    \times &\int_0^\pi R(\treco,\ttrue) \dd \ztrue \int_0^\infty R(\Ereco,\Etrue) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd \Etrue
     \,,
 \end{align}
-where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\theta_z^r$ the reconstructed 
-zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle of the incoming neutrino. 
-$E^r$ is the reconstructed energy, binned with index $j$. $R(\theta^r,\theta^t)$ is a zenith resolution function 
+where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\treco$ the reconstructed 
+zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\ttrue$ is the true zenith angle of the incoming neutrino. 
+$\Ereco$ is the reconstructed energy, binned with index $j$. $R(\treco,\ttrue)$ is a zenith resolution function 
 that describes the relationship with the reconstructed and true zenith angles, specific to the 86-string configuration of IceCube.
-$R(E^r,E^t)$ is an energy resolution function 
-that describes the relationship with the reconstructed and true energies. $\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
+Similarily, $R(\Ereco,\Etrue)$ is the resolution function for the energy relationships.
+$\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
 in accordance with Eq.~\ref{eq:propFlux}. The effective area $A^\text{eff}$ is binned and provided to us by the IceCube collaboration~\cite{ICaeff}.
@@
 \begin{align}
-    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
+    R(\xreco, \xtrue) = \frac{1}{\sqrt{2\pi} \sigma_{\xreco}\xreco} \exp\left[-\frac{(\log \xreco-\mu(\xtrue))^2}{2\sigma_{\xreco}^2}\right]\,.
 \end{align}
@@
 At the reconstructed event level, we note that the $\emt$ features discussed in Sec.~\ref{sec:nsiFluxEffects} display themselves differently in each detector.
-We investigate this for $\emt$ by in Fig.~\ref{fig:Pmm_asymmetry} plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
 %TODO: check that this is what is plotted.
 $\epsilon^\pm_{\mu\tau} = \pm 0.01$.
-Comparing Fig.~\ref{fig:Pmm_asymmetry} with the flux ratios in Fig.~\ref{fig:emt_events}, we see that the reconstruction of PINGU is
+Comparing the probability difference in Fig.~\ref{fig:Pmm_asymmetry} with the binned event count ratio in Fig.~\ref{fig:emt_events}, we see that the reconstruction of PINGU is
 superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})} = \log{N^+_{NSI}} - \log{N^-_{NSI}}$ (in reconstructed quantities) 
@@
 
-Now we turn to the effect of $\emt$. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ in this way to explain the $\emt$ features. 
-First, let $P^\pm$ denote $P_{\mu\mu}(\epsilon^\pm_{\mu\tau})$. 
-We see see that $\emt^+$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
-while $\emt^-$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
-is indeed preserved at flux level. So the flux for $\emt^+$ is higher than the flux for $\emt^-$. Is this still true at event level, i.e. after reconstruction? 
+Now we turn to the effect of $\emt$. %Muon events are the most abundant, and it suffices to study $\Pmm$ in this way to explain the $\emt$ features. 
 As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, which will give a high statistics on both sides of $\emt=0$, slightly favoring $\emt^-$.
@@
 giving weaker statistics for the negative side. Thus, we conclude that we will see a $\emt$ \si{GeV}-asymmetry stemming from the lower statistics 
-for negative $\emt$ at probability level, which is then propagated through the flux and finally affects the reconstruction. %TODO: fill more conclusion?
+for negative $\emt$ at probability level, which finally affects the reconstruction.
 
-\begin{figure}
-   \begin{subfigure}{0.25\textwidth}   
-      \includegraphics[width=1\linewidth]{figures/Pmm_asymmetry.pdf}%TODO: redo for emt=0.01x
-      \caption{$P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.01$}\label{fig:Pmm_asymmetry}
+\begin{figure} % TODO: replace true -> T in labels
+   \begin{subfigure}{1\textwidth}
+      \begin{center}
+      \includegraphics[width=0.5\linewidth]{figures/Pmm_asymmetry.pdf}
+      \caption{$\Pmm(\emt^+) - \Pmm(\emt^-)$ using  $\emt^\pm = \pm 0.01$}\label{fig:Pmm_asymmetry}
+      \end{center}
    \end{subfigure}
-   \begin{subfigure}{0.6\textwidth}
+   \qquad
+   \begin{subfigure}{0.99\textwidth}
       \includegraphics[width=1\linewidth]{figures/emt_events.pdf}
    \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$. IceCube only observes a small surplus of events for $\emt=-0.01$ compared to 
-   DeepCore and PINGU due to the weak NSI effect at high \si{\GeV} energies.}\label{fig:emt_events}%TODO: improve caption?
+   DeepCore and PINGU due to the weak NSI effect at high \si{\GeV} energies.}\label{fig:emt_events}
    \end{subfigure}
@@
     \begin{center}
-       \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
+       \includegraphics[width = 0.7\textwidth]{figures/joint_3D_NO.pdf}
        \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon.
@@
     \begin{center} 
-       \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
+       \includegraphics[width=0.5\textwidth]{figures/PID_3D_emt.pdf}
        \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
@@
     \end{tabular}
+    \vspace{1em}
     \begin{tabular}{lcc}
@@
  \begin{figure}
-    \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
+    \centering
+    \includegraphics[width=\textwidth]{figures/PINGU_2D_all_f0.pdf}
     \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
@@
 
-\newpage
-\begin{tabular}{p{55mm}p{55mm}p{55mm}}
-   DeepCore (2017)
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\times$] Only look at tracks and $\emt$
-         \vspace{1em}  
-         \item[$\times$] DC Monte Carlo from an older dataset 
-         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\times$] 8 z bins from -1 to 0 
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
-      \end{itemize} &
-    Demidov (2020) DC analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
-         \item[$\checkmark$] Data and Monte Carlo from DC 2018
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 z bins from -1 to 1
-         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
-         \item[$\times$] Prior on spectral index
-         \item[$\times$] No zenith angle normalization
-         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
-         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
-         \item[$\times$] Uncertainty on hadron production in atmosphere
-         \item[$\times$] Uncertainty on neutrino nucleon cross section 
-      \end{itemize} &
-    This DC+PINGU analysis
-      \begin{itemize}
-         \item[$\checkmark$] Honda atmospheric fluxes
-         \item[$\checkmark$] Tracks and cascades for all flavors
-         \vspace{1em} 
-         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
-         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
-         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
-         \item[$\checkmark$] Flux normalization uncertainty of 25\%
-         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
-         \item[$\checkmark$] No priors on oscillation parameters 
-         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
-      \end{itemize} 
-\end{tabular}
+%\newpage
+%\begin{tabular}{p{55mm}p{55mm}p{55mm}}
+%    DeepCore (2017)
+%       \begin{itemize}
+%          \item[$\checkmark$] Honda atmospheric fluxes
+%          \item[$\times$] Only look at tracks and $\emt$
+%          \vspace{1em}  
+%          \item[$\times$] DC Monte Carlo from an older dataset 
+%          \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+%          \item[$\times$] 8 z bins from -1 to 0 
+%          \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
+%          \item[$\times$] Prior on spectral index
+%          \item[$\times$] No zenith angle normalization
+%          \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
+%       \end{itemize} &
+%     Demidov (2020) DC analysis
+%       \begin{itemize}
+%          \item[$\checkmark$] Honda atmospheric fluxes
+%          \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
+%          \item[$\checkmark$] Data and Monte Carlo from DC 2018
+%          \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
+%          \item[$\checkmark$] 8 z bins from -1 to 1
+%          \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
+%          \item[$\times$] Prior on spectral index
+%          \item[$\times$] No zenith angle normalization
+%          \item[$\checkmark$] No priors on $\dm, \theta_{23}$
+%          \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
+%          \item[$\times$] Uncertainty on hadron production in atmosphere
+%          \item[$\times$] Uncertainty on neutrino nucleon cross section 
+%       \end{itemize} &
+%     This DC+PINGU analysis
+%       \begin{itemize}
+%          \item[$\checkmark$] Honda atmospheric fluxes
+%          \item[$\checkmark$] Tracks and cascades for all flavors
+%          \vspace{1em} 
+%          \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
+%          \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
+%          \item[$\checkmark$] 8 zenith angle bins from -1 to 1
+%          \item[$\checkmark$] Flux normalization uncertainty of 25\%
+%          \item[$\checkmark$] Zenith angle uncertainty of 4\% 
+%          \item[$\checkmark$] No priors on oscillation parameters 
+%          \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
+%       \end{itemize} 
+% \end{tabular}
 \end{document}
